### 2023-12-26 apples_and_oranges.qmd
script for metanalysis added

---
title: Fundamental Problems with the Evidence Base for Adolescent Depression Treatments.
subtitle: A conceptual and quantiative re-appraisal.
author:
  - name: Argyris Stringaris
    email: a.stringaris@ucl.ac.uk
    affiliations: 
        - id: ucl_1
          name: University College London
          department: Divisions of Psychiatry and Psychology and Language Science
          address: 1-19 Torrington Place
          city: London, UK
          state: 
          postal-code: WC1E 7HB
          country: United Kingdom
    attributes:
        corresponding: true
    note: 
  - name: Charlotte Burman
    email: c.burman@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Dayna Bhudia
    email: d.bhudia@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note:
  - name: Carmen Moreno
    email: cmoreno@hggm.es
    affiliations:
        - id: HGM
          name: Hospital Gregorio Marañón
          department: Department of Psychiatry
          address: 46 C. del Dr. Esquerdo
          city: Madrid
          state:
          postal-code: 28007
          country: Spain
  - name: Samuele Cortese
    email: samuele.cortese@soton.ac.uk
    affiliations:
        - id: soton
          name: University of Southampton
          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
          address: Highfield Campus, Building 44
          city: Southampton
          state:
          postal-code: SO17 1BJ
          country: United Kingdom
  - name: Georgina Krebs
    email: g.krebs@ucl.ac.uk
    affiliations:
        - ref: ucl_1
    note: 
abstract: |
  To follow
keywords: 
  - depression
  - adolescents
  - antidepressants
  - psychotherapy
date: last-modified
bibliography: emotion_concepts_paper.bib
format: 
  elsevier-pdf:
    keep-tex: true
    journal:
      name: Journal Name
      formatting: preprint
      model: 3p
      cite-style: super
---

# Introduction

Depression is the leading cause of disability in adolescents and influential guidelines recommend that it be treated with either psychotherapy or anti-depressant medication or their combination. The evidence base for this recommendation typically derives from the appraisal of randomised controlled trials (RCTs) in which one modality (psychotherapy or anti-depressants) are compared against a control condition. In this paper we identify a series of fundamental problems with this appraisal and make recommendations on how it can be improved.

Guidelines make implicit and explicit ... comparisons...

Network metanalyses...

Jureidini approach...summarises.

This state of affairs is reflected in textbooks and also in what trainees in psychiatry and psychology learn QUOTE.

Yet, is this approach correct?

This approach relies on a (explicit or more often implicit) comparison of the two treatment modalities. Ideally, a comparison between the treatment modalities should be direct, that is head to head. Only one such trial exists in adolescent depression (from the TADS study, see below) which showed that fluoxetine was superior to both cognitive and behavioural therapy (CBT) as well as placebo, and that CBT did not differentiate from placebo. Apart from this one study, all other comparisons indirect, that is, they have to be inferred from comparing studies where an antidepressant or a psychotherapy is compared to a control condition; the control conditions for antidepressant studies is the placebo (standard also in the rest of medicine), whilst controls for psychotherapy studies can vary substantially from waiting list, to treatment as usual to an attention control, such as psychoeducation. These comparisons therefore have to rely on testing whether the following simple equality holds or not,

$$Effect_{Med} = Effect_{Psy}$$ {#eq-1}

where *Effect* denotes the effect on depression that either medication (*Med* ) or psychotherapy (*Psy*) have. This comparison is achieved by comparing some measure of effect, e.g. percentage response or standardised mean difference, for each medication and psychotherapy. The simplest way of doing such a comparison is to take pooled estimates of such effects from metanalyses of each anti-depressants and psychotherapy and compare them informally. A more formal way of doing this is through a network metanalysis, which uses any direct comparisons to infer indirect ones.

Yet for the indirect comparison to be valid, several assumptions need to hold. The most important of these assumptions can be summarised using the technical term *ceteris paribus*, meaning that the results of this comparison are valid if all else is equal. Two important such assumptions are: a) that the control conditions for each antidepressant and psychotherapy trials are equal—we call this the *equality of controls* assumption. b) that the effects of each treatment modality have been derived from the same underlying population, that is that the people who have received the treatment are similar on important parameters on average–this we call the *one population* assumption.

Starting with the *equality of controls*, its importance can be easily intuited by expanding equation 1 to include the comparisons on which each side of that equation rests:

$$Effect_{MedActive} - Effect_{MedControls} = Effect_{PsyActive} - Effect_{PsyControls}$$ {#eq-2}

where MedActive and PsyActive are the active arms of antidepressant and psychotherapy trials, respectively, and MedControls and PsyControls the respective control arms. The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$. A few simple examples help illustrate why this assumption is important Let the two modalities of treatment be medication and surgery, and let there be a trial for each modality. In the medication trial 80% of participants respond to the antihypertensive and only 40% to placebo; in the surgery trial, 40% of people respond to surgery and 0% to sham. If one relied on Equation 1 to compare the treatments they would arrive at the absurd conclusion that the two treatments are equal and recommend to a patient that it does not really matter which one they choose. Playing around with numbers in which no equality of the respective control arms is required, leads to other risible conclusions.

Yet, surprisingly, a focus on the equality of controls is largely absent from appraisals of the evidence of medication and psychotherapy.

Moving on to the *one population* assumption, this can be formalised

@stringarisDevelopmentalPathwaysChildhood2014

# Figures and tables

![Forest Plot of Control Arms by the Control Arm of Each Treatment Modality.](forestplot.png){fig-align="left" width="1200"}

```         
```

# Tables coming from RTable

```{r}
#| label: tbl-simple
#| tbl-cap: Caption centered above table
#| echo: true
knitr::kable(head(mtcars)[,1:4])
```

#

### 2023-12-26 elsevier/CopyOfelsevier.tex
script for metanalysis added

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  super,
  preprint,
  3p]{elsarticle}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{241,243,245}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.40,0.45,0.13}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\BuiltInTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\ExtensionTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.28,0.35,0.67}{#1}}
\newcommand{\ImportTok}[1]{\textcolor[rgb]{0.00,0.46,0.62}{#1}}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\NormalTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.68,0.00,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{\textcolor[rgb]{0.00,0.23,0.31}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.07,0.07,0.07}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.13,0.47,0.30}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.37,0.37,0.37}{\textit{#1}}}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\journal{Journal Name}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage[]{natbib}
\bibliographystyle{elsarticle-num}
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Short Paper},
  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
  pdfkeywords={keyword1, keyword2},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\setlength{\parindent}{6pt}
\begin{document}

\begin{frontmatter}
\title{Short Paper \\\large{A Short Subtitle} }
\author[1]{Alice Anonymous%
\corref{cor1}%
\fnref{fn1}}
 \ead{alice@example.com} 
\author[2]{Bob Security%
%
\fnref{fn2}}
 \ead{bob@example.com} 
\author[2]{Cat Memes%
%
\fnref{fn3}}
 \ead{cat@example.com} 
\author[]{Derek Zoolander%
%
}
 \ead{derek@example.com}

\affiliation[1]{organization={Some Institute of Technology, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}
\affiliation[2]{organization={Another University, Department
Name},addressline={Street Address},city={City},postcode={Postal
Code},postcodesep={}}

\cortext[cor1]{Corresponding author}
\fntext[fn1]{This is the first author footnote.}
\fntext[fn2]{Another author footnote, this is a very long footnote and
it should be a really long footnote. But this footnote is not yet
sufficiently long enough to make two lines of footnote text.}
\fntext[fn3]{Yet another author footnote.}

\begin{abstract}
This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
tempus elit.
\end{abstract}

\begin{keyword}
    keyword1 \sep 
    keyword2
\end{keyword}
\end{frontmatter}
    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi

Please make sure that your manuscript follows the guidelines in the
Guide for Authors of the relevant journal. It is not necessary to
typeset your manuscript in exactly the same way as an article, unless
you are submitting to a camera-ready copy (CRC) journal.

For detailed instructions regarding the elsevier article class, see
\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}

\hypertarget{bibliography-styles}{%
\section{Bibliography styles}\label{bibliography-styles}}

Here are two sample references: \citet{Feynman1963118}
\citet{Dirac1953888}.

By default, natbib will be used with the \texttt{authoryear} style, set
in \texttt{classoption} variable in YAML. You can sets extra options
with \texttt{natbiboptions} variable in YAML header. Example

\begin{verbatim}
natbiboptions: longnamesfirst,angle,semicolon
\end{verbatim}

There are various more specific bibliography styles available at
\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
To use one of these, add it in the header using, for example,
\texttt{biblio-style:\ model1-num-names}.

\hypertarget{using-csl}{%
\subsection{Using CSL}\label{using-csl}}

If \texttt{cite-method} is set to \texttt{citeproc} in
\texttt{elsevier\_article()}, then pandoc is used for citations instead
of \texttt{natbib}. In this case, the \texttt{csl} option is used to
format the references. By default, this template will provide an
appropriate style, but alternative \texttt{csl} files are available from
\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
and stored locally, or the url can be used as in the example header.

\hypertarget{equations}{%
\section{Equations}\label{equations}}

Here is an equation: \[ 
  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
  \left(\frac{x}{\beta}\right)^{\alpha-1}
  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
  \alpha,\beta,x > 0 .
\]

Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)

\hypertarget{figures-and-tables}{%
\section{Figures and tables}\label{figures-and-tables}}

Figure~\ref{fig-meaningless} is generated using an R chunk.

\begin{figure}

{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{elsevier_files/figure-pdf/fig-meaningless-1.pdf}

}

\caption{\label{fig-meaningless}A meaningless scatterplot}

\end{figure}

\hypertarget{tables-coming-from-r}{%
\section{Tables coming from R}\label{tables-coming-from-r}}

Tables can also be generated using R chunks, as shown in
Table~\ref{tbl-simple} example.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{knitr}\SpecialCharTok{::}\FunctionTok{kable}\NormalTok{(}\FunctionTok{head}\NormalTok{(mtcars)[,}\DecValTok{1}\SpecialCharTok{:}\DecValTok{4}\NormalTok{])}
\end{Highlighting}
\end{Shaded}

\hypertarget{tbl-simple}{}
\begin{longtable}[]{@{}lrrrr@{}}
\caption{\label{tbl-simple}Caption centered above table}\tabularnewline
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
& mpg & cyl & disp & hp \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Mazda RX4 & 21.0 & 6 & 160 & 110 \\
Mazda RX4 Wag & 21.0 & 6 & 160 & 110 \\
Datsun 710 & 22.8 & 4 & 108 & 93 \\
Hornet 4 Drive & 21.4 & 6 & 258 & 110 \\
Hornet Sportabout & 18.7 & 8 & 360 & 175 \\
Valiant & 18.1 & 6 & 225 & 105 \\
\end{longtable}

\renewcommand\refname{References}
  \bibliography{bibliography.bib}

\end{document}

### 2023-12-26 Script for cleaning merged dataset.R

@@ -344,15 +344,15 @@ columns_to_check <- c(
   "post_mean_control", "post_sd_control"
 )
 
-# Identify which columns have missing values for each study
+# Idemissing values for each study
+tapply(print(columns_with_missing_values[,1:2]
+), columns_with_missing_values$psy_or_med)
+#identify which columns have missing values for each study
 columns_with_missing_values <- df_appl_v_orange %>%
   filter(rowSums(is.na(.[columns_to_check])) > 0) %>%
   select(psy_or_med, study, year, where(function(x) any(is.na(x))))
 
-# Print columns with missing values for each study
-tapply(print(columns_with_missing_values[,1:2]
-), columns_with_missing_values$psy_or_med)
-
+# Print columns with 
 # create excel sheet to edit
 # we have created a notes column named how_handle_es_calc where we inspect each study and its missing data
 # from there we work out which method to use to impute / derive an appropriate value to substitute missing values
@@ -678,17 +678,20 @@ studies_w_complete_sds <- df_appl_v_orange %>%
 # We only have this for one study. Hence we decided to stick with cohens d for now and perform the imputations above.
 
 
-####### Argyris additions aide memoire
+####### Argyris additions aide memoir
 test <- df_appl_v_orange  %>% 
   group_by(study_ID) %>% 
   filter(instrument_value == min(instrument_value)) %>% 
   group_by(psy_or_med) %>% 
-  summarise(av_cohens_d_ctrl = mean(cohens_d_control, na.rm = T), sd_cohens_d_ctrl = sd(cohens_d_control, na.rm = T))
+  summarise(av_cohens_d_ctrl = mean(cohens_d_control, na.rm = T), sd_cohens_d_ctrl = sd(cohens_d_control, na.rm = T),
+            av_cohens_d_actuve = mean(cohens_d_active, na.rm = T), sd_cohens_d_active = sd(cohens_d_active, na.rm = T))
+
+test
 
 # create new id
 test <- df_appl_v_orange  %>% 
   mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                        .default = study )) #case_when(psy_or_med == 1 ~ study))
+                        .default = study )) 
 
 
 
[…]

### 2023-12-27 Script for cleaning merged dataset.R
lots of new code and plots

@@ -344,15 +344,17 @@ columns_to_check <- c(
   "post_mean_control", "post_sd_control"
 )
 
-# Idemissing values for each study
-tapply(print(columns_with_missing_values[,1:2]
-), columns_with_missing_values$psy_or_med)
-#identify which columns have missing values for each study
+
+# Identify which columns have missing values for each study
 columns_with_missing_values <- df_appl_v_orange %>%
   filter(rowSums(is.na(.[columns_to_check])) > 0) %>%
   select(psy_or_med, study, year, where(function(x) any(is.na(x))))
 
-# Print columns with 
+# Print columns with missing values for each study THROWS UP ERROR TOLD CHARLOTTE
+# tapply(print(columns_with_missing_values[,1:2]
+# ), columns_with_missing_values$psy_or_med)
+
+
 # create excel sheet to edit
 # we have created a notes column named how_handle_es_calc where we inspect each study and its missing data
 # from there we work out which method to use to impute / derive an appropriate value to substitute missing values
@@ -457,7 +459,7 @@ new_columns_with_missing_values <- df_first_row %>%
   filter(rowSums(is.na(.[columns_to_check])) > 0) %>%
   filter(psy_or_med == 0) %>% 
   select(study, year, active_type, instrument_name, where(function(x) any(is.na(x))))
-tapply(print(new_columns_with_missing_values[,1:2]), new_columns_with_missing_values$psy_or_med)
+###tapply(print(new_columns_with_missing_values[,1:2]), new_columns_with_missing_values$psy_or_med) THROWS UP ERROR TOO
 openxlsx:: write.xlsx(new_columns_with_missing_values, file = "new_columns_with_missing_values.xlsx", colNames = T, borders = "columns", asTable = F)
 
 # For studies missing all sds, we will sub in an average SD taken from similar studies in the dataset. We will calculate average SDs for each arm, pre and post.
@@ -678,92 +680,1131 @@ studies_w_complete_sds <- df_appl_v_orange %>%
 # We only have this for one study. Hence we decided to stick with cohens d for now and perform the imputations above.
 
 
+############IGNORE from HERE to line 976
+
 ####### Argyris additions aide memoir
[…]

### 2023-12-31 Script for cleaning merged dataset.R
lots of changes

@@ -978,7 +978,7 @@ studies_w_complete_sds <- df_appl_v_orange %>%
 
 # Start here------------------------------------------------------
 
-#Need to use SMD, ie our Cohen's d and then use Standard error of SMD, to achieve this
+#Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
 # I need reliabilities.
 
 # note re: CDRS reliability from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
@@ -1541,7 +1541,7 @@ q2 = (n2-1)*var(x2, na.rm = T) + n2*mean(x2, na.rm = T)^2 # helps avoid sums and
 
 qc = q1 + q2
 
-combined_sd = sqrt( (qc - (n1+n2)*mean(total_sample, na.rm = T)^2)/(n1+n2-1) )
+# combined_sd = sqrt( (qc - (n1+n2)*mean(total_sample, na.rm = T)^2)/(n1+n2-1) )
 
 combined_sd  == sd(total_sample, na.rm = T) # checked it works
 
@@ -1758,53 +1758,1239 @@ update.meta(perc_women,
 
 # 3. metaregression.
 
-df_for_metareg <- 
-  df_appl_v_orange %>%  
-  dplyr:: select(new_study_id, treatment_allocation, cohens_d_control, cohens_d_active, se_change_control_0.7, 
-                 se_change_active_0.7 ) %>% 
-  pivot_longer(c(cohens_d_control, cohens_d_active, se_change_control_0.7, 
-               se_change_active_0.7), names_to = c("control", "active") , names_sep = "_", values_to = c("cohens_d", "se_change") )
+# create dataframes for metareg -------------------------------------------
 
+### We need to create dataframes for the metaregressions across the various SEs.
+### These need to be long data frames, so that we can test the treatment arm by psy_or_med allocation.
 
-df_for_metareg <- 
+# get the Cohen's ds into long format.
+
+df_for_cohens_d <- 
   df_appl_v_orange %>%  
   dplyr:: select(new_study_id, psy_or_med, cohens_d_control, cohens_d_active) %>% 
   pivot_longer(cols = c(cohens_d_control, cohens_d_active), 
-               names_to = "arm", 
+               names_to = "arm_effect_size", 
                values_to = "cohens_d") 
 
-df_for_metareg_2 <- 
+## now to the various steps for obtaining the different standard errors 
+
[…]

### 2023-12-31 Script for cleaning merged dataset.R
new plot

@@ -2808,34 +2808,41 @@ library(ggplot2)
 # Make sure to replace the column names accordingly
 
 # Calculate the size based on the difference between lower and upper
-statistics_indiv_metan$size <- statistics_indiv_metan$upper_random - statistics_indiv_metan$lower_random
-
-# Create ggplot
-ggplot(statistics_indiv_metan, aes(x = TE_random, y = c(1, 2, 3, 4))) +
-  geom_point(aes(size = size), shape = 18, position = position_stack(vjust = 0.5)) +
-  theme_minimal() +  # Adjust the theme as needed
-  scale_size_continuous(range = c(2, 8)) +  # Adjust the size range as needed
-  labs(x = "TE-random", y = NULL, title = "Stacked Diamond-shaped Objects for TE-random with Confidence Intervals")
 
 
-library(ggplot2)
-
+# Create ggplot with points and error bars
 # Assuming statistics_indiv_metan is your dataframe
 # Make sure to replace the column names accordingly
 
 # Example data (replace with your actual data)
-statistics_indiv_metan <- data.frame(
-  TE_random = c(0.2, 0.4, 0.6, 0.8),
-  lower_random = c(0.1, 0.3, 0.5, 0.7),
-  upper_random = c(0.3, 0.5, 0.7, 0.9)
+statistics_indiv_metan$text_label <-  c(
+  paste(statistics_indiv_metan$condition[1],"\n","k = ", statistics_indiv_metan$k_study[1],"\n", "tau2 = ", round(statistics_indiv_metan$tau2[1],2) ), 
+   
+  paste(statistics_indiv_metan$condition[2],"\n","k = ", statistics_indiv_metan$k_study[2],"\n", "tau2 = ", round(statistics_indiv_metan$tau2[2],2) ), 
+  
+  paste(statistics_indiv_metan$condition[3],"\n","k = ", statistics_indiv_metan$k_study[3],"\n", "tau2 = ", round(statistics_indiv_metan$tau2[3],2) ), 
+   
+  paste(statistics_indiv_metan$condition[4],"\n","k = ", statistics_indiv_metan$k_study[4],"\n", "tau2 = ", round(statistics_indiv_metan$tau2[4],2) ) 
 )
 
+
+
 # Create ggplot with points and error bars
-ggplot(statistics_indiv_metan, aes(x = TE_random, y = c(1:4) )) +
[…]

### 2024-01-01 apples_and_oranges.qmd
changes to script and quarto expansion

@@
 ---
-title: Fundamental Problems with the Evidence Base for Adolescent Depression Treatments.
-subtitle: A conceptual and quantiative re-appraisal.
+title: Apples and Oranges in Adolescent Depression Treatments.
+subtitle: A conceptual and quantiative re-appraisal of control arms in clinical trials.
 author:
@@
 The evidence base for this recommendation typically derives from the appraisal of randomised controlled trials (RCTs) in which one modality (psychotherapy or anti-depressants) are compared against a control condition.
-In this paper we identify a series of fundamental problems with this appraisal and make recommendations on how it can be improved.
+In this paper we: a) test the hypothesis that medication control arms are more efficacious than psychotherapy control arms and that this undermines the validity of treatment comparisons and therefore of existing guidelines about depression treatment; b) explore how variation in treatment control arms can itself be exploited to advance our thinking concerning the mechanisms of depression and its treatment.
 
-Guidelines make implicit and explicit ... comparisons...
+Clinicians across medicine and other health professions are faced with choices betweent different treatment modalities for their patients, be it between surgical or medical (drug-based) treatments or, in the case of adolescent depression, between psychotherapy and antidepressant medication.
+To make informed choices, clinicians rely on the extant evidence, frequently summarised in the form of national guidelines or other treatment recommendations.
+Such a comparison is inherent in the internationally influential UK National Institute of Clinical Excellence (NICE) guidelines for adolescent depression which recommend that youth be first offered psychological therapy over medication for most presentations of depression.
+Such comparisons between the etwo treatment modalities are inherent in other recommendations, e.g.
+the practice parameter issued by the American Academy of Child and Adolescent Psychiatry or the Royal Australian and New Zealand College of Psychiatrists.
 
-Network metanalyses...
+These recommendations are not based on head to head trials between modalities; only one head-to-head trial exists in adolescent depression Instead, they rely on the comparison of the results of randomised controlled trials (RCTs) of each modality against RCTs of the other.
+In other words, it rests on a comparison of comparisons.
 
-Jureidini approach...summarises.
-
-This state of affairs is reflected in textbooks and also in what trainees in psychiatry and psychology learn QUOTE.
-
-Yet, is this approach correct?
-
-This approach relies on a (explicit or more often implicit) comparison of the two treatment modalities.
-Ideally, a comparison between the treatment modalities should be direct, that is head to head.
-Only one such trial exists in adolescent depression (from the TADS study, see below) which showed that fluoxetine was superior to both cognitive and behavioural therapy (CBT) as well as placebo, and that CBT did not differentiate from placebo.
-Apart from this one study, all other comparisons indirect, that is, they have to be inferred from comparing studies where an antidepressant or a psychotherapy is compared to a control condition; the control conditions for antidepressant studies is the placebo (standard also in the rest of medicine), whilst controls for psychotherapy studies can vary substantially from waiting list, to treatment as usual to an attention control, such as psychoeducation.
-These comparisons therefore have to rely on testing whether the following simple equality holds or not,
+In the case of antidepressant studies, the control is the placebo pill (standard also in the rest of medicine), whilst controls for psychotherapy studies can vary substantially from waiting list to treatment as usual to an attention control, such as psychoeducation.
+Stated in simple formal terms, the comparison relies on testing this equality,
 
@@
 where *Effect* denotes the effect on depression that either medication (*Med* ) or psychotherapy (*Psy*) have.
-This comparison is achieved by comparing some measure of effect, e.g.
-percentage response or standardised mean difference, for each medication and psychotherapy.
-The simplest way of doing such a comparison is to take pooled estimates of such effects from metanalyses of each anti-depressants and psychotherapy and compare them informally.
-A more formal way of doing this is through a network metanalysis, which uses any direct comparisons to infer indirect ones.
+Yet for this indirect comparison to be valid, some basic assumptions need to hold.
+The most important of these is the *all-else-being-equal,* or more technically *ceteris paribus,* assumption with regards to trial design.
+By necessity, therefore, the control conditions for each antidepressant and psychotherapy trials must be equal for inferences to be valid.
+We call this the *equality of controls* assumption.
 
-Yet for the indirect comparison to be valid, several assumptions need to hold.
-The most important of these assumptions can be summarised using the technical term *ceteris paribus*, meaning that the results of this comparison are valid if all else is equal.
-Two important such assumptions are: a) that the control conditions for each antidepressant and psychotherapy trials are equal—we call this the *equality of controls* assumption.
-b) that the effects of each treatment modality have been derived from the same underlying population, that is that the people who have received the treatment are similar on important parameters on average–this we call the *one population* assumption.
-
-Starting with the *equality of controls*, its importance can be easily intuited by expanding equation 1 to include the comparisons on which each side of that equation rests:
+The importance of this assumption can be easily intuited by expanding equation 1 to include the comparisons on which each side of that equation rests:
 
@@
 where MedActive and PsyActive are the active arms of antidepressant and psychotherapy trials, respectively, and MedControls and PsyControls the respective control arms.
-The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$.
-A few simple examples help illustrate why this assumption is important Let the two modalities of treatment be medication and surgery, and let there be a trial for each modality.
+The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$ A few simple examples help illustrate why this assumption is important Let the two modalities of treatment be medication and surgery, and let there be a trial for each modality.
 In the medication trial 80% of participants respond to the antihypertensive and only 40% to placebo; in the surgery trial, 40% of people respond to surgery and 0% to sham.
@@
 Playing around with numbers in which no equality of the respective control arms is required, leads to other risible conclusions.
+Yet, a focus on the equality of controls is surprisingly absent.
 
-Yet, surprisingly, a focus on the equality of controls is largely absent from appraisals of the evidence of medication and psychotherapy.
+The importance of testing the equality of controls assumption for patients and the public can be vast because treatment guidelines, clinician's advice to patients, and patients' informed choices are all affected by the validity of treatment comparisons.
+Similarly, the rational allocation of public funds towards treatment modalities rests on valid comparisons between them.
 
-Moving on to the *one population* assumption, this can be formalised
+Beyond its immediate clinical importance, understanding the nature of controls in clinical trials of depression is key for reasons of causal inference and mechanistic understanding of treatment.
+Adolescent depression is notable for a relatively high placebo effect: the proportion of adolescents responding to placebo is higher in depression than in anxiety, and it is higher for adolescent vs adult depression.
+The reasons for these differences remain unclear and are typically treated as nuisance effects to be minimised by using trial designs such as a placebo lead in period.
+However, an alternative view is that placebo effects, or more generally, variability in the response to control arms may be informative about mechanisms of improvement.
+If, for example, the antidepressant effect of placebo is stronger than that of equivalent control arms in psychotherapy, then we ought to ask about the possible explanations of such differences and consider whether they can be exploited for improving treatment delivery, as previously suggested.
+
+In this paper, we have two aims: first, test whether the equality of controls assumption of adolescent depression treatment holds, and therefore scrutinise the validity of current recommendations concerning choice between treatment modalities; second,we explore variabiliity in trial control arms across and within the two treatment modalities and examine how they relate to anti-depressant effects.
+
+Our main hypothesis is that the within group effect of psychotherapy controls is substantially weaker than that of the placebo pill and we will test this in random effects meta-regression.
+We will also use series of sensitivity analyses concerning restricting to specific psychotherapy control groups ( e.g.
+exclude waitlist controls or include only controls to cognitive and behavioural therapy (CBT)) or medication control groups (e.g.
+trials for the FDA-approved fluoxetine and escitalopram).
+We also conduct sensitivity analyses in the form of simulations, to ensure that results are robust to estimations of the standard error of the change scores.
+
+We then go on to examine the control arms of psychological treatments in both a qualitative/descriptive way (e.g.
+the content of attention control) and by quantifying characteristics such as session frequency, duration of delivery.
+We then explore how these characteristics relate to the magnitude of within group change.
 
@@
 
-# Figures and tables
+# Results
 
-![Forest Plot of Control Arms by the Control Arm of Each Treatment Modality.](forestplot.png){fig-align="left" width="1200"}
+The data for the studies included in this metanalysis are summarised in Supplementary Table 1 and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+library(tidyverse)
+df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")
+
+# describe studies
+n_unique_studies <- length(unique(df_long_for_metan$new_study_id))
+
+df_count_studies <- df_long_for_metan %>% 
+  group_by(psy_or_med, arm_effect_size) %>% 
+  count(is.na(cohens_d))
+
+df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)
+
+df_count_studies <-
+  df_count_studies %>% 
+  mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                             psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                             psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                             psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+  )
 
 ```
-```
 
-# Tables coming from RTable
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies of which `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` belonged to active and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` to control arms of antidepressant trials; there were also `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` psychotherapy active and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` trials.
+Note that active and control arms do not exactly match because some studies used more than one control or active arm.
+There were also missing data on `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms where data were missing for medication active, mediaction contrl, psychotherapy active, and psychotherapy control respectively.
 
-```{r}
-#| label: tbl-simple
-#| tbl-cap: Caption centered above table
-#| echo: true
-knitr::kable(head(mtcars)[,1:4])
-```
-
-#
+In order to conduct a met

### 2024-01-01 Script for cleaning merged dataset.R

@@ -974,1313 +974,7 @@ studies_w_complete_sds <- df_appl_v_orange %>%
 # 
 # 
 # 
-############IGNORE UP TO HERE
 
-# Start here------------------------------------------------------
-
-#Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
-# I need reliabilities.
-
-# note re: CDRS reliability from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
-# Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
-# Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
-# for the CDRS-R total score in 53 clinic-referred6- to 12-year-olds.
-
-
-# this is a loop that creates SEs for various test-retest correlation coefficients
-
-# the formula for the calculation of the standard error
-# comes from here: https://bookdown.org/MathiasHarrer/Doing_Meta_Analysis_in_R/effects.html#s-md
-
-range_test_retest_corr <- seq(0.5, 0.9, by =0.1)
-list_SE_active <- list()
-list_SE_control <- list()
-for (i in 1: length(range_test_retest_corr)){
-
-  list_SE_active[[i]] <- sqrt(((2*(1-range_test_retest_corr[i]))/df_appl_v_orange$baseline_n_active) + 
-                                      ( df_appl_v_orange$cohens_d_active^2/(2*df_appl_v_orange$baseline_n_active)))
-  
-  list_SE_control[[i]] <- sqrt(((2*(1-range_test_retest_corr[i]))/df_appl_v_orange$baseline_n_control) + 
-                                ( df_appl_v_orange$cohens_d_control^2/(2*df_appl_v_orange$baseline_n_control)))
-  
-  
-}
-
-df_ses <- do.call("cbind", c(list_SE_active, list_SE_control))
-colnames(df_ses) <- c(paste0("se_change_active_",range_test_retest_corr ), paste0("se_change_control_",range_test_retest_corr ))
-df_appl_v_orange <-  cbind(df_appl_v_orange, df_ses )
-
-
-### A few more tidying things from Argyris before doing metanalyses
-# # discovered an error in the percentage women o fthe Fristad study. I have checked in the
-# # cuijpers dataset and the correct percentage is 43.1, but could not verify with the paper as it is not in 
[…]

### 2024-01-03 Script for cleaning merged dataset.R
new metaregressions

@@ -1145,7 +1145,7 @@ df_count_studies <-
 
 df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n
 
-
+df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
 
 
 # Generate simulations of standard errors ---------------------------------
@@ -1212,8 +1212,182 @@ list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_
 summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
 
 
-### Now run the metaregressions.
 
+# Run metaregression ------------------------------------------------------
+library(metafor)
+# add a new multilevel variable for the regression
+
+for(i in 1: length(list_df_simulated)){
+  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+  
+  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
+  
+  # relevel so that medication control becomes the reference category for the regression
+  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+}
+
+
+# check it worked
+# list_df_simulated[[2]] %>% 
+#   dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
+
+
+
+# specify the model 
+model_1 <- as.formula(~ four_level_var)
+
+# run the metaregression
+list_model_1_meta_reg <- list()
+
+for(i in 1: length(list_df_simulated)){
+  
+  list_model_1_meta_reg[[i]] <- rma(yi = cohens_d, 
+                                    sei = simulated_se, 
[…]

### 2024-01-03 Script for cleaning merged dataset.R
for Charlotte to use today

@@ -15,7 +15,7 @@ df_full_med <- read.csv("Full Medication Dataset.csv")
 merged_dataset <- bind_rows(df_full_med, df_full_psych)
 
 # fix column ordering
-merged_dataset <- select(merged_dataset, -c(primary, hierarchy, time))
+merged_dataset <- dplyr:: select(merged_dataset, -c(primary, hierarchy, time))
 merged_dataset <- merged_dataset %>% relocate(descr_active, .after = control_type)
 merged_dataset <- merged_dataset %>% relocate(descr_control, .after = descr_active)
 merged_dataset <- merged_dataset %>% relocate(mean_age, .after = age_group)
@@ -239,7 +239,7 @@ sum(is.na(filter_test$cohens_d_active))
 sum(is.na(filter_test$cohens_d_control))
 
 # start looking at demographics, baseline and post means, and cohens d per arm
-df_demographics <- df_first_row %>% select(study, year, psy_or_med, active_type, control_type, descr_active, descr_control,
+df_demographics <- df_first_row %>% dplyr:: select(study, year, psy_or_med, active_type, control_type, descr_active, descr_control,
                                            instrument_name, baseline_mean_active, baseline_sd_active, baseline_n_active,
                                            baseline_mean_control, baseline_sd_control, baseline_n_control, 
                                            post_mean_active, post_sd_active, post_n_active, post_mean_control, post_sd_control, post_n_control,
@@ -249,7 +249,7 @@ df_demographics <- df_first_row %>% select(study, year, psy_or_med, active_type,
 df_demographics$descr_active <- ifelse(is.na(df_demographics$descr_active), df_demographics$active_type, df_demographics$descr_active)
 df_demographics$descr_control <- ifelse(is.na(df_demographics$descr_control), df_demographics$control_type, df_demographics$descr_control)
 
-df_demographics <- df_demographics %>%  select(-c(active_type, control_type))
+df_demographics <- df_demographics %>%  dplyr::select(-c(active_type, control_type))
 df_demographics <- df_demographics %>%  arrange(psy_or_med)
 
 # check how many studies we have baseline means for primary instrument
[…]

### 2024-01-03 apples_and_oranges.qmd
with various new additions for Charlotte

@@
       cite-style: super
+
 ---
@@
 
+# Method
+## Studies included
+
+NOTE: **Charlotte** to please check code lines 986 to 1121
+NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect.
+In the beginning of the results below, I explain in detail what is missing where.
+
+## Statistical Analysis
+### Measures of Effect
+As the measure of effect of each individual study, we used the Standardised Mean Difference (SMD), which we defined following NOTE: **Charlotte** cite Lakens 2013 and in there Cummings 2012, as:
+
+$$\frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$  {#eq-3}
+
+where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the study respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
+NOTE **Charlotte**, please add note here with what we did to impute SDs where missing, e.g.
+using the pre to impute the post etc.
+In general state here the rules we used citing the Cochrane book.
+
+For the purposes of metanalysis, it is necessary to estimate a standard error of the change score, that is of the SMD. This is calculated according to:
+
+$$ \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$          {#eq-4}
+
+where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
+This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
+However, this practice has given rise to concerns about misestimation.
+Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e.
+bias estimation of the effects for the control group of medication compared to those of psychotherapy.
+Still, to alleviate such concerns we have used a simulations.
+
+In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
+
+$$SE_{change} \sim \mathcal{TN}(\mu, \sigma, a, b)
+$$ {#eq-5}
+
+for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
+We then used these simulated datasets in the subsequent metanalyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+library(tidyverse)
+# Start here------------------------------------------------------
+# import master dataset
+
+df_appl_v_orange <-readxl:: read_excel("df_appl_v_orange.xlsx")
+
+#Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
+# I need reliabilities.
+
+# note re: CDRS reliability from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
+# Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
+# Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
+# for the CDRS-R total score in 53 clinic-referred6- to 12-year-olds.
+
+### A few more tidying things from Argyris before doing metanalyses
+# # discovered an error in the percentage women o fthe Fristad study. I have checked in the
+# # cuijpers dataset and the correct percentage is 43.1, but could not verify with the paper as it is not in 
+# # our folder and after a quick search I could not find it online either. Messaged Charlotte on Discord to
+# # check again.
+df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1
+
+# Create SEs proportions for percentage women --------------------------------------------
+
+# # We also need to calculate SE for proportion women for the baseline calculations
+# # for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
+
+product_perc_women <-  (df_appl_v_orange$percent_women/100)*
+  (1-(df_appl_v_orange$percent_women/100) )
+
+total_n <- df_appl_v_orange$baseline_n_active + 
+  df_appl_v_orange$baseline_n_control
+
+df_appl_v_orange$percent_women_std_error <- sqrt(product_perc_women/total_n )
+
+# Calculate SE for baseline severity --------------------------------------
+
+df_appl_v_orange$baseline_st_error_active <- 
+  df_appl_v_orange$baseline_sd_active/sqrt(df_appl_v_orange$baseline_n_active)
+
+df_appl_v_orange$baseline_st_error_control <-
+  df_appl_v_orange$baseline_sd_control/sqrt(df_appl_v_orange$baseline_n_control)
+
+# Turn into a long database with unique rows ------------------------------
+
+### Important: create a dataset that will have unique control studies (see problem that we identified with Charlotte, 
+#namely common control conditions)
+# create new id with Charlotte to help with better identification and work with duplicates (see below) 
+df_appl_v_orange  <- df_appl_v_orange  %>%
+  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
+                                  .default = study ))
+
+# Step 1: keep only the rows with the top instrument in our hierarchy
+df_with_distinct_instruments <-  df_appl_v_orange %>%          
+  group_by(new_study_id) %>% 
+  filter(instrument_value == min(instrument_value)) # coded for the smallest number to be best.
+
+# Step 2: turn dataframes to long
+# A: turn long the rows with active
+turn_long_active_type <- df_with_distinct_instruments %>% 
+  dplyr:: select(new_study_id, active_type, psy_or_med, baseline_n_active, cohens_d_active) %>% 
+  pivot_longer(cols = c(cohens_d_active), 
+               names_to = "arm_effect_size", 
+               values_to = "cohens_d")
+
+# also rename active_type to treatment for the merge below.
+turn_long_active_type <- rename(turn_long_active_type,treatment = active_type,
+                                baseline_n = baseline_n_active)
+
+# # to illustrate the issue, here we have one study with two controls for which the active at the moment, also exists twice. 
+# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
+# # but here another one where the same study reasonably contributes two actives, fluoxetine and duloxetine.
+# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]
+
+# we now need to go through each study id and remove duplicates
+turn_long_active_type <-
+  turn_long_active_type %>% 
+  group_by(new_study_id) %>% 
+  distinct(treatment, .keep_all = TRUE)
+
+# # Now checking if this worked with the studies that I used to illustrate the problem above. 
+# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
+# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]
+# # also check one which is single to make sure it is kept
+# turn_long_active_type[turn_long_active_type$new_study_id == "Ackerson, 1998",]
+
+# B: turn long control rows
+turn_long_control_type <- df_with_distinct_instruments %>% 
+  dplyr:: select(new_study_id, control_type, psy_or_med, baseline_n_control, cohens_d_control) %>% 
+  pivot_longer(cols = c(cohens_d_control), 
+               names_to = "arm_effect_size", 
+               values_to = "cohens_d")
+
+# also rename active_type to treatment for the merge below.
+turn_long_control_type <- rename(turn_long_control_type,treatment = control_type,
+                                 baseline_n = baseline_n_control)
+
+# # to illustrate the issue, here we have one study with two controls that are reasonable. 
+# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
+# # but here another one where the same study reasonably contributes two placebos
+# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]
+
+# we now need to go through each study id and remove duplicates
+turn_long_control_type <-
+  turn_long_control_type %>% 
+  group_by(new_study_id) %>% 
+  distinct(treatment, .keep_all = TRUE)
+
+# # Now checking if this worked with the studies that I used to illustrate the problem above. 
+# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
+# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]
+# # also check one which is single to make sure it is kept
+# turn_long_control_type[turn_long_control_type$new_study_id == "Ackerson, 1998",]
+
+### Now merge the active and control datasets
+df_long_for_metan <-rbind(turn_long_active_type, turn_long_control_type)
+#dim(df_long_for_metan ) #check dimension
+#make sure no study lost
+#length(unique(df_long_for_metan$new_study_id ) ) == # #length(unique(df_appl_v_orange$new_study_id ) )
+
+# Now check again the studies with muliple arms
+# Now checking if this worked with the studies that I used to illustrate the problem above. 
+# df_long_for_metan[df_long_for_metan$new_study_id == "Stallard, 2012",]
+# df_long_for_metan[df_long_for_metan$new_study_id == "Atkinson, 2014",]
+# # also check one which is single to make sure it is kept
+# df_long_for_metan[df_long_for_metan$new_study_id == "Ackerson, 1998",]
+
+# save this as the master dataframe  --------------------------------------
+# use this datafram to perform all operations below in quarto
+# ask Charlotte to check steps above (lines 986 to 1121)
+write.csv(df_long_for_metan, "df_long_for_metan", row.names = F)
+
+########### simulate so that each study has a value from a distribution of 
+######## of correlations.
+
+# I will generate random numbers per study id from a distribution with these parameters. 
+# it is reasonable to generate one random correlation value per study as there is no reason why the correlation should
+# systematically vary within studies
+
+# I have created a function for this
+library(tidyverse)
+library(truncnorm)
+
+df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")
+
+simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
+                                                                                              # of unique ids to which a correlation coef
+                                                                                              # is allocated.
+  set.seed(seed)
+
+  # Empty list to store simulated dfs
+  list_df_simulated <- list()
+
+  for (i in 1:num_repetitions) {
+    # Simulate the vector
+    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations
+
+    # Create a copy of the original dataframe
+    df_simulated_copy <- df
+
+    # Add/update the sims column
+    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]
+
+    # Remove duplicated columns
+    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]
+
+    # Calculate the ses
+    df_simulated_copy <- df_simulated_copy %>% 
+      group_by(new_study_id, baseline_n) %>% 
+      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
+                                   (cohens_d^2/(2*baseline_n))))
+
+    # Add the simulated dataframe to the list
+    list_df_simulated[[i]] <- df_simulated_copy
+  }
+
+  return(list_df_simulated)
+}
+
+list_df_simulated <-  simulate_dataframes_for_st_errors (df = df_long_for_metan, 
+                                              num_repetitions = 1000, 
+                                              seed  = 1974,
+                                              n = length(unique(df_long_for_metan$new_study_id)), 
+                                              a = 0.45, 
+                                              b = .9, 
+                                              mean = 0.65, 
+                                              sd = 0.2)
+
+#check this worked
+
+#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
+#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
+
+```
+
+### Random Effects Metaregression
+We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
+The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+Therefore, we can estimate a two stage model with:
+
+$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
+$$ {#eq-5}
+
+$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
+$$ {#eq-6}
+
+where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
+Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
+
+This then gives rise to:
+
+$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-7}
+
+where,
+
+$$u_i \sim N(0, \tau^2) $${#eq-8}
+
+which describes the deviation of each study from the mean of the distribution, and,
+
+$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-9}
+
+We can then specify the following model to obtain the means of each arm of the trials as follows:
+
+$$ \begin{aligned}
+    Υ_i &=
+    \begin{cases}
+        0 & MedControl: b_0 + u_i + \epsilon_i\\
+        1 & MedActive:  b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
+        2 & PsyActive:  b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
+        3 & PsyControl: b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
+    \end{cases}
+\end{aligned}$$  {#eq-10}
+
+where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
+for level 3, $b_{3_{i}}$ the psychotherapy controls.
+The confidence intervals of the means are constructed in the standard way using the standard errors of the
+Similarly, each coefficient represents the contrast between the reference category and each level, for an exmaple and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
+Inference on the contrasts is done as follows:
+
+$$
+z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
+$$ {#eq-11}
+
+We used maximum likelihood (REML) to estimate model and applied  Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
+
 # Results
@@
 library(tidyverse)
-df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")
 
@@
 
+df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
 ```
@@
 
-In order to conduct a met
+We then applied metaregression to obtain the means and confidence intervals of each of the four arms.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# Run metaregression ------------------------------------------------------
+library(metafor)
+# add a new multilevel variable for the regression
+
+for(i in 1: length(list_df_simulated)){
+  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+
+  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+}
+
+# check it worked
+# list_df_simulated[[2]] %>% 
+#   dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
+
+# specify the model 
+model_1 <- as.formula(~ four_level_var)
+
+# run the metaregression
+list_model_1_meta_reg <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_model_1_meta_reg[[i]] <- rma(yi = cohens_d, 
+                                    sei = simulated_se, 
+                                    data = list_df_simulated[[i]] , 
+                                    method = "ML", 
+                                    mods = model_1 , 
+                                    test = "knha")
+
+}
+
+# list_model_1_meta_reg[[2]]
+
+# Function to extract parameters (coefs, ses, CI) for each level of the dummy variable
+# it is an awkward one, because I couldnt' come up with a better way to add the intercept to each coefficient
+# given the named output of the built in coef function. 
+# here I exctract the coeffcients
+extract_coefficients_func <- function(df_with_coefs){
+  list_coefs <- list()
+  coefs <- 0
+  coefficient_output <- 0
+
+  for(i in 1: length(coefficients(df_with_coefs))){
+
+    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
+                         length(coefficients(df_with_coefs)) - 1 ))
+    coefs[i] <- coef(df_with_coefs)[[i]]
+
+    coefficient_output <- temp_vec + coefs
+
+    st_error_output <- df_with_coefs$se
+
+    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))
+
+    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
+    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
+  }
+  return (df_coefficients )
+}
+
+# dummy_var_means <- extract_coefficients_func(list_model_1_meta_reg[[1]])
+
+list_dummy_var_means <-lapply(list_model_1_meta_reg, extract_coefficients_func)
+
+# this is the way to get the means and SEs from the simulation across all datasets.
+
+df_mean_coefs_from_sim <- data.frame(
+
+  condition = levels(list_df_simulated[[1]]$four_level_var),
+
+  mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),
+
+  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[4,2])))
+
+)
+
+# and add the CIs
+
+df_mean_coefs_from_sim$upper_ci <- df_mean_coefs_from_sim$mean_coefficient + 1.96 * df_mean_coefs_from_sim$mean_se
+
+df_mean_coefs_from_sim$lower_ci <- df_mean_coefs_from_sim$mean_coefficient - 1.96 * df_mean_coefs_from_sim$mean_se
+# df_mean_coefs_from_sim # this is now the dataframe containing the means you need for plotting.
+
+#also, add the n of studies non missing from variable created above
+#important first create the same condition variable: 
+df_count_studies_not_missing$condition <- str_replace_all(df_count_studies_not_missing$condition, "_", " ")
+
+# I needed to join them because of the relevelling, the rows would not align otherwise.
+# df_mean_coefs_from_sim <- right_join(df_mean_coefs_from_sim, df_count_studies_not_missing)
+
+# need to merge this with the count studies variable to obtain the ks
+library(forcats)
+ordering_criterion <- unique(df_mean_coefs_from_sim$condition)
+
+# 
+df_count_studies_not_missing <- df_count_studies_not_missing %>% arrange(ordering_criterion) %>%
+  mutate(condition = fct_relevel(condition, levels = unique(condition)))
+# I will use this for plotting below.
+
+```
+We examined the variability that the simulations of the correlations of the pre-post outcomes produced.
+As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.
+
+NOTE: **Charlotte**, this should be moved to the supplement at Table 2
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+variability_in_sims <- data.frame (mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
+                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),
+
+sd_coefficient = c(sd(sapply(list_dummy_var_means, function(df) df[1,1])),
+                      sd(sapply(list_dummy_var_means, function(df) df[2,1])),
+                      sd(sapply(list_dummy_var_means, function(df) df[3,1])),
+                      sd(sapply(list_dummy_var_means, function(df) df[4,1]))),
+
+  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
+              mean(sapply(list_dummy_var_means, function(df) df[4,2]))),
+
+  sd_se = c(sd(sapply(list_dummy_var_means, function(df) df[1,2])),
+              sd(sapply(list_dummy_var_means, function(df) df[2,2])),
+              sd(sapply(list_dummy_var_means, function(df) df[3,2])),
+              sd(sapply(list_dummy_var_means, function(df) df[4,2])))
+)
+
+```
+
+Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metanalyses. 
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# for some reason doesn't work, but will make work.
+# tab_1_df <- df_mean_coefs_from_sim[, 1:length(df_mean_coefs_from_sim)-1]
+# knitr:: kable(tab_1_df, digits = 2, 
+#              col.names = c('Trial Arm', 'Beta', 'SE', 'Upper CI', 'Lower CI') )
+```
+
+Figure 1 graphs the results with the means of each level alongside their confidence intervals.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# plot results from simulated means ---------------------------------------
+
+# Create summary stats text
+df_mean_coefs_from_sim$text_label <- 0
+for(i in 1: nrow(df_mean_coefs_from_sim))
+df_mean_coefs_from_sim$text_label[i] <-  paste(
+   "k = ", df_count_studies_not_missing $n[i],"\n", 
+   round(df_mean_coefs_from_sim$mean_coefficient[i], 2),
+   "[" ,
+ round(df_mean_coefs_from_sim$lower_ci[i],2), 
+ round(df_mean_coefs_from_sim$upper_ci[i], 2),
+"]")
+
+# recode condition for ease of plotting
+df_mean_coefs_from_sim$condition <- str_replace_all(df_mean_coefs_from_sim$condition, "_", " ")
+
+# encode colours
+redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
+blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")
+
+ggplot(df_mean_coefs_from_sim, aes(x = mean_coefficient, y = 1:nrow(df_mean_coefs_from_sim),
+                                   colour = condition, label = text_label)) +
+  geom_point(size = 3) +
+  geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
+  geom_text(vjust = +1.5, size = 4) +  # Adjust vjust and size as needed
+  scale_size_continuous(guide = "none") +
+  guides(colour = FALSE) + 
+  scale_color_manual(values = c(redish_palette, blueish_palette)) +
+  theme_minimal() +
+  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Type and Treatment Arm",
+       subtitle = "metanalytically derived estimates of within group changes") +
+  xlab("Standardized Mean Difference (SMD) with 95% CIs") +
+  ylab("") +
+  ylim(0, nrow(df_mean_coefs_from_sim) + 1) +
+  xlim(-2.5, 0.5) +
+  geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
+  geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
+  geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
+  theme(axis.title.x = element_text(size = 14), 
+        axis.text.x  = element_text(size = 14),
+        axis.text.y = (element_blank()),
+        plot.title = element_text(size = 16),
+        plot.subtitle = element_text(size = 14))+
+  geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
+  geom_text(x = 0.2, y = 4.75, label = "Line of No Effect", color = "grey", vjust = 0.5, hjust = 0)
+
+```
+
+As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms.
+Table 2 illustrates this with the output of one of the simulated models.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+coefs<- 0
+ses <- 0
+for(i in 1: length(list_model_1_meta_reg)){
+
+  coefs[[i]] <- coef(list_model_1_meta_reg[[i]])[[4]]  ### CAREFUL this is poor coding practice on my part
+  ses[[i]] <- list_model_1_meta_reg[[i]]$se[4] ### but I can't find another way of grabbing this estimate from the
+  ### rma object. It could go badly wrong if the relevelling isn't done consistently...CHECK MANUALLY
+  coefficients_from_contrasts_medcontrol_psy_control <- data.frame(Beta = mean(coefs), SE = mean(ses))
+}
+
+coefficients_from_contrasts_medcontrol_psy_control$lower_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta - 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE
+
+coefficients_from_contrasts_medcontrol_psy_control$upper_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta + 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control, col.names = c("Beta", "SE", "Lower CI", "Upper CI"), digits = 2)
+```

### 2024-01-03 acm_dir/acm_dir.tex
Having problems with my git, hoping this will fix merge errors

\documentclass[manuscript,screen]{acmart}

\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother

%%
%% This is file `sample-manuscript.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `manuscript')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-manuscript.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass command.

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}

\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}

%% PANDOC PREAMBLE BEGINS

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\definecolor{mypink}{RGB}{219, 48, 122}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
%% PANDOC PREAMBLE ENDS

\setlength{\parindent}{10pt}
\setlength{\parskip}{0pt}

\hypersetup{
  pdftitle={The Name of the Title Is Hope},
  pdfauthor={Ben Trovato; G.K.M. Tobin; Lars Thørväld; Valerie Béranger; Aparna Patel; Huifen Chan; Charles Palmer; John Smith; Julius P. Kumquat},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={red},
  pdfcreator={LaTeX via pandoc, via quarto}}

%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmcopyright}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%% These commands are for a PROCEEDINGS abstract or paper.
\acmConference[Conference acronym 'XX]{Make sure to enter the correct
conference title from your rights confirmation emai}{June 03--05,
2018}{Woodstock, NY}
\acmPrice{15.00}
\acmISBN{978-1-4503-XXXX-X/18/06}

%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references.  The command \citestyle{authoryear} switches to the
%% "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the "author year" style of
%% citations and references.
%% Uncommenting
%% the next command will enable that style.
%%\citestyle{acmauthoryear}

%% end of the preamble, start of the body of the document source.
\begin{document}

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title[Hope]{The Name of the Title Is Hope}

%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

  \author{Ben Trovato}
  \orcid{1234-5678-9012}
    \author{G.K.M. Tobin}

            \affiliation{%
                  \institution{Institute for Clarity in Documentation}
                          \streetaddress{P.O. Box 1212}
                          \city{Dublin}
                                  \country{USA}
                          \postcode{43017-6221}
              }
        \author{Lars Thørväld}

            \affiliation{%
                  \institution{The Thørväld Group}
                          \streetaddress{1 Thørväld Circle}
                          \city{Hekla}
                                  \country{Iceland}
                      }
        \author{Valerie Béranger}

            \affiliation{%
                  \institution{Inria Paris-Rocquencourt}
                                  \city{Rocquencourt}
                                  \country{France}
                      }
        \author{Aparna Patel}

            \affiliation{%
                  \institution{Rajiv Gandhi University}
                          \streetaddress{Rono-Hills}
                          \city{Doimukh}
                                  \country{India}
                      }
        \author{Huifen Chan}

            \affiliation{%
                  \institution{Tsinghua University}
                          \streetaddress{30 Shuangqing Rd}
                          \city{Haidian Qu}
                                  \country{China}
                      }
        \author{Charles Palmer}

            \affiliation{%
                  \institution{Palmer Research Laboratories}
                          \streetaddress{8600 Datapoint Drive}
                          \city{San Antonio}
                                  \country{USA}
                          \postcode{78829}
              }
        \author{John Smith}

            \affiliation{%
                  \institution{The Thørväld Group}
                          \streetaddress{1 Thørväld Circle}
                          \city{Hekla}
                                  \country{Iceland}
                      }
        \author{Julius P. Kumquat}

            \affiliation{%
                  \institution{The Kumquat Consortium}
                                  \city{New York}
                                  \country{USA}
                      }

\renewcommand{\shortauthors}{Trovato et al.}

%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
%\renewcommand{\shortauthors}{Trovato et al.}
%%  
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
A clear and well-documented \LaTeX~document is presented as an article
formatted for publication by ACM in a conference proceedings or journal
publication. Based on the ``acmart'' document class, this article
presents and explains many of the common variations, as well as many of
the formatting elements an author may use in the preparation of the
documentation of their work.    
\end{abstract}

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
\begin{CCSXML}
<ccs2012>
 <concept>
  <concept_id>10010520.10010553.10010562</concept_id>
  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
  <concept_significance>500</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010575.10010755</concept_id>
  <concept_desc>Computer systems organization~Redundancy</concept_desc>
  <concept_significance>300</concept_significance>
 </concept>
 <concept>
  <concept_id>10010520.10010553.10010554</concept_id>
  <concept_desc>Computer systems organization~Robotics</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
 <concept>
  <concept_id>10003033.10003083.10003095</concept_id>
  <concept_desc>Networks~Network reliability</concept_desc>
  <concept_significance>100</concept_significance>
 </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computer systems organization~Embedded systems}
\ccsdesc[300]{Computer systems organization~Redundancy}
\ccsdesc{Computer systems organization~Robotics}
\ccsdesc[100]{Networks~Network reliability}

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{datasets, neural networks, gaze detection, text tagging}

%%
%% This command processes the author and affiliation and title
%% information and builds the first part of the formatted document.
\maketitle

\setlength{\parskip}{-0.1pt}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX~style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX~templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable guide
to the process of preparing your work for publication. If you have
published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\texttt{acmart}'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage of
publication, from review to final ``camera-ready'' copy, to the author's
own version, with \emph{very} few changes to the source.

\hypertarget{template-overview}{%
\section{Template Overview}\label{template-overview}}

As noted in the introduction, the ``\texttt{acmart}'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate \emph{template style} and \emph{template
parameters}.

This document will explain the major features of the document class. For
further information, the \emph{\LaTeX~User's Guide} is available from
\url{https://www.acm.org/publications/proceedings-template}.

\hypertarget{template-styles}{%
\subsection{Template Styles}\label{template-styles}}

The primary parameter given to the ``\texttt{acmart}'' document class is
the \emph{template style} which corresponds to the kind of publication
or SIG publishing the work. This parameter is enclosed in square
brackets and is a part of the ``\texttt{documentclass}'' command:

\begin{verbatim}
  \documentclass[STYLE]{acmart}
\end{verbatim}

Journals use one of three template styles. All but three ACM journals
use the ``\texttt{acmsmall}'' template style:

\begin{itemize}
\tightlist
\item
  \texttt{acmsmall}: The default journal template style.
\item
  \texttt{acmlarge}: Used by JOCCH and TAP.
\item
  \texttt{acmtog}: Used by TOG.
\end{itemize}

The majority of conference proceedings documentation will use the
``\texttt{cmconf}'' template style.

\begin{itemize}
\tightlist
\item
  \texttt{acmconf}: The default proceedings template style.
\item
  \texttt{sigchi}: Used for SIGCHI conference articles.
\item
  \texttt{sigchi-a}: Used for SIGCHI ``Extended Abstract'' articles.
\item
  \texttt{sigplan}: Used for SIGPLAN conference articles.
\end{itemize}

\hypertarget{template-parameters}{%
\subsection{Template Parameters}\label{template-parameters}}

In addition to specifying the \emph{template style} to be used in
formatting your work, there are a number of \emph{template parameters}
which modify some part of the applied template style. A complete list of
these parameters can be found in the \emph{\LaTeX~User's Guide.}

Frequently-used parameters, or combinations of parameters, include:

\begin{itemize}
\tightlist
\item
  \texttt{anonymous,review}: Suitable for a ``double-blind'' conference
  submission. Anonymizes the work and includes line numbers. Use with
  the \texttt{\textbackslash{}acmSubmissionID} command to print the
  submission's unique ID on each page of the work.
\item
  \texttt{authorversion}: Produces a version of the work suitable for
  posting by the author.
\item
  \texttt{screen}: Produces colored hyperlinks.
\end{itemize}

This document uses the following string as the first command in the
source file:

\begin{verbatim}
  \documentclass[manuscript,screen,review]{acmart}
\end{verbatim}

\hypertarget{modifications}{%
\section{Modifications}\label{modifications}}

Modifying the template --- including but not limited to: adjusting
margins, typeface sizes, line spacing, paragraph and list definitions,
and the use of the \texttt{\textbackslash{}vspace} command to manually
adjust the vertical spacing between elements of your work --- is not
allowed.

\textbf{Your document will be returned to you for revision if
modifications are discovered.}

\hypertarget{typefaces}{%
\section{Typefaces}\label{typefaces}}

The ``\texttt{acmart}'' document class requires the use of the
``Libertine'' typeface family. Your \TeX~installation should include
this set of packages. Please do not substitute other typefaces. The
``\texttt{lmodern}'' and ``\texttt{ltimes}'' packages should not be
used, as they will override the built-in typeface families.

\hypertarget{title-information}{%
\section{Title Information}\label{title-information}}

The title of your work should use capital letters appropriately -
\url{https://capitalizemytitle.com/} has useful rules for
capitalization. Use the ``\texttt{title}'' command to define the title
of your work. If your work has a subtitle, define it with the
``\texttt{subtitle}'' command. Do not insert line breaks in your title.

If your title is lengthy, you must define a short version to be used in
the page headers, to prevent overlapping text. The ``\texttt{title}''
command has a ``short title'' parameter:

\begin{verbatim}
  \title[short title]{full title}
\end{verbatim}

\hypertarget{authors-and-affiliations}{%
\section{Authors and Affiliations}\label{authors-and-affiliations}}

Each author must be defined separately for accurate metadata
identification. As an exception, multiple authors may share one
affiliation. Authors' names should not be abbreviated; use full first
names wherever possible. Include authors' e-mail addresses whenever
possible.

Grouping authors' names or e-mail addresses, or providing an ``e-mail
alias,'' as shown below, is not acceptable:

\begin{verbatim}
  \author{Brooke Aster, David Mehldau}
  \email{dave,judy,steve@university.edu}
  \email{firstname.lastname@phillips.org}
\end{verbatim}

The \texttt{authornote} and \texttt{authornotemark} commands allow a
note to apply to multiple authors --- for example, if the first two
authors of an article contributed equally to the work.

If your author list is lengthy, you must define a shortened version of
the list of authors to be used in the page headers, to prevent
overlapping text. The following command should be placed just after the
last \texttt{\textbackslash{}author\{\}} definition:

\begin{verbatim}
  \renewcommand{\shortauthors}{McCartney, et al.}
\end{verbatim}

Omitting this command will force the use of a concatenated list of all
of the authors' names, which may result in overlapping text in the page
headers.

The article template's documentation, available at
\url{https://www.acm.org/publications/proceedings-template}, has a
complete explanation of these commands and tips for their effective use.

Note that authors' addresses are mandatory for journal articles.

\hypertarget{rights-information}{%
\section{Rights Information}\label{rights-information}}

Authors of any work published by ACM will need to complete a rights
form. Depending on the kind of work, and the rights management choice
made by the author, this may be copyright transfer, permission, license,
or an OA (open access) agreement.

Regardless of the rights management choice, the author will receive a
copy of the completed rights form once it has been submitted. This form
contains \LaTeX~commands that must be copied into the source document.
When the document source is compiled, these commands and their
parameters add formatted text to several areas of the final document:

\begin{itemize}
\tightlist
\item
  the ``ACM Reference Format'' text on the first page.
\item
  the ``rights management'' text on the first page.
\item
  the conference information in the page header(s).
\end{itemize}

Rights information is unique to the work; if you are preparing several
works for an event, make sure to use the correct set of commands with
each of the works.

The ACM Reference Format text is required for all articles over one page
in length, and is optional for one-page articles (abstracts).

\hypertarget{ccs-concepts-and-user-defined-keywords}{%
\section{CCS Concepts and User-Defined
Keywords}\label{ccs-concepts-and-user-defined-keywords}}

Two elements of the ``acmart'' document class provide powerful taxonomic
tools for you to help readers find your work in an online search.

The ACM Computing Classification System ---
\url{https://www.acm.org/publications/class-2012} --- is a set of
classifiers and concepts that describe the computing discipline. Authors
can select entries from this classification system, via
\url{https://dl.acm.org/ccs/ccs.cfm}, and generate the commands to be
included in the \LaTeX~source.

User-defined keywords are a comma-separated list of words and phrases of
the authors' choosing, providing a more flexible way of describing the
research being presented.

CCS concepts and user-defined keywords are required for for all articles
over two pages in length, and are optional for one- and two-page
articles (or abstracts).

\hypertarget{sectioning-commands}{%
\section{Sectioning Commands}\label{sectioning-commands}}

Your work should use standard \LaTeX~sectioning commands:
\texttt{section}, \texttt{subsection}, \texttt{subsubsection}, and
\texttt{paragraph}. They should be numbered; do not remove the numbering
from the commands.

Simulating a sectioning command by setting the first word or words of a
paragraph in boldface or italicized text is \textbf{not allowed.}

\hypertarget{tables}{%
\section{Tables}\label{tables}}

The ``\texttt{acmart}'' document class includes the
``\texttt{booktabs}'' package --- \url{https://ctan.org/pkg/booktabs}
--- for preparing high-quality tables.

Table captions are placed \emph{above} the table.

Because tables cannot be split across pages, the best placement for them
is typically the top of the page nearest their initial cite. To ensure
this proper ``floating'' placement of tables, use the environment
\textbf{table} to enclose the table's contents and the table caption.
The contents of the table itself must go in the \textbf{tabular}
environment, to be aligned properly in rows and columns, with the
desired horizontal and vertical rules. Again, detailed instructions on
\textbf{tabular} material are found in the \emph{\LaTeX~User's Guide}.

Immediately following this sentence is the point at which
Table~\ref{tbl-freq} is included in the input file; compare the
placement of the table here with the table in the printed output of this
document.

\hypertarget{tbl-freq}{}
\begin{longtable}[]{@{}ccl@{}}
\caption{\label{tbl-freq}Frequency of Special Characters}\tabularnewline
\toprule\noalign{}
Non-English or Math & Frequency & Comments \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Non-English or Math & Frequency & Comments \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Ø & 1 in 1,000 & For Swedish names \\
\(\pi\) & 1 in 5 & Common in math \\
\$ & 4 in 5 & Used in business \\
\(\Psi^2_1\) & 1 in 40,000 & Unexplained usage \\
\end{longtable}

To set a wider table, which takes up the whole width of the page's live
area, use the environment \textbf{table*} to enclose the table's
contents and the table caption. As with a single-column table, this wide
table will ``float'' to a location deemed more desirable. Immediately
following this sentence is the point at which Table~\ref{tbl-commands}
is included in the input file; again, it is instructive to compare the
placement of the table here with the table in the printed output of this
document.

\hypertarget{tbl-commands}{}
\begin{longtable}[]{@{}ccl@{}}
\caption{\label{tbl-commands}Some Typical Commands}\tabularnewline
\toprule\noalign{}
Command & A Number & Comments \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
Command & A Number & Comments \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
\texttt{\textbackslash{}author} & 100 & Author \\
\texttt{\textbackslash{}table} & 300 & For tables \\
\texttt{\textbackslash{}table*} & 400 & For wider tables \\
\end{longtable}

Always use midrule to separate table header rows from data rows, and use
it only for this purpose. This enables assistive technologies to
recognise table headers and support their users in navigating tables
more easily.

\hypertarget{math-equations}{%
\section{Math Equations}\label{math-equations}}

You may want to display math equations in three distinct styles: inline,
numbered or non-numbered display. Each of the three are discussed in the
next sections.

\hypertarget{inline-in-text-equations}{%
\subsection{Inline (In-text) Equations}\label{inline-in-text-equations}}

A formula that appears in the running text is called an inline or
in-text formula. It is produced by the \textbf{math} environment, which
can be invoked with the usual
\texttt{\textbackslash{}begin,\ ...\ \textbackslash{}end} construction
or with the short form
\texttt{\textbackslash{}\$\ ...\ \textbackslash{}\$}. You can use any of
the symbols and structures, from \(\alpha\) to \(\omega\), available in
\LaTeX\citep{Lamport:LaTeX}; this section will simply show a few
examples of in-text equations in context. Notice how this equation:
\(\lim_{n\rightarrow \infty}x=0\), set here in in-line math style, looks
slightly different when set in display style. (See next section).

\hypertarget{display-equations}{%
\subsection{Display Equations}\label{display-equations}}

A numbered display equation---one set off by vertical space from the
text and centered horizontally---is produced by the \textbf{equation}
environment. An unnumbered display equation is produced by the
\textbf{displaymath} environment.

Again, in either environment, you can use any of the symbols and
structures available in \LaTeX@; this section will just give a couple of
examples of display equations in context. First, consider
Equation~\ref{eq-oneequation}, shown as an inline equation above:

\begin{equation}\protect\hypertarget{eq-oneequation}{}{
\lim_{n\rightarrow \infty}x=0
}\label{eq-oneequation}\end{equation}

Notice how it is formatted somewhat differently in the
\textbf{displaymath} environment. Now, we'll enter an unnumbered
equation:

\[\sum_{i=0}^{\infty} x + 1\]

and follow it with Equation~\ref{eq-anotherequation}, another numbered
equation:

\begin{equation}\protect\hypertarget{eq-anotherequation}{}{
\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
}\label{eq-anotherequation}\end{equation}

just to demonstrate \LaTeX's able handling of numbering.

\hypertarget{figures}{%
\section{Figures}\label{figures}}

The ``\texttt{figure}'' environment should be used for figures. One or
more images can be placed within a figure. If your figure contains
third-party material, you must clearly identify it as such, as shown in
the example below.

\begin{figure}
{\centering \includegraphics{sample-franklin.png}}
\caption{1907 Franklin Model D roadster. Photograph by Harris \& Ewing,
Inc.~{[}Public domain{]}, via Wikimedia Commons.
(\url{https://goo.gl/VLCRBB}).}
\Description{A woman and a girl in white dresses sit in an open car.}
\end{figure}

Your figures should contain a caption which describes the figure to the
reader.

Figure captions are placed \emph{below} the figure.

Every figure should also have a figure description unless it is purely
decorative. These descriptions convey what's in the image to someone who
cannot see it. They are also used by search engine crawlers for indexing
images, and when images cannot be loaded.

A figure description must be unformatted plain text less than 2000
characters long (including spaces). \textbf{Figure descriptions should
not repeat the figure caption -- their purpose is to capture important
information that is not already provided in the caption or the main text
of the paper.} For figures that convey important and complex new
information, a short text description may not be adequate. More complex
alternative descriptions can be placed in an appendix and referenced in
a short figure description. For example, provide a data table capturing
the information in a bar chart, or a structured list representing a
graph. For additional information regarding how best to write figure
descriptions and why doing this is so important, please see
\url{https://www.acm.org/publications/taps/describing-figures/}.

\hypertarget{the-teaser-figure}{%
\subsection{The ``Teaser Figure''}\label{the-teaser-figure}}

A ``teaser figure'' is an image, or set of images in one figure, that
are placed after all author and affiliation information, and before the
body of the article, spanning the page. If you wish to have such a
figure in your article, place the command immediately before the
\texttt{\textbackslash{}maketitle} command:

\begin{verbatim}
  \begin{teaserfigure}
    \includegraphics[width=\textwidth]{sampleteaser}
    \caption{figure caption}
    \Description{figure description}
  \end{teaserfigure}
\end{verbatim}

\hypertarget{citations-and-bibliographies}{%
\section{Citations and
Bibliographies}\label{citations-and-bibliographies}}

The use of \BibTeX~for the preparation and formatting of one's
references is strongly recommended. Authors' names should be complete
--- use full first names (``Donald E. Knuth'') not initials (``D. E.
Knuth'') --- and the salient identifying features of a reference should
be included: title, year, volume, number, pages, article DOI, etc.

The bibliography is included in your source document with these two
commands, placed just before the \verb|\end{document}| command:

\begin{verbatim}
  \bibliographystyle{ACM-Reference-Format}
  \bibliography{bibfile}
\end{verbatim}

where ``\texttt{bibfile}'' is the name, without the ``\texttt{.bib}''
suffix, of the \BibTeX~file.

Citations and references are numbered by default. A small number of ACM
publications have citations and references formatted in the ``author
year'' style; for these exceptions, please include this command in the
\textbf{preamble} (before the command
``\texttt{\textbackslash{}begin\{document\}}'') of your \LaTeX~source:

\begin{verbatim}
  \citestyle{acmauthoryear}
\end{verbatim}

Some examples. A paginated journal article \citep{Abril07}, an
enumerated journal article \citep{Cohen07}, a reference to an entire
issue \citep{JCohen96}, a monograph (whole book) \citep{Kosiur01}, a
monograph/whole book in a series (see 2a in spec. document)
\citep{Harel79}, a divisible-book such as an anthology or compilation
\citep{Editor00} followed by the same example, however we only output
the series if the volume number is given \citep{Editor00a} (so
Editor00a's series should NOT be present since it has no vol.~no.), a
chapter in a divisible book \citep{Spector90}, a chapter in a divisible
book in a series \citep{Douglass98}, a multi-volume work as book
\citep{Knuth97}, a couple of articles in a proceedings (of a conference,
symposium, workshop for example) (paginated proceedings article)
\citep[\citet{Hagerup1993}]{Andler79}, a proceedings article with all
possible elements \citep{Smith10}, an example of an enumerated
proceedings article \citep{VanGundy07}, an informally published work
\citep{Harel78}, a couple of preprints
\citep[\citet{AnzarootPBM14}]{Bornmann2019}, a doctoral dissertation
\citep{Clarkson85}, a master's thesis: \citep{anisi03}, an online
document / world wide web resource \citep[\citet{Ablamowicz07},
\citet{Poker06}]{Thornburg01}, a video game (Case 1) \citep{Obama08} and
(Case 2)\citep{Novak03} and \citep{Lee05} and (Case 3) a patent
\citep{JoeScientist001}, work accepted for publication \citep{rous08},
`YYYYb'-test for prolific author \citep{SaeediMEJ10} and
\citep{SaeediJETC10}. Other cites might contain `duplicate' DOI and URLs
(some SIAM articles) \citep{Kirschmer-2010-AEI-1958016-1958018}. Boris /
Barbara Beeton: multi-volume works as books \citep{MR781536} and
\citep{MR781537}. A couple of citations with DOIs:
\citep[\citet{Kirschmer-2010-AEI-1958016-1958018}]{2004-ITE-1009386-1010128}.
Online citations: \citep[\citet{Thornburg01},
\citet{CTANacmart}]{TUGInstmem}. Artifacts: \citep{R} and
\citep{UMassCitations}.

\hypertarget{acknowledgments}{%
\section{Acknowledgments}\label{acknowledgments}}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the preparation
of the work should be included in an acknowledgment section, which is
placed just before the reference section in your document.

This section has a special environment:

\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}

so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure consistency
in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered
\texttt{\textbackslash{}section}; please the
``\texttt{\textbackslash{}acks}'' environment.

\hypertarget{appendices}{%
\section{Appendices}\label{appendices}}

If your work needs an appendix, add it before the
``\texttt{\textbackslash{}end\{document\}}'' command at the conclusion
of your source document.

Start the appendix with the ``\texttt{appendix}'' command:

\begin{verbatim}
  \appendix
\end{verbatim}

and note that in the appendix, sections are lettered, not numbered. This
document has two appendices, demonstrating the section and subsection
identification method.

\hypertarget{multi-language-papers}{%
\section{Multi-language papers}\label{multi-language-papers}}

Papers may be written in languages other than English or include titles,
subtitles, keywords and abstracts in different languages (as a rule, a
paper in a language other than English should include an English title
and an English abstract). Use \texttt{language=...} for every language
used in the paper. The last language indicated is the main language of
the paper. For example, a French paper with additional titles and
abstracts in English and German may start with the following command

\begin{verbatim}
  \documentclass[sigconf, language=english, language=german,
                 language=french]{acmart}
\end{verbatim}

The title, subtitle, keywords and abstract will be typeset in the main
language of the paper. The commands
\texttt{\textbackslash{}translatedXXX}, \texttt{XXX} being
\texttt{title}, \texttt{subtitle} and \texttt{keywords}, can be used to
set these elements in the other languages. The environment
\texttt{translatedabstract} is used to set the translation of the
abstract. These commands and environment have a mandatory first
argument: the language of the second argument. See
\texttt{sample-sigconf-i13n.tex} file for examples of their usage.

\hypertarget{sigchi-extended-abstracts}{%
\section{SIGCHI Extended Abstracts}\label{sigchi-extended-abstracts}}

The ``\texttt{sigchi-a}'' template style (available only in \LaTeX~and
not in Word) produces a landscape-orientation formatted article, with a
wide left margin. Three environments are available for use with the
``\texttt{sigchi-a}'' template style, and produce formatted output in
the margin:

\begin{itemize}
\tightlist
\item
  \textbf{\texttt{sidebar}}: Place formatted text in the margin.
\item
  \textbf{\texttt{marginfigure}}: Place a figure in the margin.
\item
  \textbf{\texttt{margintable}}: Place a table in the margin.
\end{itemize}

\begin{acks}
To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{bibliography.bib}

\renewcommand{\bibsection}{}
\bibliography{bibliography.bib}

\appendix

\hypertarget{research-methods}{%
\section{Research Methods}\label{research-methods}}

\hypertarget{part-one}{%
\subsection{Part One}\label{part-one}}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum vel
mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
lacinia dolor. Integer ultricies commodo sem nec semper.

\hypertarget{part-two}{%
\subsection{Part Two}\label{part-two}}

Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
ipsum convallis congue hendrerit vitae sapien. Donec at laoreet eros.
Vivamus non purus placerat, scelerisque diam eu, cursus ante. Etiam
aliquam tortor auctor efficitur mattis.

\hypertarget{online-resources}{%
\section{Online Resources}\label{online-resources}}

Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
enim maximus. Vestibulum gravida massa ut felis suscipit congue. Quisque
mattis elit a risus ultrices commodo venenatis eget dui. Etiam sagittis
eleifend elementum.

Nam interdum magna at lectus dignissim, ac dignissim lorem rhoncus.
Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar massa et
mattis lacinia.

%% begin pandoc before-bib
%% end pandoc before-bib
%% begin pandoc biblio
%% end pandoc biblio
%% begin pandoc include-after
%% end pandoc include-after
%% begin pandoc after-body
%% end pandoc after-body

\end{document}
\endinput
%%
%% End of file `sample-manuscript.tex'.

### 2024-01-03 apples_and_oranges.tex
Having problems with my git, hoping this will fix merge errors

--- 2023-12-26 elsevier/CopyOfelsevier.tex
@@
 \hypersetup{
-  pdftitle={Short Paper},
-  pdfauthor={Alice Anonymous; Bob Security; Cat Memes; Derek Zoolander},
-  pdfkeywords={keyword1, keyword2},
+  pdftitle={Fundamental Problems with the Evidence Base for Adolescent Depression Treatments.},
+  pdfauthor={Argyris Stringaris; Charlotte Burman; Dayna Bhudia; Carmen Moreno; Samuele Cortese; Georgina Krebs},
+  pdfkeywords={depression, adolescents, antidepressants, psychotherapy},
   colorlinks=true,
@@
 \begin{frontmatter}
-\title{Short Paper \\\large{A Short Subtitle} }
-\author[1]{Alice Anonymous%
+\title{Fundamental Problems with the Evidence Base for Adolescent
+Depression Treatments. \\\large{A conceptual and quantiative
+re-appraisal.} }
+\author[1]{Argyris Stringaris%
 \corref{cor1}%
-\fnref{fn1}}
- \ead{alice@example.com} 
-\author[2]{Bob Security%
-%
-\fnref{fn2}}
- \ead{bob@example.com} 
-\author[2]{Cat Memes%
-%
-\fnref{fn3}}
- \ead{cat@example.com} 
-\author[]{Derek Zoolander%
+}
+ \ead{a.stringaris@ucl.ac.uk} 
+\author[1]{Charlotte Burman%
 %
 }
- \ead{derek@example.com}
+ \ead{c.burman@ucl.ac.uk} 
+\author[1]{Dayna Bhudia%
+%
+}
+ \ead{d.bhudia@ucl.ac.uk} 
+\author[2]{Carmen Moreno%
+%
+}
+ \ead{cmoreno@hggm.es} 
+\author[3]{Samuele Cortese%
+%
+}
+ \ead{samuele.cortese@soton.ac.uk} 
+\author[1]{Georgina Krebs%
+%
+}
+ \ead{g.krebs@ucl.ac.uk}
 
-\affiliation[1]{organization={Some Institute of Technology, Department
-Name},addressline={Street Address},city={City},postcode={Postal
-Code},postcodesep={}}
-\affiliation[2]{organization={Another University, Department
-Name},addressline={Street Address},city={City},postcode={Postal
-Code},postcodesep={}}
+\affiliation[1]{organization={University College London, Divisions of
+Psychiatry and Psychology and Language Science},addressline={1-19
+Torrington Place},city={London, UK},country={United
+Kingdom},countrysep={,},postcode={WC1E 7HB},postcodesep={}}
+\affiliation[2]{organization={Hospital Gregorio Marañón, Department of
+Psychiatry},addressline={46 C. del
+Dr.~Esquerdo},city={Madrid},country={Spain},countrysep={,},postcode={28007},postcodesep={}}
+\affiliation[3]{organization={University of Southampton, Centre for
+Innovation in Mental Health (CIMH), School of
+Psychology},addressline={Highfield Campus, Building
+44},city={Southampton},country={United
+Kingdom},countrysep={,},postcode={SO17 1BJ},postcodesep={}}
 
 \cortext[cor1]{Corresponding author}
-\fntext[fn1]{This is the first author footnote.}
-\fntext[fn2]{Another author footnote, this is a very long footnote and
-it should be a really long footnote. But this footnote is not yet
-sufficiently long enough to make two lines of footnote text.}
-\fntext[fn3]{Yet another author footnote.}
 
 \begin{abstract}
-This is the abstract. Lorem ipsum dolor sit amet, consectetur adipiscing
-elit. Vestibulum augue turpis, dictum non malesuada a, volutpat eget
-velit. Nam placerat turpis purus, eu tristique ex tincidunt et. Mauris
-sed augue eget turpis ultrices tincidunt. Sed et mi in leo porta
-egestas. Aliquam non laoreet velit. Nunc quis ex vitae eros aliquet
-auctor nec ac libero. Duis laoreet sapien eu mi luctus, in bibendum leo
-molestie. Sed hendrerit diam diam, ac dapibus nisl volutpat vitae.
-Aliquam bibendum varius libero, eu efficitur justo rutrum at. Sed at
-tempus elit.
+To follow
 \end{abstract}
@@
 \begin{keyword}
-    keyword1 \sep 
-    keyword2
+    depression \sep adolescents \sep antidepressants \sep 
+    psychotherapy
 \end{keyword}
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, boxrule=0pt, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced]}{\end{tcolorbox}}\fi
 
-Please make sure that your manuscript follows the guidelines in the
-Guide for Authors of the relevant journal. It is not necessary to
-typeset your manuscript in exactly the same way as an article, unless
-you are submitting to a camera-ready copy (CRC) journal.
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
-For detailed instructions regarding the elsevier article class, see
-\url{https://www.elsevier.com/authors/policies-and-guidelines/latex-instructions}
+Depression is the leading cause of disability in adolescents and
+influential guidelines recommend that it be treated with either
+psychotherapy or anti-depressant medication or their combination. The
+evidence base for this recommendation typically derives from the
+appraisal of randomised controlled trials (RCTs) in which one modality
+(psychotherapy or anti-depressants) are compared against a control
+condition. In this paper we identify a series of fundamental problems
+with this appraisal and make recommendations on how it can be improved.
 
-\hypertarget{bibliography-styles}{%
-\section{Bibliography styles}\label{bibliography-styles}}
+Guidelines make implicit and explicit \ldots{} comparisons\ldots{}
 
-Here are two sample references: \citet{Feynman1963118}
-\citet{Dirac1953888}.
+Network metanalyses\ldots{}
 
-By default, natbib will be used with the \texttt{authoryear} style, set
-in \texttt{classoption} variable in YAML. You can sets extra options
-with \texttt{natbiboptions} variable in YAML header. Example
+Jureidini approach\ldots summarises.
 
-\begin{verbatim}
-natbiboptions: longnamesfirst,angle,semicolon
-\end{verbatim}
+This state of affairs is reflected in textbooks and also in what
+trainees in psychiatry and psychology learn QUOTE.
 
-There are various more specific bibliography styles available at
-\url{https://support.stmdocs.in/wiki/index.php?title=Model-wise_bibliographic_style_files}.
-To use one of these, add it in the header using, for example,
-\texttt{biblio-style:\ model1-num-names}.
+Yet, is this approach correct?
 
-\hypertarget{using-csl}{%
-\subsection{Using CSL}\label{using-csl}}
+This approach relies on a (explicit or more often implicit) comparison
+of the two treatment modalities. Ideally, a comparison between the
+treatment modalities should be direct, that is head to head. Only one
+such trial exists in adolescent depression (from the TADS study, see
+below) which showed that fluoxetine was superior to both cognitive and
+behavioural therapy (CBT) as well as placebo, and that CBT did not
+differentiate from placebo. Apart from this one study, all other
+comparisons indirect, that is, they have to be inferred from comparing
+studies where an antidepressant or a psychotherapy is compared to a
+control condition; the control conditions for antidepressant studies is
+the placebo (standard also in the rest of medicine), whilst controls for
+psychotherapy studies can vary substantially from waiting list, to
+treatment as usual to an attention control, such as psychoeducation.
+These comparisons therefore have to rely on testing whether the
+following simple equality holds or not,
 
-If \texttt{cite-method} is set to \texttt{citeproc} in
-\texttt{elsevier\_article()}, then pandoc is used for citations instead
-of \texttt{natbib}. In this case, the \texttt{csl} option is used to
-format the references. By default, this template will provide an
-appropriate style, but alternative \texttt{csl} files are available from
-\url{https://www.zotero.org/styles?q=elsevier}. These can be downloaded
-and stored locally, or the url can be used as in the example header.
+\begin{equation}\protect\hypertarget{eq-1}{}{Effect_{Med} = Effect_{Psy}}\label{eq-1}\end{equation}
 
-\hypertarget{equations}{%
-\section{Equations}\label{equations}}
+where \emph{Effect} denotes the effect on depression that either
+medication (\emph{Med} ) or psychotherapy (\emph{Psy}) have. This
+comparison is achieved by comparing some measure of effect,
+e.g.~percentage response or standardised mean difference, for each
+medication and psychotherapy. The simplest way of doing such a
+comparison is to take pooled estimates of such effects from metanalyses
+of each anti-depressants and psychotherapy and compare them informally.
+A more formal way of doing this is through a network metanalysis, which
+uses any direct comparisons to infer indirect ones.
 
-Here is an equation: \[ 
-  f_{X}(x) = \left(\frac{\alpha}{\beta}\right)
-  \left(\frac{x}{\beta}\right)^{\alpha-1}
-  e^{-\left(\frac{x}{\beta}\right)^{\alpha}}; 
-  \alpha,\beta,x > 0 .
-\]
+Yet for the indirect comparison to be valid, several assumptions need to
+hold. The most important of these assumptions can be summarised using
+the technical term \emph{ceteris paribus}, meaning that the results of
+this comparison are valid if all else is equal. Two important such
+assumptions are: a) that the control conditions for each antidepressant
+and psychotherapy trials are equal---we call this the \emph{equality of
+controls} assumption. b) that the effects of each treatment modality
+have been derived from the same underlying population, that is that the
+people who have received the treatment are similar on important
+parameters on average--this we call the \emph{one population}
+assumption.
 
-Inline equations work as well: \(\sum_{i = 2}^\infty\{\alpha_i^\beta\}\)
+Starting with the \emph{equality of controls}, its importance can be
+easily intuited by expanding equation 1 to include the comparisons on
+which each side of that equation rests:
+
+\begin{equation}\protect\hypertarget{eq-2}{}{Effect_{MedActive} - Effect_{MedControls} = Effect_{PsyActive} - Effect_{PsyControls}}\label{eq-2}\end{equation}
+
+where MedActive and PsyActive are the active arms of antidepressant and
+psychotherapy trials, respectively, and MedControls and PsyControls the
+respective control arms. The assumption here has to be that the controls
+are equal, that is, \[ Effect_{MedControls} = Effect_{PsyControls}\]. A
+few simple examples help illustrate why this assumption is important Let
+the two modalities of treatment be medication and surgery, and let there
+be a trial for each modality. In the medication trial 80\% of
+participants respond to the antihypertensive and only 40\% to placebo;
+in the surgery trial, 40\% of people respond to surgery and 0\% to sham.
+If one relied on Equation 1 to compare the treatments they would arrive
+at the absurd conclusion that the two treatments are equal and recommend
+to a patient that it does not really matter which one they choose.
+Playing around with numbers in which no equality of the respective
+control arms is required, leads to other risible conclusions.
+
+Yet, surprisingly, a focus on the equality of controls is largely absent
+from appraisals of the evidence of medication and psychotherapy.
+
+Moving on to the \emph{one population} assumption, this can be
+formalised
+
+\citet{stringarisDevelopmentalPathwaysChildhood2014}
 
@@
 
-Figure~\ref{fig-meaningless} is generated using an R chunk.
-
 \begin{figure}
 
-{\centering \includegraphics[width=0.5\textwidth,height=\textheight]{elsevier_files/figure-pdf/fig-meaningless-1.pdf}
+\includegraphics[width=12.5in,height=\textheight]{forestplot.png} \hfill{}
 
-}
-
-\caption{\label{fig-meaningless}A meaningless scatterplot}
+\caption{Forest Plot of Control Arms by the Control Arm of Each
+Treatment Modality.}
 
@@
 
-\hypertarget{tables-coming-from-r}{%
-\section{Tables coming from R}\label{tables-coming-from-r}}
+\begin{verbatim}
+\end{verbatim}
 
-Tables can also be generated using R chunks, as shown in
-Table~\ref{tbl-simple} example.
+\hypertarget{tables-coming-from-rtable}{%
+\section{Tables coming from RTable}\label{tables-coming-from-rtable}}
 
@@
 
-\renewcommand\refname{References}
-  \bibliography{bibliography.bib}
+  \bibliography{emotion\_concepts\_paper.bib}
 

### 2024-01-03 elsevier/elsevier.tex
Having problems with my git, hoping this will fix merge errors

--- 2023-12-26 elsevier/CopyOfelsevier.tex
@@
 \end{frontmatter}
-    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, enhanced, sharp corners]}{\end{tcolorbox}}\fi
+    \ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, enhanced, sharp corners]}{\end{tcolorbox}}\fi
 

### 2024-01-03 Script for cleaning merged dataset.R

@@ -15,7 +15,7 @@ df_full_med <- read.csv("Full Medication Dataset.csv")
 merged_dataset <- bind_rows(df_full_med, df_full_psych)
 
 # fix column ordering
-merged_dataset <- select(merged_dataset, -c(primary, hierarchy, time))
+merged_dataset <- dplyr:: select(merged_dataset, -c(primary, hierarchy, time))
 merged_dataset <- merged_dataset %>% relocate(descr_active, .after = control_type)
 merged_dataset <- merged_dataset %>% relocate(descr_control, .after = descr_active)
 merged_dataset <- merged_dataset %>% relocate(mean_age, .after = age_group)
@@ -239,7 +239,7 @@ sum(is.na(filter_test$cohens_d_active))
 sum(is.na(filter_test$cohens_d_control))
 
 # start looking at demographics, baseline and post means, and cohens d per arm
-df_demographics <- df_first_row %>% select(study, year, psy_or_med, active_type, control_type, descr_active, descr_control,
+df_demographics <- df_first_row %>% dplyr:: select(study, year, psy_or_med, active_type, control_type, descr_active, descr_control,
                                            instrument_name, baseline_mean_active, baseline_sd_active, baseline_n_active,
                                            baseline_mean_control, baseline_sd_control, baseline_n_control, 
                                            post_mean_active, post_sd_active, post_n_active, post_mean_control, post_sd_control, post_n_control,
@@ -249,7 +249,7 @@ df_demographics <- df_first_row %>% select(study, year, psy_or_med, active_type,
 df_demographics$descr_active <- ifelse(is.na(df_demographics$descr_active), df_demographics$active_type, df_demographics$descr_active)
 df_demographics$descr_control <- ifelse(is.na(df_demographics$descr_control), df_demographics$control_type, df_demographics$descr_control)
 
-df_demographics <- df_demographics %>%  select(-c(active_type, control_type))
+df_demographics <- df_demographics %>%  dplyr::select(-c(active_type, control_type))
 df_demographics <- df_demographics %>%  arrange(psy_or_med)
 
 # check how many studies we have baseline means for primary instrument
[…]

### 2024-01-03 apples_and_oranges.qmd
Few small changes - checking df_long_for_metan and added method re imputation of missing SDs and means

@@
   - name: Charlotte Burman
-    email: c.burman@ucl.ac.uk
+    email: charlotte.burman@ucl.ac.uk
     affiliations:
@@
   - name: Dayna Bhudia
-    email: d.bhudia@ucl.ac.uk
+    email: dayna.bhudia@ucl.ac.uk
     affiliations:
@@
 
-Clinicians across medicine and other health professions are faced with choices betweent different treatment modalities for their patients, be it between surgical or medical (drug-based) treatments or, in the case of adolescent depression, between psychotherapy and antidepressant medication.
+Clinicians across medicine and other health professions are faced with choices between different treatment modalities for their patients, be it between surgical or medical (drug-based) treatments or, in the case of adolescent depression, between psychotherapy and antidepressant medication.
 To make informed choices, clinicians rely on the extant evidence, frequently summarised in the form of national guidelines or other treatment recommendations.
 Such a comparison is inherent in the internationally influential UK National Institute of Clinical Excellence (NICE) guidelines for adolescent depression which recommend that youth be first offered psychological therapy over medication for most presentations of depression.
-Such comparisons between the etwo treatment modalities are inherent in other recommendations, e.g.
+Such comparisons between the two treatment modalities are inherent in other recommendations, e.g.
 the practice parameter issued by the American Academy of Child and Adolescent Psychiatry or the Royal Australian and New Zealand College of Psychiatrists.
 
-These recommendations are not based on head to head trials between modalities; only one head-to-head trial exists in adolescent depression Instead, they rely on the comparison of the results of randomised controlled trials (RCTs) of each modality against RCTs of the other.
+These recommendations are not based on head to head trials between modalities; only one head-to-head trial exists in adolescent depression.
+Instead, they rely on the comparison of the results of randomised controlled trials (RCTs) of each modality against RCTs of the other.
 In other words, it rests on a comparison of comparisons.
@@
 
-NOTE: **Charlotte** to please check code lines 986 to 1121
+NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: In progress.
 NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect.
 In the beginning of the results below, I explain in detail what is missing where.
+**CB**: I've checked and there are fewer psy active conditions that I expected - it seems some of the trials with multiple active arms have been filtered out.
+Also, for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
+The numbers look right for med studies.
 
@@
 In general state here the rules we used citing the Cochrane book.
+**CB** Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods recommended by X (citation), in the following order.
+If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
+For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
+If the SD was not available at either time point, an average SD was calculated by taking the mean of the SDs of all trials of the same type (i.e.
+psy or med) using the same instrument.
+These average SDs were calculated for each time point and for each arm (control and active).
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis (citation).
 

### 2024-01-03 apples_and_oranges.qmd
Fixed error causing distinct active conditions to be excluded

@@
 turn_long_active_type <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, active_type, psy_or_med, baseline_n_active, cohens_d_active) %>% 
+  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active) %>% 
   pivot_longer(cols = c(cohens_d_active), 
@@
 # also rename active_type to treatment for the merge below.
-turn_long_active_type <- rename(turn_long_active_type,treatment = active_type,
+turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
                                 baseline_n = baseline_n_active)

### 2024-01-03 apples_and_oranges.qmd
changes to figures and tables

@@
 ---
-title: Apples and Oranges in Adolescent Depression Treatments.
-subtitle: A conceptual and quantiative re-appraisal of control arms in clinical trials.
+title: Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.
+subtitle: Re-visiting the relative efficacy Control Conditions..
 author:
@@
         - ref: ucl_1
+  - name: Lucy Foulkes
+    email: lucy.foulkes@psych.ox.ac.uk
+    affiliations:
+        - id: OU
+          name: University of Oxford
+          department: Experimental Psychology
+          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
+          city: Oxford
+          postal-code: OX2 6GG
+          country: United Kingdom
     note:
@@
 
+Figure 1 graphs the results with the means of each level alongside their confidence intervals.
 Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metanalyses.
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# for some reason doesn't work, but will make work.
-# tab_1_df <- df_mean_coefs_from_sim[, 1:length(df_mean_coefs_from_sim)-1]
-# knitr:: kable(tab_1_df, digits = 2, 
-#              col.names = c('Trial Arm', 'Beta', 'SE', 'Upper CI', 'Lower CI') )
-```
-
-Figure 1 graphs the results with the means of each level alongside their confidence intervals.
+As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms.
+Table 2 illustrates this with the output of one of the simulated models.
 
@@
 
-ggplot(df_mean_coefs_from_sim, aes(x = mean_coefficient, y = 1:nrow(df_mean_coefs_from_sim),
+plot_means <- ggplot(df_mean_coefs_from_sim, aes(x = mean_coefficient, y = 1:nrow(df_mean_coefs_from_sim),
                                    colour = condition, label = text_label)) +
@@
   theme_minimal() +
-  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Type and Treatment Arm",
+  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
        subtitle = "metanalytically derived estimates of within group changes") +
@@
 
+png("plotted_means.png")
+plot_means
+dev.off()
+
 ```
 
-As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms.
-Table 2 illustrates this with the output of one of the simulated models.
+![Fig 1. Means of the Four Trial Arms](plotted_means.png){width=50%}
 
@@
 
+coefficients_from_contrasts_medcontrol_psy_control$zed_value <- coefficients_from_contrasts_medcontrol_psy_control$Beta/
+coefficients_from_contrasts_medcontrol_psy_control$SE
+
+coefficients_from_contrasts_medcontrol_psy_control$p_value <- format(1 - pnorm(coefficients_from_contrasts_medcontrol_psy_control$zed_value), scientific = TRUE)
+
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: Table 1
+#| tbl-cap: Means for the four Trial Arms alongside 95% Confidence Intervals
+tab_1_df <- df_mean_coefs_from_sim[, 1:length(df_mean_coefs_from_sim)-1]
 
-knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control, col.names = c("Beta", "SE", "Lower CI", "Upper CI"), digits = 2)
+knitr:: kable(tab_1_df, digits = 2)
 ```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: Table 2
+#| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
+knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)
+
+```

### 2024-01-04 apples_and_oranges.qmd
Some very minor changes

--- 2024-01-03 apples_and_oranges.qmd
@@
 
+df_appl_v_orange <- df_appl_v_orange %>% 
+  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))
+
 # Step 1: keep only the rows with the top instrument in our hierarchy
@@
 # also rename active_type to treatment for the merge below.
-turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
+turn_long_active_type <- rename(turn_long_active_type, treatment = descr_active,
                                 baseline_n = baseline_n_active)

### 2024-01-04 apples_and_oranges.qmd
A few notes

@@
 
-NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: In progress.
+NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: Done.
 NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect.
@@
 **CB**: I've checked and there are fewer psy active conditions that I expected - it seems some of the trials with multiple active arms have been filtered out.
-Also, for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
+I have now fixed this and the numbers look correct.
 The numbers look right for med studies.
+One thing - for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
 

### 2024-01-04 apples_and_oranges.qmd
several simplifications for now, will work more on it later. Also added a sensitivity analysis at the end.

--- 2024-01-04 apples_and_oranges.qmd
@@
 
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))
-
 # Step 1: keep only the rows with the top instrument in our hierarchy
@@
 # also rename active_type to treatment for the merge below.
-turn_long_active_type <- rename(turn_long_active_type, treatment = descr_active,
+turn_long_active_type <- rename(turn_long_active_type,treatment = descr_active,
                                 baseline_n = baseline_n_active)
@@
 
-# specify the model 
+# create a function for metaregression
+
+run_metaregression <- function(list_of_datasets, model_formula) {
+  list_model_meta_reg <- list()
+
+  for (i in seq_along(list_of_datasets)) {
+    list_model_meta_reg[[i]] <- metafor::rma(yi = cohens_d,
+                                             sei = simulated_se,
+                                             data = list_of_datasets[[i]],
+                                             method = "ML",
+                                             mods = model_formula,
+                                             test = "knha")
+  }
+
+  return(list_model_meta_reg)
+}
+
 model_1 <- as.formula(~ four_level_var)
-
-# run the metaregression
-list_model_1_meta_reg <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_model_1_meta_reg[[i]] <- rma(yi = cohens_d, 
-                                    sei = simulated_se, 
-                                    data = list_df_simulated[[i]] , 
-                                    method = "ML", 
-                                    mods = model_1 , 
-                                    test = "knha")
-
-}
+list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
 
@@
 ```
+
+We then examined whether restricting studies to the trials (US-) licensed medication fluoxetine and escitalopram and the most widely used and evidence-based psychological treatment, namely CBT would change results.
+As can be seen, the coefficient of the difference between placebo and psychotherapy control condition is very strong as judged by the z-value of the difference (8.8), and comaprable to the overall results.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# filter dataset to include only those ids with cbt fluox or escitalopram
+
+# grab those ids
+cbt_fluox_esc_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+# subset all dataframes in the list
+list_cbt_fluox_esc_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                        %in% cbt_fluox_esc_study_ids,]
+
+}
+
+# use this model as above
+model_1 <- as.formula(~ four_level_var)
+
+# apply the function to the list of cbt, fluox, esc
+list_model_1_meta_reg_cbt_fluox_esc <- run_metaregression(list_cbt_fluox_esc_study, model_1)
+
+# now use the function to extract the coefficients
+
+list_model_1_meta_reg_cbt_fluox_esc[[1]]
+```

### 2024-01-04 apples_and_oranges.qmd
A few small edits to description of studies section of results

@@
 In general state here the rules we used citing the Cochrane book.
-**CB** Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods recommended by X (citation), in the following order.
+**CB** Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised by X (citation), in the following order.
 If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
 For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
-If the SD was not available at either time point, an average SD was calculated by taking the mean of the SDs of all trials of the same type (i.e.
-psy or med) using the same instrument.
-These average SDs were calculated for each time point and for each arm (control and active).
+If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
 Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis (citation).
@@
 
-df_long_for_metan <- read.csv("~/apples_and_oranges/df_long_for_metan")
+df_long_for_metan <- read.csv("df_long_for_metan")
 
@@
 
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies of which `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` belonged to active and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` to control arms of antidepressant trials; there were also `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` psychotherapy active and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` trials.
-Note that active and control arms do not exactly match because some studies used more than one control or active arm.
-There were also missing data on `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms where data were missing for medication active, mediaction contrl, psychotherapy active, and psychotherapy control respectively.
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
+Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
 

### 2024-01-04 apples_and_oranges.qmd
Few small things

@@
 
-where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the study respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
+where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
 NOTE **Charlotte**, please add note here with what we did to impute SDs where missing, e.g.
@@
 # Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
-# for the CDRS-R total score in 53 clinic-referred6- to 12-year-olds.
+# for the CDRS-R total score in 53 clinic-referred 6- to 12-year-olds.
 
 ### A few more tidying things from Argyris before doing metanalyses
-# # discovered an error in the percentage women o fthe Fristad study. I have checked in the
+# # discovered an error in the percentage women of the Fristad study. I have checked in the
 # # cuijpers dataset and the correct percentage is 43.1, but could not verify with the paper as it is not in 
 # # our folder and after a quick search I could not find it online either. Messaged Charlotte on Discord to
-# # check again.
+# # check again. # CB checked and all good.
 df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1

### 2024-01-04 apples_and_oranges.qmd
several changes with brining functions up etc.

@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+###########Libraries needed
+library(tidyverse)
+library(truncnorm)
+library(metafor)
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#############Some custom made functions#############
+
+###### 1. Simulation Function for SEs
+simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
+                                                                                              # of unique ids to which a correlation coef
+                                                                                              # is allocated.
+  set.seed(seed)
+
+  # Empty list to store simulated dfs
+  list_df_simulated <- list()
+
+  for (i in 1:num_repetitions) {
+    # Simulate the vector
+    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations
+
+    # Create a copy of the original dataframe
+    df_simulated_copy <- df
+
+    # Add/update the sims column
+    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]
+
+    # Remove duplicated columns
+    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]
+
+    # Calculate the ses
+    df_simulated_copy <- df_simulated_copy %>% 
+      group_by(new_study_id, baseline_n) %>% 
+      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
+                                   (cohens_d^2/(2*baseline_n))))
+
+    # Add the simulated dataframe to the list
+    list_df_simulated[[i]] <- df_simulated_copy
+  }
+
+  return(list_df_simulated)
+}
+
+###############2. Simulation function for metaregression
+run_metaregression <- function(list_of_datasets, model_formula) {
+  list_model_meta_reg <- list()
+
+  for (i in seq_along(list_of_datasets)) {
+    list_model_meta_reg[[i]] <- metafor::rma(yi = cohens_d,
+                                             sei = simulated_se,
+                                             data = list_of_datasets[[i]],
+                                             method = "ML",
+                                             mods = model_formula,
+                                             test = "knha")
+  }
+
+  return(list_model_meta_reg)
+}
+
+###########3. Function to extract parameters (coefs, ses, CI) for each level of the dummy #variable
+# it is a slightly awkward one, because I couldnt' come up with a better way to add the intercept to #each coefficient
+# given the named output of the built in coef function. 
+# here I exctract the coeffcients
+extract_coefficients_func <- function(df_with_coefs){
+  list_coefs <- list()
+  coefs <- 0
+  coefficient_output <- 0
+
+  for(i in 1: length(coefficients(df_with_coefs))){
+
+    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
+                         length(coefficients(df_with_coefs)) - 1 ))
+    coefs[i] <- coef(df_with_coefs)[[i]]
+
+    coefficient_output <- temp_vec + coefs
+
+    st_error_output <- df_with_coefs$se
+
+    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))
+
+    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
+    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
+  }
+  return (df_coefficients )
+}
+
+############4. Function to get the means out of the extracted parameters
+# here the argument list_of_dfs is the list of extracted coefficients that you get out of the #extract_coefficients_func
+# which itself you get from the run_metaregression function. The argument conditions refers to #the levels of the variable that describes each study arm
+
+calculate_mean_coefs_ses <- function(list_of_dfs, conditions) {
+  df_coefs <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
+  df_se <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
+
+  for (i in 1:length(list_of_dfs)) {
+    for (j in 1:length(conditions)) {
+      df_coefs[i, j] <- list_of_dfs[[i]]$coefficients[j]
+      df_se[i, j] <- list_of_dfs[[i]]$se[j]
+    }
+  }
+
+  df_mean_coefs_ses <- data.frame(
+    coef_means = colMeans(df_coefs),
+    se_means = colMeans(df_se)
+  )
+
+  df_mean_coefs_ses$lower_ci <- df_mean_coefs_ses$coef_means - 1.96 * df_mean_coefs_ses$se_means
+  df_mean_coefs_ses$upper_ci <- df_mean_coefs_ses$coef_means + 1.96 * df_mean_coefs_ses$se_means
+
+  return(df_mean_coefs_ses)
+}
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 library(tidyverse)
@@
 
-# I have created a function for this
-library(tidyverse)
-library(truncnorm)
+# Use the function I have created for this
 
 df_long_for_metan <- read.csv("df_long_for_metan")
-
-simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
-                                                                                              # of unique ids to which a correlation coef
-                                                                                              # is allocated.
-  set.seed(seed)
-
-  # Empty list to store simulated dfs
-  list_df_simulated <- list()
-
-  for (i in 1:num_repetitions) {
-    # Simulate the vector
-    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations
-
-    # Create a copy of the original dataframe
-    df_simulated_copy <- df
-
-    # Add/update the sims column
-    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]
-
-    # Remove duplicated columns
-    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]
-
-    # Calculate the ses
-    df_simulated_copy <- df_simulated_copy %>% 
-      group_by(new_study_id, baseline_n) %>% 
-      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
-                                   (cohens_d^2/(2*baseline_n))))
-
-    # Add the simulated dataframe to the list
-    list_df_simulated[[i]] <- df_simulated_copy
-  }
-
-  return(list_df_simulated)
-}
 
@@
 
+  df_count_studies$condition <- factor(df_count_studies$condition) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
+
 df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
@@
 
-# create a function for metaregression
+######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
+# A) the overall sample
+# B) the CBT vs Fluox and Escitalopram sample
+# C) the no WL sample
 
-run_metaregression <- function(list_of_datasets, model_formula) {
-  list_model_meta_reg <- list()
+# A. Estimate Means and CIs for the overall ----------------------------------
+# specify model
+model_1 <- as.formula(~ four_level_var)
 
-  for (i in seq_along(list_of_datasets)) {
-    list_model_meta_reg[[i]] <- metafor::rma(yi = cohens_d,
-                                             sei = simulated_se,
-                                             data = list_of_datasets[[i]],
-                                             method = "ML",
-                                             mods = model_formula,
-                                             test = "knha")
-  }
+# run metareg function 
+# here you can use the simulated results directly
+list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
 
-  return(list_model_meta_reg)
+# extract coefs from the  list
+list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
+
+# calculate mean coefs and ses
+df_mean_coefs_from_sim <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)
+
+ df_mean_coefs_from_sim <- data.frame(cbind(condition,df_mean_coefs_from_sim))
+
+# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
+# first grab ids for those studies
+cbt_fluox_esc_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_cbt_fluox_esc_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% cbt_fluox_esc_study_ids,]
+
 }
@@
 model_1 <- as.formula(~ four_level_var)
-list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
 
-# list_model_1_meta_reg[[2]]
+# apply the metareg function to the list of cbt, fluox, esc
+list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)
 
-# Function to extract parameters (coefs, ses, CI) for each level of the dummy variable
-# it is an awkward one, because I couldnt' come up with a better way to add the intercept to each coefficient
-# given the named output of the built in coef function. 
-# here I exctract the coeffcients
-extract_coefficients_func <- function(df_with_coefs){
-  list_coefs <- list()
-  coefs <- 0
-  coefficient_output <- 0
+# extract coefs from the list for cbt fluox escit
+means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
 
-  for(i in 1: length(coefficients(df_with_coefs))){
+# calculate mean coefs and ses
+conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)
+ coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
 
-    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
-                         length(coefficients(df_with_coefs)) - 1 ))
-    coefs[i] <- coef(df_with_coefs)[[i]]
+# C. Estimate Means and CIs without WL ---------------------------------------
+# grab the ids for no waitlist
+no_wl_ids <-
+  df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
 
-    coefficient_output <- temp_vec + coefs
+# use them to loop over the simulated list to subset all the dataframes.
+list_no_wl <- list()
 
-    st_error_output <- df_with_coefs$se
+for(i in 1: length(list_df_simulated)){
 
-    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))
+  list_no_wl[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                            %in% no_wl_ids,]
 
-    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
-    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
-  }
-  return (df_coefficients )
 }
 
-# dummy_var_means <- extract_coefficients_func(list_model_1_meta_reg[[1]])
+# use this model as above
+model_1 <- as.formula(~ four_level_var)
 
-list_dummy_var_means <-lapply(list_model_1_meta_reg, extract_coefficients_func)
+# apply the function to the list of cbt, fluox, esc
+list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
 
-# this is the way to get the means and SEs from the simulation across all datasets.
+# now use the function to extract the coefficients
+means_no_wl <-  lapply(list_model_1_no_wl, extract_coefficients_func)
 
-df_mean_coefs_from_sim <- data.frame(
+# run the mean function for no wl
+conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, conditions)
+coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
 
-  condition = levels(list_df_simulated[[1]]$four_level_var),
+ #add the ns of studies FIX THIS
 
-  mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),
+ df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
 
-  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[4,2])))
-
-)
-
-# and add the CIs
-
-df_mean_coefs_from_sim$upper_ci <- df_mean_coefs_from_sim$mean_coefficient + 1.96 * df_mean_coefs_from_sim$mean_se
-
-df_mean_coefs_from_sim$lower_ci <- df_mean_coefs_from_sim$mean_coefficient - 1.96 * df_mean_coefs_from_sim$mean_se
-# df_mean_coefs_from_sim # this is now the dataframe containing the means you need for plotting.
-
-#also, add the n of studies non missing from variable created above
-#important first create the same condition variable: 
-df_count_studies_not_missing$condition <- str_replace_all(df_count_studies_not_missing$condition, "_", " ")
-
-# I needed to join them because of the relevelling, the rows would not align otherwise.
-# df_mean_coefs_from_sim <- right_join(df_mean_coefs_from_sim, df_count_studies_not_missing)
-
-# need to merge this with the count studies variable to obtain the ks
-library(forcats)
-ordering_criterion <- unique(df_mean_coefs_from_sim$condition)
-
-# 
-df_count_studies_not_missing <- df_count_studies_not_missing %>% arrange(ordering_criterion) %>%
-  mutate(condition = fct_relevel(condition, levels = unique(condition)))
-# I will use this for plotting below.
+# here are all three of them OVERALL, CBT and WL together. We may want to display them together. 
+# df_all_coefficients <- cbind(df_mean_coefs_from_sim, coef_and_se_means_cbt_fluox_esc_study,coef_and_se_means_no_wl)
 
@@
 As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.
-
-NOTE: **Charlotte**, this should be moved to the supplement at Table 2
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-variability_in_sims <- data.frame (mean_coefficient = c(mean(sapply(list_dummy_var_means, function(df) df[1,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[2,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[3,1])),
-                      mean(sapply(list_dummy_var_means, function(df) df[4,1]))),
-
-sd_coefficient = c(sd(sapply(list_dummy_var_means, function(df) df[1,1])),
-                      sd(sapply(list_dummy_var_means, function(df) df[2,1])),
-                      sd(sapply(list_dummy_var_means, function(df) df[3,1])),
-                      sd(sapply(list_dummy_var_means, function(df) df[4,1]))),
-
-  mean_se = c(mean(sapply(list_dummy_var_means, function(df) df[1,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[2,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[3,2])),
-              mean(sapply(list_dummy_var_means, function(df) df[4,2]))),
-
-  sd_se = c(sd(sapply(list_dummy_var_means, function(df) df[1,2])),
-              sd(sapply(list_dummy_var_means, function(df) df[2,2])),
-              sd(sapply(list_dummy_var_means, function(df) df[3,2])),
-              sd(sapply(list_dummy_var_means, function(df) df[4,2])))
-)
-
-```
 
@@
 df_mean_coefs_from_sim$text_label[i] <-  paste(
-   "k = ", df_count_studies_not_missing $n[i],"\n", 
-   round(df_mean_coefs_from_sim$mean_coefficient[i], 2),
+   "k = ", df_mean_coefs_from_sim$n[i],"\n", 
+   round(df_mean_coefs_from_sim$coef_means[i], 2),
    "[" ,
@@
 
-plot_means <- ggplot(df_mean_coefs_from_sim, aes(x = mean_coefficient, y = 1:nrow(df_mean_coefs_from_sim),
+plot_means <- ggplot(df_mean_coefs_from_sim, aes(x = coef_means, y = 1:nrow(df_mean_coefs_from_sim),
                                    colour = condition, label = text_label)) +

### 2024-01-05 apples_and_oranges.qmd
lots of new code

@@
 
-###########3. Function to extract parameters (coefs, ses, CI) for each level of the dummy #variable
+#########2. Function to count studies with missingness etc.
+
+count_studies <- function(df) {
+  df_count_studies <- df %>%
+    group_by(psy_or_med, arm_effect_size) %>%
+    count(is.na(cohens_d)) %>%
+    rename(is_missing = `is.na(cohens_d)`) %>%
+    mutate(
+      condition = case_when(
+        psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+        psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+        psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+        psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control"
+      )
+    )
+
+  df_count_studies$condition <- factor(df_count_studies$condition)  # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
+
+  return(df_count_studies)
+}
+
+##########3. Function to extract mean coefficients and to extract model characteristics
+
+aggregate_model_results <- function(list_model_1_meta_reg, condition) {
+  df_coefs <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
+  df_se <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
+  df_z_value <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
+  df_lower_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
+  df_upper_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
+  tau_sq <- rep(0, length(list_model_1_meta_reg))
+  i_sq <- rep(0, length(list_model_1_meta_reg))
+  k <- rep(0, length(list_model_1_meta_reg))
+  r_sq <- rep(0, length(list_model_1_meta_reg))
+
+  for (i in 1:length(list_model_1_meta_reg)) {
+    for (j in 1:length(condition)) {
+      df_coefs[i, j] <- list_model_1_meta_reg[[i]]$beta[[j]]
+      df_se[i, j] <- list_model_1_meta_reg[[i]]$se[[j]]
+      df_z_value[i, j] <- list_model_1_meta_reg[[i]]$zval[[j]]
+      df_lower_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.lb[[j]]
+      df_upper_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.ub[[j]]
+      tau_sq[i] <- list_model_1_meta_reg[[i]]$tau2
+      i_sq[i] <- list_model_1_meta_reg[[i]]$I2
+      k[i] <- list_model_1_meta_reg[[i]]$k
+      r_sq[i] <- list_model_1_meta_reg[[i]]$R2
+    }
+  }
+
+  df_coefficients_model <- data.frame(
+    coefficients = colMeans(df_coefs),
+    se = colMeans(df_se),
+    z_value = colMeans(df_z_value),
+    lower_ci = colMeans(df_lower_ci),
+    upper_ci = colMeans(df_upper_ci),
+    tau_sq = mean(tau_sq),
+    i_sq = mean(i_sq),
+    k = mean(k),
+    r_sq = mean(r_sq)
+  )
+
+  return(df_coefficients_model)
+}
+
+###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy #variable. The output is used below in 5.
 # it is a slightly awkward one, because I couldnt' come up with a better way to add the intercept to #each coefficient
@@
 
-############4. Function to get the means out of the extracted parameters
+############5. Function to get the means out of the SMDs (this is similar to Func 3 and I should at some point create one more general one)
 # here the argument list_of_dfs is the list of extracted coefficients that you get out of the #extract_coefficients_func
@@
   return(df_mean_coefs_ses)
+}
+
+###############6. Function for plotting the SMDs
+library(ggplot2)
+library(stringr)
+
+plot_means_function <- function(dataframe, subtitle) {
+  dataframe$text_label <- 0
+
+  for (i in 1:nrow(dataframe)) {
+    dataframe$text_label[i] <- paste(
+      "k = ", dataframe$n[i], "\n",
+      round(dataframe$coef_means[i], 2),
+      "[" ,
+      round(dataframe$lower_ci[i], 2), 
+      round(dataframe$upper_ci[i], 2),
+      "]"
+    ) 
+  }
+
+  # Recode condition for ease of plotting
+  dataframe$condition <- str_replace_all(dataframe$condition, "_", " ")
+
+  # Encode colours
+  redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
+  blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")
+
+  # Plotting
+  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
+                                      colour = condition, label = text_label)) +
+    geom_point(size = 3) +
+    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
+    geom_text(vjust = +1.5, size = 4) +
+    scale_size_continuous(guide = "none") +
+    guides(colour = FALSE) + 
+    scale_color_manual(values = c(redish_palette, blueish_palette)) +
+    theme_minimal() +
+    labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
+         subtitle = subtitle) +
+    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
+    ylab("") +
+    ylim(0, nrow(dataframe) + 1) +
+    xlim(-3.0, 0.5) +
+    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
+    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
+    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
+    theme(axis.title.x = element_text(size = 14), 
+          axis.text.x  = element_text(size = 14),
+          axis.text.y = (element_blank()),
+          plot.title = element_text(size = 16),
+          plot.subtitle = element_text(size = 14)) +
+    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
+    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey", vjust = 0.5, hjust = 0)
+
+  return(plot_means)
 }
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-library(tidyverse)
-
-# describe studies
-n_unique_studies <- length(unique(df_long_for_metan$new_study_id))
-
-df_count_studies <- df_long_for_metan %>% 
-  group_by(psy_or_med, arm_effect_size) %>% 
-  count(is.na(cohens_d))
-
-df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)
-
-df_count_studies <-
-  df_count_studies %>% 
-  mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                             psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                             psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                             psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-  )
-
-  df_count_studies$condition <- factor(df_count_studies$condition) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
-
-df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
+# library(tidyverse)
+# 
+# 
+# # describe studies
+# n_unique_studies <- length(unique(df_long_for_metan$new_study_id))
+# 
+#   
+# 
+# df_count_studies <- df_long_for_metan %>% 
+#   group_by(psy_or_med, arm_effect_size) %>% 
+#   count(is.na(cohens_d))
+# 
+# 
+# df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)
+# 
+# df_count_studies <-
+#   df_count_studies %>% 
+#   mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+#                              psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+#                              psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+#                              psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+#   )
+# 
+#   df_count_studies$condition <- factor(df_count_studies$condition) # turn to factor
+#   
+#   # relevel so that medication control becomes the reference category for the regression
+#   df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
+# 
+# df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
 ```
 
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# Get Ns, run metareg, prepare graphing ------------------------------------------------------
+library(tidyverse)
+library(metafor)
 
-We then applied metaregression to obtain the means and confidence intervals of each of the four arms.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Run metaregression ------------------------------------------------------
-library(metafor)
 # add a new multilevel variable for the regression
@@
 # A. Estimate Means and CIs for the overall ----------------------------------
+
+# count studies
+# count the number of studies
+n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
+df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
+
 # specify model
@@
 
-# extract coefs from the  list
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
+
+# extract SMDs from the  list
 list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
 
-# calculate mean coefs and ses
-df_mean_coefs_from_sim <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)
+# calculate mean SMDs and ses
+df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)
 
@@
 
+# add the ns
+df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
+
 # B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-# first grab ids for those studies
+#  grab ids for those studies
 cbt_fluox_esc_study_ids <-
@@
 
-model_1 <- as.formula(~ four_level_var)
+# count the number of studies
+study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
+# CHARLOTTE please check
 
 # apply the metareg function to the list of cbt, fluox, esc
+model_1 <- as.formula(~ four_level_var)
 list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)
 
-# extract coefs from the list for cbt fluox escit
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
+
+# extract SMDs from the list for cbt fluox escit
 means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
 
-# calculate mean coefs and ses
-conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, conditions)
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
  coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
+
+# add the ns to the dataframe
+ coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n
 
@@
 
+# count studies 
+study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
+# CHARLOTTE please check
+
 # use this model as above
@@
 
-# apply the function to the list of cbt, fluox, esc
+# apply the metareg function to the list of cbt, fluox, esc
 list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
 
@@
 # run the mean function for no wl
-conditions <- unique(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, conditions)
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
 coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
 
- #add the ns of studies FIX THIS
-
- df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
+coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
+                                                     ==FALSE,]$n
 
@@
 ```
+
+NOTE: CHARLOTTE Please create a table here with the results from the count studies or study count variables that you checked in the code chunk above for each A,B and C. 
+The table for A should be added here and accompany the description below. 
+THe other two should go below as supplementary.
+As indicated in the methods we should have one overall table with all studies and all their characteristics ala Cipriani.
+
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
+Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
+
+We then applied metaregression to obtain the means and confidence intervals of each of the four arms.
+
 We examined the variability that the simulations of the correlations of the pre-post outcomes produced.
@@
 # plot results from simulated means ---------------------------------------
+# 
+subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
+plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
+print(plot_means_all)
 
-# Create summary stats text
-df_mean_coefs_from_sim$text_label <- 0
-for(i in 1: nrow(df_mean_coefs_from_sim))
-df_mean_coefs_from_sim$text_label[i] <-  paste(
-   "k = ", df_mean_coefs_from_sim$n[i],"\n", 
-   round(df_mean_coefs_from_sim$coef_means[i], 2),
-   "[" ,
- round(df_mean_coefs_from_sim$lower_ci[i],2), 
- round(df_mean_coefs_from_sim$upper_ci[i], 2),
-"]")
+subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
+plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
+print(plot_means_cbt)
 
-# recode condition for ease of plotting
-df_mean_coefs_from_sim$condition <- str_replace_all(df_mean_coefs_from_sim$condition, "_", " ")
-
-# encode colours
-redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
-blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")
-
-plot_means <- ggplot(df_mean_coefs_from_sim, aes(x = coef_means, y = 1:nrow(df_mean_coefs_from_sim),
-                                   colour = condition, label = text_label)) +
-  geom_point(size = 3) +
-  geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
-  geom_text(vjust = +1.5, size = 4) +  # Adjust vjust and size as needed
-  scale_size_continuous(guide = "none") +
-  guides(colour = FALSE) + 
-  scale_color_manual(values = c(redish_palette, blueish_palette)) +
-  theme_minimal() +
-  labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
-       subtitle = "metanalytically derived estimates of within group changes") +
-  xlab("Standardized Mean Difference (SMD) with 95% CIs") +
-  ylab("") +
-  ylim(0, nrow(df_mean_coefs_from_sim) + 1) +
-  xlim(-2.5, 0.5) +
-  geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
-  geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
-  geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
-  theme(axis.title.x = element_text(size = 14), 
-        axis.text.x  = element_text(size = 14),
-        axis.text.y = (element_blank()),
-        plot.title = element_text(size = 16),
-        plot.subtitle = element_text(size = 14))+
-  geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
-  geom_text(x = 0.2, y = 4.75, label = "Line of No Effect", color = "grey", vjust = 0.5, hjust = 0)
-
-png("plotted_means.png")
-plot_means
-dev.off()
-
-```
-
-![Fig 1. Means of the Four Trial Arms](plotted_means.png){width=50%}
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-coefs<- 0
-ses <- 0
-for(i in 1: length(list_model_1_meta_reg)){
-
-  coefs[[i]] <- coef(list_model_1_meta_reg[[i]])[[4]]  ### CAREFUL this is poor coding practice on my part
-  ses[[i]] <- list_model_1_meta_reg[[i]]$se[4] ### but I can't find another way of grabbing this estimate from the
-  ### rma object. It could go badly wrong if the relevelling isn't done consistently...CHECK MANUALLY
-  coefficients_from_contrasts_medcontrol_psy_control <- data.frame(Beta = mean(coefs), SE = mean(ses))
-}
-
-coefficients_from_contrasts_medcontrol_psy_control$lower_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta - 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE
-
-coefficients_from_contrasts_medcontrol_psy_control$upper_ci <- coefficients_from_contrasts_medcontrol_psy_control$Beta + 1.96*coefficients_from_contrasts_medcontrol_psy_control$SE
-
-coefficients_from_contrasts_medcontrol_psy_control$zed_value <- coefficients_from_contrasts_medcontrol_psy_control$Beta/
-coefficients_from_contrasts_medcontrol_psy_control$SE
-
-coefficients_from_contrasts_medcontrol_psy_control$p_value <- format(1 - pnorm(coefficients_from_contrasts_medcontrol_psy_control$zed_value), scientific = TRUE)
+subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+print(plot_means_wl)
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: Table 2
-#| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
-knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)
+# #| label: Table 2
+# #| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
+# knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# filter dataset to include only those ids with cbt fluox or escitalopram
+```{r}
+# examine the stability of the simulations
+stability_sims %>%
+  ggplot(aes(x = n_sims, y = z_value)) +
+  geom_point() +
+  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line are statistically significant)", hjust = -0.1, vjust = 0) +
+  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
+           hjust = -0.1, vjust = 0) +
+  theme_minimal() +
+  labs(
+    x = "Number of Simulations",
+    y = "z-value",
+    title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
+    subtitle = "Results from 1000 simulations with within-group standard errors"
+  )
 
-# grab those ids
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# subset all dataframes in the list
-list_cbt_fluox_esc_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                        %in% cbt_fluox_esc_study_ids,]
-
-}
-
-# use this model as above
-model_1 <- as.formula(~ four_level_var)
-
-# apply the function to the list of cbt, fluox, esc
-list_model_1_meta_reg_cbt_fluox_esc <- run_metaregression(list_cbt_fluox_esc_study, model_1)
-
-# now use the function to extract the coefficients
-
-list_model_1_meta_reg_cbt_fluox_esc[[1]]
 ```

### 2024-01-05 apples_and_oranges.qmd
one more change

@@
 # examine the stability of the simulations
-stability_sims %>%
+
+z_psy_con_vs_med_con <- 0
+for(i in 1: length(list_model_1_no_wl)){
+z_psy_con_vs_med_con[i] <- list_model_1_no_wl[[i]]$zval[[4]]
+}
+
+stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+
+stab_sims <- stability_sims %>%
   ggplot(aes(x = n_sims, y = z_value)) +
@@
                color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line are statistically significant)", hjust = -0.1, vjust = 0) +
+  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
   geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
@@
   )
+stab_sims
 

### 2024-01-05 apples_and_oranges.qmd
some more minor changes

@@
 Figure 1 graphs the results with the means of each level alongside their confidence intervals.
-Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metanalyses.
+Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metaregressions.
 As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms.
@@
 
-```{r}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # examine the stability of the simulations

### 2024-01-06 apples_and_oranges.qmd
results have more logical consistency (I hope) have added html comments for Charlotte.

@@
       cite-style: super
-
 ---
@@
 # Method
+
 ## Studies included
 
-NOTE: **Charlotte** to please check code lines 986 to 1121. **CB**: Done.
+NOTE: **Charlotte** to please check code lines 986 to 1121.
+**CB**: Done.
 NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect.
@@
 One thing - for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
+<!--# Charlotte, that's all great.
+What we now need here is an account of exactly how  we searched and how we used the other datasets.
+Follow previous examples, though in our case, it will be a lot about how we used the accounts of others.
+Please make sure to say where that we asked about missing information.
+-->
 
 ## Statistical Analysis
+
 ### Measures of Effect
+
 As the measure of effect of each individual study, we used the Standardised Mean Difference (SMD), which we defined following NOTE: **Charlotte** cite Lakens 2013 and in there Cummings 2012, as:
@@
 
-In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
+In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics: <!--# Georgina, I have used the Truncated Normal, we can obviously do sensitivity analyses with other ones -->
 
@@
 We then used these simulated datasets in the subsequent metanalyses.
+
+<!--# Charlotte, I am particularly keen for you to code independently the SE calculation, maybe use all the other parts as they are, but check the SEs.
+Once you have re-assured yourself about it, could you please read the code for the other steps below, but break it down by taking it out of the function and probably out of the loop and verifying that you would get the same results for one dataset, e.g.
+the first one in the list of 1000.
+It would be amazing to verify the results this way.
+Finally, as discussed, we can vary the parammeters of the distribution if we have better a prioris-->
 
@@
 ### Random Effects Metaregression
+
 We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
@@
 $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$ {#eq-5}
+$$
 
@@
 
-$$u_i \sim N(0, \tau^2) $${#eq-8}
+$$u_i \sim N(0, \tau^2) $$ {#eq-8}
 
@@
 for level 3, $b_{3_{i}}$ the psychotherapy controls.
-The confidence intervals of the means are constructed in the standard way using the standard errors of the
-Similarly, each coefficient represents the contrast between the reference category and each level, for an exmaple and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
+The confidence intervals of the means are constructed in the standard way using the standard errors of the Similarly, each coefficient represents the contrast between the reference category and each level, for an exmaple and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
 Inference on the contrasts is done as follows:
@@
 
-We used maximum likelihood (REML) to estimate model and applied  Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
+We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
+
+We present our main results as means of the estimates across simulated datasets, for example, the SMDs of each level of the dummy variable above are means across the simulations.
 
@@
 
+Studies included in the metaregression.
+
 The data for the studies included in this metanalysis are summarised in Supplementary Table 1 and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+<!--# Charlotte, this should essentially be our df_long dataset, right?
+Perhaps, for the puproses of the table we can get rid of some of the columns.
+It would be good to have it in the way Pim had it-->
 
@@
 
-# add a new multilevel variable for the regression
+# add a new multilevel variable to the simulated data for the regression
 
@@
 aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
+aggregate_results_overall <- cbind(aggregate_results_overall, condition)
 
@@
 
-NOTE: CHARLOTTE Please create a table here with the results from the count studies or study count variables that you checked in the code chunk above for each A,B and C. 
-The table for A should be added here and accompany the description below. 
-THe other two should go below as supplementary.
-As indicated in the methods we should have one overall table with all studies and all their characteristics ala Cipriani.
+### Analysis of all studies
+
+#### Number of studies included
 
@@
 
-We then applied metaregression to obtain the means and confidence intervals of each of the four arms.
+#### Metaregression analysis.
 
-We examined the variability that the simulations of the correlations of the pre-post outcomes produced.
-As shown in Supplemenatry Table 2, the standard deviation of the simulated mean varied in the third decimal point, indicating minimal influence of the correlations on the outcomes.
+We applied metaregression to obtain the SMDs and confidence intervals of each of the four arms.
 
-Figure 1 graphs the results with the means of each level alongside their confidence intervals.
-Table 1 shows the results containing the means and standard errors for each level, derived as the average of 1000 metaregressions.
-As can be intuited from the confidence intervals displayed, there are statistically significant differences at p<0.05 between the two control arms.
-Table 2 illustrates this with the output of one of the simulated models.
+As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking difference being the medication and the psychotherapy control arms.
+In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)`.
 
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# plot results from simulated means ---------------------------------------
-# 
 subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
 plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
-print(plot_means_all)
-
-subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
-plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
-print(plot_means_cbt)
-
-subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
-print(plot_means_wl)
-
+#print(plot_means_all)
+pdf(file = "plot_means_all.pdf")
+plot_means_all
 ```
 
+![Figure 1.](plot_means_all.pdf)
+
+Table 1 summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: Table 1
-#| tbl-cap: Means for the four Trial Arms alongside 95% Confidence Intervals
-tab_1_df <- df_mean_coefs_from_sim[, 1:length(df_mean_coefs_from_sim)-1]
 
-knitr:: kable(tab_1_df, digits = 2)
+knitr:: kable(df_mean_coefs_from_sim, caption = "Table 1")
 ```
 
+In Table 2, we present the regression that tests our hypothesis about differences between medication and psychotherapy control.
+In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable, including psychotherapy control, are compared.
+The strongest difference betwen arms, as judged by the z-value, is between the psychotherapy and medication control with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# #| label: Table 2
-# #| tbl-cap: Statistics of the Difference Between Medication and Psychotherapy Control Conditions
-# knitr:: kable(coefficients_from_contrasts_medcontrol_psy_control,col.names = c("Beta", "SE", "Lower CI", "Upper CI", "z-value", "p-value"), digits = 2)
-
+knitr:: kable(aggregate_results_overall, caption = "Table 2")
 ```
 
-We then examined whether restricting studies to the trials (US-) licensed medication fluoxetine and escitalopram and the most widely used and evidence-based psychological treatment, namely CBT would change results.
-As can be seen, the coefficient of the difference between placebo and psychotherapy control condition is very strong as judged by the z-value of the difference (8.8), and comaprable to the overall results.
+### Sensitivity Analyses
+
+We then conducted a series of sensitivity analyses of our results.
+
+#### Effect of standard errors of the SMDs .
+
+It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
+To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
+If standard error distributions were influential, this should show up as substantial variability across simulations.
+We test this idea in the Figure 1 which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table 2).
+As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
+the value of z = 1.645.
 
@@
   )
+
+pdf(file = "stab_sims.pdf")
 stab_sims
+dev.off()
+```
+
+![](stab_sims.pdf)
+
+#### Comparison of CBT with fluoxetine and escitalopram
+
+CBT is the most widely studied treatment and, similar to fluoxetine, it has metanalytic evidence supporting its use.
+Both fluoxetine and escitalopram are approved by the FDA as treatments for adolescent depression.
+As can be seen in Figure 3, the pattern of results is very similar to that of the overall analyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
+plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
+pdf(file = "plot_means_cbt.pdf")
+plot_means_cbt
+dev.off()
+```
+
+![](plot_means_cbt.pdf)
+
+#### Excluding studies with waitlist control arms.
+
+It could be argued that waitlist control arms represent outliers amongst psychotherapy control studies that reduce the estimate of the overall efficacy.
+We therefore analysed the data excluding waitlist control studies.
+As can be seen, the pattern of results is very similar to that of the overall analyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+#print(plot_means_wl)
+
+pdf(file = "plot_means_wl.pdf")
+plot_means_wl
+dev.off()
+```
+
+![](plot_means_wl.pdf)
 
 ```         
+```

### 2024-01-06 apples_and_oranges.qmd
corrected title
changed plots slightly

@@
 title: Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.
-subtitle: Re-visiting the relative efficacy Control Conditions..
+subtitle: Insights from the relative efficacy of Control Conditions.
 author:
@@
 ###############6. Function for plotting the SMDs
-library(ggplot2)
-library(stringr)
-
 plot_means_function <- function(dataframe, subtitle) {
@@
     dataframe$text_label[i] <- paste(
-      "k = ", dataframe$n[i], "\n",
+      dataframe$condition[i], "\n",
       round(dataframe$coef_means[i], 2),
@@
                                       colour = condition, label = text_label)) +
-    geom_point(size = 3) +
+    geom_point(label=dataframe$k) +
     geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
@@
     geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
-    theme(axis.title.x = element_text(size = 14), 
-          axis.text.x  = element_text(size = 14),
+    theme(axis.title.x = element_text(size = 12), 
+          axis.text.x  = element_text(size = 12),
           axis.text.y = (element_blank()),
-          plot.title = element_text(size = 16),
-          plot.subtitle = element_text(size = 14)) +
+          plot.title = element_text(size = 12),
+          plot.subtitle = element_text(size = 12)) +
     geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +

### 2024-01-07 apples_and_oranges.qmd
changes to the text.

@@
 where MedActive and PsyActive are the active arms of antidepressant and psychotherapy trials, respectively, and MedControls and PsyControls the respective control arms.
-The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$ A few simple examples help illustrate why this assumption is important Let the two modalities of treatment be medication and surgery, and let there be a trial for each modality.
-In the medication trial 80% of participants respond to the antihypertensive and only 40% to placebo; in the surgery trial, 40% of people respond to surgery and 0% to sham.
+The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$ A simple example from medicine helps illustrate why this assumption is important Let the two modalities of treatment for appendicitis be antibiotic medication and surgery, and let there be a set of trials for each modality.
+In the medication trials, on average 40% of participants respond to the antibiotics and only 0% to placebo; in the surgery trial, 80% of people respond to surgery and 40% to sham.
 If one relied on Equation 1 to compare the treatments they would arrive at the absurd conclusion that the two treatments are equal and recommend to a patient that it does not really matter which one they choose.
 Playing around with numbers in which no equality of the respective control arms is required, leads to other risible conclusions.
-Yet, a focus on the equality of controls is surprisingly absent.
+Yet, in the dicussion about depression treatments, a focus on the equality of controls is surprisingly absent.
 
-The importance of testing the equality of controls assumption for patients and the public can be vast because treatment guidelines, clinician's advice to patients, and patients' informed choices are all affected by the validity of treatment comparisons.
+The importance of testing the equality of controls assumption for patients and the public can be vast because treatment guidelines, clinicians' advice to patients, and patients' informed choices are all affected by the validity of treatment comparisons.
 Similarly, the rational allocation of public funds towards treatment modalities rests on valid comparisons between them.
@@
 The reasons for these differences remain unclear and are typically treated as nuisance effects to be minimised by using trial designs such as a placebo lead in period.
-However, an alternative view is that placebo effects, or more generally, variability in the response to control arms may be informative about mechanisms of improvement.
+However, an alternative view is that placebo effects, or more generally, variability in the response to control conditions, may be informative about mechanisms of improvement.
 If, for example, the antidepressant effect of placebo is stronger than that of equivalent control arms in psychotherapy, then we ought to ask about the possible explanations of such differences and consider whether they can be exploited for improving treatment delivery, as previously suggested.
 
-In this paper, we have two aims: first, test whether the equality of controls assumption of adolescent depression treatment holds, and therefore scrutinise the validity of current recommendations concerning choice between treatment modalities; second,we explore variabiliity in trial control arms across and within the two treatment modalities and examine how they relate to anti-depressant effects.
+In this paper, we have two aims: first, test whether the equality of controls assumption of adolescent depression treatment holds, and therefore scrutinise the validity of current recommendations concerning choice between treatment modalities; second,we explore the variabiliity in trial control arms across and within the two treatment modalities and examine how they relate to anti-depressant effects.
 
-Our main hypothesis is that the within group effect of psychotherapy controls is substantially weaker than that of the placebo pill and we will test this in random effects meta-regression.
-We will also use series of sensitivity analyses concerning restricting to specific psychotherapy control groups ( e.g.
-exclude waitlist controls or include only controls to cognitive and behavioural therapy (CBT)) or medication control groups (e.g.
-trials for the FDA-approved fluoxetine and escitalopram).
-We also conduct sensitivity analyses in the form of simulations, to ensure that results are robust to estimations of the standard error of the change scores.
+Our main hypothesis is that the within group effect of psychotherapy controls is substantially weaker than that of the placebo pill and we will test this using random effects meta-regression.
+We will also use series of sensitivity analyses.
+First we compared CBT trial arms with those of trials involving fluoxetine and escitalopram.
+CBT is the most widely studied treatment and, similar to fluoxetine, it has metanalytic evidence supporting its use.
+Both fluoxetine and escitalopram are approved by the FDA as treatments for adolescent depression.
+We also conduct analyses excluding waitlist control arms as it could be argued that waitlist control arms represent outliers amongst psychotherapy control studies that reduce the estimate of the overall efficacy.
+Finally, we also conduct sensitivity analyses in the form of simulations, to ensure that results are robust to estimations of the standard error of the change scores.
 
@@
 
-which describes the deviation of each study from the mean of the distribution, and,
+describes the deviation of each study from the mean of the distribution, and,
 
 $$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-9}
+
+describes the sampling error.
 
@@
 for level 3, $b_{3_{i}}$ the psychotherapy controls.
-The confidence intervals of the means are constructed in the standard way using the standard errors of the Similarly, each coefficient represents the contrast between the reference category and each level, for an exmaple and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
+The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
+Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
 Inference on the contrasts is done as follows:
@@
 # grab the ids for no waitlist
-no_wl_ids <-
-  df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
+no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
 
@@
 
-#### Number of studies included
+#### Number and type of of studies included
 
@@
 There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
+
+<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X -->
+
+Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as <!--# X -->fluoxetine and <!--# X -->escitalopram, to tricylics, such as <!--# X -->notriptylin.
+In psychological trials, the control arm included <!--# X -->WL controls, care as usual <!--# X --> and several other conditions such as attention control <!--# X -->; the active arm included CBT <!--# X -->, IPT <!--# X --> and psychodynamic therapy <!--# X --> amongst others.
+All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
 
@@
 
-CBT is the most widely studied treatment and, similar to fluoxetine, it has metanalytic evidence supporting its use.
-Both fluoxetine and escitalopram are approved by the FDA as treatments for adolescent depression.
-As can be seen in Figure 3, the pattern of results is very similar to that of the overall analyses.
+We next compared the control and active arms of CBT studies to those of fluoxetine and escitalopram studies. As can be seen, the pattern of results is very similar to that of the ovarall analyses.
 
@@
 
-It could be argued that waitlist control arms represent outliers amongst psychotherapy control studies that reduce the estimate of the overall efficacy.
-We therefore analysed the data excluding waitlist control studies.
-As can be seen, the pattern of results is very similar to that of the overall analyses.
+We next analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.
 

### 2024-01-08 Script for cleaning merged dataset.R
Just wrote csv to compare against Dayna's categorisations

@@ -232,6 +232,7 @@ df_appl_v_orange <- df_appl_v_orange %>% arrange(study_ID, instrument_value)
 
 # retain only first row to look at demographics as this will keep one row per study_ID, taking the primary instrument
 df_first_row <- df_appl_v_orange %>% distinct(study_ID, .keep_all = TRUE) 
+write.csv(df_first_row, "df_first_row.csv")
 
 #check how many med comparisons we cannot calc cohens d for (for primary instrument)
 filter_test <- df_first_row %>% filter(psy_or_med == 0)

### 2024-01-10 apples_and_oranges.qmd
Responded to comments including: describing how we used Cipriani and Cuijpers metanalyses, checked study counts as requested, inputed numbers to summarise types of active and control arms included, added code from Argyris

@@
 
+For this review, we primarily drew upon studies included in two recent meta-analyses.
+Please refer to these original meta-analyses for a detailed description of study selection criteria.
+Psychotherapy studies were drawn from Cuijpers' (2023) systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions.
+Cuijpers made available a full dataset of psychotherapy trials (via https://www.metapsy.org/), which we used for the current study.
+Whilst Cuijpers (2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to Cuijpers' (2023) meta-analysis.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuipers' (2023) literature search.
+
+Medication studies were drawn from Cipriani's (2016) network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in young people.
+The study dataset was made available online though did not include means or standard deviations at baseline or post-test.
+We emailed the study authors requesting a full dataset with this data, though did not receive a reply, and hence conducted data extraction for medication studies.
+We excluded three studies because they did not include a control arm.
+We were unable to locate and therefore complete extraction for two papers.
+Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive replies from any authors.
+**Yet to do** We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
+We used the same search terms outlined in Cipriani (2016).
+
 NOTE: **Charlotte** to please check code lines 986 to 1121.
@@
 Please make sure to say where that we asked about missing information.
+**CB** Completed above.
 -->
@@
 
-As the measure of effect of each individual study, we used the Standardised Mean Difference (SMD), which we defined following NOTE: **Charlotte** cite Lakens 2013 and in there Cummings 2012, as:
-
-$$\frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-3}
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
+
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
 
@@
 
-$$ \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$ {#eq-4}
+$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$
 
@@
 
-$$SE_{change} \sim \mathcal{TN}(\mu, \sigma, a, b)
-$$ {#eq-5}
+$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
 
@@
 # ask Charlotte to check steps above (lines 986 to 1121)
-write.csv(df_long_for_metan, "df_long_for_metan", row.names = F)
+write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
 
@@
 
-df_long_for_metan <- read.csv("df_long_for_metan")
+df_long_for_metan <- read.csv("df_long_for_metan.csv")
 
@@
 Perhaps, for the puproses of the table we can get rid of some of the columns.
-It would be good to have it in the way Pim had it-->
+It would be good to have it in the way Pim had it.
+CB - I'm not sure I entirely understand.
+df_long_for_metan is already quite succinct (6 columns).
+I wonder if you are thinking of df_appl_v_orange which is more complete and includes means and sds etc.
+I'd say that's probably more appropriate to make available.
+I agree we should simplify it down a bit.
+Happy to do that once you confirm I'm on the right track here.
+If we decide to format it to be consistent with Cuijpers' data, we would have one row per comparison, rather than the long format we have in df_long_for_metan.
+-->
 
@@
 df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
+# CB checked both, both correct.
 
@@
 study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
-# CHARLOTTE please check
+# CHARLOTTE please check. CB - checked and correct.
 
@@
 # CHARLOTTE please check
+# CB checked and correct
 
@@
 
+# D. CDRS Sensitivity Analysis ---------------------------------------
+
+cdrs_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_cdrs_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% cdrs_study_ids,]
+
+}
+
+# count the number of studies
+study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
+
+#CHARLOTTE please check. CB checked, all good.
+
+# apply the metareg function to the list of cbt, fluox, esc
+model_1 <- as.formula(~ four_level_var)
+list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
+
+# extract SMDs from the list for cbt fluox escit
+means_cdrs_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
+coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
+
+# add the ns to the dataframe
+coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
+
 ```
-
 ### Analysis of all studies
@@
 Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
-
-<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X -->
-
-Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as <!--# X -->fluoxetine and <!--# X -->escitalopram, to tricylics, such as <!--# X -->notriptylin.
-In psychological trials, the control arm included <!--# X -->WL controls, care as usual <!--# X --> and several other conditions such as attention control <!--# X -->; the active arm included CBT <!--# X -->, IPT <!--# X --> and psychodynamic therapy <!--# X --> amongst others.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
+
+<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X.
+CB - done.
+I removed psychodynamic because there weren't any active conditions of this type.
+-->
+
+Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
+In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
 All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
@@
 
+#### Meta-analysis of baseline values
+
+We next conducted a meta-analysis to test for differences in means at baseline.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# Metanalysis of CDRS at baseline #
+
+df_with_cdrs <-  df_appl_v_orange %>%          
+  filter(instrument_name == "cdrs")
+
+library(meta)
+means_cdrs_baseline_control <- metamean(n = baseline_n_control,
+                   mean = baseline_mean_control,
+                   sd = baseline_sd_control,
+                   studlab = new_study_id,
+                   data = df_with_cdrs,
+                   sm = "MRAW",
+                   fixed = FALSE,
+                   random = TRUE,
+                   method.tau = "REML",
+                   hakn = TRUE,
+                   title = "CDRS Scores at Baseline")
+summary(means_cdrs_baseline_control)
+
+update.meta(means_cdrs_baseline_control, 
+            subgroup = psy_or_med, 
+            tau.common = FALSE)
+
+means_cdrs_baseline_active <- metamean(n = baseline_n_active,
+                                        mean = baseline_mean_active,
+                                        sd = baseline_sd_active,
+                                        studlab = new_study_id,
+                                        data = df_with_cdrs,
+                                        sm = "MRAW",
+                                        fixed = FALSE,
+                                        random = TRUE,
+                                        method.tau = "REML",
+                                        hakn = TRUE,
+                                        title = "CDRS Scores at Baseline")
+summary(means_cdrs_active)
+
+update.meta(means_cdrs_baseline_active, 
+            subgroup = psy_or_med, 
+            tau.common = FALSE)
+
+# Metanalysis of HAMD at baseline #
+df_with_hamd <-  df_appl_v_orange %>%          
+  filter(instrument_name == "hamd")
+
+library(meta)
+means_hamd_baseline_control <- metamean(n = baseline_n_control,
+                                        mean = baseline_mean_control,
+                                        sd = baseline_sd_control,
+                                        studlab = new_study_id,
+                                        data = df_with_hamd,
+                                        sm = "MRAW",
+                                        fixed = FALSE,
+                                        random = TRUE,
+                                        method.tau = "REML",
+                                        hakn = TRUE,
+                                        title = "HAMD Scores at Baseline")
+summary(means_hamd_baseline_control)
+
+update.meta(means_hamd_baseline_control, 
+            subgroup = psy_or_med, 
+            tau.common = FALSE)
+
+means_hamd_baseline_active <- metamean(n = baseline_n_active,
+                                       mean = baseline_mean_active,
+                                       sd = baseline_sd_active,
+                                       studlab = new_study_id,
+                                       data = df_with_hamd,
+                                       sm = "MRAW",
+                                       fixed = FALSE,
+                                       random = TRUE,
+                                       method.tau = "REML",
+                                       hakn = TRUE,
+                                       title = "HAMD Scores at Baseline")
+summary(means_hamd_baseline_active)
+
+update.meta(means_hamd_baseline_active, 
+            subgroup = psy_or_med, 
+            tau.common = FALSE)
+
 ```
-```

### 2024-01-10 apples_and_oranges.qmd
Fixed small typo

@@
 We were unable to locate and therefore complete extraction for two papers.
-Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive replies from any authors.
+Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive any responses.
 **Yet to do** We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.

### 2024-01-10 apples_and_oranges.qmd
Added in code for metaregression excluding wl and cau

@@
 study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
-# CHARLOTTE please check. CB - checked and correct.
+# CHARLOTTE please check. CB - come back to this, possible problem.
 
@@
 # CHARLOTTE please check
-# CB checked and correct
+# CB come back to this, possible problem.
 
@@
 
+# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
+# grab the ids for no waitlist and cau
+no_wl_or_cau_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl" & df_appl_v_orange$control_type != "cau",]$new_study_id
+
+# use them to loop over the simulated list to subset all the dataframes.
+list_no_wl_or_cau <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_no_wl_or_cau[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                            %in% no_wl_or_cau_ids,]
+
+}
+
+# count studies 
+study_count_no_wl_or_cau_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_or_cau_ids,])
+# CHARLOTTE please check
+
+# use this model as above
+model_1 <- as.formula(~ four_level_var)
+
+# apply the metareg function to the list of cbt, fluox, esc
+list_model_1_no_wl <- run_metaregression(list_no_wl_or_cau , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_no_wl_or_cau <-  aggregate_model_results(list_model_1_no_wl_or_cau, condition)
+
+# now use the function to extract the coefficients
+means_no_wl_or_cau <-  lapply(list_model_1_no_wl_or_cau, extract_coefficients_func)
+
+# run the mean function for no wl
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
+coef_and_se_means_no_wl_or_cau <- calculate_mean_coefs_ses(means_no_wl_or_cau, condition)
+coef_and_se_means_no_wl_or_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_or_cau))
+
+coef_and_se_means_no_wl_or_cau$n <- study_count_no_wl_or_cau_study[study_count_no_wl_or_cau_study$is_missing 
+                                                     ==FALSE,]$n
+
 # here are all three of them OVERALL, CBT and WL together. We may want to display them together. 
@@
 
-# D. CDRS Sensitivity Analysis ---------------------------------------
+# E. CDRS Sensitivity Analysis ---------------------------------------
 
@@
 
-#CHARLOTTE please check. CB checked, all good.
+#CHARLOTTE please check. CB - come back to this, possible problem.
 

### 2024-01-11 apples_and_oranges.qmd
Small things

@@
 # C) the no WL sample
+# D) the no WL or CAU sample
+# E) the CDRS only sample
 

### 2024-01-11 apples_and_oranges.qmd
a few minor changes before pull

--- 2024-01-10 apples_and_oranges.qmd
@@
 
-For this review, we primarily drew upon studies included in two recent meta-analyses.
-Please refer to these original meta-analyses for a detailed description of study selection criteria.
-Psychotherapy studies were drawn from Cuijpers' (2023) systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions.
-Cuijpers made available a full dataset of psychotherapy trials (via https://www.metapsy.org/), which we used for the current study.
-Whilst Cuijpers (2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to Cuijpers' (2023) meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuipers' (2023) literature search.
-
-Medication studies were drawn from Cipriani's (2016) network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in young people.
-The study dataset was made available online though did not include means or standard deviations at baseline or post-test.
-We emailed the study authors requesting a full dataset with this data, though did not receive a reply, and hence conducted data extraction for medication studies.
-We excluded three studies because they did not include a control arm.
-We were unable to locate and therefore complete extraction for two papers.
-Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive any responses.
-**Yet to do** We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
-We used the same search terms outlined in Cipriani (2016).
-
 NOTE: **Charlotte** to please check code lines 986 to 1121.
@@
 Please make sure to say where that we asked about missing information.
-**CB** Completed above.
 -->
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
-
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: **Charlotte** cite Lakens 2013 and in there Cummings 2012, as:
+
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-3}
 
@@
 
-$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$
+$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$ {#eq-4}
 
@@
 
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
+$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)
+$$ {#eq-5}
 
@@
 # ask Charlotte to check steps above (lines 986 to 1121)
-write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
+write.csv(df_long_for_metan, "df_long_for_metan", row.names = F)
 
@@
 
-df_long_for_metan <- read.csv("df_long_for_metan.csv")
+df_long_for_metan <- read.csv("df_long_for_metan")
 
@@
 Perhaps, for the puproses of the table we can get rid of some of the columns.
-It would be good to have it in the way Pim had it.
-CB - I'm not sure I entirely understand.
-df_long_for_metan is already quite succinct (6 columns).
-I wonder if you are thinking of df_appl_v_orange which is more complete and includes means and sds etc.
-I'd say that's probably more appropriate to make available.
-I agree we should simplify it down a bit.
-Happy to do that once you confirm I'm on the right track here.
-If we decide to format it to be consistent with Cuijpers' data, we would have one row per comparison, rather than the long format we have in df_long_for_metan.
--->
+It would be good to have it in the way Pim had it-->
 
@@
 df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
-# CB checked both, both correct.
 
@@
 study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
-# CHARLOTTE please check. CB - checked and correct.
+# CHARLOTTE please check
 
@@
 # CHARLOTTE please check
-# CB checked and correct
 
@@
 
-# D. CDRS Sensitivity Analysis ---------------------------------------
-
-cdrs_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_cdrs_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% cdrs_study_ids,]
-
-}
-
-# count the number of studies
-study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
-
-#CHARLOTTE please check. CB checked, all good.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cdrs_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
-coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
-
-```
+```
+
 ### Analysis of all studies
@@
 Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
-
-<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X.
-CB - done.
-I removed psychodynamic because there weren't any active conditions of this type.
--->
-
-Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
-In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to compute the SMD was missing and could not be imputed by any of the methods outlined above.
+
+<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X -->
+
+Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as <!--# X -->fluoxetine and <!--# X -->escitalopram, to tricylics, such as <!--# X -->notriptylin.
+In psychological trials, the control arm included <!--# X -->WL controls, care as usual <!--# X --> and several other conditions such as attention control <!--# X -->; the active arm included CBT <!--# X -->, IPT <!--# X --> and psychodynamic therapy <!--# X --> amongst others.
 All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(aggregate_results_overall, caption = "Table 2")
+knitr:: kable(aggregate_results_overall, caption = "Table 2", digits = 2)
 ```
@@
 
-#### Meta-analysis of baseline values
-
-We next conducted a meta-analysis to test for differences in means at baseline.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Metanalysis of CDRS at baseline #
-
-df_with_cdrs <-  df_appl_v_orange %>%          
-  filter(instrument_name == "cdrs")
-
-library(meta)
-means_cdrs_baseline_control <- metamean(n = baseline_n_control,
-                   mean = baseline_mean_control,
-                   sd = baseline_sd_control,
-                   studlab = new_study_id,
-                   data = df_with_cdrs,
-                   sm = "MRAW",
-                   fixed = FALSE,
-                   random = TRUE,
-                   method.tau = "REML",
-                   hakn = TRUE,
-                   title = "CDRS Scores at Baseline")
-summary(means_cdrs_baseline_control)
-
-update.meta(means_cdrs_baseline_control, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-means_cdrs_baseline_active <- metamean(n = baseline_n_active,
-                                        mean = baseline_mean_active,
-                                        sd = baseline_sd_active,
-                                        studlab = new_study_id,
-                                        data = df_with_cdrs,
-                                        sm = "MRAW",
-                                        fixed = FALSE,
-                                        random = TRUE,
-                                        method.tau = "REML",
-                                        hakn = TRUE,
-                                        title = "CDRS Scores at Baseline")
-summary(means_cdrs_active)
-
-update.meta(means_cdrs_baseline_active, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-# Metanalysis of HAMD at baseline #
-df_with_hamd <-  df_appl_v_orange %>%          
-  filter(instrument_name == "hamd")
-
-library(meta)
-means_hamd_baseline_control <- metamean(n = baseline_n_control,
-                                        mean = baseline_mean_control,
-                                        sd = baseline_sd_control,
-                                        studlab = new_study_id,
-                                        data = df_with_hamd,
-                                        sm = "MRAW",
-                                        fixed = FALSE,
-                                        random = TRUE,
-                                        method.tau = "REML",
-                                        hakn = TRUE,
-                                        title = "HAMD Scores at Baseline")
-summary(means_hamd_baseline_control)
-
-update.meta(means_hamd_baseline_control, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-means_hamd_baseline_active <- metamean(n = baseline_n_active,
-                                       mean = baseline_mean_active,
-                                       sd = baseline_sd_active,
-                                       studlab = new_study_id,
-                                       data = df_with_hamd,
-                                       sm = "MRAW",
-                                       fixed = FALSE,
-                                       random = TRUE,
-                                       method.tau = "REML",
-                                       hakn = TRUE,
-                                       title = "HAMD Scores at Baseline")
-summary(means_hamd_baseline_active)
-
-update.meta(means_hamd_baseline_active, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-```
+```         
+```

### 2024-01-11 Festschrift_Ellen.qmd
test

---
title: "Fundamental Flaws in the Appraisal of Adolescent Depression Treatment"
subtitle: "In honour of Dr Ellen Leibenluft"
author: "Professor Argyris Stringaris, MD, PhD, FRCPsych"
format: revealjs
logo: ucl_brain_sciences.png
fontsize: "22pt"
include-in-header:
  - text: |
      <style>
      .reveal .slide-logo {
        max-height: unset;
        height: 150px;
      }
      </style>
---

## Overview

-   Importance of Adolescent Depression

-   How Do We Treat Adolescent Depression?

-   The Problem With Comparing Treatments

-   Vast Differences in the Control Conditions between Treatment Types.

-   Dubious Control Groups for Psychotherapy

-   Understanding Human Expectations and Psychiatric Treatments

## What I learnt from Ellen

![](ArgyrisandEllen.png)

## What I learnt from Ellen

Ellen,

-   gave meaning to the concept of irritability and more generally that of negative and aggressive **mood**, something with vast public health implications.

-   injected rationality into an extraordinary debate that of the US "Pediatric Bipolar", and curbing excesses that came from very powerful places.

-   is consistently a **Clinical Researcher** with an instinct for what matters to patients and public.

-   worked together with an extraordinary team of people and bringing out the most of each.

-   is an extraordinary writer.

-   has a keen sense and knowledge of history and therefore human fallibility.

## Importance of Adolescent Depression

![](adolescent_mental_health.jpeg){fig-align="left"}

## How Do We Treat Adolescent Depression?

![National Institute of Clinical Excellence Guidelines](NICE_1.png){fig-align="left"}

## How Do We Treat Adolescent Depression

![National Institute of Clinical Excellence Guidelines](NICE_2.png){fig-align="left"}

## How Do We Treat Adolescent Depression

![American Academy of C&A Psychiatry Practice Parameter](AACAP_1.png){fig-align="left"}

## How do We Treat Adolescent Depression

![](AACAP_2.png){fig-align="left"}

## Comparing Treatments

These recommendations are not based on head to head trials between modalities.

-   only one head-to-head trial exists in adolescent depression.
-   comparisons rely on the comparison of the results of randomised controlled trials (RCTs) of each modality against RCTs of the other.
-   In other words, they rest on comparison of comparisons.

## Comparing Treatments: Clinical Importance

This has potentially vast implications for the health of the public:

-   As a patient/carer: which treatment should I/my child take?

-   As a health professional: you can take A or/over B

-   As a public health official: doctors should ...

## The Problem With Comparing Treatments

-   In antidepressant studies, the control is the placebo pill

-   In psychotherapy studies controls vary substantially

    What is tested is:

$$Effect_{Med} = Effect_{Psy}$$

where *Effect* denotes the effect on depression that either medication (*Med* ) or psychotherapy (*Psy*) have.

## The Problem With Comparing Treatments

In particular, it relies on the equality of controls:

$$Effect_{MedActive} - Effect_{MedControls} = Effect_{PsyActive} - Effect_{PsyControls}$$

or:

$$ Effect_{MedControls} = Effect_{PsyControls}$$

## The Problem with Comparing Treatments

![](appendicitis.png){fig-align="left" width="340"}

Compare: antibiotics vs surgery:

-   Antibiotics improvement rate: 40% on active; 2% on control

-   Surgery improvement rate: 80% on active, 42% on control

## The Problem with Comparing Treatments

Compare: antibiotics vs surgery:

-   Antibiotics improvement rate: 40% on active; 0% on control

-   Surgery improvement rate: 80% on active, 40% on control

Would you tell your patient that these are equally good treatments?

## Comparing Treatments: Mechanistic Implications

If there is variability in control arms, then:

-   is it random?

-   does it tell us something about how treatments work? e.g. :

    -   what are the psychological mechanisms of placebo?

    -   why would people find other control groups unfavourable?

-   more generally, what is an appropriate counterfactual to treatment?

## Assessing Treatment Comparisons: Methods

-   Extracted baseline and follow up means and sds for each study (where available) from all randomised controlled trials (RCTs) in adolescent depression using medication or psychotherapy.

-   Estimated Standardised Mean Differences (SMD) for each study.

    $$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\  $$

## Assessing Treatment Comparisons: Methods

We also needed the estimation of the standard errors. For this we require the test-retest correlation coefficient of the instrument, which is not reported in studies:

$$SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$

We therefore simulated 1000 datasets with correlations coefficients from a broad distribution and used these for our calculations–the magnitude of $r_{t_{1}t_{2}}$ made very little difference to results.

## Assessing Treatment Comparisons: Methods

Random Effects Meta-Regression

$$Y_i = x_i\beta_i + u_i + \epsilon_i$$

where

$$ \begin{aligned}
    Υ_i &=
    \begin{cases}
        0 & MedControl:  b_0 + u_i + \epsilon_i\\
        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
    \end{cases}
\end{aligned}$$

## Assessing Treatment Comparisons: Results

There were 81 studies in total

-   antidepressants: 28 active arms and 25 control arms of antidepressant trials;

-   psychotherapy: 55 active arms and 52 control arms from psychotherapy trials.

-   Placebo was the control condition for all medication trials

-   WL controls, care as usual and several other conditions such as attention control for psychotherapy

## Assessing Treatment Comparisons: SMDs overall

![](plot_means_all.png){fig-align="left"}

## Assessing Treatment Comparisons: SMDs CBT and SRI only

![](plot_means_cbt.png){fig-align="left"}

## Assessing Treatment Comparisons: SMDs no waitlist

![](plot_means_wl.png){fig-align="left"}

## Assessing Treatment Comparisons: differences

![](coef_pic.png){fig-align="left" width="361"}

## What were the controls?

-   Mostly waitlist (WL) and care-as-usual (CAU).

-   Others were attention controls, which were typically poorly matched to active groups.

-   Often information was missing on key variables.

## What is a good control?

Controls should serve as counterfactuals: what would an individual look like if they did not receive treatment?

There should be a **latent true value** of what an individual would look like had they not received the treatment.

## What is a good control?

A good control is crucially **ΝΟΤ** being told that you were allocated to:

-   simply waiting (WL control)

-   getting what they would have gotten anyway (CAU control), which is heterogeneous (and in our field sometimes not much at all).

-   receiving a sub-par treatment that the experimenter themselves do not believe in (some ill-designed control).

    All this also whilst **knowing** that someone else (other people in the trial) got the "real thing". This creates negative counterfactual compared to treatment.

## Are there alternative explanations for the finding?

-   could it be due to different instruments used?

    -   No, even when using common instruments, such as CDRS and HAM-D, the results were the same.

-   could there be more regression to the mean in the medication group.

    -   There could be, the values are higher at baseline in most studies (with common instruments)

    -   But the difference is very large, even when matching studies with the same baseline values.

    -   We are thinking of ways of dealing with this statistically at present.

## Where to next?

At a practical level:

-   change guidelines, at the very least they should be toned down.

-   impose more rigorous controls on psychotherapy studies.

-   actively research the social and neurobiological underpinnings of control conditions. This has to include:

    -   expectancy effects

    -   opportunity cost

-   think about the ethical implications of control groups.

### 2024-01-12 apples_and_oranges.qmd
several changes to code

--- 2024-01-11 apples_and_oranges.qmd
@@
 # A: turn long the rows with active
-turn_long_active_type <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active) %>% 
-  pivot_longer(cols = c(cohens_d_active), 
-               names_to = "arm_effect_size", 
-               values_to = "cohens_d")
-
-# also rename active_type to treatment for the merge below.
-turn_long_active_type <- rename(turn_long_active_type, treatment = descr_active,
-                                baseline_n = baseline_n_active)
-
-# # to illustrate the issue, here we have one study with two controls for which the active at the moment, also exists twice. 
-# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
-# # but here another one where the same study reasonably contributes two actives, fluoxetine and duloxetine.
-# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]
-
-# we now need to go through each study id and remove duplicates
-turn_long_active_type <-
-  turn_long_active_type %>% 
-  group_by(new_study_id) %>% 
+active_df <- df_with_distinct_instruments %>% 
+  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
+                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
+  rename(treatment = descr_active) %>% 
+  rename_with(~ str_remove(., "_active")) %>% 
+  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
+  group_by(new_study_id) %>% #go through each study id and remove duplicates
   distinct(treatment, .keep_all = TRUE)
 
-# # Now checking if this worked with the studies that I used to illustrate the problem above. 
-# turn_long_active_type[turn_long_active_type$new_study_id == "Stallard, 2012",]
-# turn_long_active_type[turn_long_active_type$new_study_id == "Atkinson, 2014",]
-# # also check one which is single to make sure it is kept
-# turn_long_active_type[turn_long_active_type$new_study_id == "Ackerson, 1998",]
-
-# B: turn long control rows
-turn_long_control_type <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, control_type, psy_or_med, baseline_n_control, cohens_d_control) %>% 
-  pivot_longer(cols = c(cohens_d_control), 
-               names_to = "arm_effect_size", 
-               values_to = "cohens_d")
-
-# also rename active_type to treatment for the merge below.
-turn_long_control_type <- rename(turn_long_control_type,treatment = control_type,
-                                 baseline_n = baseline_n_control)
-
-# # to illustrate the issue, here we have one study with two controls that are reasonable. 
-# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
-# # but here another one where the same study reasonably contributes two placebos
-# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]
-
-# we now need to go through each study id and remove duplicates
-turn_long_control_type <-
-  turn_long_control_type %>% 
-  group_by(new_study_id) %>% 
+control_df <- df_with_distinct_instruments %>% 
+  dplyr:: select(new_study_id, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
+                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
+  rename(treatment = descr_control) %>% 
+  rename_with(~ str_remove(., "_control")) %>% 
+  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
+  group_by(new_study_id) %>% #go through each study id and remove duplicates
   distinct(treatment, .keep_all = TRUE)
 
-# # Now checking if this worked with the studies that I used to illustrate the problem above. 
-# turn_long_control_type[turn_long_control_type$new_study_id == "Stallard, 2012",]
-# turn_long_control_type[turn_long_control_type$new_study_id == "Atkinson, 2014",]
-# # also check one which is single to make sure it is kept
-# turn_long_control_type[turn_long_control_type$new_study_id == "Ackerson, 1998",]
-
-### Now merge the active and control datasets
-df_long_for_metan <-rbind(turn_long_active_type, turn_long_control_type)
+df_long_for_metan <- rbind(active_df, control_df)
+
 #dim(df_long_for_metan ) #check dimension
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# library(tidyverse)
-# 
-# 
-# # describe studies
-# n_unique_studies <- length(unique(df_long_for_metan$new_study_id))
-# 
-#   
-# 
-# df_count_studies <- df_long_for_metan %>% 
-#   group_by(psy_or_med, arm_effect_size) %>% 
-#   count(is.na(cohens_d))
-# 
-# 
-# df_count_studies <-rename(df_count_studies, is_missing = `is.na(cohens_d)`)
-# 
-# df_count_studies <-
-#   df_count_studies %>% 
-#   mutate(condition = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-#                              psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-#                              psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-#                              psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-#   )
-# 
-#   df_count_studies$condition <- factor(df_count_studies$condition) # turn to factor
-#   
-#   # relevel so that medication control becomes the reference category for the regression
-#   df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
-# 
-# df_count_studies_not_missing <- df_count_studies[df_count_studies$is_missing == FALSE,]
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Get Ns, run metareg, prepare graphing ------------------------------------------------------
@@
 for(i in 1: length(list_df_simulated)){
+
+list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
   list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
@@
   # relevel so that medication control becomes the reference category for the regression
-  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
+                                                       "medication_control",
+                                                       "medication_active", 
+                                                       "psychotherapy_control",
+                                                       "psychotherapy_active")
 }
@@
 aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
+aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
 
@@
 aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
+aggregate_results_no_wl <- cbind(aggregate_results_no_wl, condition)
 
@@
 # apply the metareg function to the list of cbt, fluox, esc
-list_model_1_no_wl <- run_metaregression(list_no_wl_or_cau , model_1)
+list_model_1_no_wl_or_cau <- run_metaregression(list_no_wl_or_cau , model_1)
 
@@
 aggregate_results_no_wl_or_cau <-  aggregate_model_results(list_model_1_no_wl_or_cau, condition)
+aggregate_results_no_wl_or_cau <- cbind(aggregate_results_no_wl_or_cau, condition)
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(aggregate_results_overall, caption = "Table 2")
+knitr:: kable(aggregate_results_overall, caption = "Table 2", digits = 2
+              )
 ```
@@
 for(i in 1: length(list_model_1_no_wl)){
-z_psy_con_vs_med_con[i] <- list_model_1_no_wl[[i]]$zval[[4]]
+z_psy_con_vs_med_con[i] <- list_model_1_no_wl[[i]]$zval[condition=="psychotherapy_control"]
+
 }
@@
 
-update.meta(means_cdrs_baseline_control, 
+subgroup_cdrs_baseline_control <- update.meta(means_cdrs_baseline_control, 
             subgroup = psy_or_med, 
@@
                                         title = "CDRS Scores at Baseline")
-summary(means_cdrs_active)
-
-update.meta(means_cdrs_baseline_active, 
+#summary(means_cdrs_baseline_active)
+
+subgroup_cdrs_baseline_active <- update.meta(means_cdrs_baseline_active, 
             subgroup = psy_or_med, 
@@
                                         title = "HAMD Scores at Baseline")
-summary(means_hamd_baseline_control)
-
-update.meta(means_hamd_baseline_control, 
+#summary(means_hamd_baseline_control)
+
+subgroup_hamd_baseline_control <- update.meta(means_hamd_baseline_control, 
             subgroup = psy_or_med, 
@@
                                        title = "HAMD Scores at Baseline")
-summary(means_hamd_baseline_active)
-
-update.meta(means_hamd_baseline_active, 
+#summary(means_hamd_baseline_active)
+
+subgroup_hamd_baseline_active <- update.meta(means_hamd_baseline_active, 
             subgroup = psy_or_med, 

### 2024-01-12 apples_and_oranges.qmd
Fixed error resulting in smaller number of med controls than expected

@@
 
+# We are going to use the descr_active and descr_control columns rather than active_type and control_type columns, as these have unique values for each study.
+However the descr columns are empty for med studies, so I'm going to paste values across to fix this error.
 df_appl_v_orange <- df_appl_v_orange %>% 
   mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))
+
+df_appl_v_orange <- df_appl_v_orange %>% 
+  mutate(descr_control = if_else(is.na(descr_control), control_type, descr_control ))
 
@@
 df_long_for_metan <- rbind(active_df, control_df)
+
+# I'm going to remove the March / TADS psy control row. It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist.
+
+df_long_for_metan <- df_long_for_metan %>%
+  filter(!(new_study_id == "March, 2004" & is.na(treatment)))
 
@@
 n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
-df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
+df_count_studies <- count_studies(df_long_for_metan ) # CHARLOTTE please check
 # CB checked both, both correct.

### 2024-01-12 apples_and_oranges.qmd
Tried adding a key column

@@
 
+# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
+# for CBT, fluox, esc
+cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
+  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
+  pull(new_study_id)
+df_with_distinct_instruments <- df_with_distinct_instruments %>%
+  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))
+
+# for wl 
+wl_study_ids <- df_with_distinct_instruments %>%
+  filter(control_type == "wl") %>%
+  pull(new_study_id)
+df_with_distinct_instruments <- df_with_distinct_instruments %>%
+  mutate(key2 = ifelse(new_study_id %in% wl_study_ids, 2, NA))
+
+df_with_distinct_instruments <- df_with_distinct_instruments %>%
+  mutate(key = paste(key1, key2, sep = "_"))
+
 # Step 2: turn dataframes to long
@@
 active_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
+  dplyr:: select(new_study_id, key, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
@@
 control_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
+  dplyr:: select(new_study_id, key, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 

### 2024-01-13 apples_and_oranges.qmd
updated the adjusted cohens d

@@
 
+###########7. Function for baseline SMD results
+library(broom)
+run_metareg_and_extract <- function(dataframe, model_1, condition) {
+  # Run metareg
+  inst_baseline_metareg <- rma(yi = baseline_mean,
+                               sei = baseline_stand_error,
+                               data = dataframe,
+                               method = "ML",
+                               mods = model_1,
+                               test = "knha")
+
+  # Extract coefficients from the list
+  baseline_metareg_results <- tidy(inst_baseline_metareg)
+  baseline_metareg_results$condition <- condition
+  coefs_for_inst_baseline <- tidy(inst_baseline_metareg)$estimate
+
+  # Calculate SMDs
+  smds_for_inst_baseline <- c(coefs_for_inst_baseline[1], coefs_for_inst_baseline[-1] + coefs_for_inst_baseline[1])
+
+  # Calculate upper and lower CIs
+  upper_cis_for_inst_baseline <- smds_for_inst_baseline + 1.96 * tidy(inst_baseline_metareg)$std.error
+  lower_cis_for_inst_baseline <- smds_for_inst_baseline - 1.96 * tidy(inst_baseline_metareg)$std.error
+
+  # Create dataframe with results
+  df_baseline_means_with_cis <- data.frame(
+    baseline_smds = smds_for_inst_baseline,
+    upper_cis_smds = upper_cis_for_inst_baseline,
+    lower_cis_smds = lower_cis_for_inst_baseline,
+    condition = condition
+  )
+
+  # Return the two dataframes
+  return(list(baseline_metareg_results = baseline_metareg_results, df_baseline_means_with_cis = df_baseline_means_with_cis))
+}
+
 ```
@@
 We present our main results as means of the estimates across simulated datasets, for example, the SMDs of each level of the dummy variable above are means across the simulations.
+
+### Sensitivity Analyses
+
+We conducted a number of additional analyses to test for the robustness of our results.
+
+First, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
+To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
+We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+# my alpha for the z 
+target_probability <- 1 - 0.05
+
+#start here 
+x <- 1
+
+# two decimals should be fine
+tolerance <- 1e-3
+
+#find the z value using the pnorm function
+while (abs(pnorm(x)) < target_probability ) {
+  x <- x + tolerance  
+}
+
+# Adjust the step size based on your problem  
+cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
+
+```
+
+Second, we restricted the metaregression to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram.
+
+Third, we restricted the metaregression to studies that *did not* use waitlist as their control.
+
+Fourth, we tested whether our results could be accounted for by differential regression to the mean.
+In an initial step, we tested in metaregression as above for differences in baseline means for those medication and psychotherapy studies that shared the same instruments.
+We then accounted for the effect that possible differing baseline values across all studies studies' outcomes by regressing the SMDs of studies on their respective baseline values of the instrument with which the SMD was calculated.
+For example, in a study that used the CDRS, this was used to calculate the SMD.
+This SMD was then used as the outcome and the baseline value of the CDRS, termed *BaselineScore* below, in that study was used as the independent variable as follows: $$
+SMD = \beta_0 + \beta_1 BaselineScore + \epsilon
+$$ {#eq-12}
+
+This allows us to estimate the effect of the baseline score on the SMD by evaluating $\beta_1$.
+We can then re-arrange Equation 12 to extract the residuals, that is, the variability in the SMD that is not accounted for by the baseline score.
+
+$$
+\epsilon = SMD - (\beta_0 + \beta_1 BaselineScore) ) \
+$$
+
+where, $\epsilon$ is the adjusted SMD, for which we simulated standard errors and then used it the outcome in metaregression, as described above for the unadjusted SMDs.
 
@@
 ```
+
 ### Analysis of all studies
@@
 z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_no_wl)){
-z_psy_con_vs_med_con[i] <- list_model_1_no_wl[[i]]$zval[condition=="psychotherapy_control"]
+for(i in 1: length(list_model_1_meta_reg)){
+z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
 
@@
 
-#### Meta-analysis of baseline values
-
-We next conducted a meta-analysis to test for differences in means at baseline.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Metanalysis of CDRS at baseline #
-
-df_with_cdrs <-  df_appl_v_orange %>%          
-  filter(instrument_name == "cdrs")
-
-library(meta)
-means_cdrs_baseline_control <- metamean(n = baseline_n_control,
-                   mean = baseline_mean_control,
-                   sd = baseline_sd_control,
-                   studlab = new_study_id,
-                   data = df_with_cdrs,
-                   sm = "MRAW",
-                   fixed = FALSE,
-                   random = TRUE,
-                   method.tau = "REML",
-                   hakn = TRUE,
-                   title = "CDRS Scores at Baseline")
-summary(means_cdrs_baseline_control)
-
-subgroup_cdrs_baseline_control <- update.meta(means_cdrs_baseline_control, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-means_cdrs_baseline_active <- metamean(n = baseline_n_active,
-                                        mean = baseline_mean_active,
-                                        sd = baseline_sd_active,
-                                        studlab = new_study_id,
-                                        data = df_with_cdrs,
-                                        sm = "MRAW",
-                                        fixed = FALSE,
-                                        random = TRUE,
-                                        method.tau = "REML",
-                                        hakn = TRUE,
-                                        title = "CDRS Scores at Baseline")
-#summary(means_cdrs_baseline_active)
-
-subgroup_cdrs_baseline_active <- update.meta(means_cdrs_baseline_active, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-# Metanalysis of HAMD at baseline #
-df_with_hamd <-  df_appl_v_orange %>%          
-  filter(instrument_name == "hamd")
-
-library(meta)
-means_hamd_baseline_control <- metamean(n = baseline_n_control,
-                                        mean = baseline_mean_control,
-                                        sd = baseline_sd_control,
-                                        studlab = new_study_id,
-                                        data = df_with_hamd,
-                                        sm = "MRAW",
-                                        fixed = FALSE,
-                                        random = TRUE,
-                                        method.tau = "REML",
-                                        hakn = TRUE,
-                                        title = "HAMD Scores at Baseline")
-#summary(means_hamd_baseline_control)
-
-subgroup_hamd_baseline_control <- update.meta(means_hamd_baseline_control, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-means_hamd_baseline_active <- metamean(n = baseline_n_active,
-                                       mean = baseline_mean_active,
-                                       sd = baseline_sd_active,
-                                       studlab = new_study_id,
-                                       data = df_with_hamd,
-                                       sm = "MRAW",
-                                       fixed = FALSE,
-                                       random = TRUE,
-                                       method.tau = "REML",
-                                       hakn = TRUE,
-                                       title = "HAMD Scores at Baseline")
-#summary(means_hamd_baseline_active)
-
-subgroup_hamd_baseline_active <- update.meta(means_hamd_baseline_active, 
-            subgroup = psy_or_med, 
-            tau.common = FALSE)
-
-```
+#### Addressing Regression to the Mean
+
+We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D on which there was a sufficient number of studies to metanalyse.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+### get CDRS studies
+cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
+
+#turn sds to sec
+cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+
+results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
+                                                         model_1, condition)
+
+### get HAM-D studies
+hamd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
+
+list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
+                                                          %in% hamd_study_ids,]
+
+hamd_studies_for_baseline_metareg <- list_hamd_study #
+
+#turn sds to sec
+hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
+                                                         model_1, condition)
+
+results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+
+```
+
+As can be seen in Table 3a and 3b, there baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
+As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+<!--# Charlotte, please add the n for each row.
+Easiest to modify the function so that it appends the baseline n together with the condition.
+-->
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3 HAM-D baselilne scores")
+```
+
+We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#### Let's start from the beginning and regress cohens on the baseline dataframe.
+
+# create a new list with dfs for the sims
+df_long_for_metan_adj_cohens_d <- df_long_for_metan
+# rename the cohens_d value to make space for the new cohen's d
+df_long_for_metan_adj_cohens_d <-
+  df_long_for_metan_adj_cohens_d %>% 
+rename(unadjusted_cohens_d = cohens_d,
+) 
+# estimate the cohen's d from the residuals
+model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$baseline_mean, na.action=na.exclude)
+
+# there is a great effect of the baseline means, as shown here
+results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
+
+# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
+df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
+
+# apply function to simulate standard errors
+list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d, 
+                                   num_repetitions = 1000, 
+                                   seed  = 1974,
+                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)), 
+                                   a = 0.45, 
+                                   b = .9, 
+                                   mean = 0.65, 
+                                   sd = 0.2)
+
+# add the four level variable and re-level
+for(i in 1: length(list_df_simulated_adj_cohens_d)){
+
+  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
+  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>% 
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
+                                                         "medication_control",
+                                                         "medication_active", 
+                                                         "psychotherapy_control",
+                                                         "psychotherapy_active")
+}
+
+# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
+# specify model
+model_1 <- as.formula(~ four_level_var)
+
+# run metareg function 
+# here you can use the simulated results directly
+list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
+aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
+aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
+
+# extract SMDs from the  list
+list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
+
+df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+
+```
+
+As can be seen in Table 4, the baseline mean has a very strong association with the SMD.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable(results_adjusted_cohens_d
+
+              , caption = "Table 4. Effect of baseline values on SMDs")
+```
+
+Table 5 shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
+As can be inferred from the non-overlapping confidence intervals, the difference between the two control conditions was significant (details of the regression model can be found in Supplementary Table XX <!--# Charlotte, please add there the aggregate_results_overall_adjusted_cohens_d -->).
+Differences were significant between active medication and psychotherapy control, but not between any of the other groups.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
+```
+
+Finally, we tested whether the simulated correlation values we used for simulation of the standard errors had an appreciable effect on the values of the adjusted SMDs.
+Supplemental Figure X shows that the variability of the estimated z-value was minimal<!--# Charlotte, the figure below should be supplemental-->.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# plot the mean z for the difference between controls
+z_psy_con_vs_med_con <- 0
+for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
+  z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
+
+}
+
+stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+
+stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
+  ggplot(aes(x = n_sims, y = z_value)) +
+  geom_point() +
+  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+  annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
+           hjust = -0.1, vjust = 0) +
+  theme_minimal() +
+  labs(
+    x = "Number of Simulations",
+    y = "z-value",
+    title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
+    subtitle = "Results from 1000 simulations with within-group standard errors"
+  )
+stab_sims_adjusted_cohens_d
+pdf(file = "stab_sims_adjusted_cohens_d.pdf")
+stab_sims_adjusted_cohens_d
+dev.off()
+
+```

### 2024-01-15 apples_and_oranges.qmd
Playing around with 'key' column, trying to find a solution

@@
 # Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
-# for CBT, fluox, esc
+# for CBT, fluox, esc. I am calling this cfe
 cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
@@
 
+# for wl and cau
+wl_or_cau_study_ids <- df_with_distinct_instruments %>%
+  filter(control_type %in% c("wl", "cau")) %>%
+  pull(new_study_id)
 df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key = paste(key1, key2, sep = "_"))
+  mutate(key3 = ifelse(new_study_id %in% wl_or_cau_study_ids, 3, NA))
+
+# for cdrs only
+cdrs_study_ids <- df_with_distinct_instruments %>%
+  filter(instrument_name == "cdrs")) %>%
+  pull(new_study_id)
+df_with_distinct_instruments <- df_with_distinct_instruments %>%
+  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))
+
+df_with_distinct_instruments <- df_with_distinct_instruments %>%
+  mutate(key = paste(key1, key2, key3, key4, sep = "_"))
 

### 2024-01-15 apples_and_oranges.qmd

@@
 cdrs_study_ids <- df_with_distinct_instruments %>%
-  filter(instrument_name == "cdrs")) %>%
+  filter(instrument_name == "cdrs") %>%
   pull(new_study_id)
@@
 ```
+
+We have also run models to take into accountregression to the mean within CDRS and HAMD.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+####code to extract baseline-adjusted post means for CDRS and HAMD
+
+de_meaned_baselilne_mean_cdrs <- (list_cdrs_study[[1]]$baseline_mean - mean(list_cdrs_study[[1]]$baseline_mean, na.rm = TRUE))
+
+lm_for_cdrs_smds <- lm(list_cdrs_study[[1]]$post_mean ~ de_meaned_baselilne_mean_cdrs +list_cdrs_study[[1]]$four_level_var,
+
+  na.action=na.exclude,
+
+   )
+
+#summary(lm_for_cdrs_smds)
+
+coefs_lm_for_cdrs_smds  <- broom:: tidy(lm_for_cdrs_smds)
+
+condition <- coefs_lm_for_cdrs_smds$term
+
+cdrs_smds <-c(coefs_lm_for_cdrs_smds$estimate[1], coefs_lm_for_cdrs_smds$estimate[-1] + coefs_lm_for_cdrs_smds$estimate[1])
+
+cdrs_upper_ci <- cdrs_smds + coefs_lm_for_cdrs_smds$std.error*1.96
+
+cdrs_lower_ci <- cdrs_smds - coefs_lm_for_cdrs_smds$std.error*1.96
+
+cdrs_smd_with_cis <- data.frame (
+
+  condition = levels(list_hamd_study$four_level_var),
+
+  cdrs_smds = cdrs_smds[-2],
+
+  cdrs_upper_ci = cdrs_upper_ci[-2],
+
+  cdrs_lower_ci = cdrs_lower_ci[-2]
+
+)
+
+# do the same for hamd
+
+de_meaned_baselilne_mean_hamd <- (list_hamd_study$baseline_mean - mean(list_hamd_study$baseline_mean, na.rm = TRUE))
+
+lm_for_hamd_smds <- lm(list_hamd_study$post_mean ~ de_meaned_baselilne_mean_hamd +list_hamd_study$four_level_var,
+
+                       na.action=na.exclude,
+
+)
+
+#summary(lm_for_hamd_smds)
+
+coefs_lm_for_hamd_smds  <- broom:: tidy(lm_for_hamd_smds)
+
+condition <- coefs_lm_for_hamd_smds$term
+
+hamd_smds <-c(coefs_lm_for_hamd_smds$estimate[1], coefs_lm_for_hamd_smds$estimate[-1] + coefs_lm_for_hamd_smds$estimate[1])
+
+hamd_upper_ci <- hamd_smds + coefs_lm_for_hamd_smds$std.error*1.96
+
+hamd_lower_ci <- hamd_smds - coefs_lm_for_hamd_smds$std.error*1.96
+
+hamd_smd_with_cis <- data.frame (
+
+condition = levels(list_hamd_study$four_level_var),
+
+hamd_smds = hamd_smds[-2],
+
+hamd_upper_ci = hamd_upper_ci[-2],
+
+hamd_lower_ci = hamd_lower_ci[-2]
+
+)
+
+```
+
+Tables 6a and 6b show the baeline-mean adjusted SMDs for the CDRS at outcome when the baseline measurement has been taken into account.
+<!--# Here Intercept refers to teh psychotherapy control.
+Sorry about the labelling of the rows, will improve.
+-->
+
+```{r}
+knitr:: kable(cdrs_smd_with_cis, caption = "Table 6a. CDRS baseline mean adjsuted SMDs")
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable(hamd_smd_with_cis, caption = "Table 6. HAM-D baseline-mean adjusted SMDs")
+```

### 2024-01-16 apples_and_oranges.qmd
I think I have fixed the problem with filtering IDs for the CBT, fluox, esc meta regression.

@@
 
-# Here I am creating a new column for df_long_for_metan, to be able to identify which studies featured a condition of interest. 
-# for CBT, fluox, esc. I am calling this cfe
-cbt_fluox_esc_study_ids <- df_with_distinct_instruments %>%
-  filter(active_type %in% c("cbt", "Fluoxetine", "Escitalopram")) %>%
-  pull(new_study_id)
-df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key1 = ifelse(new_study_id %in% cbt_fluox_esc_study_ids, 1, NA))
-
-# for wl 
-wl_study_ids <- df_with_distinct_instruments %>%
-  filter(control_type == "wl") %>%
-  pull(new_study_id)
-df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key2 = ifelse(new_study_id %in% wl_study_ids, 2, NA))
-
-# for wl and cau
-wl_or_cau_study_ids <- df_with_distinct_instruments %>%
-  filter(control_type %in% c("wl", "cau")) %>%
-  pull(new_study_id)
-df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key3 = ifelse(new_study_id %in% wl_or_cau_study_ids, 3, NA))
-
-# for cdrs only
-cdrs_study_ids <- df_with_distinct_instruments %>%
-  filter(instrument_name == "cdrs") %>%
-  pull(new_study_id)
-df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key4 = ifelse(new_study_id %in% cdrs_study_ids, 4, NA))
-
-df_with_distinct_instruments <- df_with_distinct_instruments %>%
-  mutate(key = paste(key1, key2, key3, key4, sep = "_"))
-
 # Step 2: turn dataframes to long
@@
 active_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, key, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
+  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
   rename(treatment = descr_active) %>% 
+  rename(type = active_type) %>% 
   rename_with(~ str_remove(., "_active")) %>% 
@@
 control_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, key, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
+  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
   rename(treatment = descr_control) %>% 
+  rename(type = control_type) %>% 
   rename_with(~ str_remove(., "_control")) %>% 
@@
 # save this as the master dataframe  --------------------------------------
-# use this datafram to perform all operations below in quarto
+# use this dataframe to perform all operations below in quarto
 # ask Charlotte to check steps above (lines 986 to 1121)
 write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
+
+#this will be important later in checking for multi arm psy studies 
+check_active_dups <- df_long_for_metan %>%
+  filter(new_study_id %in% cbt_fluox_esc_study_ids) %>% 
+  filter (psy_or_med == 1) %>% 
+  group_by(new_study_id) %>%
+  filter(n() >= 3)
+write.csv(check_active_dups, "check_active_dups.csv")
 
@@
 
-# use those ids to subset all dataframes in the list
-list_cbt_fluox_esc_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_cbt_fluox_esc_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% cbt_fluox_esc_study_ids,]
-
-}
+# Use those ids to subset all dataframes in the list
+# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
+# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criterion. 
+# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
+# We may have multiple controls per study id for this reason, though this isn't a problem 
+# conceptually.
+
+list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+})
 
 # count the number of studies
-study_count_cbt_fluox_esc_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cbt_fluox_esc_study_ids,])
-# CHARLOTTE please check. CB - come back to this, possible problem.
+cbt_fluox_esc_study <- df_long_for_metan %>%
+  filter(new_study_id %in% cbt_fluox_esc_study_ids,
+         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
+study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
 

### 2024-01-18 apples_and_oranges.qmd
Added in filtering for no wl and no wl or cau regressions. Checked study counts and they all seem correct.

@@
 # By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criterion. 
+# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
 # This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
@@
 study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
+# CB checked, looks good now.
 
@@
 # C. Estimate Means and CIs without WL ---------------------------------------
+
  # grab the ids for no waitlist
@@
 # use them to loop over the simulated list to subset all the dataframes.
-list_no_wl <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_no_wl[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                            %in% no_wl_ids,]
-
-}
+
+list_no_wl <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% no_wl_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
+})
 
 # count studies 
-study_count_no_wl_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_ids,])
-# CHARLOTTE please check
-# CB come back to this, possible problem.
+no_wl_studies <- df_long_for_metan %>% 
+  filter(new_study_id %in% no_wl_ids) %>%
+  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
+study_count_no_wl_study <- count_studies(no_wl_studies)
+# CB checked, looks good!
 
@@
  # grab the ids for no waitlist and cau
-no_wl_or_cau_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl" & df_appl_v_orange$control_type != "cau",]$new_study_id
+no_wl_cau_ids <- df_appl_v_orange %>%
+  filter(!(control_type %in% c("wl", "cau"))) %>%
+  pull(new_study_id)
 
 # use them to loop over the simulated list to subset all the dataframes.
-list_no_wl_or_cau <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_no_wl_or_cau[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                            %in% no_wl_or_cau_ids,]
-
-}
+
+list_no_wl_cau <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% no_wl_cau_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
+})
 
 # count studies 
-study_count_no_wl_or_cau_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% no_wl_or_cau_ids,])
-# CHARLOTTE please check
+no_wl_cau_studies <- df_long_for_metan %>% 
+  filter(new_study_id %in% no_wl_cau_ids) %>%
+  filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
+study_count_no_wl_cau_study <- count_studies(no_wl_cau_studies)
+# CB checked, looks good!
 
@@
 study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
-
-#CHARLOTTE please check. CB - come back to this, possible problem.
+# CB checked, correct.
 

### 2024-01-19 apples_and_oranges.qmd
Performed transformation of means and sds into percentages using min and max values of relevant scale.

@@
 
+# Charlotte to add in instrument end point values (mins / maxs)
+# We will use these to transform the scale into % as follows: (score - min of the scale)/(max-min)
+# We have done this for both means and standard deviations
+
+df_scale_ranges <- read.csv("scale_ranges.csv")
+df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
+
+df_appl_v_orange <- df_appl_v_orange %>% 
+  mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_baseline_sd_active = (baseline_sd_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_baseline_sd_control = (baseline_sd_control - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_post_sd_active = (post_sd_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_post_sd_control = (post_sd_control - scale_min) / (scale_max - scale_min))
+
 #Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
@@
 
+write.csv(df_with_distinct_instruments, "df_with_distinct_instruments.csv")
+
 # Step 2: turn dataframes to long
@@
   dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
-                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active) %>% 
+                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
+                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active) %>% 
   rename(treatment = descr_active) %>% 
@@
   dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
-                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control) %>% 
+                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
+                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control) %>% 
   rename(treatment = descr_control) %>% 
@@
 })
+
+view(list_cbt_fluox_esc_study[[1]])
 

### 2024-01-19 Script for cleaning merged dataset.R

@@ -55,7 +55,8 @@ merged_dataset <- merged_dataset %>%
       instrument %in% c("BDI", "bdi", "bdi-ii") ~ "bdi",
       instrument %in% c("cdi") ~ "cdi",
       instrument %in% c("K-SADS-L", "K-SADS", "K-SADS (adapted)") ~ "ksads",
-      instrument %in% c("mfq", "smfq") ~ "mfq",
+      instrument %in% c("mfq") ~ "mfq",
+      instrument %in% c("smfq") ~ "smfq",
       instrument %in% c("RADS", "rads") ~ "rads",
       instrument %in% c("bid") ~ "bid",
       instrument %in% c("CDS") ~ "cds",

### 2024-01-23 apples_and_oranges.qmd
Fixed bug

@@
 
-#this will be important later in checking for multi arm psy studies 
-check_active_dups <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids) %>% 
-  filter (psy_or_med == 1) %>% 
-  group_by(new_study_id) %>%
-  filter(n() >= 3)
-write.csv(check_active_dups, "check_active_dups.csv")
-
 ########### simulate so that each study has a value from a distribution of 
@@
 
-view(list_cbt_fluox_esc_study[[1]])
-
 # count the number of studies
@@
 
-# apply the metareg function to the list of cbt, fluox, esc
+# apply the metareg function to the list of no wl
 list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
@@
 
-# apply the metareg function to the list of cbt, fluox, esc
-list_model_1_no_wl_or_cau <- run_metaregression(list_no_wl_or_cau , model_1)
+# apply the metareg function to the list of no wl or cau
+list_model_1_no_wl_cau <- run_metaregression(list_no_wl_cau , model_1)
 
@@
 condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_no_wl_or_cau <-  aggregate_model_results(list_model_1_no_wl_or_cau, condition)
-aggregate_results_no_wl_or_cau <- cbind(aggregate_results_no_wl_or_cau, condition)
+aggregate_results_no_wl_cau <- aggregate_model_results(list_model_1_no_wl_cau, condition)
+aggregate_results_no_wl_cau <- cbind(aggregate_results_no_wl_cau, condition)
 
 # now use the function to extract the coefficients
-means_no_wl_or_cau <-  lapply(list_model_1_no_wl_or_cau, extract_coefficients_func)
+means_no_wl_cau <-  lapply(list_model_1_no_wl_cau, extract_coefficients_func)
 
@@
 condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
-coef_and_se_means_no_wl_or_cau <- calculate_mean_coefs_ses(means_no_wl_or_cau, condition)
-coef_and_se_means_no_wl_or_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_or_cau))
-
-coef_and_se_means_no_wl_or_cau$n <- study_count_no_wl_or_cau_study[study_count_no_wl_or_cau_study$is_missing 
+coef_and_se_means_no_wl_cau <- calculate_mean_coefs_ses(means_no_wl_cau, condition)
+coef_and_se_means_no_wl_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_cau))
+
+coef_and_se_means_no_wl_cau$n <- study_count_no_wl_cau_study[study_count_no_wl_cau_study$is_missing 
                                                      ==FALSE,]$n
@@
 
-# apply the metareg function to the list of cbt, fluox, esc
+# apply the metareg function to the list of cdrs studies
 model_1 <- as.formula(~ four_level_var)
@@
 
-# extract SMDs from the list for cbt fluox escit
-means_cdrs_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
+# extract SMDs from the list for cdrs
+means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
 

### 2024-01-23 Script for cleaning medication data.R
Merged in new age variables Calculated pooled sd for age

@@ -14,7 +14,8 @@ Working_Dataset_Medication <- read_excel("Working_Dataset_Medication.xlsx",
                                                        "numeric", "numeric", "numeric", "numeric", 
                                                        "numeric", "numeric", "text", "numeric", 
                                                        "text", "text", "text", "text", 
-                                                       "numeric", "numeric", "numeric", "numeric", 
+                                                       "numeric", "numeric", "numeric", "numeric",
+                                                       "numeric", "numeric", "numeric", "numeric",
                                                        "text", "text"))
 View(Working_Dataset_Medication)
 
@@ -30,9 +31,10 @@ Working_Dataset_Medication <- Working_Dataset_Medication %>% rename(active_type 
                               baseline_mean_active = dru_baseline_m, baseline_sd_active	= dru_baseline_sd, baseline_n_active =	dru_baseline_n_arm1,
                               baseline_mean_control = pla_baseline_m, baseline_sd_control	= pla_baseline_sd, baseline_n_control =	pla_baseline_n, 
                               active_mean_change = dru_mean_change,	active_sd_change = dru_sd_change, active_n_change =	dru_n_change,	
-                              control_mean_change = pla_mean_change, control_sd_change = pla_sd_change, control_n_change	= pla_n_change)
-Working_Dataset_Medication <- Working_Dataset_Medication %>% rename(active_mean_age = dru_mean_age, control_mean_age = pla_mean_age, 
-                                                                    active_percent_women	= dru_percent_women, control_percent_women =	pla_percent_women)
+                              control_mean_change = pla_mean_change, control_sd_change = pla_sd_change, control_n_change	= pla_n_change,
+                              age_m_active = dru_mean_age, age_sd_active = dru_sd_age, age_m_control = pla_mean_age, 
+                              age_sd_control = pla_sd_age, 
+                              active_percent_women	= dru_percent_women, control_percent_women =	pla_percent_women)
 
 #rename response variables to clarify that these numbers represent OBSERVED/REPORTED response rates
 # rather than those estimated by us

### 2024-01-23 Script for cleaning merged dataset.R

@@ -18,8 +18,6 @@ merged_dataset <- bind_rows(df_full_med, df_full_psych)
 merged_dataset <- dplyr:: select(merged_dataset, -c(primary, hierarchy, time))
 merged_dataset <- merged_dataset %>% relocate(descr_active, .after = control_type)
 merged_dataset <- merged_dataset %>% relocate(descr_control, .after = descr_active)
-merged_dataset <- merged_dataset %>% relocate(mean_age, .after = age_group)
-merged_dataset <- merged_dataset %>% relocate(percent_women, .after = control_mean_age)
 merged_dataset <- merged_dataset %>% relocate(responders_active: cuij_responders_control, .after = observed_resp_rate_control)
 
 #create vector indicating instrument primacy according to our hierarchy
@@ -110,17 +108,24 @@ cor(merged_dataset$responders_control, merged_dataset$cuij_responders_control, m
 #rename dataframe
 df_appl_v_orange <- merged_dataset
 
-# We have mean_age and percent_women reported overall for psy trials but per arm for med trials
-
-# create overall mean age variable for all studies 
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_mean_age = (active_mean_age * baseline_n_active + control_mean_age * baseline_n_control)
-                                                 /(baseline_n_active + baseline_n_control))
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(mean_age = coalesce(mean_age, overall_mean_age))
-
+# We have percent_women reported overall for psy trials but per arm for med trials
 #create overall percent women variable for all studies
 df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_percent_women = (active_percent_women * baseline_n_active + control_percent_women * baseline_n_control)
                                                  /(baseline_n_active + baseline_n_control))
 df_appl_v_orange <- df_appl_v_orange %>%  mutate(percent_women = coalesce(percent_women, overall_percent_women))
+
+# we have separate age variables for each arm and for overall. Where age is reported per arm, I will calculate an overall. 
+# I'm using an old variable name so I don't have the change the rest of the code
+ 
+df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_mean_age = (age_m_active * baseline_n_active + age_m_control * baseline_n_control)
+                                                 /(baseline_n_active + baseline_n_control))
[…]

### 2024-01-23 Script for cleaning psychotherapy data.R

@@ -1,11 +1,11 @@
 library(tidyverse)
 library(dplyr)
 library(readxl)
+library(stringr)
 
 set.seed(1998) # to reproduce anything with random numbers
 
 Full_Dataset_Cuijpers_MA <- read_excel("Full_Dataset_Cuijpers_MA.xlsx")
-View(Full_Dataset_Cuijpers_MA)
 
 # Sub commas for dots and convert to numeric variables
 
@@ -88,7 +88,7 @@ df_full <- full_join(df_full, for_merge)
 # create dataframe with main variables needed for meta-analysis
 df_full_psych <- df_full %>% 
   select(c(Column1, study, year, condition_arm1, condition_arm2, descr_arm1, descr_arm2, instrument, rating,
-           mean_arm1: n_arm2, baseline_m_arm1:baseline_n_arm2, mean_age, percent_women, responders_arm1, responders_arm2, 
+           mean_arm1: n_arm2, baseline_m_arm1:baseline_n_arm2, percent_women, responders_arm1, responders_arm2, 
            ee, ec, country, comorbid_mental, `comorbid_mental?`, diagnosis))
 
 # rename variables
@@ -112,17 +112,26 @@ df_full_psych$baseline_sd_active <- gsub(",", ".", df_full_psych$baseline_sd_act
 df_full_psych$baseline_n_active <- gsub(",", ".", df_full_psych$baseline_n_active)
 df_full_psych$baseline_sd_control <- gsub(",", ".", df_full_psych$baseline_sd_control)
 df_full_psych$baseline_n_control <- gsub(",", ".", df_full_psych$baseline_n_control)
-df_full_psych$mean_age <- gsub(",", ".", df_full_psych$mean_age)
 
 df_full_psych$baseline_sd_active <- as.numeric(df_full_psych$baseline_sd_active)
 df_full_psych$baseline_n_active <- as.numeric(df_full_psych$baseline_n_active)
 df_full_psych$baseline_sd_control <- as.numeric(df_full_psych$baseline_sd_control)
 df_full_psych$baseline_n_control <- as.numeric(df_full_psych$baseline_n_control)
-df_full_psych$mean_age <- as.numeric(df_full_psych$mean_age)
 
 # We have noticed a few errors in Cuijpers dataset
-# One is regarding the incorrect extraction of data for De Jong Heesen 2020. I have fixed this in full dataset Cuijpers MA. 
[…]

### 2024-01-23 Script for cleaning medication data.R
Debugging and fixing a few small errors

@@ -17,7 +17,7 @@ Working_Dataset_Medication <- read_excel("Working_Dataset_Medication.xlsx",
                                                        "numeric", "numeric", "numeric", "numeric",
                                                        "numeric", "numeric", "numeric", "numeric",
                                                        "text", "text"))
-View(Working_Dataset_Medication)
+Working_Dataset_Medication$year <- sub("\\.0$", "", Working_Dataset_Medication$year)
 
 #add vector indicating whether psychotherapy or medication, where 1 is psych and 0 is med
 psy_or_med <- rep(0, nrow(Working_Dataset_Medication))

### 2024-01-24 apples_and_oranges.qmd
Added meta regression F, using baseline percentage values

@@
 # E) the CDRS only sample
+# F) percentage variables
 
@@
 coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
+
+# F. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------
+
+# count studies - same as for overall sample
+n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) 
+df_count_studies <- count_studies(df_long_for_metan )
+
+# specify model
+model_1 <- as.formula(~ four_level_var + perc_baseline_mean )
+
+# run metareg function 
+# here you can use the simulated results directly
+list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_perc <-  aggregate_model_results(list_model_1_meta_reg_perc, condition)
+aggregate_results_perc <- cbind(aggregate_results_perc, condition)
+
+# extract SMDs from the  list
+means_perc <-  lapply(list_model_1_meta_reg_perc, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_perc <- calculate_mean_coefs_ses(means_perc, condition)
+df_mean_coefs_perc <- data.frame(cbind(condition,df_mean_coefs_perc))
+
+# add the ns
+df_mean_coefs_perc <- data.frame(cbind(df_mean_coefs_perc, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
 

### 2024-01-25 apples_and_oranges.qmd
Added plots

@@
 
+# Plots  -----------------------
+
+#define groups
+df_long_for_metan <- df_long_for_metan %>%
+  mutate(
+    group = case_when(
+      psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
+      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
+      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
+      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
+      TRUE ~ NA_character_  
+    )
+  )
+
+group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
+
+#Plot cohens d per arm
+
+ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
+  geom_point(position = position_jitter(width = 0.2), size = 3) +
+  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+  scale_color_manual(values = group_colors) +
+  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+#Plot percentage  baseline means
+
+ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+  geom_point(position = position_jitter(width = 0.2), size = 3) +
+  scale_color_manual(values = group_colors) +
+  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+# Box plots
+
+ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
+  geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
+  scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
+  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
+  geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+  geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+  scale_fill_manual(values = group_colors) +
+  labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
 ```

### 2024-01-26 apples_and_oranges.qmd
Calculated change scores using percentage transformed variables

@@
 
-#Plot cohens d per arm
+# Plot cohens d per arm
 
@@
 
-#Plot percentage  baseline means
-
-ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+# Now look at change scores of percentage transformed variables
+
+df_long_for_metan <- df_long_for_metan %>% 
+  mutate(perc_change = perc_post_mean - perc_baseline_mean)
+
+ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
   geom_point(position = position_jitter(width = 0.2), size = 3) +
+  geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
+  geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
   scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+  labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
   theme_minimal() +
   theme(legend.position = "none")
+
+# # Plot percentage  baseline means 
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
 

### 2024-01-28 apples_and_oranges.qmd
several changes with percent variable

@@
   mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_active = (baseline_sd_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this #is the best way to estimate the SD of the linear transform of the percentage
+
   mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_control = (baseline_sd_control - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_baseline_sd_control = baseline_sd_control  / (scale_max - scale_min)) %>% 
   mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_active = (post_sd_active - scale_min) / (scale_max - scale_min)) %>% 
+  mutate(perc_post_sd_active = post_sd_active  / (scale_max - scale_min)) %>% 
   mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_control = (post_sd_control - scale_min) / (scale_max - scale_min))
+  mutate(perc_post_sd_control = post_sd_control  / (scale_max - scale_min))
 
@@
 
-# count studies - same as for overall sample
-n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) 
-df_count_studies <- count_studies(df_long_for_metan )
+# the first thing to do is to create a new dataset with the percentage cohen's d
+
+list_df_simulated_percentage <- list_df_simulated
+
+for(i in 1: length(list_df_simulated_percentage)){
+
+  list_df_simulated_percentage[[i]]$cohens_d <- 
+            (list_df_simulated_percentage[[i]]$perc_post_mean - list_df_simulated_percentage[[i]]$perc_baseline_mean)/
+    ((list_df_simulated_percentage[[i]]$perc_post_sd + list_df_simulated_percentage[[i]]$perc_baseline_sd)/2)
+
+}
 
 # specify model
-model_1 <- as.formula(~ four_level_var + perc_baseline_mean )
+model_1 <- as.formula(~ four_level_var )
 
@@
 # here you can use the simulated results directly
-list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated, model_1)
+list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_1)
 
@@
 df_mean_coefs_perc <- data.frame(cbind(df_mean_coefs_perc, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
+
+##### now for the baseline controlled variable
+# specify model
+model_2 <- as.formula(~ four_level_var + perc_baseline_mean )
+
+# run metareg function 
+# here you can use the simulated results directly
+list_model_2_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_2)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_perc_mod_2 <-  aggregate_model_results(list_model_2_meta_reg_perc, condition)
+aggregate_results_perc_mod_2 <- cbind(aggregate_results_perc_mod_2, condition)
+
+# extract SMDs from the  list
+means_perc_mod_2 <-  lapply(list_model_2_meta_reg_perc, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_perc_mod_2 <- calculate_mean_coefs_ses(means_perc_mod_2, condition)
+df_mean_coefs_perc_mod_2 <- data.frame(cbind(condition,df_mean_coefs_perc_mod_2))
+
+# add the ns
+df_mean_coefs_perc_mod_2 <- data.frame(cbind(df_mean_coefs_perc_mod_2, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
 

### 2024-02-05 apples_and_oranges.qmd
several changes

@@
 
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-4}
 
@@
 
-$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$
+$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$ {#eq-5}
 
@@
 
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
+$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$ {#eq-6}
 
@@
 $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$
+$$ {#eq-7}
 
 $$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
-$$ {#eq-6}
+$$ {#eq-8}
 
@@
 
-$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-7}
+$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-9}
 
@@
 
-$$u_i \sim N(0, \tau^2) $$ {#eq-8}
+$$u_i \sim N(0, \tau^2) $$ {#eq-10}
 
@@
 
-$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-9}
+$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-11}
 
@@
     \end{cases}
-\end{aligned}$$ {#eq-10}
+\end{aligned}$$ {#eq-12}
 
@@
 z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
-$$ {#eq-11}
+$$ {#eq-13}
 
@@
 Fourth, we tested whether our results could be accounted for by differential regression to the mean.
-In an initial step, we tested in metaregression as above for differences in baseline means for those medication and psychotherapy studies that shared the same instruments.
-We then accounted for the effect that possible differing baseline values across all studies studies' outcomes by regressing the SMDs of studies on their respective baseline values of the instrument with which the SMD was calculated.
-For example, in a study that used the CDRS, this was used to calculate the SMD.
-This SMD was then used as the outcome and the baseline value of the CDRS, termed *BaselineScore* below, in that study was used as the independent variable as follows: $$
-SMD = \beta_0 + \beta_1 BaselineScore + \epsilon
-$$ {#eq-12}
-
-This allows us to estimate the effect of the baseline score on the SMD by evaluating $\beta_1$.
-We can then re-arrange Equation 12 to extract the residuals, that is, the variability in the SMD that is not accounted for by the baseline score.
+In an initial step, we tested in metaregression as above for differences in baseline means.
+For this we used a min-max normalisation to turn each study arm mean score into a percentage using the following formalism:
 
 $$
-\epsilon = SMD - (\beta_0 + \beta_1 BaselineScore) ) \
+\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
+$$ {#eq-14}
+
+where, $$\bar{X}$$ is the mean score of each study arm on the primary questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible value of the scale in question, and for which the the standard deviation is calculated thus:
+
 $$
-
-where, $\epsilon$ is the adjusted SMD, for which we simulated standard errors and then used it the outcome in metaregression, as described above for the unadjusted SMDs.
+\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
+$$ {#eq-15}
+
+where $\text{SD}_{X}$ is the original standard deviation of the mean for X.
+Applying equations (12) and (13) on the baseline and outcome means and standard deviations of each study allowed us to then calculate SMDs and standard errors using equations (4) and (5)
 
@@
 # Plots  -----------------------
-
-#define groups
-df_long_for_metan <- df_long_for_metan %>%
-  mutate(
-    group = case_when(
-      psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-      TRUE ~ NA_character_  
-    )
-  )
-
-group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-
-# Plot cohens d per arm
-
-ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-  geom_point(position = position_jitter(width = 0.2), size = 3) +
-  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-  scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-  theme_minimal() +
-  theme(legend.position = "none")
-
-# Now look at change scores of percentage transformed variables
-
-df_long_for_metan <- df_long_for_metan %>% 
-  mutate(perc_change = perc_post_mean - perc_baseline_mean)
-
-ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
-  geom_point(position = position_jitter(width = 0.2), size = 3) +
-  geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
-  geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
-  scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
-  theme_minimal() +
-  theme(legend.position = "none")
-
-# # Plot percentage  baseline means 
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+# 
+# #define groups
+# df_long_for_metan <- df_long_for_metan %>%
+#   mutate(
+#     group = case_when(
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
+#       TRUE ~ NA_character_  
+#     )
+#   )
+
+# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
+# 
+# # Plot cohens d per arm
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
 #   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
 #   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
 #   theme_minimal() +
 #   theme(legend.position = "none")
-
-# Box plots
-
-ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-  geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-  scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-  geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-  geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-  scale_fill_manual(values = group_colors) +
-  labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-  theme_minimal() +
-  theme(legend.position = "none")
+# 
+# # Now look at change scores of percentage transformed variables
+# 
+# df_long_for_metan <- df_long_for_metan %>% 
+#   mutate(perc_change = perc_post_mean - perc_baseline_mean)
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
+# 
+# # # Plot percentage  baseline means 
+# # 
+# # ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+# #   geom_point(position = position_jitter(width = 0.2), size = 3) +
+# #   scale_color_manual(values = group_colors) +
+# #   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+# #   theme_minimal() +
+# #   theme(legend.position = "none")
+# 
+# # Box plots
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
+#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
+#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
+#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+#   scale_fill_manual(values = group_colors) +
+#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
 
@@
 
+### do ALL studies using percentage at baseline
+all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
+
+#turn sds to sec
+all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
+                                        sqrt(all_studies_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+# also change this for the function to work
+all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
+results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
+                                                         model_1, condition)
+
 ### get CDRS studies
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3 HAM-D baselilne scores")
-```
-
-We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
+knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+```
+
+We next addressed the e
 
@@
 
-# create a new list with dfs for the sims
-df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# rename the cohens_d value to make space for the new cohen's d
-df_long_for_metan_adj_cohens_d <-
-  df_long_for_metan_adj_cohens_d %>% 
-rename(unadjusted_cohens_d = cohens_d,
-) 
-# estimate the cohen's d from the residuals
-model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$baseline_mean, na.action=na.exclude)
-
-# there is a great effect of the baseline means, as shown here
-results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-
-# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-
-# apply function to simulate standard errors
-list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d, 
-                                   num_repetitions = 1000, 
-                                   seed  = 1974,
-                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)), 
-                                   a = 0.45, 
-                                   b = .9, 
-                                   mean = 0.65, 
-                                   sd = 0.2)
-
-# add the four level variable and re-level
-for(i in 1: length(list_df_simulated_adj_cohens_d)){
-
-  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>% 
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-                                                         "medication_control",
-                                                         "medication_active", 
-                                                         "psychotherapy_control",
-                                                         "psychotherapy_active")
-}
-
-# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# specify model
-model_1 <- as.formula(~ four_level_var)
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-
-df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+# # create a new list with dfs for the sims
+# df_long_for_metan_adj_cohens_d <- df_long_for_metan
+# # rename the cohens_d value to make space for the new cohen's d
+# df_long_for_metan_adj_cohens_d <-
+#   df_long_for_metan_adj_cohens_d %>% 
+# rename(unadjusted_cohens_d = cohens_d,
+# ) 
+# # estimate the cohen's d from the residuals
+# model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$baseline_mean, na.action=na.exclude)
+# 
+# # there is a great effect of the baseline means, as shown here
+# results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
+# 
+# # extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
+# df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
+# 
+# # apply function to simulate standard errors
+# list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d, 
+#                                    num_repetitions = 1000, 
+#                                    seed  = 1974,
+#                                    n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)), 
+#                                    a = 0.45, 
+#                                    b = .9, 
+#                                    mean = 0.65, 
+#                                    sd = 0.2)
+# 
+# 
+# # add the four level variable and re-level
+# for(i in 1: length(list_df_simulated_adj_cohens_d)){
+#   
+#   list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
+#   list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>% 
+#     mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+#                                       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+#     )
+#   
+#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
+#   
+#   # relevel so that medication control becomes the reference category for the regression
+#   #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
+#                                                          "medication_control",
+#                                                          "medication_active", 
+#                                                          "psychotherapy_control",
+#                                                          "psychotherapy_active")
+# }
+# 
+# 
+# 
+# 
+# 
+# # Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
+# # specify model
+# model_1 <- as.formula(~ four_level_var)
+# 
+# # run metareg function 
+# # here you can use the simulated results directly
+# list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
+# 
+# # extract coefficients and model characteristics.
+# condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
+# aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
+# aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
+# 
+# # extract SMDs from the  list
+# list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
+# 
+# # calculate mean SMDs and ses
+# df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
+# 
+# df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+# 
+# 
+# 
+#
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_adjusted_cohens_d
-
-              , caption = "Table 4. Effect of baseline values on SMDs")
+# knitr:: kable(results_adjusted_cohens_d 
+#               
+#               , caption = "Table 4. Effect of baseline values on SMDs")
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# plot the mean z for the difference between controls
-z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
-  z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
-
-}
-
-stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-
-stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
-  ggplot(aes(x = n_sims, y = z_value)) +
-  geom_point() +
-  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-  annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
-           hjust = -0.1, vjust = 0) +
-  theme_minimal() +
-  labs(
-    x = "Number of Simulations",
-    y = "z-value",
-    title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
-    subtitle = "Results from 1000 simulations with within-group standard errors"
-  )
-stab_sims_adjusted_cohens_d
-pdf(file = "stab_sims_adjusted_cohens_d.pdf")
-stab_sims_adjusted_cohens_d
-dev.off()
+# 
+# # plot the mean z for the difference between controls
+# z_psy_con_vs_med_con <- 0
+# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
+#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
+#   
+# }
+# 
+# 
+# 
+# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+# 
+# 
+# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
+#   ggplot(aes(x = n_sims, y = z_value)) +
+#   geom_point() +
+#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+#                arrow = arrow(length = unit(0.3, "cm")),
+#                color = "black") +
+#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
+#            hjust = -0.1, vjust = 0) +
+#   theme_minimal() +
+#   labs(
+#     x = "Number of Simulations",
+#     y = "z-value",
+#     title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
+#     subtitle = "Results from 1000 simulations with within-group standard errors"
+#   )
+# stab_sims_adjusted_cohens_d
+# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
+# stab_sims_adjusted_cohens_d
+# dev.off()
+#
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-####code to extract baseline-adjusted post means for CDRS and HAMD
-
-de_meaned_baselilne_mean_cdrs <- (list_cdrs_study[[1]]$baseline_mean - mean(list_cdrs_study[[1]]$baseline_mean, na.rm = TRUE))
-
-lm_for_cdrs_smds <- lm(list_cdrs_study[[1]]$post_mean ~ de_meaned_baselilne_mean_cdrs +list_cdrs_study[[1]]$four_level_var,
-
-  na.action=na.exclude,
-
-   )
-
-#summary(lm_for_cdrs_smds)
-
-coefs_lm_for_cdrs_smds  <- broom:: tidy(lm_for_cdrs_smds)
-
-condition <- coefs_lm_for_cdrs_smds$term
-
-cdrs_smds <-c(coefs_lm_for_cdrs_smds$estimate[1], coefs_lm_for_cdrs_smds$estimate[-1] + coefs_lm_for_cdrs_smds$estimate[1])
-
-cdrs_upper_ci <- cdrs_smds + coefs_lm_for_cdrs_smds$std.error*1.96
-
-cdrs_lower_ci <- cdrs_smds - coefs_lm_for_cdrs_smds$std.error*1.96
-
-cdrs_smd_with_cis <- data.frame (
-
-  condition = levels(list_hamd_study$four_level_var),
-
-  cdrs_smds = cdrs_smds[-2],
-
-  cdrs_upper_ci = cdrs_upper_ci[-2],
-
-  cdrs_lower_ci = cdrs_lower_ci[-2]
-
-)
-
-# do the same for hamd
-
-de_meaned_baselilne_mean_hamd <- (list_hamd_study$baseline_mean - mean(list_hamd_study$baseline_mean, na.rm = TRUE))
-
-lm_for_hamd_smds <- lm(list_hamd_study$post_mean ~ de_meaned_baselilne_mean_hamd +list_hamd_study$four_level_var,
-
-                       na.action=na.exclude,
-
-)
-
-#summary(lm_for_hamd_smds)
-
-coefs_lm_for_hamd_smds  <- broom:: tidy(lm_for_hamd_smds)
-
-condition <- coefs_lm_for_hamd_smds$term
-
-hamd_smds <-c(coefs_lm_for_hamd_smds$estimate[1], coefs_lm_for_hamd_smds$estimate[-1] + coefs_lm_for_hamd_smds$estimate[1])
-
-hamd_upper_ci <- hamd_smds + coefs_lm_for_hamd_smds$std.error*1.96
-
-hamd_lower_ci <- hamd_smds - coefs_lm_for_hamd_smds$std.error*1.96
-
-hamd_smd_with_cis <- data.frame (
-
-condition = levels(list_hamd_study$four_level_var),
-
-hamd_smds = hamd_smds[-2],
-
-hamd_upper_ci = hamd_upper_ci[-2],
-
-hamd_lower_ci = hamd_lower_ci[-2]
-
-)
+```{# {r, warning=FALSE, message = FALSE, echo=FALSE}
+# ####code to extract baseline-adjusted post means for CDRS and HAMD 
+# 
+#  
+# 
+# de_meaned_baselilne_mean_cdrs <- (list_cdrs_study[[1]]$baseline_mean - mean(list_cdrs_study[[1]]$baseline_mean, na.rm = TRUE)) 
+# 
+#                                     
+# 
+#  
+# 
+#                                  
+# 
+# lm_for_cdrs_smds <- lm(list_cdrs_study[[1]]$post_mean ~ de_meaned_baselilne_mean_cdrs +list_cdrs_study[[1]]$four_level_var,
+# 
+#  
+# 
+#   na.action=na.exclude,
+# 
+#    )
+# 
+#  
+# 
+#  
+# 
+# #summary(lm_for_cdrs_smds)
+# 
+#  
+# 
+# coefs_lm_for_cdrs_smds  <- broom:: tidy(lm_for_cdrs_smds)
+# 
+#  
+# 
+# condition <- coefs_lm_for_cdrs_smds$term
+# 
+# cdrs_smds <-c(coefs_lm_for_cdrs_smds$estimate[1], coefs_lm_for_cdrs_smds$estimate[-1] + coefs_lm_for_cdrs_smds$estimate[1])
+# 
+# cdrs_upper_ci <- cdrs_smds + coefs_lm_for_cdrs_smds$std.error*1.96
+# 
+# cdrs_lower_ci <- cdrs_smds - coefs_lm_for_cdrs_smds$std.error*1.96
+# 
+#  
+# 
+# cdrs_smd_with_cis <- data.frame (
+# 
+#   condition = levels(list_hamd_study$four_level_var),
+# 
+#   cdrs_smds = cdrs_smds[-2],
+# 
+#   cdrs_upper_ci = cdrs_upper_ci[-2],
+# 
+#   cdrs_lower_ci = cdrs_lower_ci[-2]
+# 
+# )
+# 
+#  
+# 
+#  
+# 
+# # do the same for hamd
+# 
+# de_meaned_baselilne_mean_hamd <- (list_hamd_study$baseline_mean - mean(list_hamd_study$baseline_mean, na.rm = TRUE)) 
+# 
+#  
+# 
+#  
+# 
+#  
+# 
+# lm_for_hamd_smds <- lm(list_hamd_study$post_mean ~ de_meaned_baselilne_mean_hamd +list_hamd_study$four_level_var,
+# 
+#                       
+# 
+#                        na.action=na.exclude,
+# 
+# )
+# 
+#  
+# 
+#  
+# 
+# #summary(lm_for_hamd_smds)
+# 
+#  
+# 
+# coefs_lm_for_hamd_smds  <- broom:: tidy(lm_for_hamd_smds)
+# 
+#  
+# 
+#  
+# 
+# condition <- coefs_lm_for_hamd_smds$term
+# 
+# hamd_smds <-c(coefs_lm_for_hamd_smds$estimate[1], coefs_lm_for_hamd_smds$estimate[-1] + coefs_lm_for_hamd_smds$estimate[1])
+# 
+# hamd_upper_ci <- hamd_smds + coefs_lm_for_hamd_smds$std.error*1.96
+# 
+# hamd_lower_ci <- hamd_smds - coefs_lm_for_hamd_smds$std.error*1.96
+# 
+#  
+# 
+# hamd_smd_with_cis <- data.frame (
+# 
+# condition = levels(list_hamd_study$four_level_var),
+# 
+# hamd_smds = hamd_smds[-2],
+# 
+# hamd_upper_ci = hamd_upper_ci[-2],
+# 
+# hamd_lower_ci = hamd_lower_ci[-2]
+# 
+# )
+# 
+#  
+# 
+#
 

### 2024-02-22 apples_and_oranges.qmd
Clinical sample

@@
 
-# F. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------
+# F Clinical Levels Depression Sensitivity Analysis ---------------------------------------
+
+# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
+
+# test <- df_appl_v_orange %>%
+#   filter(psy_or_med == 1) %>%
+#   distinct(new_study_id, .keep_all = TRUE)
+# 
+# summary_test <- test %>%
+#   group_by(diagnosis) %>%
+#   summarise(count = n())
+
+#take study ids where sample has clinical levels of depression
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_clin_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% clin_study_ids,]
+
+}
+
+# count the number of studies
+study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
+# CB checked, correct.
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
+coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
+
+# add the ns to the dataframe
+coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n
+
+# G. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------
 

### 2024-02-23 apples_and_oranges.qmd
Trying to debug error with the percent_women variable, will revisit on Monday

@@
 library(metafor)
+library(meta)
 ```
@@
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active) %>% 
+                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
   rename(treatment = descr_active) %>% 
@@
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control) %>% 
+                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
   rename(treatment = descr_control) %>% 
@@
 results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+
+# Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels
+
+# We will do in two ways
+# First by excluding studies with a diagnostic classification of "sub"
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+  filter(new_study_id %in% clin_study_ids)
+
+#turn sds to sec
+clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
+                                        sqrt(clin_studies_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+# also change this for the function to work
+clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
+results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
+                                                         model_1, condition)
+
+# Now lets include only studies with classification of "mdd"
+
+mdd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id
+
+mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+  filter(new_study_id %in% mdd_study_ids)
+
+mdd_studies_baseline_metareg %>% 
+  filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
+  summarise(n = n())
+
+#turn sds to sec
+mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
+                                        sqrt(mdd_studies_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+# also change this for the function to work
+mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
+results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
+                                                         model_1, condition)
+
+# # Now CBT studies
+# 
+# cbt_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt",]$new_study_id
+# 
+# cbt_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+#   filter(new_study_id %in% cbt_study_ids) %>% 
+#   filter(!(arm_effect_size == "cohens_d_active" & !(type == "cbt")))
+# 
+# 
+# #turn sds to sec
+# cbt_studies_baseline_metareg$baseline_stand_error <- cbt_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(cbt_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# cbt_studies_baseline_metareg$baseline_mean <- cbt_studies_baseline_metareg$perc_baseline_mean
+# results_cbt_studies_baseline_metareg <- run_metareg_and_extract(cbt_studies_baseline_metareg,  
+#                                                          model_1, condition)
+
+# Now CBT + all med studies
+
+cbt_meds_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
+
+cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+#turn sds to sec
+cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
+                                        sqrt(cbt_meds_studies_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+# also change this for the function to work
+cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
+results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
+                                                         model_1, condition)
+
+# Look at the diagnostics of included studies
+
+filtered_data <- df_appl_v_orange %>%
+  filter(psy_or_med == 1) %>% 
+  filter(new_study_id %in% cbt_meds_study_ids) %>%
+  distinct(new_study_id, .keep_all = TRUE)
+
+summary_result <- filtered_data %>%
+  group_by(diagnosis) %>%
+  summarise(count = n())
+
+# Now the CBT + med studies, filtering out the subclinical studies
+
+# Now CBT + all med studies
+
+clin_cbt_meds_study_ids <-
+  df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id
+
+clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+  filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+#turn sds to sec
+clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
+                                        sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+# also change this for the function to work
+clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
+results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
+                                                         model_1, condition)
+
+# Now start looking at perc_women variable
+
+met_perc_women <- metagen(TE = "percent_women",
+                           seTE = "percent_women_std_error",
+                           studlab = "new_study_id",
+                          data = df_long_for_metan,
+                           sm = "SMD",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across studies",
+                          subgroup = "four_level_var",
+                          tau.common = FALSE,
+                          na.rm = TRUE)
+
+# ### get CDRS clin studies
+#  clin_cdrs_studies_baseline_metareg <- cdrs_studies_for_baseline_metareg %>% 
+#    filter(new_study_id %in% clin_study_ids)
+#  
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# 
+# results_clin_cdrs_metareg_baseline <- run_metareg_and_extract(clin_cdrs_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# # Just realised this is identical, as all the studies that use the CDRS have clinical samples. 
+# 
+# ### get HAM-D clin studies
+#  clin_hamd_studies_for_baseline_metareg <- hamd_studies_for_baseline_metareg %>% 
+#    filter(new_study_id %in% clin_study_ids)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# results_clin_hamd_studies_for_baseline_metareg <- run_metareg_and_extract(clin_hamd_studies_for_baseline_metareg, 
+#                                                          model_1, condition)
+# 
+# results_clin_hamd_studies_for_baseline_metareg$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+# 
+#
 

### 2024-02-26 apples_and_oranges.qmd
Meta-analysis for percent women

@@
 
+# Turn age sd into se
+
+df_long_for_metan <- df_long_for_metan %>% 
+  mutate (se_age = sd_age / sqrt(baseline_n) )
+
 #dim(df_long_for_metan ) #check dimension
@@
 
-# Now CBT + all med studies
-
 clin_cbt_meds_study_ids <-
@@
 
-met_perc_women <- metagen(TE = "percent_women",
-                           seTE = "percent_women_std_error",
-                           studlab = "new_study_id",
-                          data = df_long_for_metan,
+df_for_gender_metan <- list_df_simulated[[1]] %>% 
+  filter(!is.na(percent_women))
+
+met_perc_women <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan,
                            sm = "SMD",
@@
                            title = "percentage women across studies",
-                          subgroup = "four_level_var",
-                          tau.common = FALSE,
-                          na.rm = TRUE)
+                           subgroup = four_level_var,
+                           tau.common = FALSE)
+met_perc_women
+
+# Now start looking at age variable
+
+df_for_age_metan <- list_df_simulated[[1]] %>% 
+  filter(!is.na(mean_age))
+
+met_age <- metagen(TE = mean_age,
+                           seTE = sd_age / sqrt(baseline_n),
+                           studlab = new_study_id,
+                           data = df_for_age_metan,
+                           sm = "SMD",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across studies",
+                           subgroup = four_level_var,
+                           tau.common = FALSE)
+
+met_age
 

### 2024-02-26 Script for control characteristics.R
Giannis' script

@@ -1,0 +1,68 @@
+library(readxl)
+library(tidyverse)
+
+psy_controls_data <- read_excel("for_despina_and_giannis_200224.xlsx")
+
+# List of columns to clean
+columns_to_clean <- c(
+  "number_of_sites",
+  "Number_of_sessions",
+  "frequency_weeks",
+  "Length_of_sessions_mins",
+  "Total_hours_of_intervention_hours",
+  "Total_period_of_intervention_weeks"
+)
+
+# Convert non-numeric values to NA in specified columns
+cleaned_data <- psy_controls_data %>%
+  mutate_at(vars(columns_to_clean), ~as.numeric(as.character(.)))
+
+
+group_function <- function(dataframe, my_groups,columns) {
+  result_dataframe <- data.frame(
+    Group = character(),
+    Column = character(),
+    N = numeric(),
+    Mean = numeric(),
+    Std_Dev = numeric(),
+    Median = numeric(),
+    IQR = numeric(),
+    stringsAsFactors = FALSE
+  )
+  unique_groups <- unique(dataframe[[my_groups]])
+  for (group in unique_groups) {
+    group_data <- dataframe[dataframe[[my_groups]] == group, ]
+    for (col in columns) {
+      col_data <- group_data[[col]]
+      n <- sum(!is.na(col_data))
+      mean_val <- mean(col_data, na.rm = TRUE)
+      std_dev <- sd(col_data, na.rm = TRUE)
+      median_val <- median(col_data, na.rm = TRUE)
+      iqr <- IQR(col_data, na.rm = TRUE)
+      result_dataframe <- rbind(result_dataframe,
+                                data.frame(Group = group,
+                                           Column = col, N = n, Mean = mean_val,
+                                           Std_Dev = std_dev, Median = median_val,
+                                           IQR = iqr, stringsAsFactors = FALSE))
+    }
+  }
+  return(result_dataframe)
+}
+
+sessions <- group_function(cleaned_data,"levels_var","Number_of_sessions")
+print(sessions)
+
+frequency <- group_function(cleaned_data,"levels_var","frequency_weeks")
+print(frequency)
+
+Length_sessions <- group_function(cleaned_data,"levels_var","Length_of_sessions_mins")
+print(Length_sessions)
+
+Total_hours <- group_function(cleaned_data,"levels_var","Total_hours_of_intervention_hours")
+print(Total_hours)
+
[…]

### 2024-02-26 apples_and_oranges.qmd
Added code for looking and gender and age

@@
 
-# # Now CBT studies
-# 
-# cbt_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt",]$new_study_id
-# 
-# cbt_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-#   filter(new_study_id %in% cbt_study_ids) %>% 
-#   filter(!(arm_effect_size == "cohens_d_active" & !(type == "cbt")))
-# 
-# 
-# #turn sds to sec
-# cbt_studies_baseline_metareg$baseline_stand_error <- cbt_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(cbt_studies_baseline_metareg$baseline_n)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# cbt_studies_baseline_metareg$baseline_mean <- cbt_studies_baseline_metareg$perc_baseline_mean
-# results_cbt_studies_baseline_metareg <- run_metareg_and_extract(cbt_studies_baseline_metareg,  
-#                                                          model_1, condition)
-
 # Now CBT + all med studies
@@
                            data = df_for_gender_metan,
-                           sm = "SMD",
+                           sm = "",
                            fixed = FALSE,
@@
 
+# looking at clinical sample only
+
+df_for_gender_metan_clin <- df_for_gender_metan %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_perc_women_clin <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across clinical studies",
+                           subgroup = four_level_var,
+                           tau.common = FALSE)
+met_perc_women_clin
+
 # Now start looking at age variable
@@
                            data = df_for_age_metan,
-                           sm = "SMD",
+                           sm = "",
                            fixed = FALSE,
@@
                            title = "age across studies",
+                           subgroup = four_level_var,
+                           tau.common = FALSE)
+
+met_age
+
+# looking at clinical sample only
+
+df_for_age_metan_clin <- df_for_age_metan %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_age <- metagen(TE = mean_age,
+                           seTE = sd_age / sqrt(baseline_n),
+                           studlab = new_study_id,
+                           data = df_for_age_metan_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across clinical studies",
                            subgroup = four_level_var,

### 2024-02-27 apples_and_oranges.qmd
Age variable transformations

@@
 
-# Create SEs proportions for percentage women --------------------------------------------
-
-# # We also need to calculate SE for proportion women for the baseline calculations
-# # for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
-
-product_perc_women <-  (df_appl_v_orange$percent_women/100)*
-  (1-(df_appl_v_orange$percent_women/100) )
-
-total_n <- df_appl_v_orange$baseline_n_active + 
-  df_appl_v_orange$baseline_n_control
-
-df_appl_v_orange$percent_women_std_error <- sqrt(product_perc_women/total_n )
-
 # Calculate SE for baseline severity --------------------------------------
@@
 # Step 2: turn dataframes to long
+
+# A small bit of cleaning
+
+df_with_distinct_instruments <- df_with_distinct_instruments %>% 
+  rename (percent_women_active = active_percent_women, 
+          percent_women_control = control_percent_women,
+          percent_women_overall = percent_women)
+
 # A: turn long the rows with active
@@
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
+                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall) %>%
   rename(treatment = descr_active) %>% 
@@
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women, percent_women_std_error, mean_age, sd_age) %>% 
+                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall) %>%
   rename(treatment = descr_control) %>% 
@@
 
-# Turn age sd into se
+# I'm going to perform  the operations to calculate overall age and percent women here now, I previously did this in the other script, however it actually needs to be done once the dataframe is turned long.
 
 df_long_for_metan <- df_long_for_metan %>% 
-  mutate (se_age = sd_age / sqrt(baseline_n) )
+  group_by(new_study_id) %>%
+  mutate(n_overall = sum(baseline_n)) %>% 
+  mutate(age_overall = sum(age_m * baseline_n) / sum(baseline_n)) %>% 
+  mutate(mean_age = coalesce(age_overall, age_m_overall)) %>% 
+  mutate(pooled_sd_age = sqrt(sum((age_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
+  mutate(se_age = pooled_sd_age / sqrt(n_overall)) %>% 
+  mutate(gender_overall = sum(percent_women * baseline_n) / sum(baseline_n)) %>% 
+  mutate(percent_women = coalesce(percent_women_overall, gender_overall))
+
+# now just get rid of the unnecessary columns as these are causing clutter
+
+df_long_for_metan <- df_long_for_metan %>% 
+  select(-c(percent_women_overall, age_m, age_sd, age_m_overall, age_sd_overall, age_overall, gender_overall))
+
+# Create SEs proportions for percentage women --------------------------------------------
+
+# # We also need to calculate SE for proportion women for the baseline calculations
+# # for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
+
+df_long_for_metan <- df_long_for_metan %>% 
+  mutate(product_perc_women = (percent_women/100)* (1-(percent_women/100)) )
+
+df_long_for_metan <- df_long_for_metan %>% 
+  mutate(percent_women_std_error = sqrt(product_perc_women/ n_overall ))
 
@@
 
+# Looking at demographics at baseline
+# Currently we have both control and active conditions, we just need each study once
+
+df_baseline_demographics <- df_long_for_metan %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
 # Now start looking at perc_women variable
 
-df_for_gender_metan <- list_df_simulated[[1]] %>% 
+df_for_gender_metan <- df_baseline_demographics %>% 
   filter(!is.na(percent_women))
@@
                            title = "percentage women across studies",
-                           subgroup = four_level_var,
+                           subgroup = psy_or_med,
                            tau.common = FALSE)
@@
                            title = "percentage women across clinical studies",
-                           subgroup = four_level_var,
+                           subgroup = psy_or_med,
                            tau.common = FALSE)
@@
 
+# Now looking at the CBT + med studies only
+
+cbt_meds_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
+
+df_for_gender_metan_cbt <- df_for_gender_metan %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_perc_women_cbt <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across cbt and med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_perc_women_cbt
+
 # Now start looking at age variable
 
-df_for_age_metan <- list_df_simulated[[1]] %>% 
+df_for_age_metan <- df_baseline_demographics %>% 
   filter(!is.na(mean_age))
@@
 met_age <- metagen(TE = mean_age,
-                           seTE = sd_age / sqrt(baseline_n),
+                           seTE = se_age,
                            studlab = new_study_id,
@@
                            title = "age across studies",
-                           subgroup = four_level_var,
+                           subgroup = psy_or_med,
                            tau.common = FALSE)
@@
 
-met_age <- metagen(TE = mean_age,
-                           seTE = sd_age / sqrt(baseline_n),
+met_age_clin <- metagen(TE = mean_age,
+                           seTE = se_age,
                            studlab = new_study_id,
@@
                            title = "age across clinical studies",
-                           subgroup = four_level_var,
+                           subgroup = psy_or_med,
                            tau.common = FALSE)
 
-met_age
+met_age_clin
+
+# Now cbt studies only
+
+df_for_age_metan_cbt <- df_for_age_metan %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_age_cbt <- metagen(TE = mean_age,
+                           seTE = se_age,
+                           studlab = new_study_id,
+                           data = df_for_age_metan_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across cbt + med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+met_age_cbt
+
+# Now look at baseline severity for overall psy vs med
+# Need to calculate the variables first
+
+df_for_baseline_severity <- df_long_for_metan %>% 
+  group_by(new_study_id) %>%
+  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
+  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
+  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
+
+df_for_baseline_severity <- df_for_baseline_severity %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
+met_sev <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
 

### 2024-02-27 Script for cleaning merged dataset.R

@@ -108,24 +108,26 @@ cor(merged_dataset$responders_control, merged_dataset$cuij_responders_control, m
 #rename dataframe
 df_appl_v_orange <- merged_dataset
 
-# We have percent_women reported overall for psy trials but per arm for med trials
-#create overall percent women variable for all studies
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_percent_women = (active_percent_women * baseline_n_active + control_percent_women * baseline_n_control)
-                                                 /(baseline_n_active + baseline_n_control))
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(percent_women = coalesce(percent_women, overall_percent_women))
+# The code below should actually be implemented once we turn the dataframe to long, which we do in the quarto. So I will not run this code here. 
 
-# we have separate age variables for each arm and for overall. Where age is reported per arm, I will calculate an overall. 
-# I'm using an old variable name so I don't have the change the rest of the code
- 
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_mean_age = (age_m_active * baseline_n_active + age_m_control * baseline_n_control)
-                                                 /(baseline_n_active + baseline_n_control))
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(mean_age = coalesce(age_m_overall, overall_mean_age))
-
-# I'd like to create a pooled SD for age
-df_appl_v_orange <- df_appl_v_orange %>%  
-  mutate(pooled_sd_age = sqrt(  (   (baseline_n_active - 1)*((age_sd_active)^2)   + (baseline_n_control - 1)*((age_sd_control)^2)) /
-                                                                        (baseline_n_active + baseline_n_control - 2)))
-df_appl_v_orange <- df_appl_v_orange %>%  mutate(sd_age = coalesce(age_sd_overall , pooled_sd_age))
+# # We have percent_women reported overall for psy trials but per arm for med trials
+# #create overall percent women variable for all studies
+# df_appl_v_orange <- df_appl_v_orange %>%  mutate(overall_percent_women = (active_percent_women * baseline_n_active + control_percent_women * baseline_n_control)
+#                                                  /(baseline_n_active + baseline_n_control))
[…]

### 2024-02-28 apples_and_oranges.qmd
Checking SE coding Add new intro

@@
 
-Depression is the leading cause of disability in adolescents and influential guidelines recommend that it be treated with either psychotherapy or anti-depressant medication or their combination.
-The evidence base for this recommendation typically derives from the appraisal of randomised controlled trials (RCTs) in which one modality (psychotherapy or anti-depressants) are compared against a control condition.
-In this paper we: a) test the hypothesis that medication control arms are more efficacious than psychotherapy control arms and that this undermines the validity of treatment comparisons and therefore of existing guidelines about depression treatment; b) explore how variation in treatment control arms can itself be exploited to advance our thinking concerning the mechanisms of depression and its treatment.
-
-Clinicians across medicine and other health professions are faced with choices between different treatment modalities for their patients, be it between surgical or medical (drug-based) treatments or, in the case of adolescent depression, between psychotherapy and antidepressant medication.
-To make informed choices, clinicians rely on the extant evidence, frequently summarised in the form of national guidelines or other treatment recommendations.
-Such a comparison is inherent in the internationally influential UK National Institute of Clinical Excellence (NICE) guidelines for adolescent depression which recommend that youth be first offered psychological therapy over medication for most presentations of depression.
-Such comparisons between the two treatment modalities are inherent in other recommendations, e.g.
-the practice parameter issued by the American Academy of Child and Adolescent Psychiatry or the Royal Australian and New Zealand College of Psychiatrists.
-
-These recommendations are not based on head to head trials between modalities; only one head-to-head trial exists in adolescent depression.
-Instead, they rely on the comparison of the results of randomised controlled trials (RCTs) of each modality against RCTs of the other.
-In other words, it rests on a comparison of comparisons.
-
-In the case of antidepressant studies, the control is the placebo pill (standard also in the rest of medicine), whilst controls for psychotherapy studies can vary substantially from waiting list to treatment as usual to an attention control, such as psychoeducation.
-Stated in simple formal terms, the comparison relies on testing this equality,
-
-$$Effect_{Med} = Effect_{Psy}$$ {#eq-1}
-
-where *Effect* denotes the effect on depression that either medication (*Med* ) or psychotherapy (*Psy*) have.
-Yet for this indirect comparison to be valid, some basic assumptions need to hold.
-The most important of these is the *all-else-being-equal,* or more technically *ceteris paribus,* assumption with regards to trial design.
-By necessity, therefore, the control conditions for each antidepressant and psychotherapy trials must be equal for inferences to be valid.
-We call this the *equality of controls* assumption.
-
-The importance of this assumption can be easily intuited by expanding equation 1 to include the comparisons on which each side of that equation rests:
-
-$$Effect_{MedActive} - Effect_{MedControls} = Effect_{PsyActive} - Effect_{PsyControls}$$ {#eq-2}
-
-where MedActive and PsyActive are the active arms of antidepressant and psychotherapy trials, respectively, and MedControls and PsyControls the respective control arms.
-The assumption here has to be that the controls are equal, that is, $$ Effect_{MedControls} = Effect_{PsyControls}$$ A simple example from medicine helps illustrate why this assumption is important Let the two modalities of treatment for appendicitis be antibiotic medication and surgery, and let there be a set of trials for each modality.
-In the medication trials, on average 40% of participants respond to the antibiotics and only 0% to placebo; in the surgery trial, 80% of people respond to surgery and 40% to sham.
-If one relied on Equation 1 to compare the treatments they would arrive at the absurd conclusion that the two treatments are equal and recommend to a patient that it does not really matter which one they choose.
-Playing around with numbers in which no equality of the respective control arms is required, leads to other risible conclusions.
-Yet, in the dicussion about depression treatments, a focus on the equality of controls is surprisingly absent.
-
-The importance of testing the equality of controls assumption for patients and the public can be vast because treatment guidelines, clinicians' advice to patients, and patients' informed choices are all affected by the validity of treatment comparisons.
-Similarly, the rational allocation of public funds towards treatment modalities rests on valid comparisons between them.
-
-Beyond its immediate clinical importance, understanding the nature of controls in clinical trials of depression is key for reasons of causal inference and mechanistic understanding of treatment.
-Adolescent depression is notable for a relatively high placebo effect: the proportion of adolescents responding to placebo is higher in depression than in anxiety, and it is higher for adolescent vs adult depression.
-The reasons for these differences remain unclear and are typically treated as nuisance effects to be minimised by using trial designs such as a placebo lead in period.
-However, an alternative view is that placebo effects, or more generally, variability in the response to control conditions, may be informative about mechanisms of improvement.
-If, for example, the antidepressant effect of placebo is stronger than that of equivalent control arms in psychotherapy, then we ought to ask about the possible explanations of such differences and consider whether they can be exploited for improving treatment delivery, as previously suggested.
-
-In this paper, we have two aims: first, test whether the equality of controls assumption of adolescent depression treatment holds, and therefore scrutinise the validity of current recommendations concerning choice between treatment modalities; second,we explore the variabiliity in trial control arms across and within the two treatment modalities and examine how they relate to anti-depressant effects.
-
-Our main hypothesis is that the within group effect of psychotherapy controls is substantially weaker than that of the placebo pill and we will test this using random effects meta-regression.
-We will also use series of sensitivity analyses.
-First we compared CBT trial arms with those of trials involving fluoxetine and escitalopram.
-CBT is the most widely studied treatment and, similar to fluoxetine, it has metanalytic evidence supporting its use.
-Both fluoxetine and escitalopram are approved by the FDA as treatments for adolescent depression.
-We also conduct analyses excluding waitlist control arms as it could be argued that waitlist control arms represent outliers amongst psychotherapy control studies that reduce the estimate of the overall efficacy.
-Finally, we also conduct sensitivity analyses in the form of simulations, to ensure that results are robust to estimations of the standard error of the change scores.
-
-We then go on to examine the control arms of psychological treatments in both a qualitative/descriptive way (e.g.
-the content of attention control) and by quantifying characteristics such as session frequency, duration of delivery.
-We then explore how these characteristics relate to the magnitude of within group change.
+There are two principal treatment modalities for adolescent depression: psychotherapy, medication, or both.
+Where does one turn to find the evidence that will inform their treatment options?
+This question is relevant for patients and their carers, for clinicians and for policy makers when they plan services.
+However, the question is particularly difficult to answer for adolescent depression, where there are limited data from head-to-head trials of medication and psychotherapy, and where recommendations must therefore be derived from indirect comparisons of treatment efficacy.
+
+Guidelines, such as the ones that the internationally influential UK National Institute of Clinical Excellence (NICE) have produced for adolescent depression, are a principal source of such information.
+NICE recommend that youth be first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression.
+This conclusion is in keeping with two sources of evidence.
+On the one hand, medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine (ref); and on the other hand, psychotherapy meta-analyses that conclude psychotherapy to be effective for adolescent depression (ref).
+However, such conclusions seem at odds with those of a recent network meta-analysis (ref), an established method of comparing treatments with each other using both direct (head-to-head) and indirect (indirectly treatment A with treatment C, via studies that directly compare treatments A with B and B with C) evidence.
+Indeed, the network meta-analysis concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than pill placebo or psychological controls.
+Given this confusing evidence base, how should patients, carers, clinicians and policy makers make decisions on treatment options for adolescent depression?
+
+In this paper, we examine whether the existing evidence base for adolescent depression treatment can offer valid answers to such questions.
+Below, we provide a conceptual framework for answering such questions and state our hypotheses that we will test using data from existing trials.
+Two points are relevant to indirect comparisons of treatment modalities with each other.
+
+First, whether the participants of trials in one modality are comparable to those in another modality.
+Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved in a trial, are comparable.
+
+Starting with the first point, to be able to compare between different trials one must assume that these trials sample from the same population.
+If they do not, then the validity of any comparisons, including those conducted through network metanalysis (which rests on the principal of transitivity) are questionable.
+
+Indeed, comparing outcomes (Y) between psychotherapy and medication trials requires us to contrast what is called the sample average treatment effect $\tau$ of each, defined in the following way:
+
+$$
+\tau_{psy} =  E(Y_{1} - Y_{0} \,|\, S, psy)
+$$
+$$
+\tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\ 
+$$ {#eq-1}
+
+where the operator E denotes the expectation over the differences in outcomes between those who received the intervention (T = 1) and those who received the control condition (T = 0), for each sample, $S$, where psy and med stand for psychotherapy and medication respectively.
+
+Obviously, this comparison rests on the assumption that trials in both modalities sample from the same population, $P$, of patients. Formally, this can be expressed as follows:
+
+$$E(Y_{1} \,|\, \text{S, psy}) = E(Y_{1} \,|\, P, \text{psy})$$
+
+$$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$ {#eq-2}
+
+signifying that the effect found in the population would be expected to be found in the same population for each treatment.
+
+This assumption may be hard to meet.
+Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
+Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
+Some of these characteristics, particularly baseline severity, may moderate treatment response (ref) and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
+
+Here we will compare between four key sample characteristics, namely baseline severity in the outcome, number of sites, gender and age in each sample.
+
+In terms of the second point, differences in trial design may impact outcomes in a differential way between antidepressant and psychotherapy trials.
+Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation; by contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation (cite: Assessment of blinding in randomized controlled trials of antidepressants for depressive disorders 2000−2020: A systematic review and meta-analysis, Lancet).
+This creates differential expectations between medication and psychotherapy trials.
+Importantly, the placebo control has been developed in order to match as closely as possible the intervention condition, so as to minimise differences in expectancy between conditions.
+By contrast, psychotherapy control arms vary across waitlist controls, treatment as usual and active controls.
+These differences in expectation essentially favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially the difference between them), because participants in the active condition could be content for receiving the “cutting edge treatment” whilst those in the control will be dissatisfied for having  missed out on “proper treatment”.
+And this is important because expectancy is associated with treatment outcomes.
+This also poses problems when trying to infer indirect comparisons in network metanalyses where, for example, CBT is compared to placebo control and medication — given the likely differential expectation effects, comparisons to the unblinded psychotherapy controls may be biased.
+
+Another difference in design that has potential implications for which patients are selected into the trial is the number of sites in a trial.
+Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response.
+This phenomenon is hard to explain fully with the data available, but may be due to lower quality of phenotyping in such studies, with higher measurement (and therefore diagnostic classification) errors, leading to issues such as spontaneous remission or regression to the mean.
+In contrast to medication trials, psychotherapy trials typically involve one or fewer sites.
+
+An inter-related issue concerns the nature of control interventions being used.
+Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al) to the intervention: what would have been the outcome in an individual had they not received the intervention.
+This implies that there is a latent distribution of values that represent that counterfactual condition which control arms in trials are meant to approximate.
+Those latent values of the counterfactual condition should, on average, not be different between psychotherapy and medication trials, provided that the samples are representative of the same underlying population (see Eqs 1& 2).
+If the average response to placebo and psychotherapy controls differs systematically from each other, then this is either due to the fact that the trials sample from different populations or because the control conditions differ in their effects (e.g.
+because of how much they do or do not protect against expectancy effects).
+
+Understanding the nature of controls for each treatment modality is important for a similar reason.
+Often, in the public domain, psychotherapy and medication are compared to each other on the basis of their respective effect sizes.
+However, as evident from Eqs 1 and 2, these effect sizes represent differences between the active intervention and the control condition (placebo or psychotherapy control).
+For these effect sizes to be comparable, placebo and psychotherapy controls ought to be the equal.
+Otherwise, misleading conclusions could be drawn, e.g.
+two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% - 60% and another arose from a difference of 40% - 0%.
+
+In this paper, we examine psychotherapy and medication trials in the following ways.
+First, we compare key baseline characteristics of medication vs psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity; b) number of sites involved; c) gender composition and d) age.
+Second, we assess the mean efficacy of psychotherapy controls vs placebo.
+We recognise that both these sets of analyses pull data out of the randomised comparisons between treatment arms.
+However, we believe that this is justified for two reasons: a) because it is important to make transparent to all, particularly decision makers in healthcare, the raw data before these are entered into more complex modelling such as network metanalysis, as this allows them to form opinions about the quality and limitations of the input data; b) our aim here is not to make claims about the relative efficacy of each treatment arm, but rather establish whether the conditions for the possibility of comparisons are fulfilled.
+Thus, the comparisons between control conditions are not meant to lead to inferences about placebo being “more efficacious” than psychotherapy controls, but rather to make transparent the problem that they seem to derive from different distributions.
+Third, we examine the quality of psychotherapy controls as such, by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
 
@@
 Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive any responses.
-**Yet to do** We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
+We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
 We used the same search terms outlined in Cipriani (2016).
 
-NOTE: **Charlotte** to please check code lines 986 to 1121.
-**CB**: Done.
-NOTE: **Charlotte** please check that the studies I have in the *df_long_for_metan* dataframe makes sense and correspond to what you would expect.
-In the beginning of the results below, I explain in detail what is missing where.
-**CB**: I've checked and there are fewer psy active conditions that I expected - it seems some of the trials with multiple active arms have been filtered out.
-I have now fixed this and the numbers look correct.
-The numbers look right for med studies.
-One thing - for psy the no of studies with missing Cohens d for controls should probably be considered 6 (not 7) as it is absent for March/TADS because we removed it (didn't want placebo to be considered as a psy control) rather than there being missing data.
-<!--# Charlotte, that's all great.
-What we now need here is an account of exactly how  we searched and how we used the other datasets.
-Follow previous examples, though in our case, it will be a lot about how we used the accounts of others.
-Please make sure to say where that we asked about missing information.
-**CB** Completed above.
--->
-
 ## Statistical Analysis
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
-
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-4}
+As the measure of effect of each individual study, we used the within-group standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
+
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-3}
 
@@
 
-For the purposes of metanalysis, it is necessary to estimate a standard error of the change score, that is of the SMD. This is calculated according to:
-
-$$ SE_{change} = \sqrt{\frac{r_{t_{1}t_{2}}}{n} + \frac{SMD^2}{2n}}$$ {#eq-5}
+For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
+
+$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$ {#eq-5}
 
@@
 
-In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics: <!--# Georgina, I have used the Truncated Normal, we can obviously do sensitivity analyses with other ones -->
+In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
 
@@
 
-###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy #variable. The output is used below in 5.
-# it is a slightly awkward one, because I couldnt' come up with a better way to add the intercept to #each coefficient
+###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy variable. The output is used below in 5.
+# it is a slightly awkward one, because I couldn't' come up with a better way to add the intercept to each coefficient
 # given the named output of the built in coef function. 
-# here I exctract the coeffcients
+# here I extract the coefficients
 extract_coefficients_func <- function(df_with_coefs){
@@
 ############5. Function to get the means out of the SMDs (this is similar to Func 3 and I should at some point create one more general one)
-# here the argument list_of_dfs is the list of extracted coefficients that you get out of the #extract_coefficients_func
-# which itself you get from the run_metaregression function. The argument conditions refers to #the levels of the variable that describes each study arm
+# here the argument list_of_dfs is the list of extracted coefficients that you get out of the extract_coefficients_func
+# which itself you get from the run_metaregression function. The argument conditions refers to the levels of the variable that describes each study arm
 
@@
 
+# Double coding SE for argyris
+double_check <- list_df_simulated[[1]]
+
+double_check <- double_check %>% 
+  mutate (se_check = sqrt(  ((2*(1 - correlation_sim_values )/baseline_n) + (cohens_d^2/ 2*baseline_n) )))
+
+view(double_check)
+
 ```
@@
 
-# Charlotte to add in instrument end point values (mins / maxs)
-# We will use these to transform the scale into % as follows: (score - min of the scale)/(max-min)
-# We have done this for both means and standard deviations
+# Here we add in instrument end point values (mins / maxs).
+# We will use these to transform the scale into % as follows: (observed score - min of the scale)/(max-min)
+# We have done this for both means and standard deviations.
 
@@
   mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this #is the best way to estimate the SD of the linear transform of the percentage
-
+  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this is the best way to estimate the SD of the linear transformation of the score 
   mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
@@
 
-#Need to use SMDs, ie our Cohen's d and then use Standard error of SMD, to achieve this
-# I need reliabilities.
-
-# note re: CDRS reliability from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
+# Need to use SMDs (ie our Cohen's d) and then use standard error of SMD, to achieve this I need test-retest reliabilities of instruments.
+
+# CDRS reliability taken from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
 # Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
@@
 ### A few more tidying things from Argyris before doing metanalyses
-# # discovered an error in the percentage women of the Fristad study. I have checked in the
-# # cuijpers dataset and the correct percentage is 43.1, but could not verify with the paper as it is not in 
-# # our folder and after a quick search I could not find it online either. Messaged Charlotte on Discord to
-# # check again. # CB checked and all good.
+# Discovered some errors in the percentage women variable. Have gone back and checked. 
 df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1
@@
 
-### Important: create a dataset that will have unique control studies (see problem that we identified with Charlotte, 
-#namely common control conditions)
-# create new id with Charlotte to help with better identification and work with duplicates (see below) 
+### Important: create a dataset that will have unique control studies (see problem that we identified, namely common control conditions)
+# create new id to help with better identification and work with duplicates (see below) 
 df_appl_v_orange  <- df_appl_v_orange  %>%
@@
 However the descr columns are empty for med studies, so I'm going to paste values across to fix this error.
+
 df_appl_v_orange <- df_appl_v_orange %>% 
@@
 
-# A small bit of cleaning
+# A small bit of cleaning so the code below will work
 
@@
 
-# I'm going to remove the March / TADS psy control row. It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist.
+# I'm going to remove the March / TADS psy control row.
+It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist as such (the control is placebo, which is not a psy control).
 
@@
 
-# I'm going to perform  the operations to calculate overall age and percent women here now, I previously did this in the other script, however it actually needs to be done once the dataframe is turned long.
+# I'm going to perform  the operations to calculate overall age and percent women here now.
 
@@
 # use this dataframe to perform all operations below in quarto
-# ask Charlotte to check steps above (lines 986 to 1121)
+
 write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
@@
                            tau.common = FALSE)
+
+met_sev
+
+# clinical sample
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+df_for_baseline_severity_clin <- df_for_baseline_severity %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_sev_clin <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity clinical",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_sev_clin
+
+# cbt + med
+
+df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_sev_cbt <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity cbt + med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_sev_cbt
 

### 2024-03-01 apples_and_oranges.qmd
Running some baseline analyses

@@
 
+### Sample characteristics
+
+We will test in a metaregression for differences between psychotherapy versus medication trials in sample characteristics at baseline.
+
+First, we compared depression severity levels at baseline.
+In order to compare across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
+
+$$
+\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
+$$ {#eq-3}
+
+where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
+The standard deviation is calculated thus:
+
+$$
+\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
+$$ {#eq-4}
+
+where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline.
+
+We also conducted metaregressions to compare psychotherapy vs medication trials on the gender composition of the sample, mean age, and number of trial sites.
+
 ### Measures of Effect
@@
 We then used these simulated datasets in the subsequent metanalyses.
-
-<!--# Charlotte, I am particularly keen for you to code independently the SE calculation, maybe use all the other parts as they are, but check the SEs.
-Once you have re-assured yourself about it, could you please read the code for the other steps below, but break it down by taking it out of the function and probably out of the loop and verifying that you would get the same results for one dataset, e.g.
-the first one in the list of 1000.
-It would be amazing to verify the results this way.
-Finally, as discussed, we can vary the parammeters of the distribution if we have better a prioris-->
 
@@
 # it is a slightly awkward one, because I couldn't' come up with a better way to add the intercept to each coefficient
-# given the named output of the built in coef function. 
-# here I extract the coefficients
+# given the named output of the built in coef function. here I extract the coefficients
+
 extract_coefficients_func <- function(df_with_coefs){
@@
 
-# Double coding SE for argyris
-double_check <- list_df_simulated[[1]]
-
-double_check <- double_check %>% 
-  mutate (se_check = sqrt(  ((2*(1 - correlation_sim_values )/baseline_n) + (cohens_d^2/ 2*baseline_n) )))
-
-view(double_check)
-
 ```
@@
 library(tidyverse)
-# Start here------------------------------------------------------
+# Transforming data ------------------------------------------------------
 # import master dataset
@@
 df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1
+df_appl_v_orange[df_appl_v_orange$study=="Clarke, 1995",]$percent_women <-47.3
+df_appl_v_orange[df_appl_v_orange$study=="Moeini, 2019",]$percent_women <-100
+df_appl_v_orange[df_appl_v_orange$study=="Santomauro, 2016",]$percent_women <-40
 
@@
 
-# now just get rid of the unnecessary columns as these are causing clutter
+# Now just get rid of the unnecessary columns as these are causing clutter
 
@@
 # save this as the master dataframe  --------------------------------------
-# use this dataframe to perform all operations below in quarto
+# use this dataframe to perform all operations below
 
@@
 
-Fourth, we tested whether our results could be accounted for by differential regression to the mean.
-In an initial step, we tested in metaregression as above for differences in baseline means.
-For this we used a min-max normalisation to turn each study arm mean score into a percentage using the following formalism:
-
-$$
-\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
-$$ {#eq-14}
-
-where, $$\bar{X}$$ is the mean score of each study arm on the primary questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible value of the scale in question, and for which the the standard deviation is calculated thus:
-
-$$
-\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
-$$ {#eq-15}
-
-where $\text{SD}_{X}$ is the original standard deviation of the mean for X.
-Applying equations (12) and (13) on the baseline and outcome means and standard deviations of each study allowed us to then calculate SMDs and standard errors using equations (4) and (5)
-
 # Results
 
-Studies included in the metaregression.
+## Included studies
 
@@
 
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
+Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
+
+<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X.
+CB - done.
+I removed psychodynamic because there weren't any active conditions of this type.
+-->
+
+Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
+In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
+All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
+
+## Sample characteristics at baseline in medication versus psychotherapy trials
+
+Using a random effects meta-regression we compared psychotherapy versus medication trials on four domains: gender composition, age, baseline depression severity levels, and number of trial sites.
+We first examined each of these across all studies, and then conducted two sensitivity analyses where we excluded psychotherapy studies which 1) recruited participants with sub clinical depression levels and 2) did not use CBT as the active intervention.
+
+### Gender
+
+Gender composition was similar across psychotherapy and medication trials,
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# Start by looking at demographics at baseline
+# Currently we have both control and active conditions, we just need each study once
+
+df_baseline_demographics <- df_long_for_metan %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
+# Now start looking at perc_women variable
+
+# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs
+
+df_for_gender_metan <- df_baseline_demographics %>% 
+  filter(!is.na(percent_women))
+
+met_perc_women <- metagen(TE.random = percent_women,
+                           seTE.random = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+summary_results <- summary(met_perc_women, byvar = "subgroup")
+
+# Convert the results to a dataframe
+result_df <- data.frame(
+  TE = summary_met_perc_women$TE.random,
+  seTE = summary_met_perc_women$seTE.random,
+  lower = summary_met_perc_women$lower.random,
+  upper = summary_met_perc_women$upper.random
+)
+
+# looking at clinical sample only
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+df_for_gender_metan_clin <- df_for_gender_metan %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_perc_women_clin <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across clinical studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_perc_women_clin
+
+# Now looking at the CBT + med studies only
+
+cbt_meds_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
+
+df_for_gender_metan_cbt <- df_for_gender_metan %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_perc_women_cbt <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across cbt and med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_perc_women_cbt
+
+knitr:: kable(summary_table, "latex", caption = "Gender composition")
+
+# Now start looking at age variable
+
+df_for_age_metan <- df_baseline_demographics %>% 
+  filter(!is.na(mean_age))
+
+met_age <- metagen(TE = mean_age,
+                           seTE = se_age,
+                           studlab = new_study_id,
+                           data = df_for_age_metan,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+met_age
+
+# looking at clinical sample only
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+df_for_age_metan_clin <- df_for_age_metan %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_age_clin <- metagen(TE = mean_age,
+                           seTE = se_age,
+                           studlab = new_study_id,
+                           data = df_for_age_metan_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across clinical studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+met_age_clin
+
+# Now cbt studies only
+
+df_for_age_metan_cbt <- df_for_age_metan %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_age_cbt <- metagen(TE = mean_age,
+                           seTE = se_age,
+                           studlab = new_study_id,
+                           data = df_for_age_metan_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "age across cbt + med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+met_age_cbt
+
+# Now look at baseline severity for overall psy vs med
+# Need to calculate the variables first
+
+df_for_baseline_severity <- df_long_for_metan %>% 
+  group_by(new_study_id) %>%
+  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
+  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
+  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
+
+df_for_baseline_severity <- df_for_baseline_severity %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
+met_sev <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+met_sev
+
+# clinical sample
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+df_for_baseline_severity_clin <- df_for_baseline_severity %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_sev_clin <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity clinical",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_sev_clin
+
+# cbt + med
+
+df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
+  filter(new_study_id %in% cbt_meds_study_ids) %>% 
+  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+
+met_sev_cbt <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity cbt + med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+met_sev_cbt
+
+# ### do ALL studies using percentage at baseline
+# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
+# 
+# 
+# #turn sds to sec
+# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(all_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
+# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# ### get CDRS studies
+# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
+# 
+# #turn sds to sec
+# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
+#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# 
+# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# ### get HAM-D studies
+# hamd_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
+# 
+# 
+# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
+#                                                           %in% hamd_study_ids,]
+# 
+# hamd_studies_for_baseline_metareg <- list_hamd_study # 
+# 
+# #turn sds to sec
+# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
+#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
+#                                                          model_1, condition)
+# 
+# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+# 
+# 
+# # Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels
+# 
+# # We will do in two ways
+# # First by excluding studies with a diagnostic classification of "sub"
+# 
+# clin_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+# 
+# clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+#   filter(new_study_id %in% clin_study_ids)
+# 
+# #turn sds to sec
+# clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(clin_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
+# results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# # Now lets include only studies with classification of "mdd"
+# 
+# mdd_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id
+# 
+# mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+#   filter(new_study_id %in% mdd_study_ids)
+# 
+# mdd_studies_baseline_metareg %>% 
+#   filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
+#   summarise(n = n())
+# 
+# #turn sds to sec
+# mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(mdd_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
+# results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# # Now CBT + all med studies
+# 
+# cbt_meds_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
+# 
+# cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+#   filter(new_study_id %in% cbt_meds_study_ids) %>% 
+#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+# 
+# #turn sds to sec
+# cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(cbt_meds_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
+# results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# # Look at the diagnostics of included studies 
+# 
+# filtered_data <- df_appl_v_orange %>%
+#   filter(psy_or_med == 1) %>% 
+#   filter(new_study_id %in% cbt_meds_study_ids) %>%
+#   distinct(new_study_id, .keep_all = TRUE)
+# 
+# summary_result <- filtered_data %>%
+#   group_by(diagnosis) %>%
+#   summarise(count = n())
+# 
+# # Now the CBT + med studies, filtering out the subclinical studies
+# 
+# clin_cbt_meds_study_ids <-
+#   df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id
+# 
+# clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
+#   filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
+#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+# 
+# #turn sds to sec
+# clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
+#                                         sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# # also change this for the function to work
+# clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
+# results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
+#                                                          model_1, condition)
+
+# ### get CDRS clin studies
+#  clin_cdrs_studies_baseline_metareg <- cdrs_studies_for_baseline_metareg %>% 
+#    filter(new_study_id %in% clin_study_ids)
+#  
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# 
+# results_clin_cdrs_metareg_baseline <- run_metareg_and_extract(clin_cdrs_studies_baseline_metareg,  
+#                                                          model_1, condition)
+# 
+# # Just realised this is identical, as all the studies that use the CDRS have clinical samples. 
+# 
+# ### get HAM-D clin studies
+#  clin_hamd_studies_for_baseline_metareg <- hamd_studies_for_baseline_metareg %>% 
+#    filter(new_study_id %in% clin_study_ids)
+# 
+# 
+# model_1 <- as.formula(~ four_level_var)
+# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+#                                                               #throughout
+# results_clin_hamd_studies_for_baseline_metareg <- run_metareg_and_extract(clin_hamd_studies_for_baseline_metareg, 
+#                                                          model_1, condition)
+# 
+# results_clin_hamd_studies_for_baseline_metareg$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+# 
+#
+```
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 }
+
+list_df_simulated_percentage[[1]]
+
+list_df_simulated[[1]]
 
@@
 
-### Analysis of all studies
-
-#### Number and type of of studies included
-
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
-
-<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X.
-CB - done.
-I removed psychodynamic because there weren't any active conditions of this type.
--->
-
-Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
-In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
-All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
-
-#### Metaregression analysis.
+#### Mean efficacy of psychotherapy versus medication control conditions
+
+#### Quality and nature of psychotherapy controls across trials
 
@@
 We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D on which there was a sufficient number of studies to metanalyse.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-### do ALL studies using percentage at baseline
-all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
-
-#turn sds to sec
-all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
-                                        sqrt(all_studies_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-# also change this for the function to work
-all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
-results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
-                                                         model_1, condition)
-
-### get CDRS studies
-cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-
-#turn sds to sec
-cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-
-results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
-                                                         model_1, condition)
-
-### get HAM-D studies
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-                                                          %in% hamd_study_ids,]
-
-hamd_studies_for_baseline_metareg <- list_hamd_study #
-
-#turn sds to sec
-hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
-                                                         model_1, condition)
-
-results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-# Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels
-
-# We will do in two ways
-# First by excluding studies with a diagnostic classification of "sub"
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-  filter(new_study_id %in% clin_study_ids)
-
-#turn sds to sec
-clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
-                                        sqrt(clin_studies_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-# also change this for the function to work
-clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
-results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
-                                                         model_1, condition)
-
-# Now lets include only studies with classification of "mdd"
-
-mdd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id
-
-mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-  filter(new_study_id %in% mdd_study_ids)
-
-mdd_studies_baseline_metareg %>% 
-  filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
-  summarise(n = n())
-
-#turn sds to sec
-mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
-                                        sqrt(mdd_studies_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-# also change this for the function to work
-mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
-results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
-                                                         model_1, condition)
-
-# Now CBT + all med studies
-
-cbt_meds_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
-
-cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-
-#turn sds to sec
-cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
-                                        sqrt(cbt_meds_studies_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-# also change this for the function to work
-cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
-results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
-                                                         model_1, condition)
-
-# Look at the diagnostics of included studies
-
-filtered_data <- df_appl_v_orange %>%
-  filter(psy_or_med == 1) %>% 
-  filter(new_study_id %in% cbt_meds_study_ids) %>%
-  distinct(new_study_id, .keep_all = TRUE)
-
-summary_result <- filtered_data %>%
-  group_by(diagnosis) %>%
-  summarise(count = n())
-
-# Now the CBT + med studies, filtering out the subclinical studies
-
-clin_cbt_meds_study_ids <-
-  df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id
-
-clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-  filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-
-#turn sds to sec
-clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
-                                        sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-# also change this for the function to work
-clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
-results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
-                                                         model_1, condition)
-
-# Looking at demographics at baseline
-# Currently we have both control and active conditions, we just need each study once
-
-df_baseline_demographics <- df_long_for_metan %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-# Now start looking at perc_women variable
-
-df_for_gender_metan <- df_baseline_demographics %>% 
-  filter(!is.na(percent_women))
-
-met_perc_women <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_gender_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-met_perc_women
-
-# looking at clinical sample only
-
-df_for_gender_metan_clin <- df_for_gender_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_perc_women_clin <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_gender_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across clinical studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-met_perc_women_clin
-
-# Now looking at the CBT + med studies only
-
-cbt_meds_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
-
-df_for_gender_metan_cbt <- df_for_gender_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-
-met_perc_women_cbt <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_gender_metan_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across cbt and med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-met_perc_women_cbt
-
-# Now start looking at age variable
-
-df_for_age_metan <- df_baseline_demographics %>% 
-  filter(!is.na(mean_age))
-
-met_age <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-met_age
-
-# looking at clinical sample only
-
-df_for_age_metan_clin <- df_for_age_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_age_clin <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across clinical studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-met_age_clin
-
-# Now cbt studies only
-
-df_for_age_metan_cbt <- df_for_age_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-
-met_age_cbt <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across cbt + med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-met_age_cbt
-
-# Now look at baseline severity for overall psy vs med
-# Need to calculate the variables first
-
-df_for_baseline_severity <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-met_sev <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-met_sev
-
-# clinical sample
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_baseline_severity_clin <- df_for_baseline_severity %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_sev_clin <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity clinical",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-met_sev_clin
-
-# cbt + med
-
-df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-
-met_sev_cbt <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cbt + med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-met_sev_cbt
-
-# ### get CDRS clin studies
-#  clin_cdrs_studies_baseline_metareg <- cdrs_studies_for_baseline_metareg %>% 
-#    filter(new_study_id %in% clin_study_ids)
-#  
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# 
-# results_clin_cdrs_metareg_baseline <- run_metareg_and_extract(clin_cdrs_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# # Just realised this is identical, as all the studies that use the CDRS have clinical samples. 
-# 
-# ### get HAM-D clin studies
-#  clin_hamd_studies_for_baseline_metareg <- hamd_studies_for_baseline_metareg %>% 
-#    filter(new_study_id %in% clin_study_ids)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# results_clin_hamd_studies_for_baseline_metareg <- run_metareg_and_extract(clin_hamd_studies_for_baseline_metareg, 
-#                                                          model_1, condition)
-# 
-# results_clin_hamd_studies_for_baseline_metareg$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-# 
-#
 

### 2024-03-06 apples_and_oranges.qmd
Cleaning control dataset, few other changes to code

@@
 
-# # We also need to calculate SE for proportion women for the baseline calculations
-# # for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
+# We also need to calculate SE for proportion women for the baseline calculations
+# for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
 
@@
 The data for the studies included in this metanalysis are summarised in Supplementary Table 1 and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-<!--# Charlotte, this should essentially be our df_long dataset, right?
-Perhaps, for the puproses of the table we can get rid of some of the columns.
-It would be good to have it in the way Pim had it.
-CB - I'm not sure I entirely understand.
-df_long_for_metan is already quite succinct (6 columns).
-I wonder if you are thinking of df_appl_v_orange which is more complete and includes means and sds etc.
-I'd say that's probably more appropriate to make available.
-I agree we should simplify it down a bit.
-Happy to do that once you confirm I'm on the right track here.
-If we decide to format it to be consistent with Cuijpers' data, we would have one row per comparison, rather than the long format we have in df_long_for_metan.
--->
 
@@
 
-Gender composition was similar across psychotherapy and medication trials,
+Gender composition did not differ significantly between psychotherapy and medication trials (stats).
 
@@
 #### Mean efficacy of psychotherapy versus medication control conditions
-
-#### Quality and nature of psychotherapy controls across trials
 
@@
 ![](plot_means_wl.pdf)
+
+### Comparing the nature and intensity of control conditions in psychotherapy trials
+
+Text.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# We need to read in the appropriate dataset which describes the active and control conditions used in
+# psychotherapy trials.
+
+df_descr_psy_conditions <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
+
+# checking id matchup
+# discrepancies <- setdiff(df_descr_psy_conditions$new_study_id, df_long_for_metan$new_study_id)
+
+# Cleaning the dataset
+# For now lets look at variables pertaining to the nature / intensity of interventions
+
+colnames(df_descr_psy_conditions)
+
+df_descr_psy_conditions <- df_descr_psy_conditions %>% 
+  select(c(new_study_id, `Psychotherapy/control`, levels_var, number_of_sites, Number_of_sessions,
+           frequency_weeks, Length_of_sessions_mins, Total_hours_of_intervention_hours, total_hours_gsh,
+           Total_period_of_intervention_weeks, Format_group_individual, Delivery, Involvement_of_others))
+
+# rename for clarity and to match master dataframe
+df_descr_psy_conditions <- df_descr_psy_conditions %>% 
+  rename(treatment = 'Psychotherapy/control', no_sites = number_of_sites, no_sessions =
+           Number_of_sessions, freq_weeks = frequency_weeks, length_sessions_mins =
+           Length_of_sessions_mins, total_hours = Total_hours_of_intervention_hours,
+         total_period_weeks = Total_period_of_intervention_weeks, format = Format_group_individual, delivery =
+           Delivery, family_involv = Involvement_of_others)
+
+check <- df_descr_psy_conditions %>% 
+  filter(treatment == 'wlc')
+
+# Visual inspection
+
+# There are two studies where the waitlist condition has some intervention (i.e. values should not be set to 0)
+# Otherwise, I want values to be set to 0, not NA.
+
+df_descr_psy_conditions <- df_descr_psy_conditions %>%
+  mutate(
+    no_sessions = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, no_sessions),
+    freq_weeks = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, freq_weeks),
+    length_sessions_mins = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, length_sessions_mins),
+    total_hours = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, total_hours)
+  )
+
+# Now cau
+
+check <- df_descr_psy_conditions %>% 
+  filter(treatment == 'cau')
+
+# All studies except for Martinovic, Srivastava, Stikkelbroek and Weisz 2009 should have variables set to NA. 
+# This is because we cannot say that they did not feature 0 hours of intervention, but that for the most part
+# it is not reported or it is not possible to quantify.
+
+df_descr_psy_conditions <- df_descr_psy_conditions %>%
+  mutate(
+    no_sessions = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, no_sessions),
+    freq_weeks = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, freq_weeks),
+    length_sessions_mins = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, length_sessions_mins),
+    total_hours = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, total_hours)
+  )
+
+# Now other controls
+
+check <- df_descr_psy_conditions %>%
+  filter(!(treatment %in% c('cau', 'wlc'))) %>% 
+  filter(levels_var == "psychotherapy_control")
+
+# Made a few manual adjustments in the original excel sheet.
+
+# List of columns to clean
+columns_to_clean <- c(
+  "no_sessions",
+  "freq_weeks",
+  "length_sessions_mins",
+  "total_hours",
+  "total_period_weeks"
+)
+
+# Convert non-numeric values to NA in specified columns
+df_descr_psy_conditions <- df_descr_psy_conditions %>%
+  mutate_at(vars(columns_to_clean), ~as.numeric(as.character(.)))
+
+# Define the function for summary stats
+
+group_function <- function(dataframe, my_groups, columns) {
+  result_dataframe <- data.frame(
+    Group = character(),
+    Column = character(),
+    N = numeric(),
+    Mean = numeric(),
+    Std_Dev = numeric(),
+    Median = numeric(),
+    IQR = numeric(),
+    stringsAsFactors = FALSE
+  )
+  unique_groups <- unique(dataframe[[my_groups]])
+  for (group in unique_groups) {
+    group_data <- dataframe[dataframe[[my_groups]] == group, ]
+    for (col in columns) {
+      col_data <- group_data[[col]]
+      n <- sum(!is.na(col_data))
+      mean_val <- mean(col_data, na.rm = TRUE)
+      std_dev <- sd(col_data, na.rm = TRUE)
+      median_val <- median(col_data, na.rm = TRUE)
+      iqr <- IQR(col_data, na.rm = TRUE)
+      result_dataframe <- rbind(result_dataframe,
+                                data.frame(Group = group,
+                                           Column = col, N = n, Mean = mean_val,
+                                           Std_Dev = std_dev, Median = median_val,
+                                           IQR = iqr, stringsAsFactors = FALSE))
+    }
+  }
+  return(result_dataframe)
+}
+
+sessions <- group_function(df_descr_psy_conditions,"levels_var","no_sessions")
+frequency <- group_function(df_descr_psy_conditions,"levels_var","freq_weeks")
+length_sessions_mins <- group_function(df_descr_psy_conditions,"levels_var","length_sessions_mins")
+total_hours <- group_function(df_descr_psy_conditions,"levels_var","total_hours")
+total_period_weeks <- group_function(df_descr_psy_conditions,"levels_var","total_period_weeks")
+
+control_summary <- rbind(sessions, frequency, length_sessions_mins, total_hours, total_period_weeks)
+
+```
 

### 2024-03-07 apples_and_oranges.qmd
Some organising Describing control vs actives for psy studies

@@
 
-### Sample characteristics
-
-We will test in a metaregression for differences between psychotherapy versus medication trials in sample characteristics at baseline.
+### Trial and sample characteristics
+
+We conducted a meta-analysis to test for differences between psychotherapy versus medication trials in sample characteristics at baseline.
 
@@
 
-We also conducted metaregressions to compare psychotherapy vs medication trials on the gender composition of the sample, mean age, and number of trial sites.
+We also performed meta-analyses implemented in R's meta package to compare psychotherapy versus medication trials on the gender composition of the sample, mean age, and number of trial sites.
 
@@
 
-As the measure of effect of each individual study, we used the within-group standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
 
@@
 where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-NOTE **Charlotte**, please add note here with what we did to impute SDs where missing, e.g.
-using the pre to impute the post etc.
-In general state here the rules we used citing the Cochrane book.
-**CB** Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised by X (citation), in the following order.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised by X (citation), in the following order.
 If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
@@
 We then used these simulated datasets in the subsequent metanalyses.
+
+### Random Effects Metaregression
+
+We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
+The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+Therefore, we can estimate a two stage model with:
+
+$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
+$$ {#eq-7}
+
+$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
+$$ {#eq-8}
+
+where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
+Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
+
+This then gives rise to:
+
+$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-9}
+
+where,
+
+$$u_i \sim N(0, \tau^2) $$ {#eq-10}
+
+describes the deviation of each study from the mean of the distribution, and,
+
+$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-11}
+
+describes the sampling error.
+
+We can then specify the following model to obtain the means of each arm of the trials as follows:
+
+$$ \begin{aligned}
+    Υ_i &=
+    \begin{cases}
+        0 & MedControl:  b_0 + u_i + \epsilon_i\\
+        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
+        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
+        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
+    \end{cases}
+\end{aligned}$$ {#eq-12}
+
+where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
+for level 3, $b_{3_{i}}$ the psychotherapy controls.
+The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
+Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
+Inference on the contrasts is done as follows:
+
+$$
+z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
+$$ {#eq-13}
+
+We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
+
+We present our main results as means of the estimates across simulated datasets, for example, the SMDs of each level of the dummy variable above are means across the simulations.
+
+### Sensitivity Analyses
+
+We conducted a number of additional analyses to test for the robustness of our results.
+
+First, for each of the the meta-analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways.
+First, we excluded studies which recruited participants with subclinical levels of depression.
+Second, we restricted the analyses to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram.
+Third, we restricted the metaregression to studies that *did not* use waitlist as their control.
+
+Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
+To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
+We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+# my alpha for the z 
+target_probability <- 1 - 0.05
+
+#start here 
+x <- 1
+
+# two decimals should be fine
+tolerance <- 1e-3
+
+#find the z value using the pnorm function
+while (abs(pnorm(x)) < target_probability ) {
+  x <- x + tolerance  
+}
+
+# Adjust the step size based on your problem  
+cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
+
+```
+
+### Comparing the control versus active arms of psychotherapy trials
+
+We ran a random effects meta-analysis in R's Meta package to compare the active versus control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
+We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and period of the intervention.
+Where a range was provided, the maximum was encoded (e.g.
+if a paper reported that an intervention involved 8-10 sessions lasting 50-60 minutes, we encoded the number and duration of sessions as 10 and 60, respectively).
+If sessions varied in frequency across an intervention, we calculated an average by dividing total number of sessions by length of intervention period.
+Similarly, if the length of sessions varied across the course of the intervention, we calculated a weighted average.
+Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
 
@@
 
-### Random Effects Metaregression
-
-We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
-The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
-Therefore, we can estimate a two stage model with:
-
-$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$ {#eq-7}
-
-$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
-$$ {#eq-8}
-
-where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
-Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
-
-This then gives rise to:
-
-$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-9}
-
-where,
-
-$$u_i \sim N(0, \tau^2) $$ {#eq-10}
-
-describes the deviation of each study from the mean of the distribution, and,
-
-$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-11}
-
-describes the sampling error.
-
-We can then specify the following model to obtain the means of each arm of the trials as follows:
-
-$$ \begin{aligned}
-    Υ_i &=
-    \begin{cases}
-        0 & MedControl:  b_0 + u_i + \epsilon_i\\
-        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
-        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
-        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
-    \end{cases}
-\end{aligned}$$ {#eq-12}
-
-where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
-for level 3, $b_{3_{i}}$ the psychotherapy controls.
-The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
-Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on the contrasts is done as follows:
-
-$$
-z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
-$$ {#eq-13}
-
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
-
-We present our main results as means of the estimates across simulated datasets, for example, the SMDs of each level of the dummy variable above are means across the simulations.
-
-### Sensitivity Analyses
-
-We conducted a number of additional analyses to test for the robustness of our results.
-
-First, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
-To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
-# my alpha for the z 
-target_probability <- 1 - 0.05
-
-#start here 
-x <- 1
-
-# two decimals should be fine
-tolerance <- 1e-3
-
-#find the z value using the pnorm function
-while (abs(pnorm(x)) < target_probability ) {
-  x <- x + tolerance  
-}
-
-# Adjust the step size based on your problem  
-cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
-
-```
-
-Second, we restricted the metaregression to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram.
-
-Third, we restricted the metaregression to studies that *did not* use waitlist as their control.
-
 # Results
@@
 
-Using a random effects meta-regression we compared psychotherapy versus medication trials on four domains: gender composition, age, baseline depression severity levels, and number of trial sites.
-We first examined each of these across all studies, and then conducted two sensitivity analyses where we excluded psychotherapy studies which 1) recruited participants with sub clinical depression levels and 2) did not use CBT as the active intervention.
-
 ### Gender
 
-Gender composition did not differ significantly between psychotherapy and medication trials (stats).
+Psychotherapy trials featured a higher percentage of women when compared to medication trials.
+This subgroup difference in gender composition reached statistical significance (stats).
+Excluding sub-clinical studies yielded very similar results (stats).
+This difference in gender composition however did not reach statistical significance when only CBT and medication trials were included (stats).
 
@@
 
-# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs
+# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.
 
@@
 
-met_perc_women <- metagen(TE.random = percent_women,
-                           seTE.random = percent_women_std_error,
+met_perc_women <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
                            studlab = new_study_id,
@@
 
-summary_results <- summary(met_perc_women, byvar = "subgroup")
-
 # Convert the results to a dataframe
 result_df <- data.frame(
-  TE = summary_met_perc_women$TE.random,
-  seTE = summary_met_perc_women$seTE.random,
-  lower = summary_met_perc_women$lower.random,
-  upper = summary_met_perc_women$upper.random
+   subgroup = met_perc_women$subgroup.name,
+   TE = met_perc_women$TE.random,
+  seTE = met_perc_women$seTE.random,
+  lower = met_perc_women$lower.random,
+  upper = met_perc_women$upper.random
 )
+
+knitr:: kable(result_df, "latex", caption = "Gender composition")
 
@@
                            tau.common = FALSE)
-met_perc_women_clin
 
@@
 
+#  grab ids for those studies
 cbt_meds_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+# Use those ids to subset all dataframes in the list
+# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
+# So we need to further subset. For the active arms, I am filtering out conditions that do not meet our criteria. 
+# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
+# We may have multiple controls per study id for this reason, though this isn't a problem conceptually.
 
@@
   filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
+  filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
 
@@
                            tau.common = FALSE)
-met_perc_women_cbt
-
-knitr:: kable(summary_table, "latex", caption = "Gender composition")
-
+```
+
+### Age
+
+Description of results X.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Now start looking at age variable
+
+# We have several studies for which we are missing SE for age. I am going to perform an imputation by taking an average
+# for the studies we do have, per modality, and substituting this in for missing values.
+
+df_baseline_demographics$se_age <- as.numeric(df_baseline_demographics$se_age)
+
+mean_se_age_psy <- df_baseline_demographics %>%
+  filter(psy_or_med == 1) %>%
+  summarise(mean_se_age_psy = mean(se_age, na.rm = TRUE))
+
+mean_se_age_med <- df_baseline_demographics %>%
+  filter(psy_or_med == 0) %>%
+  summarise(mean_se_age_med = mean(se_age, na.rm = TRUE))
+
+df_baseline_demographics <- df_baseline_demographics %>% 
+  mutate(se_age = ifelse(!is.na(se_age), se_age,
+                         ifelse(psy_or_med == 1, mean_se_age_psy, mean_se_age_med)))
 
@@
   filter(!is.na(mean_age))
+
+# Age meta analysis
 
@@
 
-met_age
-
-# looking at clinical sample only
+# Looking at clinical sample only
 
@@
 
-met_age_clin
-
-# Now cbt studies only
+# Now cbt + med studies only
 
@@
                            tau.common = FALSE)
-
-met_age_cbt
-
+```
+### Baseline severity
+
+Describe results here
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Now look at baseline severity for overall psy vs med
@@
 
-met_sev
-
 # clinical sample
@@
                            tau.common = FALSE)
-met_sev_clin
 
@@
                            tau.common = FALSE)
-met_sev_cbt
 
@@
 #                                                          model_1, condition)
-
-# ### get CDRS clin studies
-#  clin_cdrs_studies_baseline_metareg <- cdrs_studies_for_baseline_metareg %>% 
-#    filter(new_study_id %in% clin_study_ids)
-#  
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# 
-# results_clin_cdrs_metareg_baseline <- run_metareg_and_extract(clin_cdrs_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# # Just realised this is identical, as all the studies that use the CDRS have clinical samples. 
-# 
-# ### get HAM-D clin studies
-#  clin_hamd_studies_for_baseline_metareg <- hamd_studies_for_baseline_metareg %>% 
-#    filter(new_study_id %in% clin_study_ids)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# results_clin_hamd_studies_for_baseline_metareg <- run_metareg_and_extract(clin_hamd_studies_for_baseline_metareg, 
-#                                                          model_1, condition)
-# 
-# results_clin_hamd_studies_for_baseline_metareg$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-# 
-#
 ```
@@
 
+knitr:: kable(control_summary, caption="Characteristics of the active and control arms of psychotherapy trials")
+
 ```
@@
 knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
-```
-
-We next addressed the e
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#### Let's start from the beginning and regress cohens on the baseline dataframe.
-
-# # create a new list with dfs for the sims
-# df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# # rename the cohens_d value to make space for the new cohen's d
-# df_long_for_metan_adj_cohens_d <-
-#   df_long_for_metan_adj_cohens_d %>% 
-# rename(unadjusted_cohens_d = cohens_d,
-# ) 
-# # estimate the cohen's d from the residuals
-# model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$baseline_mean, na.action=na.exclude)
-# 
-# # there is a great effect of the baseline means, as shown here
-# results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-# 
-# # extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-# df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-# 
-# # apply function to simulate standard errors
-# list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d, 
-#                                    num_repetitions = 1000, 
-#                                    seed  = 1974,
-#                                    n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)), 
-#                                    a = 0.45, 
-#                                    b = .9, 
-#                                    mean = 0.65, 
-#                                    sd = 0.2)
-# 
-# 
-# # add the four level variable and re-level
-# for(i in 1: length(list_df_simulated_adj_cohens_d)){
-#   
-#   list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-#   list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>% 
-#     mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-#                                       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-#     )
-#   
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-#   
-#   # relevel so that medication control becomes the reference category for the regression
-#   #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-#                                                          "medication_control",
-#                                                          "medication_active", 
-#                                                          "psychotherapy_control",
-#                                                          "psychotherapy_active")
-# }
-# 
-# 
-# 
-# 
-# 
-# # Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# # specify model
-# model_1 <- as.formula(~ four_level_var)
-# 
-# # run metareg function 
-# # here you can use the simulated results directly
-# list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-# aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-# aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-# 
-# # extract SMDs from the  list
-# list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-# 
-# df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
-# 
-# 
-# 
-#
-
 ```
@@
 
-We have also run models to take into accountregression to the mean within CDRS and HAMD.
-
-```{# {r, warning=FALSE, message = FALSE, echo=FALSE}
-# ####code to extract baseline-adjusted post means for CDRS and HAMD 
-# 
-#  
-# 
-# de_meaned_baselilne_mean_cdrs <- (list_cdrs_study[[1]]$baseline_mean - mean(list_cdrs_study[[1]]$baseline_mean, na.rm = TRUE)) 
-# 
-#                                     
-# 
-#  
-# 
-#                                  
-# 
-# lm_for_cdrs_smds <- lm(list_cdrs_study[[1]]$post_mean ~ de_meaned_baselilne_mean_cdrs +list_cdrs_study[[1]]$four_level_var,
-# 
-#  
-# 
-#   na.action=na.exclude,
-# 
-#    )
-# 
-#  
-# 
-#  
-# 
-# #summary(lm_for_cdrs_smds)
-# 
-#  
-# 
-# coefs_lm_for_cdrs_smds  <- broom:: tidy(lm_for_cdrs_smds)
-# 
-#  
-# 
-# condition <- coefs_lm_for_cdrs_smds$term
-# 
-# cdrs_smds <-c(coefs_lm_for_cdrs_smds$estimate[1], coefs_lm_for_cdrs_smds$estimate[-1] + coefs_lm_for_cdrs_smds$estimate[1])
-# 
-# cdrs_upper_ci <- cdrs_smds + coefs_lm_for_cdrs_smds$std.error*1.96
-# 
-# cdrs_lower_ci <- cdrs_smds - coefs_lm_for_cdrs_smds$std.error*1.96
-# 
-#  
-# 
-# cdrs_smd_with_cis <- data.frame (
-# 
-#   condition = levels(list_hamd_study$four_level_var),
-# 
-#   cdrs_smds = cdrs_smds[-2],
-# 
-#   cdrs_upper_ci = cdrs_upper_ci[-2],
-# 
-#   cdrs_lower_ci = cdrs_lower_ci[-2]
-# 
-# )
-# 
-#  
-# 
-#  
-# 
-# # do the same for hamd
-# 
-# de_meaned_baselilne_mean_hamd <- (list_hamd_study$baseline_mean - mean(list_hamd_study$baseline_mean, na.rm = TRUE)) 
-# 
-#  
-# 
-#  
-# 
-#  
-# 
-# lm_for_hamd_smds <- lm(list_hamd_study$post_mean ~ de_meaned_baselilne_mean_hamd +list_hamd_study$four_level_var,
-# 
-#                       
-# 
-#                        na.action=na.exclude,
-# 
-# )
-# 
-#  
-# 
-#  
-# 
-# #summary(lm_for_hamd_smds)
-# 
-#  
-# 
-# coefs_lm_for_hamd_smds  <- broom:: tidy(lm_for_hamd_smds)
-# 
-#  
-# 
-#  
-# 
-# condition <- coefs_lm_for_hamd_smds$term
-# 
-# hamd_smds <-c(coefs_lm_for_hamd_smds$estimate[1], coefs_lm_for_hamd_smds$estimate[-1] + coefs_lm_for_hamd_smds$estimate[1])
-# 
-# hamd_upper_ci <- hamd_smds + coefs_lm_for_hamd_smds$std.error*1.96
-# 
-# hamd_lower_ci <- hamd_smds - coefs_lm_for_hamd_smds$std.error*1.96
-# 
-#  
-# 
-# hamd_smd_with_cis <- data.frame (
-# 
-# condition = levels(list_hamd_study$four_level_var),
-# 
-# hamd_smds = hamd_smds[-2],
-# 
-# hamd_upper_ci = hamd_upper_ci[-2],
-# 
-# hamd_lower_ci = hamd_lower_ci[-2]
-# 
-# )
-# 
-#  
-# 
-#
-
 ```

### 2024-03-08 apples_and_oranges.qmd
Quite a few changes

@@
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall) %>%
+                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall, no_sites) %>%
   rename(treatment = descr_active) %>% 
@@
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall) %>%
+                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall, no_sites) %>%
   rename(treatment = descr_control) %>% 
@@
 
-# I'm going to perform  the operations to calculate overall age and percent women here now.
+# I'm going to perform  the operations to calculate overall age and percent women here now. We just want this per study rather than per arm
+# as we are going to compare psy vs med (2 subgroups) rather than the 4 arms
 
@@
 
+# Remember that these are now per study, not per arm.
+
 # Create SEs proportions for percentage women --------------------------------------------
@@
 Excluding sub-clinical studies yielded very similar results (stats).
-This difference in gender composition however did not reach statistical significance when only CBT and medication trials were included (stats).
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (stats).
 
@@
                            tau.common = FALSE)
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+### Number of sites
+## This data lives in this spreadsheet for psy trials, we need to merge it in
+
+df_no_sites <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
+
+df_no_sites <- df_no_sites %>% 
+  select(c(new_study_id, number_of_sites)) %>% 
+  filter(!is.na(number_of_sites)) %>% 
+  distinct(new_study_id, .keep_all = TRUE) %>% 
+  mutate(number_of_sites = as.numeric(number_of_sites))
+
+df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
+
+# we have different vectors for psy and med trials, lets coalesce
+
+df_baseline_demographics <- df_baseline_demographics %>%
+  mutate(no_sites = as.numeric(no_sites)) %>% 
+  mutate(sites = coalesce(no_sites, number_of_sites)) %>%
+  select(-no_sites, -number_of_sites)
+
+# we have a few rogue studies (Kitchen, McCarty and Wright). Kitchen was too recent (after 2021), McCarty and Wright are not in Cuijpers' master
+# dataset for some reason, though they are in the list of included studies in the table in his MA. For now I'm going to remove them because 
+# we don't have data for these trials.
+
+df_baseline_demographics <- df_baseline_demographics %>% 
+  filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
+
+# Lets look at results
+
+df_sites_summary_stats <- df_baseline_demographics %>%
+  group_by(psy_or_med) %>%
+  summarise(
+    mean_sites = mean(sites, na.rm = TRUE),
+    sd_sites = sd(sites, na.rm = TRUE),
+    n = n()
+  )
+
+# plot
+
+ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
+  geom_point(position = position_jitter(width = 0.2), size = 2) +
+  labs(title = "Number of Sites for Psychotherapy and Medication Trials",
+       x = "Treatment Modality",
+       y = "Number of Sites") +
+  scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
 
@@
 
-Text.
+Write results here.
 
@@
 
-# Define the function for summary stats
+# Giannis' function for summary stats
 

### 2024-03-08 Script for cleaning medication data.R

@@ -16,7 +16,7 @@ Working_Dataset_Medication <- read_excel("Working_Dataset_Medication.xlsx",
                                                        "text", "text", "text", "text", 
                                                        "numeric", "numeric", "numeric", "numeric",
                                                        "numeric", "numeric", "numeric", "numeric",
-                                                       "text", "text"))
+                                                       "text", "text", "numeric"))
 Working_Dataset_Medication$year <- sub("\\.0$", "", Working_Dataset_Medication$year)
 
 #add vector indicating whether psychotherapy or medication, where 1 is psych and 0 is med

### 2024-03-08 Script for cleaning merged dataset.R

@@ -1623,9 +1623,6 @@ statistics_indiv_metan$treatment <- stringr::str_extract(statistics_indiv_metan$
 statistics_indiv_metan$arm <- stringr::str_remove(statistics_indiv_metan$condition, stringr::regex(pattern = "[a-z,-]+(?=\\s)", ignore_case = F)) 
 
 
-  
-
-
 
 # ATTEMPTS AT GRAPHING. ---------------------------------------------------
 

### 2024-03-08 apples_and_oranges.qmd
Trying to workout how to extract stats for subgroup analyses

@@
 
+# Define function for baseline metaanalyses  ----------------------------------------------
+
+# subgroup_df <- data.frame(psy_or_med = c(0, 1))
+# 
+# result <- list()
+# name_vec <- character()
+# 
+# # Loop over rows in the subgroup_df
+# for (i in 1:nrow(subgroup_df)) {
+#   
+#   # Call the metagen function for each row
+#   result[[i]] <- metagen(
+#     TE = percent_women,
+#     seTE = percent_women_std_error,
+#     studlab = new_study_id,
+#     data = df_for_gender_metan[df_for_gender_metan$psy_or_med == subgroup_df$psy_or_med[i], ],
+#     sm = "",
+#     fixed = FALSE,
+#     random = TRUE,
+#     method.tau = "REML",
+#     hakn = TRUE,
+#     title = paste("Subgroup:", subgroup_df$psy_or_med[i])
+#   )
+#   
+#   name_vec[i] = paste("Subgroup:", subgroup_df$psy_or_med[i])
+# }
+# 
+# # Now result contains the metagen results for each subgroup
+# # name_vec contains names for each subgroup
+# 
+# ## Function to extrac the key results for graphing and tabulating.
+# 
+# extract_stats <- function(result) {
+#  
+#   # get the summary table with results
+#   statistics <- summary(result)
+#   
+#   # Extract specific stats
+#   extracted_stats <- c(
+#     k_study = statistics$k.study,
+#     TE_random = statistics$TE.random,
+#     lower_random = statistics$lower.random,
+#     upper_random = statistics$upper.random,
+#     pval = statistics$pval.random,
+#     tau2 = statistics$tau2,
+#     lower_tau2 = statistics$lower.tau2,
+#     upper_tau2 = statistics$upper.tau2
+#   )
+#   
+#   return(extracted_stats)
+# }
+# 
+# extract_stats(result[[1]])
+# extract_stats(result[[2]])
+# 
+# # create a dataframe with the results
+# statistics_indiv_metan <- lapply(result, extract_stats) 
+# statistics_indiv_metan <- data.frame(do.call("rbind", statistics_indiv_metan))
+# statistics_indiv_metan$condition <- name_vec
+
 # Now start looking at perc_women variable
@@
 
-# Convert the results to a dataframe
+# met_perc_women_overall <- metagen(TE = percent_women,
+#                            seTE = percent_women_std_error,
+#                            studlab = new_study_id,
+#                            data = df_for_gender_metan,
+#                            sm = "",
+#                            fixed = FALSE,
+#                            random = TRUE,
+#                            method.tau = "REML",
+#                            hakn = TRUE,
+#                            title = "percentage women across studies")
+# 
+# subgroup_metan <-update.meta(met_perc_women_overall  , 
+#                               subgroup = df_for_gender_metan$psy_or_med, subgroup.name = "treatment modality",
+#                               tau.common = FALSE)
+
+# Use the summary function with the 'byvar' argument
+summary_met_perc_women <- summary(met_perc_women, byvar = "psy_or_med")
+
+# Extract specific statistics for each subgroup
+subgroup_names <- summary_met_perc_women$subgroup.name
+TE_random <- summary_met_perc_women$TE.random
+seTE_random <- summary_met_perc_women$seTE.random
+lower_random <- summary_met_perc_women$lower.random
+upper_random <- summary_met_perc_women$upper.random
+pval <- summary_met_perc_women$pval.random
+tau2 <- summary_met_perc_women$tau2
+lower_tau2 <- summary_met_perc_women$lower.tau2
+upper_tau2 <- summary_met_perc_women$upper.tau2
+
+# Create a data frame to store the results
 result_df <- data.frame(
-   subgroup = met_perc_women$subgroup.name,
-   TE = met_perc_women$TE.random,
-  seTE = met_perc_women$seTE.random,
-  lower = met_perc_women$lower.random,
-  upper = met_perc_women$upper.random
+  subgroup = subgroup_names,
+  TE_random = TE_random,
+  seTE_random = seTE_random,
+  lower_random = lower_random,
+  upper_random = upper_random,
+  pval = pval,
+  tau2 = tau2,
+  lower_tau2 = lower_tau2,
+  upper_tau2 = upper_tau2
 )
@@
 
-Description of results X.
+Description of results X + table.
 
@@
 ### Number of sites
+Write results, tabulate.
+
 ## This data lives in this spreadsheet for psy trials, we need to merge it in
@@
 #
-# # Now we want to do look at baseline severity when we exclude psy studies with sub clinical depression levels
-# 
-# # We will do in two ways
-# # First by excluding studies with a diagnostic classification of "sub"
-# 
-# clin_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-# 
-# clin_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-#   filter(new_study_id %in% clin_study_ids)
-# 
-# #turn sds to sec
-# clin_studies_baseline_metareg$baseline_stand_error <- clin_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(clin_studies_baseline_metareg$baseline_n)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# clin_studies_baseline_metareg$baseline_mean <- clin_studies_baseline_metareg$perc_baseline_mean
-# results_clin_studies_baseline_metareg <- run_metareg_and_extract(clin_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# # Now lets include only studies with classification of "mdd"
-# 
-# mdd_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$diagnosis == "mdd",]$new_study_id
-# 
-# mdd_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-#   filter(new_study_id %in% mdd_study_ids)
-# 
-# mdd_studies_baseline_metareg %>% 
-#   filter(four_level_var %in% c("psychotherapy_active","psychotherapy_control")) %>%
-#   summarise(n = n())
-# 
-# #turn sds to sec
-# mdd_studies_baseline_metareg$baseline_stand_error <- mdd_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(mdd_studies_baseline_metareg$baseline_n)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# mdd_studies_baseline_metareg$baseline_mean <- mdd_studies_baseline_metareg$perc_baseline_mean
-# results_mdd_studies_baseline_metareg <- run_metareg_and_extract(mdd_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# # Now CBT + all med studies
-# 
-# cbt_meds_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0, ]$new_study_id
-# 
-# cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) %>% 
-#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-# 
-# #turn sds to sec
-# cbt_meds_studies_baseline_metareg$baseline_stand_error <- cbt_meds_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(cbt_meds_studies_baseline_metareg$baseline_n)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# cbt_meds_studies_baseline_metareg$baseline_mean <- cbt_meds_studies_baseline_metareg$perc_baseline_mean
-# results_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(cbt_meds_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
+
 # # Look at the diagnostics of included studies 
@@
 #
-# # Now the CBT + med studies, filtering out the subclinical studies
-# 
-# clin_cbt_meds_study_ids <-
-#   df_appl_v_orange[(df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$psy_or_med == 0) & df_appl_v_orange$diagnosis != "sub", ]$new_study_id
-# 
-# clin_cbt_meds_studies_baseline_metareg <- all_studies_baseline_metareg %>%
-#   filter(new_study_id %in% clin_cbt_meds_study_ids) %>% 
-#   filter(!(arm_effect_size == "cohens_d_active" & psy_or_med == 1 & !(type == "cbt")))
-# 
-# #turn sds to sec
-# clin_cbt_meds_studies_baseline_metareg$baseline_stand_error <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(clin_cbt_meds_studies_baseline_metareg$baseline_n)
-# 
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# clin_cbt_meds_studies_baseline_metareg$baseline_mean <- clin_cbt_meds_studies_baseline_metareg$perc_baseline_mean
-# results_clin_cbt_meds_studies_baseline_metareg <- run_metareg_and_extract(clin_cbt_meds_studies_baseline_metareg,  
-#                                                          model_1, condition)
+
 ```
@@
 # C) the no WL sample
-# D) the no WL or CAU sample
-# E) the CDRS only sample
-# F) percentage variables
+# E) the CDRS only sample (**Argyris** do we still want this?)
+# F) Clinical Levels Depression
 
@@
 
-# D. Estimate Means and CIs without WL and CAU --------------------------------------- 
- # grab the ids for no waitlist and cau
-no_wl_cau_ids <- df_appl_v_orange %>%
-  filter(!(control_type %in% c("wl", "cau"))) %>%
-  pull(new_study_id)
-
-# use them to loop over the simulated list to subset all the dataframes.
-
-list_no_wl_cau <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% no_wl_cau_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
-})
-
-# count studies 
-no_wl_cau_studies <- df_long_for_metan %>% 
-  filter(new_study_id %in% no_wl_cau_ids) %>%
-  filter(!(arm_effect_size == "cohens_d_control" & type %in% c("wl", "cau")))
-study_count_no_wl_cau_study <- count_studies(no_wl_cau_studies)
-# CB checked, looks good!
-
-# use this model as above
-model_1 <- as.formula(~ four_level_var)
-
-# apply the metareg function to the list of no wl or cau
-list_model_1_no_wl_cau <- run_metaregression(list_no_wl_cau , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_no_wl_cau <- aggregate_model_results(list_model_1_no_wl_cau, condition)
-aggregate_results_no_wl_cau <- cbind(aggregate_results_no_wl_cau, condition)
-
-# now use the function to extract the coefficients
-means_no_wl_cau <-  lapply(list_model_1_no_wl_cau, extract_coefficients_func)
-
-# run the mean function for no wl
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the condition argument
-coef_and_se_means_no_wl_cau <- calculate_mean_coefs_ses(means_no_wl_cau, condition)
-coef_and_se_means_no_wl_cau <- data.frame(cbind(condition,coef_and_se_means_no_wl_cau))
-
-coef_and_se_means_no_wl_cau$n <- study_count_no_wl_cau_study[study_count_no_wl_cau_study$is_missing 
-                                                     ==FALSE,]$n
-
-# here are all three of them OVERALL, CBT and WL together. We may want to display them together. 
-# df_all_coefficients <- cbind(df_mean_coefs_from_sim, coef_and_se_means_cbt_fluox_esc_study,coef_and_se_means_no_wl)
-
 # E. CDRS Sensitivity Analysis ---------------------------------------
@@
 
-# test <- df_appl_v_orange %>%
-#   filter(psy_or_med == 1) %>%
-#   distinct(new_study_id, .keep_all = TRUE)
-# 
-# summary_test <- test %>%
-#   group_by(diagnosis) %>%
-#   summarise(count = n())
-
 #take study ids where sample has clinical levels of depression
@@
 coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n
-
-# G. Estimate Means and CIs for the overall sample using baseline percentage variable ----------------------------------
-
-# the first thing to do is to create a new dataset with the percentage cohen's d
-
-list_df_simulated_percentage <- list_df_simulated
-
-for(i in 1: length(list_df_simulated_percentage)){
-
-  list_df_simulated_percentage[[i]]$cohens_d <- 
-            (list_df_simulated_percentage[[i]]$perc_post_mean - list_df_simulated_percentage[[i]]$perc_baseline_mean)/
-    ((list_df_simulated_percentage[[i]]$perc_post_sd + list_df_simulated_percentage[[i]]$perc_baseline_sd)/2)
-
-}
-
-list_df_simulated_percentage[[1]]
-
-list_df_simulated[[1]]
-
-# specify model
-model_1 <- as.formula(~ four_level_var )
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_1_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_perc <-  aggregate_model_results(list_model_1_meta_reg_perc, condition)
-aggregate_results_perc <- cbind(aggregate_results_perc, condition)
-
-# extract SMDs from the  list
-means_perc <-  lapply(list_model_1_meta_reg_perc, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_perc <- calculate_mean_coefs_ses(means_perc, condition)
-df_mean_coefs_perc <- data.frame(cbind(condition,df_mean_coefs_perc))
-
-# add the ns
-df_mean_coefs_perc <- data.frame(cbind(df_mean_coefs_perc, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
-
-##### now for the baseline controlled variable
-# specify model
-model_2 <- as.formula(~ four_level_var + perc_baseline_mean )
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_2_meta_reg_perc <- run_metaregression(list_df_simulated_percentage, model_2)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_perc_mod_2 <-  aggregate_model_results(list_model_2_meta_reg_perc, condition)
-aggregate_results_perc_mod_2 <- cbind(aggregate_results_perc_mod_2, condition)
-
-# extract SMDs from the  list
-means_perc_mod_2 <-  lapply(list_model_2_meta_reg_perc, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_perc_mod_2 <- calculate_mean_coefs_ses(means_perc_mod_2, condition)
-df_mean_coefs_perc_mod_2 <- data.frame(cbind(condition,df_mean_coefs_perc_mod_2))
-
-# add the ns
-df_mean_coefs_perc_mod_2 <- data.frame(cbind(df_mean_coefs_perc_mod_2, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
-
-# Plots  -----------------------
-# 
-# #define groups
-# df_long_for_metan <- df_long_for_metan %>%
-#   mutate(
-#     group = case_when(
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-#       TRUE ~ NA_character_  
-#     )
-#   )
-
-# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-# 
-# # Plot cohens d per arm
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-# 
-# # Now look at change scores of percentage transformed variables
-# 
-# df_long_for_metan <- df_long_for_metan %>% 
-#   mutate(perc_change = perc_post_mean - perc_baseline_mean)
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-# 
-# # # Plot percentage  baseline means 
-# # 
-# # ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
-# #   geom_point(position = position_jitter(width = 0.2), size = 3) +
-# #   scale_color_manual(values = group_colors) +
-# #   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
-# #   theme_minimal() +
-# #   theme(legend.position = "none")
-# 
-# # Box plots
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_fill_manual(values = group_colors) +
-#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
 
@@
 ```
+
+```{r}
+# Plots  -----------------------
+# 
+# #define groups
+# df_long_for_metan <- df_long_for_metan %>%
+#   mutate(
+#     group = case_when(
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
+#       TRUE ~ NA_character_  
+#     )
+#   )
+
+# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
+# 
+# # Plot cohens d per arm
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
+# 
+# # Now look at change scores of percentage transformed variables
+# 
+# df_long_for_metan <- df_long_for_metan %>% 
+#   mutate(perc_change = perc_post_mean - perc_baseline_mean)
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
+# 
+# # # Plot percentage  baseline means 
+# # 
+# # ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+# #   geom_point(position = position_jitter(width = 0.2), size = 3) +
+# #   scale_color_manual(values = group_colors) +
+# #   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+# #   theme_minimal() +
+# #   theme(legend.position = "none")
+# 
+# # Box plots
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
+#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
+#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
+#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+#   scale_fill_manual(values = group_colors) +
+#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
+
+```

### 2024-03-08 Script for cleaning merged dataset.R

@@ -1529,7 +1529,7 @@ list_df_simulated[[i]]$weights <-  weights(list_mod_3_meta_reg[[i]])  # this is 
 
 }
 
-
+library(tidyverse)
 
 # Run individual metanalyses ----------------------------------------------
 

### 2024-03-11 apples_and_oranges.qmd
Extracting coefficients for meta-analyses

@@
 
-We ran a random effects meta-analysis in R's Meta package to compare the active versus control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
+We ran t-tests to compare the active versus control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
 We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and period of the intervention.
@@
 
-Psychotherapy trials featured a higher percentage of women when compared to medication trials.
-This subgroup difference in gender composition reached statistical significance (stats).
-Excluding sub-clinical studies yielded very similar results (stats).
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (stats).
+Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`).
+On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% women across medication trials.
+Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`).
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).
 
@@
 
-# Define function for baseline metaanalyses  ----------------------------------------------
-
-# subgroup_df <- data.frame(psy_or_med = c(0, 1))
-# 
-# result <- list()
-# name_vec <- character()
-# 
-# # Loop over rows in the subgroup_df
-# for (i in 1:nrow(subgroup_df)) {
-#   
-#   # Call the metagen function for each row
-#   result[[i]] <- metagen(
-#     TE = percent_women,
-#     seTE = percent_women_std_error,
-#     studlab = new_study_id,
-#     data = df_for_gender_metan[df_for_gender_metan$psy_or_med == subgroup_df$psy_or_med[i], ],
-#     sm = "",
-#     fixed = FALSE,
-#     random = TRUE,
-#     method.tau = "REML",
-#     hakn = TRUE,
-#     title = paste("Subgroup:", subgroup_df$psy_or_med[i])
-#   )
-#   
-#   name_vec[i] = paste("Subgroup:", subgroup_df$psy_or_med[i])
-# }
-# 
-# # Now result contains the metagen results for each subgroup
-# # name_vec contains names for each subgroup
-# 
-# ## Function to extrac the key results for graphing and tabulating.
-# 
-# extract_stats <- function(result) {
-#  
-#   # get the summary table with results
-#   statistics <- summary(result)
-#   
-#   # Extract specific stats
-#   extracted_stats <- c(
-#     k_study = statistics$k.study,
-#     TE_random = statistics$TE.random,
-#     lower_random = statistics$lower.random,
-#     upper_random = statistics$upper.random,
-#     pval = statistics$pval.random,
-#     tau2 = statistics$tau2,
-#     lower_tau2 = statistics$lower.tau2,
-#     upper_tau2 = statistics$upper.tau2
-#   )
-#   
-#   return(extracted_stats)
-# }
-# 
-# extract_stats(result[[1]])
-# extract_stats(result[[2]])
-# 
-# # create a dataframe with the results
-# statistics_indiv_metan <- lapply(result, extract_stats) 
-# statistics_indiv_metan <- data.frame(do.call("rbind", statistics_indiv_metan))
-# statistics_indiv_metan$condition <- name_vec
+# This is the function to extract statistics
+
+extract_stats <- function(df) {
+
+  # get the summary table with results
+  statistics <- summary(df, byvar = "psy_or_med")
+
+  df_stats <- data.frame(
+  subgroup = statistics$subgroup.levels,
+  k_study = statistics$k.study.w,
+  TE_random = statistics$TE.random.w,
+  seTE_random = statistics$seTE.random.w,
+  lower_random = statistics$lower.random.w,
+  upper_random = statistics$upper.random.w,
+  tau2 = statistics$tau2.w)
+
+  # Add an empty row at the top and column on right (this is for the test for subgroup differences p value)
+  df_stats <- rbind(data_frame(subgroup = NA, k_study = NA, TE_random = NA, seTE_random = NA, 
+                             lower_random = NA, upper_random = NA, tau2 = NA), df_stats)
+  df_stats <- cbind(df_stats, pval_between = NA)
+
+  # Set the value in the last row and last column as the between groups p val
+  df_stats[1, "pval_between"] <- statistics$pval.Q.b.random
+
+  return(df_stats)
+
+}
 
@@
 
-met_perc_women <- metagen(TE = percent_women,
+met_perc_women_overall <- metagen(TE = percent_women,
                            seTE = percent_women_std_error,
@@
                            hakn = TRUE,
-                           title = "percentage women across studies",
-                           subgroup = psy_or_med,
+                           title = "percentage women across studies")
+
+met_perc_women_overall <- update(met_perc_women_overall,
+                              subgroup = df_for_gender_metan$psy_or_med, subgroup.name = "treatment modality",
                               tau.common = FALSE)
 
-# met_perc_women_overall <- metagen(TE = percent_women,
-#                            seTE = percent_women_std_error,
-#                            studlab = new_study_id,
-#                            data = df_for_gender_metan,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "percentage women across studies")
-# 
-# subgroup_metan <-update.meta(met_perc_women_overall  , 
-#                               subgroup = df_for_gender_metan$psy_or_med, subgroup.name = "treatment modality",
-#                               tau.common = FALSE)
-
-# Use the summary function with the 'byvar' argument
-summary_met_perc_women <- summary(met_perc_women, byvar = "psy_or_med")
-
-# Extract specific statistics for each subgroup
-subgroup_names <- summary_met_perc_women$subgroup.name
-TE_random <- summary_met_perc_women$TE.random
-seTE_random <- summary_met_perc_women$seTE.random
-lower_random <- summary_met_perc_women$lower.random
-upper_random <- summary_met_perc_women$upper.random
-pval <- summary_met_perc_women$pval.random
-tau2 <- summary_met_perc_women$tau2
-lower_tau2 <- summary_met_perc_women$lower.tau2
-upper_tau2 <- summary_met_perc_women$upper.tau2
-
-# Create a data frame to store the results
-result_df <- data.frame(
-  subgroup = subgroup_names,
-  TE_random = TE_random,
-  seTE_random = seTE_random,
-  lower_random = lower_random,
-  upper_random = upper_random,
-  pval = pval,
-  tau2 = tau2,
-  lower_tau2 = lower_tau2,
-  upper_tau2 = upper_tau2
-)
-
-knitr:: kable(result_df, "latex", caption = "Gender composition")
+# Apply the function to the meta-analysis result
+results_met_perc_women_overall <- extract_stats(met_perc_women_overall)
+
+knitr:: kable(results_met_perc_women_overall, caption = "Gender composition")
 
@@
                            hakn = TRUE,
-                           title = "percentage women across clinical studies",
-                           subgroup = psy_or_med,
+                           title = "percentage women across clinical studies")
+
+met_perc_women_clin <- update(met_perc_women_clin,
+                           subgroup = df_for_gender_metan_clin$psy_or_med, subgroup.name = "treatment modality",
                            tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+results_met_perc_women_clin <- extract_stats(met_perc_women_clin)
+
+knitr:: kable(results_met_perc_women_clin, caption = "Gender composition in clinical studies")
 
@@
 df_for_gender_metan_cbt <- df_for_gender_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+  filter(new_study_id %in% cbt_meds_study_ids)
 
@@
                            tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+results_met_perc_women_cbt <- extract_stats(met_perc_women_cbt)
+
+knitr:: kable(results_met_perc_women_cbt, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")
+
 ```
@@
 
-Description of results X + table.
+Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
+There were no significant differences in mean age between modalities on further sensitivity analyses.
 
@@
 
+results_met_age <- extract_stats(met_age)
+
+knitr:: kable(results_met_age, caption = "Average age in psychotherapy vs medication trials")
+
 # Looking at clinical sample only
@@
 
+results_met_age_clin <- extract_stats(met_age_clin)
+
+knitr:: kable(results_met_age_clin, caption = "Average age in clinical studies")
+
 # Now cbt + med studies only
@@
 df_for_age_metan_cbt <- df_for_age_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>% 
-  filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+  filter(new_study_id %in% cbt_meds_study_ids)
 
@@
                            tau.common = FALSE)
+
+results_met_age_cbt <- extract_stats(met_age_cbt)
+
+knitr:: kable(results_met_age_cbt, caption = "Average age in cbt, fluox, escit studies")
+
 ```
@@
 
-Describe results here
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was eiter CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
+When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference no longer reached statistical significance (p = `results_met_sev_clin$pval_between`).
 
@@
 
+results_met_sev <- extract_stats(met_sev)
+
+knitr:: kable(results_met_sev, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials")
+
 # clinical sample
@@
 
+results_met_sev_clin <- extract_stats(met_sev_clin)
+
+knitr:: kable(results_met_sev_clin, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials, excluding subclinical studies")
+
 # cbt + med
@@
   filter(new_study_id %in% cbt_meds_study_ids) %>%
-  filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
 
@@
                            tau.common = FALSE)
+
+results_met_sev_cbt <- extract_stats(met_sev_cbt)
+
+knitr:: kable(results_met_sev_cbt, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials with CBT, fluoxetine and escitaloptram as the active intervention")
+
+ggplot(df_for_baseline_severity, aes(x = factor(psy_or_med), y = perc_baseline_mean, color = factor(psy_or_med))) +
+  geom_point(position = position_jitter(width = 0.2), size = 2) +
+  labs(
+    title = "Baseline Depression Severity in Psychotherapy vs Medication trials",
+    x = "Treatment Modality",
+    y = "Baseline Depression Levels (transformed)",
+    color = "Treatment Type"
+  ) +
+  scale_color_discrete(labels = c("Medication", "Psychotherapy"))
+
 ```

### 2024-03-12 apples_and_oranges.qmd
Attempts at tabulating

@@
 library(meta)
+library(kableExtra)
 ```
@@
 
+# plot for overall severity results
+
 ggplot(df_for_baseline_severity, aes(x = factor(psy_or_med), y = perc_baseline_mean, color = factor(psy_or_med))) +
@@
 
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# Now lets make a table that combines across these baseline characteristics variables
+
+df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
+
+# For row names
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(subgroup = case_when(
+    row_number() == 1 ~ "Gender",
+    row_number() == 4 ~ "Age",
+    row_number() == 7 ~ "Severity",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Rounding
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+df_overall_baseline_results %>%
+  kbl(caption = "Sample characteristics at baseline") %>%
+  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#D3D3D3",  extra_css = "border-bottom: 2px solid grey;" ) %>% 
+  row_spec(c(1, 4, 7), bold = T, extra_css = "border-top: 2px solid grey;") %>%
+  column_spec(column = 1, border_right = T) %>% 
+  add_indent(c(2, 3, 5, 6, 8, 9))
+
+df_overall_baseline_results <- options(knitr.kable.NA = "")
+
+```
+### Number of trial sites
+
+Average number of trial sites was significantly higher across medication studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]` compared to psychotherapy studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* = `r sites_t_test$p.value`).
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]
 
 ### Number of sites
-Write results, tabulate.
+# Write results, tabulate.
 
@@
 
+# summary stats
 df_sites_summary_stats <- df_baseline_demographics %>%
@@
   summarise(
+    n = n(),
     mean_sites = mean(sites, na.rm = TRUE),
     sd_sites = sd(sites, na.rm = TRUE),
-    n = n()
   )
+
+# t-test
+sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
 
@@
   scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
+
+# Tabulate
+# Rounding
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+# Row names
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  mutate(psy_or_med = case_when(
+    psy_or_med == 0 ~ "Medication",
+    psy_or_med == 1 ~ "Psychotherapy",
+    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
+  ))
+
+df_sites_summary_stats %>%
+  kbl(col.names = c("Modality", "N", "Mean", "SD")) %>% 
+  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE)
 

### 2024-03-13 apples_and_oranges.qmd
More tabulating and added bits to method

@@
 
-We conducted a meta-analysis to test for differences between psychotherapy versus medication trials in sample characteristics at baseline.
-
-First, we compared depression severity levels at baseline.
-In order to compare across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
+We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including gender, age, and severity of depressive symptoms at baseline.
+Meta-analyses were implemented using R's meta package.
+
+In order to compare depression severity across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
 
@@
 
-We also performed meta-analyses implemented in R's meta package to compare psychotherapy versus medication trials on the gender composition of the sample, mean age, and number of trial sites.
+We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
 
@@
 
-First, for each of the the meta-analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways.
+First, for each of the the analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways.
 First, we excluded studies which recruited participants with subclinical levels of depression.
 Second, we restricted the analyses to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram.
-Third, we restricted the metaregression to studies that *did not* use waitlist as their control.
+Third, we excluded studies that used waitlist as their control condition.
 
@@
 In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
-All included trials and the types of treatment controls can be found in Suppelmenateray Table 1.
+All included trials and the types of treatment controls can be found in Supplementary Table 1.
 
@@
 
-### Gender
-
-Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`).
-On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% women across medication trials.
-Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`).
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).
+Table 1 summarises the results from each of the meta-analyses examining sample characteristics at baseline.
+The summary statistics are provided for each subgroup (i.e.
+for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences.
+Full results for each of the sensitivity analyses are included in the Supplementary Materials (Table X - Y).
 
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 # Start by looking at demographics at baseline
@@
 # Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
-# So we need to further subset. For the active arms, I am filtering out conditions that do not meet our criteria. 
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
-# We may have multiple controls per study id for this reason, though this isn't a problem conceptually.
 
@@
 
-```
-
-### Age
-
-Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (`r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
-There were no significant differences in mean age between modalities on further sensitivity analyses.
+# Now the no waitlist group
+
+no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
+
+df_for_gender_metan_no_wl <- df_for_gender_metan %>%
+  filter(new_study_id %in% no_wl_ids)
+
+met_perc_women_no_wl <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_gender_metan_no_wl,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across studies with controls that are not wl",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+results_met_perc_women_no_wl <- extract_stats(met_perc_women_no_wl)
+
+knitr:: kable(results_met_perc_women_no_wl, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")
+
+```
+### Gender
+
+Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`).
+On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.
+Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`).
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).
 
@@
 # Age meta analysis
+
+df_for_age_metan$se_age <- as.numeric(df_for_age_metan$se_age)
 
@@
 ```
-### Baseline severity
-
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was eiter CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
-When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference no longer reached statistical significance (p = `results_met_sev_clin$pval_between`).
+
+### Age
+
+Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
+There were no significant differences in mean age between modalities on further sensitivity analyses.
 
@@
 
-# Now lets make a table that combines across these baseline characteristics variables
+# Now overall
+# Lets make a table that combines across these baseline characteristics variables
 
 df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
+
+df_overall_baseline_results <- options(knitr.kable.NA = "")
 
@@
   mutate(subgroup = case_when(
-    row_number() == 1 ~ "Gender",
+    row_number() == 1 ~ "Percent Women",
     row_number() == 4 ~ "Age",
@@
 df_overall_baseline_results %>%
-  kbl(caption = "Sample characteristics at baseline") %>%
-  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#D3D3D3",  extra_css = "border-bottom: 2px solid grey;" ) %>% 
-  row_spec(c(1, 4, 7), bold = T, extra_css = "border-top: 2px solid grey;") %>%
+  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  row_spec(row = 1, bold = T) %>% 
+  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
   column_spec(column = 1, border_right = T) %>% 
-  add_indent(c(2, 3, 5, 6, 8, 9))
-
-df_overall_baseline_results <- options(knitr.kable.NA = "")
-
-```
-### Number of trial sites
-
-Average number of trial sites was significantly higher across medication studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]` compared to psychotherapy studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* = `r sites_t_test$p.value`).
+  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))
+
+```
+### Baseline severity
+
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
+When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).
 
@@
 
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  rename(
+    Modality = psy_or_med,
+    N = n,
+    Mean = mean_sites,
+    SD = sd_sites
+  )
+
 df_sites_summary_stats %>%
-  kbl(col.names = c("Modality", "N", "Mean", "SD")) %>% 
-  kable_styling(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE)
+  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
 
@@
 # all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
-# 
 # 
@@
 #                                         sqrt(all_studies_baseline_metareg$baseline_n)
-# 
 # 
@@
 # 
-# 
 # list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
@@
 # results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-# 
-#
-
-# # Look at the diagnostics of included studies 
-# 
-# filtered_data <- df_appl_v_orange %>%
-#   filter(psy_or_med == 1) %>% 
-#   filter(new_study_id %in% cbt_meds_study_ids) %>%
-#   distinct(new_study_id, .keep_all = TRUE)
-# 
-# summary_result <- filtered_data %>%
-#   group_by(diagnosis) %>%
-#   summarise(count = n())
-#
-
-```
+
+```
+
+### Number of trial sites
+
+Average number of trial sites was significantly higher across medication studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]` compared to psychotherapy studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* = `r sites_t_test$p.value`).
 
@@
 
-Table 1 summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->
+Table X summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->
 
@@
 
-knitr:: kable(df_mean_coefs_from_sim, caption = "Table 1")
+# Prepare to tabulate
+
+df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("n", .after = "condition")
+
+df_mean_coefs_from_sim %>%
+  kbl(caption = "Table X: Summary statistics of the estimated SMDs") %>% 
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(aggregate_results_overall, caption = "Table 2", digits = 2
-              )
+
+# Prepare to tabulate
+
+aggregate_results_overall <- aggregate_results_overall %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "coefficients")
+
+aggregate_results_overall %>%
+  kbl(caption = "Table X: Meta-regression results") %>% 
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+
 ```
@@
 # dev.off()
-#
-
-```
 
@@
 
+### Supplement
+
 ```{r}
+
+# Tables for baseline comparisons
+
+# Gender first
+
+# Now overall
+# Lets make a table that combines across these baseline characteristics variables
+
+df_overall_baseline_results <- options(knitr.kable.NA = "")
+
+df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
+
+# For row names
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(subgroup = case_when(
+    row_number() == 1 ~ "Percent Women",
+    row_number() == 4 ~ "Age",
+    row_number() == 7 ~ "Severity",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Rounding
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+df_overall_baseline_results %>%
+  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  row_spec(row = 1, bold = T) %>% 
+  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+  column_spec(column = 1, border_right = T) %>% 
+  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))
+
 # Plots  -----------------------
-# 
-# #define groups
-# df_long_for_metan <- df_long_for_metan %>%
-#   mutate(
-#     group = case_when(
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-#       TRUE ~ NA_character_  
-#     )
-#   )
-
-# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-# 
-# # Plot cohens d per arm
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-# 
-# # Now look at change scores of percentage transformed variables
-# 
-# df_long_for_metan <- df_long_for_metan %>% 
-#   mutate(perc_change = perc_post_mean - perc_baseline_mean)
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = perc_change, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -0.3, yend = -0.25, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -0.3, label = "Less Effective", color = "grey", vjust = 0, hjust = .3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -0.4, yend = -0.45, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -0.4, label = "More Effective", color = "grey", vjust = 0, hjust = .3) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of change scores (percentage transformed) by group", x = NULL, y = "Change") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-# 
-# # # Plot percentage  baseline means 
-# # 
-# # ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
-# #   geom_point(position = position_jitter(width = 0.2), size = 3) +
-# #   scale_color_manual(values = group_colors) +
-# #   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
-# #   theme_minimal() +
-# #   theme(legend.position = "none")
-# 
-# # Box plots
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5, 
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_fill_manual(values = group_colors) +
-#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
-```
+
+#define groups
+df_long_for_metan <- df_long_for_metan %>%
+  mutate(
+    group = case_when(
+      psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
+      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
+      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
+      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
+      TRUE ~ NA_character_
+    )
+  )
+
+group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
+
+# Plot cohens d per arm
+
+ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
+  geom_point(position = position_jitter(width = 0.2), size = 3) +
+  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+  scale_color_manual(values = group_colors) +
+  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+# Plot percentage baseline means
+
+ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+  geom_point(position = position_jitter(width = 0.2), size = 3) +
+  scale_color_manual(values = group_colors) +
+  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+# Box plot Cohens d by group
+
+ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
+  geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
+  scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
+  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
+  geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+  geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
+               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+  geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+  scale_fill_manual(values = group_colors) +
+  labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+```

### 2024-03-14 apples_and_oranges.qmd
More tabulating, running t tests for control vs active comparison in psy trials

@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 # Start by looking at demographics at baseline
@@
 
+# Now look at baseline severity for overall psy vs med
+# Need to calculate the variables first
+
+df_for_baseline_severity <- df_long_for_metan %>% 
+  group_by(new_study_id) %>%
+  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
+  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
+  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
+
+df_for_baseline_severity <- df_for_baseline_severity %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
+met_sev <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev <- extract_stats(met_sev)
+
+# clinical sample
+
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+df_for_baseline_severity_clin <- df_for_baseline_severity %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_sev_clin <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity clinical",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev_clin <- extract_stats(met_sev_clin)
+
+# cbt + med
+
+cbt_meds_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
+  filter(new_study_id %in% cbt_meds_study_ids)
+
+met_sev_cbt <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_cbt,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity cbt + med studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev_cbt <- extract_stats(met_sev_cbt)
+
+# no wl
+
+no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
+
+df_for_baseline_severity_no_wl <- df_for_baseline_severity %>%
+  filter(new_study_id %in% no_wl_ids)
+
+met_sev_no_wl <- metagen(TE = perc_baseline_overall,
+                           seTE = perc_se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_no_wl,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity no wl studies",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev_no_wl <- extract_stats(met_sev_no_wl)
+
+```
+### Baseline severity
+
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials for the overall sample (p = `results_met_sev$pval_between`).The statistics provided in Table 1 represent the transformed mean scores at baseline on the
+
+and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
+When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 # Now start looking at perc_women variable 
-
 # The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.
@@
 # Apply the function to the meta-analysis result
+
 results_met_perc_women_overall <- extract_stats(met_perc_women_overall)
 
-knitr:: kable(results_met_perc_women_overall, caption = "Gender composition")
-
 # looking at clinical sample only
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
 
@@
 
-knitr:: kable(results_met_perc_women_clin, caption = "Gender composition in clinical studies")
-
 # Now looking at the CBT + med studies only
-
-#  grab ids for those studies
-cbt_meds_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
 
@@
 
-knitr:: kable(results_met_perc_women_cbt, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")
-
 # Now the no waitlist group
-
-no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
 
@@
 
-knitr:: kable(results_met_perc_women_no_wl, caption = "Gender composition in studies with CBT, escitalopram or fluoxetine")
-
 ```
@@
 On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.
-Excluding sub-clinical studies yielded very similar results (p = `results_met_perc_women_clin$pval_between`).
+Excluding sub-clinical studies (p = `results_met_perc_women_clin$pval_between`) and studies that used waitlist as their control condition yielded very similar results (p = `results_met_perc_women_no_wl$pval_between`).
 This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).
@@
 
-knitr:: kable(results_met_age, caption = "Average age in psychotherapy vs medication trials")
-
 # Looking at clinical sample only
@@
 
-knitr:: kable(results_met_age_clin, caption = "Average age in clinical studies")
-
 # Now cbt + med studies only
@@
 
-knitr:: kable(results_met_age_cbt, caption = "Average age in cbt, fluox, escit studies")
-
-```
-
-### Age
-
-Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
-There were no significant differences in mean age between modalities on further sensitivity analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Now look at baseline severity for overall psy vs med
-# Need to calculate the variables first
-
-df_for_baseline_severity <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-met_sev <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
+# Now excluding wl
+
+df_for_age_metan_no_wl <- df_for_age_metan %>%
+  filter(new_study_id %in% no_wl_ids)
+
+met_age_no_wl <- metagen(TE = mean_age,
+                           seTE = se_age,
                            studlab = new_study_id,
-                           data = df_for_baseline_severity,
+                           data = df_for_age_metan_no_wl,
                            sm = "",
@@
                            hakn = TRUE,
-                           title = "baseline severity",
+                           title = "age across no wl studies",
                            subgroup = psy_or_med,
@@
 
-results_met_sev <- extract_stats(met_sev)
-
-knitr:: kable(results_met_sev, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials")
-
-# clinical sample
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_baseline_severity_clin <- df_for_baseline_severity %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_sev_clin <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity clinical",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_clin <- extract_stats(met_sev_clin)
-
-knitr:: kable(results_met_sev_clin, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials, excluding subclinical studies")
-
-# cbt + med
-
-df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
-  filter(new_study_id %in% cbt_meds_study_ids) %>%
-
-met_sev_cbt <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cbt + med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_cbt <- extract_stats(met_sev_cbt)
-
-knitr:: kable(results_met_sev_cbt, caption = "Baseline Depression Severity in Psychotherapy vs Medication trials with CBT, fluoxetine and escitaloptram as the active intervention")
-
-# plot for overall severity results
-
-ggplot(df_for_baseline_severity, aes(x = factor(psy_or_med), y = perc_baseline_mean, color = factor(psy_or_med))) +
-  geom_point(position = position_jitter(width = 0.2), size = 2) +
-  labs(
-    title = "Baseline Depression Severity in Psychotherapy vs Medication trials",
-    x = "Treatment Modality",
-    y = "Baseline Depression Levels (transformed)",
-    color = "Treatment Type"
-  ) +
-  scale_color_discrete(labels = c("Medication", "Psychotherapy"))
-
-# Now overall
+results_met_age_no_wl <- extract_stats(met_age_no_wl)
+
+```
+### Age
+
+Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
+There were no significant differences in mean age between modalities on further sensitivity analyses.
+
+```{r}
+
 # Lets make a table that combines across these baseline characteristics variables
@@
 df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
-
-df_overall_baseline_results <- options(knitr.kable.NA = "")
 
@@
 
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_overall_baseline_results) <- new_column_names
+
 # Rounding
 df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3))
+
+colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
 
 df_overall_baseline_results %>%
-  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  kbl(align = "l", caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
   kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
@@
   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(column = 1, border_right = T) %>% 
+  column_spec(1, border_right = T) %>% 
   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))
-
-```
-### Baseline severity
-
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials, for both the overall sample (p = `results_met_sev$pval_between`) and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
-When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).
+  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+df_overall_baseline_results <- options(knitr.kable.NA = "")
+
+```
 
@@
 
-# t-test
-sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
-
-# plot
-
-ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
-  geom_point(position = position_jitter(width = 0.2), size = 2) +
-  labs(title = "Number of Sites for Psychotherapy and Medication Trials",
-       x = "Treatment Modality",
-       y = "Number of Sites") +
-  scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
-
 # Tabulate
@@
 
-# ### do ALL studies using percentage at baseline
-# all_studies_baseline_metareg <- list_df_simulated_percentage[[1]]
-# 
-# #turn sds to sec
-# all_studies_baseline_metareg$baseline_stand_error <- all_studies_baseline_metareg$perc_baseline_sd/
-#                                         sqrt(all_studies_baseline_metareg$baseline_n)
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# # also change this for the function to work
-# all_studies_baseline_metareg$baseline_mean <- all_studies_baseline_metareg$perc_baseline_mean
-# results_all_studies_metareg_baseline <- run_metareg_and_extract(all_studies_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# ### get CDRS studies
-# cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-# 
-# #turn sds to sec
-# cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-#                                         sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# 
-# results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
-#                                                          model_1, condition)
-# 
-# ### get HAM-D studies
-# hamd_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-# 
-# list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-#                                                           %in% hamd_study_ids,]
-# 
-# hamd_studies_for_baseline_metareg <- list_hamd_study # 
-# 
-# #turn sds to sec
-# hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-#                                         sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-# 
-# model_1 <- as.formula(~ four_level_var)
-# condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-#                                                               #throughout
-# results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
-#                                                          model_1, condition)
-# 
-# results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-```
-
+# t-test
+sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
+
+sites_t_test_stats <- data.frame(
+  statistic = sites_t_test$statistic,
+  df = sites_t_test$parameter,
+  p_value = sites_t_test$p.value,
+  ci_lower = sites_t_test$conf.int[1],
+  ci_upper = sites_t_test$conf.int[2]
+)
+
+sites_t_test_stats <- sites_t_test_stats %>%
+  dplyr:: mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2)))
+
+sites_t_test_stats %>%
+  kbl(caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+
+# plot
+
+ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
+  geom_point(position = position_jitter(width = 0.2), size = 2) +
+  labs(title = "Number of Sites for Psychotherapy and Medication Trials",
+       x = "Treatment Modality",
+       y = "Number of Sites") +
+  scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
+
+```
 ### Number of trial sites
@@
 
-### Comparing the nature and intensity of control conditions in psychotherapy trials
-
-Write results here.
-
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
     Mean = numeric(),
-    Std_Dev = numeric(),
+    SD = numeric(),
     Median = numeric(),
@@
       mean_val <- mean(col_data, na.rm = TRUE)
-      std_dev <- sd(col_data, na.rm = TRUE)
+      SD <- sd(col_data, na.rm = TRUE)
       median_val <- median(col_data, na.rm = TRUE)
@@
                                            Column = col, N = n, Mean = mean_val,
-                                           Std_Dev = std_dev, Median = median_val,
+                                           SD = SD, Median = median_val,
                                            IQR = iqr, stringsAsFactors = FALSE))
@@
 
-knitr:: kable(control_summary, caption="Characteristics of the active and control arms of psychotherapy trials")
-
-```
+control_summary <- control_summary %>% 
+  select(-c(Column, Median, IQR))
+
+control_summary <- control_summary %>%
+  mutate(Group = case_when(
+    Group == "psychotherapy_active" ~ "Active",
+    Group == "psychotherapy_control" ~ "Control",
+    TRUE ~ as.character(Group)  # Keep other values unchanged
+  ))
+
+control_summary <- control_summary %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+control_summary %>%
+  kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  column_spec(1, border_right = T) %>% 
+  pack_rows("Number of sessions", 1, 2) %>% 
+  pack_rows("Frequency (weeks)", 3, 4) %>% 
+  pack_rows("Session length (mins)", 5, 6) %>%
+  pack_rows("Total intervention hours", 7, 8) %>%
+  pack_rows("Total intervention period (weeks)", 9, 10)
+
+# t tests
+
+session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
+freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
+session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
+total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
+total_period_t_test <- t.test(total_period_weeks ~ levels_var, data = df_descr_psy_conditions)
+
+extract_t_test_stats <- function(df) {
+
+  t_test_stats <- data.frame(
+  outcome = df$data.name,
+  statistic = df$statistic,
+  df = df$parameter,
+  p_value = df$p.value,
+  ci_lower = df$conf.int[1],
+  ci_upper = df$conf.int[2])
+
+  return(t_test_stats)
+
+}
+
+results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
+results_freq_t_test <- extract_t_test_stats(freq_t_test)
+results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
+results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
+results_total_period_t_test <- extract_t_test_stats(total_period_t_test)
+
+control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test, results_total_period_t_test)
+
+```
+### Comparing the nature and intensity of control conditions in psychotherapy trials
+
+Write results here.
 
@@
 We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D on which there was a sufficient number of studies to metanalyse.
-
-```
 
@@
 
-# Gender first
-
-# Now overall
-# Lets make a table that combines across these baseline characteristics variables
-
-df_overall_baseline_results <- options(knitr.kable.NA = "")
-
-df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
+# Lets make a table that combines across the sensitivity analyses for severity
+
+df_severity_sens <- rbind(results_met_sev_cbt, results_met_sev_clin, results_met_sev_no_wl)
 
 # For row names
-df_overall_baseline_results <- df_overall_baseline_results %>%
+df_severity_sens <- df_severity_sens %>%
   mutate(subgroup = case_when(
-    row_number() == 1 ~ "Percent Women",
-    row_number() == 4 ~ "Age",
-    row_number() == 7 ~ "Severity",
+    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+    row_number() == 4 ~ "Excluding subclinical",
+    row_number() == 7 ~ "Excluding waitlist",
     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
@@
 
+# Define new column names
+new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_severity_sens) <- new_column_names
+
 # Rounding
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-df_overall_baseline_results %>%
-  kbl(caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies") %>%
+df_severity_sens <- df_severity_sens %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3))
+
+colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))
+
+df_severity_sens %>%
+  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
   kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
@@
   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(column = 1, border_right = T) %>% 
+  column_spec(1, border_right = T) %>% 
   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(alphabet = c("Values for baseline severity represent the percentage transformed depression scores", "pval_between = the p-value from the test for subgroup differences from the relevant meta-analysis"))
+  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+# Now gender
+
+df_gender_sens <- rbind(results_met_perc_women_cbt, results_met_perc_women_clin, results_met_perc_women_no_wl)
+
+# For row names
+df_gender_sens <- df_gender_sens %>%
+  mutate(subgroup = case_when(
+    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+    row_number() == 4 ~ "Excluding subclinical",
+    row_number() == 7 ~ "Excluding waitlist",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Define new column names
+new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_gender_sens) <- new_column_names
+
+# Rounding
+df_gender_sens <- df_gender_sens %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3))
+
+colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))
+
+df_gender_sens %>%
+  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  row_spec(row = 1, bold = T) %>% 
+  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+  column_spec(1, border_right = T) %>% 
+  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+# Now age
+
+df_age_sens <- rbind(results_met_age_cbt, results_met_age_clin, results_met_age_clin)
+
+# For row names
+df_age_sens <- df_age_sens %>%
+  mutate(subgroup = case_when(
+    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+    row_number() == 4 ~ "Excluding subclinical",
+    row_number() == 7 ~ "Excluding waitlist",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Define new column names
+new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_age_sens) <- new_column_names
+
+# Rounding
+df_age_sens <- df_age_sens %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3))
+
+colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))
+
+df_age_sens %>%
+  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  row_spec(row = 1, bold = T) %>% 
+  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+  column_spec(1, border_right = T) %>% 
+  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
 

### 2024-03-15 apples_and_oranges.qmd
Tabulating for psy control comparison

@@
 
+# For row names
+control_summary_t_tests <- control_summary_t_tests %>%
+  mutate(outcome = case_when(
+    row_number() == 1 ~ "Number of sessions",
+    row_number() == 2 ~ "Frequency (weeks)",
+    row_number() == 3 ~ "Session length (mins)",
+    row_number() == 4 ~ "Total intervention hours",
+    row_number() == 5 ~ "Total intervention period (weeks)"
+  ))
+
+# Define new column names
+new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(control_summary_t_tests) <- new_column_names
+
+#Rounding
+control_summary_t_tests <- control_summary_t_tests %>%
+  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
+  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+
+colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
+
+control_summary_t_tests %>%
+  kbl(align = "l", caption = "Table X: Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+
 ```
@@
 
-# Plot cohens d per arm
+# Scatter plot cohens d per arm
 
@@
   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-  theme_minimal() +
-  theme(legend.position = "none")
-
-# Plot percentage baseline means
-
-ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
-  geom_point(position = position_jitter(width = 0.2), size = 3) +
-  scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
   theme_minimal() +
@@
 
-```
+# Plot percentage baseline means
+
+ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+  geom_point(position = position_jitter(width = 0.2), size = 3) +
+  scale_color_manual(values = group_colors) +
+  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+  theme_minimal() +
+  theme(legend.position = "none")
+
+```

### 2024-03-15 apples_and_oranges.qmd
Tabulating

@@
 This assumption may be hard to meet.
-Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
+Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self- %>% ion bias with respect to who participates in psychotherapy versus medication trials.
 Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
@@
 ```
-
 # Results
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# This chunk of code needs to be here because some of the data needed for the included studies summary lives here
+
+# Get Ns, run metareg, prepare graphing ------------------------------------------------------
+library(tidyverse)
+library(metafor)
+
+# add a new multilevel variable to the simulated data for the regression
+
+for(i in 1: length(list_df_simulated)){
+
+list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
+  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+
+  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
+                                                       "medication_control",
+                                                       "medication_active", 
+                                                       "psychotherapy_control",
+                                                       "psychotherapy_active")
+}
+
+# check it worked
+# list_df_simulated[[2]] %>% 
+# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
+
+######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
+# A) the overall sample
+# B) the CBT vs Fluox and Escitalopram sample
+# C) the no WL sample
+# E) the CDRS only sample (**Argyris** do we still want this?)
+# F) Clinical Levels Depression
+
+# A. Estimate Means and CIs for the overall ----------------------------------
+
+# count studies
+# count the number of studies
+n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
+df_count_studies <- count_studies(df_long_for_metan ) # CHARLOTTE please check
+# CB checked both, both correct.
+
+# specify model
+model_1 <- as.formula(~ four_level_var)
+
+# run metareg function 
+# here you can use the simulated results directly
+list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
+aggregate_results_overall <- cbind(aggregate_results_overall, condition)
+
+# extract SMDs from the  list
+list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)
+
+df_mean_coefs_from_sim <- data.frame(cbind(condition,df_mean_coefs_from_sim))
+
+# add the ns
+df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
+
+# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
+#  grab ids for those studies
+cbt_fluox_esc_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+# Use those ids to subset all dataframes in the list
+# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
+# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
+# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
+# We may have multiple controls per study id for this reason, though this isn't a problem 
+# conceptually.
+
+list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+})
+
+# count the number of studies
+cbt_fluox_esc_study <- df_long_for_metan %>%
+  filter(new_study_id %in% cbt_fluox_esc_study_ids,
+         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
+study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
+# CB checked, looks good now.
+
+# apply the metareg function to the list of cbt, fluox, esc
+model_1 <- as.formula(~ four_level_var)
+list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
+aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
+
+# extract SMDs from the list for cbt fluox escit
+means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
+ coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
+
+# add the ns to the dataframe
+ coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n
+
+# C. Estimate Means and CIs without WL ---------------------------------------
+
+ # grab the ids for no waitlist
+no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
+
+# use them to loop over the simulated list to subset all the dataframes.
+
+list_no_wl <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% no_wl_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
+})
+
+# count studies 
+no_wl_studies <- df_long_for_metan %>% 
+  filter(new_study_id %in% no_wl_ids) %>%
+  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
+study_count_no_wl_study <- count_studies(no_wl_studies)
+# CB checked, looks good!
+
+# use this model as above
+model_1 <- as.formula(~ four_level_var)
+
+# apply the metareg function to the list of no wl
+list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
+aggregate_results_no_wl <- cbind(aggregate_results_no_wl, condition)
+
+# now use the function to extract the coefficients
+means_no_wl <-  lapply(list_model_1_no_wl, extract_coefficients_func)
+
+# run the mean function for no wl
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
+coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
+
+coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
+                                                     ==FALSE,]$n
+
+# E. CDRS Sensitivity Analysis ---------------------------------------
+
+cdrs_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_cdrs_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% cdrs_study_ids,]
+}
+
+# count the number of studies
+study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
+# CB checked, correct.
+
+# apply the metareg function to the list of cdrs studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
+
+# extract SMDs from the list for cdrs
+means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
+coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
+
+# add the ns to the dataframe
+coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
+
+# F Clinical Levels Depression Sensitivity Analysis ---------------------------------------
+
+# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
+
+#take study ids where sample has clinical levels of depression
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_clin_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% clin_study_ids,]
+}
+
+# count the number of studies
+study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
+# CB checked, correct.
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
+coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
+
+# add the ns to the dataframe
+coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n
+
+```
 
@@
 
-  df_stats <- data.frame(
+  df_stats <- tibble(
   subgroup = statistics$subgroup.levels,
@@
   # Add an empty row at the top and column on right (this is for the test for subgroup differences p value)
-  df_stats <- rbind(data_frame(subgroup = NA, k_study = NA, TE_random = NA, seTE_random = NA, 
+  df_stats <- rbind(data.frame(subgroup = NA, k_study = NA, TE_random = NA, seTE_random = NA, 
                              lower_random = NA, upper_random = NA, tau2 = NA), df_stats)
@@
 
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials for the overall sample (p = `results_met_sev$pval_between`).The statistics provided in Table 1 represent the transformed mean scores at baseline on the
-
-and when taking only those studies where the active arm was either CBT, fluoxetine or escitalopram (p = `results_met_sev_cbt$pval_between`).
-When excluding psychotherapy studies that recruited samples with sub-clinical depression, this difference did not reach statistical significance (p = `results_met_sev_clin$pval_between`).
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials (*p* = `r results_met_sev$pval_between`).
+The statistics provided in Table 1 are baseline depression scores transformed to reflect percentage of a scale range.
+To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
+range of 96).
+From Table 1, mean severity was `r results_met_sev$seTE_random[results_met_sev$subgroup == 1]` for psychotherapy studies and `r results_met_sev$seTE_random[results_met_sev$subgroup == 0]` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
+
+When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies (*p* = `r results_met_sev_cbt$pval_between`).
+This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression (*p* = `r results_met_sev_clin$pval_between`) or when excluding studies that used wait list as their control (*p* = `r results_met_sev_no_wl$pval_between`).
 
@@
 
-Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`results_met_perc_women_overall$pval_between`).
+Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`r results_met_perc_women_overall$pval_between`).
 On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.
-Excluding sub-clinical studies (p = `results_met_perc_women_clin$pval_between`) and studies that used waitlist as their control condition yielded very similar results (p = `results_met_perc_women_no_wl$pval_between`).
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (p = `results_met_perc_women_cbt$pval_between`).
+Excluding sub-clinical (*p* = `results_met_perc_women_clin$pval_between`) and waitlist control studies (*p* = `results_met_perc_women_no_wl$pval_between`) yielded very similar results.
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (*p* = `results_met_perc_women_cbt$pval_between`).
 
@@
 
-Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (p = `r results_met_age$pval_between`).
+Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (*p* = `r results_met_age$pval_between`).
 There were no significant differences in mean age between modalities on further sensitivity analyses.
 
-```{r}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
-df_overall_baseline_results <- rbind(results_met_perc_women_overall, results_met_age, results_met_sev)
+df_overall_baseline_results <- rbind(results_met_sev, results_met_perc_women_overall, results_met_age)
 
@@
   mutate(subgroup = case_when(
-    row_number() == 1 ~ "Percent Women",
-    row_number() == 4 ~ "Age",
-    row_number() == 7 ~ "Severity",
+    row_number() == 1 ~ "Severity",
+    row_number() == 4 ~ "Percent Women",
+    row_number() == 7 ~ "Age",
     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
@@
 df_overall_baseline_results %>%
-  kbl(align = "l", caption = "Table X: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
+  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
   kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
@@
 df_overall_baseline_results <- options(knitr.kable.NA = "")
+
+# This is weird, you have to run this line and then re chunk above
+
+df_overall_baseline_results %>%
+  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
+  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+  row_spec(row = 1, bold = T) %>% 
+  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+  column_spec(1, border_right = T) %>% 
+  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
 
@@
 sites_t_test_stats <- sites_t_test_stats %>%
-  dplyr:: mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2)))
+  mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2))) %>% 
+  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
 
 sites_t_test_stats %>%
-  kbl(caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
+  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
   kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
@@
 
-# plot
+# scatter plot
 
@@
 
+#### Mean efficacy of psychotherapy versus medication control conditions
+
+We applied metaregression to obtain the SMDs and confidence intervals of each of the four arms.
+
+As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
+In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` (see Table X).
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Get Ns, run metareg, prepare graphing ------------------------------------------------------
-library(tidyverse)
-library(metafor)
-
-# add a new multilevel variable to the simulated data for the regression
-
-for(i in 1: length(list_df_simulated)){
-
-list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
-  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
-                                                       "medication_control",
-                                                       "medication_active", 
-                                                       "psychotherapy_control",
-                                                       "psychotherapy_active")
-}
-
-# check it worked
-# list_df_simulated[[2]] %>% 
-# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
-
-######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
-# A) the overall sample
-# B) the CBT vs Fluox and Escitalopram sample
-# C) the no WL sample
-# E) the CDRS only sample (**Argyris** do we still want this?)
-# F) Clinical Levels Depression
-
-# A. Estimate Means and CIs for the overall ----------------------------------
-
-# count studies
-# count the number of studies
-n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
-df_count_studies <- count_studies(df_long_for_metan ) # CHARLOTTE please check
-# CB checked both, both correct.
-
-# specify model
-model_1 <- as.formula(~ four_level_var)
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
-aggregate_results_overall <- cbind(aggregate_results_overall, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)
-
-df_mean_coefs_from_sim <- data.frame(cbind(condition,df_mean_coefs_from_sim))
-
-# add the ns
-df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
-
-# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-#  grab ids for those studies
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
-# We may have multiple controls per study id for this reason, though this isn't a problem 
-# conceptually.
-
-list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-})
-
-# count the number of studies
-cbt_fluox_esc_study <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids,
-         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
-study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# CB checked, looks good now.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
- coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-
-# add the ns to the dataframe
- coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n
-
-# C. Estimate Means and CIs without WL ---------------------------------------
-
- # grab the ids for no waitlist
-no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
-
-# use them to loop over the simulated list to subset all the dataframes.
-
-list_no_wl <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% no_wl_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
-})
-
-# count studies 
-no_wl_studies <- df_long_for_metan %>% 
-  filter(new_study_id %in% no_wl_ids) %>%
-  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
-study_count_no_wl_study <- count_studies(no_wl_studies)
-# CB checked, looks good!
-
-# use this model as above
-model_1 <- as.formula(~ four_level_var)
-
-# apply the metareg function to the list of no wl
-list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
-aggregate_results_no_wl <- cbind(aggregate_results_no_wl, condition)
-
-# now use the function to extract the coefficients
-means_no_wl <-  lapply(list_model_1_no_wl, extract_coefficients_func)
-
-# run the mean function for no wl
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
-coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
-
-coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
-                                                     ==FALSE,]$n
-
-# E. CDRS Sensitivity Analysis ---------------------------------------
-
-cdrs_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_cdrs_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% cdrs_study_ids,]
-
-}
-
-# count the number of studies
-study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of cdrs studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
-
-# extract SMDs from the list for cdrs
-means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
-coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
-
-# F Clinical Levels Depression Sensitivity Analysis ---------------------------------------
-
-# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
-
-#take study ids where sample has clinical levels of depression
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_clin_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% clin_study_ids,]
-
-}
-
-# count the number of studies
-study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
-coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
-
-# add the ns to the dataframe
-coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n
-
-```
-
-#### Mean efficacy of psychotherapy versus medication control conditions
-
-We applied metaregression to obtain the SMDs and confidence intervals of each of the four arms.
-
-As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking difference being the medication and the psychotherapy control arms.
-In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)`.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
@@
 plot_means_all
-```
-
-![Figure 1.](plot_means_all.pdf)
-
-Table X summarises the statistics of the estimated SMDs. <!--# Charlotte, we need to turn these into nice tables with proper columns, rounding etc. -->
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
+new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(df_mean_coefs_from_sim) <- new_column_names
+
 df_mean_coefs_from_sim %>%
-  kbl(caption = "Table X: Summary statistics of the estimated SMDs") %>% 
+  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
   kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
@@
 
-```
-
-In Table 2, we present the regression that tests our hypothesis about differences between medication and psychotherapy control.
-In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable, including psychotherapy control, are compared.
-The strongest difference betwen arms, as judged by the z-value, is between the psychotherapy and medication control with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Prepare to tabulate
+# Regression results
 
@@
 
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
+
+# Assign new column names to the data frame
+colnames(aggregate_results_overall) <- new_column_names
+
 aggregate_results_overall %>%
@@
 
-### Sensitivity Analyses
+![Figure 1.](plot_means_all.pdf)
+
+`r df_mean_coefs_from_sim`
+
+In Table X, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
+
+##### Sensitivity analyses
 
 We then conducted a series of sensitivity analyses of our results.
+We compared the control and active arms of CBT studies to those of fluoxetine and escitalopram studies.
+As can be seen, the pattern of results is very similar to that of the overall analyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
+plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
+pdf(file = "plot_means_cbt.pdf")
+plot_means_cbt
+dev.off()
+
+```
+
+![](plot_means_cbt.pdf)
+
+We next analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+#print(plot_means_wl)
+pdf(file = "plot_means_wl.pdf")
+plot_means_wl
+dev.off()
+
+```
+![](plot_means_wl.pdf)
+
+We next analysed the data after excluding sub-clinical studies. Again, the pattern of results was very similar to that of the overall analyses.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
+plot_means_clin <- plot_means_function(coef_and_se_means_clin_study, subtitle_text_clin)
+pdf(file = "plot_means_clin.pdf")
+plot_means_clin
+dev.off()
+
+```
+
+![](plot_means_clin.pdf)
 
 #### Effect of standard errors of the SMDs .
-
-It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
-To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
-If standard error distributions were influential, this should show up as substantial variability across simulations.
-We test this idea in the Figure 1 which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table 2).
-As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
-the value of z = 1.645.
 
@@
 
+It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
+To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
+If standard error distributions were influential, this should show up as substantial variability across simulations.
+We test this idea in the Figure X which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table X).
+As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
+the value of z = 1.645.
+
 ![](stab_sims.pdf)
 
-#### Comparison of CBT with fluoxetine and escitalopram
-
-We next compared the control and active arms of CBT studies to those of fluoxetine and escitalopram studies. As can be seen, the pattern of results is very similar to that of the ovarall analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
-plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
-pdf(file = "plot_means_cbt.pdf")
-plot_means_cbt
-dev.off()
-```
-
-![](plot_means_cbt.pdf)
-
-#### Excluding studies with waitlist control arms.
-
-We next analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
-#print(plot_means_wl)
-
-pdf(file = "plot_means_wl.pdf")
-plot_means_wl
-dev.off()
-```
-
-![](plot_means_wl.pdf)
+### Comparing the nature and intensity of control conditions in psychotherapy trials
 
@@
 ```
-### Comparing the nature and intensity of control conditions in psychotherapy trials
-
-Write results here.
+
+Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see Table X for summary statistics).
+Active intervention arms featured significantly more sessions than control arms (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
+These sessions were also significantly longer (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`).
+The total hours involved in an intervention were higher in active vs control arms (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`) though the total period of the intervention was similar (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`).
+
+*Write up results for sensitivity analyses*
 
 #### Addressing Regression to the Mean
+**Argyris** are we happy to remove this whole section?
 
@@
 As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
-<!--# Charlotte, please add the n for each row.
-Easiest to modify the function so that it appends the baseline n together with the condition.
--->
 

### 2024-03-15 apples_and_oranges.qmd
Test

@@
   kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
@@
   kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
   row_spec(row = 0, background = "#EBEBEB") %>% 
@@
   kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
   row_spec(row = 0, background = "#EBEBEB") %>% 
@@
   kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
   row_spec(row = 0, background = "#EBEBEB") %>% 
@@
   kbl(caption = "Table X: Meta-regression results") %>% 
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB") %>% 
@@
   kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
@@
   kbl(align = "l", caption = "Table X: Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
   row_spec(row = 0, background = "#EBEBEB") %>% 
@@
   kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
@@
   kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
@@
   kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
-  kable_material(bootstrap_options = c("hover", "condensed", "bordered"), full_width = FALSE) %>%
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 

### 2024-03-15 apples_and_oranges.qmd
This is the best i can do before weekend

@@
 \tau_{psy} =  E(Y_{1} - Y_{0} \,|\, S, psy)
-$$
-$$
+$$ $$
 \tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\ 
@@
 This assumption may be hard to meet.
-Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self- %>% ion bias with respect to who participates in psychotherapy versus medication trials.
+Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self- %\>% ion bias with respect to who participates in psychotherapy versus medication trials.
 Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
@@
 By contrast, psychotherapy control arms vary across waitlist controls, treatment as usual and active controls.
-These differences in expectation essentially favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially the difference between them), because participants in the active condition could be content for receiving the “cutting edge treatment” whilst those in the control will be dissatisfied for having  missed out on “proper treatment”.
+These differences in expectation essentially favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially the difference between them), because participants in the active condition could be content for receiving the "cutting edge treatment" whilst those in the control will be dissatisfied for having missed out on "proper treatment".
 And this is important because expectancy is associated with treatment outcomes.
-This also poses problems when trying to infer indirect comparisons in network metanalyses where, for example, CBT is compared to placebo control and medication — given the likely differential expectation effects, comparisons to the unblinded psychotherapy controls may be biased.
+This also poses problems when trying to infer indirect comparisons in network metanalyses where, for example, CBT is compared to placebo control and medication --- given the likely differential expectation effects, comparisons to the unblinded psychotherapy controls may be biased.
 
@@
 However, we believe that this is justified for two reasons: a) because it is important to make transparent to all, particularly decision makers in healthcare, the raw data before these are entered into more complex modelling such as network metanalysis, as this allows them to form opinions about the quality and limitations of the input data; b) our aim here is not to make claims about the relative efficacy of each treatment arm, but rather establish whether the conditions for the possibility of comparisons are fulfilled.
-Thus, the comparisons between control conditions are not meant to lead to inferences about placebo being “more efficacious” than psychotherapy controls, but rather to make transparent the problem that they seem to derive from different distributions.
+Thus, the comparisons between control conditions are not meant to lead to inferences about placebo being "more efficacious" than psychotherapy controls, but rather to make transparent the problem that they seem to derive from different distributions.
 Third, we examine the quality of psychotherapy controls as such, by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
@@
 
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ {#eq-3}
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
 
@@
 ```
+
 # Results
@@
 There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
-
-<!--# Charlotte, for the paragraph below, please provide the numbers for each of the numbers wherever I have put an X.
-CB - done.
-I removed psychodynamic because there weren't any active conditions of this type.
--->
 
@@
 ```
+
 ### Baseline severity
@@
 ```
+
 ### Gender
@@
 ```
+
 ### Age
@@
 
+df_overall_baseline_results <- options(knitr.kable.NA = "")
+
+```
+
+```{r, warning=FALSE, message = FALSE}
 df_overall_baseline_results %>%
@@
   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
-df_overall_baseline_results <- options(knitr.kable.NA = "")
-
-# This is weird, you have to run this line and then re chunk above
-
-df_overall_baseline_results %>%
-  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-  row_spec(row = 1, bold = T) %>% 
-  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(1, border_right = T) %>% 
-  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
-df_sites_summary_stats %>%
-  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
-  row_spec(row = 0, background = "#EBEBEB") %>% 
-  column_spec(column = 1, border_right = T)
-
 # t-test
@@
 
-sites_t_test_stats %>%
-  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
-  row_spec(row = 0, background = "#EBEBEB") %>% 
-  column_spec(column = 1, border_right = T)
-
 # scatter plot
@@
 ```
+
 ### Number of trial sites
 
-Average number of trial sites was significantly higher across medication studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]` compared to psychotherapy studies ( *M* = `r `df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* = `r `df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* = `r sites_t_test$p.value`).
+Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* =`r`df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]`compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* =`r df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* =`r sites_t_test$p.value`).
+
+```{r, warning=FALSE, message = FALSE}
+df_sites_summary_stats %>%
+  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+
+sites_t_test_stats %>%
+  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+```
 
@@
 
-df_mean_coefs_from_sim %>%
-  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
-  row_spec(row = 0, background = "#EBEBEB") %>% 
-  column_spec(column = 1, border_right = T)
-
 # Regression results
@@
 
+```
+
+![Figure 1.](plot_means_all.pdf)
+
+```{r, warning=FALSE, message = FALSE}
+df_mean_coefs_from_sim %>%
+  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
+  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
+  row_spec(row = 0, background = "#EBEBEB") %>% 
+  column_spec(column = 1, border_right = T)
+```
+
+In Table X, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
+
+```{r, warning=FALSE, message = FALSE}
 aggregate_results_overall %>%
@@
   column_spec(column = 1, border_right = T)
-
-```
-
-![Figure 1.](plot_means_all.pdf)
-
-`r df_mean_coefs_from_sim`
-
-In Table X, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
+```
 
@@
 ```
+
 ![](plot_means_wl.pdf)
@@
     y = "z-value",
-    title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
+    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
     subtitle = "Results from 1000 simulations with within-group standard errors"
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 # We need to read in the appropriate dataset which describes the active and control conditions used in
@@
 colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
-
+```
+
+```{r, warning=FALSE, message = FALSE}
 control_summary_t_tests %>%
@@
 #### Addressing Regression to the Mean
+
 **Argyris** are we happy to remove this whole section?
@@
 As can be seen in Table 3a and 3b, there baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
-As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
+# knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
 ```
@@
 #     y = "z-value",
-#     title = "Stability of the Statistic of the Difference between \nMedication and Psychotherapy Control Arms",
+#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
 #     subtitle = "Results from 1000 simulations with within-group standard errors"
@@
 ```{r}
-knitr:: kable(cdrs_smd_with_cis, caption = "Table 6a. CDRS baseline mean adjsuted SMDs")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(hamd_smd_with_cis, caption = "Table 6. HAM-D baseline-mean adjusted SMDs")
+# knitr:: kable(cdrs_smd_with_cis, caption = "Table 6a. CDRS baseline mean adjsuted SMDs")
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable(hamd_smd_with_cis, caption = "Table 6. HAM-D baseline-mean adjusted SMDs")
 ```
@@
 
-```{r}
-
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Tables for baseline comparisons
@@
 colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))
-
+```
+
+```{r, warning=FALSE, message = FALSE}
 df_severity_sens %>%
@@
   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Now gender
@@
 colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))
-
+```
+
+```{r, warning=FALSE, message = FALSE}
 df_gender_sens %>%
@@
   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Now age
@@
 colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))
-
+```
+
+```{r, warning=FALSE, message = FALSE}
 df_age_sens %>%
@@
   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Plots  -----------------------

### 2024-03-15 apples_and_oranges.qmd
Everything here just can't render

@@
 ```{r, warning=FALSE, message = FALSE}
+
 df_sites_summary_stats %>%
@@
   column_spec(column = 1, border_right = T)
+
 ```
@@
 ```{r, warning=FALSE, message = FALSE}
+
 df_mean_coefs_from_sim %>%
@@
 ```{r, warning=FALSE, message = FALSE}
+
 aggregate_results_overall %>%

### 2024-03-18 Untitled.qmd
some updates from Argyris Untitled is the doc file

--- 2024-03-15 apples_and_oranges.qmd
@@
 ---
-title: Fundamental Problems with the Evidence Base of Adolescent Depression Treatments.
-subtitle: Insights from the relative efficacy of Control Conditions.
-author:
-  - name: Argyris Stringaris
-    email: a.stringaris@ucl.ac.uk
-    affiliations: 
-        - id: ucl_1
-          name: University College London
-          department: Divisions of Psychiatry and Psychology and Language Science
-          address: 1-19 Torrington Place
-          city: London, UK
-          state: 
-          postal-code: WC1E 7HB
-          country: United Kingdom
-    attributes:
-        corresponding: true
-    note: 
-  - name: Charlotte Burman
-    email: charlotte.burman@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-  - name: Dayna Bhudia
-    email: dayna.bhudia@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Lucy Foulkes
-    email: lucy.foulkes@psych.ox.ac.uk
-    affiliations:
-        - id: OU
-          name: University of Oxford
-          department: Experimental Psychology
-          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
-          city: Oxford
-          postal-code: OX2 6GG
-          country: United Kingdom
-    note:
-  - name: Carmen Moreno
-    email: cmoreno@hggm.es
-    affiliations:
-        - id: HGM
-          name: Hospital Gregorio Marañón
-          department: Department of Psychiatry
-          address: 46 C. del Dr. Esquerdo
-          city: Madrid
-          state:
-          postal-code: 28007
-          country: Spain
-  - name: Samuele Cortese
-    email: samuele.cortese@soton.ac.uk
-    affiliations:
-        - id: soton
-          name: University of Southampton
-          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
-          address: Highfield Campus, Building 44
-          city: Southampton
-          state:
-          postal-code: SO17 1BJ
-          country: United Kingdom
-  - name: Georgina Krebs
-    email: g.krebs@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note: 
-abstract: |
-  To follow
-keywords: 
-  - depression
-  - adolescents
-  - antidepressants
-  - psychotherapy
-date: last-modified
-bibliography: emotion_concepts_paper.bib
-format: 
-  elsevier-pdf:
-    keep-tex: true
-    journal:
-      name: Journal Name
-      formatting: preprint
-      model: 3p
-      cite-style: super
+title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
+author: "Stringaris et al"
+prefer-html: true
+format: docx
+editor: visual
+---
+
+##
+
+---
+
 ---
@@
 \tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\ 
-$$ {#eq-1}
+$$
 
@@
 
-$$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$ {#eq-2}
+$$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$
 
@@
 \text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
-$$ {#eq-3}
+$$
 
@@
 \text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
-$$ {#eq-4}
+$$
 
@@
 
-$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$ {#eq-5}
+$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$
 
@@
 
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$ {#eq-6}
+$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
 
@@
 $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$ {#eq-7}
+$$
 
 $$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
-$$ {#eq-8}
+$$
 
@@
 
-$$Y_i = x_i\beta_i + u_i + \epsilon_i$$ {#eq-9}
+$$Y_i = x_i\beta_i + u_i + \epsilon_i$$
 
@@
 
-$$u_i \sim N(0, \tau^2) $$ {#eq-10}
+$$u_i \sim N(0, \tau^2) $$
 
@@
 
-$$\epsilon_i \sim N(0, \sigma^2)$$ {#eq-11}
+$$\epsilon_i \sim N(0, \sigma^2)$$
 
@@
     \end{cases}
-\end{aligned}$$ {#eq-12}
+\end{aligned}$$
 
@@
 z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
-$$ {#eq-13}
+$$
 
@@
 
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials (*p* = `r results_met_sev$pval_between`).
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials.
 The statistics provided in Table 1 are baseline depression scores transformed to reflect percentage of a scale range.
@@
 range of 96).
-From Table 1, mean severity was `r results_met_sev$seTE_random[results_met_sev$subgroup == 1]` for psychotherapy studies and `r results_met_sev$seTE_random[results_met_sev$subgroup == 0]` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
-
-When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies (*p* = `r results_met_sev_cbt$pval_between`).
-This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression (*p* = `r results_met_sev_clin$pval_between`) or when excluding studies that used wait list as their control (*p* = `r results_met_sev_no_wl$pval_between`).
+From Table 1, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
+
+When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies.
+This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
+Please refer to Table XXXXX for these results.
+<!-- Charlotte, please point to the Supplementary Table where these results live -->
 
@@
 
-Psychotherapy trials featured a significantly higher percentage of women when compared to medication trials (`r results_met_perc_women_overall$pval_between`).
-On average, samples were comprised of `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1]` women across psychotherapy trials and `r results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0]`% (*SE* = `r results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0]`women across medication trials.
-Excluding sub-clinical (*p* = `results_met_perc_women_clin$pval_between`) and waitlist control studies (*p* = `results_met_perc_women_no_wl$pval_between`) yielded very similar results.
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (*p* = `results_met_perc_women_cbt$pval_between`).
+As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
+On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)` women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)` women across medication trials.
+Excluding sub-clinical and waitlist control studies yielded very similar results.
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included .
+<!-- Charlotte please refer to Supple Table -->
 
@@
 
-Mean age was `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 1]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 1]`) across psychotherapy trials and `r results_met_age$TE_random[results_met_perc_women_overall$subgroup == 0]` (*SE* = `r results_met_age$seTE_random[results_met_perc_women_overall$subgroup == 0]`) across medication trials, with no significant between group differences (*p* = `r results_met_age$pval_between`).
+As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
 
-df_overall_baseline_results <- options(knitr.kable.NA = "")
-
-```
-
-```{r, warning=FALSE, message = FALSE}
+#df_overall_baseline_results <- options(knitr.kable.NA = "") # CHARLOTTE THIS IS PROBABLY OFFENDING
+
+#df_overall_baseline_results 
+```
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+#df_overall_baseline_results
+
 df_overall_baseline_results %>%
@@
 
-Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 0]`, *SD* =`r`df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 0]`compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$mean_sites[df_sites_summary_stats$psy_or_med == 1]`, *SD* =`r df_sites_summary_stats$sd_sites[df_sites_summary_stats$psy_or_med == 1]`(*t* (`r sites_t_test$parameter`) = `r sites_t_test$statistic`, *p* =`r sites_t_test$p.value`).
-
-```{r, warning=FALSE, message = FALSE}
-
-df_sites_summary_stats %>%
-  kbl(caption = "Table X: Number of sites across medication and psychotherapy studies") %>% 
+There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
+Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`(*t* (`r sites_t_test$parameter`) = `r round(sites_t_test$statistic,2)`, *p* =`r round(sites_t_test$p.value,3)`).
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+
+df_sitest_summary_stats <- df_sites_summary_stats %>%
+  kbl(caption = " Number of sites across medication and psychotherapy studies") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 sites_t_test_stats %>%
-  kbl(align = "l", caption = "Table X: Results for t-test comparing number of sites between medication and psychotherapy studies") %>% 
+  kbl(align = "l", caption = "Results for t-test comparing number of sites between medication and psychotherapy studies") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` (see Table X).
+In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` (see Table 4 below).
 
@@
 
-![Figure 1.](plot_means_all.pdf)
-
-```{r, warning=FALSE, message = FALSE}
-
+![Figure 1.](plot_means_all.pdf){alt="Figure 1."}
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# df_mean_coefs_from_sim
 df_mean_coefs_from_sim %>%
-  kbl(align = "l", caption = "Table X: Summary statistics of the estimated SMDs") %>% 
+  kbl(align = "l", caption = " Summary statistics of the estimated SMDs") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 
-In Table X, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+In Table 5, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
 In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
@@
 
-```{r, warning=FALSE, message = FALSE}
-
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+#aggregate_results_overall
 aggregate_results_overall %>%
-  kbl(caption = "Table X: Meta-regression results") %>% 
+  kbl(caption = "Table 5: Meta-regression results") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 The total hours involved in an intervention were higher in active vs control arms (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`) though the total period of the intervention was similar (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`).
+<!-- Charlotte, we need to have all the t-values and dfs for the t-tests -->
+
+#######END HERE########
 
@@
 As can be seen in Table 3a and 3b, there baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
-As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
 

### 2024-03-20 Untitled.qmd
Updating untitled.qmd doc to fix some formatting problems. Playing around with rendering to see if I can get it to work in PDF.

@@
 author: "Stringaris et al"
-prefer-html: true
-format: docx
-editor: visual
+output:
+  quarto::pdf_document:
+    pandoc_args: --pdf-engine=pdflatex
 ---
@@
 
----
-
----
+------------------------------------------------------------------------
+
+------------------------------------------------------------------------
 
@@
 This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
-Please refer to Table XXXXX for these results.
-<!-- Charlotte, please point to the Supplementary Table where these results live -->
+Please refer to Table S1 for these results.
 
@@
 As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
-On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)` women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)` women across medication trials.
+On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`) women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`) women across medication trials.
 Excluding sub-clinical and waitlist control studies yielded very similar results.
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included .
-<!-- Charlotte please refer to Supple Table -->
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (see Table S2).
 
@@
 As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
-There were no significant differences in mean age between modalities on further sensitivity analyses.
+There were no significant differences in mean age between modalities on further sensitivity analyses (see Table S3).
 
@@
 ```{r, warning=FALSE, message = FALSE, echo = FALSE}
-#df_overall_baseline_results
 
 df_overall_baseline_results %>%
-  kbl(align = "l", caption = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
 
@@
 
-ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
-  geom_point(position = position_jitter(width = 0.2), size = 2) +
-  labs(title = "Number of Sites for Psychotherapy and Medication Trials",
-       x = "Treatment Modality",
-       y = "Number of Sites") +
-  scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
-
-```
-
+# ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
+#   geom_point(position = position_jitter(width = 0.2), size = 2) +
+#   labs(title = "Number of Sites for Psychotherapy and Medication Trials",
+#        x = "Treatment Modality",
+#        y = "Number of Sites") +
+#   scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
+
+```
 ### Number of trial sites
@@
 There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
-Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`(*t* (`r sites_t_test$parameter`) = `r round(sites_t_test$statistic,2)`, *p* =`r round(sites_t_test$p.value,3)`).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
-
-df_sitest_summary_stats <- df_sites_summary_stats %>%
-  kbl(caption = " Number of sites across medication and psychotherapy studies") %>%
+Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE, asis = TRUE }
+
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  kbl(caption = "Number of sites across medication and psychotherapy studies") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)`, 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`, whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` , 95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` (see Table 4 below).
+In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 4 below).
 
@@
 
-![Figure 1.](plot_means_all.pdf){alt="Figure 1."}
+![Figure 1.](plot_means_all.pdf)
 
@@
 # df_mean_coefs_from_sim
+
 df_mean_coefs_from_sim %>%
-  kbl(align = "l", caption = " Summary statistics of the estimated SMDs") %>%
+  kbl(align = "l", caption = "Summary statistics of the estimated SMDs") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 ```{r, warning=FALSE, message = FALSE, echo = FALSE}
+
 #aggregate_results_overall
 aggregate_results_overall %>%
-  kbl(caption = "Table 5: Meta-regression results") %>%
+  kbl(caption = "Meta-regression results") %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 # We need to read in the appropriate dataset which describes the active and control conditions used in
@@
 # For now lets look at variables pertaining to the nature / intensity of interventions
-
-colnames(df_descr_psy_conditions)
 
@@
 control_summary %>%
-  kbl(align = "l", caption = "Table X: Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
+  kbl(align = "l", caption = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
-```
-
-```{r, warning=FALSE, message = FALSE}
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 control_summary_t_tests %>%
-  kbl(align = "l", caption = "Table X: Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
+  kbl(align = "l", caption = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
@@
 
-Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see Table X for summary statistics).
-Active intervention arms featured significantly more sessions than control arms (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
-These sessions were also significantly longer (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`).
-The total hours involved in an intervention were higher in active vs control arms (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`) though the total period of the intervention was similar (*p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`).
-<!-- Charlotte, we need to have all the t-values and dfs for the t-tests -->
+Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see Table 6 for summary statistics).
+Active intervention arms featured significantly more sessions than control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
+These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Frequency (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`).
+The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`).
 
@@
 
-```{r, warning=FALSE, message = FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 df_severity_sens %>%
-  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  kbl(align = "l", caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 
-```{r, warning=FALSE, message = FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 df_gender_sens %>%
-  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  kbl(align = "l", caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
@@
 
-```{r, warning=FALSE, message = FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 df_age_sens %>%
-  kbl(align = "l", caption = "Table X: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  kbl(align = "l", caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%

### 2024-03-25 Untitled.qmd
Response rate calcualtion

@@
 author: "Stringaris et al"
-output:
-  quarto::pdf_document:
-    pandoc_args: --pdf-engine=pdflatex
+prefer-html: true
+format: docx
+editor: visual
 ---
@@
 
+# For response rate, recalculating after turning long and doing all the imputations
+
+# df_long_for_metan <- df_long_for_metan %>%
+#   rowwise() %>%
+#   mutate(responders = sum(rnorm(baseline_n, post_mean, 
+#                                 post_sd) < (baseline_mean/ 2)))
+# 
+# df_long_for_metan <- df_long_for_metan %>%
+#   rowwise() %>%
+#   mutate(resp_rate = responders/baseline_n)
+# 
+# summary_resp_rate <- df_long_for_metan %>%
+#   group_by(group) %>%
+#   summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
+#             sd_resp_rate = sd(resp_rate, na.rm = TRUE), 
+#             n = n())
+
 # save this as the master dataframe  --------------------------------------
@@
 #summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+df_long_for_metan <- df_long_for_metan %>%
+  rowwise() %>%
+  mutate(responders = sum(rnorm(baseline_n, post_mean, 
+                                post_sd) < (baseline_mean/ 2)))
+
+df_long_for_metan <- df_long_for_metan %>%
+  rowwise() %>%
+  mutate(resp_rate = responders/baseline_n)
+
+summary_resp_rate <- df_long_for_metan %>%
+  group_by(group) %>%
+  summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
+            sd_resp_rate = sd(resp_rate, na.rm = TRUE))
+
+test_summary <- df_with_distinct_instruments %>% 
+  group_by(psy_or_med) %>% 
+  summarise(rr_active = mean(resp_rate_active, na.rm = TRUE),
+            rr_control = mean(resp_rate_control, na.rm = TRUE),
+            n = n())
 
@@
 }
+
+# Filter out wl conditions
+df_descr_psy_conditions <- df_descr_psy_conditions %>% 
+  filter(new_study_id %in% no_wl_ids)
+
+# count_wl <- df_long_for_metan %>% 
+#   filter(treatment == "wlc") %>% 
+#   distinct(new_study_id) %>% 
+#   nrow()
+# 
+# count_cau <- df_long_for_metan %>% 
+#   filter(treatment == "cau") %>% 
+#   distinct(new_study_id) %>% 
+#   nrow()
 

### 2024-03-25 Untitled.qmd
Fixing up tables so that they render to word - using flextable

@@
 editor: visual
+font:
+  family: "Calibri"
 ---
@@
 library(kableExtra)
+library(flextable)
+library(magrittr)
+library(officer)
 ```
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-df_long_for_metan <- df_long_for_metan %>%
-  rowwise() %>%
-  mutate(responders = sum(rnorm(baseline_n, post_mean, 
-                                post_sd) < (baseline_mean/ 2)))
-
-df_long_for_metan <- df_long_for_metan %>%
-  rowwise() %>%
-  mutate(resp_rate = responders/baseline_n)
-
-summary_resp_rate <- df_long_for_metan %>%
-  group_by(group) %>%
-  summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
-            sd_resp_rate = sd(resp_rate, na.rm = TRUE))
-
-test_summary <- df_with_distinct_instruments %>% 
-  group_by(psy_or_med) %>% 
-  summarise(rr_active = mean(resp_rate_active, na.rm = TRUE),
-            rr_control = mean(resp_rate_control, na.rm = TRUE),
-            n = n())
-
-```
-
 # Results
@@
 
-```
-
-### Baseline severity
-
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials.
-The statistics provided in Table 1 are baseline depression scores transformed to reflect percentage of a scale range.
-To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
-range of 96).
-From Table 1, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
-
-When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies.
-This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
-Please refer to Table S1 for these results.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 # Now start looking at perc_women variable 
@@
 
-```
-
-### Gender
-
-As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
-On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`) women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`) women across medication trials.
-Excluding sub-clinical and waitlist control studies yielded very similar results.
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (see Table S2).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Now start looking at age variable
@@
 
-```
-
-### Age
-
-As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
-There were no significant differences in mean age between modalities on further sensitivity analyses (see Table S3).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 # Lets make a table that combines across these baseline characteristics variables
@@
   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3))
-
-colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
-
-#df_overall_baseline_results <- options(knitr.kable.NA = "") # CHARLOTTE THIS IS PROBABLY OFFENDING
-
-#df_overall_baseline_results 
-```
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
-
-df_overall_baseline_results %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
-  row_spec(row = 1, bold = T) %>%
-  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(1, border_right = T) %>%
-  add_indent(c(2, 3, 5, 6, 8, 9)) %>%
-  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+big_border = fp_border(color="black", width = 1)
+small_border = fp_border(color="lightgray", width = 1)
+
+# Create a flextable object
+flextable(df_overall_baseline_results) %>%
+  set_caption (autonum = TRUE, "Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  bold(part = "header") %>%  # Bold the header row
+  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  border_outer(border = small_border) %>%  # Add outer borders
+  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+  hline(part = "header", border = big_border) %>% 
+  vline(j = 1, border = big_border) %>% 
+  set_table_properties(width = .75) %>%  # Set table width
+  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+  autofit() %>%  # Autofit column widths
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+
+# This doesn't work when rendering to word doc
+#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
+#   row_spec(row = 1, bold = T) %>%
+#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+#   column_spec(1, border_right = T) %>%
+#   add_indent(c(2, 3, 5, 6, 8, 9))
+
+```
+
+### Baseline severity
+
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials.
+The statistics provided in Table 1 are baseline depression scores transformed to reflect percentage of a scale range.
+To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
+range of 96).
+From Table 1, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
+
+When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies.
+This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
+Please refer to Table S1 for these results.
+
+### Gender
+
+As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
+On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`) women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`) women across medication trials.
+Excluding sub-clinical and waitlist control studies yielded very similar results.
+This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (see Table S2).
+
+### Age
+
+As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+There were no significant differences in mean age between modalities on further sensitivity analyses (see Table S3).
+
+### Number of trial sites
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
+colnames(sites_t_test_stats) <- c("Statistic", "df", "p-value", "Lower CI", "Upper CI")
+
 # scatter plot
@@
 
-```
-### Number of trial sites
-
+# Create a flextable object
+
+flextable(df_sites_summary_stats) %>%
+  set_caption (autonum = TRUE, "Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
+  bold(part = "header") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "all", border = small_border) %>% 
+  hline(part = "header", border = big_border) %>% 
+  vline(j = 1, border = big_border) %>% 
+  set_table_properties(width = .75) %>% 
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  autofit() %>% 
+  font(fontname = "Calibri", part = "all") %>%   
+  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all")
+
+flextable(sites_t_test_stats) %>%
+  set_caption (autonum = TRUE, "Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
+  bold(part = "header") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "header", border = big_border) %>% 
+  set_table_properties(width = .75) %>% 
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  autofit() %>% 
+  font(fontname = "Calibri", part = "all") %>%   
+  align(align = "center", part = "all")
+
+# This is for if we want to render to pdf
+
+# df_sites_summary_stats <- df_sites_summary_stats %>%
+#   kbl(caption = "Number of sites across medication and psychotherapy studies") %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB") %>%
+#   column_spec(column = 1, border_right = T)
+
+# sites_t_test_stats %>%
+#   kbl(align = "l", caption = "Results for t-test comparing number of sites between medication and psychotherapy studies") %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB") %>%
+#   column_spec(column = 1, border_right = T)
+
+```
 There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
 Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE, asis = TRUE }
-
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  kbl(caption = "Number of sites across medication and psychotherapy studies") %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB") %>%
-  column_spec(column = 1, border_right = T)
-
-sites_t_test_stats %>%
-  kbl(align = "l", caption = "Results for t-test comparing number of sites between medication and psychotherapy studies") %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB") %>%
-  column_spec(column = 1, border_right = T)
-
-```
 
@@
 
+flextable(df_mean_coefs_from_sim) %>%
+  set_caption (autonum = TRUE, "Summary statistics of the estimated SMDs") %>%
+  bold(part = "header") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "header", border = big_border) %>% 
+  set_table_properties(width = .75) %>% 
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  autofit() %>% 
+  font(fontname = "Calibri", part = "all") %>%   
+  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center")
+
 ```
@@
 ![Figure 1.](plot_means_all.pdf)
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# df_mean_coefs_from_sim
-
-df_mean_coefs_from_sim %>%
-  kbl(align = "l", caption = "Summary statistics of the estimated SMDs") %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB") %>%
-  column_spec(column = 1, border_right = T)
-
-```
 
@@
 #aggregate_results_overall
-aggregate_results_overall %>%
-  kbl(caption = "Meta-regression results") %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB") %>%
-  column_spec(column = 1, border_right = T)
+flextable(aggregate_results_overall) %>%
+  set_caption (autonum = TRUE, "Metaregression results") %>%
+  bold(part = "header") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "header", border = big_border) %>% 
+  set_table_properties(width = .75) %>% 
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  autofit() %>% 
+  font(fontname = "Calibri", part = "all") %>%   
+  align(j = 2:ncol(aggregate_results_overall), align = "center")
 
@@
       result_dataframe <- rbind(result_dataframe,
-                                data.frame(Group = group,
-                                           Column = col, N = n, Mean = mean_val,
+                                data.frame(Column = col, Group = group, N = n, Mean = mean_val,
                                            SD = SD, Median = median_val,
@@
 control_summary <- control_summary %>% 
-  select(-c(Column, Median, IQR))
+  select(-c(Median, IQR))
 
@@
 control_summary <- control_summary %>%
+  mutate(Column = case_when(
+    Column == "no_sessions" ~ "Number of sessions",
+    Column == "freq_weeks" ~ "Frequency (weeks)",
+    Column == "length_sessions_mins" ~ "Session length (mins)",
+    Column == "total_hours" ~ "Total intervention hours",
+    Column == "total_period_weeks" ~ "Total intervention period (weeks)",
+    TRUE ~ as.character(Column)  # Keep original value if no match
+  ))
+
+control_summary <- control_summary %>% 
   mutate(across(where(is.numeric), ~round(., 2)))
 
-control_summary %>%
-  kbl(align = "l", caption = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-  column_spec(1, border_right = T) %>% 
-  pack_rows("Number of sessions", 1, 2) %>% 
-  pack_rows("Frequency (weeks)", 3, 4) %>% 
-  pack_rows("Session length (mins)", 5, 6) %>%
-  pack_rows("Total intervention hours", 7, 8) %>%
-  pack_rows("Total intervention period (weeks)", 9, 10)
+as_grouped_data(control_summary, groups = "Column") %>% 
+  as_flextable(hide_grouplabel = TRUE ) %>% 
+  set_caption (autonum = TRUE, "Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
+  bold(part = "header") %>%
+  bold(i = c(1, 4, 7, 10, 13), j = NULL, bold = TRUE, part = "body") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(i = c(3, 6, 9, 12), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+  hline(part = "header", border = big_border) %>% 
+  set_table_properties(width = 1) %>%  
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  font(fontname = "Calibri", part = "all")
 
@@
 
-colnames(df_overall_baseline_results)[8] <- paste0(colnames(df_overall_baseline_results)[8], footnote_marker_number(1))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-control_summary_t_tests %>%
-  kbl(align = "l", caption = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials") %>% 
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>% 
-  row_spec(row = 0, background = "#EBEBEB") %>% 
-  column_spec(column = 1, border_right = T)
+flextable(control_summary_t_tests) %>%
+  set_caption (autonum = TRUE, "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
+  bold(part = "header") %>%  
+  border_outer(border = small_border) %>%  
+  hline(part = "header", border = big_border) %>% 
+  set_table_properties(width = .75) %>% 
+  bg(bg = "#F2F2F2", part = "header") %>%  
+  autofit() %>% 
+  font(fontname = "Calibri", part = "all") %>%   
+  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all")
 
@@
 colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-df_severity_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  kbl(align = "l", caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-  row_spec(row = 1, bold = T) %>% 
-  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(1, border_right = T) %>% 
-  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# df_severity_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+#   kbl(align = "l", caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+#   row_spec(row = 1, bold = T) %>% 
+#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+#   column_spec(1, border_right = T) %>% 
+#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 # Now gender
@@
 colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-df_gender_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  kbl(align = "l", caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-  row_spec(row = 1, bold = T) %>% 
-  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(1, border_right = T) %>% 
-  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# df_gender_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+#   kbl(align = "l", caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+#   row_spec(row = 1, bold = T) %>% 
+#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+#   column_spec(1, border_right = T) %>% 
+#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
 ```
@@
 colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-df_age_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  kbl(align = "l", caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
-  kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-  row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-  row_spec(row = 1, bold = T) %>% 
-  row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-  column_spec(1, border_right = T) %>% 
-  add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-  footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# df_age_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+#   kbl(align = "l", caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
+#   row_spec(row = 1, bold = T) %>% 
+#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+#   column_spec(1, border_right = T) %>% 
+#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
+#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+
 ```

### 2024-03-26 Untitled.qmd
Added references

@@
 editor: visual
+bibliography: "emotion_concepts_paper.bib"
 font:
@@
 
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+###########Libraries needed
+library(tidyverse)
+library(truncnorm)
+library(metafor)
+library(meta)
+library(kableExtra)
+library(flextable)
+library(magrittr)
+library(officer)
+library(RefManageR)
+
+# For referencing
+bib_data <- ReadBib("emotion_concepts_paper.bib")
+
+```
 # Introduction
@@
 Guidelines, such as the ones that the internationally influential UK National Institute of Clinical Excellence (NICE) have produced for adolescent depression, are a principal source of such information.
-NICE recommend that youth be first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression.
+NICE recommend that youth be first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
 This conclusion is in keeping with two sources of evidence.
-On the one hand, medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine (ref); and on the other hand, psychotherapy meta-analyses that conclude psychotherapy to be effective for adolescent depression (ref).
-However, such conclusions seem at odds with those of a recent network meta-analysis (ref), an established method of comparing treatments with each other using both direct (head-to-head) and indirect (indirectly treatment A with treatment C, via studies that directly compare treatments A with B and B with C) evidence.
+On the one hand, medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and on the other hand, psychotherapy meta-analyses that conclude psychotherapy to be effective for adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
+However, such conclusions seem at odds with those of a recent network meta-analysis [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments with each other using both direct (head-to-head) and indirect (indirectly treatment A with treatment C, via studies that directly compare treatments A with B and B with C) evidence.
 Indeed, the network meta-analysis concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than pill placebo or psychological controls.
@@
 In terms of the second point, differences in trial design may impact outcomes in a differential way between antidepressant and psychotherapy trials.
-Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation; by contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation (cite: Assessment of blinding in randomized controlled trials of antidepressants for depressive disorders 2000−2020: A systematic review and meta-analysis, Lancet).
+Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation; by contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation [@linAssessmentBlindingRandomized2022].
 This creates differential expectations between medication and psychotherapy trials.
@@
 Please refer to these original meta-analyses for a detailed description of study selection criteria.
-Psychotherapy studies were drawn from Cuijpers' (2023) systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions.
-Cuijpers made available a full dataset of psychotherapy trials (via https://www.metapsy.org/), which we used for the current study.
-Whilst Cuijpers (2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to Cuijpers' (2023) meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuipers' (2023) literature search.
-
-Medication studies were drawn from Cipriani's (2016) network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in young people.
+Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021].
+Cuijpers et al.
+made available a full dataset of psychotherapy trials (via https://www.metapsy.org/), which we used for the current study.
+Whilst Cuijpers et al.
+(2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to the first meta-analysis.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuipers et al.'s (2023) literature search.
+
+Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in young people [@ciprianiComparativeEfficacyTolerability2016].
 The study dataset was made available online though did not include means or standard deviations at baseline or post-test.
@@
 Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive any responses.
-We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers' (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
-We used the same search terms outlined in Cipriani (2016).
+
+We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review (May 31 2015 up to Jan 1 2021) to ensure we analysed an equivalently up-to-date database of medication trials.
+We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
+We also searched trial registers for published and unpublished studies.
+We used the same search strategy as Cipriani (2016) with an additional search term to include only placebo-controlled trials (see Supplement X for further details).
+We used Covidence, an online software tool, to manage our systematic review.
+In total, our search produced 538 studies, 85 of which were duplicates and subsequently removed.
+Two study authors independently completed title and abstract screenings for 453 studies, and full text screening for 41 studies.
+X studies met inclusion criteria and data extraction was completed for these papers.
 
@@
 We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including gender, age, and severity of depressive symptoms at baseline.
-Meta-analyses were implemented using R's meta package.
+Meta-analyses were implemented using R's Meta package.
 
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following NOTE: Charlotte cite Lakens 2013 and in there Cummings 2012, as:
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as:
 
@@
 where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised by X (citation), in the following order.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
 If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
@@
 If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis (citation).
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis.
 
@@
 
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives (NOTE: **Charlotte**cite Ioannides on this).
+We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
 
@@
 Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-###########Libraries needed
-library(tidyverse)
-library(truncnorm)
-library(metafor)
-library(meta)
-library(kableExtra)
-library(flextable)
-library(magrittr)
-library(officer)
-```
 
@@
 
-### Supplement
+# Supplement
 
@@
   theme(legend.position = "none")
-
-```
+```

### 2024-03-27 Untitled.qmd
Cleaned and read in data from additional trials from systematic review

@@
 title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
-author: "Stringaris et al"
+author:
+  - name: Argyris Stringaris
+    email: a.stringaris@ucl.ac.uk
+    affiliations: 
+        - id: ucl_1
+          name: University College London
+          department: Divisions of Psychiatry and Psychology and Language Science
+          address: 1-19 Torrington Place
+          city: London, UK
+          state: 
+          postal-code: WC1E 7HB
+          country: United Kingdom
+    attributes:
+        corresponding: true
+    note: 
+  - name: Charlotte Burman
+    email: charlotte.burman@ucl.ac.uk
+    affiliations:
+        - ref: ucl_1
+    note:
+  - name: Dayna Bhudia
+    email: dayna.bhudia@ucl.ac.uk
+    affiliations:
+        - ref: ucl_1
+  - name: Despina Miliou
+    email: dgmiliou@outlook.com.gr
+    affiliations:
+        - ref: ucl_1
+  - name: Giannis Rokas
+    email: <rokasgiannis93@gmail.com
+    affiliations:
+        - ref: ucl_1
+  - name: Lucy Foulkes
+    email: lucy.foulkes@psych.ox.ac.uk
+    affiliations:
+        - id: OU
+          name: University of Oxford
+          department: Experimental Psychology
+          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
+          city: Oxford
+          postal-code: OX2 6GG
+          country: United Kingdom
+    note:
+  - name: Carmen Moreno
+    email: cmoreno@hggm.es
+    affiliations:
+        - id: HGM
+          name: Hospital Gregorio Marañón
+          department: Department of Psychiatry
+          address: 46 C. del Dr. Esquerdo
+          city: Madrid
+          state:
+          postal-code: 28007
+          country: Spain
+  - name: Samuele Cortese
+    email: samuele.cortese@soton.ac.uk
+    affiliations:
+        - id: soton
+          name: University of Southampton
+          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
+          address: Highfield Campus, Building 44
+          city: Southampton
+          state:
+          postal-code: SO17 1BJ
+          country: United Kingdom
+  - name: Georgina Krebs
+    email: g.krebs@ucl.ac.uk
+    affiliations:
+        - ref: ucl_1
+    note:
+keywords: 
+  - depression
+  - adolescents
+  - antidepressants
+  - psychotherapy
+date: last-modified
 prefer-html: true
@@
 ```
+
 # Introduction
@@
 This assumption may be hard to meet.
-Clinical experience and empirical evidence (ref: (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156137/>, <https://www.ncbi.nlm.nih.gov/pmc/articles/PMC7669695/#:~:text=Adolescents%20also%20may%20be%20more,medications%2C%20and%20fewer%20anxiety%20symptoms.> , <https://pubmed.ncbi.nlm.nih.gov/16502131/>) indicate that patients and parents often have preferences between psychotherapy and medication, meaning that there is likely to be a self- %\>% ion bias with respect to who participates in psychotherapy versus medication trials.
+Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication[@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
 Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
-Some of these characteristics, particularly baseline severity, may moderate treatment response (ref) and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
+Some of these characteristics, particularly baseline severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
 
@@
 An inter-related issue concerns the nature of control interventions being used.
-Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al) to the intervention: what would have been the outcome in an individual had they not received the intervention.
+Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al: **Argyris** how's this?
+https://us.sagepub.com/sites/default/files/upm-assets/62640_book_item_62640.pdf) to the intervention: what would have been the outcome in an individual had they not received the intervention.
 This implies that there is a latent distribution of values that represent that counterfactual condition which control arms in trials are meant to approximate.
@@
 Third, we examine the quality of psychotherapy controls as such, by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
-
-@stringarisDevelopmentalPathwaysChildhood2014
 
@@
 for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences.
-Full results for each of the sensitivity analyses are included in the Supplementary Materials (Table X - Y).
+Full results for each of the sensitivity analyses are included in the Supplementary Materials (Tables S1 - S3).
 
@@
 # Create a flextable object
+
 flextable(df_overall_baseline_results) %>%
-  set_caption (autonum = TRUE, "Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
   bold(part = "header") %>%  # Bold the header row
@@
 flextable(df_sites_summary_stats) %>%
-  set_caption (autonum = TRUE, "Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
+  set_caption ("Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
   bold(part = "header") %>%  
@@
 flextable(sites_t_test_stats) %>%
-  set_caption (autonum = TRUE, "Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
+  set_caption ("Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
   bold(part = "header") %>%  
@@
 ```
+
 There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
@@
 
-#### Mean efficacy of psychotherapy versus medication control conditions
+## Mean efficacy of psychotherapy versus medication control conditions
 
@@
 flextable(df_mean_coefs_from_sim) %>%
-  set_caption (autonum = TRUE, "Summary statistics of the estimated SMDs") %>%
+  set_caption ("Summary statistics of the estimated SMDs") %>%
   bold(part = "header") %>%  
@@
 #aggregate_results_overall
+
 flextable(aggregate_results_overall) %>%
-  set_caption (autonum = TRUE, "Metaregression results") %>%
+  set_caption ("Metaregression results") %>%
   bold(part = "header") %>%  
@@
 
-### Comparing the nature and intensity of control conditions in psychotherapy trials
+## Comparing the nature and intensity of control conditions in psychotherapy trials
 
@@
   as_flextable(hide_grouplabel = TRUE ) %>% 
-  set_caption (autonum = TRUE, "Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
+  set_caption ("Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
   bold(part = "header") %>%
@@
 flextable(control_summary_t_tests) %>%
-  set_caption (autonum = TRUE, "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
+  set_caption ("Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
   bold(part = "header") %>%  
@@
 
-colnames(df_severity_sens)[8] <- paste0(colnames(df_severity_sens)[8], footnote_marker_number(1))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# df_severity_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-#   kbl(align = "l", caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials", escape = F) %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-#   row_spec(row = 1, bold = T) %>% 
-#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-#   column_spec(1, border_right = T) %>% 
-#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+df_severity_sens %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+flextable(df_severity_sens) %>%
+  set_caption(caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials") %>%
+  bold(part = "header") %>%  # Bold the header row
+  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  border_outer(border = small_border) %>%  # Add outer borders
+  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+  hline(part = "header", border = big_border) %>% 
+  vline(j = 1, border = big_border) %>% 
+  set_table_properties(width = .75) %>%  # Set table width
+  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+  autofit() %>%  # Autofit column widths
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
 
@@
 
-colnames(df_gender_sens)[8] <- paste0(colnames(df_gender_sens)[8], footnote_marker_number(1))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# df_gender_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-#   kbl(align = "l", caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials", escape = F) %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-#   row_spec(row = 1, bold = T) %>% 
-#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-#   column_spec(1, border_right = T) %>% 
-#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+df_gender_sens %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+flextable(df_gender_sens) %>%
+  set_caption(caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials") %>%
+  bold(part = "header") %>%  # Bold the header row
+  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  border_outer(border = small_border) %>%  # Add outer borders
+  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+  hline(part = "header", border = big_border) %>% 
+  vline(j = 1, border = big_border) %>% 
+  set_table_properties(width = .75) %>%  # Set table width
+  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+  autofit() %>%  # Autofit column widths
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+
 # Now age
@@
 
-colnames(df_age_sens)[8] <- paste0(colnames(df_age_sens)[8], footnote_marker_number(1))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# df_age_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-#   kbl(align = "l", caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials", escape = F) %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>% 
-#   row_spec(row = 1, bold = T) %>% 
-#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-#   column_spec(1, border_right = T) %>% 
-#   add_indent(c(2, 3, 5, 6, 8, 9)) %>% 
-#   footnote(number = c("Statistic derived from the test for subgroup differences in the relevant meta-analysis"))
+df_age_sens %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+flextable(df_age_sens) %>%
+  set_caption(caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials") %>%
+  bold(part = "header") %>%  # Bold the header row
+  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  border_outer(border = small_border) %>%  # Add outer borders
+  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+  hline(part = "header", border = big_border) %>% 
+  vline(j = 1, border = big_border) %>% 
+  set_table_properties(width = .75) %>%  # Set table width
+  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+  autofit() %>%  # Autofit column widths
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
 
@@
 
-# Scatter plot cohens d per arm
-
-ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-  geom_point(position = position_jitter(width = 0.2), size = 3) +
-  geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-  geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-  scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-  theme_minimal() +
-  theme(legend.position = "none")
+# # Scatter plot cohens d per arm
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
 
@@
 
-# Plot percentage baseline means
-
-ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
-  geom_point(position = position_jitter(width = 0.2), size = 3) +
-  scale_color_manual(values = group_colors) +
-  labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
-  theme_minimal() +
-  theme(legend.position = "none")
+# # Plot percentage baseline means
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
+#   geom_point(position = position_jitter(width = 0.2), size = 3) +
+#   scale_color_manual(values = group_colors) +
+#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
+
 ```

### 2024-03-27 Script for cleaning medication data.R

@@ -1,5 +1,6 @@
 # script for cleaning medication data
 # open working_dataset_medication
+
 library(readxl)
 library(tidyverse)
 

### 2024-04-08 Manuscript_for_rendering_in_word.qmd
Discussion added - still need to finalise citations

--- 2024-03-27 Untitled.qmd
@@
 This assumption may be hard to meet.
-Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication[@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
+Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
 Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
@@
 Another difference in design that has potential implications for which patients are selected into the trial is the number of sites in a trial.
-Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response.
+Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response [@bridgePlaceboResponseRandomized2009].
 This phenomenon is hard to explain fully with the data available, but may be due to lower quality of phenotyping in such studies, with higher measurement (and therefore diagnostic classification) errors, leading to issues such as spontaneous remission or regression to the mean.
@@
 If the average response to placebo and psychotherapy controls differs systematically from each other, then this is either due to the fact that the trials sample from different populations or because the control conditions differ in their effects (e.g.
-because of how much they do or do not protect against expectancy effects).
+because of how much they do or do not protect against expectancy effects), or both.
 
@@
 In total, our search produced 538 studies, 85 of which were duplicates and subsequently removed.
-Two study authors independently completed title and abstract screenings for 453 studies, and full text screening for 41 studies.
-X studies met inclusion criteria and data extraction was completed for these papers.
+Two study authors independently completed title and abstract screenings for 450 studies, and full text screening for 38 studies.
+7 studies met inclusion criteria and data extraction was completed for these papers.
 
@@
 Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD was missing and could not be imputed by any of the methods outlined above.
+There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD were missing and could not be imputed by any of the methods outlined above.
 
 Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
-In psychological trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
+In psychotherapy trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
 All included trials and the types of treatment controls can be found in Supplementary Table 1.
@@
 
-When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, there was a significant difference between psychotherapy and medication studies.
+When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, baseline severity remained significantly higher in medication versus psychotherapy studies.
 This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
@@
 There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
-Average number of trial sites was significantly higher across medication studies ( *M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies ( *M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).
+Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r round(sites_t_test$p.value, 3`).
 
@@
 
+# Discussion
+
+This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression.
+In order to address this question, we asked whether the two treatment modalities — medication and psychotherapy — are comparable on the basis of the existing evidence.
+Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two treatment modalities.
+
+First, whether the participants of trials in one modality are comparable to those in another modality.
+Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved in a trial, are comparable.
+
+Starting with the first question, we find evidence that participants in the two treatment modalities differ in the following key aspects: those enrolled in medication trials are more likely to be male and have more severe depression compared to those in psychotherapy trials.
+By contrast, there were no significant differences in age.
+
+Severity is important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to placebo response is lower [@bridgePlaceboResponseRandomized2009].
+Some studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g.
+within CBT studies),  i.e.
+within those people who have chosen to be in the particular trial and modality.
+Moreover, there is evidence that severity may represent different subtypes in terms of course of depression and its outcomes in real life settings [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
+
+Similarly, we found that on average there were about 7% more women in psychotherapy trials.
+Whilst there is little evidence that sex or gender moderate treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
+
+We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We find a series of critical differences between the two modalities.
+
+First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts—CITE PROBABILITIES.
+Multisite trials are associated with higher placebo response [@bridgePlaceboResponseRandomized2009], and are less common in NIH-funded (i.e.
+non industry trials) which are also more likely to show higher placebo efficacy.
+Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where primacy is given to the number of recruited participants which is the primary unit of reimbursement.
+
+Second, the control conditions of psychotherapy trials are much weaker than those of their medication counterparts.
+Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally advised against (CITE).
+This criticism would apply if our aim were to draw inferences about the efficacy of each arm — in which case preserving the randomization (in order to balance confounders) is critical.
+However, we note that, our findings are largely in keeping with those of the network metanalysis, which is designed to preserve the randomization structure.
+More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because of the fact that the people who attend psychotherapy and medication trials are different and therefore respond differently.
+In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison between the two modalities.
+This is all the more so as clinicians as well as policy makers often resort to effect sizes to summarise findings, with SMD being the one used as per standard.
+Our findings make obvious that comparing treatment modalities based on the effect size of each modality is misleading.
+
+Moving beyond the comparison of the controls between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment.
+An optimal control condition is one where the treatment differs (e.g.
+treatment vs no treatment), but everything else is equal (in technical terms, the ceteris paribus assumption).
+An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind).
+Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the “all else is equal” assumption.
+Most (XXX %) of psychotherapy RCT control conditions are either waitlist control or treatment as usual, both of which are very likely to create negative expectations for participants not randomized to treatment; thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
+But we also find that even psychological controls were unreasonable counterfactuals.
+In order to test that a psychological treatment is effective per se (e.g.
+because of the cognitive techniques the therapist deploys) rather than because of generic effects (e.g.
+pleasant human contact), aspects such as human contact time should be matched.
+We find that there are vast differences between treatment and control arms in psychotherapy trials (CITE NUMBER) which may lead to an inflation of the true efficacy of psychological treatments.
+
+Given all of the above, the certainty with which guidelines, including UK’s NICE recommend psychotherapy over medication for adolescent depression is surprising.
+Indeed, we believe that our findings have a number of profound implications for patients, their families, clinicians and policy makers and we list these below.
+
+First, the grounds for a comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is an urgent need to revisit guidelines and public information in light of the limitations.
+
+Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of how these studies are appraised and what needs to be done to create fair and realistic comparators.
+Indeed, investment of effort and funds should be directed into providing rigorous evidence that established depression psychotherapies are more efficacious than fair controls.
+There are examples of child psychological therapies, e.g.
+in social anxiety (CITE David Clark’s comparisons with behavioural interventions) where such rigor has been applied.
+
+Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials (CITE Sam and Andrea’s paper).
+The first obstacle is the comparability of the populations taking part.
+Even if a trial were designed to conduct a head-to-head comparison of psychotherapy with medication (as has been done CITE), it might sample the population of those who are indifferent to which one they would receive.
+And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
+
+In summary, our data give cause for consternation about the state of the evidence of youth depression, one of the most common and debilitating disorders in young people.
+Our data question the state of knowledge about the efficacy of youth psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
+Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choice than currently exists.
+
 # Supplement

### 2024-04-09 Manuscript_for_rendering_in_word.qmd
Finished discussion referencing

@@
 Indeed, investment of effort and funds should be directed into providing rigorous evidence that established depression psychotherapies are more efficacious than fair controls.
-There are examples of child psychological therapies, e.g.
-in social anxiety (CITE David Clark’s comparisons with behavioural interventions) where such rigor has been applied.
-
-Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials (CITE Sam and Andrea’s paper).
+There are examples of such psychotherapy RCTS, e.g.
+in social anxiety [@clarkCognitiveTherapyExposure2006a] where such rigor has been applied.
+
+Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
 The first obstacle is the comparability of the populations taking part.
-Even if a trial were designed to conduct a head-to-head comparison of psychotherapy with medication (as has been done CITE), it might sample the population of those who are indifferent to which one they would receive.
+Even if a trial were designed to conduct a head-to-head comparison of psychotherapy with medication (as has been done in [@FluoxetineCognitiveBehavioralTherapy2004]), it might sample the population of those who are indifferent to which one they would receive.
 And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.

### 2024-04-09 Manuscript_for_rendering_in_word.qmd
Few small things

@@
 
+df_for_gender_metan <- df_for_gender_metan %>% 
+  filter(percent_women != 100)
+
 met_perc_women_overall <- metagen(TE = percent_women,
@@
 
+For this analysis, we excluded the two psychotherapy trials which included entirely female samples.
 As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
@@
   filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
+
+# Now create binary variable, single or multi site trial
+
+df_baseline_demographics <- df_baseline_demographics %>% 
+  mutate(site_binary = case_when(sites == 1 ~ "single", 
+                                 sites > 1 ~ "multi",
+                                 TRUE ~ NA_character_))
+
+df_baseline_demographics %>%
+  group_by(psy_or_med, site_binary) %>%
+  summarize(num_trials = n())
 
@@
 Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r round(sites_t_test$p.value, 3`).
+Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 

### 2024-04-12 Manuscript_for_rendering_in_word.qmd
Test

@@
 library(RefManageR)
+library(gt)
+library(officer)
+library(officedown)
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-library(tidyverse)
+
 # Transforming data ------------------------------------------------------
@@
 # Get Ns, run metareg, prepare graphing ------------------------------------------------------
-library(tidyverse)
-library(metafor)
 
@@
 
-# Create a flextable object
-
-flextable(df_overall_baseline_results) %>%
+# knitr:: kable(df_overall_baseline_results, caption="Sample characteristics at baseline across medication and psychotherapy studies")
+# 
+# gt(df_overall_baseline_results) %>% 
+#   tab_header(
+#     title = md("Test this"),
+#     subtitle = md("And this"))
+
+# This doesn't work when rendering to word doc
+#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
+#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
+#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
+#   row_spec(row = 1, bold = T) %>%
+#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
+#   column_spec(1, border_right = T) %>%
+#   add_indent(c(2, 3, 5, 6, 8, 9))
+
+```
+
+```{r, echo=FALSE}
+
+#| label: tbl-flextable
+#| tbl-cap: Caption **strong**
+flextable:: flextable(df_overall_baseline_results) %>%
   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
@@
 
-# This doesn't work when rendering to word doc
-#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
-#   row_spec(row = 1, bold = T) %>%
-#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-#   column_spec(1, border_right = T) %>%
-#   add_indent(c(2, 3, 5, 6, 8, 9))
-
 ```
@@
 
-### Number of trial sites
+## Number of trial sites
 
@@
 
-df_baseline_demographics %>%
-  group_by(psy_or_med, site_binary) %>%
-  summarize(num_trials = n())
+# df_baseline_demographics %>%
+#   group_by(psy_or_med, site_binary) %>%
+#   summarize(num_trials = n())
 
@@
 flextable(df_sites_summary_stats) %>%
-  set_caption ("Number of sites across medication and psychotherapy studies", style = "Table Caption") %>%
+  set_caption ("Number of sites across medication and psychotherapy studies") %>%
   bold(part = "header") %>%
@@
 There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
-Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r round(sites_t_test$p.value, 3`).
+Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).
 Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 
-## Mean efficacy of psychotherapy versus medication control conditions
+## Mean efficacy of control conditions in psychotherapy versus medication studies
 
@@
 # knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+```
+
+```{r, eval=FALSE} 
+#### Let's start from the beginning and regress cohens on the baseline dataframe.
+
+# create a new list with dfs for the sims
+df_long_for_metan_adj_cohens_d <- df_long_for_metan
+# rename the cohens_d value to make space for the new cohen's d
+df_long_for_metan_adj_cohens_d <-
+  df_long_for_metan_adj_cohens_d %>%
+rename(unadjusted_cohens_d = cohens_d,
+)
+# estimate the cohen's d from the residuals
+model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
+
+# there is a great effect of the baseline means, as shown here
+results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
+
+# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
+df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
+
+# apply function to simulate standard errors
+list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
+                                   num_repetitions = 1000,
+                                   seed  = 1974,
+                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
+                                   a = 0.45,
+                                   b = .9,
+                                   mean = 0.65,
+                                   sd = 0.2)
+
+# add the four level variable and re-level
+for(i in 1: length(list_df_simulated_adj_cohens_d)){
+
+  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
+  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
+                                                         "medication_control",
+                                                         "medication_active",
+                                                         "psychotherapy_control",
+                                                         "psychotherapy_active")
+}
+
+# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
+# specify model
+model_1 <- as.formula(~ four_level_var)
+
+# run metareg function
+# here you can use the simulated results directly
+list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
+aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
+aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
+
+# extract SMDs from the  list
+list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
+
+df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+
+results_adjusted_cohens_d
+
 ```
@@
 
-Tables 6a and 6b show the baeline-mean adjusted SMDs for the CDRS at outcome when the baseline measurement has been taken into account.
+Tables 6a and 6b show the baseline-mean adjusted SMDs for the CDRS at outcome when the baseline measurement has been taken into account.
 <!--# Here Intercept refers to teh psychotherapy control.

### 2024-04-12 Manuscript_for_rendering_in_word.qmd
Trying to fix issue with tables, trying different packages, still running into problems

@@
 date: last-modified
-prefer-html: true
+
 format: docx
@@
 library(RefManageR)
-library(gt)
-library(officer)
-library(officedown)
 
@@
 
+# Too basic, limited formatting options
+# 
 # knitr:: kable(df_overall_baseline_results, caption="Sample characteristics at baseline across medication and psychotherapy studies")
@@
 #     subtitle = md("And this"))
-
+# 
 # This doesn't work when rendering to word doc
+# 
 #   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
@@
 #   add_indent(c(2, 3, 5, 6, 8, 9))
-
-```
-
-```{r, echo=FALSE}
-
-#| label: tbl-flextable
-#| tbl-cap: Caption **strong**
-flextable:: flextable(df_overall_baseline_results) %>%
+# 
+# this doesn't have a caption when rendering to word
+
+flextable(df_overall_baseline_results) %>%
   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
@@
 
+# this doesn't work either
+#
+# table_sample_result <- flextable(df_overall_baseline_results) %>%
+#   bold(part = "header") %>%  # Bold the header row
+#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+#   border_outer(border = small_border) %>%  # Add outer borders
+#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>%
+#   hline(part = "header", border = big_border) %>%
+#   vline(j = 1, border = big_border) %>%
+#   set_table_properties(width = .75) %>%  # Set table width
+#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+#   autofit() %>%  # Autofit column widths
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>%
+#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+# 
+# table_sample_result <- set_caption(table_sample_result, caption = "Testing")
+# 
+# table_sample_result
+
+```
+
+```{r}
+#| label: tbl-flextable
+#| tbl-cap: "Testing"
+flextable::flextable(df_overall_baseline_results)
+# the caption isn't working here either
 ```
@@
 pdf(file = "plot_means_all.pdf")
-plot_means_all
+# Instead of PDF
+png(file = "plot_means_all.png")
+dev.off()
 
@@
 
-![Figure 1.](plot_means_all.pdf)
+![Figure 1.](plot_means_all.png)
 
@@
 
-```{r, eval=FALSE} 
+```{r, echo = FALSE}
 #### Let's start from the beginning and regress cohens on the baseline dataframe.
@@
 This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression.
-In order to address this question, we asked whether the two treatment modalities — medication and psychotherapy — are comparable on the basis of the existing evidence.
+In order to address this question, we asked whether the two treatment modalities --- medication and psychotherapy --- are comparable on the basis of the existing evidence.
 Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two treatment modalities.
@@
 
-First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts—CITE PROBABILITIES.
+First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts---CITE PROBABILITIES.
 Multisite trials are associated with higher placebo response [@bridgePlaceboResponseRandomized2009], and are less common in NIH-funded (i.e.
@@
 Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally advised against (CITE).
-This criticism would apply if our aim were to draw inferences about the efficacy of each arm — in which case preserving the randomization (in order to balance confounders) is critical.
+This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical.
 However, we note that, our findings are largely in keeping with those of the network metanalysis, which is designed to preserve the randomization structure.
@@
 An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind).
-Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the “all else is equal” assumption.
+Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption.
 Most (XXX %) of psychotherapy RCT control conditions are either waitlist control or treatment as usual, both of which are very likely to create negative expectations for participants not randomized to treatment; thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
@@
 
-Given all of the above, the certainty with which guidelines, including UK’s NICE recommend psychotherapy over medication for adolescent depression is surprising.
+Given all of the above, the certainty with which guidelines, including UK's NICE recommend psychotherapy over medication for adolescent depression is surprising.
 Indeed, we believe that our findings have a number of profound implications for patients, their families, clinicians and policy makers and we list these below.

### 2024-04-18 Manuscript_for_rendering_in_word.qmd
Implementing feedback from co-authors and Argyris

@@
 ---
-title: "Fundamental Problems with the Evidence Base of Adolescent Depression Treatments"
+title: "Fundamental Problems with Child and Adolecsent Depression Treatments: A Quantitative Reappraisal of the Evidence Base"
 author:
@@
 library(RefManageR)
+library(ftExtra)
 
@@
 
-There are two principal treatment modalities for adolescent depression: psychotherapy, medication, or both.
+There are two principal treatment modalities for adolescent depression: psychotherapy and medication.
 Where does one turn to find the evidence that will inform their treatment options?
-This question is relevant for patients and their carers, for clinicians and for policy makers when they plan services.
+This question is relevant for patients and their carers, for clinicians and for policy makers.
 However, the question is particularly difficult to answer for adolescent depression, where there are limited data from head-to-head trials of medication and psychotherapy, and where recommendations must therefore be derived from indirect comparisons of treatment efficacy.
 
-Guidelines, such as the ones that the internationally influential UK National Institute of Clinical Excellence (NICE) have produced for adolescent depression, are a principal source of such information.
-NICE recommend that youth be first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
-This conclusion is in keeping with two sources of evidence.
-On the one hand, medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and on the other hand, psychotherapy meta-analyses that conclude psychotherapy to be effective for adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
+Guidelines, such as the ones that the internationally influential UK National Institute of Health and Care Excellence (NICE) have produced for adolescent depression, are a principal source of such information.
+NICE recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
+This conclusion is in keeping with two sources of evidence: medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine, for child and adolescent depression [@ciprianiComparativeEfficacyTolerability2016]; and psychotherapy meta-analyses that conclude psychotherapy to be efficacious for child and adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
 However, such conclusions seem at odds with those of a recent network meta-analysis [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments with each other using both direct (head-to-head) and indirect (indirectly treatment A with treatment C, via studies that directly compare treatments A with B and B with C) evidence.
-Indeed, the network meta-analysis concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than pill placebo or psychological controls.
-Given this confusing evidence base, how should patients, carers, clinicians and policy makers make decisions on treatment options for adolescent depression?
+Indeed, the network meta-analysis concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
+pill placebo) or psychotherapy controls.
+Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions for adolescent depression?
 
 In this paper, we examine whether the existing evidence base for adolescent depression treatment can offer valid answers to such questions.
-Below, we provide a conceptual framework for answering such questions and state our hypotheses that we will test using data from existing trials.
-Two points are relevant to indirect comparisons of treatment modalities with each other.
+Below, we provide a conceptual framework for answering such questions and test a series of hypotheses using data from existing trials.
+Two points are crucial to indirect comparisons of treatment modalities with each other.
 
@@
 Starting with the first point, to be able to compare between different trials one must assume that these trials sample from the same population.
-If they do not, then the validity of any comparisons, including those conducted through network metanalysis (which rests on the principal of transitivity) are questionable.
+If they do not, then the validity of any comparisons, including those conducted through network metanalysis (which rests on the principal of transitivity, i.e.
+the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable (we provide a more formal account of this in the Supplement).
 
@@
 
-This assumption may be hard to meet.
+This assumption, that medication and psychotherapy trials sample from the same population, may be hard to meet.
 Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
-Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, gender and comorbidity.
+Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, sex and comorbidity.
 Some of these characteristics, particularly baseline severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
 
-Here we will compare between four key sample characteristics, namely baseline severity in the outcome, number of sites, gender and age in each sample.
-
-In terms of the second point, differences in trial design may impact outcomes in a differential way between antidepressant and psychotherapy trials.
-Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation; by contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation [@linAssessmentBlindingRandomized2022].
+In terms of the second point, differences in trial design may impact outcomes in a differential way between antidepressant and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
+Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
+By contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation [@linAssessmentBlindingRandomized2022].
 This creates differential expectations between medication and psychotherapy trials.
-Importantly, the placebo control has been developed in order to match as closely as possible the intervention condition, so as to minimise differences in expectancy between conditions.
+Importantly, pill-placebo has been developed as the standard medication control in order to match as closely as possible the intervention condition, so as to minimise differences in expectancy between conditions.
 By contrast, psychotherapy control arms vary across waitlist controls, treatment as usual and active controls.
-These differences in expectation essentially favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially the difference between them), because participants in the active condition could be content for receiving the "cutting edge treatment" whilst those in the control will be dissatisfied for having missed out on "proper treatment".
-And this is important because expectancy is associated with treatment outcomes.
-This also poses problems when trying to infer indirect comparisons in network metanalyses where, for example, CBT is compared to placebo control and medication --- given the likely differential expectation effects, comparisons to the unblinded psychotherapy controls may be biased.
+These differences in expectation favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially magnifying the difference between them).
+This is because of what has been aptly described as "disappointment bias" [@thespininvestigatorsEthicsTrialsCohorts2017], where participants in the active condition are content for receiving the "cutting edge treatment" whilst those in the control are dissatisfied for having missed out on "proper treatment".
+Expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011]; i.e., it is an effect modifier.
+If expectancy effects are different for psychotherapy controls and pill placebo, comparisons between them, including in network metanalysis, become questionable.
 
 Another difference in design that has potential implications for which patients are selected into the trial is the number of sites in a trial.
-Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response [@bridgePlaceboResponseRandomized2009].
-This phenomenon is hard to explain fully with the data available, but may be due to lower quality of phenotyping in such studies, with higher measurement (and therefore diagnostic classification) errors, leading to issues such as spontaneous remission or regression to the mean.
-In contrast to medication trials, psychotherapy trials typically involve one or fewer sites.
+Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
+This phenomenon may be due to lower quality of phenotyping in such studies, with higher rates of classification errors, entailing higher rates of spontaneous remission or regression to the mean.
+It is therefore important to examine whether this basic trial design feature differs between medication and psychotherapy trials.
 
 An inter-related issue concerns the nature of control interventions being used.
-Control conditions in trials are meant to generate counterfactual conditions (CITE RUBIN et al: **Argyris** how's this?
-https://us.sagepub.com/sites/default/files/upm-assets/62640_book_item_62640.pdf) to the intervention: what would have been the outcome in an individual had they not received the intervention.
-This implies that there is a latent distribution of values that represent that counterfactual condition which control arms in trials are meant to approximate.
-Those latent values of the counterfactual condition should, on average, not be different between psychotherapy and medication trials, provided that the samples are representative of the same underlying population (see Eqs 1& 2).
-If the average response to placebo and psychotherapy controls differs systematically from each other, then this is either due to the fact that the trials sample from different populations or because the control conditions differ in their effects (e.g.
-because of how much they do or do not protect against expectancy effects), or both.
+Control conditions in trials are meant to generate counterfactual conditions [@guoChapterCounterfactualFramework2014] to the intervention: what would have been the outcome in an individual had they not received the intervention, with all else being equal.
+A control condition such as pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
+The question is whether psychotherapy trials make a similar effort: are for example the number of hours of contact with a human comparable between active and control arms in psychotherapy trials?
 
@@
 Often, in the public domain, psychotherapy and medication are compared to each other on the basis of their respective effect sizes.
-However, as evident from Eqs 1 and 2, these effect sizes represent differences between the active intervention and the control condition (placebo or psychotherapy control).
+However, these effect sizes represent differences between the active intervention and the control condition (placebo or psychotherapy control).
 For these effect sizes to be comparable, placebo and psychotherapy controls ought to be the equal.
@@
 
-In this paper, we examine psychotherapy and medication trials in the following ways.
-First, we compare key baseline characteristics of medication vs psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity; b) number of sites involved; c) gender composition and d) age.
-Second, we assess the mean efficacy of psychotherapy controls vs placebo.
-We recognise that both these sets of analyses pull data out of the randomised comparisons between treatment arms.
-However, we believe that this is justified for two reasons: a) because it is important to make transparent to all, particularly decision makers in healthcare, the raw data before these are entered into more complex modelling such as network metanalysis, as this allows them to form opinions about the quality and limitations of the input data; b) our aim here is not to make claims about the relative efficacy of each treatment arm, but rather establish whether the conditions for the possibility of comparisons are fulfilled.
-Thus, the comparisons between control conditions are not meant to lead to inferences about placebo being "more efficacious" than psychotherapy controls, but rather to make transparent the problem that they seem to derive from different distributions.
-Third, we examine the quality of psychotherapy controls as such, by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
+In this paper, we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent depression in the following ways.
+First, we compare key baseline characteristics of medication vs psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity of depression; b) percentage females vs males; c) mean age; and d) number of sites involved.
+Second, we determine the standardised mean differences of psychotherapy controls vs medication controls using random effects metanalysis.
+Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
 
@@
 
+This study was registered on the Open Science Framework (OSF); the protocol can be found [here](https://osf.io/bfmc6). In Supplement X we outline deviations from this pre-registered protocol.
+
 ## Studies included
 
-For this review, we primarily drew upon studies included in two recent meta-analyses.
-Please refer to these original meta-analyses for a detailed description of study selection criteria.
+We primarily drew upon RCTs included in two recent comprehensive meta-analyses with open data available for each medication and psychotherapy, and supplemented them with an updated systematic review, described below and in extensive detail in the supplement.
+Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
 Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021].
@@
 Whilst Cuijpers et al.
-(2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to the first meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuipers et al.'s (2023) literature search.
-
-Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in young people [@ciprianiComparativeEfficacyTolerability2016].
-The study dataset was made available online though did not include means or standard deviations at baseline or post-test.
-We emailed the study authors requesting a full dataset with this data, though did not receive a reply, and hence conducted data extraction for medication studies.
+(2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s (2023) literature search.
+
+Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
+A dataset was made available online though did not include means or standard deviations at baseline or post-test.
+We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
 We excluded three studies because they did not include a control arm.
 We were unable to locate and therefore complete extraction for two papers.
-Many studies did not report complete data, and so we emailed all corresponding authors to request missing data, though did not receive any responses.
+Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
 
@@
 We also searched trial registers for published and unpublished studies.
-We used the same search strategy as Cipriani (2016) with an additional search term to include only placebo-controlled trials (see Supplement X for further details).
+We used the same search terms as Cipriani (2016) with one additional search term to include only placebo-controlled trials (see Supplement X for further details).
 We used Covidence, an online software tool, to manage our systematic review.
-In total, our search produced 538 studies, 85 of which were duplicates and subsequently removed.
+In total, our search produced 538 studies, 88 of which were duplicates and subsequently removed.
 Two study authors independently completed title and abstract screenings for 450 studies, and full text screening for 38 studies.
 7 studies met inclusion criteria and data extraction was completed for these papers.
+Clinical trial registers were also systematically searched however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
 
@@
 
-We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including gender, age, and severity of depressive symptoms at baseline.
+We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
 Meta-analyses were implemented using R's Meta package.
 
-In order to compare depression severity across different instruments, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
+In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
 
@@
 
-We present our main results as means of the estimates across simulated datasets, for example, the SMDs of each level of the dummy variable above are means across the simulations.
+We present the SMDs of each level of the dummy variable of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
+The SMDs are the means across the 1000 simulated datasets.
 
@@
 
-We conducted a number of additional analyses to test for the robustness of our results.
-
-First, for each of the the analyses comparing trial and sample characteristics at baseline, and control efficacy between study arms, we performed sensitivity analyses where we restricted the included studies in the following ways.
-First, we excluded studies which recruited participants with subclinical levels of depression.
-Second, we restricted the analyses to studies using CBT and the FDA-approved antidepressants fluoxetine and escitalopram.
-Third, we excluded studies that used waitlist as their control condition.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
-To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
+```{r, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
 # my alpha for the z 
@@
 
+x
+
 ```
+
+We then conducted a series of sensitivity analyses of our results.
+For each of the metanalyses we excluded 1) studies which recruited participants with subclinical levels of depression and 2) studies that used waitlist as their control condition.
+
+Next, we compared the control and active arms of studies where either the CDRS or the HAM-D where used as outcome instruments.
+
+Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
+To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
+We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
 
@@
   mutate(se_age = pooled_sd_age / sqrt(n_overall)) %>% 
-  mutate(gender_overall = sum(percent_women * baseline_n) / sum(baseline_n)) %>% 
-  mutate(percent_women = coalesce(percent_women_overall, gender_overall))
+  mutate(sex_overall = sum(percent_women * baseline_n) / sum(baseline_n)) %>% 
+  mutate(percent_women = coalesce(percent_women_overall, sex_overall))
 
@@
 df_long_for_metan <- df_long_for_metan %>% 
-  select(-c(percent_women_overall, age_m, age_sd, age_m_overall, age_sd_overall, age_overall, gender_overall))
+  select(-c(percent_women_overall, age_m, age_sd, age_m_overall, age_sd_overall, age_overall, sex_overall))
 
@@
 
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` studies which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy trials.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy RCTs Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
 There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD were missing and could not be imputed by any of the methods outlined above.
 
-Placebo was the control condition for all medication trials; the active arm ranged from serotonin reuptake inhibitors, such as 6 fluoxetine and 2 escitalopram, to tricylics, such as 2 nortriptyline.
-In psychotherapy trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions; the active arm included 43 CBT and 8 IPT amongst others.
+Placebo pill was the control condition for all medication trials.
+In psychotherapy trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions.
 All included trials and the types of treatment controls can be found in Supplementary Table 1.
@@
 
+**Table 1**: Sample characteristics at baseline across medication and psychotherapy studies
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 
-cbt_meds_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
-  filter(new_study_id %in% cbt_meds_study_ids)
-
-met_sev_cbt <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cbt + med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_cbt <- extract_stats(met_sev_cbt)
+# cbt_meds_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+# 
+# df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
+#   filter(new_study_id %in% cbt_meds_study_ids) 
+# 
+# met_sev_cbt <- metagen(TE = perc_baseline_overall,
+#                            seTE = perc_se_baseline,
+#                            studlab = new_study_id,
+#                            data = df_for_baseline_severity_cbt,
+#                            sm = "",
+#                            fixed = FALSE,
+#                            random = TRUE,
+#                            method.tau = "REML",
+#                            hakn = TRUE,
+#                            title = "baseline severity cbt + med studies",
+#                            subgroup = psy_or_med,
+#                            tau.common = FALSE)
+# 
+# results_met_sev_cbt <- extract_stats(met_sev_cbt)
 
@@
 
-df_for_gender_metan <- df_baseline_demographics %>% 
+df_for_sex_metan <- df_baseline_demographics %>% 
   filter(!is.na(percent_women))
 
-df_for_gender_metan <- df_for_gender_metan %>% 
+df_for_sex_metan <- df_for_sex_metan %>% 
   filter(percent_women != 100)
@@
                            studlab = new_study_id,
-                           data = df_for_gender_metan,
+                           data = df_for_sex_metan,
                            sm = "",
@@
 met_perc_women_overall <- update(met_perc_women_overall,
-                              subgroup = df_for_gender_metan$psy_or_med, subgroup.name = "treatment modality",
+                              subgroup = df_for_sex_metan$psy_or_med, subgroup.name = "treatment modality",
                               tau.common = FALSE)
@@
 
-df_for_gender_metan_clin <- df_for_gender_metan %>%
+df_for_sex_metan_clin <- df_for_sex_metan %>%
   filter(new_study_id %in% clin_study_ids)
@@
                            studlab = new_study_id,
-                           data = df_for_gender_metan_clin,
+                           data = df_for_sex_metan_clin,
                            sm = "",
@@
 met_perc_women_clin <- update(met_perc_women_clin,
-                           subgroup = df_for_gender_metan_clin$psy_or_med, subgroup.name = "treatment modality",
+                           subgroup = df_for_sex_metan_clin$psy_or_med, subgroup.name = "treatment modality",
                            tau.common = FALSE)
@@
 
-# Now looking at the CBT + med studies only
-
-df_for_gender_metan_cbt <- df_for_gender_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids)
-
-met_perc_women_cbt <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_gender_metan_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across cbt and med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_cbt <- extract_stats(met_perc_women_cbt)
+# # Now looking at the CBT + med studies only
+# 
+# df_for_sex_metan_cbt <- df_for_sex_metan %>%
+#   filter(new_study_id %in% cbt_meds_study_ids) 
+# 
+# met_perc_women_cbt <- metagen(TE = percent_women,
+#                            seTE = percent_women_std_error,
+#                            studlab = new_study_id,
+#                            data = df_for_sex_metan_cbt,
+#                            sm = "",
+#                            fixed = FALSE,
+#                            random = TRUE,
+#                            method.tau = "REML",
+#                            hakn = TRUE,
+#                            title = "percentage women across cbt and med studies",
+#                            subgroup = psy_or_med,
+#                            tau.common = FALSE)
+# 
+# # Apply the function to the meta-analysis result
+# results_met_perc_women_cbt <- extract_stats(met_perc_women_cbt)
 
@@
 
-df_for_gender_metan_no_wl <- df_for_gender_metan %>%
+df_for_sex_metan_no_wl <- df_for_sex_metan %>%
   filter(new_study_id %in% no_wl_ids)
@@
                            studlab = new_study_id,
-                           data = df_for_gender_metan_no_wl,
+                           data = df_for_sex_metan_no_wl,
                            sm = "",
@@
   filter(!is.na(mean_age))
+
+weighted_average_age <- sum(df_baseline_demographics$mean_age * df_baseline_demographics$baseline_n, na.rm = TRUE) / sum(df_baseline_demographics$baseline_n, na.rm = TRUE)
+tst <- mean(df_baseline_demographics$mean_age, na.rm = TRUE)
 
@@
 
-# Now cbt + med studies only
-
-df_for_age_metan_cbt <- df_for_age_metan %>%
-  filter(new_study_id %in% cbt_meds_study_ids)
-
-met_age_cbt <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_cbt,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across cbt + med studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age_cbt <- extract_stats(met_age_cbt)
+# # Now cbt + med studies only
+# 
+# df_for_age_metan_cbt <- df_for_age_metan %>%
+#   filter(new_study_id %in% cbt_meds_study_ids) 
+# 
+# met_age_cbt <- metagen(TE = mean_age,
+#                            seTE = se_age,
+#                            studlab = new_study_id,
+#                            data = df_for_age_metan_cbt,
+#                            sm = "",
+#                            fixed = FALSE,
+#                            random = TRUE,
+#                            method.tau = "REML",
+#                            hakn = TRUE,
+#                            title = "age across cbt + med studies",
+#                            subgroup = psy_or_med,
+#                            tau.common = FALSE)
+# 
+# results_met_age_cbt <- extract_stats(met_age_cbt)
 
@@
 # Lets make a table that combines across these baseline characteristics variables
-
-df_overall_baseline_results <- rbind(results_met_sev, results_met_perc_women_overall, results_met_age)
-
-# For row names
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(subgroup = case_when(
-    row_number() == 1 ~ "Severity",
-    row_number() == 4 ~ "Percent Women",
-    row_number() == 7 ~ "Age",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_overall_baseline_results) <- new_column_names
-
-# Rounding
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-big_border = fp_border(color="black", width = 1)
-small_border = fp_border(color="lightgray", width = 1)
+# This is for overall sample only, with separate sensitivity analyses in the supplement
+
+# df_overall_baseline_results <- rbind(results_met_sev, results_met_perc_women_overall, results_met_age)
+# 
+# # For row names
+# df_overall_baseline_results <- df_overall_baseline_results %>%
+#   mutate(subgroup = case_when(
+#     row_number() == 1 ~ "Severity",
+#     row_number() == 4 ~ "Percent Female",
+#     row_number() == 7 ~ "Age",
+#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+#   )) 
+# 
+# # Define new column names
+# new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+# 
+# # Assign new column names to the data frame
+# colnames(df_overall_baseline_results) <- new_column_names
+# 
+# # Rounding
+# df_overall_baseline_results <- df_overall_baseline_results %>%
+#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+#   mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
+# 
+# big_border = fp_border(color="black", width = 1)
+# small_border = fp_border(color="lightgray", width = 1)
 
@@
 # this doesn't have a caption when rendering to word
-
-flextable(df_overall_baseline_results) %>%
-  set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
-  bold(part = "header") %>%  # Bold the header row
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  border_outer(border = small_border) %>%  # Add outer borders
-  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>%
-  hline(part = "header", border = big_border) %>%
-  vline(j = 1, border = big_border) %>%
-  set_table_properties(width = .75) %>%  # Set table width
-  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-  autofit() %>%  # Autofit column widths
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>%
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-
-# this doesn't work either
-#
-# table_sample_result <- flextable(df_overall_baseline_results) %>%
+# 
+# flextable(df_overall_baseline_results) %>%
+#   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
 #   bold(part = "header") %>%  # Bold the header row
@@
 #   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-# 
-# table_sample_result <- set_caption(table_sample_result, caption = "Testing")
-# 
-# table_sample_result
-
-```
-
-```{r}
-#| label: tbl-flextable
-#| tbl-cap: "Testing"
-flextable::flextable(df_overall_baseline_results)
-# the caption isn't working here either
+
+# This is if we want to have all sensitivity analyses in table one
+
+df_overall_baseline_results <- rbind(results_met_sev, results_met_sev_clin, results_met_sev_no_wl, results_met_perc_women_overall, results_met_perc_women_clin, results_met_perc_women_no_wl, results_met_age, results_met_age_clin, results_met_age_no_wl)
+
+# For row names
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(subgroup = case_when(
+    row_number() %in% c(1, 10, 19) ~ "Overall",
+    row_number() %in% c(4, 13, 22) ~ "Excluding subclinical",
+    row_number() %in% c(7, 16, 25) ~ "Excluding waitlist",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_overall_baseline_results) <- new_column_names
+
+# Rounding
+df_overall_baseline_results <- df_overall_baseline_results %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+big_border = fp_border(color="black", width = 1)
+small_border = fp_border(color="lightgray", width = 1)
+
+df_overall_baseline_results <- df_overall_baseline_results %>% 
+  mutate(category = case_when(
+    row_number() %in% 1:9 ~ "Baseline Severity",
+    row_number() %in% 10:18 ~ "Percent Female",
+    row_number() %in% 19:27 ~ "Age",
+    TRUE ~ ""
+  )) %>% # grouping rows
+  group_by(category) %>%
+  as_flextable(hide_grouplabel = TRUE) %>% 
+  add_header_row(values = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% 
+  set_caption("Table 1: Sample characteristics at baseline across medication and psychotherapy studies") %>%
+  bold(part = "header") %>%  # Bold the header row
+  bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  border_outer(border = small_border) %>%  # Add outer borders
+  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  hline(part = "header", border = big_border) %>%
+  vline(j = 1, border = small_border) %>%
+  set_table_properties(width = .75) %>%  # Set table width
+  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% 
+  autofit() %>%  # Autofit column widths
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>%
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>%
+
+df_overall_baseline_results
+
 ```
@@
 
-When taking only those studies where the active arm was either CBT, fluoxetine or escitalopram, baseline severity remained significantly higher in medication versus psychotherapy studies.
-This difference did not reach statistical significance when excluding psychotherapy studies that recruited samples with sub-clinical depression or when excluding studies that used wait list as their control.
-Please refer to Table S1 for these results.
-
-### Gender
+When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
+This difference did not reach statistical significance when excluding studies that recruited samples with sub-clinical depression.
+
+### Sex
 
 For this analysis, we excluded the two psychotherapy trials which included entirely female samples.
-As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of women when compared to medication trials.
-On average, samples were comprised of `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],1)`) women across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],1)`) women across medication trials.
-Excluding sub-clinical and waitlist control studies yielded very similar results.
-This difference in gender composition however did not reach statistical significance when only CBT, fluoxetine and escitalopram trials were included (see Table S2).
+As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
+On average, samples were `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`) female across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`) female across medication trials.
+Excluding sub-clinical and waitlist control studies yielded similar results.
 
@@
 As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
-There were no significant differences in mean age between modalities on further sensitivity analyses (see Table S3).
+There were no significant differences in mean age between modalities on further sensitivity analyses.
 
@@
 flextable(df_sites_summary_stats) %>%
-  set_caption ("Number of sites across medication and psychotherapy studies") %>%
+  set_caption ("Table 2: Number of sites across medication and psychotherapy studies") %>%
   bold(part = "header") %>%
@@
   hline(part = "header", border = big_border) %>%
-  vline(j = 1, border = big_border) %>%
+  vline(j = 1, border = small_border) %>%
   set_table_properties(width = .75) %>%
@@
 
-## Mean efficacy of control conditions in psychotherapy versus medication studies
+## Standardised mean differences of control conditions in psychotherapy and medication studies
 
@@
 As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 4 below).
+In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 4 below).
 
@@
 
+![](plot_means_all.pdf)
+
 In Table 5, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
@@
 
-We then conducted a series of sensitivity analyses of our results.
-We compared the control and active arms of CBT studies to those of fluoxetine and escitalopram studies.
+We then conducted a series of sensitivity analyses of our results.First, we analysed the data after excluding waitlist control studies.
 As can be seen, the pattern of results is very similar to that of the overall analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-subtitle_text_cbt <- "Metanalytic estimates of within-group changes: cbt, fluox, escit"
-plot_means_cbt <- plot_means_function(coef_and_se_means_cbt_fluox_esc_study , subtitle_text_cbt)
-pdf(file = "plot_means_cbt.pdf")
-plot_means_cbt
-dev.off()
-
-```
-
-![](plot_means_cbt.pdf)
-
-We next analysed the data after excluding waitlist control studies. As can be seen, the pattern of results is very similar to that of the overall analyses.
 
@@
 
-#######END HERE########
-
-*Write up results for sensitivity analyses*
-
 #### Addressing Regression to the Mean
 
-**Argyris** are we happy to remove this whole section?
-
-We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D on which there was a sufficient number of studies to metanalyse.
-
-As can be seen in Table 3a and 3b, there baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
-As can be seen in Supplementary Tables XX <!--# Charlotte, please create these out of results_cdrs_metareg_baseline[[1]]  and the same for HAM-D--> the differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
 
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
+
+### get CDRS studies
+cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
+
+#turn sds to sec
+cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+
+results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
+                                                         model_1, condition)
+
+### get HAM-D studies
+hamd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
+
+list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
+                                                          %in% hamd_study_ids,]
+
+hamd_studies_for_baseline_metareg <- list_hamd_study #
+
+#turn sds to sec
+hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
+                                                         model_1, condition)
+
+results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+
 ```
 
+As can be seen in Tables X and Y, the baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
+The differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
 ```
 
-```{r, echo = FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+```
+
+We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 #### Let's start from the beginning and regress cohens on the baseline dataframe.
@@
 # specify model
-model_1 <- as.formula(~ four_level_var)
+model_x <- as.formula(~ four_level_var)
 
@@
 # here you can use the simulated results directly
-list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_1)
+list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
 
@@
 
-results_adjusted_cohens_d
-
 ```
 
-As can be seen in Table 4, the baseline mean has a very strong association with the SMD.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(results_adjusted_cohens_d 
-#               
-#               , caption = "Table 4. Effect of baseline values on SMDs")
-```
-
-Table 5 shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
-As can be inferred from the non-overlapping confidence intervals, the difference between the two control conditions was significant (details of the regression model can be found in Supplementary Table XX <!--# Charlotte, please add there the aggregate_results_overall_adjusted_cohens_d -->).
-Differences were significant between active medication and psychotherapy control, but not between any of the other groups.
+Table X shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
+As can be inferred from the non-overlapping confidence intervals, there were significant differences between the medication control and psychotherapy control arms.
 
@@
 
-Tables 6a and 6b show the baseline-mean adjusted SMDs for the CDRS at outcome when the baseline measurement has been taken into account.
-<!--# Here Intercept refers to teh psychotherapy control.
-Sorry about the labelling of the rows, will improve.
--->
-
-```{r}
-# knitr:: kable(cdrs_smd_with_cis, caption = "Table 6a. CDRS baseline mean adjsuted SMDs")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(hamd_smd_with_cis, caption = "Table 6. HAM-D baseline-mean adjusted SMDs")
-```
-
 # Discussion
@@
 
-Severity is important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to placebo response is lower [@bridgePlaceboResponseRandomized2009].
+Severity is important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
 Some studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g.
@@
 
-Similarly, we found that on average there were about 7% more women in psychotherapy trials.
-Whilst there is little evidence that sex or gender moderate treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
+Similarly, we found that on average there were about 7% more females in psychotherapy trials.
+Whilst there is little evidence that sex or sex moderate treatment response within modality in adult trials of depression [@cuijperssexPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
 
@@
 
-First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts---CITE PROBABILITIES.
-Multisite trials are associated with higher placebo response [@bridgePlaceboResponseRandomized2009], and are less common in NIH-funded (i.e.
-non industry trials) which are also more likely to show higher placebo efficacy.
+First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in NIH-funded (i.e.
+non industry) trials which are also more likely to show higher pill placebo efficacy.
 Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where primacy is given to the number of recruited participants which is the primary unit of reimbursement.
@@
 
+PRISMA chart summarising the screening process for the systematic review.
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Tables for baseline comparisons
-
-# Lets make a table that combines across the sensitivity analyses for severity
-
-df_severity_sens <- rbind(results_met_sev_cbt, results_met_sev_clin, results_met_sev_no_wl)
-
-# For row names
-df_severity_sens <- df_severity_sens %>%
-  mutate(subgroup = case_when(
-    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-    row_number() == 4 ~ "Excluding subclinical",
-    row_number() == 7 ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_severity_sens) <- new_column_names
-
-# Rounding
-df_severity_sens <- df_severity_sens %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3))
-
-df_severity_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-flextable(df_severity_sens) %>%
-  set_caption(caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials") %>%
-  bold(part = "header") %>%  # Bold the header row
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  border_outer(border = small_border) %>%  # Add outer borders
-  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-  hline(part = "header", border = big_border) %>% 
-  vline(j = 1, border = big_border) %>% 
-  set_table_properties(width = .75) %>%  # Set table width
-  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-  autofit() %>%  # Autofit column widths
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-
-# Now gender
-
-df_gender_sens <- rbind(results_met_perc_women_cbt, results_met_perc_women_clin, results_met_perc_women_no_wl)
-
-# For row names
-df_gender_sens <- df_gender_sens %>%
-  mutate(subgroup = case_when(
-    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-    row_number() == 4 ~ "Excluding subclinical",
-    row_number() == 7 ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_gender_sens) <- new_column_names
-
-# Rounding
-df_gender_sens <- df_gender_sens %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3))
-
-df_gender_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-flextable(df_gender_sens) %>%
-  set_caption(caption = "Table S2: Sensitivity analyses for comparison of gender composition between psychotherapy and medication trials") %>%
-  bold(part = "header") %>%  # Bold the header row
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  border_outer(border = small_border) %>%  # Add outer borders
-  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-  hline(part = "header", border = big_border) %>% 
-  vline(j = 1, border = big_border) %>% 
-  set_table_properties(width = .75) %>%  # Set table width
-  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-  autofit() %>%  # Autofit column widths
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-
-# Now age
-
-df_age_sens <- rbind(results_met_age_cbt, results_met_age_clin, results_met_age_clin)
-
-# For row names
-df_age_sens <- df_age_sens %>%
-  mutate(subgroup = case_when(
-    row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-    row_number() == 4 ~ "Excluding subclinical",
-    row_number() == 7 ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_age_sens) <- new_column_names
-
-# Rounding
-df_age_sens <- df_age_sens %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3))
-
-df_age_sens %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-flextable(df_age_sens) %>%
-  set_caption(caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials") %>%
-  bold(part = "header") %>%  # Bold the header row
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  border_outer(border = small_border) %>%  # Add outer borders
-  hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-  hline(part = "header", border = big_border) %>% 
-  vline(j = 1, border = big_border) %>% 
-  set_table_properties(width = .75) %>%  # Set table width
-  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-  autofit() %>%  # Autofit column widths
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+# # Tables for baseline comparisons
+# 
+# # Lets make a table that combines across the sensitivity analyses for severity
+# 
+# df_severity_sens <- rbind(results_met_sev_cbt, results_met_sev_clin, results_met_sev_no_wl)
+# 
+# # For row names
+# df_severity_sens <- df_severity_sens %>%
+#   mutate(subgroup = case_when(
+#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+#     row_number() == 4 ~ "Excluding subclinical",
+#     row_number() == 7 ~ "Excluding waitlist",
+#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+#   )) 
+# 
+# # Define new column names
+# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+# 
+# # Assign new column names to the data frame
+# colnames(df_severity_sens) <- new_column_names
+# 
+# # Rounding
+# df_severity_sens <- df_severity_sens %>%
+#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+#   mutate_at(vars(ncol(.)), ~ round(., 3))
+# 
+# df_severity_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
+# 
+# flextable(df_severity_sens) %>%
+#   set_caption(caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials") %>%
+#   bold(part = "header") %>%  # Bold the header row
+#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+#   border_outer(border = small_border) %>%  # Add outer borders
+#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+#   hline(part = "header", border = big_border) %>% 
+#   vline(j = 1, border = big_border) %>% 
+#   set_table_properties(width = .75) %>%  # Set table width
+#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+#   autofit() %>%  # Autofit column widths
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+# 
+# # Now sex
+# 
+# df_sex_sens <- rbind(results_met_perc_women_cbt, results_met_perc_women_clin, results_met_perc_women_no_wl) 
+# 
+# # For row names
+# df_sex_sens <- df_sex_sens %>%
+#   mutate(subgroup = case_when(
+#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+#     row_number() == 4 ~ "Excluding subclinical",
+#     row_number() == 7 ~ "Excluding waitlist",
+#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+#   )) 
+# 
+# # Define new column names
+# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+# 
+# # Assign new column names to the data frame
+# colnames(df_sex_sens) <- new_column_names
+# 
+# # Rounding
+# df_sex_sens <- df_sex_sens %>%
+#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+#   mutate_at(vars(ncol(.)), ~ round(., 3))
+# 
+# df_sex_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
+# 
+# flextable(df_sex_sens) %>%
+#   set_caption(caption = "Table S2: Sensitivity analyses for comparison of sex composition between psychotherapy and medication trials") %>%
+#   bold(part = "header") %>%  # Bold the header row
+#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+#   border_outer(border = small_border) %>%  # Add outer borders
+#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+#   hline(part = "header", border = big_border) %>% 
+#   vline(j = 1, border = big_border) %>% 
+#   set_table_properties(width = .75) %>%  # Set table width
+#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+#   autofit() %>%  # Autofit column widths
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
+# 
+# # Now age
+# 
+# df_age_sens <- rbind(results_met_age_cbt, results_met_age_clin, results_met_age_clin) 
+# 
+# # For row names
+# df_age_sens <- df_age_sens %>%
+#   mutate(subgroup = case_when(
+#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
+#     row_number() == 4 ~ "Excluding subclinical",
+#     row_number() == 7 ~ "Excluding waitlist",
+#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+#   )) 
+# 
+# # Define new column names
+# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+# 
+# # Assign new column names to the data frame
+# colnames(df_age_sens) <- new_column_names
+# 
+# # Rounding
+# df_age_sens <- df_age_sens %>%
+#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+#   mutate_at(vars(ncol(.)), ~ round(., 3))
+# 
+# df_age_sens %>%
+#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
+# 
+# flextable(df_age_sens) %>%
+#   set_caption(caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials") %>%
+#   bold(part = "header") %>%  # Bold the header row
+#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+#   border_outer(border = small_border) %>%  # Add outer borders
+#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
+#   hline(part = "header", border = big_border) %>% 
+#   vline(j = 1, border = big_border) %>% 
+#   set_table_properties(width = .75) %>%  # Set table width
+#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
+#   autofit() %>%  # Autofit column widths
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
+#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
+#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
 

### 2024-04-19 Manuscript_for_rendering_in_word.qmd
Lots of formatting things, success in fixing up tables Next to address are issues with the figures

@@
 ---
-title: "Fundamental Problems with Child and Adolecsent Depression Treatments: A Quantitative Reappraisal of the Evidence Base"
+title: "Fundamental Problems with Child and Adolescent Depression Treatments"
+subtitle: "A Quantitative Reappraisal of the Evidence Base"
 author:
@@
 date: last-modified
-
-format: docx
+format:
+  docx:
+    reference-doc: custom-reference-doc.docx
 editor: visual
@@
 library(ftExtra)
+library(dplyr)
 
@@
                                       colour = condition, label = text_label)) +
-    geom_point(label=dataframe$k) +
     geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
@@
 #summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
+
 ```
-
 # Results
@@
 # add the ns
-df_mean_coefs_from_sim <- data.frame(cbind(df_mean_coefs_from_sim, n = df_count_studies[df_count_studies$is_missing == FALSE, ]$n))
+df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 # add the ns to the dataframe
- coef_and_se_means_cbt_fluox_esc_study$n  <- study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing ==F,]$n
+coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 
-coef_and_se_means_no_wl$n <- study_count_no_wl_study[study_count_no_wl_study$is_missing 
-                                                     ==FALSE,]$n
+coef_and_se_means_no_wl <- left_join(coef_and_se_means_no_wl, study_count_no_wl_study[study_count_no_wl_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 # add the ns to the dataframe
-coef_and_se_means_cdrs_study$n  <- study_count_cdrs_study[study_count_cdrs_study$is_missing ==F,]$n
+coef_and_se_means_cdrs_study <- left_join(coef_and_se_means_cdrs_study, study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 # add the ns to the dataframe
-coef_and_se_means_clin_study$n  <- study_count_clin_study[study_count_clin_study$is_missing ==F,]$n
+coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 
-**Table 1**: Sample characteristics at baseline across medication and psychotherapy studies
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 # 
-# this doesn't have a caption when rendering to word
+# this doesn't have a caption when rendering to word. workaround below, adding caption as header row.
 # 
@@
 
-df_overall_baseline_results <- df_overall_baseline_results %>% 
+df_overall_baseline_results %>% 
   mutate(category = case_when(
@@
   as_flextable(hide_grouplabel = TRUE) %>% 
-  add_header_row(values = "Table 1: Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% 
-  set_caption("Table 1: Sample characteristics at baseline across medication and psychotherapy studies") %>%
-  bold(part = "header") %>%  # Bold the header row
+  paginate(group = "category", group_def = "rle") %>% 
   bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  border_outer(border = small_border) %>%  # Add outer borders
-  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(part = "header", border = big_border) %>%
-  vline(j = 1, border = small_border) %>%
-  set_table_properties(width = .75) %>%  # Set table width
-  bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% 
+  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width
+  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
   autofit() %>%  # Autofit column widths
+  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>% # indent some rows
+  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>% 
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>%
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>%
-
-df_overall_baseline_results
+  add_header_row(values = "Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% # This is a work around for the problems with rendering captions
+  add_header_row(values = "Table 1", colwidths = 8) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-colnames(sites_t_test_stats) <- c("Statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# scatter plot
-
-# ggplot(df_baseline_demographics, aes(x = factor(psy_or_med), y = sites, color = factor(psy_or_med))) +
-#   geom_point(position = position_jitter(width = 0.2), size = 2) +
-#   labs(title = "Number of Sites for Psychotherapy and Medication Trials",
-#        x = "Treatment Modality",
-#        y = "Number of Sites") +
-#   scale_color_discrete(name = "Treatment Type", labels = c("Medication", "Psychotherapy"))
-
-# Create a flextable object
-
 flextable(df_sites_summary_stats) %>%
-  set_caption ("Table 2: Number of sites across medication and psychotherapy studies") %>%
-  bold(part = "header") %>%
-  border_outer(border = small_border) %>%
-  hline(part = "all", border = small_border) %>%
-  hline(part = "header", border = big_border) %>%
-  vline(j = 1, border = small_border) %>%
-  set_table_properties(width = .75) %>%
-  bg(bg = "#F2F2F2", part = "header") %>%
+  set_table_properties(width = 1, layout = "autofit") %>%
+  add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
+                      "; ", as_i("p "), sites_t_test_stats$p_value, 
+                      "; 95% CI: ", sites_t_test_stats$ci_lower,
+                      "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
+  add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
+  add_header_row(values = "Table 2", colwidths = 4) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>%
+  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
+  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>% 
   autofit() %>% 
-  font(fontname = "Calibri", part = "all") %>%
-  padding(i = c(1, 2), j = 1, padding.left = 10) %>%
-  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all")
-
-flextable(sites_t_test_stats) %>%
-  set_caption ("Results for t-test comparing number of sites between medication and psychotherapy studies", style = "Table Caption") %>%
-  bold(part = "header") %>%  
-  border_outer(border = small_border) %>%  
-  hline(part = "header", border = big_border) %>% 
-  set_table_properties(width = .75) %>% 
-  bg(bg = "#F2F2F2", part = "header") %>%  
-  autofit() %>% 
-  font(fontname = "Calibri", part = "all") %>%   
-  align(align = "center", part = "all")
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Tables 2 and 3.
-Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test$p.value`).
+There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Table 2.
+Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
 Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
@@
 As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 4 below).
+In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 3 below).
 
@@
 plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
-#print(plot_means_all)
 pdf(file = "plot_means_all.pdf")
-# Instead of PDF
-png(file = "plot_means_all.png")
-dev.off()
 
@@
 
-df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
+table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 # Assign new column names to the data frame
-colnames(df_mean_coefs_from_sim) <- new_column_names
+colnames(table_mean_coefs_from_sim) <- new_column_names
 
@@
 
-flextable(df_mean_coefs_from_sim) %>%
-  set_caption ("Summary statistics of the estimated SMDs") %>%
-  bold(part = "header") %>%  
-  border_outer(border = small_border) %>%  
-  hline(part = "header", border = big_border) %>% 
-  set_table_properties(width = .75) %>% 
-  bg(bg = "#F2F2F2", part = "header") %>%  
+flextable(table_mean_coefs_from_sim) %>%
+  set_table_properties(width = 1, layout = "autofit") %>%
   autofit() %>%
   font(fontname = "Calibri", part = "all") %>% 
-  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center")
+  add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
+  add_header_row(values = "Table 3", colwidths = 6) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-![Figure 1.](plot_means_all.png)
+![Figure 1.](plot_means_all.pdf)
 
@@
 
-In Table 5, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+In Table 4, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
 In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
@@
 
-#aggregate_results_overall
-
-flextable(aggregate_results_overall) %>%
-  set_caption ("Metaregression results") %>%
-  bold(part = "header") %>%  
-  border_outer(border = small_border) %>%  
-  hline(part = "header", border = big_border) %>% 
-  set_table_properties(width = .75) %>% 
-  bg(bg = "#F2F2F2", part = "header") %>%  
+table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
+
+flextable(table_aggregate_results_overall) %>%
+  set_table_properties(width = 1, layout = "autofit") %>%
   autofit() %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
+                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
+                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
+  add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
+  add_header_row(values = "Table 4", colwidths = 6) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
   font(fontname = "Calibri", part = "all") %>% 
-  align(j = 2:ncol(aggregate_results_overall), align = "center")
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-We then conducted a series of sensitivity analyses of our results.First, we analysed the data after excluding waitlist control studies.
+We then conducted a series of sensitivity analyses of our results.
+First, we analysed the data after excluding waitlist control studies.
 As can be seen, the pattern of results is very similar to that of the overall analyses.
@@
 ![](plot_means_clin.pdf)
+
+Finally, we examined the data including only those studies that used the CDRS, which yielded a very similar pattern of results.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
+plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
+pdf(file = "plot_means_cdrs.pdf")
+plot_means_cdrs
+dev.off()
+
+```
+
+![](plot_means_cdrs.pdf)
 
@@
 ![](stab_sims.pdf)
+
+#### Addressing Regression to the Mean
+
+We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+### get CDRS studies
+cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
+
+#turn sds to sec
+cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+
+results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
+                                                         model_1, condition)
+
+### get HAM-D studies
+hamd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
+
+list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
+                                                          %in% hamd_study_ids,]
+
+hamd_studies_for_baseline_metareg <- list_hamd_study #
+
+#turn sds to sec
+hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
+                                                              #throughout
+results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
+                                                         model_1, condition)
+
+results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+
+```
+
+As can be seen in Tables X and Y, the baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
+The differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
+```
+
+We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#### Let's start from the beginning and regress cohens on the baseline dataframe.
+
+# create a new list with dfs for the sims
+df_long_for_metan_adj_cohens_d <- df_long_for_metan
+# rename the cohens_d value to make space for the new cohen's d
+df_long_for_metan_adj_cohens_d <-
+  df_long_for_metan_adj_cohens_d %>%
+rename(unadjusted_cohens_d = cohens_d,
+)
+# estimate the cohen's d from the residuals
+model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
+
+# there is a great effect of the baseline means, as shown here
+results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
+
+# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
+df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
+
+# apply function to simulate standard errors
+list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
+                                   num_repetitions = 1000,
+                                   seed  = 1974,
+                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
+                                   a = 0.45,
+                                   b = .9,
+                                   mean = 0.65,
+                                   sd = 0.2)
+
+# add the four level variable and re-level
+for(i in 1: length(list_df_simulated_adj_cohens_d)){
+
+  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
+  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
+
+  # relevel so that medication control becomes the reference category for the regression
+  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
+                                                         "medication_control",
+                                                         "medication_active",
+                                                         "psychotherapy_control",
+                                                         "psychotherapy_active")
+}
+
+# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
+# specify model
+model_x <- as.formula(~ four_level_var)
+
+# run metareg function
+# here you can use the simulated results directly
+list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
+aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
+aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
+
+# extract SMDs from the  list
+list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
+
+df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+
+```
+
+Table X shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
+As can be inferred from the non-overlapping confidence intervals, there were significant differences between the medication control and psychotherapy control arms.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
+```
+
+Finally, we tested whether the simulated correlation values we used for simulation of the standard errors had an appreciable effect on the values of the adjusted SMDs.
+Supplemental Figure X shows that the variability of the estimated z-value was minimal<!--# Charlotte, the figure below should be supplemental-->.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# 
+# # plot the mean z for the difference between controls
+# z_psy_con_vs_med_con <- 0
+# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
+#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
+#   
+# }
+# 
+# 
+# 
+# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+# 
+# 
+# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
+#   ggplot(aes(x = n_sims, y = z_value)) +
+#   geom_point() +
+#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+#                arrow = arrow(length = unit(0.3, "cm")),
+#                color = "black") +
+#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
+#            hjust = -0.1, vjust = 0) +
+#   theme_minimal() +
+#   labs(
+#     x = "Number of Simulations",
+#     y = "z-value",
+#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
+#     subtitle = "Results from 1000 simulations with within-group standard errors"
+#   )
+# stab_sims_adjusted_cohens_d
+# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
+# stab_sims_adjusted_cohens_d
+# dev.off()
+
+```
 
@@
     Column == "no_sessions" ~ "Number of sessions",
-    Column == "freq_weeks" ~ "Frequency (weeks)",
+    Column == "freq_weeks" ~ "Intensity (sessions per week)",
     Column == "length_sessions_mins" ~ "Session length (mins)",
     Column == "total_hours" ~ "Total intervention hours",
-    Column == "total_period_weeks" ~ "Total intervention period (weeks)",
+    Column == "total_period_weeks" ~ "Intervention duration (weeks)",
     TRUE ~ as.character(Column)  # Keep original value if no match
@@
   as_flextable(hide_grouplabel = TRUE ) %>% 
-  set_caption ("Comparing the intensity of the intervention between active and control arms of psychotherapy studies") %>%
-  bold(part = "header") %>%
-  bold(i = c(1, 4, 7, 10, 13), j = NULL, bold = TRUE, part = "body") %>%  
-  border_outer(border = small_border) %>%  
-  hline(part = "all", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  hline(i = c(3, 6, 9, 12), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-  hline(part = "header", border = big_border) %>% 
-  set_table_properties(width = 1) %>%  
-  bg(bg = "#F2F2F2", part = "header") %>%  
-  font(fontname = "Calibri", part = "all")
+  bold(i = c(1, 4, 7, 10, 13), bold = TRUE, part = "body") %>%  
+  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width 
+  autofit() %>%  # Autofit column widths 
+  align(j = 2:4, align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
+  add_header_row(values = "Table 5", colwidths = 4) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  paginate(init = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
     row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Frequency (weeks)",
+    row_number() == 2 ~ "Intensity (sessions per week)",
     row_number() == 3 ~ "Session length (mins)",
     row_number() == 4 ~ "Total intervention hours",
-    row_number() == 5 ~ "Total intervention period (weeks)"
+    row_number() == 5 ~ "Intervention duration (weeks)"
   ))
@@
 flextable(control_summary_t_tests) %>%
-  set_caption ("Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", style = "Table Caption") %>%
-  bold(part = "header") %>%  
-  border_outer(border = small_border) %>%  
-  hline(part = "header", border = big_border) %>% 
-  set_table_properties(width = .75) %>% 
-  bg(bg = "#F2F2F2", part = "header") %>%  
-  autofit() %>% 
-  font(fontname = "Calibri", part = "all") %>%   
-  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all")
+  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width %>% 
+  autofit() %>%  # Autofit column widths 
+  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
+  add_header_row(values = "Table 6", colwidths = 6) %>% 
+  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
+  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(i = 3, part = "header", border = big_border) %>% 
+  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  paginate(init = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 Active intervention arms featured significantly more sessions than control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
-These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Frequency (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Frequency (weeks)"]`).
-The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`).
-
-#### Addressing Regression to the Mean
-
-We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-### get CDRS studies
-cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-
-#turn sds to sec
-cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-
-results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
-                                                         model_1, condition)
-
-### get HAM-D studies
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-                                                          %in% hamd_study_ids,]
-
-hamd_studies_for_baseline_metareg <- list_hamd_study #
-
-#turn sds to sec
-hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
-                                                         model_1, condition)
-
-results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-```
-
-As can be seen in Tables X and Y, the baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
-The differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
-```
-
-We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#### Let's start from the beginning and regress cohens on the baseline dataframe.
-
-# create a new list with dfs for the sims
-df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# rename the cohens_d value to make space for the new cohen's d
-df_long_for_metan_adj_cohens_d <-
-  df_long_for_metan_adj_cohens_d %>%
-rename(unadjusted_cohens_d = cohens_d,
-)
-# estimate the cohen's d from the residuals
-model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
-
-# there is a great effect of the baseline means, as shown here
-results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-
-# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-
-# apply function to simulate standard errors
-list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
-                                   num_repetitions = 1000,
-                                   seed  = 1974,
-                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
-                                   a = 0.45,
-                                   b = .9,
-                                   mean = 0.65,
-                                   sd = 0.2)
-
-# add the four level variable and re-level
-for(i in 1: length(list_df_simulated_adj_cohens_d)){
-
-  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-                                                         "medication_control",
-                                                         "medication_active",
-                                                         "psychotherapy_control",
-                                                         "psychotherapy_active")
-}
-
-# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# specify model
-model_x <- as.formula(~ four_level_var)
-
-# run metareg function
-# here you can use the simulated results directly
-list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-
-df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
-
-```
-
-Table X shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
-As can be inferred from the non-overlapping confidence intervals, there were significant differences between the medication control and psychotherapy control arms.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
-```
-
-Finally, we tested whether the simulated correlation values we used for simulation of the standard errors had an appreciable effect on the values of the adjusted SMDs.
-Supplemental Figure X shows that the variability of the estimated z-value was minimal<!--# Charlotte, the figure below should be supplemental-->.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# 
-# # plot the mean z for the difference between controls
-# z_psy_con_vs_med_con <- 0
-# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
-#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
-#   
-# }
-# 
-# 
-# 
-# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-# 
-# 
-# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
-#   ggplot(aes(x = n_sims, y = z_value)) +
-#   geom_point() +
-#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-#                arrow = arrow(length = unit(0.3, "cm")),
-#                color = "black") +
-#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
-#            hjust = -0.1, vjust = 0) +
-#   theme_minimal() +
-#   labs(
-#     x = "Number of Simulations",
-#     y = "z-value",
-#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-#     subtitle = "Results from 1000 simulations with within-group standard errors"
-#   )
-# stab_sims_adjusted_cohens_d
-# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
-# stab_sims_adjusted_cohens_d
-# dev.off()
-
-```
+These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`).
+The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
 
@@
 Similarly, we found that on average there were about 7% more females in psychotherapy trials.
-Whilst there is little evidence that sex or sex moderate treatment response within modality in adult trials of depression [@cuijperssexPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
+Whilst there is little evidence that sex or sex moderate treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
 
@@
 
-Second, the control conditions of psychotherapy trials are much weaker than those of their medication counterparts.
+Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9).
 Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally advised against (CITE).
@@
 ```
+
+# References

### 2024-04-22 Manuscript_for_rendering_in_word.qmd
Trying this
Fixed some problems with numbering of tables and figures

@@
     reference-doc: custom-reference-doc.docx
+    fig-width: 9
+    fig-height: 7
+    fig_caption: yes
+    tbl_caption: yes
 editor: visual
@@
   family: "Calibri"
+prefer-html: true
+fig-format: png
+fig-cap-location: top
+
 ---
@@
   # Encode colours
-  redish_palette <- c("medication control" = "deeppink", "medication active" = "deeppink3")
-  blueish_palette <- c("psychotherapy active" = "steelblue1", "psychotherapy control" = "steelblue3")
+  redish_palette <- c("Medication Control" = "deeppink4", "Medication Active" = "deeppink")
+  blueish_palette <- c("Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
 
@@
                                       colour = condition, label = text_label)) +
+    geom_point(label=dataframe$k) +
     geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
@@
     theme_minimal() +
-    labs(x = "TE-random", y = NULL, title = "Adolescent Depression Trial Efficacy by Treatment Arm",
+    labs(x = "TE-random", y = NULL, title = "Trial Efficacy by Treatment Arm",
          subtitle = subtitle) +
@@
     geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
-    theme(axis.title.x = element_text(size = 12), 
-          axis.text.x  = element_text(size = 12),
+    theme(axis.title.x = element_text(size = 12, family  = "Calibri"), 
+          axis.text.x  = element_text(size = 12, family = "Calibri"),
           axis.text.y = (element_blank()),
-          plot.title = element_text(size = 12),
-          plot.subtitle = element_text(size = 12)) +
+          plot.title = element_text(size = 12, family =  "Calibri", face= "italic"),
+          plot.subtitle = element_text(size = 12, family =  "Calibri", face= "italic")) +
     geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
@@
 
-As can be seen in Figure 1, there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
+As can be seen in @fig-plot-means-all there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
 In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 3 below).
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
-plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
-pdf(file = "plot_means_all.pdf")
-
-# Prepare to tabulate
-
-table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
+#| label: fig-plot-means-all
+#| fig-cap: "Metanalytic estimates of within-group changes: all studies"
+#| fig-cap-location: top
+
+df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
   mutate(condition = case_when(
@@
     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
+    TRUE ~ as.character(condition)))
+
+subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
+plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
+print(plot_means_all)
+
+# png("plot_means_all.png")
+# plot_means_all
+# dev.off()
+
+```
+@tbl-coefs
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-coefs
+#| tbl-cap: "Summary statistics of the estimated SMDs"
+#| tbl-cap-location: top
+
+# Prepare to tabulate
+
+table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
   relocate("n", .after = "condition")
@@
 ```
-
-![Figure 1.](plot_means_all.pdf)
-
-![](plot_means_all.pdf)
 
@@
 
+coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
 subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
-#print(plot_means_wl)
-pdf(file = "plot_means_wl.pdf")
-plot_means_wl
-dev.off()
+plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+print(plot_means_no_wl)
+
+# png("plot_means_no_wl.png")
+# plot_means_no_wl
+# dev.off()
 
@@
 
-![](plot_means_wl.pdf)
-
 We next analysed the data after excluding sub-clinical studies. Again, the pattern of results was very similar to that of the overall analyses.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
 
@@
 plot_means_clin <- plot_means_function(coef_and_se_means_clin_study, subtitle_text_clin)
-pdf(file = "plot_means_clin.pdf")
-plot_means_clin
-dev.off()
+print(plot_means_clin)
+
+# png("plot_means_clin.png")
+# plot_means_clin
+# dev.off()
 
@@
 
-![](plot_means_clin.pdf)
-
 Finally, we examined the data including only those studies that used the CDRS, which yielded a very similar pattern of results.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
 
@@
 plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
-pdf(file = "plot_means_cdrs.pdf")
-plot_means_cdrs
-dev.off()
+print(plot_means_cdrs)
+
+# png("plot_means_cdrs.png")
+# plot_means_cdrs
+# dev.off()
 
@@
 
-![](plot_means_cdrs.pdf)
-
-#### Effect of standard errors of the SMDs .
+#### Effect of standard errors of the SMDs
+
+It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
+To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
+If standard error distributions were influential, this should show up as substantial variability across simulations.
+We test this idea in the Figure X which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table X).
+As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
+the value of z = 1.645.
 
@@
 
-pdf(file = "stab_sims.pdf")
-stab_sims
-dev.off()
+print(stab_sims)
+
 ```
-
-It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
-To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
-If standard error distributions were influential, this should show up as substantial variability across simulations.
-We test this idea in the Figure X which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table X).
-As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
-the value of z = 1.645.
-
-![](stab_sims.pdf)
 
@@
 
-PRISMA chart summarising the screening process for the systematic review.
+Table S1: Included studies.
+
+Figure S1: PRISMA chart summarising the screening process for the systematic review.
+
+![Figure S1](PRISMA.png)
 

### 2024-04-23 Manuscript_for_rendering_in_word.qmd
Getting there Autonumbering of tables and figures now working

@@
     note:
+  - name: Rudolf Uher
+    email: uher@Dal.Ca
+    affiliations:
+        - id: dal
+          name: Dalhousie University
+          department: Department of Psychiatry
+          address: 
+          city: Nova Scotia
+          state: 
+          postal-code: 
+          country: Canada
   - name: Dayna Bhudia
@@
         - ref: ucl_1
-  - name: Despina Miliou
+  - name: Despoina Miliou
     email: dgmiliou@outlook.com.gr
@@
         - ref: ucl_1
-  - name: Giannis Rokas
+  - name: Ioannis-Marios Rokas
     email: <rokasgiannis93@gmail.com
@@
         - ref: ucl_1
+  - name: Marinos Kyriakopoulos 
   - name: Lucy Foulkes
@@
 fig-cap-location: top
-
 ---
@@
 library(dplyr)
+library(broom)
 
@@
 
-Indeed, comparing outcomes (Y) between psychotherapy and medication trials requires us to contrast what is called the sample average treatment effect $\tau$ of each, defined in the following way:
-
-$$
-\tau_{psy} =  E(Y_{1} - Y_{0} \,|\, S, psy)
-$$ $$
-\tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\ 
-$$
-
-where the operator E denotes the expectation over the differences in outcomes between those who received the intervention (T = 1) and those who received the control condition (T = 0), for each sample, $S$, where psy and med stand for psychotherapy and medication respectively.
-
-Obviously, this comparison rests on the assumption that trials in both modalities sample from the same population, $P$, of patients. Formally, this can be expressed as follows:
-
-$$E(Y_{1} \,|\, \text{S, psy}) = E(Y_{1} \,|\, P, \text{psy})$$
-
-$$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$
-
-signifying that the effect found in the population would be expected to be found in the same population for each treatment.
+<!-- Indeed, comparing outcomes (Y) between psychotherapy and medication trials requires us to contrast what is called the sample average treatment effect $\tau$ of each, defined in the following way: -->
+
+<!-- $$ -->
+
+<!-- \tau_{psy} =  E(Y_{1} - Y_{0} \,|\, S, psy) -->
+
+<!-- $$ $$ -->
+
+<!-- \tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\  -->
+
+<!-- $$ -->
+
+<!-- where the operator E denotes the expectation over the differences in outcomes between those who received the intervention (T = 1) and those who received the control condition (T = 0), for each sample, $S$, where psy and med stand for psychotherapy and medication respectively.
+-->
+
+<!-- Obviously, this comparison rests on the assumption that trials in both modalities sample from the same population, $P$, of patients. Formally, this can be expressed as follows: -->
+
+<!-- $$E(Y_{1} \,|\, \text{S, psy}) = E(Y_{1} \,|\, P, \text{psy})$$ -->
+
+<!-- $$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$ -->
+
+<!-- signifying that the effect found in the population would be expected to be found in the same population for each treatment. -->
 
 This assumption, that medication and psychotherapy trials sample from the same population, may be hard to meet.
-Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy versus medication trials.
+Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy and medication trials.
 Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, sex and comorbidity.
@@
 
-We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review (May 31 2015 up to Jan 1 2021) to ensure we analysed an equivalently up-to-date database of medication trials.
-We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
-We also searched trial registers for published and unpublished studies.
-We used the same search terms as Cipriani (2016) with one additional search term to include only placebo-controlled trials (see Supplement X for further details).
-We used Covidence, an online software tool, to manage our systematic review.
-In total, our search produced 538 studies, 88 of which were duplicates and subsequently removed.
+We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
+Please see the Supplementary Materials for further details.
+Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
 Two study authors independently completed title and abstract screenings for 450 studies, and full text screening for 38 studies.
 7 studies met inclusion criteria and data extraction was completed for these papers.
-Clinical trial registers were also systematically searched however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
 
@@
 
+Please refer to the Supplementary Materials for a detailed description of our analyses including the formalisms on which they are based.
+
 ### Trial and sample characteristics
 
-We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy versus medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
+We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
 Meta-analyses were implemented using R's Meta package.
 
-In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
-
-$$
-\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
-The standard deviation is calculated thus:
-
-$$
-\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline.
+<!-- In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism: -->
+
+<!-- $$ -->
+<!-- \text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}} -->
+<!-- $$ -->
+
+<!-- where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
+The standard deviation is calculated thus: -->
+
+<!-- $$ -->
+<!-- \text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}} -->
+<!-- $$ -->
+
+<!-- where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline. -->
 
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as:
-
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
-
-where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
-If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD).
+
+<!-- which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as: -->
+
+<!-- $$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ -->
+
+<!-- where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
+-->
+
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], as detailed in the Supplementary Materials.
+
+<!-- If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
 For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
@@
 Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis.
-
-For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
-
-$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$
-
-where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
+-->
+
+For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD.
+This requires a correlation between the pre- and post-measures, an effect typically not reported.
+To ensure that our results are not biased by misestimation we simulated n = 1000 datasets for different ranges (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
+
+<!-- This is calculated according to: -->
+
+<!-- $$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$ -->
+
+<!-- where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
 This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
@@
 Still, to alleviate such concerns we have used a simulations.
-
-In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
-
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
-
-for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
+-->
+
+<!-- In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics: -->
+
+<!-- $$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$ -->
+
+<!-- for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
 We then used these simulated datasets in the subsequent metanalyses.
+-->
 
@@
 We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
-The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
-Therefore, we can estimate a two stage model with:
-
-$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$
-
-$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
-$$
-
-where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
+
+<!-- The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+Therefore, we can estimate a two stage model with: -->
+
+<!-- $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2) -->
+<!-- $$ -->
+
+<!-- $$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2) -->
+<!-- $$ -->
+
+<!-- where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
 Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
-
-This then gives rise to:
-
-$$Y_i = x_i\beta_i + u_i + \epsilon_i$$
-
-where,
-
-$$u_i \sim N(0, \tau^2) $$
-
-describes the deviation of each study from the mean of the distribution, and,
-
-$$\epsilon_i \sim N(0, \sigma^2)$$
-
-describes the sampling error.
-
-We can then specify the following model to obtain the means of each arm of the trials as follows:
-
-$$ \begin{aligned}
-    Υ_i &=
-    \begin{cases}
-        0 & MedControl:  b_0 + u_i + \epsilon_i\\
-        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
-        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
-        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
-    \end{cases}
-\end{aligned}$$
-
-where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
+-->
+
+<!-- This then gives rise to: -->
+
+<!-- $$Y_i = x_i\beta_i + u_i + \epsilon_i$$ -->
+
+<!-- where, -->
+
+<!-- $$u_i \sim N(0, \tau^2) $$ -->
+
+<!-- describes the deviation of each study from the mean of the distribution, and, -->
+
+<!-- $$\epsilon_i \sim N(0, \sigma^2)$$ -->
+
+<!-- describes the sampling error. -->
+
+<!-- We can then specify the following model to obtain the means of each arm of the trials as follows: -->
+
+<!-- $$ \begin{aligned} -->
+<!--     Υ_i &= -->
+<!--     \begin{cases} -->
+<!--         0 & MedControl:  b_0 + u_i + \epsilon_i\\ -->
+<!--         1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\ -->
+<!--         2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\ -->
+<!--         3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\ -->
+<!--     \end{cases} -->
+<!-- \end{aligned}$$ -->
+
+<!-- where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
 for level 3, $b_{3_{i}}$ the psychotherapy controls.
@@
 Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on the contrasts is done as follows:
-
-$$
-z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
-$$
-
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
+Inference on the contrasts is done as follows: -->
+
+<!-- $$ -->
+<!-- z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} -->
+<!-- $$ -->
+
+<!-- We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014]. -->
 
@@
 We then conducted a series of sensitivity analyses of our results.
-For each of the metanalyses we excluded 1) studies which recruited participants with subclinical levels of depression and 2) studies that used waitlist as their control condition.
+For each of the metanalyses we excluded 1) studies that used waitlist as their control condition and 2) studies which recruited participants with subclinical levels of depression.
 
@@
 
-### Comparing the control versus active arms of psychotherapy trials
-
-We ran t-tests to compare the active versus control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
+### Comparing the control and active arms of psychotherapy trials
+
+We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
 We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and period of the intervention.
@@
 
+# D Clinical Levels Depression Sensitivity Analysis ---------------------------------------
+
+# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
+
+#take study ids where sample has clinical levels of depression
+clin_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_clin_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% clin_study_ids,]
+}
+
+# count the number of studies
+study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
+# CB checked, correct.
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
+coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
+
+# add the ns to the dataframe
+coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
+
 # E. CDRS Sensitivity Analysis ---------------------------------------
@@
 
-# F Clinical Levels Depression Sensitivity Analysis ---------------------------------------
-
-# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
-
-#take study ids where sample has clinical levels of depression
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
+# E. HAMD Sensitivity Analysis ---------------------------------------
+
+hamd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
 
 # use those ids to subset all dataframes in the list
-list_clin_study <- list()
+list_hamd_study <- list()
 
@@
 
-  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% clin_study_ids,]
+  list_hamd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                          %in% hamd_study_ids,]
 }
@@
 # count the number of studies
-study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
+study_count_hamd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% hamd_study_ids,])
 # CB checked, correct.
 
-# apply the metareg function to the list of clinical studies
+# apply the metareg function to the list of cdrs studies
 model_1 <- as.formula(~ four_level_var)
-list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
+list_model_1_hamd_study <- run_metaregression(list_hamd_study , model_1)
 
@@
 condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
+aggregate_results_hamd_study <-  aggregate_model_results(list_model_1_hamd_study, condition)
+
+# extract SMDs from the list for cdrs
+means_hamd_study <-  lapply(list_model_1_hamd_study, extract_coefficients_func)
 
@@
 condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
-coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
+coef_and_se_means_hamd_study <- calculate_mean_coefs_ses(means_hamd_study, condition)
+coef_and_se_means_hamd_study <- data.frame(cbind(condition, coef_and_se_means_hamd_study))
 
 # add the ns to the dataframe
-coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
+coef_and_se_means_hamd_study <- left_join(coef_and_se_means_hamd_study, study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>% 
                                         ungroup() %>% 
@@
 
-## Sample characteristics at baseline in medication versus psychotherapy trials
-
-Table 1 summarises the results from each of the meta-analyses examining sample characteristics at baseline.
+## Sample characteristics at baseline in medication and psychotherapy trials
+
+@tbl-baseline_results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
 The summary statistics are provided for each subgroup (i.e.
-for medication and psychotherapy trials) and the p-value derives from the test for subgroup differences.
-Full results for each of the sensitivity analyses are included in the Supplementary Materials (Tables S1 - S3).
+for medication and psychotherapy RCTs) and the p-value derives from the test for subgroup differences.
 
@@
 
-# Lets make a table that combines across these baseline characteristics variables
-# This is for overall sample only, with separate sensitivity analyses in the supplement
-
-# df_overall_baseline_results <- rbind(results_met_sev, results_met_perc_women_overall, results_met_age)
-# 
-# # For row names
-# df_overall_baseline_results <- df_overall_baseline_results %>%
-#   mutate(subgroup = case_when(
-#     row_number() == 1 ~ "Severity",
-#     row_number() == 4 ~ "Percent Female",
-#     row_number() == 7 ~ "Age",
-#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-#   )) 
-# 
-# # Define new column names
-# new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-# 
-# # Assign new column names to the data frame
-# colnames(df_overall_baseline_results) <- new_column_names
-# 
-# # Rounding
-# df_overall_baseline_results <- df_overall_baseline_results %>%
-#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-#   mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
-# 
-# big_border = fp_border(color="black", width = 1)
-# small_border = fp_border(color="lightgray", width = 1)
-
-# Too basic, limited formatting options
-# 
-# knitr:: kable(df_overall_baseline_results, caption="Sample characteristics at baseline across medication and psychotherapy studies")
-# 
-# gt(df_overall_baseline_results) %>%
-#   tab_header(
-#     title = md("Test this"),
-#     subtitle = md("And this"))
-# 
-# This doesn't work when rendering to word doc
-# 
-#   kbl(align = "l", caption = "Sample characteristics at baseline across medication and psychotherapy studies", escape = F) %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB", extra_css = "border-bottom: 1px black;" ) %>%
-#   row_spec(row = 1, bold = T) %>%
-#   row_spec(c(4, 7), bold = T, extra_css = "border-top: 1px solid black;") %>%
-#   column_spec(1, border_right = T) %>%
-#   add_indent(c(2, 3, 5, 6, 8, 9))
-# 
-# this doesn't have a caption when rendering to word. workaround below, adding caption as header row.
-# 
-# flextable(df_overall_baseline_results) %>%
-#   set_caption("Sample characteristics at baseline across medication and psychotherapy studies") %>%
-#   bold(part = "header") %>%  # Bold the header row
-#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-#   border_outer(border = small_border) %>%  # Add outer borders
-#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>%
-#   hline(part = "header", border = big_border) %>%
-#   vline(j = 1, border = big_border) %>%
-#   set_table_properties(width = .75) %>%  # Set table width
-#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-#   autofit() %>%  # Autofit column widths
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>%
-#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-
 # This is if we want to have all sensitivity analyses in table one
@@
 small_border = fp_border(color="lightgray", width = 1)
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-baseline_results
+#| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies"
+#| tbl-cap-location: top
 
@@
   as_flextable(hide_grouplabel = TRUE) %>% 
-  paginate(group = "category", group_def = "rle") %>% 
+  paginate(group = "category") %>% 
   bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width
+  autofit() %>%  # Autofit column widths
   bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
-  autofit() %>%  # Autofit column widths
   padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>% # indent some rows
@@
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  add_header_row(values = "Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% # This is a work around for the problems with rendering captions
-  add_header_row(values = "Table 1", colwidths = 8) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
+  # add_header_row(values = "Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% # This is a work around for the problems with rendering captions
+  # add_header_row(values = "Table 1", colwidths = 8) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders that look strange
   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
   vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
   line_spacing(space = .7, part = "all")
@@
 On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials.
-The statistics provided in Table 1 are baseline depression scores transformed to reflect percentage of a scale range.
+The statistics provided in @tbl-baseline_results are baseline depression scores transformed to reflect percentage of a scale range.
 To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
 range of 96).
-From Table 1, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
+From @tbl-baseline_results, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
 
@@
 For this analysis, we excluded the two psychotherapy trials which included entirely female samples.
-As can be seen in Table 1, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
+As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
 On average, samples were `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`) female across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`) female across medication trials.
@@
 
-As can be seen in Table 1, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+As can be seen in @tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 ### Number of sites
@@
   mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-sites-summary
+#| tbl-cap: "Number of sites across medication and psychotherapy studies"
+#| tbl-cap-location: top
 
 flextable(df_sites_summary_stats) %>%
-  set_table_properties(width = 1, layout = "autofit") %>%
+  # set_table_properties(width = 1, layout = "autofit") %>%
   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
@@
                       "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
-  add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
-  add_header_row(values = "Table 2", colwidths = 4) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
+  # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
+  # add_header_row(values = "Table 2", colwidths = 4) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>%
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>%
   padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
@@
 
-# This is for if we want to render to pdf
-
-# df_sites_summary_stats <- df_sites_summary_stats %>%
-#   kbl(caption = "Number of sites across medication and psychotherapy studies") %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB") %>%
-#   column_spec(column = 1, border_right = T)
-
-# sites_t_test_stats %>%
-#   kbl(align = "l", caption = "Results for t-test comparing number of sites between medication and psychotherapy studies") %>%
-#   kable_material(lightable_options = c("hover"), full_width = FALSE) %>%
-#   row_spec(row = 0, background = "#EBEBEB") %>%
-#   column_spec(column = 1, border_right = T)
-
 ```
 
-There was a significant difference between the number of sites in medication versus psychotherapy trials, as can be seen in Table 2.
+There was a significant difference between the number of sites in medication and psychotherapy trials, as can be seen in @tbl-sites-summary.
 Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
@@
 As can be seen in @fig-plot-means-all there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see Table 3 below).
+In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see @tbl-coefs-overall).
 
@@
 ```
-@tbl-coefs
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: tbl-coefs
+#| label: tbl-coefs-overall
 #| tbl-cap: "Summary statistics of the estimated SMDs"
@@
 flextable(table_mean_coefs_from_sim) %>%
-  set_table_properties(width = 1, layout = "autofit") %>%
+  set_table_properties(width = 1) %>%
   autofit() %>%
   font(fontname = "Calibri", part = "all") %>% 
-  add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
-  add_header_row(values = "Table 3", colwidths = 6) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
+  # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
+  # add_header_row(values = "Table 3", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
   align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
@@
 
-In Table 4, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
 In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
@@
 ```{r, warning=FALSE, message = FALSE, echo = FALSE}
+#| label: tbl-results-overall
+#| tbl-cap: "Results from metaregression with overall sample"
+#| tbl-cap-location: top
 
@@
 flextable(table_aggregate_results_overall) %>%
-  set_table_properties(width = 1, layout = "autofit") %>%
+  set_table_properties(width = 1) %>%
   autofit() %>%
@@
                       "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
-  add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-  add_header_row(values = "Table 4", colwidths = 6) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
+  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
+  # add_header_row(values = "Table 4", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
   align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
@@
 
-##### Sensitivity analyses
+#### Sensitivity analyses
 
@@
 First, we analysed the data after excluding waitlist control studies.
-As can be seen, the pattern of results is very similar to that of the overall analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
-print(plot_means_no_wl)
-
-# png("plot_means_no_wl.png")
-# plot_means_no_wl
-# dev.off()
-
-```
-
-We next analysed the data after excluding sub-clinical studies. Again, the pattern of results was very similar to that of the overall analyses.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
-plot_means_clin <- plot_means_function(coef_and_se_means_clin_study, subtitle_text_clin)
-print(plot_means_clin)
-
-# png("plot_means_clin.png")
-# plot_means_clin
-# dev.off()
-
-```
-
-Finally, we examined the data including only those studies that used the CDRS, which yielded a very similar pattern of results.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
-plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
-print(plot_means_cdrs)
-
-# png("plot_means_cdrs.png")
-# plot_means_cdrs
-# dev.off()
-
-```
-
-#### Effect of standard errors of the SMDs
-
-It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
-To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
-If standard error distributions were influential, this should show up as substantial variability across simulations.
-We test this idea in the Figure X which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in Table X).
-As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
-the value of z = 1.645.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# examine the stability of the simulations
-
-z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_meta_reg)){
-z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
-
-}
-
-stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-
-stab_sims <- stability_sims %>%
-  ggplot(aes(x = n_sims, y = z_value)) +
-  geom_point() +
-  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
-           hjust = -0.1, vjust = 0) +
-  theme_minimal() +
-  labs(
-    x = "Number of Simulations",
-    y = "z-value",
-    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-    subtitle = "Results from 1000 simulations with within-group standard errors"
-  )
-
-print(stab_sims)
-
-```
+As can be seen in @fig-plot-means-no-wl (see Supplementary Materials), the pattern of results is very similar to that of the overall analyses.
+
+We next analysed the data after excluding sub-clinical studies. Again, the pattern of results was very similar to that of the overall analyses (see @fig-plot-means-clin in Supplementary Materials).
+
+Next, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs in Supplementary Materials).
+Medication control and psychotherapy control conditions remained significantly different, however the small number of psychotherapy studies using the CDRS resulted in less precise metanalytic estimates of within-group changes.
+
+Similarly, when we examined the data including only those studies that used the HAM-D (see @fig-plot-means-hamd in Supplementary Materials), medication control and psychotherapy control conditions remained significantly different though the small number of medication studies using the HAM-D resulted in less precise metanalytic estimates of within-group changes.
+
+Further, we showed with our simulations that the effects of different values for the pre-post measures has minimal effect on the estimated outcomes; please refer to @fig-stab-sims in the Supplement.
 
@@
 
-As can be seen in Tables X and Y, the baseline scores in medication studies were on average substantially higher for the CDRS (10.9 points for the control arms) and the HAM-D (7.3 points for the control arms), respectively.
-The differences were significant at p\<0.05 for CDRS, thought they did not reach statistical significance for the HAM-D (p = 0.0573).
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(results_cdrs_metareg_baseline[[2]], caption="Table 3a CDRS baselilne scores")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable(results_hamd_metareg_baseline[[2]], caption="Table 3b HAM-D baselilne scores")
-```
-
-We next addressed potential regression to the mean by residualising SMDs by the baseline scores in one regression model.
+As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher for the CDRS and the HAM-D.
+The differences between medication control and psychotherapy control arms were significant at p\<0.05 for the CDRS, though they did not reach statistical significance for the HAM-D (p = `r round(results_hamd_metareg_baseline[[1]][results_hamd_metareg_baseline[[1]]$condition == "psychotherapy_control", "p.value"], 3)`).
 
@@
 
-Table X shows the adjusted SMDs with their confidence intervals that we estimated in metaregression.
+We next addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplementary Materials for the adjusted SMDs with their confidence intervals).
 As can be inferred from the non-overlapping confidence intervals, there were significant differences between the medication control and psychotherapy control arms.
 
+## Comparing the nature and intensity of control conditions in psychotherapy trials
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# knitr:: kable (df_mean_coefs_from_sim_adjusted_cohens_d, caption = "Table 5. SMDs Adjusted by baseline score" )
-```
-
-Finally, we tested whether the simulated correlation values we used for simulation of the standard errors had an appreciable effect on the values of the adjusted SMDs.
-Supplemental Figure X shows that the variability of the estimated z-value was minimal<!--# Charlotte, the figure below should be supplemental-->.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# 
-# # plot the mean z for the difference between controls
-# z_psy_con_vs_med_con <- 0
-# for(i in 1: length(list_model_1_meta_reg_adj_cohens_d )){
-#   z_psy_con_vs_med_con[i] <- list_model_1_meta_reg_adj_cohens_d [[i]]$zval[condition=="psychotherapy_control"]
-#   
-# }
-# 
-# 
-# 
-# stability_sims_adjusted_cohens_d <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-# 
-# 
-# stab_sims_adjusted_cohens_d <- stability_sims_adjusted_cohens_d %>%
-#   ggplot(aes(x = n_sims, y = z_value)) +
-#   geom_point() +
-#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-#                arrow = arrow(length = unit(0.3, "cm")),
-#                color = "black") +
-#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-#   annotate("text", x = 300, y = stability_sims_adjusted_cohens_d$z_value[1] - 0.1, label = "simulated z-values",
-#            hjust = -0.1, vjust = 0) +
-#   theme_minimal() +
-#   labs(
-#     x = "Number of Simulations",
-#     y = "z-value",
-#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-#     subtitle = "Results from 1000 simulations with within-group standard errors"
-#   )
-# stab_sims_adjusted_cohens_d
-# pdf(file = "stab_sims_adjusted_cohens_d.pdf")
-# stab_sims_adjusted_cohens_d
-# dev.off()
-
-```
-
-## Comparing the nature and intensity of control conditions in psychotherapy trials
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 # We need to read in the appropriate dataset which describes the active and control conditions used in
@@
   mutate(across(where(is.numeric), ~round(., 2)))
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-intensity-of-int
+#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
+#| tbl-cap-location: top
 
@@
   bold(i = c(1, 4, 7, 10, 13), bold = TRUE, part = "body") %>%  
-  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width 
+  set_table_properties(width = 1) %>%  # Set table width 
   autofit() %>%  # Autofit column widths 
@@
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
-  add_header_row(values = "Table 5", colwidths = 4) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
+  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
+  # add_header_row(values = "Table 5", colwidths = 4) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  #italic(i = 2, italic = TRUE, part = "header") %>% 
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  hline(part = "header", border = big_border) %>% 
+  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
   paginate(init = TRUE) %>% 
   line_spacing(space = .7, part = "all")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
   mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-t-tests-intensity
+#| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
+#| tbl-cap-location: top
 
 flextable(control_summary_t_tests) %>%
-  set_table_properties(width = 1, layout = "autofit") %>%  # Set table width %>% 
+  set_table_properties(width = 1) %>%  # Set table width %>% 
   autofit() %>%  # Autofit column widths 
@@
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-  add_header_row(values = "Table 6", colwidths = 6) %>% 
-  bold(i = c(1, 3), part = "header") %>%   # Bold the relevant header rows
-  bg(i = 3, bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  italic(i = 2, italic = TRUE, part = "header") %>% 
+  #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
+  #add_header_row(values = "Table 6", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  #italic(i = 2, italic = TRUE, part = "header") %>% 
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(i = 3, part = "header", border = big_border) %>% 
-  padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  hline(part = "header", border = big_border) %>% 
+  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
   paginate(init = TRUE) %>% 
@@
 
-Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see Table 6 for summary statistics).
+Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see @tbl-intensity-of-int for summary statistics).
 Active intervention arms featured significantly more sessions than control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
 These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`).
-The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention period (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
+The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
 
@@
 
-# Supplement
-
-Table S1: Included studies.
-
-Figure S1: PRISMA chart summarising the screening process for the systematic review.
-
-![Figure S1](PRISMA.png)
+# Supplementary Materials
+
+## Systematic review
+
+We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
+after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review).
+We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
+We used the same search terms as Cipriani (2016) with one additional search term to include only placebo-controlled trials (see below).
+We additionally applied filters to specify our date range, and to exclude reviews and non-human studies.
+We also searched clinical trial registers for published and unpublished studies however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
+Please see @fig-prisma for the PRISMA flow diagram.
+We used Covidence, an online software tool, to manage our systematic review.
+
+**Search terms**
+
+Explicit search strategy: title/abstract = (depress* or dysthymi\* or "mood disorder\*" or "affective disorder*") AND (adolesc\* or child\* or boy\* or girl\* or juvenil\* or minors or paediatri\* or pediatri\* or pubescen\* or school\* or student\* or teen\* or young or youth\*) AND (selective serotonin reuptake inhibitor or SSRI or citalopram or fluoxetine or paroxetine or sertraline or escitalopram or fluvoxamine or serotonin norepinephrine reuptake inhibitor\* or SNRI or venlafaxine or duloxetine or milnacipran or reboxetine or bupropion or noradrenergic and specific serotonergic antidepressants or NaSSA or mirtazapine or TCA or tricyclic or amersergide or amineptine or amitriptyline or amoxapine or butriptyline or chlorpoxiten or clomipramine or clorimipramine or demexiptiline or desipramine or dibenzipin or dothiepin or doxepin or imipramine or lofepramine or melitracen or metapramine or nortriptyline or noxiptiline or opipramol or protriptyline or quinupramine or tianeptine or trimipramine) AND (placebo)
+
+```{r, echo=FALSE}
+#| label: fig-prisma
+#| fig-cap: "PRISMA chart summarising the screening process for the systematic review"
+#| fig-cap-location: top
+knitr::include_graphics("PRISMA.png")
+```
+
+## Statistical Analysis (including formalisms)
+
+### Trial and sample characteristics
+
+We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
+Meta-analyses were implemented using R's Meta package.
+
+In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
+
+$$
+\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
+$$
+
+where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
+The standard deviation is calculated thus:
+
+$$
+\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
+$$
+
+where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline.
+
+We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
+
+### Measures of Effect
+
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as:
+
+$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
+
+where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
+If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
+For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
+If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis.
+
+For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
+
+$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$
+
+where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
+This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
+However, this practice has given rise to concerns about misestimation.
+Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e.
+bias estimation of the effects for the control group of medication compared to those of psychotherapy.
+Still, to alleviate such concerns we have used a simulations.
+
+In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
+
+$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
+
+for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
+We then used these simulated datasets in the subsequent metanalyses.
+
+### Random Effects Metaregression
+
+We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
+The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+Therefore, we can estimate a two stage model with:
+
+$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
+$$
+
+$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
+$$
+
+where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
+Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
+
+This then gives rise to:
+
+$$Y_i = x_i\beta_i + u_i + \epsilon_i$$
+
+where,
+
+$$u_i \sim N(0, \tau^2) $$
+
+describes the deviation of each study from the mean of the distribution, and,
+
+$$\epsilon_i \sim N(0, \sigma^2)$$
+
+describes the sampling error.
+
+We can then specify the following model to obtain the means of each arm of the trials as follows:
+
+$$ \begin{aligned}
+    Υ_i &=
+    \begin{cases}
+        0 & MedControl:  b_0 + u_i + \epsilon_i\\
+        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
+        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
+        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
+    \end{cases}
+\end{aligned}$$
+
+where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
+for level 3, $b_{3_{i}}$ the psychotherapy controls.
+The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
+Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
+Inference on the contrasts is done as follows:
+
+$$
+z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
+$$
+
+We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
+
+We present the SMDs of each level of the dummy variable of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
+The SMDs are the means across the 1000 simulated datasets.
+
+## Metaregression sensitivity analyses
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-no-wl
+#| fig-cap: "Metanalytic estimates of within-group changes: wl excluded"
+#| fig-cap-location: top
+
+coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+print(plot_means_no_wl)
+
+# png("plot_means_no_wl.png")
+# plot_means_no_wl
+# dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-clin
+#| fig-cap: "Metanalytic estimates of within-group changes: subclinical studies excluded"
+#| fig-cap-location: top
+
+coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
+plot_means_clin <- plot_means_function(coef_and_se_means_clin_study, subtitle_text_clin)
+print(plot_means_clin)
+
+# png("plot_means_clin.png")
+# plot_means_clin
+# dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-cdrs
+#| fig-cap: "Metanalytic estimates of within-group changes: CDRS studies only"
+#| fig-cap-location: top
+
+coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
+plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
+print(plot_means_cdrs)
+
+# png("plot_means_cdrs.png")
+# plot_means_cdrs
+# dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-hamd
+#| fig-cap: "Metanalytic estimates of within-group changes: HAM-D studies only"
+#| fig-cap-location: top
+
+coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study, subtitle_text_hamd)
+print(plot_means_hamd)
+
+# png("plot_means_cdrs.png")
+# plot_means_cdrs
+# dev.off()
+
+```
+
+#### Effect of standard errors of the SMDs
+
+It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
+To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
+If standard error distributions were influential, this should show up as substantial variability across simulations.
+We test this idea in the @fig-stab-sims which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in @tbl-results-overall).
+As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
+the value of z = 1.645.
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-stab-sims
+#| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
+#| fig-cap-location: top
+
+# examine the stability of the simulations
+
+z_psy_con_vs_med_con <- 0
+for(i in 1: length(list_model_1_meta_reg)){
+z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
+
+}
+
+stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+
+stab_sims <- stability_sims %>%
+  ggplot(aes(x = n_sims, y = z_value)) +
+  geom_point() +
+  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
+           hjust = -0.1, vjust = 0) +
+  theme_minimal() +
+  labs(
+    x = "Number of Simulations",
+    y = "z-value",
+    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
+    subtitle = "Results from 1000 simulations with within-group standard errors"
+  )
+
+print(stab_sims)
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-cdrs-baseline
+#| tbl-cap: "CDRS Baseline Scores"
+#| tbl-cap-location: top
+
+flextable(results_cdrs_metareg_baseline[[1]])
+flextable(results_cdrs_metareg_baseline[[2]])
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-hamd-baseline
+#| tbl-cap: "HAM-D Baseline Scores"
+#| tbl-cap-location: top
+
+flextable(results_hamd_metareg_baseline[[1]])
+flextable(results_hamd_metareg_baseline[[2]])
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-adj-smds
+#| tbl-cap: "SMDs adjusted by baseline scores"
+#| tbl-cap-location: top
+
+flextable(df_mean_coefs_from_sim_adjusted_cohens_d)
+
+```
 

### 2024-04-24 Manuscript_for_rendering_in_word.qmd
Fiddling

@@
   bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  autofit() %>%  # Autofit column widths
+  set_table_properties(layout = "autofit") %>%  # Autofit column widths
   bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
@@
 flextable(df_sites_summary_stats) %>%
-  # set_table_properties(width = 1, layout = "autofit") %>%
+  set_table_properties(width = 1, layout = "fixed") %>%
   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
@@
 
-As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher for the CDRS and the HAM-D.
+As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher than psychotherapy studies for the CDRS and the HAM-D.
 The differences between medication control and psychotherapy control arms were significant at p\<0.05 for the CDRS, though they did not reach statistical significance for the HAM-D (p = `r round(results_hamd_metareg_baseline[[1]][results_hamd_metareg_baseline[[1]]$condition == "psychotherapy_control", "p.value"], 3)`).
@@
 ```
+The following tables still need some work including adding n
 
@@
 
-flextable(results_cdrs_metareg_baseline[[1]])
-flextable(results_cdrs_metareg_baseline[[2]])
+# Prepare to tabulate
+
+# Regression results
+
+table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
+  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "term") %>% 
+  select(-c("term", "type"))
+
+flextable(table_1_cdrs_metareg_baseline) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
+table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
+  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "baseline_smds")
+
+flextable(table_2_cdrs_metareg_baseline) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-flextable(results_hamd_metareg_baseline[[1]])
-flextable(results_hamd_metareg_baseline[[2]])
+table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
+  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "term") %>% 
+  select(-c("term", "type"))
+
+flextable(table_1_hamd_metareg_baseline) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
+table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
+  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "baseline_smds")
+
+flextable(table_2_hamd_metareg_baseline) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-flextable(df_mean_coefs_from_sim_adjusted_cohens_d)
+table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
+  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+flextable(table_mean_coefs_from_sim_adjusted_cohens_d) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_mean_coefs_from_sim_adjusted_cohens_d), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
 
@@
 
-# # Plot percentage baseline means
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = perc_baseline_mean, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of % baseline mean by group", x = NULL, y = "Percentage Baseline Mean") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
 ```

### 2024-04-25 Manuscript_for_rendering_in_word.qmd
Fixed HAMD and CDRS tables

@@
 
-There are two principal treatment modalities for adolescent depression: psychotherapy and medication.
+Should a child or an adolescent receive psychotherapy or medication for their depression, and what information should patients, carers and clinicians use to decide?
+
+<!-- There are two principal treatment modalities for adolescent depression: psychotherapy and medication.
 Where does one turn to find the evidence that will inform their treatment options?
@@
 However, the question is particularly difficult to answer for adolescent depression, where there are limited data from head-to-head trials of medication and psychotherapy, and where recommendations must therefore be derived from indirect comparisons of treatment efficacy.
-
-Guidelines, such as the ones that the internationally influential UK National Institute of Health and Care Excellence (NICE) have produced for adolescent depression, are a principal source of such information.
-NICE recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
+-->
+
+The internationally influential UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
 This conclusion is in keeping with two sources of evidence: medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine, for child and adolescent depression [@ciprianiComparativeEfficacyTolerability2016]; and psychotherapy meta-analyses that conclude psychotherapy to be efficacious for child and adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
@@
 In this paper, we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent depression in the following ways.
-First, we compare key baseline characteristics of medication vs psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity of depression; b) percentage females vs males; c) mean age; and d) number of sites involved.
-Second, we determine the standardised mean differences of psychotherapy controls vs medication controls using random effects metanalysis.
-Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number or frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
+First, we compare key baseline characteristics of medication and psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity of depression; b) percentage females vs males; c) mean age; and d) number of sites involved.
+Second, we determine the standardised mean differences of psychotherapy controls and medication controls using random effects metanalysis.
+Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
 
@@
 
-This study was registered on the Open Science Framework (OSF); the protocol can be found [here](https://osf.io/bfmc6). In Supplement X we outline deviations from this pre-registered protocol.
+This study was registered on the Open Science Framework (OSF); the protocol can be found [here](https://osf.io/bfmc6).
 
@@
 
-We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
+We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including severity of depressive symptoms at baseline, sex and age.
 Meta-analyses were implemented using R's Meta package.
@@
 For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD.
-This requires a correlation between the pre- and post-measures, an effect typically not reported.
-To ensure that our results are not biased by misestimation we simulated n = 1000 datasets for different ranges (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
+This requires a correlation between the pre- and post-measures, a statistic typically not reported.
+To ensure that our results are not biased by misestimation we simulated n = 1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
 
@@
 
+Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
+
 ### Comparing the control and active arms of psychotherapy trials
@@
 We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
-We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and period of the intervention.
+We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
 Where a range was provided, the maximum was encoded (e.g.
@@
 In psychotherapy trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions.
-All included trials and the types of treatment controls can be found in Supplementary Table 1.
+All included trials and the types of treatment controls can be found in Table X in the Supplementary Materials.
 
@@
 #| tbl-cap-location: top
-
+knitr::opts_chunk$set(fp_text_default(bold = TRUE))
 df_overall_baseline_results %>% 
@@
   bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  set_table_properties(layout = "autofit") %>%  # Autofit column widths
+  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
   bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  line_spacing(space = .7, part = "all")
+  line_spacing(space = .7, part = "all") %>% 
+  # set_table_properties(width = 1, layout = "autofit") %>% 
+  autofit()
 
@@
 
-We applied metaregression to obtain the SMDs and confidence intervals of each of the four arms.
+We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
 
@@
 
-Similarly, when we examined the data including only those studies that used the HAM-D (see @fig-plot-means-hamd in Supplementary Materials), medication control and psychotherapy control conditions remained significantly different though the small number of medication studies using the HAM-D resulted in less precise metanalytic estimates of within-group changes.
-
-Further, we showed with our simulations that the effects of different values for the pre-post measures has minimal effect on the estimated outcomes; please refer to @fig-stab-sims in the Supplement.
-
-#### Addressing Regression to the Mean
+Similarly, when we examined the data including only those studies that used the HAM-D (see @fig-plot-means-hamd in Supplementary Materials), medication control and psychotherapy control conditions remained significantly different though the small number of medication studies using the HAM-D resulted in less precise metanalytic estimates.
+
+Further, we showed with our simulations that the effects of different values for the pre-post measures had minimal effect on the estimated outcomes; please refer to @fig-stab-sims in the Supplement.
+
+##### Addressing Regression to the Mean
 
@@
                                                          model_1, condition)
+
+results_cdrs_metareg_baseline[[2]] <- left_join(results_cdrs_metareg_baseline[[2]], study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 
@@
 
+results_hamd_metareg_baseline[[2]] <- left_join(results_hamd_metareg_baseline[[2]], study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>% 
+                                        ungroup() %>% 
+                                      select(condition, n),  
+                                    by = "condition")
 ```
@@
   mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+
 ```
@@
 
+```{r, echo=FALSE}
+# Filter the dataframe
+filtered_df <- df_long_for_metan %>%
+  filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
+
+# Count the occurrences of each type
+type_counts <- filtered_df %>%
+  count(type) %>%
+  mutate(total_count = sum(n),
+         wl_cau_sum = sum(n[type %in% c("wl", "cau")]),
+         wl_cau_percentage = wl_cau_sum / total_count * 100)
+
+```
+
 This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression.
@@
 Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9).
-Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally advised against (CITE).
+Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally ill advised.
 This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical.
@@
 Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption.
-Most (XXX %) of psychotherapy RCT control conditions are either waitlist control or treatment as usual, both of which are very likely to create negative expectations for participants not randomized to treatment; thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
+Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either waitlist control or treatment as usual, both of which are very likely to create negative expectations for participants not randomized to treatment; thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
 But we also find that even psychological controls were unreasonable counterfactuals.
@@
 pleasant human contact), aspects such as human contact time should be matched.
-We find that there are vast differences between treatment and control arms in psychotherapy trials (CITE NUMBER) which may lead to an inflation of the true efficacy of psychological treatments.
+We find that there are vast differences between treatment and control arms in psychotherapy trials which may lead to an inflation of the true efficacy of psychological treatments.
 
@@
 Indeed, investment of effort and funds should be directed into providing rigorous evidence that established depression psychotherapies are more efficacious than fair controls.
-There are examples of such psychotherapy RCTS, e.g.
-in social anxiety [@clarkCognitiveTherapyExposure2006a] where such rigor has been applied.
+There are examples of such psychotherapy RCTs, such as @youngRandomizedDepressionPrevention2016 in the current study, where such rigor has been applied.
 
@@
 
+table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "baseline_smds") %>% 
+  relocate("n", .before = "baseline_smds") %>% 
+  relocate("lower_cis_smds", .before = "upper_cis_smds")
+
+new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(table_2_cdrs_metareg_baseline) <- new_column_names
+
+flextable(table_2_cdrs_metareg_baseline) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  font(fontname = "Calibri", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
 # Regression results
@@
 table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
-  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
   mutate(condition = case_when(
@@
   select(-c("term", "type"))
+
+new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+
+# Assign new column names to the data frame
+colnames(table_1_cdrs_metareg_baseline) <- new_column_names
 
@@
 
-table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
-  mutate(across(where(is.numeric), ~round(., 3))) %>%
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-hamd-baseline
+#| tbl-cap: "HAM-D Baseline Scores"
+#| tbl-cap-location: top
+
+# Prepare to tabulate
+
+table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
   mutate(condition = case_when(
@@
     TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "baseline_smds")
-
-flextable(table_2_cdrs_metareg_baseline) %>%
+  relocate("condition", .before = "baseline_smds") %>% 
+  relocate("n", .before = "baseline_smds") %>% 
+  relocate("lower_cis_smds", .before = "upper_cis_smds")
+
+new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(table_2_hamd_metareg_baseline) <- new_column_names
+
+flextable(table_2_hamd_metareg_baseline) %>%
   set_table_properties(width = 1) %>%
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>% 
+  align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>% 
   align(j = 1, align = "left", part = "all") %>% 
@@
 
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: tbl-hamd-baseline
-#| tbl-cap: "HAM-D Baseline Scores"
-#| tbl-cap-location: top
+# Regression results
 
 table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
-  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
   mutate(condition = case_when(
@@
   select(-c("term", "type"))
+
+new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+
+# Assign new column names to the data frame
+colnames(table_1_hamd_metareg_baseline) <- new_column_names
 
@@
 
-table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
-  mutate(across(where(is.numeric), ~round(., 3))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "baseline_smds")
-
-flextable(table_2_hamd_metareg_baseline) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
 ```
@@
 table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
-  mutate(across(where(is.numeric), ~round(., 3))) %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
   mutate(condition = case_when(
@@
     TRUE ~ as.character(condition)))
+
+new_column_names <- c("Condition", "Coefficient", "SE", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(table_mean_coefs_from_sim_adjusted_cohens_d) <- new_column_names
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# # Tables for baseline comparisons
-# 
-# # Lets make a table that combines across the sensitivity analyses for severity
-# 
-# df_severity_sens <- rbind(results_met_sev_cbt, results_met_sev_clin, results_met_sev_no_wl)
-# 
-# # For row names
-# df_severity_sens <- df_severity_sens %>%
-#   mutate(subgroup = case_when(
-#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-#     row_number() == 4 ~ "Excluding subclinical",
-#     row_number() == 7 ~ "Excluding waitlist",
-#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-#   )) 
-# 
-# # Define new column names
-# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-# 
-# # Assign new column names to the data frame
-# colnames(df_severity_sens) <- new_column_names
-# 
-# # Rounding
-# df_severity_sens <- df_severity_sens %>%
-#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-#   mutate_at(vars(ncol(.)), ~ round(., 3))
-# 
-# df_severity_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
-# 
-# flextable(df_severity_sens) %>%
-#   set_caption(caption = "Table S1: Sensitivity analyses for comparison of baseline severity levels between psychotherapy and medication trials") %>%
-#   bold(part = "header") %>%  # Bold the header row
-#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-#   border_outer(border = small_border) %>%  # Add outer borders
-#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-#   hline(part = "header", border = big_border) %>% 
-#   vline(j = 1, border = big_border) %>% 
-#   set_table_properties(width = .75) %>%  # Set table width
-#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-#   autofit() %>%  # Autofit column widths
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-# 
-# # Now sex
-# 
-# df_sex_sens <- rbind(results_met_perc_women_cbt, results_met_perc_women_clin, results_met_perc_women_no_wl) 
-# 
-# # For row names
-# df_sex_sens <- df_sex_sens %>%
-#   mutate(subgroup = case_when(
-#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-#     row_number() == 4 ~ "Excluding subclinical",
-#     row_number() == 7 ~ "Excluding waitlist",
-#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-#   )) 
-# 
-# # Define new column names
-# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-# 
-# # Assign new column names to the data frame
-# colnames(df_sex_sens) <- new_column_names
-# 
-# # Rounding
-# df_sex_sens <- df_sex_sens %>%
-#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-#   mutate_at(vars(ncol(.)), ~ round(., 3))
-# 
-# df_sex_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
-# 
-# flextable(df_sex_sens) %>%
-#   set_caption(caption = "Table S2: Sensitivity analyses for comparison of sex composition between psychotherapy and medication trials") %>%
-#   bold(part = "header") %>%  # Bold the header row
-#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-#   border_outer(border = small_border) %>%  # Add outer borders
-#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-#   hline(part = "header", border = big_border) %>% 
-#   vline(j = 1, border = big_border) %>% 
-#   set_table_properties(width = .75) %>%  # Set table width
-#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-#   autofit() %>%  # Autofit column widths
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-# 
-# # Now age
-# 
-# df_age_sens <- rbind(results_met_age_cbt, results_met_age_clin, results_met_age_clin) 
-# 
-# # For row names
-# df_age_sens <- df_age_sens %>%
-#   mutate(subgroup = case_when(
-#     row_number() == 1 ~ "CBT, fluoxetine and escitalopram",
-#     row_number() == 4 ~ "Excluding subclinical",
-#     row_number() == 7 ~ "Excluding waitlist",
-#     TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-#   )) 
-# 
-# # Define new column names
-# new_column_names <- c(" ", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-# 
-# # Assign new column names to the data frame
-# colnames(df_age_sens) <- new_column_names
-# 
-# # Rounding
-# df_age_sens <- df_age_sens %>%
-#   mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-#   mutate_at(vars(ncol(.)), ~ round(., 3))
-# 
-# df_age_sens %>%
-#   mutate_all(~if_else(is.na(.), "", as.character(.))) 
-# 
-# flextable(df_age_sens) %>%
-#   set_caption(caption = "Table S3: Sensitivity analyses for comparison of age between psychotherapy and medication trials") %>%
-#   bold(part = "header") %>%  # Bold the header row
-#   bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-#   border_outer(border = small_border) %>%  # Add outer borders
-#   hline(i = c(1, 2, 4, 5, 7, 8), border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   hline(i = c(3, 6), border = big_border) %>%  # Add darker horizontal lines after specific rows %>% 
-#   hline(part = "header", border = big_border) %>% 
-#   vline(j = 1, border = big_border) %>% 
-#   set_table_properties(width = .75) %>%  # Set table width
-#   bg(bg = "#F2F2F2", part = "header") %>%  # Add light grey background to header row
-#   autofit() %>%  # Autofit column widths
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri 
-#   padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # Plots  -----------------------

### 2024-04-26 Manuscript_for_rendering_in_word.qmd
fixed alignment + added a few extra bits

@@
     tbl_caption: yes
+    numer-sections: true
+    tbl_align: left
 editor: visual
@@
 fig-cap-location: top
+
 ---
@@
 library(officer)
+library(officedown)
 library(RefManageR)
@@
 bib_data <- ReadBib("emotion_concepts_paper.bib")
+
+knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
 
@@
 
-In this paper, we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent depression in the following ways.
+In this paper, we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent (mean age = 14.05, SE = 0.26) depression in the following ways.
 First, we compare key baseline characteristics of medication and psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity of depression; b) percentage females vs males; c) mean age; and d) number of sites involved.
@@
 
-### Measures of Effect
+### Trial efficacy
+
+#### Measures of Effect
 
@@
 
-### Random Effects Metaregression
+#### Random Effects Metaregression
 
@@
 
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of antidepressant trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy RCTs Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-There were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD were missing and could not be imputed by any of the methods outlined above.
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of medication trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy RCTs.
+Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
+For the meta-regression examining trial efficacy, there were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD were missing and could not be imputed by any of the methods outlined above.
 
@@
 
+met_age$seTE.random
+
 # Looking at clinical sample only
@@
 #| tbl-cap-location: top
-knitr::opts_chunk$set(fp_text_default(bold = TRUE))
+
 df_overall_baseline_results %>% 
@@
   line_spacing(space = .7, part = "all") %>% 
-  # set_table_properties(width = 1, layout = "autofit") %>% 
   autofit()
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-sites-summary
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-coefs-overall
@@
 
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
+```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
 #| label: tbl-results-overall
@@
 #| tbl-cap-location: top
-
+fp_text
 table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-intensity-of-int
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-t-tests-intensity
@@
 
-## Systematic review
+## Systematic review search terms and PRISMA chart
 
@@
 
-## Statistical Analysis (including formalisms)
+## Full description of statistical analysis (including formalisms)
 
@@
 #| fig-cap-location: top
+#| fig-title: Figure S
 
@@
 ```
-
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-cdrs-baseline
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-hamd-baseline
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-adj-smds

### 2024-04-26 Manuscript_for_rendering_in_word.qmd
Most recent version

@@
     numer-sections: true
-    tbl_align: left
 editor: visual
@@
 library(officer)
-library(officedown)
 library(RefManageR)
@@
 
+```
+```{r global_options, include=FALSE}
 knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
-
 ```
@@
 
-met_age$seTE.random
-
 # Looking at clinical sample only
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 #| label: tbl-baseline_results
@@
 #| tbl-cap-location: top
-fp_text
+
 table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
@@
 ```
-The following tables still need some work including adding n
 
@@
 #define groups
-df_long_for_metan <- df_long_for_metan %>%
-  mutate(
-    group = case_when(
-      psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-      TRUE ~ NA_character_
-    )
-  )
-
-group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
+# df_long_for_metan <- df_long_for_metan %>%
+#   mutate(
+#     group = case_when(
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
+#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
+#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
+#       TRUE ~ NA_character_
+#     )
+#   )
+# 
+# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
 
@@
 # Box plot Cohens d by group
-
-ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-  geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-  scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-  geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-  geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-  geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
-               arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-  geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-  scale_fill_manual(values = group_colors) +
-  labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-  theme_minimal() +
-  theme(legend.position = "none")
+# 
+# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
+#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
+#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
+#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
+#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
+#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
+#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
+#   scale_fill_manual(values = group_colors) +
+#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
+#   theme_minimal() +
+#   theme(legend.position = "none")
 

### 2024-05-03 Manuscript_for_rendering_in_word.qmd
Final draft

@@
 
-<!-- There are two principal treatment modalities for adolescent depression: psychotherapy and medication.
-Where does one turn to find the evidence that will inform their treatment options?
-This question is relevant for patients and their carers, for clinicians and for policy makers.
-However, the question is particularly difficult to answer for adolescent depression, where there are limited data from head-to-head trials of medication and psychotherapy, and where recommendations must therefore be derived from indirect comparisons of treatment efficacy.
--->
-
-The internationally influential UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy and interpersonal therapy) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
-This conclusion is in keeping with two sources of evidence: medication meta-analyses that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine, for child and adolescent depression [@ciprianiComparativeEfficacyTolerability2016]; and psychotherapy meta-analyses that conclude psychotherapy to be efficacious for child and adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
-However, such conclusions seem at odds with those of a recent network meta-analysis [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments with each other using both direct (head-to-head) and indirect (indirectly treatment A with treatment C, via studies that directly compare treatments A with B and B with C) evidence.
-Indeed, the network meta-analysis concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
+This question is particularly difficult to answer as there are limited data from head-to-head trials of medication and psychotherapy for adolescent depression, and hence recommendations must be derived from indirect comparisons of treatment efficacy.
+The internationally influential UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
+This conclusion is in keeping with two sources of evidence: meta-analyses of medication trials that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine, for child and adolescent depression [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy trials that conclude psychotherapy to be efficacious for child and adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
+However, such conclusions seem at odds with those of a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
+treatment A with treatment C, via studies that directly compare A with B and B with C) evidence.
+Indeed, this NMA concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
 pill placebo) or psychotherapy controls.
-Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions for adolescent depression?
-
-In this paper, we examine whether the existing evidence base for adolescent depression treatment can offer valid answers to such questions.
-Below, we provide a conceptual framework for answering such questions and test a series of hypotheses using data from existing trials.
+Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
+
+In this paper, we examine whether the existing evidence base for adolescent depression treatment can offer valid answers to this question.
+We provide a conceptual framework for answering such questions and test a series of hypotheses using data from existing trials.
 Two points are crucial to indirect comparisons of treatment modalities with each other.
-
 First, whether the participants of trials in one modality are comparable to those in another modality.
-Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved in a trial, are comparable.
-
-Starting with the first point, to be able to compare between different trials one must assume that these trials sample from the same population.
-If they do not, then the validity of any comparisons, including those conducted through network metanalysis (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable (we provide a more formal account of this in the Supplement).
+Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
+
+Starting with the first point, to compare between different trials one must assume that these trials sample from the same population.
+If they do not, then the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
+the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
+We provide a more formal account of this in the Supplement.
 
@@
 
-This assumption, that medication and psychotherapy trials sample from the same population, may be hard to meet.
-Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias with respect to who participates in psychotherapy and medication trials.
-Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity, sex and comorbidity.
+This assumption that medication and psychotherapy trials sample from the same population may be hard to meet.
+Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
+Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity and sex.
 Some of these characteristics, particularly baseline severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
 
-In terms of the second point, differences in trial design may impact outcomes in a differential way between antidepressant and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-Perhaps the most obvious way in which this happens is the fact that participants in psychotherapy trials are unblinded in terms of treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-By contrast, in new antidepressant trials, patients (and raters) were found to be unlikely to be able to judge treatment allocation [@linAssessmentBlindingRandomized2022].
+In terms of the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
+Most obviously, participants in psychotherapy trials are unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
+By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022].
 This creates differential expectations between medication and psychotherapy trials.
 Importantly, pill-placebo has been developed as the standard medication control in order to match as closely as possible the intervention condition, so as to minimise differences in expectancy between conditions.
-By contrast, psychotherapy control arms vary across waitlist controls, treatment as usual and active controls.
-These differences in expectation favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially magnifying the difference between them).
-This is because of what has been aptly described as "disappointment bias" [@thespininvestigatorsEthicsTrialsCohorts2017], where participants in the active condition are content for receiving the "cutting edge treatment" whilst those in the control are dissatisfied for having missed out on "proper treatment".
-Expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011]; i.e., it is an effect modifier.
-If expectancy effects are different for psychotherapy controls and pill placebo, comparisons between them, including in network metanalysis, become questionable.
-
-Another difference in design that has potential implications for which patients are selected into the trial is the number of sites in a trial.
+By contrast, psychotherapy control arms vary across waitlist controls (WL), treatment as usual (TAU), and active controls.
+Differences in expectation may favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially magnifying the difference between them).
+This is because of what has been aptly described as "disappointment bias" [@reltonEthicsTrialsCohorts2017], where participants in the active condition are content for receiving the "cutting edge treatment" whilst those in the control are dissatisfied for having missed out on "proper treatment".
+Expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011].
+If expectancy effects are different for psychotherapy controls and pill placebo, comparisons between them, including in NMA, become questionable.
+
+Another difference in design is the number of trial sites.
 Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
-This phenomenon may be due to lower quality of phenotyping in such studies, with higher rates of classification errors, entailing higher rates of spontaneous remission or regression to the mean.
+This phenomenon may be due to lower quality of assessments in trials with more sites, with higher rates of classification errors, entailing higher rates of spontaneous remission or regression to the mean.
 It is therefore important to examine whether this basic trial design feature differs between medication and psychotherapy trials.
@@
 Control conditions in trials are meant to generate counterfactual conditions [@guoChapterCounterfactualFramework2014] to the intervention: what would have been the outcome in an individual had they not received the intervention, with all else being equal.
-A control condition such as pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
+A pill placebo condition, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
 The question is whether psychotherapy trials make a similar effort: are for example the number of hours of contact with a human comparable between active and control arms in psychotherapy trials?
@@
 Often, in the public domain, psychotherapy and medication are compared to each other on the basis of their respective effect sizes.
-However, these effect sizes represent differences between the active intervention and the control condition (placebo or psychotherapy control).
-For these effect sizes to be comparable, placebo and psychotherapy controls ought to be the equal.
+However, these effect sizes represent differences between the active intervention and the control condition for each modality.
+For these effect sizes to be comparable, placebo and psychotherapy controls ought to be equal in their effects.
 Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% - 60% and another arose from a difference of 40% - 0%.
-
-In this paper, we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent (mean age = 14.05, SE = 0.26) depression in the following ways.
-First, we compare key baseline characteristics of medication and psychotherapy trials, specifically the extent to which they are comparable in a) baseline severity of depression; b) percentage females vs males; c) mean age; and d) number of sites involved.
-Second, we determine the standardised mean differences of psychotherapy controls and medication controls using random effects metanalysis.
-Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and therefore, whether they represent fair pairings from which to draw valid efficacy inferences.
+two effect sizes of 40% would be considered equal, even if one arose from a difference of 100%-60% and another arose from a difference of 40%-0%.
+
+In this study we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+We hypothesise that there are substantial differences between these modalities, which we examine in the following ways.
+First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including a) baseline severity of depression; b) percentage females; and c) mean age.
+Second, we examine trial characteristics including the efficacy of the control arms, where we determine the standardised mean differences of psychotherapy controls and medication controls using random effects meta-regression, and the number of trial sites.
+Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
 
@@
 
-This study was registered on the Open Science Framework (OSF); the protocol can be found [here](https://osf.io/bfmc6).
-
-## Studies included
-
-We primarily drew upon RCTs included in two recent comprehensive meta-analyses with open data available for each medication and psychotherapy, and supplemented them with an updated systematic review, described below and in extensive detail in the supplement.
-Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021].
-Cuijpers et al.
-made available a full dataset of psychotherapy trials (via https://www.metapsy.org/), which we used for the current study.
-Whilst Cuijpers et al.
-(2023) excluded those studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s (2023) literature search.
-
-Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of a range of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
-A dataset was made available online though did not include means or standard deviations at baseline or post-test.
-We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
-We excluded three studies because they did not include a control arm.
-We were unable to locate and therefore complete extraction for two papers.
+The study protocol was registered on the Open Science Framework (OSF) and can be found [here](https://osf.io/bfmc6).
+
+A more detailed description of our methods, including the formalisms on which analyses are based, can be found in the Supplement.
+
+## Included studies
+
+We drew upon RCTs included in two recent comprehensive meta-analyses for each medication and psychotherapy with open data available, and supplemented them with an updated systematic review.
+Psychotherapy studies were drawn from a meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://www.metapsy.org/)).
+Medication studies were drawn from a NMA examining the efficacy of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
+We were unable to access the full dataset used in this NMA and hence completed extraction from the included studies ourselves.
+We excluded three studies because they had no control arm.
+We were unable to locate and complete extraction for one RCT (Almeida-Montes et al., 2005).
 Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
 
-We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review to ensure we analysed an equivalently up-to-date database of medication trials.
-Please see the Supplementary Materials for further details.
-Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
-Two study authors independently completed title and abstract screenings for 450 studies, and full text screening for 38 studies.
-7 studies met inclusion criteria and data extraction was completed for these papers.
+We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
+Please see the Supplement for further details.
+Seven studies met inclusion criteria and data extraction was completed for these papers.
 
@@
 
-Please refer to the Supplementary Materials for a detailed description of our analyses including the formalisms on which they are based.
-
-### Trial and sample characteristics
+### Sample characteristics
 
 We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including severity of depressive symptoms at baseline, sex and age.
-Meta-analyses were implemented using R's Meta package.
+Meta-analyses were implemented using R's meta package (version 7.0-0).
 
@@
 
-We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
-
-### Trial efficacy
+### Trial design
 
@@
 
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], as detailed in the Supplementary Materials.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023].
 
@@
 
-For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD.
+For the purposes of meta-analysis, it is necessary to estimate a standard error of the SMD.
 This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation we simulated n = 1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
+To ensure that our results are not biased by misestimation, we simulated n = 1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
 
@@
 <!-- for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
-We then used these simulated datasets in the subsequent metanalyses.
+We then used these simulated datasets in the subsequent meta-analyses.
 -->
@@
 
-We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
-
-<!-- The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+We estimated the pooled standardised mean difference for each arm by using a random effects meta-analysis implemented in R's metafor package (version 4.4-0).
+
+<!-- The main underlying assumption of random effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
 Therefore, we can estimate a two stage model with: -->
@@
 
-We present the SMDs of each level of the dummy variable of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
+We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
 The SMDs are the means across the 1000 simulated datasets.
+
+#### Number of sites
+
+We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
 
@@
 ```
-
-We then conducted a series of sensitivity analyses of our results.
-For each of the metanalyses we excluded 1) studies that used waitlist as their control condition and 2) studies which recruited participants with subclinical levels of depression.
-
-Next, we compared the control and active arms of studies where either the CDRS or the HAM-D where used as outcome instruments.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication vs psychotherapy control condition.
+We conducted a series of sensitivity analyses.
+For each of the meta-analyses we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
+Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
+
+Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
 To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
@@
 
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the nature and intensity of the interventions.
+We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions.
 We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
-Where a range was provided, the maximum was encoded (e.g.
-if a paper reported that an intervention involved 8-10 sessions lasting 50-60 minutes, we encoded the number and duration of sessions as 10 and 60, respectively).
-If sessions varied in frequency across an intervention, we calculated an average by dividing total number of sessions by length of intervention period.
-Similarly, if the length of sessions varied across the course of the intervention, we calculated a weighted average.
-Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
 
@@
 ###############6. Function for plotting the SMDs
-plot_means_function <- function(dataframe, subtitle) {
+plot_means_function <- function(dataframe) {
   dataframe$text_label <- 0
@@
     theme_minimal() +
-    labs(x = "TE-random", y = NULL, title = "Trial Efficacy by Treatment Arm",
-         subtitle = subtitle) +
     xlab("Standardized Mean Difference (SMD) with 95% CIs") +
@@
 
-### A few more tidying things from Argyris before doing metanalyses
+### A few more tidying things from Argyris before doing meta-analyses
 # Discovered some errors in the percentage women variable. Have gone back and checked. 
@@
                  baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall, no_sites) %>%
+                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
   rename(treatment = descr_active) %>% 
@@
                  baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall, no_sites) %>%
+                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
   rename(treatment = descr_control) %>% 
@@
 
-# I'm going to perform  the operations to calculate overall age and percent women here now. We just want this per study rather than per arm
-# as we are going to compare psy vs med (2 subgroups) rather than the 4 arms
+# I'm going to perform  the operations to calculate overall age and percent women here now.
+We just want this per study rather than per arm for the first set of meta-analyses as we are going to compare psy vs med (2 subgroups) rather than the 4 arms
 
@@
 
-The data for the studies included in this metanalysis are summarised in Supplementary Table 1 and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == FALSE,]$n` control arms of medication trials; and `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == FALSE,]$n` active arms and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == FALSE,]$n` control arms from psychotherapy RCTs.
+The data for the studies included in this meta-analysis are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+
+In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r sum(df_count_studies[df_count_studies$condition == "medication_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "medication_control", "n"])` control arms of medication trials; and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_control", "n"])` control arms from psychotherapy RCTs.
 Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-For the meta-regression examining trial efficacy, there were also missing data for `r df_count_studies[df_count_studies$condition == "medication_active"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "medication_control"& df_count_studies$is_missing == TRUE,]$n`, `r df_count_studies[df_count_studies$condition == "psychotherapy_active"& df_count_studies$is_missing == TRUE,]$n`, and `r df_count_studies[df_count_studies$condition == "psychotherapy_control"& df_count_studies$is_missing == TRUE,]$n` trial arms for medication active, medication control, psychotherapy active, and psychotherapy control conditions respectively, as the data needed to calculate the SMD were missing and could not be imputed by any of the methods outlined above.
-
-Placebo pill was the control condition for all medication trials.
-In psychotherapy trials, the control arm included 14 WL controls, 25 care as usual and several other conditions such as 4 attention control conditions.
-All included trials and the types of treatment controls can be found in Table X in the Supplementary Materials.
+
+Placebo pill was the control condition for all medication trials. In psychotherapy trials, the control arm included 14 WL, 25 TAU, and 19 other control conditions.
 
@@
   mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall))
+  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall)) %>%  # now also do this for untransformed variable
+  mutate(baseline_overall = sum(baseline_mean * baseline_n) / sum(baseline_n)) %>% 
+  mutate(pooled_sd_baseline = sqrt(sum((baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
+  mutate(se_baseline = pooled_sd_baseline / sqrt(n_overall))
 
@@
 #| label: tbl-baseline_results
-#| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies"
+#| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies: Results for overall sample and sensitivity analyses"
 #| tbl-cap-location: top
@@
   mutate(category = case_when(
-    row_number() %in% 1:9 ~ "Baseline Severity",
+    row_number() %in% 1:9 ~ "Baseline Severity of Depressive Symptoms*",
     row_number() %in% 10:18 ~ "Percent Female",
@@
   align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  # add_header_row(values = "Sample characteristics at baseline across medication and psychotherapy studies", colwidths = 8) %>% # This is a work around for the problems with rendering captions
-  # add_header_row(values = "Table 1", colwidths = 8) %>% 
   bold(part = "header") %>%   # Bold the relevant header rows
@@
   line_spacing(space = .7, part = "all") %>% 
+  add_footer_row(values = as_paragraph("*To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
+range of 96).
+Mean severity was 0.36 for psychotherapy studies and 0.42 for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS."), colwidths = 8) %>%
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
   autofit()
@@
 ```
-
 ### Baseline severity
 
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials when compared to psychotherapy trials.
-The statistics provided in @tbl-baseline_results are baseline depression scores transformed to reflect percentage of a scale range.
-To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
-range of 96).
-From @tbl-baseline_results, mean severity was `r round(results_met_sev$TE_random[results_met_sev$subgroup == 1][[2]], 2)` for psychotherapy studies and `r round(results_met_sev$TE_random[results_met_sev$subgroup == 0][[2]], 2)` for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS.
-
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials compared to psychotherapy trials.
+The statistics provided in @tbl-baseline_results are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).
 When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
@@
 
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# looking at CDRS studies only, this is with only 2 levels
+
+df_for_baseline_severity_cdrs <- df_for_baseline_severity %>%
+  filter(new_study_id %in% cdrs_study_ids)
+
+met_sev_cdrs <- metagen(TE = baseline_overall,
+                           seTE = se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_cdrs,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity cdrs",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev_cdrs <- extract_stats(met_sev_cdrs)
+
+# looking at HAMD studies only,
+
+df_for_baseline_severity_hamd <- df_for_baseline_severity %>%
+  filter(new_study_id %in% hamd_study_ids)
+
+met_sev_hamd <- metagen(TE = baseline_overall,
+                           seTE = se_baseline,
+                           studlab = new_study_id,
+                           data = df_for_baseline_severity_hamd,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "baseline severity cdrs",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+results_met_sev_hamd <- extract_stats(met_sev_hamd)
+
+# tabulate
+
+# For row names
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(results_met_sev_cdrs) <- new_column_names
+
+# Rounding
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+results_met_sev_cdrs %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+# now for the ham-d
+# For row names
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(results_met_sev_hamd) <- new_column_names
+
+# Rounding
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+results_met_sev_hamd %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+## this is for four levels
+### get CDRS studies
+cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
+
+#turn sds to sec
+cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
+                                                              #throughout
+
+results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,
+                                                         model_1, condition)
+
+results_cdrs_metareg_baseline[[2]] <- left_join(results_cdrs_metareg_baseline[[2]], study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>%
+                                        ungroup() %>%
+                                      select(condition, n),
+                                    by = "condition")
+
+### get HAM-D studies
+hamd_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
+
+list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
+                                                          %in% hamd_study_ids,]
+
+hamd_studies_for_baseline_metareg <- list_hamd_study #
+
+#turn sds to sec
+hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
+                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
+
+model_1 <- as.formula(~ four_level_var)
+condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
+                                                              #throughout
+results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg,
+                                                         model_1, condition)
+
+results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
+
+results_hamd_metareg_baseline[[2]] <- left_join(results_hamd_metareg_baseline[[2]], study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>%
+                                        ungroup() %>%
+                                      select(condition, n),
+                                    by = "condition")
+
+```
+
+To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
+As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher than psychotherapy studies for the CDRS and the HAM-D.
+The differences between medication control and psychotherapy control arms were significant at p\<0.05 for the CDRS and HAM-D.
+
+**still working on the 2 v 4 level analysis**
+
 ### Sex
 
-For this analysis, we excluded the two psychotherapy trials which included entirely female samples.
+For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016).
 As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
@@
 
-## Number of trial sites
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-### Number of sites
-# Write results, tabulate.
-
-## This data lives in this spreadsheet for psy trials, we need to merge it in
-
-df_no_sites <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
-
-df_no_sites <- df_no_sites %>% 
-  select(c(new_study_id, number_of_sites)) %>% 
-  filter(!is.na(number_of_sites)) %>% 
-  distinct(new_study_id, .keep_all = TRUE) %>% 
-  mutate(number_of_sites = as.numeric(number_of_sites))
-
-df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
-
-# we have different vectors for psy and med trials, lets coalesce
-
-df_baseline_demographics <- df_baseline_demographics %>%
-  mutate(no_sites = as.numeric(no_sites)) %>% 
-  mutate(sites = coalesce(no_sites, number_of_sites)) %>%
-  select(-no_sites, -number_of_sites)
-
-# we have a few rogue studies (Kitchen, McCarty and Wright). Kitchen was too recent (after 2021), McCarty and Wright are not in Cuijpers' master
-# dataset for some reason, though they are in the list of included studies in the table in his MA. For now I'm going to remove them because 
-# we don't have data for these trials.
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
-
-# Now create binary variable, single or multi site trial
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  mutate(site_binary = case_when(sites == 1 ~ "single", 
-                                 sites > 1 ~ "multi",
-                                 TRUE ~ NA_character_))
-
-# df_baseline_demographics %>%
-#   group_by(psy_or_med, site_binary) %>%
-#   summarize(num_trials = n())
-
-# Lets look at results
-
-# summary stats
-df_sites_summary_stats <- df_baseline_demographics %>%
-  group_by(psy_or_med) %>%
-  summarise(
-    n = n(),
-    mean_sites = mean(sites, na.rm = TRUE),
-    sd_sites = sd(sites, na.rm = TRUE),
-  )
-
-# Tabulate
-# Rounding
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-# Row names
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(psy_or_med = case_when(
-    psy_or_med == 0 ~ "Medication",
-    psy_or_med == 1 ~ "Psychotherapy",
-    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
-  ))
-
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  rename(
-    Modality = psy_or_med,
-    N = n,
-    Mean = mean_sites,
-    SD = sd_sites
-  )
-
-# t-test
-sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
-
-sites_t_test_stats <- data.frame(
-  statistic = sites_t_test$statistic,
-  df = sites_t_test$parameter,
-  p_value = sites_t_test$p.value,
-  ci_lower = sites_t_test$conf.int[1],
-  ci_upper = sites_t_test$conf.int[2]
-)
-
-sites_t_test_stats <- sites_t_test_stats %>%
-  mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2))) %>% 
-  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-sites-summary
-#| tbl-cap: "Number of sites across medication and psychotherapy studies"
-#| tbl-cap-location: top
-
-flextable(df_sites_summary_stats) %>%
-  set_table_properties(width = 1, layout = "fixed") %>%
-  add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
-                      "; ", as_i("p "), sites_t_test_stats$p_value, 
-                      "; 95% CI: ", sites_t_test_stats$ci_lower,
-                      "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
-  # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
-  # add_header_row(values = "Table 2", colwidths = 4) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
-  align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>% 
-  autofit() %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
-There was a significant difference between the number of sites in medication and psychotherapy trials, as can be seen in @tbl-sites-summary.
-Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
-
-## Standardised mean differences of control conditions in psychotherapy and medication studies
+## Trial design
+
+### Standardised mean differences of control conditions in psychotherapy and medication studies
 
 We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-
-As can be seen in @fig-plot-means-all there were substantial differences between the four arms of the metanalysis with striking differences between the medication and the psychotherapy control arms.
-In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ) (see @tbl-coefs-overall).
+As can be seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and the psychotherapy control arms.
+In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
 
@@
 
-subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
-plot_means_all <- plot_means_function(df_mean_coefs_from_sim, subtitle_text_all)
+# subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
+plot_means_all <- plot_means_function(df_mean_coefs_from_sim)
 print(plot_means_all)
 
-# png("plot_means_all.png")
-# plot_means_all
-# dev.off()
-
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-coefs-overall
-#| tbl-cap: "Summary statistics of the estimated SMDs"
+# #| label: tbl-coefs-overall
+# #| tbl-cap: "Summary statistics of the estimated SMDs"
+# #| tbl-cap-location: top
+# 
+# # Prepare to tabulate
+# 
+# table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   relocate("n", .after = "condition") 
+# 
+# new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
+# 
+# # Assign new column names to the data frame
+# colnames(table_mean_coefs_from_sim) <- new_column_names
+# 
+# flextable(table_mean_coefs_from_sim) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>% 
+#   # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
+#   # add_header_row(values = "Table 3", colwidths = 6) %>% 
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+#   # italic(i = 2, italic = TRUE, part = "header") %>% 
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>% 
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>% 
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+#   align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
+#   align(j = 1, align = "left", part = "all") %>% 
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+#   line_spacing(space = .7, part = "all")
+
+```
+
+In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+Here, medication control is the reference category (termed intercept) to which all other categories are compared.
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value (<0.0001).
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
+#| label: tbl-results-overall
+#| tbl-cap: "Results from metaregression with overall sample"
 #| tbl-cap-location: top
-
-# Prepare to tabulate
-
-table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  relocate("n", .after = "condition")
-
-new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(table_mean_coefs_from_sim) <- new_column_names
 
@@
 
-flextable(table_mean_coefs_from_sim) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>% 
-  # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
-  # add_header_row(values = "Table 3", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
-In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-In particular, in this metaregression model, medication control is the reference category (termed intercept) to which all other categories of the dummy variable are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value ( `r sprintf("%.3e",(1-(pnorm(8.949921))))` ).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
-#| label: tbl-results-overall
-#| tbl-cap: "Results from metaregression with overall sample"
-#| tbl-cap-location: top
-
 table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
+table_aggregate_results_overall[1, 4] <- NA
 
@@
 
-#### Sensitivity analyses
-
-We then conducted a series of sensitivity analyses of our results.
-First, we analysed the data after excluding waitlist control studies.
-As can be seen in @fig-plot-means-no-wl (see Supplementary Materials), the pattern of results is very similar to that of the overall analyses.
-
-We next analysed the data after excluding sub-clinical studies. Again, the pattern of results was very similar to that of the overall analyses (see @fig-plot-means-clin in Supplementary Materials).
-
-Next, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs in Supplementary Materials).
-Medication control and psychotherapy control conditions remained significantly different, however the small number of psychotherapy studies using the CDRS resulted in less precise metanalytic estimates of within-group changes.
-
-Similarly, when we examined the data including only those studies that used the HAM-D (see @fig-plot-means-hamd in Supplementary Materials), medication control and psychotherapy control conditions remained significantly different though the small number of medication studies using the HAM-D resulted in less precise metanalytic estimates.
-
-Further, we showed with our simulations that the effects of different values for the pre-post measures had minimal effect on the estimated outcomes; please refer to @fig-stab-sims in the Supplement.
+##### Sensitivity analyses
+
+We then conducted a series of sensitivity analyses of our results (all figures can be found in the Supplementary Materials).
+First, we analysed the data after excluding WL control studies, which yielded a pattern of results is very similar to that of the overall analyses (see @fig-plot-means-no-wl).
+Secondly, we analysed the data after excluding sub-clinical studies, which again yielded a similar pattern of results (see @fig-plot-means-clin).
+Thirdly, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAM-D (see @fig-plot-means-hamd).
+Medication control and psychotherapy control conditions remained significantly different, however the small number of studies using each of these instruments resulted in less precise meta-analytic estimates of the SMDs.
+Finally, we showed different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
 
 ##### Addressing Regression to the Mean
-
-We first conducted a meta-analysis to test for differences in means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-### get CDRS studies
-cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-
-#turn sds to sec
-cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-
-results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,  
-                                                         model_1, condition)
-
-results_cdrs_metareg_baseline[[2]] <- left_join(results_cdrs_metareg_baseline[[2]], study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-
-### get HAM-D studies
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-                                                          %in% hamd_study_ids,]
-
-hamd_studies_for_baseline_metareg <- list_hamd_study #
-
-#turn sds to sec
-hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var 
-                                                              #throughout
-results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg, 
-                                                         model_1, condition)
-
-results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-results_hamd_metareg_baseline[[2]] <- left_join(results_hamd_metareg_baseline[[2]], study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher than psychotherapy studies for the CDRS and the HAM-D.
-The differences between medication control and psychotherapy control arms were significant at p\<0.05 for the CDRS, though they did not reach statistical significance for the HAM-D (p = `r round(results_hamd_metareg_baseline[[1]][results_hamd_metareg_baseline[[1]]$condition == "psychotherapy_control", "p.value"], 3)`).
 
@@
 ```
-
-We next addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplementary Materials for the adjusted SMDs with their confidence intervals).
-As can be inferred from the non-overlapping confidence intervals, there were significant differences between the medication control and psychotherapy control arms.
+We addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplementary Materials for the adjusted SMDs with their confidence intervals).
+The difference between the medication control and psychotherapy control arms remained similar to the overall analyses.
+
+### Number of trial sites
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+### Number of sites
+# Write results, tabulate.
+
+## This data lives in this spreadsheet for psy trials, we need to merge it in
+
+df_no_sites <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
+
+df_no_sites <- df_no_sites %>% 
+  select(c(new_study_id, number_of_sites)) %>% 
+  filter(!is.na(number_of_sites)) %>% 
+  distinct(new_study_id, .keep_all = TRUE) %>% 
+  mutate(number_of_sites = as.numeric(number_of_sites))
+
+df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
+
+# we have different vectors for psy and med trials, lets coalesce
+
+df_baseline_demographics <- df_baseline_demographics %>%
+  mutate(no_sites = as.numeric(no_sites)) %>% 
+  mutate(sites = coalesce(no_sites, number_of_sites)) %>%
+  select(-no_sites, -number_of_sites)
+
+# we have a few rogue studies (Kitchen, McCarty and Wright). Kitchen was too recent (after 2021), McCarty and Wright are not in Cuijpers' master
+# dataset for some reason, though they are in the list of included studies in the table in his MA. For now I'm going to remove them because 
+# we don't have data for these trials.
+
+df_baseline_demographics <- df_baseline_demographics %>% 
+  filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
+
+# Now create binary variable, single or multi site trial
+
+df_baseline_demographics <- df_baseline_demographics %>% 
+  mutate(site_binary = case_when(sites == 1 ~ "single", 
+                                 sites > 1 ~ "multi",
+                                 TRUE ~ NA_character_))
+
+# df_baseline_demographics %>%
+#   group_by(psy_or_med, site_binary) %>%
+#   summarize(num_trials = n())
+
+# Lets look at results
+
+# summary stats
+df_sites_summary_stats <- df_baseline_demographics %>%
+  group_by(psy_or_med) %>%
+  summarise(
+    n = n(),
+    mean_sites = mean(sites, na.rm = TRUE),
+    sd_sites = sd(sites, na.rm = TRUE),
+  )
+
+# Tabulate
+# Rounding
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  mutate(across(where(is.numeric), ~round(., 2)))
+
+# Row names
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  mutate(psy_or_med = case_when(
+    psy_or_med == 0 ~ "Medication",
+    psy_or_med == 1 ~ "Psychotherapy",
+    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
+  ))
+
+df_sites_summary_stats <- df_sites_summary_stats %>%
+  rename(
+    Modality = psy_or_med,
+    N = n,
+    Mean = mean_sites,
+    SD = sd_sites
+  )
+
+# t-test
+sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
+
+sites_t_test_stats <- data.frame(
+  statistic = sites_t_test$statistic,
+  df = sites_t_test$parameter,
+  p_value = sites_t_test$p.value,
+  ci_lower = sites_t_test$conf.int[1],
+  ci_upper = sites_t_test$conf.int[2]
+)
+
+sites_t_test_stats <- sites_t_test_stats %>%
+  mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2))) %>% 
+  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+## | label: tbl-sites-summary
+## | tbl-cap: "Number of sites across medication and psychotherapy studies"
+## | tbl-cap-location: top
+#
+# flextable(df_sites_summary_stats) %>%
+#   set_table_properties(width = 1, layout = "fixed") %>%
+#   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
+#                       "; ", as_i("p "), sites_t_test_stats$p_value, 
+#                       "; 95% CI: ", sites_t_test_stats$ci_lower,
+#                       "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
+#   # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
+#   # add_header_row(values = "Table 2", colwidths = 4) %>% 
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+#   # italic(i = 2, italic = TRUE, part = "header") %>% 
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>% 
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>% 
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
+#   align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
+#   align(j = 1, align = "left", part = "all") %>% 
+#   font(fontname = "Calibri", part = "all") %>% 
+#   autofit() %>% 
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+#   line_spacing(space = .7, part = "all")
+
+```
+
+Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
+Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 
@@
 # Filter out wl conditions
-df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  filter(new_study_id %in% no_wl_ids)
+# df_descr_psy_conditions <- df_descr_psy_conditions %>% 
+  # filter(new_study_id %in% no_wl_ids)
 
@@
 This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression.
-In order to address this question, we asked whether the two treatment modalities --- medication and psychotherapy --- are comparable on the basis of the existing evidence.
-Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two treatment modalities.
-
+In order to address this question, we asked whether psychotherapy and medication are comparable on the basis of the existing evidence.
+Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two modalities.
 First, whether the participants of trials in one modality are comparable to those in another modality.
-Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved in a trial, are comparable.
+Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
 
@@
 Similarly, we found that on average there were about 7% more females in psychotherapy trials.
-Whilst there is little evidence that sex or sex moderate treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
+Whilst there is little evidence that sex moderates treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
 
@@
 
-First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in NIH-funded (i.e.
-non industry) trials which are also more likely to show higher pill placebo efficacy.
+First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
+Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in non-industry trials which are also more likely to show lower pill placebo efficacy.
 Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where primacy is given to the number of recruited participants which is the primary unit of reimbursement.
@@
 This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical.
-However, we note that, our findings are largely in keeping with those of the network metanalysis, which is designed to preserve the randomization structure.
+However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomization structure.
 More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because of the fact that the people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison between the two modalities.
-This is all the more so as clinicians as well as policy makers often resort to effect sizes to summarise findings, with SMD being the one used as per standard.
-Our findings make obvious that comparing treatment modalities based on the effect size of each modality is misleading.
-
-Moving beyond the comparison of the controls between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment.
-An optimal control condition is one where the treatment differs (e.g.
-treatment vs no treatment), but everything else is equal (in technical terms, the ceteris paribus assumption).
+In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison of the two modalities.
+This is all the more so as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings.
+Our results make obvious that comparing treatments based on the effect sizes of each modality (relative to their respective control arms) is misleading.
+
+Moving beyond comparison between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment.
+An optimal control condition is one where the treatment differs but everything else is equal.
 An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind).
 Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption.
-Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either waitlist control or treatment as usual, both of which are very likely to create negative expectations for participants not randomized to treatment; thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
+Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either WL or TAU, both of which are very likely to create negative expectations for participants not randomized to treatment.
+Thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
 But we also find that even psychological controls were unreasonable counterfactuals.
@@
 
-Given all of the above, the certainty with which guidelines, including UK's NICE recommend psychotherapy over medication for adolescent depression is surprising.
+Given all of the above, the certainty with which guidelines recommend psychotherapy over medication for adolescent depression is surprising.
 Indeed, we believe that our findings have a number of profound implications for patients, their families, clinicians and policy makers and we list these below.
@@
 
-Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of how these studies are appraised and what needs to be done to create fair and realistic comparators.
-Indeed, investment of effort and funds should be directed into providing rigorous evidence that established depression psychotherapies are more efficacious than fair controls.
-There are examples of such psychotherapy RCTs, such as @youngRandomizedDepressionPrevention2016 in the current study, where such rigor has been applied.
+Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of what needs to be done to create fair comparators.
+Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
+There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, as well as human contact with both therapists and group-members.
 
@@
 The first obstacle is the comparability of the populations taking part.
-Even if a trial were designed to conduct a head-to-head comparison of psychotherapy with medication (as has been done in [@FluoxetineCognitiveBehavioralTherapy2004]), it might sample the population of those who are indifferent to which one they would receive.
+Head-to-head comparisons of psychotherapy with medication (as has been done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they would receive.
 And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
 
-In summary, our data give cause for consternation about the state of the evidence of youth depression, one of the most common and debilitating disorders in young people.
-Our data question the state of knowledge about the efficacy of youth psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choice than currently exists.
+In summary, our data give cause for consternation about the state of the evidence for treatments of youth depression, one of the most common and debilitating disorders in young people.
+Our data question the state of knowledge about the efficacy of psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
+Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices than what currently exists.
 
@@
 We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
-after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2023) review).
+after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review).
 We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
@@
 Please see @fig-prisma for the PRISMA flow diagram.
+
 We used Covidence, an online software tool, to manage our systematic review.
+Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
+Two authors screened 450 titles and abstracts, and 38 full text records.
+Seven studies met inclusion criteria and data extraction was completed for these papers.
 
@@
 
-## Full description of statistical analysis (including formalisms)
-
-### Trial and sample characteristics
+## Full description of methods (including formalisms)
+
+## Included studies
+
+We drew upon RCTs included in two recent comprehensive meta-analyses with open data available for each medication and psychotherapy, and supplemented them with an updated systematic review.
+Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
+Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://www.metapsy.org/)).
+Whilst Cuijpers et al.
+(2021) excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
+We also included studies which had data available for other variables in interest, including number of sites or baseline demographics; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s (2021) literature search.
+
+Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
+A dataset was made available online though did not include means or standard deviations at baseline or post-test.
+We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
+We excluded three studies because they had no control arm.
+We were unable to locate and therefore complete extraction for one RCT (Almeida-Montes et al., 2005).
+Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
+
+We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
+Please see the Supplementary Materials for further details.
+Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
+Two authors screened 450 titles and abstracts, and 38 full text records.
+Seven studies met inclusion criteria and data extraction was completed for these papers.
+
+## Statistical Analysis
+
+### Sample characteristics
 
@@
 If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis.
-
-For the purposes of metanalysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis (for medication studies only).
+
+For the purposes of meta-analysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
 
@@
 for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
-We then used these simulated datasets in the subsequent metanalyses.
+We then used these simulated datasets in the subsequent meta-analyses.
 
@@
 
-We estimated the pooled standardised mean difference for each arm by using a random effects metanalysis implemented in R's metafor package.
-The main underlying assumption of random effects metanalysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+We estimated the pooled standardised mean difference for each arm by using a random effects meta-analysis implemented in R's metafor package.
+The main underlying assumption of random effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
 Therefore, we can estimate a two stage model with:
@@
 
-We present the SMDs of each level of the dummy variable of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
+We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
 The SMDs are the means across the 1000 simulated datasets.
+
+#### Number of sites
+
+We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
+
+### Sensitivity Analyses
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
+# my alpha for the z 
+target_probability <- 1 - 0.05
+
+#start here 
+x <- 1
+
+# two decimals should be fine
+tolerance <- 1e-3
+
+#find the z value using the pnorm function
+while (abs(pnorm(x)) < target_probability ) {
+  x <- x + tolerance  
+}
+
+# Adjust the step size based on your problem  
+cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
+
+x
+
+```
+
+We conducted a series of sensitivity analyses.
+For each of the meta-analyses we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
+Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
+
+Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
+To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
+We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
+
+Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
+
+### Comparing the control and active arms of psychotherapy trials
+
+We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions.
+We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
+Where a range was provided, the maximum was encoded (e.g.
+if a paper reported that an intervention involved 8-10 sessions lasting 50-60 minutes, we encoded the number and duration of sessions as 10 and 60, respectively).
+If sessions varied in frequency across an intervention, we calculated an average by dividing total number of sessions by length of intervention period.
+Similarly, if the length of sessions varied across the course of the intervention, we calculated a weighted average.
+Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
+
+## Summary of all included trials
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: tbl-all-trials
+#| tbl-cap: "Summary of included RCTs"
+#| tbl-cap-location: top
+
+table_all_trials <- df_long_for_metan %>% 
+  select(psy_or_med, new_study_id, arm_effect_size, type, baseline_n, instrument_name, baseline_mean, baseline_sd, post_mean, post_sd, cohens_d)
+
+table_all_trials <- table_all_trials %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(psy_or_med = ifelse(psy_or_med == 0, "Medication", "Psychotherapy")) %>% 
+  mutate(arm_effect_size = ifelse(arm_effect_size == "cohens_d_active", "Active", "Control"))
+
+new_column_names <- c("psy_or_med", "Study", "Arm", "Description", "N", "Instrument", "Baseline M", "Baseline SD", "Post M", "Post SD", "Cohen's d")
+
+# Assign new column names to the data frame
+colnames(table_all_trials) <- new_column_names
+
+table_all_trials %>% 
+  arrange(psy_or_med, Study) %>% 
+  group_by(psy_or_med) %>%
+  as_flextable(hide_grouplabel = TRUE) %>% 
+  merge_v(j = ~Study) %>% 
+  align(j = 4:10, align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  bg(i = c(1, 86), bg = "#F2F2F2", part = "body") %>% 
+  bold(i = c(1, 86), bold = TRUE, part = "body") %>% 
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  set_table_properties(width = 1, layout = "autofit")
+
+```
 
@@
 #| label: fig-plot-means-no-wl
-#| fig-cap: "Metanalytic estimates of within-group changes: wl excluded"
+#| fig-cap: "Metanalytic estimates of within-group changes: waitlist studies excluded"
 #| fig-cap-location: top
@@
 
-subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl, subtitle_text_no_wl)
+# subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl)
 print(plot_means_no_wl)
@@
 
-subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
-plot_means_clin <- plot_means_function(coef_and_se_means_clin_study, subtitle_text_clin)
+# subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
+plot_means_clin <- plot_means_function(coef_and_se_means_clin_study)
 print(plot_means_clin)
@@
 
-subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
-plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study, subtitle_text_cdrs)
+# subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
+plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study)
 print(plot_means_cdrs)
@@
 
-subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study, subtitle_text_hamd)
+# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study)
 print(plot_means_hamd)
@@
 
+aggregate_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "coefficients")
+
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
+
+# Assign new column names to the data frame
+colnames(aggregate_results_overall_adjusted_cohens_d) <- new_column_names
+
+table_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d[, 1:6]
+
+flextable(table_results_overall_adjusted_cohens_d) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "T2"],
+                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "I2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "k"],
+                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "R2"], "."), colwidths = 6) %>%
+  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
+  # add_header_row(values = "Table 4", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+
+# We want to compare active v control arms when we filter out wl conditions
+
+df_descr_psy_conditions_no_wl <- df_descr_psy_conditions %>% 
+  filter(new_study_id %in% no_wl_ids)
+
+df_descr_psy_conditions_no_wl <- df_descr_psy_conditions_no_wl %>% 
+    filter(!(treatment == "wlc"))
+
+sessions <- group_function(df_descr_psy_conditions_no_wl,"levels_var","no_sessions")
+frequency <- group_function(df_descr_psy_conditions_no_wl,"levels_var","freq_weeks")
+length_sessions_mins <- group_function(df_descr_psy_conditions_no_wl,"levels_var","length_sessions_mins")
+total_hours <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_hours")
+total_period_weeks <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_period_weeks")
+
+control_summary_no_wl <- rbind(sessions, frequency, length_sessions_mins, total_hours, total_period_weeks)
+
+control_summary_no_wl <- control_summary_no_wl %>% 
+  select(-c(Median, IQR))
+
+control_summary_no_wl <- control_summary_no_wl %>%
+  mutate(Group = case_when(
+    Group == "psychotherapy_active" ~ "Active",
+    Group == "psychotherapy_control" ~ "Control",
+    TRUE ~ as.character(Group)  # Keep other values unchanged
+  ))
+
+control_summary_no_wl <- control_summary_no_wl %>%
+  mutate(Column = case_when(
+    Column == "no_sessions" ~ "Number of sessions",
+    Column == "freq_weeks" ~ "Intensity (sessions per week)",
+    Column == "length_sessions_mins" ~ "Session length (mins)",
+    Column == "total_hours" ~ "Total intervention hours",
+    Column == "total_period_weeks" ~ "Intervention duration (weeks)",
+    TRUE ~ as.character(Column)  # Keep original value if no match
+  ))
+
+control_summary_no_wl <- control_summary_no_wl %>% 
+  mutate(across(where(is.numeric), ~round(., 2)))
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-intensity-of-int-no-wl
+#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
+#| tbl-cap-location: top
+
+as_grouped_data(control_summary_no_wl, groups = "Column") %>% 
+  as_flextable(hide_grouplabel = TRUE ) %>% 
+  bold(i = c(1, 4, 7, 10, 13), bold = TRUE, part = "body") %>%  
+  set_table_properties(width = 1) %>%  # Set table width 
+  autofit() %>%  # Autofit column widths 
+  align(j = 2:4, align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
+  # add_header_row(values = "Table 5", colwidths = 4) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  #italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  paginate(init = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+# t tests
+
+session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions_no_wl)
+freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
+session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions_no_wl)
+total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions_no_wl)
+total_period_t_test <- t.test(total_period_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
+
+extract_t_test_stats <- function(df) {
+
+  t_test_stats <- data.frame(
+  outcome = df$data.name,
+  statistic = df$statistic,
+  df = df$parameter,
+  p_value = df$p.value,
+  ci_lower = df$conf.int[1],
+  ci_upper = df$conf.int[2])
+
+  return(t_test_stats)
+
+}
+
+results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
+results_freq_t_test <- extract_t_test_stats(freq_t_test)
+results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
+results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
+results_total_period_t_test <- extract_t_test_stats(total_period_t_test)
+
+control_summary_t_tests_no_wl <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test, results_total_period_t_test)
+
+# For row names
+control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
+  mutate(outcome = case_when(
+    row_number() == 1 ~ "Number of sessions",
+    row_number() == 2 ~ "Intensity (sessions per week)",
+    row_number() == 3 ~ "Session length (mins)",
+    row_number() == 4 ~ "Total intervention hours",
+    row_number() == 5 ~ "Intervention duration (weeks)"
+  ))
+
+# Define new column names
+new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(control_summary_t_tests_no_wl) <- new_column_names
+
+#Rounding
+control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
+  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
+  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-t-tests-intensity-no-wl
+#| tbl-cap: "Results for t-tests comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
+#| tbl-cap-location: top
+
+flextable(control_summary_t_tests_no_wl) %>%
+  set_table_properties(width = 1) %>%  # Set table width %>% 
+  autofit() %>%  # Autofit column widths 
+  align(j = 2:ncol(control_summary_t_tests_no_wl), align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
+  #add_header_row(values = "Table 6", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  #italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  paginate(init = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+
 ```

### 2024-05-09 Manuscript_for_rendering_in_word.qmd
Implementing some changes from georgina's comments

@@
 ---
-title: "Fundamental Problems with Child and Adolescent Depression Treatments"
-subtitle: "A Quantitative Reappraisal of the Evidence Base"
+title: "Revisiting Child and Adolescent Depression Treatments"
+subtitle: "A Quantitative Critique of the Evidence Base"
 author:
@@
 
-Should a child or an adolescent receive psychotherapy or medication for their depression, and what information should patients, carers and clinicians use to decide?
-
-This question is particularly difficult to answer as there are limited data from head-to-head trials of medication and psychotherapy for adolescent depression, and hence recommendations must be derived from indirect comparisons of treatment efficacy.
-The internationally influential UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication for most presentations of depression [@niceDepressionChildrenYoung2023].
-This conclusion is in keeping with two sources of evidence: meta-analyses of medication trials that cast doubt on the efficacy of most antidepressants, with the exception of fluoxetine, for child and adolescent depression [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy trials that conclude psychotherapy to be efficacious for child and adolescent depression [@cuijpersEffectsPsychologicalTreatments2021].
-However, such conclusions seem at odds with those of a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
-treatment A with treatment C, via studies that directly compare A with B and B with C) evidence.
-Indeed, this NMA concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
+Should a child or an adolescent receive psychotherapy or medication for their depression, and what information should be used to guide decision-making?
+
+For adolescent depression, there are limited data from head-to-head trials of medication and psychotherapy, and hence recommendations must be derived from indirect comparisons of treatment efficacy.
+The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2023].
+This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
+However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
+treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
 pill placebo) or psychotherapy controls.
+The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
 Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
 
-In this paper, we examine whether the existing evidence base for adolescent depression treatment can offer valid answers to this question.
-We provide a conceptual framework for answering such questions and test a series of hypotheses using data from existing trials.
-Two points are crucial to indirect comparisons of treatment modalities with each other.
+In this paper, we examine whether the existing evidence for adolescent depression treatment can offer valid answers to this question.
+We provide a conceptual framework and test a series of hypotheses using data from existing trials.
+Two points are crucial to indirect comparisons of treatment modalities.
 First, whether the participants of trials in one modality are comparable to those in another modality.
@@
 
-Starting with the first point, to compare between different trials one must assume that these trials sample from the same population.
-If they do not, then the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
-We provide a more formal account of this in the Supplement.
+Starting with the first point, comparison between different trials assumes that they sample from the same population.
+If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
+the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable (see Supplement for further details).
 
@@
 
-This assumption that medication and psychotherapy trials sample from the same population may be hard to meet.
-Clinical experience and empirical evidence indicate that patients and parents often have preferences between psychotherapy and medication [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
-Moreover, these treatment preferences correlate with clinically-relevant characteristics of the participants, including severity and sex.
-Some of these characteristics, particularly baseline severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
+The assumption that medication and psychotherapy trials sample from the same population may not be valid as patients and parents often have treatment preferences [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
+Moreover, treatment preferences correlate with clinically-relevant characteristics of the participants, including severity and sex.
+Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
 
@@
 Most obviously, participants in psychotherapy trials are unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022].
-This creates differential expectations between medication and psychotherapy trials.
-Importantly, pill-placebo has been developed as the standard medication control in order to match as closely as possible the intervention condition, so as to minimise differences in expectancy between conditions.
-By contrast, psychotherapy control arms vary across waitlist controls (WL), treatment as usual (TAU), and active controls.
-Differences in expectation may favour the psychotherapy active condition and disadvantage the psychotherapy control (thus potentially magnifying the difference between them).
-This is because of what has been aptly described as "disappointment bias" [@reltonEthicsTrialsCohorts2017], where participants in the active condition are content for receiving the "cutting edge treatment" whilst those in the control are dissatisfied for having missed out on "proper treatment".
-Expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011].
-If expectancy effects are different for psychotherapy controls and pill placebo, comparisons between them, including in NMA, become questionable.
+This creates differential expectations which may favour the psychotherapy active condition and disadvantage the psychotherapy control; participants in the active condition are content to be receiving the “cutting edge” treatment whilst those in the control are dissatisfied for having missed out (i.e.
+“disappointment bias” [@reltonEthicsTrialsCohorts2017].
+By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022], suggesting that expectancy effects are well-matched across conditions.
+Since expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011], if expectancy differs between medication and psychotherapy trials, comparisons between them, including in NMA, become questionable.
 
 Another difference in design is the number of trial sites.
-Previous research has shown that in medication trials the number of sites is positively related to the magnitude of the placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
-This phenomenon may be due to lower quality of assessments in trials with more sites, with higher rates of classification errors, entailing higher rates of spontaneous remission or regression to the mean.
-It is therefore important to examine whether this basic trial design feature differs between medication and psychotherapy trials.
-
-An inter-related issue concerns the nature of control interventions being used.
-Control conditions in trials are meant to generate counterfactual conditions [@guoChapterCounterfactualFramework2014] to the intervention: what would have been the outcome in an individual had they not received the intervention, with all else being equal.
-A pill placebo condition, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
-The question is whether psychotherapy trials make a similar effort: are for example the number of hours of contact with a human comparable between active and control arms in psychotherapy trials?
-
-Understanding the nature of controls for each treatment modality is important for a similar reason.
+Previous research has shown that the number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
+This phenomenon may be due to lower quality of assessments in trials with more sites, with higher rates of classification errors, entailing higher rates of apparent spontaneous remission or regression to the mean.
+
+An inter-related issue concerns the effect of control conditions.
 Often, in the public domain, psychotherapy and medication are compared to each other on the basis of their respective effect sizes.
@@
 
-In this study we examine randomised controlled trials (RCTs) of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-We hypothesise that there are substantial differences between these modalities, which we examine in the following ways.
-First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including a) baseline severity of depression; b) percentage females; and c) mean age.
-Second, we examine trial characteristics including the efficacy of the control arms, where we determine the standardised mean differences of psychotherapy controls and medication controls using random effects meta-regression, and the number of trial sites.
+Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention [@guoChapterCounterfactualFramework2014]: what would have been the outcome had an individual not received the intervention, with all else being equal.
+A pill placebo condition, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
+In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g.
+with respect to number of hours of therapist contact).
+
+In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+We hypothesise that there are substantial methodological differences between psychotherapy and medication RCTs, making comparisons problematic, and we examine this in the following ways.
+First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline severity of depression; b) percentage females; and c) mean age.
+Second, we examine trial characteristics including the efficacy of the control arms, using random effects meta-regression, and the number of trial sites.
 Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
@@
 
-We drew upon RCTs included in two recent comprehensive meta-analyses for each medication and psychotherapy with open data available, and supplemented them with an updated systematic review.
-Psychotherapy studies were drawn from a meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://www.metapsy.org/)).
-Medication studies were drawn from a NMA examining the efficacy of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
-We were unable to access the full dataset used in this NMA and hence completed extraction from the included studies ourselves.
+We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
+For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://www.metapsy.org/)).
+For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
 We excluded three studies because they had no control arm.
@@
 
-We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
-Please see the Supplement for further details.
-Seven studies met inclusion criteria and data extraction was completed for these papers.
+For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
+Two authors screened 450 titles and abstracts, and 38 full text records.
+Seven studies met inclusion criteria and one author completed data extraction for these papers.
+See @fig-prisma in the Supplement for PRISMA diagram.
 
@@
 
-We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including severity of depressive symptoms at baseline, sex and age.
+We conducted a series of random effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms at baseline, sex and age.
 Meta-analyses were implemented using R's meta package (version 7.0-0).
@@
 
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions.
-We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
+We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions: the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
 
@@
 
-Placebo pill was the control condition for all medication trials. In psychotherapy trials, the control arm included 14 WL, 25 TAU, and 19 other control conditions.
+Placebo pill was the control condition for all medication trials.
+In psychotherapy trials, the control arm included 14 waitlist, 25 treatment-as-usual (TAU), and 19 other control conditions (e.g.
+relaxation training, attention control, counselling).
 
@@
   line_spacing(space = .7, part = "all") %>% 
-  add_footer_row(values = as_paragraph("*To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
+  add_footer_row(values = as_paragraph("*These are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
 range of 96).
@@
 
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials compared to psychotherapy trials.
-The statistics provided in @tbl-baseline_results are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).
+On average, severity of depressive symptoms at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline_results).
 When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
@@
 results_met_sev_hamd <- extract_stats(met_sev_hamd)
-
-# tabulate
-
-# For row names
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_cdrs) <- new_column_names
-
-# Rounding
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-results_met_sev_cdrs %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# now for the ham-d
-# For row names
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_hamd) <- new_column_names
-
-# Rounding
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-results_met_sev_hamd %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
 ```
@@
 To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
-As can be seen in @tbl-cdrs-baseline and @tbl-hamd-baseline (see Supplementary Materials), the baseline scores in medication studies were on average substantially higher than psychotherapy studies for the CDRS and the HAM-D.
-The differences between medication control and psychotherapy control arms were significant at p\<0.05 for the CDRS and HAM-D.
-
-**still working on the 2 v 4 level analysis**
+As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplementary Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
 
@@
 In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-Here, medication control is the reference category (termed intercept) to which all other categories are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value` , which yields a very low p-value (<0.0001).
+Here, medication control is the reference category to which all others are compared.
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p<0.0001).
 
@@
 
-We then conducted a series of sensitivity analyses of our results (all figures can be found in the Supplementary Materials).
-First, we analysed the data after excluding WL control studies, which yielded a pattern of results is very similar to that of the overall analyses (see @fig-plot-means-no-wl).
-Secondly, we analysed the data after excluding sub-clinical studies, which again yielded a similar pattern of results (see @fig-plot-means-clin).
-Thirdly, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAM-D (see @fig-plot-means-hamd).
+We  conducted a series of sensitivity analyses (all figures can be found in the Supplementary Materials).
+First, we analysed the data after excluding waitlist control studies, which yielded a pattern of results is very similar to that of the overall analyses (see @fig-plot-means-no-wl).
+Second, we analysed the data after excluding sub-clinical studies, which again yielded a similar pattern of results (see @fig-plot-means-clin).
+Third, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAM-D (see @fig-plot-means-hamd).
 Medication control and psychotherapy control conditions remained significantly different, however the small number of studies using each of these instruments resulted in less precise meta-analytic estimates of the SMDs.
@@
 
-Average number of trial sites was significantly higher across medication studies (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
+Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
 Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
@@
 Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption.
-Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either WL or TAU, both of which are very likely to create negative expectations for participants not randomized to treatment.
+Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either waitlist or TAU, both of which are very likely to create negative expectations for participants not randomized to treatment.
 Thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-cdrs-baseline
-#| tbl-cap: "CDRS Baseline Scores"
+#| label: tbl-hamd-baseline
+#| tbl-cap: "HAM-D Baseline Scores across Psychotherapy and Medication RCTs"
 #| tbl-cap-location: top
 
-# Prepare to tabulate
-
-table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>%
-  relocate("condition", .before = "baseline_smds") %>%
-  relocate("n", .before = "baseline_smds") %>%
-  relocate("lower_cis_smds", .before = "upper_cis_smds")
-
-new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+# now for the ham-d
+# For row names
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
 
 # Assign new column names to the data frame
-colnames(table_2_cdrs_metareg_baseline) <- new_column_names
-
-flextable(table_2_cdrs_metareg_baseline) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
+colnames(results_met_sev_hamd) <- new_column_names
+
+# Rounding
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+results_met_sev_hamd %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
   bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
   vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
   hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-
-# Regression results
-
-table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>%
-  relocate("condition", .before = "term") %>%
-  select(-c("term", "type"))
-
-new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+# # All of the below is for the HAMD baseline meta-analysis when we have 4 levels
+# # Prepare to tabulate
+# 
+# table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "baseline_smds") %>%
+#   relocate("n", .before = "baseline_smds") %>%
+#   relocate("lower_cis_smds", .before = "upper_cis_smds")
+# 
+# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+# 
+# # Assign new column names to the data frame
+# colnames(table_2_hamd_metareg_baseline) <- new_column_names
+# 
+# flextable(table_2_hamd_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+# 
+# # Regression results
+# 
+# table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "term") %>%
+#   select(-c("term", "type"))
+# 
+# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+# 
+# # Assign new column names to the data frame
+# colnames(table_1_hamd_metareg_baseline) <- new_column_names
+# 
+# flextable(table_1_hamd_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-cdrs-baseline
+#| tbl-cap: "CDRS Baseline Scores across Psychotherapy and Medication RCTs"
+#| tbl-cap-location: top
+
+# For row names
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
 
 # Assign new column names to the data frame
-colnames(table_1_cdrs_metareg_baseline) <- new_column_names
-
-flextable(table_1_cdrs_metareg_baseline) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
+colnames(results_met_sev_cdrs) <- new_column_names
+
+# Rounding
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  slice(1, 3, 2)
+
+results_met_sev_cdrs %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
   bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
   vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
   hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-hamd-baseline
-#| tbl-cap: "HAM-D Baseline Scores"
-#| tbl-cap-location: top
-
-# Prepare to tabulate
-
-table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>%
-  relocate("condition", .before = "baseline_smds") %>%
-  relocate("n", .before = "baseline_smds") %>%
-  relocate("lower_cis_smds", .before = "upper_cis_smds")
-
-new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(table_2_hamd_metareg_baseline) <- new_column_names
-
-flextable(table_2_hamd_metareg_baseline) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-
-# Regression results
-
-table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>%
-  relocate("condition", .before = "term") %>%
-  select(-c("term", "type"))
-
-new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-
-# Assign new column names to the data frame
-colnames(table_1_hamd_metareg_baseline) <- new_column_names
-
-flextable(table_1_hamd_metareg_baseline) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+# # All of the below is for the CDRS baseline meta-analysis when we have 4 levels
+# # Prepare to tabulate
+# 
+# table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "baseline_smds") %>%
+#   relocate("n", .before = "baseline_smds") %>%
+#   relocate("lower_cis_smds", .before = "upper_cis_smds")
+# 
+# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+# 
+# # Assign new column names to the data frame
+# colnames(table_2_cdrs_metareg_baseline) <- new_column_names
+# 
+# flextable(table_2_cdrs_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+# 
+# # Regression results
+# 
+# table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "term") %>%
+#   select(-c("term", "type"))
+# 
+# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+# 
+# # Assign new column names to the data frame
+# colnames(table_1_cdrs_metareg_baseline) <- new_column_names
+# 
+# flextable(table_1_cdrs_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
 

### 2024-05-10 Manuscript_for_rendering_in_word.qmd
new prisma

@@
 For adolescent depression, there are limited data from head-to-head trials of medication and psychotherapy, and hence recommendations must be derived from indirect comparisons of treatment efficacy.
-The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2023].
+The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
 This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
@@
 We excluded three studies because they had no control arm.
-We were unable to locate and complete extraction for one RCT (Almeida-Montes et al., 2005).
+We were unable to locate and complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986).
 Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
@@
 Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and one author completed data extraction for these papers.
-See @fig-prisma in the Supplement for PRISMA diagram.
+Seven studies met inclusion criteria and one author completed data extraction for these papers (see @fig-prisma for PRISMA diagram).
 
@@
 The data for the studies included in this meta-analysis are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+Please see @fig-prisma for a summary of the systematic review and the sources of included RCTs.
 
@@
 relaxation training, attention control, counselling).
+
+```{r, echo=FALSE}
+#| label: fig-prisma
+#| fig-cap: "PRISMA chart summarising sources of included studies"
+#| fig-cap-location: top
+knitr::include_graphics("PRISMA.png")
+```
 
@@
 #| label: fig-plot-means-all
-#| fig-cap: "Metanalytic estimates of within-group changes: all studies"
+#| fig-cap: "Meta-analytic estimates of within-group changes: all studies"
 #| fig-cap-location: top
@@
 
-Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
+As shown in Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
 Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
@@
 
-Overall, the active arms of psychotherapy studies were considerably more intensive than the control arms they were compared against (see @tbl-intensity-of-int for summary statistics).
-Active intervention arms featured significantly more sessions than control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
+As seen in @tbl-intensity-of-int active conditions featured significantly more sessions than control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
 These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`).
-The total hours involved in an intervention were higher in active vs control arms (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the total period of the intervention was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
+The total intervention hours were higher in active vs control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the duration was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
 
@@
 
-This paper took as its starting point the question of how anyone, be it a patient, parent, or clinician, should decide whether to opt for medication or psychotherapy for the treatment of adolescent depression.
-In order to address this question, we asked whether psychotherapy and medication are comparable on the basis of the existing evidence.
+This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence.
 Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two modalities.
@@
 
-Starting with the first question, we find evidence that participants in the two treatment modalities differ in the following key aspects: those enrolled in medication trials are more likely to be male and have more severe depression compared to those in psychotherapy trials.
-By contrast, there were no significant differences in age.
-
-Severity is important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
-Some studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g.
+Starting with the first question, we found that participants in medication trials are comparable on age but more likely to be male and have more severe depression compared to those in psychotherapy trials.
+These are indicators that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability between trials for each modality.
+
+Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
+Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g.
 within CBT studies), i.e.
@@
 
-Similarly, we found that on average there were about 7% more females in psychotherapy trials.
-Whilst there is little evidence that sex moderates treatment response within modality in adult trials of depression [@cuijpersGENDERPREDICTORMODERATOR2014], this is yet another indicator that different people enter trials of each modality type, which would violate basic assumptions of comparability between trials.
-
-We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We find a series of critical differences between the two modalities.
+We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We found a series of critical differences between the two modalities.
 
@@
 Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in non-industry trials which are also more likely to show lower pill placebo efficacy.
-Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where primacy is given to the number of recruited participants which is the primary unit of reimbursement.
+Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
 
 Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9).
-Our analysis could be critiqued as it relies on comparing the within arm symptom change of each trial taken out of randomization, which is generally ill advised.
+Our analysis could be critiqued as it relies on comparing within arm symptom change per trial, therefore effectively breaking randomization.
 This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical.
 However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomization structure.
-More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because of the fact that the people who attend psychotherapy and medication trials are different and therefore respond differently.
+More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
 In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison of the two modalities.
-This is all the more so as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings.
-Our results make obvious that comparing treatments based on the effect sizes of each modality (relative to their respective control arms) is misleading.
+This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings.
+Our results make obvious that comparing treatments based on the between-group effect sizes of each modality is misleading.
 
 Moving beyond comparison between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment.
-An optimal control condition is one where the treatment differs but everything else is equal.
 An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind).
-Yet, our results show that psychotherapy trials are unlikely to fulfill some other very basic conditions of the "all else is equal" assumption.
-Most (`r round(type_counts$wl_cau_percentage[1], 2)`%) of psychotherapy RCT control conditions are either waitlist or TAU, both of which are very likely to create negative expectations for participants not randomized to treatment.
-Thus, the comparison is not between treatment and no treatment, but rather treatment and the poor luck of being randomized to waiting.
-But we also find that even psychological controls were unreasonable counterfactuals.
+Yet, our results show that psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption of a counterfactual condition.
 In order to test that a psychological treatment is effective per se (e.g.
-because of the cognitive techniques the therapist deploys) rather than because of generic effects (e.g.
-pleasant human contact), aspects such as human contact time should be matched.
-We find that there are vast differences between treatment and control arms in psychotherapy trials which may lead to an inflation of the true efficacy of psychological treatments.
+because of the specific techniques) rather than because of generic effects (e.g.
+pleasant human contact), aspects such as therapist contact time should be matched.
+We find that there are vast differences between treatment and control arms in psychotherapy trials which may artificially inflate estimates of the efficacy of psychological treatments.
+Additionally, it is notable that most (67.24%) psychotherapy RCT control conditions are either WL or TAU, both of which are likely to be associated with disappointment bias, thereby further inflating estimates of efficacy of psychological treatments.
 
 Given all of the above, the certainty with which guidelines recommend psychotherapy over medication for adolescent depression is surprising.
-Indeed, we believe that our findings have a number of profound implications for patients, their families, clinicians and policy makers and we list these below.
+Indeed, we believe that our findings have several profound implications for patients, their families, clinicians and policy makers.
 
@@
 Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, as well as human contact with both therapists and group-members.
+There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, and total amount of contact.
 
@@
 
-In summary, our data give cause for consternation about the state of the evidence for treatments of youth depression, one of the most common and debilitating disorders in young people.
+In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression.
 Our data question the state of knowledge about the efficacy of psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices than what currently exists.
+Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices.
 
@@
 
-```{r, echo=FALSE}
-#| label: fig-prisma
-#| fig-cap: "PRISMA chart summarising the screening process for the systematic review"
-#| fig-cap-location: top
-knitr::include_graphics("PRISMA.png")
-```
-
 ## Full description of methods (including formalisms)
@@
 We excluded three studies because they had no control arm.
-We were unable to locate and therefore complete extraction for one RCT (Almeida-Montes et al., 2005).
+We were unable to locate and therefore complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986).
 Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
@@
 #| label: fig-plot-means-no-wl
-#| fig-cap: "Metanalytic estimates of within-group changes: waitlist studies excluded"
+#| fig-cap: "Meta-analytic estimates of within-group changes: waitlist studies excluded"
 #| fig-cap-location: top
@@
 #| label: fig-plot-means-clin
-#| fig-cap: "Metanalytic estimates of within-group changes: subclinical studies excluded"
+#| fig-cap: "Meta-analytic estimates of within-group changes: subclinical studies excluded"
 #| fig-cap-location: top
@@
 #| label: fig-plot-means-cdrs
-#| fig-cap: "Metanalytic estimates of within-group changes: CDRS studies only"
+#| fig-cap: "Meta-analytic estimates of within-group changes: CDRS studies only"
 #| fig-cap-location: top
@@
 #| label: fig-plot-means-hamd
-#| fig-cap: "Metanalytic estimates of within-group changes: HAM-D studies only"
+#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
 #| fig-cap-location: top

### 2024-05-13 Manuscript_for_rendering_in_word.qmd
Removed TADS from baseline comparisons Calculated between group effect sizes for psy active vs control

@@
 We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
-For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://www.metapsy.org/)).
+For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/)).
 For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD).
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression symptom scale used (selected according to the hierarchy defined in the Supplement).
 
@@
 df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE)
+  distinct(new_study_id, .keep_all = TRUE) %>% 
+  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
 
@@
 df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(percent_women != 100)
+  filter(percent_women != 100) # filter out studies with only women %>% 
+  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
 
@@
 df_for_age_metan <- df_baseline_demographics %>% 
-  filter(!is.na(mean_age))
-
-weighted_average_age <- sum(df_baseline_demographics$mean_age * df_baseline_demographics$baseline_n, na.rm = TRUE) / sum(df_baseline_demographics$baseline_n, na.rm = TRUE)
-tst <- mean(df_baseline_demographics$mean_age, na.rm = TRUE)
+  filter(!is.na(mean_age)) %>% 
+  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
 
@@
 ```
+
 We addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplementary Materials for the adjusted SMDs with their confidence intervals).
@@
 
-df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
+df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id") %>% 
+  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
 
@@
   mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
+
 ```
@@
 
-As shown in Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
+Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
 Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
@@
   mutate(across(where(is.numeric), ~round(., 2)))
+
+#function for between group effect sizes (cohens d)
+
+effect_btwn <- function(df) {
+  pooled_sd <- sqrt(((df$N[1]-1)*df$SD[1]^2 + (df$N[2]-1)*df$SD[2]^2) / (df$N[1] + df$N[2] - 2))
+  mean_diff <- df$Mean[1] - df$Mean[2]
+  effect_btwn <- mean_diff / pooled_sd
+  return(effect_btwn)
+}
+
+session_es <- effect_btwn(sessions)
+frequency_es <- effect_btwn(frequency)
+length_sessions_mins_es <- effect_btwn(length_sessions_mins)
+total_hours_es <- effect_btwn(total_hours)
+total_period_weeks_es <- effect_btwn(total_period_weeks)
+
+view(df_descr_psy_conditions)
+testing <- df_descr_psy_conditions %>% 
+  filter()
+
+other_ctr_ids <- df_long_for_metan[df_long_for_metan$type == "other ctr",]$new_study_id
+testing <- df_descr_psy_conditions %>% 
+  filter(new_study_id %in% other_ctr_ids)
+view(testing)
 ```
@@
 
+**References for included trials**
+
+References for trials included in the existing meta-analyses drawn upon for this study can be found [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/) for psychotherapy RCTs and [here](https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5) for medication RCTs.
+Below are references for the seven additional RCTs identified in the original systematic review conducted for the current study.
+
+*Publications*
+
+Atkinson, S., Lubaczewski, S., Ramaker, S., England, R.
+D., Wajsbrot, D.
+B., Abbas, R., & Findling, R.
+L.
+(2018).
+Desvenlafaxine versus placebo in the treatment of children and adolescents with major depressive disorder.
+*Journal of Child and Adolescent Psychopharmacology, 28(1),* 55-65.
+DOI: 10.1089/cap.2017.0099
+
+Durgam, S., Chen, C.
+Z., Migliore, R., Prakash, C., Edwards, J., & Findling, R.
+L.
+(2018).
+A phase 3, double-blind, randomized, placebo-controlled study of vilazodone in adolescents with major depressive disorder.
+*Pediatric Drugs, 20(4),* 353-363.
+DOI: 10.1007/s40272-018-0290-4
+
+Findling, R.
+L., McCusker, E., & Strawn, J.
+R.
+(2020).
+A randomized, double-blind, placebo-controlled trial of vilazodone in children and adolescents with major depressive disorder with twenty-six-week open-label follow-up.
+*Journal of Child and Adolescent Psychopharmacology, 30(6),* 355-365.
+DOI: 10.1089/cap.2019.0176
+
+Le Noury, J., Nardo, J.
+M., Healy, D., Jureidini, J., Raven, M., Tufanaru, C., & Abi-Jaoude, E.
+(2015).
+Restoring Study 329: efficacy and harms of paroxetine and imipramine in treatment of major depression in adolescence.
+*BMJ, 351,*, h4320.
+DOI: 10.1136/bmj.h4320
+
+Weihs, K.
+L., Murphy, W., Abbas, R., Chiles, D., England, R.
+D., Ramaker, S., & Wajsbrot, D.
+B.
+(2018).
+Desvenlafaxine versus placebo in a fluoxetine-referenced study of children and adolescents with major depressive disorder.
+Journal of Child and Adolescent Psychopharmacology, 28(1), 36-46.
+DOI: 10.1089/cap.2017.0100
+
+*Unpublished clinical trials*
+
+Active Reference (Fluoxetine) Fixed-dose Study of Vortioxetine in Paediatric Patients Aged 12 to 17 Years With Major Depressive Disorder (MDD).
+ClinicalTrials.gov Identifier: NCT02709746.
+Accessed 17 Jan 2024.
+
+Safety and Efficacy of Levomilnacipran ER in Adolescent Participants With Major Depressive Disorder. ClinicalTrials.gov Identifier: NCT02431806. Accessed 17 Jan 2024.
+
+**Hierarchy of depression symptom severity measurement scales**
+
+Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. (2016).
+
+1. Children’s Depression Rating Scale (CDRS)
+1. Hamilton Depression Rating Scale (HAMD)
+1. Montgomery Asberg Depression Rating Scale (MADRS)
+1. Beck Depression Inventory (BDI)
+1. Children’s Depression Inventory (CDI)
+1. Schedule for Affective Disorders and Schizophrenia for School-Aged Children (K-SADS)
+1. Mood and Feeling Questionnaire (MFQ)
+1. Reynolds Adolescent Depression Scale (RADS)
+1. Bellevue Index of Depression (BID)
+1. Child Depression Scale (CDS)
+1. Centre for Epidemiological Studies Depression Scale (CES-D)
+1. Child Assessment Schedule (CAS)
+1. Child Behaviour Checklist-Depression (CBCL-D)
+
 ## Full description of methods (including formalisms)
@@
 Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://www.metapsy.org/)).
+Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/)).
 Whilst Cuijpers et al.
@@
   mutate(across(where(is.numeric), ~round(., 2)))
+
+session_es_no_wl <- effect_btwn(sessions)
+frequency_es_no_wl <- effect_btwn(frequency)
+length_sessions_mins_es_no_wl <- effect_btwn(length_sessions_mins)
+total_hours_es_no_wl <- effect_btwn(total_hours)
+total_period_weeks_es_no_wl <- effect_btwn(total_period_weeks)
+
 ```

### 2024-05-15 Manuscript_for_rendering_in_word.qmd
Final draft

@@
 library(broom)
+library(effsize)
 
@@
 
-# Introduction
+# Abstract
+**Question:** Psychotherapy and medication are the main treatments for adolescent depression, with guidelines recommending psychotherapy as the first-line treatment for most cases.
+Given the scarcity of head-to-head comparisons, recommendations are based on indirect comparisons of outcomes obtained in randomised controlled trials (RCTs) within each modality.
+Here we examine whether basic conditions required to draw valid inferences from these indirect comparisons are met.
+**Study selection and analysis:** Drawing upon studies included in two recent meta-analyses, and supplementing with an original systematic search, 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years) were identified.
+Using meta-analytic approaches, we examined comparability of a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
+Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
+**Findings:** Participants in medication RCTs had higher depression severity and were more likely to be male compared to psychotherapy RCTs.
+The pooled effect size of medication controls was very large (SMD=-1.9), and was medium for psychotherapy controls (SMD=-0.5).
+Medication RCTs also had significantly more trial sites.
+Within psychotherapy RCTs, control conditions were less intensive on average than active conditions (e.g.
+fewer contact hours).
+**Conclusions:** Medication and psychotherapy RCTs differ on both participant and methodological characteristics, thereby violating the conditions for valid comparison between modalities.
+Psychotherapy controls often involve little therapist contact and are easy-to-beat comparators.
+These findings cast doubt on the confidence with which psychotherapy is recommended over medication for youth depression, and highlight the pressing need to improve the evidence base.
+
+# Key messages
+Psychotherapy is recommended before medication for most cases of depression in children and adolescents, a recommendation that is based on indirect comparisons of outcomes from randomised controlled trials (RCTs) within each treatment modality.
+We examine the validity of these inferences by scrutinising the comparability of psychotherapy and medication RCTs.
+We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the effect sizes of medication controls (i.e.
+pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
+We also examine the quality of controls used in psychotherapy RCTs and find that they are poorly matched to active intervention arms in ways such as human contact hours, and hence represent poor and easy to beat comparators.
+Our findings underscore the need for a higher quality evidence base upon which to base treatment guidelines and clinical decision making.
+
+# Background
 
@@
 
+# Objective
+
 In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
@@
 
-# Method
+# Study selection and analysis
 
@@
 
-# Results
+# Findings
 
@@
 df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE) %>% 
+  distinct(new_study_id, .keep_all = TRUE)
+
+df_for_baseline_severity <- df_for_baseline_severity %>% 
     filter(new_study_id != "March, 2004")  # removing TADS because it does not technically belong to either the psy or med groups
@@
   filter(percent_women != 100) # filter out studies with only women %>%
+
+df_for_sex_metan <- df_for_sex_metan %>% 
   filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
@@
 df_for_age_metan <- df_baseline_demographics %>% 
-  filter(!is.na(mean_age)) %>% 
+  filter(!is.na(mean_age))
+
+df_for_age_metan <- df_for_age_metan %>% 
   filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
@@
 
-df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id") %>% 
+df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
+
+df_baseline_demographics <- df_baseline_demographics %>% 
   filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
@@
 
-control_summary <- rbind(sessions, frequency, length_sessions_mins, total_hours, total_period_weeks)
+control_summary <- rbind(sessions, frequency, length_sessions_mins, total_hours)
 
@@
     Column == "total_hours" ~ "Total intervention hours",
-    Column == "total_period_weeks" ~ "Intervention duration (weeks)",
     TRUE ~ as.character(Column)  # Keep original value if no match
@@
 
+# other_ctr_ids <- df_long_for_metan[df_long_for_metan$type == "other ctr",]$new_study_id
+# testing <- df_descr_psy_conditions %>% 
+#   filter(new_study_id %in% other_ctr_ids)
+# view(testing)
+
+# t tests
+
+session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
+freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
+session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
+total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
+
+extract_t_test_stats <- function(df) {
+
+  t_test_stats <- data.frame(
+  outcome = df$data.name,
+  statistic = df$statistic,
+  df = df$parameter,
+  p_value = df$p.value,
+  ci_lower = df$conf.int[1],
+  ci_upper = df$conf.int[2])
+
+  return(t_test_stats)
+
+}
+
+results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
+results_freq_t_test <- extract_t_test_stats(freq_t_test)
+results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
+results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
+
+# for t test table
+
+control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
+
+# For row names
+control_summary_t_tests <- control_summary_t_tests %>%
+  mutate(outcome = case_when(
+    row_number() == 1 ~ "Number of sessions",
+    row_number() == 2 ~ "Intensity (sessions per week)",
+    row_number() == 3 ~ "Session length (mins)",
+    row_number() == 4 ~ "Total intervention hours"
+  ))
+
+# Define new column names
+new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(control_summary_t_tests) <- new_column_names
+
+#Rounding
+control_summary_t_tests <- control_summary_t_tests %>%
+  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
+  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+
+# function for between group effect sizes (cohens d)
+# 
+# effect_btwn <- function(df) {
+#   pooled_sd <- sqrt(((df$N[1]-1)*df$SD[1]^2 + (df$N[2]-1)*df$SD[2]^2) / (df$N[1] + df$N[2] - 2))
+#   mean_diff <- df$Mean[1] - df$Mean[2]
+#   effect_btwn <- mean_diff / pooled_sd
+#   return(effect_btwn)
+# }
+# 
+# session_es <- effect_btwn(sessions)
+# frequency_es <- effect_btwn(frequency)
+# length_sessions_mins_es <- effect_btwn(length_sessions_mins)
+# total_hours_es <- effect_btwn(total_hours)
+# total_period_weeks_es <- effect_btwn(total_period_weeks)
+
+# using a package to calculate instead
+
+session_es <- cohen.d(df_descr_psy_conditions$no_sessions ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+frequency_es <- cohen.d(df_descr_psy_conditions$freq_weeks ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+length_sessions_mins_es <- cohen.d(df_descr_psy_conditions$length_sessions_mins ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+total_hours_es <- cohen.d(df_descr_psy_conditions$total_hours ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+
+# going to try displaying summary statistics and t-tests in one place
+
+control_summary <- cbind(control_summary, 
+                          "Cohen's d" = rep(NA, nrow(control_summary)),
+                         "Upper CI" = rep(NA, nrow(control_summary)),
+                         "Lower CI" = rep(NA, nrow(control_summary)),
+                         t = rep(NA, nrow(control_summary)), 
+                          df = rep(NA, nrow(control_summary)), 
+                          "p-value" = rep(NA, nrow(control_summary)))
+
+# Update the first row with session_es
+control_summary[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  session_es$estimate, session_es$conf.int[1], session_es$conf.int[2], 
+  control_summary_t_tests$`t statistic`[1], control_summary_t_tests$df[1], 
+  control_summary_t_tests$`p-value`[1]
+)
+
+# Update the third row with frequency_es
+control_summary[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  frequency_es$estimate, frequency_es$conf.int[1], frequency_es$conf.int[2], 
+  control_summary_t_tests$`t statistic`[2], control_summary_t_tests$df[2], 
+  control_summary_t_tests$`p-value`[2]
+)
+
+# Update the fifth row with length_sessions_mins_es
+control_summary[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  length_sessions_mins_es$estimate, length_sessions_mins_es$conf.int[1], length_sessions_mins_es$conf.int[2], 
+  control_summary_t_tests$`t statistic`[3], control_summary_t_tests$df[3], 
+  control_summary_t_tests$`p-value`[3]
+)
+
+# Update the seventh row with total_hours_es
+control_summary[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  total_hours_es$estimate, total_hours_es$conf.int[1], total_hours_es$conf.int[2], 
+  control_summary_t_tests$`t statistic`[4], control_summary_t_tests$df[4], 
+  control_summary_t_tests$`p-value`[4]
+)
+
 control_summary <- control_summary %>%
+  mutate(
+    `Cohen's d` = as.numeric(`Cohen's d`),
+    `Upper CI` = as.numeric(`Upper CI`),
+    `Lower CI` = as.numeric(`Lower CI`)
+  ) %>%
   mutate(across(where(is.numeric), ~round(., 2)))
 
-#function for between group effect sizes (cohens d)
-
-effect_btwn <- function(df) {
-  pooled_sd <- sqrt(((df$N[1]-1)*df$SD[1]^2 + (df$N[2]-1)*df$SD[2]^2) / (df$N[1] + df$N[2] - 2))
-  mean_diff <- df$Mean[1] - df$Mean[2]
-  effect_btwn <- mean_diff / pooled_sd
-  return(effect_btwn)
-}
-
-session_es <- effect_btwn(sessions)
-frequency_es <- effect_btwn(frequency)
-length_sessions_mins_es <- effect_btwn(length_sessions_mins)
-total_hours_es <- effect_btwn(total_hours)
-total_period_weeks_es <- effect_btwn(total_period_weeks)
-
-view(df_descr_psy_conditions)
-testing <- df_descr_psy_conditions %>% 
-  filter()
-
-other_ctr_ids <- df_long_for_metan[df_long_for_metan$type == "other ctr",]$new_study_id
-testing <- df_descr_psy_conditions %>% 
-  filter(new_study_id %in% other_ctr_ids)
-view(testing)
+# # plot
+# 
+# ggplot(df_descr_psy_conditions_no_wl, aes(x = total_hours, fill = levels_var)) +
+#   geom_histogram(position = "identity", alpha = 0.5, binwidth = 5, color = "black") +
+#   facet_wrap(~ levels_var, ncol = 2) +
+#   theme_minimal() +
+#   labs(title = "Histograms of Number of Total Hours by Group",
+#        x = "Number of Hours",
+#        y = "Frequency") +
+#   scale_fill_manual(values = c("lightpink", "lightblue"))
+
 ```
@@
   as_flextable(hide_grouplabel = TRUE ) %>% 
-  bold(i = c(1, 4, 7, 10, 13), bold = TRUE, part = "body") %>%  
+  bold(i = c(1, 4, 7, 10), bold = TRUE, part = "body") %>%  
   set_table_properties(width = 1) %>%  # Set table width 
   autofit() %>%  # Autofit column widths 
-  align(j = 2:4, align = "center", part = "all") %>% 
+  align(j = 2:9, align = "center", part = "all") %>% 
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
@@
   border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
+  hline(j = 1:4, part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = c(1,4), part = "body", border = small_border) %>% 
   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
@@
   line_spacing(space = .7, part = "all") 
-
 ```
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
-total_period_t_test <- t.test(total_period_weeks ~ levels_var, data = df_descr_psy_conditions)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-results_total_period_t_test <- extract_t_test_stats(total_period_t_test)
-
-control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test, results_total_period_t_test)
-
-# For row names
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours",
-    row_number() == 5 ~ "Intervention duration (weeks)"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests) <- new_column_names
-
-#Rounding
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+# #| label: tbl-t-tests-intensity
+# #| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
+# #| tbl-cap-location: top
+# 
+# flextable(control_summary_t_tests) %>%
+#   set_table_properties(width = 1) %>%  # Set table width %>% 
+#   autofit() %>%  # Autofit column widths 
+#   align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
+#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+#   #italic(i = 2, italic = TRUE, part = "header") %>% 
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>% 
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>% 
+#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
+#   paginate(init = TRUE) %>% 
+#   line_spacing(space = .7, part = "all")
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-t-tests-intensity
-#| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-#| tbl-cap-location: top
-
-flextable(control_summary_t_tests) %>%
-  set_table_properties(width = 1) %>%  # Set table width %>% 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-  #add_header_row(values = "Table 6", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
-As seen in @tbl-intensity-of-int active conditions featured significantly more sessions than control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
+<!-- As seen in @tbl-intensity-of-int active conditions featured significantly more sessions than control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
 These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`).
 The total intervention hours were higher in active vs control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the duration was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
-
-# Discussion
+-->
+
+As seen in @tbl-intensity-of-int, active conditions featured significantly more sessions when compared to control conditions.
+Sessions in active conditions were longer and more frequent, resulting in significantly more intervention hours overall.
+Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data for a number of trials.
+We performed a sensitivity analysis where we excluded trials that used a WL control condition; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
+
+# Conclusions and Clinical Implications
 
@@
   mutate(total_count = sum(n),
-         wl_cau_sum = sum(n[type %in% c("wl", "cau")]),
-         wl_cau_percentage = wl_cau_sum / total_count * 100)
+         wl_sum = sum(n[type == "wl"]),
+         wl_percentage = wl_sum / total_count * 100)
+
+# how many examples of matching of active and control in number of hours
+
+# instances_count <- df_descr_psy_conditions_no_wl %>%
+#   filter(!is.na(total_hours)) %>%
+#   group_by(new_study_id, total_hours) %>%
+#   summarise(count = n()) %>%
+#   filter(count > 1) %>%
+#   summarise(total_instances = n())
 
@@
 pleasant human contact), aspects such as therapist contact time should be matched.
-We find that there are vast differences between treatment and control arms in psychotherapy trials which may artificially inflate estimates of the efficacy of psychological treatments.
-Additionally, it is notable that most (67.24%) psychotherapy RCT control conditions are either WL or TAU, both of which are likely to be associated with disappointment bias, thereby further inflating estimates of efficacy of psychological treatments.
+Many (24%) psychotherapy RCTs use waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
+TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy (e.g.
+an educational brochure) or online-only control conditions which did not involve any direct therapist contact.
+Importantly, controls were often very poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
+Overall, there is a lack of rigor in matching control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
 
@@
 Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of psychotherapy RCTs where such rigor has been applied, such as @youngRandomizedDepressionPrevention2016 where active and control arms were matched on frequency and duration of sessions, and total amount of contact.
+There are examples of psychotherapy RCTs where such rigor has been applied (e.g.
+Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
 
@@
 total_hours <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_hours")
-total_period_weeks <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_period_weeks")
-
-control_summary_no_wl <- rbind(sessions, frequency, length_sessions_mins, total_hours, total_period_weeks)
+
+control_summary_no_wl <- rbind(sessions, frequency, length_sessions_mins, total_hours)
 
@@
 
+# t tests
+
+session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions_no_wl)
+freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
+session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions_no_wl)
+total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions_no_wl)
+
+extract_t_test_stats <- function(df) {
+
+  t_test_stats <- data.frame(
+  outcome = df$data.name,
+  statistic = df$statistic,
+  df = df$parameter,
+  p_value = df$p.value,
+  ci_lower = df$conf.int[1],
+  ci_upper = df$conf.int[2])
+
+  return(t_test_stats)
+
+}
+
+results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
+results_freq_t_test <- extract_t_test_stats(freq_t_test)
+results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
+results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
+
+control_summary_t_tests_no_wl <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
+
+# For row names
+control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
+  mutate(outcome = case_when(
+    row_number() == 1 ~ "Number of sessions",
+    row_number() == 2 ~ "Intensity (sessions per week)",
+    row_number() == 3 ~ "Session length (mins)",
+    row_number() == 4 ~ "Total intervention hours"
+  ))
+
+# Define new column names
+new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
+
+# Assign new column names to the data frame
+colnames(control_summary_t_tests_no_wl) <- new_column_names
+
+#Rounding
+control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
+  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
+  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
+
+# calculating with my function
+
+# session_es_no_wl <- effect_btwn(sessions)
+# frequency_es_no_wl <- effect_btwn(frequency)
+# length_sessions_mins_es_no_wl <- effect_btwn(length_sessions_mins)
+# total_hours_es_no_wl <- effect_btwn(total_hours)
+# total_period_weeks_es_no_wl <- effect_btwn(total_period_weeks)
+
+# using a package to calculate instead
+
+session_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$no_sessions ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+frequency_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$freq_weeks ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+length_sessions_mins_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$length_sessions_mins ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+total_hours_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$total_hours ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
+
+# going to try displaying summary statistics and t-tests in one place
+
+control_summary_no_wl <- cbind(control_summary_no_wl, 
+                          "Cohen's d" = rep(NA, nrow(control_summary_no_wl)),
+                         "Upper CI" = rep(NA, nrow(control_summary_no_wl)),
+                         "Lower CI" = rep(NA, nrow(control_summary_no_wl)),
+                         t = rep(NA, nrow(control_summary_no_wl)), 
+                          df = rep(NA, nrow(control_summary_no_wl)), 
+                          "p-value" = rep(NA, nrow(control_summary_no_wl)))
+
+# Update the first row with session_es_no_wl
+control_summary_no_wl[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  session_es_no_wl$estimate, session_es_no_wl$conf.int[1], session_es_no_wl$conf.int[2], 
+  control_summary_t_tests_no_wl$`t statistic`[1], control_summary_t_tests_no_wl$df[1], 
+  control_summary_t_tests_no_wl$`p-value`[1]
+)
+
+# Update the third row with frequency_es_no_wl
+control_summary_no_wl[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  frequency_es_no_wl$estimate, frequency_es_no_wl$conf.int[1], frequency_es_no_wl$conf.int[2], 
+  control_summary_t_tests_no_wl$`t statistic`[2], control_summary_t_tests_no_wl$df[2], 
+  control_summary_t_tests_no_wl$`p-value`[2]
+)
+
+# Update the fifth row with length_sessions_mins_es_no_wl
+control_summary_no_wl[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  length_sessions_mins_es_no_wl$estimate, length_sessions_mins_es_no_wl$conf.int[1], length_sessions_mins_es_no_wl$conf.int[2], 
+  control_summary_t_tests_no_wl$`t statistic`[3], control_summary_t_tests_no_wl$df[3], 
+  control_summary_t_tests_no_wl$`p-value`[3]
+)
+
+# Update the seventh row with total_hours_es_no_wl
+control_summary_no_wl[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
+  total_hours_es_no_wl$estimate, total_hours_es_no_wl$conf.int[1], total_hours_es_no_wl$conf.int[2], 
+  control_summary_t_tests_no_wl$`t statistic`[4], control_summary_t_tests_no_wl$df[4], 
+  control_summary_t_tests_no_wl$`p-value`[4]
+)
+
 control_summary_no_wl <- control_summary_no_wl %>%
+  mutate(
+    `Cohen's d` = as.numeric(`Cohen's d`),
+    `Upper CI` = as.numeric(`Upper CI`),
+    `Lower CI` = as.numeric(`Lower CI`)
+  ) %>%
   mutate(across(where(is.numeric), ~round(., 2)))
-
-session_es_no_wl <- effect_btwn(sessions)
-frequency_es_no_wl <- effect_btwn(frequency)
-length_sessions_mins_es_no_wl <- effect_btwn(length_sessions_mins)
-total_hours_es_no_wl <- effect_btwn(total_hours)
-total_period_weeks_es_no_wl <- effect_btwn(total_period_weeks)
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions_no_wl)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions_no_wl)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions_no_wl)
-total_period_t_test <- t.test(total_period_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-results_total_period_t_test <- extract_t_test_stats(total_period_t_test)
-
-control_summary_t_tests_no_wl <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test, results_total_period_t_test)
-
-# For row names
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours",
-    row_number() == 5 ~ "Intervention duration (weeks)"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests_no_wl) <- new_column_names
-
-#Rounding
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
-
-```
-
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-t-tests-intensity-no-wl
-#| tbl-cap: "Results for t-tests comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
-#| tbl-cap-location: top
-
-flextable(control_summary_t_tests_no_wl) %>%
-  set_table_properties(width = 1) %>%  # Set table width %>% 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:ncol(control_summary_t_tests_no_wl), align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-  #add_header_row(values = "Table 6", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
+# #| label: tbl-t-tests-intensity-no-wl
+# #| tbl-cap: "Results for t-tests comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
+# #| tbl-cap-location: top
+# 
+# flextable(control_summary_t_tests_no_wl) %>%
+#   set_table_properties(width = 1) %>%  # Set table width %>% 
+#   autofit() %>%  # Autofit column widths 
+#   align(j = 2:ncol(control_summary_t_tests_no_wl), align = "center", part = "all") %>% 
+#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
+#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+#   #italic(i = 2, italic = TRUE, part = "header") %>% 
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>% 
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>% 
+#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
+#   paginate(init = TRUE) %>% 
+#   line_spacing(space = .7, part = "all")
 

### 2024-05-16 Manuscript_for_rendering_in_word.qmd
Vancouver formatting style and word cuts

@@
 ---
-title: "Revisiting Child and Adolescent Depression Treatments"
-subtitle: "A Quantitative Critique of the Evidence Base"
+title: "Comparing Apples and Oranges in Youth Depression Treatments?"
+subtitle: "A Quantitative Critique of the Evidence Base and Guidelines"
 author:
@@
 bibliography: "emotion_concepts_paper.bib"
+csl: "vancouver.csl"
 font:
@@
 # Abstract
-**Question:** Psychotherapy and medication are the main treatments for adolescent depression, with guidelines recommending psychotherapy as the first-line treatment for most cases.
-Given the scarcity of head-to-head comparisons, recommendations are based on indirect comparisons of outcomes obtained in randomised controlled trials (RCTs) within each modality.
-Here we examine whether basic conditions required to draw valid inferences from these indirect comparisons are met.
-**Study selection and analysis:** Drawing upon studies included in two recent meta-analyses, and supplementing with an original systematic search, 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years) were identified.
-Using meta-analytic approaches, we examined comparability of a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
+**Question:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
+In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
+**Study selection and analysis:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+Using meta-analyses, we compared a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
 Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
-**Findings:** Participants in medication RCTs had higher depression severity and were more likely to be male compared to psychotherapy RCTs.
-The pooled effect size of medication controls was very large (SMD=-1.9), and was medium for psychotherapy controls (SMD=-0.5).
-Medication RCTs also had significantly more trial sites.
-Within psychotherapy RCTs, control conditions were less intensive on average than active conditions (e.g.
-fewer contact hours).
-**Conclusions:** Medication and psychotherapy RCTs differ on both participant and methodological characteristics, thereby violating the conditions for valid comparison between modalities.
+**Findings:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
+There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.70)) vs psychotherapy controls (SMD=-0.5 (95% CI: -0.75 to -0.25)).
+Within psychotherapy RCTs, control conditions were less intensive on average than active conditions.
+**Conclusions:** Medication and psychotherapy RCTs differ on fundamental participant and methodological characteristics, thereby violating key conditions for valid comparison between them.
 Psychotherapy controls often involve little therapist contact and are easy-to-beat comparators.
-These findings cast doubt on the confidence with which psychotherapy is recommended over medication for youth depression, and highlight the pressing need to improve the evidence base.
+These findings cast doubt on the confidence with which psychotherapy is recommended for youth depression, and highlight the pressing need to improve the evidence base.
 
@@
 
-For adolescent depression, there are limited data from head-to-head trials of medication and psychotherapy, and hence recommendations must be derived from indirect comparisons of treatment efficacy.
-The UK National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend that youth are first offered psychological therapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
+For adolescent depression, there are limited head-to-head trials of medication and psychotherapy, and hence recommendations are derived from indirect comparisons of treatment efficacy.
+The National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend psychotherapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
 This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
@@
 
-In this paper, we examine whether the existing evidence for adolescent depression treatment can offer valid answers to this question.
+In this paper, we examine whether the existing evidence for adolescent depression treatments can offer valid answers to this question.
 We provide a conceptual framework and test a series of hypotheses using data from existing trials.
 Two points are crucial to indirect comparisons of treatment modalities.
-First, whether the participants of trials in one modality are comparable to those in another modality.
+First, whether the participants in trials are comparable across modalities.
 Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
@@
 If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable (see Supplement for further details).
+the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
 
@@
 The assumption that medication and psychotherapy trials sample from the same population may not be valid as patients and parents often have treatment preferences [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
-Moreover, treatment preferences correlate with clinically-relevant characteristics of the participants, including severity and sex.
-Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and therefore, if they differ across psychotherapy and medication trials, they may confound comparisons.
-
-In terms of the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-Most obviously, participants in psychotherapy trials are unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-This creates differential expectations which may favour the psychotherapy active condition and disadvantage the psychotherapy control; participants in the active condition are content to be receiving the “cutting edge” treatment whilst those in the control are dissatisfied for having missed out (i.e.
+Moreover, treatment preferences correlate with clinically-relevant participant characteristics, including severity and sex.
+Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and if they differ across psychotherapy and medication trials they may confound comparisons.
+
+Regarding the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
+Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
+This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the “cutting edge” treatment, whilst those in the control are dissatisfied for having missed out (i.e.
 “disappointment bias” [@reltonEthicsTrialsCohorts2017].
@@
 Another difference in design is the number of trial sites.
-Previous research has shown that the number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
-This phenomenon may be due to lower quality of assessments in trials with more sites, with higher rates of classification errors, entailing higher rates of apparent spontaneous remission or regression to the mean.
+The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
+This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
 
 An inter-related issue concerns the effect of control conditions.
-Often, in the public domain, psychotherapy and medication are compared to each other on the basis of their respective effect sizes.
-However, these effect sizes represent differences between the active intervention and the control condition for each modality.
-For these effect sizes to be comparable, placebo and psychotherapy controls ought to be equal in their effects.
+Often psychotherapy and medication are compared on the basis of their respective effect sizes (i.e.
+differences between the active and control conditions for each modality).
+For these to be comparable, medication and psychotherapy controls ought to be equal in their effects.
 Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100%-60% and another arose from a difference of 40%-0%.
+two effect sizes of 40% would be considered equal, even if one arose from a difference of 100%-60% and another from a difference of 40%-0%.
 
 Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention [@guoChapterCounterfactualFramework2014]: what would have been the outcome had an individual not received the intervention, with all else being equal.
-A pill placebo condition, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
+Pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
 In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g.
-with respect to number of hours of therapist contact).
+in number of hours of therapist contact).
 
@@
 In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-We hypothesise that there are substantial methodological differences between psychotherapy and medication RCTs, making comparisons problematic, and we examine this in the following ways.
-First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline severity of depression; b) percentage females; and c) mean age.
-Second, we examine trial characteristics including the efficacy of the control arms, using random effects meta-regression, and the number of trial sites.
+We hypothesise that there are substantial differences between psychotherapy and medication RCTs, making their comparison problematic, which we examine in the following ways.
+First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline depression severity; b) percentage females; and c) mean age.
+Second, we examine trial characteristics including the efficacy of the control arms, using random-effects meta-regression, and the number of trial sites.
 Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
@@
 
-A more detailed description of our methods, including the formalisms on which analyses are based, can be found in the Supplement.
+A detailed description of our methods, including formalisms on which analyses are based, can be found in the Supplement.
 
@@
 For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
-We excluded three studies because they had no control arm.
-We were unable to locate and complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986).
-Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
-
-For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
+
+For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
 Two authors screened 450 titles and abstracts, and 38 full text records.
@@
 
-We conducted a series of random effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms at baseline, sex and age.
-Meta-analyses were implemented using R's meta package (version 7.0-0).
+We conducted random-effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms, sex and age.
+Meta-analyses were implemented using R's meta package.
 
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression symptom scale used (selected according to the hierarchy defined in the Supplement).
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression scale used (selected according to the hierarchy defined in the Supplement).
 
@@
 If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis.
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani et al.'s meta-analysis.
 -->
 
-For the purposes of meta-analysis, it is necessary to estimate a standard error of the SMD.
+For meta-analysis it is necessary to estimate a standard error of the SMD.
 This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation, we simulated n = 1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in the subsequent analyses (please refer to Supplement for full details).
+To ensure that our results are not biased by misestimation, we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
 
@@
 
-#### Random Effects Metaregression
-
-We estimated the pooled standardised mean difference for each arm by using a random effects meta-analysis implemented in R's metafor package (version 4.4-0).
-
-<!-- The main underlying assumption of random effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+#### Random-effects Metaregression
+
+We estimated the pooled SMD for each arm by using a random-effects meta-analysis implemented in R's metafor package.
+
+<!-- The main underlying assumption of random-effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
 Therefore, we can estimate a two stage model with: -->
@@
 ```
-We conducted a series of sensitivity analyses.
-For each of the meta-analyses we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
+We conducted a series of sensitivity analyses where we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
 Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
@@
 Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
-To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
+We plotted the z-value of the difference between the two coefficients against the number of simulations.
 We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
@@
 
-The data for the studies included in this meta-analysis are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-Please see @fig-prisma for a summary of the systematic review and the sources of included RCTs.
+Data for included are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+Please see @fig-prisma for a summary of the sources of included RCTs.
 
@@
 The summary statistics are provided for each subgroup (i.e.
-for medication and psychotherapy RCTs) and the p-value derives from the test for subgroup differences.
+medication and psychotherapy) and the p-value derives from the test for subgroup differences.
 
@@
 
-On average, severity of depressive symptoms at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline_results).
+On average, depression severity at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline_results).
 When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
@@
 
-To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS-R and HAM-D, on which there was a sufficient number of studies to metanalyse.
-As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplementary Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
+To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS and HAM-D, on which there was a sufficient number of studies to metanalyse.
+As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplemental Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
 
@@
 We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-As can be seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and the psychotherapy control arms.
+As seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
 In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
@@
 Here, medication control is the reference category to which all others are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p<0.0001).
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p<0.0001).
 
@@
 
-We  conducted a series of sensitivity analyses (all figures can be found in the Supplementary Materials).
-First, we analysed the data after excluding waitlist control studies, which yielded a pattern of results is very similar to that of the overall analyses (see @fig-plot-means-no-wl).
-Second, we analysed the data after excluding sub-clinical studies, which again yielded a similar pattern of results (see @fig-plot-means-clin).
-Third, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAM-D (see @fig-plot-means-hamd).
-Medication control and psychotherapy control conditions remained significantly different, however the small number of studies using each of these instruments resulted in less precise meta-analytic estimates of the SMDs.
-Finally, we showed different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
+We  conducted a series of sensitivity analyses (all figures in the Supplemental Materials).
+Excluding waitlist control studies (see @fig-plot-means-no-wl) and sub-clinical studies (see @fig-plot-means-clin) yielded a pattern of results very similar to the overall analyses.
+Next, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAMD (see @fig-plot-means-hamd).
+Medication control and psychotherapy control conditions remained significantly different, though the small number of studies resulted in less precise estimates of the SMDs.
+Finally, we showed that different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
 
@@
 
-We addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplementary Materials for the adjusted SMDs with their confidence intervals).
+We addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplement).
 The difference between the medication control and psychotherapy control arms remained similar to the overall analyses.
@@
 Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies for which we had data on number of sites, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
+Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 
@@
 
-<!-- As seen in @tbl-intensity-of-int active conditions featured significantly more sessions than control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Number of sessions"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Number of sessions"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Number of sessions"]`).
-These sessions were also significantly longer (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Session length (mins)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Session length (mins)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Session length (mins)"]`) and more frequent (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intensity (sessions per week)"]`).
-The total intervention hours were higher in active vs control conditions (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Total intervention hours"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Total intervention hours"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Total intervention hours"]`), though the duration was similar (*t* (`r control_summary_t_tests$df[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`) = `r control_summary_t_tests$"t statistic"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`, *p* = `r control_summary_t_tests$"p-value"[control_summary_t_tests$Outcome == "Intervention duration (weeks)"]`).
--->
-
 As seen in @tbl-intensity-of-int, active conditions featured significantly more sessions when compared to control conditions.
 Sessions in active conditions were longer and more frequent, resulting in significantly more intervention hours overall.
-Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data for a number of trials.
-We performed a sensitivity analysis where we excluded trials that used a WL control condition; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
+Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data.
+We performed a sensitivity analysis where we excluded trials using waitlist controls; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
 
@@
 
-This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence.
-Specifically, our paper answered two questions that are fundamental to any attempts at comparing the two modalities.
+This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence, by looking at two key conditions for comparability.
 First, whether the participants of trials in one modality are comparable to those in another modality.
-Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
-
-Starting with the first question, we found that participants in medication trials are comparable on age but more likely to be male and have more severe depression compared to those in psychotherapy trials.
-These are indicators that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability between trials for each modality.
-
-Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressant therapy [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
-Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however, these are within modality (e.g.
-within CBT studies), i.e.
-within those people who have chosen to be in the particular trial and modality.
-Moreover, there is evidence that severity may represent different subtypes in terms of course of depression and its outcomes in real life settings [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
-
-We then turned to our second basic question, about whether key conditions of the trial design were comparable between modalities. We found a series of critical differences between the two modalities.
-
-First, medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
-Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in non-industry trials which are also more likely to show lower pill placebo efficacy.
+Second, whether conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
+
+Starting with the first question, we found that participants in medication trials are comparable on age but are more likely to be male and have more severe depression compared to those in psychotherapy trials.
+This indicates that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability.
+
+Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressants [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
+Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however these are within people who have chosen to be in the particular trial and modality.
+Moreover, severity may represent different subtypes in terms of course of depression and real-life outcomes [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
+
+We then turned to our second question about whether trial design conditions are comparable between modalities.
+We found that medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
+Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy.
 Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
 
-Second, psychotherapy controls have moderate effect size (-0.5) whereas pill-placebo has very large effect size (-1.9).
-Our analysis could be critiqued as it relies on comparing within arm symptom change per trial, therefore effectively breaking randomization.
-This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving the randomization (in order to balance confounders) is critical.
-However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomization structure.
-More importantly, we do not make the claim with our analyses that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences concerning the comparison of the two modalities.
-This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings.
-Our results make obvious that comparing treatments based on the between-group effect sizes of each modality is misleading.
-
-Moving beyond comparison between the two modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving the treatment.
-An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind).
-Yet, our results show that psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption of a counterfactual condition.
+Second, psychotherapy controls have moderate effect sizes (-0.5) whereas medication controls have very large effect sizes (-1.9).
+Our analysis could be critiqued as it compares within arm symptom change per trial, therefore effectively breaking randomisation.
+This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving randomisation to balance confounders is critical.
+However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
+More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
+In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences from comparisons of modalities.
+This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
+
+Moving beyond comparison between modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving treatment.
+An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind) yet psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption.
 In order to test that a psychological treatment is effective per se (e.g.
@@
 Many (24%) psychotherapy RCTs use waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
-TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy (e.g.
-an educational brochure) or online-only control conditions which did not involve any direct therapist contact.
+TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
 Importantly, controls were often very poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
@@
 
-First, the grounds for a comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is an urgent need to revisit guidelines and public information in light of the limitations.
-
-Second, the low quality of control conditions of psychotherapy trials for adolescent depression should prompt a rethinking of what needs to be done to create fair comparators.
-Indeed, investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of psychotherapy RCTs where such rigor has been applied (e.g.
+First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is an urgent need to revisit guidelines and public information in light of the limitations.
+
+Second, the low quality of psychotherapy control conditions should prompt consideration of how to create fair comparators.
+Investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
+There are examples of RCTs where such rigor has been applied (e.g.
 Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
@@
 The first obstacle is the comparability of the populations taking part.
-Head-to-head comparisons of psychotherapy with medication (as has been done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they would receive.
+Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive.
 And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
@@
 In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression.
-Our data question the state of knowledge about the efficacy of psychotherapies and, in particular, the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
+Our data question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
 Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices.
 
-# Supplementary Materials
+# Supplemental Materials
 
@@
 We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
-after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review).
+after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review).
 We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
-We used the same search terms as Cipriani (2016) with one additional search term to include only placebo-controlled trials (see below).
+We used the same search terms as Cipriani [@ciprianiComparativeEfficacyTolerability2016] with one additional search term to include only placebo-controlled trials (see below).
 We additionally applied filters to specify our date range, and to exclude reviews and non-human studies.
@@
 
-Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. (2016).
+Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. [@ciprianiComparativeEfficacyTolerability2016].
 
@@
 Whilst Cuijpers et al.
-(2021) excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
+[@cuijpersEffectsPsychologicalTreatments2021] excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
 We also included studies which had data available for other variables in interest, including number of sites or baseline demographics; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s (2021) literature search.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpersEffectsPsychologicalTreatments2021] literature search.
 
@@
 
-We conducted a systematic search for medication studies published after the final search date of Cipriani's (2016) review up to the final search date of Cuijpers et al's (2021) review to ensure we analysed an equivalently up-to-date database of medication trials.
-Please see the Supplementary Materials for further details.
+We conducted a systematic search for medication studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
+Please see the Supplemental Materials for further details.
 Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
@@
 
-We conducted a series of random effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
-Meta-analyses were implemented using R's Meta package.
+We conducted a series of random-effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
+Meta-analyses were implemented using R's Meta package (version 7.0-0).
 
@@
 If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani's meta-analysis (for medication studies only).
+Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani et al.'s meta-analysis (for medication studies only).
 
@@
 
-#### Random Effects Metaregression
-
-We estimated the pooled standardised mean difference for each arm by using a random effects meta-analysis implemented in R's metafor package.
-The main underlying assumption of random effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
+#### Random-effects Metaregression
+
+We estimated the pooled standardised mean difference for each arm by using a random-effects meta-analysis implemented in R's metafor package (version 4.4-0).
+The main underlying assumption of random-effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
 Therefore, we can estimate a two stage model with:

### 2024-05-17 Manuscript_for_rendering_in_word.qmd
Fixed regression to mean analysis

@@
           country: United Kingdom
+  - name: Glyn Lewis
+    email: glyn.lewis@ucl.ac.uk
+    affiliations:
+        - ref: ucl_1        
   - name: Georgina Krebs
@@
 We examine the validity of these inferences by scrutinising the comparability of psychotherapy and medication RCTs.
-We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the effect sizes of medication controls (i.e.
+We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the within-group effect sizes of medication controls (i.e.
 pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
@@
 Another difference in design is the number of trial sites.
-The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011].
+The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011; @meisterPlaceboResponseRates2020].
 This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
@@
 Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100%-60% and another from a difference of 40%-0%.
+two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% versus 60% and another from a difference of 40% versus 0% (i.e.
+from different points of reference).
 
@@
 #| label: fig-plot-means-all
-#| fig-cap: "Meta-analytic estimates of within-group changes: all studies"
+#| fig-cap: "Meta-analytic estimates of within-group changes for overall sample"
 #| fig-cap-location: top
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#### Let's start from the beginning and regress cohens on the baseline dataframe.
-
-# create a new list with dfs for the sims
-df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# rename the cohens_d value to make space for the new cohen's d
-df_long_for_metan_adj_cohens_d <-
-  df_long_for_metan_adj_cohens_d %>%
-rename(unadjusted_cohens_d = cohens_d,
+# #### Let's start from the beginning and regress cohens on the baseline dataframe.
+# 
+# # create a new list with dfs for the sims
+# df_long_for_metan_adj_cohens_d <- df_long_for_metan
+# # rename the cohens_d value to make space for the new cohen's d
+# df_long_for_metan_adj_cohens_d <-
+#   df_long_for_metan_adj_cohens_d %>%
+# rename(unadjusted_cohens_d = cohens_d,
+# )
+# # estimate the cohen's d from the residuals
+# model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
+# 
+# # there is a great effect of the baseline means, as shown here
+# results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
+# 
+# # extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
+# df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
+# 
+# # apply function to simulate standard errors
+# list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
+#                                    num_repetitions = 1000,
+#                                    seed  = 1974,
+#                                    n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
+#                                    a = 0.45,
+#                                    b = .9,
+#                                    mean = 0.65,
+#                                    sd = 0.2)
+# 
+# 
+# # add the four level variable and re-level
+# for(i in 1: length(list_df_simulated_adj_cohens_d)){
+# 
+#   list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
+#   list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
+#     mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+#                                       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+#     )
+# 
+#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
+# 
+#   # relevel so that medication control becomes the reference category for the regression
+#   #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
+#                                                          "medication_control",
+#                                                          "medication_active",
+#                                                          "psychotherapy_control",
+#                                                          "psychotherapy_active")
+# }
+# 
+# 
+# 
+# 
+# 
+# # Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
+# # specify model
+# model_x <- as.formula(~ four_level_var)
+# 
+# # run metareg function
+# # here you can use the simulated results directly
+# list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
+# 
+# # extract coefficients and model characteristics.
+# condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
+# aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
+# aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
+# 
+# # extract SMDs from the  list
+# list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
+# 
+# # calculate mean SMDs and ses
+# df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
+# 
+# df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
+#
+
+####code to extract baseline-adjusted post means for CDRS and HAMD
+
+de_meaned_baseline_mean <- (list_df_simulated[[1]]$perc_baseline_mean - mean(list_df_simulated[[1]]$perc_baseline_mean, na.rm = TRUE))
+
+lm_for_baseline_means <- lm(list_df_simulated[[1]]$perc_post_mean ~ de_meaned_baseline_mean + list_df_simulated[[1]]$four_level_var, na.action=na.exclude, )
+
+coefs_lm_for_baseline_means  <- broom:: tidy(lm_for_baseline_means)
+
+condition <- coefs_lm_for_baseline_means$term
+
+smds <-c(coefs_lm_for_baseline_means$estimate[1], coefs_lm_for_baseline_means$estimate[-1] + coefs_lm_for_baseline_means$estimate[1])
+
+upper_ci <- smds + coefs_lm_for_baseline_means$std.error*1.96
+
+lower_ci <- smds - coefs_lm_for_baseline_means$std.error*1.96
+
+de_meaned_smd_with_cis <- data.frame (
+
+  condition = levels(list_df_simulated[[1]]$four_level_var),
+
+  smds = smds[-2],
+
+  lower_ci = lower_ci[-2],
+
+  upper_ci = upper_ci[-2]
+
 )
-# estimate the cohen's d from the residuals
-model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
-
-# there is a great effect of the baseline means, as shown here
-results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-
-# extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-
-# apply function to simulate standard errors
-list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
-                                   num_repetitions = 1000,
-                                   seed  = 1974,
-                                   n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
-                                   a = 0.45,
-                                   b = .9,
-                                   mean = 0.65,
-                                   sd = 0.2)
-
-# add the four level variable and re-level
-for(i in 1: length(list_df_simulated_adj_cohens_d)){
-
-  list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-  list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-  list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-                                                         "medication_control",
-                                                         "medication_active",
-                                                         "psychotherapy_control",
-                                                         "psychotherapy_active")
-}
-
-# Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# specify model
-model_x <- as.formula(~ four_level_var)
-
-# run metareg function
-# here you can use the simulated results directly
-list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-
-df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
 
@@
 
-We addressed potential regression to the mean by residualising SMDs by the percentage adjusted baseline scores in one regression model (see @tbl-adj-smds in the Supplement).
-The difference between the medication control and psychotherapy control arms remained similar to the overall analyses.
+We addressed potential regression to the mean by including the baseline score for each depression scale in the linear regression model as per equation 3 in @barnettRegressionMeanWhat2004 (see @tbl-de-meaned in the Supplement).
+The difference between the medication control and psychotherapy control arms remained significantly different.
 
@@
 However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
+Indeed, in Zhou et al.
+[@zhouComparativeEfficacyAcceptability2020] the estimates for psychotherapy controls, TAU and waitlist conditions favoured placebo (though CIs were broad because these were indirectly estimated), as did estimates for psychodynamic and behavioural therapy.
+CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial [@marchFluoxetineCognitiveBehavioralTherapy2004].
 More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
@@
 Importantly, controls were often very poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
-Overall, there is a lack of rigor in matching control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
+Overall, there is very poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
 
@@
 Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
+Moreover, there is a place for comparing interventions to TAU, however issues of disappointment bias should be addressed to avoid inflating treatment estimates.
 
@@
 The first obstacle is the comparability of the populations taking part.
-Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive.
+Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive [@kingImpactParticipantPhysician2005].
 And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
@@
 
-## Systematic review search terms and PRISMA chart
+## Systematic review description and search terms
 
@@
 
-**References for included trials**
+##References for included trials
 
@@
 
-**Hierarchy of depression symptom severity measurement scales**
+## Hierarchy of depression symptom severity measurement scales
 
@@
   set_table_properties(width = 1, layout = "autofit")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-hamd-baseline
+#| tbl-cap: "HAM-D scores at baseline across psychotherapy and medication RCTs"
+#| tbl-cap-location: top
+
+# now for the ham-d
+# For row names
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(results_met_sev_hamd) <- new_column_names
+
+# Rounding
+results_met_sev_hamd <- results_met_sev_hamd %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+results_met_sev_hamd %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+# # All of the below is for the HAMD baseline meta-analysis when we have 4 levels
+# # Prepare to tabulate
+# 
+# table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "baseline_smds") %>%
+#   relocate("n", .before = "baseline_smds") %>%
+#   relocate("lower_cis_smds", .before = "upper_cis_smds")
+# 
+# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+# 
+# # Assign new column names to the data frame
+# colnames(table_2_hamd_metareg_baseline) <- new_column_names
+# 
+# flextable(table_2_hamd_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+# 
+# # Regression results
+# 
+# table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "term") %>%
+#   select(-c("term", "type"))
+# 
+# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+# 
+# # Assign new column names to the data frame
+# colnames(table_1_hamd_metareg_baseline) <- new_column_names
+# 
+# flextable(table_1_hamd_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-cdrs-baseline
+#| tbl-cap: "CDRS scores at baseline across psychotherapy and medication RCTs"
+#| tbl-cap-location: top
+
+# For row names
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(results_met_sev_cdrs) <- new_column_names
+
+# Rounding
+results_met_sev_cdrs <- results_met_sev_cdrs %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
+  slice(1, 3, 2)
+
+results_met_sev_cdrs %>% 
+  as_flextable() %>% 
+  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+# # All of the below is for the CDRS baseline meta-analysis when we have 4 levels
+# # Prepare to tabulate
+# 
+# table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "baseline_smds") %>%
+#   relocate("n", .before = "baseline_smds") %>%
+#   relocate("lower_cis_smds", .before = "upper_cis_smds")
+# 
+# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+# 
+# # Assign new column names to the data frame
+# colnames(table_2_cdrs_metareg_baseline) <- new_column_names
+# 
+# flextable(table_2_cdrs_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
+# 
+# # Regression results
+# 
+# table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
+#   mutate(across(where(is.numeric), ~round(., 2))) %>%
+#   mutate(condition = case_when(
+#     condition == "medication_control" ~ "Medication Control",
+#     condition == "medication_active" ~ "Medication Active",
+#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
+#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
+#     TRUE ~ as.character(condition))) %>%
+#   relocate("condition", .before = "term") %>%
+#   select(-c("term", "type"))
+# 
+# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+# 
+# # Assign new column names to the data frame
+# colnames(table_1_cdrs_metareg_baseline) <- new_column_names
+# 
+# flextable(table_1_cdrs_metareg_baseline) %>%
+#   set_table_properties(width = 1) %>%
+#   autofit() %>%
+#   font(fontname = "Calibri", part = "all") %>%
+#   bold(part = "header") %>%   # Bold the relevant header rows
+#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
+#   border_remove() %>% # this is to remove borders around the caption that look strange
+#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+#   vline(j = 1, part = "body", border = small_border) %>%
+#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+#   hline(part = "header", border = big_border) %>%
+#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
+#   align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 1, align = "left", part = "all") %>%
+#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
+#   line_spacing(space = .7, part = "all")
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-hamd-baseline
-#| tbl-cap: "HAM-D Baseline Scores across Psychotherapy and Medication RCTs"
-#| tbl-cap-location: top
-
-# now for the ham-d
-# For row names
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_hamd) <- new_column_names
-
-# Rounding
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-results_met_sev_hamd %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the HAMD baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
+# #| label: tbl-adj-smds
+# #| tbl-cap: "SMDs adjusted by baseline scores"
+# #| tbl-cap-location: top
+# 
+# table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
 #   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 #     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
+#     TRUE ~ as.character(condition))) 
+# 
+# new_column_names <- c("Condition", "Coefficient", "SE", "Lower CI", "Upper CI")
 # 
 # # Assign new column names to the data frame
-# colnames(table_2_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_hamd_metareg_baseline) %>%
+# colnames(table_mean_coefs_from_sim_adjusted_cohens_d) <- new_column_names
+# 
+# flextable(table_mean_coefs_from_sim_adjusted_cohens_d) %>%
 #   set_table_properties(width = 1) %>%
@@
 #   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 2:ncol(table_mean_coefs_from_sim_adjusted_cohens_d), align = "center", part = "all") %>% 
 #   align(j = 1, align = "left", part = "all") %>% 
@@
 # 
-# # Regression results
-# 
-# table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
+# aggregate_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d %>%
 #   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 #     TRUE ~ as.character(condition))) %>% 
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
+#   relocate("condition", .before = "coefficients") 
+# 
+# new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
 # 
 # # Assign new column names to the data frame
-# colnames(table_1_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_hamd_metareg_baseline) %>%
+# colnames(aggregate_results_overall_adjusted_cohens_d) <- new_column_names
+# 
+# table_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d[, 1:6]
+# 
+# flextable(table_results_overall_adjusted_cohens_d) %>%
 #   set_table_properties(width = 1) %>%
 #   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
+#   add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "T2"],
+#                       "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "I2"], 
+#                       "; ", as_i("K"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "k"],
+#                       "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "R2"], "."), colwidths = 6) %>%
+#   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
+#   # add_header_row(values = "Table 4", colwidths = 6) %>% 
 #   bold(part = "header") %>%   # Bold the relevant header rows
 #   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+#   # italic(i = 2, italic = TRUE, part = "header") %>% 
 #   border_remove() %>% # this is to remove borders around the caption that look strange
@@
 #   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
+#   align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
 #   align(j = 1, align = "left", part = "all") %>% 
+#   font(fontname = "Calibri", part = "all") %>% 
 #   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-cdrs-baseline
-#| tbl-cap: "CDRS Baseline Scores across Psychotherapy and Medication RCTs"
+#| label: tbl-de-meaned
+#| tbl-cap: "Results from baseline-adjusted model"
 #| tbl-cap-location: top
 
-# For row names
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_cdrs) <- new_column_names
-
-# Rounding
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  slice(1, 3, 2)
-
-results_met_sev_cdrs %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the CDRS baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_2_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-# 
-# # Regression results
-# 
-# table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-# 
-# # Assign new column names to the data frame
-# colnames(table_1_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-adj-smds
-#| tbl-cap: "SMDs adjusted by baseline scores"
-#| tbl-cap-location: top
-
-table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
+de_meaned_smd_with_cis <- de_meaned_smd_with_cis %>%
   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 
-new_column_names <- c("Condition", "Coefficient", "SE", "Lower CI", "Upper CI")
+new_column_names <- c("Condition", "SMDs", "Lower CI", "Upper CI")
 
 # Assign new column names to the data frame
-colnames(table_mean_coefs_from_sim_adjusted_cohens_d) <- new_column_names
-
-flextable(table_mean_coefs_from_sim_adjusted_cohens_d) %>%
+colnames(de_meaned_smd_with_cis) <- new_column_names
+
+flextable(de_meaned_smd_with_cis) %>%
   set_table_properties(width = 1) %>%
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_mean_coefs_from_sim_adjusted_cohens_d), align = "center", part = "all") %>% 
+  align(j = 2:ncol(de_meaned_smd_with_cis), align = "center", part = "all") %>%
   align(j = 1, align = "left", part = "all") %>%
@@
 
-aggregate_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "coefficients")
-
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
+table_coefs_lm_for_baseline_means <- coefs_lm_for_baseline_means[c(1, 3:5),]
+
+table_coefs_lm_for_baseline_means <- table_coefs_lm_for_baseline_means %>%
+  mutate(across(where(is.numeric) & !matches("p.value"), ~ round(., 2))) %>%
+  mutate(`p.value` = ifelse(`p.value` < 0.001, "< 0.001", sprintf("%.3f", `p.value`)))
+
+new_column_names <- c("Condition", "Estimate", "SE", "t value", "p-value")
 
 # Assign new column names to the data frame
-colnames(aggregate_results_overall_adjusted_cohens_d) <- new_column_names
-
-table_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d[, 1:6]
-
-flextable(table_results_overall_adjusted_cohens_d) %>%
+colnames(table_coefs_lm_for_baseline_means) <- new_column_names
+
+table_coefs_lm_for_baseline_means$Condition <- c("Medication Control", "Medication Active", "Psychotherapy Control", "Psychotherapy Active")
+
+flextable(table_coefs_lm_for_baseline_means) %>%
   set_table_properties(width = 1) %>%
   autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "T2"],
-                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "I2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "k"],
-                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "R2"], "."), colwidths = 6) %>%
-  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-  # add_header_row(values = "Table 4", colwidths = 6) %>% 
   bold(part = "header") %>%   # Bold the relevant header rows
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
+  align(j = 2:ncol(table_coefs_lm_for_baseline_means), align = "center", part = "all") %>%
   align(j = 1, align = "left", part = "all") %>%
@@
   line_spacing(space = .7, part = "all")
-
 ```

### 2024-07-26 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
qmd with code for multilevel metaregression
New functions for metaregression that take into account studies with multiple arms.

--- 2024-05-17 Manuscript_for_rendering_in_word.qmd
@@
 ```
+
 ```{r global_options, include=FALSE}
@@
 # Abstract
+
 **Question:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
@@
 # Key messages
+
 Psychotherapy is recommended before medication for most cases of depression in children and adolescents, a recommendation that is based on indirect comparisons of outcomes from randomised controlled trials (RCTs) within each treatment modality.
@@
 Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the “cutting edge” treatment, whilst those in the control are dissatisfied for having missed out (i.e.
-“disappointment bias” [@reltonEthicsTrialsCohorts2017].
+This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the "cutting edge" treatment, whilst those in the control are dissatisfied for having missed out (i.e.
+"disappointment bias" [@reltonEthicsTrialsCohorts2017].
 By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022], suggesting that expectancy effects are well-matched across conditions.
@@
 <!-- $$ -->
+
 <!-- \text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}} -->
+
 <!-- $$ -->
@@
 <!-- $$ -->
+
 <!-- \text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}} -->
+
 <!-- $$ -->
@@
 <!-- $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2) -->
+
 <!-- $$ -->
@@
 <!-- $$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2) -->
+
 <!-- $$ -->
@@
 <!-- $$ \begin{aligned} -->
+
 <!--     Υ_i &= -->
+
 <!--     \begin{cases} -->
+
 <!--         0 & MedControl:  b_0 + u_i + \epsilon_i\\ -->
+
 <!--         1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\ -->
+
 <!--         2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\ -->
+
 <!--         3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\ -->
+
 <!--     \end{cases} -->
+
 <!-- \end{aligned}$$ -->
@@
 <!-- $$ -->
+
 <!-- z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} -->
+
 <!-- $$ -->
@@
 ```
+
 We conducted a series of sensitivity analyses where we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
@@
 
-###############2. Simulation function for metaregression
-run_metaregression <- function(list_of_datasets, model_formula) {
+###############2. Simulation function for multilevel metaregression
+
+  run_multi_metaregression <- function(list_of_datasets, model_formula) {
     list_model_meta_reg <- list()
@@
     for (i in seq_along(list_of_datasets)) {
-    list_model_meta_reg[[i]] <- metafor::rma(yi = cohens_d,
-                                             sei = simulated_se,
+      # Check if required columns are present
+      if(!all(c("cohens_d", "simulated_se", "new_study_id", "arm_id") %in% names(list_of_datasets[[i]]))) {
+        stop("Dataset is missing one or more required columns: 'cohens_d', 'simulated_se', 'new_study_id', 'arm_id'")
+      }
+
+      # Fit the meta-regression model
+      list_model_meta_reg[[i]] <- metafor::rma.mv(yi = cohens_d,
+                                                  V = simulated_se^2,
+                                                  random = ~ 1 | new_study_id/arm_id,
+                                                  # this is where 
+                                                  # we specify the random
+                                                  # effect structure
                                                   data = list_of_datasets[[i]],
@@
                                                   mods = model_formula,
+                                                  # here we specify the 
+                                                  # fixed effects as before
                                                   test = "knha")
@@
 
-#########2. Function to count studies with missingness etc.
+#########3. Function to count studies with missingness etc.
 
@@
 
-##########3. Function to extract mean coefficients and to extract model characteristics
+##########4. Function to extract mean coefficients and to extract model characteristics
 
 aggregate_model_results <- function(list_model_1_meta_reg, condition) {
-  df_coefs <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
-  df_se <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
-  df_z_value <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
-  df_lower_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
-  df_upper_ci <- matrix(NA, nrow = length(list_model_1_meta_reg), ncol = length(condition))
-  tau_sq <- rep(0, length(list_model_1_meta_reg))
-  i_sq <- rep(0, length(list_model_1_meta_reg))
-  k <- rep(0, length(list_model_1_meta_reg))
-  r_sq <- rep(0, length(list_model_1_meta_reg))
-
-  for (i in 1:length(list_model_1_meta_reg)) {
-    for (j in 1:length(condition)) {
-      df_coefs[i, j] <- list_model_1_meta_reg[[i]]$beta[[j]]
-      df_se[i, j] <- list_model_1_meta_reg[[i]]$se[[j]]
-      df_z_value[i, j] <- list_model_1_meta_reg[[i]]$zval[[j]]
-      df_lower_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.lb[[j]]
-      df_upper_ci[i, j] <- list_model_1_meta_reg[[i]]$ci.ub[[j]]
-      tau_sq[i] <- list_model_1_meta_reg[[i]]$tau2
-      i_sq[i] <- list_model_1_meta_reg[[i]]$I2
-      k[i] <- list_model_1_meta_reg[[i]]$k
-      r_sq[i] <- list_model_1_meta_reg[[i]]$R2
+  n_models <- length(list_model_1_meta_reg)
+  n_conditions <- length(condition)
+
+  df_coefs <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_se <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_z_value <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_lower_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  tau_sq <- rep(NA, n_models)
+  qe <- rep(NA, n_models)
+  k <- rep(NA, n_models)
+
+  for (i in seq_len(n_models)) {
+    model <- list_model_1_meta_reg[[i]]
+    tau_sq[i] <- model$tau2
+    qe[i] <- model$QE
+    k[i] <- model$k
+    coefs <- model$beta
+    ses <- model$se
+    zvals <- model$zval
+    lower_ci <- model$ci.lb
+    upper_ci <- model$ci.ub
+
+    for (j in seq_len(n_conditions)) {
+      if (!is.null(coefs[j])) {
+        df_coefs[i, j] <- coefs[j]
+        df_se[i, j] <- ses[j]
+        df_z_value[i, j] <- zvals[j]
+        df_lower_ci[i, j] <- lower_ci[j]
+        df_upper_ci[i, j] <- upper_ci[j]
       }
     }
+  }
 
   df_coefficients_model <- data.frame(
-    coefficients = colMeans(df_coefs),
-    se = colMeans(df_se),
-    z_value = colMeans(df_z_value),
-    lower_ci = colMeans(df_lower_ci),
-    upper_ci = colMeans(df_upper_ci),
-    tau_sq = mean(tau_sq),
-    i_sq = mean(i_sq),
-    k = mean(k),
-    r_sq = mean(r_sq)
+    coefficients = colMeans(df_coefs, na.rm = TRUE),
+    se = colMeans(df_se, na.rm = TRUE),
+    z_value = colMeans(df_z_value, na.rm = TRUE),
+    lower_ci = colMeans(df_lower_ci, na.rm = TRUE),
+    upper_ci = colMeans(df_upper_ci, na.rm = TRUE),
+    tau_sq = mean(tau_sq, na.rm = TRUE),
+    qe = mean(qe, na.rm = TRUE),
+    k = mean(k, na.rm = TRUE)
   )
@@
 
+# Create unique IDs by arm for multilevel metaregression
+
+df_long_for_metan <- df_long_for_metan %>%
+  group_by(new_study_id) %>%
+  mutate(arm_id = paste0(new_study_id, "_", row_number())) %>%
+  ungroup()
+
 #dim(df_long_for_metan ) #check dimension
@@
 n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
-df_count_studies <- count_studies(df_long_for_metan ) # CHARLOTTE please check
+df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
 # CB checked both, both correct.
@@
 # here you can use the simulated results directly
-list_model_1_meta_reg <- run_metaregression(list_df_simulated, model_1)
+list_model_1_meta_reg <- run_multi_metaregression(list_df_simulated, model_1)
 
@@
 model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_metaregression(list_cbt_fluox_esc_study , model_1)
+list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
 
@@
 # apply the metareg function to the list of no wl
-list_model_1_no_wl <- run_metaregression(list_no_wl , model_1)
+list_model_1_no_wl <- run_multi_metaregression(list_no_wl , model_1)
 
@@
 model_1 <- as.formula(~ four_level_var)
-list_model_1_clin_study <- run_metaregression(list_clin_study , model_1)
+list_model_1_clin_study <- run_multi_metaregression(list_clin_study , model_1)
 
@@
 model_1 <- as.formula(~ four_level_var)
-list_model_1_cdrs_study <- run_metaregression(list_cdrs_study , model_1)
+list_model_1_cdrs_study <- run_multi_metaregression(list_cdrs_study , model_1)
 
@@
 model_1 <- as.formula(~ four_level_var)
-list_model_1_hamd_study <- run_metaregression(list_hamd_study , model_1)
+list_model_1_hamd_study <- run_multi_metaregression(list_hamd_study , model_1)
 
@@
 
+```{r, warning=FALSE, message = FALSE, echo = FALSE}
+#| label: smd-diff-control
+#| fig-cap: "Pre-Post Standardised Mean Differences (SMD) of Control Arms"
+#| fig-cap-location: top
+
+list_df_simulated[[1]] %>% 
+  filter(arm_effect_size == "cohens_d_control") %>% 
+  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
+  geom_jitter(height = 0.2, alpha = 0.7) +
+  geom_point(alpha = 0.7) +
+  labs(
+    x = "SMD",
+    y = "",
+    color = "Type of Study",
+    size = "Baseline n"
+  ) +
+  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_blank(),
+    axis.ticks.y = element_blank(),
+    axis.title.y = element_blank()
+  )
+```
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 # subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
-plot_means_all <- plot_means_function(df_mean_coefs_from_sim)
+plot_means_multi_all <- plot_means_function(df_mean_coefs_from_sim)
 print(plot_means_all)
+
+ #png("plot_means_multi_all.png")
+ #plot_means_multi_all
+ #dev.off()
 
@@
 Here, medication control is the reference category to which all others are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p<0.0001).
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p\<0.0001).
 
@@
 
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")
 
@@
 
-####code to extract baseline-adjusted post means for CDRS and HAMD
+####code to extract baseline-adjusted post means
 
@@
 
-Explicit search strategy: title/abstract = (depress* or dysthymi\* or "mood disorder\*" or "affective disorder*") AND (adolesc\* or child\* or boy\* or girl\* or juvenil\* or minors or paediatri\* or pediatri\* or pubescen\* or school\* or student\* or teen\* or young or youth\*) AND (selective serotonin reuptake inhibitor or SSRI or citalopram or fluoxetine or paroxetine or sertraline or escitalopram or fluvoxamine or serotonin norepinephrine reuptake inhibitor\* or SNRI or venlafaxine or duloxetine or milnacipran or reboxetine or bupropion or noradrenergic and specific serotonergic antidepressants or NaSSA or mirtazapine or TCA or tricyclic or amersergide or amineptine or amitriptyline or amoxapine or butriptyline or chlorpoxiten or clomipramine or clorimipramine or demexiptiline or desipramine or dibenzipin or dothiepin or doxepin or imipramine or lofepramine or melitracen or metapramine or nortriptyline or noxiptiline or opipramol or protriptyline or quinupramine or tianeptine or trimipramine) AND (placebo)
+Explicit search strategy: title/abstract = (depress\* or dysthymi\* or "mood disorder\*" or "affective disorder\*") AND (adolesc\* or child\* or boy\* or girl\* or juvenil\* or minors or paediatri\* or pediatri\* or pubescen\* or school\* or student\* or teen\* or young or youth\*) AND (selective serotonin reuptake inhibitor or SSRI or citalopram or fluoxetine or paroxetine or sertraline or escitalopram or fluvoxamine or serotonin norepinephrine reuptake inhibitor\* or SNRI or venlafaxine or duloxetine or milnacipran or reboxetine or bupropion or noradrenergic and specific serotonergic antidepressants or NaSSA or mirtazapine or TCA or tricyclic or amersergide or amineptine or amitriptyline or amoxapine or butriptyline or chlorpoxiten or clomipramine or clorimipramine or demexiptiline or desipramine or dibenzipin or dothiepin or doxepin or imipramine or lofepramine or melitracen or metapramine or nortriptyline or noxiptiline or opipramol or protriptyline or quinupramine or tianeptine or trimipramine) AND (placebo)
 
@@
 
-1. Children’s Depression Rating Scale (CDRS)
-1. Hamilton Depression Rating Scale (HAMD)
-1. Montgomery Asberg Depression Rating Scale (MADRS)
-1. Beck Depression Inventory (BDI)
-1. Children’s Depression Inventory (CDI)
-1. Schedule for Affective Disorders and Schizophrenia for School-Aged Children (K-SADS)
-1. Mood and Feeling Questionnaire (MFQ)
-1. Reynolds Adolescent Depression Scale (RADS)
-1. Bellevue Index of Depression (BID)
-1. Child Depression Scale (CDS)
-1. Centre for Epidemiological Studies Depression Scale (CES-D)
-1. Child Assessment Schedule (CAS)
-1. Child Behaviour Checklist-Depression (CBCL-D)
+1.  Children's Depression Rating Scale (CDRS)
+2.  Hamilton Depression Rating Scale (HAMD)
+3.  Montgomery Asberg Depression Rating Scale (MADRS)
+4.  Beck Depression Inventory (BDI)
+5.  Children's Depression Inventory (CDI)
+6.  Schedule for Affective Disorders and Schizophrenia for School-Aged Children (K-SADS)
+7.  Mood and Feeling Questionnaire (MFQ)
+8.  Reynolds Adolescent Depression Scale (RADS)
+9.  Bellevue Index of Depression (BID)
+10. Child Depression Scale (CDS)
+11. Centre for Epidemiological Studies Depression Scale (CES-D)
+12. Child Assessment Schedule (CAS)
+13. Child Behaviour Checklist-Depression (CBCL-D)
 
@@
 
-# png("plot_means_no_wl.png")
-# plot_means_no_wl
-# dev.off()
+ #png("plot_means_multi_no_wl.png")
+ #plot_means_no_wl
+ #dev.off()
 
@@
 
-# png("plot_means_clin.png")
-# plot_means_clin
-# dev.off()
+png("plot_means_multi_clin.png")
+plot_means_clin
+dev.off()
 
 ```
+
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
@@
 
-# png("plot_means_cdrs.png")
+# png("plot_means_multi_cdrs.png")
 # plot_means_cdrs
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-stab-sims
-#| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
-#| fig-cap-location: top
-
-# examine the stability of the simulations
-
-z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_meta_reg)){
-z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
-
-}
-
-stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-
-stab_sims <- stability_sims %>%
-  ggplot(aes(x = n_sims, y = z_value)) +
-  geom_point() +
-  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
-           hjust = -0.1, vjust = 0) +
-  theme_minimal() +
-  labs(
-    x = "Number of Simulations",
-    y = "z-value",
-    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-    subtitle = "Results from 1000 simulations with within-group standard errors"
-  )
-
-print(stab_sims)
+# #| label: fig-stab-sims
+# #| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
+# #| fig-cap-location: top
+# 
+# # examine the stability of the simulations
+# 
+# z_psy_con_vs_med_con <- 0
+# for(i in 1: length(list_model_1_meta_reg)){
+# z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
+# 
+# }
+# 
+# stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+# 
+# stab_sims <- stability_sims %>%
+#   ggplot(aes(x = n_sims, y = z_value)) +
+#   geom_point() +
+#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+#                arrow = arrow(length = unit(0.3, "cm")),
+#                color = "black") +
+#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+#   geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
+#                arrow = arrow(length = unit(0.3, "cm")),
+#                color = "black") +
+#   annotate("text", x = 300, y = 7.5, label = "simulated z-values",
+#            hjust = -0.1, vjust = 0) +
+#   theme_minimal() +
+#   labs(
+#     x = "Number of Simulations",
+#     y = "z-value",
+#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
+#     subtitle = "Results from 1000 simulations with within-group standard errors"
+#   )
+# 
+# print(stab_sims)
 

### 2024-08-06 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Corrected typos

@@
 
-**Question:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
+**Objectives:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
 In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
-**Study selection and analysis:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+**Methods:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
 Using meta-analyses, we compared a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
 Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
-**Findings:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
+**Results:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
 There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.70)) vs psychotherapy controls (SMD=-0.5 (95% CI: -0.75 to -0.25)).
@@
 
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023].
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023].
 
@@
 pleasant human contact), aspects such as therapist contact time should be matched.
-Many (24%) psychotherapy RCTs use waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
+Many (24%) psychotherapy RCTs used waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
 TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
@@
 where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
 If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.

### 2024-08-08 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
added sensitivity analyses and sex meta-analysis with all studies in supplement

@@
 # For referencing
-bib_data <- ReadBib("emotion_concepts_paper.bib")
+bib_data <- ReadBib("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/emotion_concepts_paper.bib")
 
@@
 
-df_appl_v_orange <-readxl:: read_excel("df_appl_v_orange.xlsx")
+df_appl_v_orange <-readxl::read_excel("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/df_appl_v_orange.xlsx")
 
@@
 
-df_scale_ranges <- read.csv("scale_ranges.csv")
+df_scale_ranges <- read.csv("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/scale_ranges.csv")
 df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
@@
 # C) the no WL sample
-# E) the CDRS only sample (**Argyris** do we still want this?)
-# F) Clinical Levels Depression
+# D) clinical levels of depression
+# E) the CDRS only sample
+# E) HAMD sensitivity analysis
+# G) Studies with post SD
+# H) Studies with variance <.02
 
@@
 
-# D Clinical Levels Depression Sensitivity Analysis ---------------------------------------
+# D. Clinical Levels Depression Sensitivity Analysis---------------------------------------
 
@@
 
-# E. HAMD Sensitivity Analysis ---------------------------------------
+# F. HAMD Sensitivity Analysis ---------------------------------------
 
@@
 
+# G. Post SD Sensitivity Analysis ---------------------------------------
+
+##--------- Data preparation
+
+#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
+
+#create subset of first_row
+
+df_first_row <- read.csv("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/df_first_row.csv")
+
+#create new_study_ids to match master dataset
+df_first_row  <- df_first_row  %>%
+  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
+                                  .default = study ))
+
+df_first_row_reduced <- df_first_row %>%
+  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
+  select(new_study_id, post_sd_active, post_sd_control)
+
+#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
+
+df_first_row_reduced <- df_first_row_reduced %>%
+  group_by(new_study_id) %>%
+  slice_head(n = 1) %>%
+  ungroup()
+
+#create a column in master df that shows 1 if any missing post sds in first_row
+
+df_long_for_metan_with_missing <- df_long_for_metan %>%
+  left_join(df_first_row_reduced, by = "new_study_id") %>%
+  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
+  select(-post_sd_active, -post_sd_control) %>%
+  arrange(arm_effect_size, new_study_id)
+
+#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
+
+df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
+  filter(missing_post_sd == 0)
+
+n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
+n_distinct(df_long_for_metan$new_study_id) #88 studies total
+nrow(df_long_for_metan_without_missing) #140 arms
+nrow(df_long_for_metan) #203 arms
+
+##------------ Estimates
+
+#take study ids where study does not have missing post SD
+sd_study_ids <-
+  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_sd_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                 %in% sd_study_ids,]
+}
+
+# count the number of studies
+study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
+coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
+
+# add the ns to the dataframe
+coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>% 
+                                            ungroup() %>% 
+                                            select(condition, n),  
+                                          by = "condition")
+
+#H. Studies with variances <.02-----------------------------
+
+##-----------Data preparation
+
+#create column with variance in master df
+df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
+
+#take study ids where variance =2 or less
+var2_study_ids <-
+  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
+length(var2_study_ids)
+
+##------------Estimates
+
+# use those ids to subset all dataframes in the list
+list_var2_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                               %in% var2_study_ids,]
+}
+
+# count the number of studies
+study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
+coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
+
+# add the ns to the dataframe
+coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>% 
+                                          ungroup() %>% 
+                                          select(condition, n),  
+                                        by = "condition")
+
 ```
@@
 
-Data for included are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
+Data for included studies are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
 Please see @fig-prisma for a summary of the sources of included RCTs.
@@
 
-First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is an urgent need to revisit guidelines and public information in light of the limitations.
+First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is a need to revisit guidelines and public information in light of the limitations.
 

### 2024-08-12 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
added sensitivity analysis and sex meta-analysis with all studies

@@
 library(effsize)
+library(here)
+
+#setting paths using here package
+here::here()
 
 # For referencing
-bib_data <- ReadBib("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/emotion_concepts_paper.bib")
+bib_data <- ReadBib(here("emotion_concepts_paper.bib"))
 
@@
 
-df_appl_v_orange <-readxl::read_excel("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/df_appl_v_orange.xlsx")
+df_appl_v_orange <-readxl::read_excel(here("df_appl_v_orange.xlsx"))
 
@@
 
-df_scale_ranges <- read.csv("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/scale_ranges.csv")
+df_scale_ranges <- read.csv(here("scale_ranges.csv"))
 df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
@@
 df_long_for_metan <- df_long_for_metan %>% 
-  mutate(percent_women_std_error = sqrt(product_perc_women/ n_overall ))
+  mutate(percent_women_std_error = sqrt(product_perc_women/ n_overall))
 
@@
 
-df_first_row <- read.csv("C:/Users/Raphaelle/Documents/AIM Lab/apples_and_oranges/main_git/apples_oranges/df_first_row.csv")
+df_first_row <- read.csv(here("df_first_row.csv"))
 
@@
 #| fig-cap-location: top
-knitr::include_graphics("PRISMA.png")
+knitr::include_graphics(here("PRISMA.png"))
 ```
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
 # Start by looking at demographics at baseline
@@
 
-# Now look at baseline severity for overall psy vs med
+#A. Baseline severity meta-analysis--------------
+
+# Overall psy vs med
+
 # Need to calculate the variables first
-
 df_for_baseline_severity <- df_long_for_metan %>% 
@@
 
-# clinical sample
+# Clinical sample
 
@@
 
+#B. Sex meta-analysis
+
 # Now start looking at perc_women variable
@@
 df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(percent_women != 100) # filter out studies with only women %>%
+  filter(percent_women != 100) # filter out studies with only women
 
@@
 
-# Now start looking at age variable
+# C. Age meta-analysis--------------------
 
@@
 
-For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016).
+For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016; see @tbl-all-studies-percfemale-results in Supplement for results with full sample).
 As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
@@
 
-We conducted a series of sensitivity analyses (all figures in the Supplemental Materials).
+We conducted a series of sensitivity analyses (all figures in the Supplement).
 Excluding waitlist control studies (see @fig-plot-means-no-wl) and sub-clinical studies (see @fig-plot-means-clin) yielded a pattern of results very similar to the overall analyses.
@@
 
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+#Repeating meta-analyses on sample characteristics including studies with females only
+
+#An issue that arise when trying to include studies with 100% female is that their SE ends up being 0, which is treated as NA in the metagen function.
+One way to circumvent this is to apply a continuity correction by adding a constant (e.g 0.5) to percent female.
+These studies will now be treated as having 99.5% females.
+
+#overall sample------------
+
+df_for_sex_metan_no_excl <- df_baseline_demographics %>% 
+  filter(!is.na(percent_women)) %>% #use full dataset to include all studies
+  filter(new_study_id != "March, 2004")# removing TADS because it does not technically belong to either the psy or med groups
+
+#using the formula for se (p*(1-p)/n) we add a constant for studies w 100% female
+
+correction_constant <- 0.5
+
+df_for_sex_metan_no_excl <- df_for_sex_metan_no_excl %>% 
+  mutate(constant_percent_women = ifelse(percent_women==100,percent_women-correction_constant,percent_women)) %>%
+  mutate(product_perc_women=(constant_percent_women/100)*(1-(constant_percent_women/100))) %>%
+  mutate(percent_women_std_error = sqrt(product_perc_women / n_overall))
+
+met_perc_women_no_excl  <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_sex_metan_no_excl,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across studies")
+
+    #Issue: standard error is 0 for 100% female studies so the model     treats them as NA! fix if we want to include all studies in these analyses
+
+met_perc_women_no_excl <- update(met_perc_women_no_excl,
+                              subgroup = df_for_sex_metan_no_excl$psy_or_med, subgroup.name = "treatment modality",
+                              tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+
+results_met_perc_women_no_excl <- extract_stats(met_perc_women_no_excl)
+
+# Clinical only-------------
+
+df_for_sex_metan_no_excl_clin <- df_for_sex_metan_no_excl %>%
+  filter(new_study_id %in% clin_study_ids)
+
+met_perc_women_no_excl_clin <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_sex_metan_no_excl_clin,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across clinical studies")
+
+met_perc_women_no_excl_clin <- update(met_perc_women_no_excl_clin,
+                           subgroup = df_for_sex_metan_no_excl_clin$psy_or_med, subgroup.name = "treatment modality",
+                           tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+results_met_perc_women_no_excl_clin <- extract_stats(met_perc_women_no_excl_clin)
+
+# Excluding wl--------------
+
+df_for_sex_metan_no_excl_no_wl <- df_for_sex_metan_no_excl %>%
+  filter(new_study_id %in% no_wl_ids)
+
+met_perc_women_no_excl_no_wl <- metagen(TE = percent_women,
+                           seTE = percent_women_std_error,
+                           studlab = new_study_id,
+                           data = df_for_sex_metan_no_excl_no_wl,
+                           sm = "",
+                           fixed = FALSE,
+                           random = TRUE,
+                           method.tau = "REML",
+                           hakn = TRUE,
+                           title = "percentage women across studies with controls that are not wl",
+                           subgroup = psy_or_med,
+                           tau.common = FALSE)
+
+# Apply the function to the meta-analysis result
+results_met_perc_women_no_excl_no_wl <- extract_stats(met_perc_women_no_excl_no_wl)
+
+## Combine results for table
+
+df_baseline_results_no_excl <- rbind(results_met_perc_women_no_excl, results_met_perc_women_no_excl_clin, results_met_perc_women_no_excl_no_wl)
+
+# For row names
+df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
+  mutate(subgroup = case_when(
+    row_number() %in% 1 ~ "Overall",
+    row_number() %in% 4 ~ "Excluding subclinical",
+    row_number() %in% 7 ~ "Excluding waitlist",
+    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
+  ))
+
+# Define new column names
+new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
+
+# Assign new column names to the data frame
+colnames(df_baseline_results_no_excl) <- new_column_names
+
+# Rounding
+df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
+  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
+  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
+  mutate_all(~if_else(is.na(.), "", as.character(.)))
+
+big_border = fp_border(color="black", width = 1)
+small_border = fp_border(color="lightgray", width = 1)
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+#| label: tbl-all-studies-percfemale-results
+#| tbl-cap: "Percentage female at baseline across medication and psychotherapy studies: Results for sample including all female studies"
+#| tbl-cap-location: top
+
+df_baseline_results_no_excl %>% 
+  as_flextable() %>% 
+  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
+  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
+  bg(i = 1, bg  = "#F2F2F2", part = "body") %>% # identify category sections
+  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% # indent some rows
+  align(j = 2:ncol(df_baseline_results_no_excl), align = "center", part = "all") %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  line_spacing(space = .7, part = "all") %>%
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  autofit()
+
+```
+
 ## Metaregression sensitivity analyses
@@
 print(plot_means_cdrs)
+
+# png("plot_means_multi_cdrs.png")
+# plot_means_cdrs
+# dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-hamd
+#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
+#| fig-cap-location: top
+
+coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study)
+print(plot_means_hamd)
 

### 2024-08-12 multilevel_metaregression/manuscript_with_multilevel_metan.qmd

@@
 
-#### Random-effects Metaregression
-
-We estimated the pooled SMD for each arm by using a random-effects meta-analysis implemented in R's metafor package.
-
-<!-- The main underlying assumption of random-effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
-Therefore, we can estimate a two stage model with: -->
-
-<!-- $$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2) -->
-
-<!-- $$ -->
-
-<!-- $$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2) -->
-
-<!-- $$ -->
-
-<!-- where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
-Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
--->
-
-<!-- This then gives rise to: -->
-
-<!-- $$Y_i = x_i\beta_i + u_i + \epsilon_i$$ -->
-
-<!-- where, -->
-
-<!-- $$u_i \sim N(0, \tau^2) $$ -->
-
-<!-- describes the deviation of each study from the mean of the distribution, and, -->
-
-<!-- $$\epsilon_i \sim N(0, \sigma^2)$$ -->
-
-<!-- describes the sampling error. -->
-
-<!-- We can then specify the following model to obtain the means of each arm of the trials as follows: -->
-
-<!-- $$ \begin{aligned} -->
-
-<!--     Υ_i &= -->
-
-<!--     \begin{cases} -->
-
-<!--         0 & MedControl:  b_0 + u_i + \epsilon_i\\ -->
-
-<!--         1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\ -->
-
-<!--         2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\ -->
-
-<!--         3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\ -->
-
-<!--     \end{cases} -->
-
-<!-- \end{aligned}$$ -->
-
-<!-- where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
-for level 3, $b_{3_{i}}$ the psychotherapy controls.
-The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
-Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on the contrasts is done as follows: -->
-
-<!-- $$ -->
-
-<!-- z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} -->
-
-<!-- $$ -->
-
-<!-- We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014]. -->
+#### Multilevel model metaregression
+
+We estimated pooled SMDs for each arm by using multilevel models implemented in R's metafor package.
+
+<!--  Unlike the traditional random effects meta-analysis, which assumes that each study's true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
+This allows us to model variability at both the study level and the study arm level.
+The multilevel model assumes that each study's true effect size $\theta_{ij}$ (where $i$ indexes the study and $j$ indexes the study arm) is influenced by both the variability between studies and the variability between arms within each study.
+The model can be expressed as:
+
+ $$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$
+
+where,
+
+$$θij​∼N(xij​β,τi2​)$$
+
+{#eq-8}
+
+where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
+The true effect size $\theta_{ij}$ is modeled as a study-specific effect with an additional term representing the variability between arms within the study.
+
+This gives rise to the following model:
+
+$$ Yij=xijβ+ui+vij+ϵij $$
+
+{#eq-9}
+
+where,
+
+$$ ui​∼N(0,τ2) $$
+
+{#eq-10} describes the deviation of each study from the overall mean effect size, and
+
+$$vij∼N(0,τi2)$$ {#eq11}
+
+describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally,
+
+$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$
+
+{#eq-12}
+
+represents the sampling error.
+
+In this framework, we can model the means for each arm of the trials as follows:
+
+$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$
+
+{#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
+The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
+The confidence intervals for the means are constructed using the standard errors of the means, which account for the hierarchical structure of the data.
+Each coefficient represents the contrast between the reference category and each level.
+For example, $b_{3_{ij}}$ represents the contrast between psychotherapy and medication control arms.
+Inference on these contrasts is conducted using the following test statistic:
+
+$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$
+
+{#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms. -->
 
@@
 
-#### Random-effects Metaregression
-
-We estimated the pooled standardised mean difference for each arm by using a random-effects meta-analysis implemented in R's metafor package (version 4.4-0).
-The main underlying assumption of random-effects meta-analysis is that each study's true effect size $\theta_{k}$ is affected not only by sampling error $\epsilon_{k}$, but also by $\zeta$ which represents heterogeneity between studies, allowing each study's estimate to vary along a distribution of effects, and the distribution of true effect sizes termed $\tau^2$.
-Therefore, we can estimate a two stage model with:
-
-$$Y_i \sim \mathcal{N}(\theta_i, \sigma_i^2)
-$$
-
-$$\theta_i \sim \mathcal{N}(x_i\beta, \tau_i^2)
-$$
-
-where $Y_i$ is the estimated effect size for study i, has a normal distribution with $\theta_i$ as its true mean effect and sampling error $\sigma^2$.
-Whereas $\theta_i$ is a study-specific instantiation of the distribution of effect sizes, with $\tau^2$ representing heterogeneity.
-
-This then gives rise to:
-
-$$Y_i = x_i\beta_i + u_i + \epsilon_i$$
+#### Multilevel model metaregression
+
+We estimated pooled standardized mean differences for each arm by using multilevel models implemented in R's metafor package.
+Unlike the traditional random effects meta-analysis, which assumes that each study's true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
+This allows us to model variability at both the study level and the study arm level.
+
+The multilevel model assumes that each study's true effect size $\theta_{ij}$ (where $i$ indexes the study and $j$ indexes the study arm) is influenced by both the variability between studies and the variability between arms within each study.
+The model can be expressed as:
+
+$$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$
 
@@
 
-$$u_i \sim N(0, \tau^2) $$
-
-describes the deviation of each study from the mean of the distribution, and,
-
-$$\epsilon_i \sim N(0, \sigma^2)$$
-
-describes the sampling error.
-
-We can then specify the following model to obtain the means of each arm of the trials as follows:
-
-$$ \begin{aligned}
-    Υ_i &=
-    \begin{cases}
-        0 & MedControl:  b_0 + u_i + \epsilon_i\\
-        1 & MedActive:   b_0 + b_{1_{i}} +  u_i + \epsilon_i \\
-        2 & PsyActive:   b_0 + b_{2_{i}}  +  u_i + \epsilon_i \\
-        3 & PsyControl:  b_0 + b_{3_{i}}  +  u_i + \epsilon_i \\
-    \end{cases}
-\end{aligned}$$
-
-where to obtain the mean of each level is the sum of $b_0$, the intercept for the reference category of medication control, with the coefficient of each level, e.g.
-for level 3, $b_{3_{i}}$ the psychotherapy controls.
-The confidence intervals of the means are constructed in the standard way using the standard errors of the mean.
-Similarly, each coefficient represents the contrast between the reference category and each level, for an example and of main interest to us $b_{3_{i}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on the contrasts is done as follows:
-
-$$
-z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
-$$
+$$θij​∼N(xij​β,τi2​)$$
+
+{#eq-8}
+
+where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
+The true effect size $\theta_{ij}$ is modeled as a study-specific effect with an additional term representing the variability between arms within the study.
+
+This gives rise to the following model:
+
+$$ Yij=xijβ+ui+vij+ϵij $$
+
+{#eq-9}
+
+where,
+
+$$ ui​∼N(0,τ2) $$
+
+{#eq-10} describes the deviation of each study from the overall mean effect size, and
+
+$$vij∼N(0,τi2)$$ {#eq11}
+
+describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally,
+
+$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$
+
+{#eq-12}
+
+represents the sampling error.
+
+In this framework, we can model the means for each arm of the trials as follows:
+
+$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$
+
+{#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
+The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
+The confidence intervals for the means are constructed using the standard errors of the means, which account for the hierarchical structure of the data.
+Each coefficient represents the contrast between the reference category and each level.
+For example, $b_{3_{ij}}$ represents the contrast between psychotherapy and medication control arms.
+Inference on these contrasts is conducted using the following test statistic:
+
+$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$
+
+{#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms.
 

### 2024-08-13 revision1_reply_to_reviewers.qmd
added qmd for reply to reviewers

---
title: "revision1_reply_to_reviewers"
format: docx
editor: visual
---

### Reviewer 1

#### Comment 1.7

I could not see the rational for excluding the all female trials in the sex analyses. \[Comment 1.7\]

#### Response to 1.7

This is to not unduly bias the results. We now present the analyses with all studies included in the Supplemental Materials.

```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}

#| label: tbl-all-studies-percfemale-results
#| tbl-cap: "Percentage female at baseline across medication and psychotherapy studies: Results for sample including all female studies"
#| tbl-cap-location: top

df_baseline_results_no_excl %>% 
  as_flextable() %>% 
  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
  bg(i = 1, bg  = "#F2F2F2", part = "body") %>% # identify category sections
  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% # indent some rows
  align(j = 2:ncol(df_baseline_results_no_excl), align = "center", part = "all") %>% 
  bold(part = "header") %>%   # Bold the relevant header rows
  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
  # italic(i = 2, italic = TRUE, part = "header") %>% 
  border_remove() %>% # this is to remove borders that look strange
  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
  vline(j = 1, part = "body", border = small_border) %>% 
  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
  hline(part = "header", border = big_border) %>% 
  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
  line_spacing(space = .7, part = "all") %>%
  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
  autofit()

```

### Reviewer 3

#### Comment 3.5a: Effect modification

1\) Let's first start with a pairwise meta-analysis (MA). In the MA, we are usually pooling RR (or OR) and not RD, simply because the former is more generalizable. For example,

|         |                          |                               |     |
|---------|--------------------------|-------------------------------|-----|
|         | Control event rate (CER) | Experimental event rate (EER) | RR  |
| Trial 1 | 5/100                    | 10/100                        | 2.0 |
| Trial 2 | 30/100                   | 60/100                        | 2.0 |

In this case, even though the CER (and probably patient characteristics) differ markedly between Trial1 and Trial2, the RR is the same between the two trials and there is no problem pooling these two (no heterogeneity).

Factors that change the CER are called prognostic factors, and factors that change the EER/CER are called effect modifiers. In this case there are apparently differences in PFs between the two trials but there are no differences in EMs. \[Comment 3.5a\]

#### Response to 3.5a

We thank the reviewer for this example which perfectly illustrates our point and the rationale for our manuscript.

First, let's start with a widely accepted definition of the effect modification as represented by the European Medicines Agency's (EMA) group [European Network of Centres for Pharmacoepidemiology and Pharmacovigilance (ENcePP) entry on effect modification](https://encepp.europa.eu/encepp-toolkit/methodological-guide/chapter-7-effect-modification-and-interaction_en) and the publications it recommends on this topic:

The clinical motivation behind the assessment of effect modification is to identify whether the effect of a treatment (or exposure) is different in groups of patients with different characteristics. If the effects are the same, the treatment (or exposure) effect is called homogeneous; if the effects are different, they are called heterogeneous (<https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5476432/> )

The ENcePP [also clearly states that](https://encepp.europa.eu/encepp-toolkit/methodological-guide/chapter-7-effect-modification-and-interaction_en):

The presence of effect modification depends on which measure is used in the study (**absolute or relative** \[added emphasis by us\]**)** and can be measured in two ways: on an additive scale (based on risk differences \[RD\]), or on a multiplicative scale (based on relative risks \[RR\]).

To make this clear, we reproduce the table above, only adding another two column, one is the Odds Ratio (OR) another relative/multiplicative measure of relative risk that the reviewer also refers to as "more generalizable", and that of absolute risk, AR (i.e. the risk difference), an additive measure.

|         |                          |                               |     |     |      |
|---------|--------------------------|-------------------------------|-----|-----|------|
|         | Control event rate (CER) | Experimental event rate (EER) | RR  | OR  | AR   |
| Trial 1 | 5/100                    | 10/100                        | 2.0 | 2.1 | 0.05 |
| Trial 2 | 30/100                   | 60/100                        | 2.0 | 3.5 | 0.3  |

As can be seen the ORs differ quite substantially and the ARs differ by an order of magnitude. There is clearly an effect modification of some sort going on, when considering the OR or AR. Indeed, as the EMA and ENcePP state, whether effect modification is present (also) depends on the measure used. We therefore disagree with the reviewer that differences in the control event rate are ipso facto prognostic factors (PFs) if they do not affect the RR. Importantly, the RR is notorious for being potentially misleading (<https://pubmed.ncbi.nlm.nih.gov/15823376/>) and the necessity of reporting absolute risks is emphasised in standard clinical publications (e.g. <https://academic.oup.com/ndt/article/32/suppl_2/ii13/3056571> ).

To illustrate this point further in the context of trials, we point out that a key metric in intervention evaluation is the Numbers Needed to Treat (NNT) or its counterpart Numbers Needed to Harm (NNH). The NNT simply defined as the inverse of the AR, namely:

NNT = 1/AR

In the case above

NNT_trial_1 = 1/0.05 = 20

whereas

NNT_trial_2 = 1/0.3 = 3.3

The interpretation of NNT in the context of a placebo-controlled trial is simply: the average number of people who need to be treated with active treatment rather than placebo for one additional person to benefit. It is obvious from the above that, were such numbers to occur in a clinical trial, the clinical and public health implications of the difference between two treatments would be potentially vast and that it would be wrong to have considered RRs alone.

But we would go a step further and argue that all summary measures, including the AR, can conceal important clinical and public health facts, and that therefore reporting data that are close as possible to the raw numbers is key. We will illustrate this with an example.

Let there be two treatments A and B, with data on their efficacy coming comparisons that each has had with A_control and B_control, respectively. The efficacy of A is defined as

Eff_A = A -- A_control = 90% -- 60% = 30

and that of B as

Eff_B = B - B_control = 40% -- 10% = 30

And therefore

Eff_A = Eff_B

Since the AR is the same in each case, and one might conclude that we should be indifferent between the two treatments. However, it should be obvious that any rational agent, i.e. an agent who want so maximise benefit for themselves, would choose treatment A over B, if this were the data that they had to base their decision upon; indeed, nobody woudl choose a treatment with 40% probability recovery over one with 90% probability recovery? Unless of course there were a fundamental difference in the composition or circumstances of the trials.

All these considerations are very important and relevant to our paper and in the spirit of being very clear with the primary data, we have added, in addition to the  figure with the summary SMDs, this figure which presents the SMD of each study separately.

```{r, warning=F}

list_df_simulated[[1]] %>% 
  filter(arm_effect_size == "cohens_d_control") %>% 
  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
  geom_jitter(height = 0.2, alpha = 0.7) +
  geom_point(alpha = 0.7) +
  labs(
    title = "Pre-Post Standardised Mean Differences (SMD) of Control Arms",
    x = "SMD",
    y = "",
    color = "Type of Study",
    size = "Baseline n"
  ) +
  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
  theme_minimal() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank()
  )
```

Given this finding, there must be two possibilities about such a difference (given what we have written above). First, the difference may be due to differences the method of control. It is easy to conceive of this as a difference in the quality of the controls, i.e. how well they were blinded, or what exactly participants in the trial were told.

Second, there may be differences in the members of the control group (and therefore, in the context of a successful randomisation of all trial members).

#### Comment 3.8: Inaccurate statements

Given these theoretical considerations, here are examples of inaccurate or inadequate statements in the current manuscript. \[Comment 3.8\]

#### Response to 3.8

Before we respond to the reviewer's point one by one, we would like to suggest that a more useful---not least because more formally stated and generalizable---framework for theoretical considerations is the issue of external validity. We had included these formal treatments in previous versions of the manuscript, but decided to remove them becauseBriefly,

The average treatment effect is the measure of interest, defined as:

ATE = E\[Y(1)\] - E\[Y(0)\]

And the conditional treatment effect

CATE(X = x) = E\[Y(1) - Y(0) \\mid X = x\]

The CATE allows us to consider what may threaten external validity.

\
For example, if we consider W as a set of covariates affecting representativeness, then external validity would be violated if the following weren't true.

E\[Y \\mid W = w\] \\approx E\[Y \\mid W = w\\text{ in the population}\]

Similarly, if we considered Z as a set of covariates related to trial conditions, then external validity would be violated if the following weren't true.

E\[Y \\mid T = z\] \\approx E\[Y \\mid Z = z \\

It is obvious, that these formalisms that apply to the relationship between a sample and a population, also apply when two samples are compared with each other, in other words, the apples vs oranges situation that we describe in our paper.

We have added these formalisms with an explanation to the Supplemental Materials of the paper.

#### Comment 3.10: Use of baseline SD

Aside from this fundamental problem associated with pre-post SMDs, the current authors' handling of pre-post SMDs has further problems.

1.  The authors used the mean of the baseline SD and the endpoint SD to calculate the pre-post SMD. The use of baseline SD is problematic in depression trials, many of which use thresholds for baseline eligibility 2. In other words, the baseline SD is unnaturally small and, moreover, how small it is is partially determined by the threshold of the study, which can be different from study to study. \[Comment 3.10\]

#### Response to 3.10

We thank the reviewer for pointing this out. The key question is whether the baseline SDs are systematically different between medication and psychological therapy trials, i.e. whether this introduces a bias. If the differences are random, then this only contributes to noise. We are doing two things to address this.

First, we plot the mean differences (endpoint -- baseline) of the min-max transformed scores. As can be seen these are substantial, indicating that the difference is unlikely to stem simply from a difference in standard deviation calculation.

```{r, warning=F}

df_long_for_metan %>%
  filter(arm_effect_size == "cohens_d_control") %>%
  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>%
  ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) +
  geom_jitter(width = 0.2) + # Add jitter to points
  ggtitle("Post-Pre Differences in Mean Min-Max Scores") +
  ylab("Post-Pre Difference") +
  xlab("Type of Study") +
  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + # Customize x-axis labels
  theme_minimal()

```

Second, we plot below the baseline variances (i.e. squared sds), which largely overlap, making it unlikely that differences in baseline SD is the cause of the difference in the outcome.

```{r, warning=F}
# create baseline variances
df_long_for_metan$variances <- (df_long_for_metan$perc_baseline_sd)^2

df_long_for_metan %>%
  filter(arm_effect_size == "cohens_d_control") %>%
  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>%
  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) +
  geom_jitter(width = 0.2) + # Add jitter to points
  ggtitle("Post-Pre Differences in Study Baseline Variances") +
  ylab("Baseline Variance") +
  xlab("Type of Study") +
  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + # Customize x-axis labels
  theme_minimal()

```

Third, we conducted an addition analysis, restricting to studies with variances below 0.02 (see graph above).

```{r, warning=F}

#| label: fig-plot-means-var2
#| fig-cap: "Meta-analytic estimates of within-group changes: studies with variance <0.02"
#| fig-cap-location: top

coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition)))

# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study)
print(plot_means_multi_var2)

# png("plot_means_multi_var2.png")
# plot_means_multi_var2
# dev.off()

```

#### Comment 3.11: Studies with post SD

2.  I would predict that few studies, if any, reported both the baseline and endpoint SD and the authors have apparently used various imputations based on so many assumptions to impute the pre-post SMD. \[Comment 3.11\]

#### Response to 3.11

Actually, we have endpoint SDs in 61 (69.3% of) trials. To address the reviewer's point, we have now reanalysed our data restricted to just those studies and as can be seen below, the same inferences hold as before. We include this figure now as Fig XXX in the Supplement.

```{r, warning=F}
#| label: fig-plot-means-var2
#| fig-cap: "Meta-analytic estimates of within-group changes: studies with post SD"
#| fig-cap-location: top

coef_and_se_means_sd_study <- coef_and_se_means_sd_study %>%
  mutate(condition = case_when(
    condition == "medication_control" ~ "Medication Control",
    condition == "medication_active" ~ "Medication Active",
    condition == "psychotherapy_control" ~ "Psychotherapy Control",
    condition == "psychotherapy_active" ~ "Psychotherapy Active",
    TRUE ~ as.character(condition)))

# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: studies with post SD"
plot_means_multi_sd <- plot_means_function(coef_and_se_means_sd_study)
print(plot_means_multi_sd)

# png("plot_means_multi_var2.png")
# plot_means_multi_sd
# dev.off()
```

Coefficients across simulations (not sure in which response to add this):

```{r, warning=F}

coefs_test <- do.call(rbind, lapply(list_dummy_var_means, function(sim) sim$coefficients))
df_coefs_test <- data.frame(coefs_test)

col_names <- c("Medication_Control", "Medication_Active", "Psychotherapy_Control", "Psychotherapy_Active")
colnames(df_coefs_test) <- col_names

df_coefs_long <- gather(df_coefs_test, key = "condition", value = "coefs", Medication_Control:Psychotherapy_Active)

#creating separate histograms

coefs_hist <- ggplot(df_coefs_long, aes(x = coefs)) +
  geom_histogram(binwidth = 0.001, color = "black", fill = "lightblue") +
  facet_wrap(~ condition, scales = "free_x") +
  theme_minimal() +
  labs(title = "Distribution of Coefficients by Condition",
       x = "Coefficient",
       y = "Frequency") +
  theme(panel.spacing.x = unit(3, "lines"))
print(coefs_hist)

#ggsave("simulated_coefficients_by_condition_hist.jpeg", coefs_hist)
```

### 2024-08-14 revision1_reply_to_reviewers.qmd
formatted equations

@@
 ---
-title: "revision1_reply_to_reviewers"
+title: "Comparing Apples and Oranges in Youth Depression Treatments? A Quantitative Critique of the Evidence Base and Guidelines"
+subtitle: "Major Revision: Letter to Reviewers"
 format: docx
@@
 ---
+
+```{r}
+library(tidyverse)
+library(truncnorm)
+library(metafor)
+library(meta)
+library(kableExtra)
+library(flextable)
+library(magrittr)
+library(officer)
+library(RefManageR)
+library(ftExtra)
+library(dplyr)
+library(broom)
+library(effsize)
+library(here)
+
+#set source
+load("my_environment.RData")
+```
 
@@
 |         |                          |                               |     |     |      |
-|---------|--------------------------|-------------------------------|-----|-----|------|
+|------------|------------|-------------|------------|------------|------------|
 |         | Control event rate (CER) | Experimental event rate (EER) | RR  | OR  | AR   |
@@
 
-NNT = 1/AR
+$$
+NNT = \frac{1}{AR}
+$$
 
-In the case above
+In the case above:
 
-NNT_trial_1 = 1/0.05 = 20
+$$
+NNT_{Trial_1} = \frac{1}{0.05} = 20 
+$$
 
-whereas
+whereas:
 
-NNT_trial_2 = 1/0.3 = 3.3
+$$
+NNT_{Trial_2} = \frac{1}{0.3} = 3.3 
+$$
 
@@
 
-Let there be two treatments A and B, with data on their efficacy coming comparisons that each has had with A_control and B_control, respectively. The efficacy of A is defined as
+Let there be two treatments A and B, with data on their efficacy coming comparisons that each has had with A_control and B_control, respectively. The efficacy of A is defined as:
 
-Eff_A = A -- A_control = 90% -- 60% = 30
+$$
+Eff_{A} = A - A_{Control} = 90% - 60% = 30%
+$$
 
-and that of B as
+and that of B as:
 
-Eff_B = B - B_control = 40% -- 10% = 30
+$$
+Eff_{B} = B - B_{Control} = 40% - 10% = 30%
+$$
 
-And therefore
+And therefore:
 
+$$
 Eff_A = Eff_B
+$$
 
@@
 
+$$
 ATE = E\[Y(1)\] - E\[Y(0)\] 
+$$
 
-And the conditional treatment effect
+And the conditional treatment effect:
 
+$$
 CATE(X = x) = E\[Y(1) - Y(0) \\mid X = x\]
+$$
 

### 2024-08-21 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
edits to address comment - ready to render

@@
 
-The study protocol was registered on the Open Science Framework (OSF) and can be found [here](https://osf.io/bfmc6).
+The study protocol was registered on the Open Science Framework (OSF) and can be found at <https://osf.io/bfmc6>.
 
@@
 We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
-For the psychotherapy trials, we utilised open data from the previous meta-analysis (see [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/)).
+For the psychotherapy trials, we utilised open data from the previous meta-analysis (see <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
 For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
@@
 
-## Statistical Analysis
+## Statistical analysis
 
@@
 
-#### Measures of Effect
+#### Measures of effect
 
@@
 The multilevel model assumes that each study's true effect size $\theta_{ij}$ (where $i$ indexes the study and $j$ indexes the study arm) is influenced by both the variability between studies and the variability between arms within each study.
-The model can be expressed as:
-
- $$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$
-
-where,
-
-$$θij​∼N(xij​β,τi2​)$$
-
-{#eq-8}
-
-where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
+The model can be expressed as: -->
+
+<!-- $$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$ -->
+
+<!-- where, -->
+
+<!-- $$θij​∼N(xij​β,τi2​)$$ -->
+
+<!-- where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
 The true effect size $\theta_{ij}$ is modeled as a study-specific effect with an additional term representing the variability between arms within the study.
-
-This gives rise to the following model:
-
-$$ Yij=xijβ+ui+vij+ϵij $$
-
-{#eq-9}
-
-where,
-
-$$ ui​∼N(0,τ2) $$
-
-{#eq-10} describes the deviation of each study from the overall mean effect size, and
-
-$$vij∼N(0,τi2)$$ {#eq11}
-
-describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally,
-
-$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$
-
-{#eq-12}
-
-represents the sampling error.
-
-In this framework, we can model the means for each arm of the trials as follows:
-
-$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$
-
-{#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
+-->
+
+<!-- This gives rise to the following model: -->
+
+<!-- $$ Yij=xijβ+ui+vij+ϵij $$ -->
+
+<!-- where, -->
+
+<!-- $$ ui​∼N(0,τ2) $$ -->
+
+<!-- {#eq-10} describes the deviation of each study from the overall mean effect size, and -->
+
+<!-- $$vij∼N(0,τi2)$$ -->
+
+<!-- describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally, -->
+
+<!-- $$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$ -->
+
+<!-- {#eq-12} represents the sampling error. -->
+
+<!-- In this framework, we can model the means for each arm of the trials as follows: -->
+
+<!-- $$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$ -->
+
+<!-- {#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
 The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
@@
 For example, $b_{3_{ij}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on these contrasts is conducted using the following test statistic:
-
-$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$
-
-{#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms. -->
+Inference on these contrasts is conducted using the following test statistic: -->
+
+<!-- $$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$ -->
+
+<!-- {#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms. -->
 
@@
 
-### Sensitivity Analyses
+### Sensitivity analyses
 
@@
     geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
-    geom_text(vjust = +1.5, size = 4) +
+    geom_text(vjust = +1.5, size = 4.5) +
     scale_size_continuous(guide = "none") +
@@
     xlim(-3.0, 0.5) +
-    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey") +
-    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey", vjust = 0.5, hjust = 1) +
-    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey", vjust = 0.5, hjust = 0)+
+    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey50") +
+    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
+    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey50", vjust = 0.5, hjust = 1, size = 4.5) +
+    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
+    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)+
     theme(axis.title.x = element_text(size = 12, family  = "Calibri"), 
@@
           plot.subtitle = element_text(size = 12, family =  "Calibri", face= "italic")) +
-    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
-    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey", vjust = 0.5, hjust = 0)
+    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey50", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
+    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)
 
@@
   line_spacing(space = .7, part = "all") %>% 
-  add_footer_row(values = as_paragraph("*These are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
+  add_footer_row(values = as_paragraph(
+    "Abbreviations: K = number of studies, SE = standard error, CI = 95% confidence interval, T2 = estimate of between-study heterogeneity",
+    "*These are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
 range of 96).
@@
 plot_means_multi_all <- plot_means_function(df_mean_coefs_from_sim)
-print(plot_means_all)
-
- #png("plot_means_multi_all.png")
- #plot_means_multi_all
- #dev.off()
+print(plot_means_multi_all)
+
+ png("plot_means_multi_all.png")
+ plot_means_multi_all
+ dev.off()
 
@@
 
-In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-Here, medication control is the reference category to which all others are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p\<0.0001).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
-#| label: tbl-results-overall
-#| tbl-cap: "Results from metaregression with overall sample"
-#| tbl-cap-location: top
-
-# Regression results
-
-aggregate_results_overall <- aggregate_results_overall %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "coefficients")
-
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")
-
-# Assign new column names to the data frame
-colnames(aggregate_results_overall) <- new_column_names
-
-table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
-table_aggregate_results_overall[1, 4] <- NA
-
-flextable(table_aggregate_results_overall) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
-                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
-                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
-  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-  # add_header_row(values = "Table 4", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
 ##### Sensitivity analyses
@@
 Medication control and psychotherapy control conditions remained significantly different, though the small number of studies resulted in less precise estimates of the SMDs.
+Conversely, restricting the analysis to studies with variance below 0.02 yielded a similar pattern of results, but with increased precision in SMD estimates across conditions (see @fig-plot-means-var2).
 Finally, we showed that different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
 
-##### Addressing Regression to the Mean
+##### Addressing regression to the mean
 
@@
     Modality = psy_or_med,
-    N = n,
+    K = n,
     Mean = mean_sites,
@@
 
-df_descr_psy_conditions <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
+df_descr_psy_conditions <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
 
@@
     Column = character(),
-    N = numeric(),
+    K = numeric(),
     Mean = numeric(),
@@
       result_dataframe <- rbind(result_dataframe,
-                                data.frame(Column = col, Group = group, N = n, Mean = mean_val,
+                                data.frame(Column = col, Group = group, K = n, Mean = mean_val,
                                            SD = SD, Median = median_val,
@@
   align(j = 2:9, align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
   # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
@@
   #italic(i = 2, italic = TRUE, part = "header") %>% 
+  add_footer_row(values = as_paragraph("Abbreviations: K = number of studies, SD = standard deviation, CI = 95% confidence interval, df = degrees of freedom"), colwidths = 10) %>%
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
   border_remove() %>% # this is to remove borders around the caption that look strange
@@
 We found that medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
-Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy.
+Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy [@dechartresSingleCenterTrialsShow2011]; [@meisterPlaceboResponseRates2020].
 Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
@@
 More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the vast disparity in the response to control conditions is reason for major concern about our ability to draw inferences from comparisons of modalities.
+In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
 This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
@@
 TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
-Importantly, controls were often very poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
-Overall, there is very poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
-
-Given all of the above, the certainty with which guidelines recommend psychotherapy over medication for adolescent depression is surprising.
-Indeed, we believe that our findings have several profound implications for patients, their families, clinicians and policy makers.
+Importantly, controls were often poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
+Overall, there is poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
+
+Given all of the above, the empirical basis for comparing psychotherapy and medication for adolescent depression is weak, and hence it is difficult to generate guidelines and recommend one treatment over another.
+Indeed, we believe that our findings have several implications for patients, their families, clinicians and policy makers.
 
@@
 Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
-Moreover, there is a place for comparing interventions to TAU, however issues of disappointment bias should be addressed to avoid inflating treatment estimates.
+Moreover, there is a place for comparing interventions to TAU, since these represent real-world comparators.
+However issues of disappointment bias should be addressed to avoid inflating treatment estimates.
 
@@
 Our data question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, deserve better evidence on which to base their choices.
+Returning to our motivating question, the stakeholders, including patients and clinicians, need better evidence on which to base their choices.
 
@@
 
-References for trials included in the existing meta-analyses drawn upon for this study can be found [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/) for psychotherapy RCTs and [here](https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5) for medication RCTs.
+References for trials included in the existing meta-analyses drawn upon for this study can be found at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>
+for psychotherapy RCTs and at <https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5> for medication RCTs.
 Below are references for the seven additional RCTs identified in the original systematic review conducted for the current study.
@@
 
+#### Multilevel metaregression results
+
+In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
+Here, medication control is the reference category to which all others are compared.
+The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p\<0.0001).
+
+```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
+#| label: tbl-results-overall
+#| tbl-cap: "Results from metaregression with overall sample"
+#| tbl-cap-location: top
+
+# Regression results
+
+aggregate_results_overall <- aggregate_results_overall %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition))) %>% 
+  relocate("condition", .before = "coefficients")
+
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")
+
+# Assign new column names to the data frame
+colnames(aggregate_results_overall) <- new_column_names
+
+table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
+table_aggregate_results_overall[1, 4] <- NA
+
+flextable(table_aggregate_results_overall) %>%
+  set_table_properties(width = 1) %>%
+  autofit() %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
+                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
+                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
+  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
+  # add_header_row(values = "Table 4", colwidths = 6) %>% 
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
+  # italic(i = 2, italic = TRUE, part = "header") %>% 
+  border_remove() %>% # this is to remove borders around the caption that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
+  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
+  align(j = 1, align = "left", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>% 
+  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
+  line_spacing(space = .7, part = "all")
+```
+
 ## Metaregression sensitivity analyses
@@
 
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+#| label: fig-plot-means-postsd
+#| fig-cap: "Meta-analytic estimates of within-group changes: studies with post SD"
+#| fig-cap-location: top
+
+coef_and_se_means_sd_study <- coef_and_se_means_sd_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: studies with post SD"
+plot_means_multi_sd <- plot_means_function(coef_and_se_means_sd_study)
+print(plot_means_multi_sd)
+
+ png("plot_means_multi_sd.png")
+ plot_means_multi_sd
+ dev.off()
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+
+#| label: fig-plot-means-var2
+#| fig-cap: "Meta-analytic estimates of within-group changes: studies with variance <0.02"
+#| fig-cap-location: top
+
+coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study)
+print(plot_means_multi_var2)
+
+ png("plot_means_multi_var2.png")
+ plot_means_multi_var2
+ dev.off()
 ```

### 2024-09-03 Script for cleaning psychotherapy data.R
Added new studies from Zhou NMA

@@ -87,9 +87,10 @@ df_full <- full_join(df_full, for_merge)
                       
 # create dataframe with main variables needed for meta-analysis
 df_full_psych <- df_full %>% 
-  select(c(Column1, study, year, condition_arm1, condition_arm2, descr_arm1, descr_arm2, instrument, rating,
-           mean_arm1: n_arm2, baseline_m_arm1:baseline_n_arm2, percent_women, responders_arm1, responders_arm2, 
-           ee, ec, country, comorbid_mental, `comorbid_mental?`, diagnosis))
+  select(Column1, study, year, condition_arm1, condition_arm2, descr_arm1, descr_arm2, instrument, rating,
+         mean_arm1, sd_arm1, n_arm1, mean_arm2, sd_arm2, n_arm2, baseline_m_arm1, baseline_sd_arm1, baseline_n_arm1, baseline_m_arm2, 
+         baseline_sd_arm2, baseline_n_arm2, percent_women, responders_arm1, responders_arm2, 
+         ee, ec, country, comorbid_mental, `comorbid_mental?`, diagnosis)
 
 # rename variables
 df_full_psych <- df_full_psych %>% rename(active_type = condition_arm1, control_type = condition_arm2, descr_active = descr_arm1, descr_control = descr_arm2, 
@@ -133,6 +134,71 @@ Working_Dataset_Psychotherapy <- Working_Dataset_Psychotherapy %>%
 
 df_full_psych <- full_join(df_full_psych, Working_Dataset_Psychotherapy, by = "Column1")
 
+# Append studies from Zhou et al
+
+  # Following comments from reviewers, we are now including studies from the Zhou NMA that are not covered in Cuijpers (there are not med studies)
+
+df_studies_from_zhou <- read_excel("Studies_from_Zhou_NMA.xlsx") #3 studies
+df_studies_from_zhou <- df_studies_from_zhou %>%
+  mutate(across(c(post_mean_active, post_sd_active, post_mean_control, post_sd_control,
+                 baseline_mean_active, baseline_sd_active, baseline_mean_control, baseline_sd_control,
+                 post_n_active, post_n_control, baseline_n_active, baseline_n_control, percent_women,
+                 age_m_active, age_sd_active, age_m_control, age_sd_control, age_m_overall, age_sd_overall), as.numeric)) # convert to numeric 
+
+# compute response rates as previous
+
+  # create dataframe with vectors needed to calculate no of responders
+
+df_clean_zhou <- df_studies_from_zhou %>% 
[…]

### 2024-09-03 Script for cleaning merged dataset.R
Added studies from Zhou NMA

@@ -244,8 +244,8 @@ write.csv(df_first_row, "df_first_row.csv")
 
 #check how many med comparisons we cannot calc cohens d for (for primary instrument)
 filter_test <- df_first_row %>% filter(psy_or_med == 0)
-sum(is.na(filter_test$cohens_d_active))
-sum(is.na(filter_test$cohens_d_control))
+sum(is.na(filter_test$cohens_d_active)) # 33
+sum(is.na(filter_test$cohens_d_control)) # 33
 
 # start looking at demographics, baseline and post means, and cohens d per arm
 df_demographics <- df_first_row %>% dplyr:: select(study, year, psy_or_med, active_type, control_type, descr_active, descr_control,
@@ -261,11 +261,12 @@ df_demographics$descr_control <- ifelse(is.na(df_demographics$descr_control), df
 df_demographics <- df_demographics %>%  dplyr::select(-c(active_type, control_type))
 df_demographics <- df_demographics %>%  arrange(psy_or_med)
 
-# check how many studies we have baseline means for primary instrument
+# check how many studies we have baseline means and sd for primary instrument
 df_summary_missing_data <- df_demographics %>% 
   group_by(psy_or_med) %>% 
   summarise(n_reporting_base_means_act = sum(!is.na(baseline_mean_active)), n_reporting_base_means_contr = sum(!is.na(baseline_mean_control)),
-  n_reporting_post_means_act = sum(!is.na(post_mean_active)), n_reporting_post_means_contr = sum(!is.na(post_mean_control)))
+  n_reporting_post_means_act = sum(!is.na(post_mean_active)), n_reporting_post_means_contr = sum(!is.na(post_mean_control)),
+  n_reporting_post_sd_act = sum(!is.na(post_sd_active)), n_reporting_post_sd_contr = sum(!is.na(post_sd_control)))
 
 # average cohens d, mean age and percent women, summarising across psy and med
 df_means_demo <- df_demographics %>%  
@@ -278,32 +279,32 @@ df_means_demo <- df_demographics %>%
 
 # Argyris looking at stats per instr
 
-# keep only non_zero values
-test_2 <- df_stats_per_instrument %>% 
-  filter((type == "med" & n != 0) | (type == "psy" & n != 0) )
-
-# keep only duplicated rows
-library(misty)
-test_2 <- df.duplicated(test_2, instr)
-
[…]

### 2024-09-04 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
added some text changes for revision

@@
     note:
+  - name: Raphaelle Delpech
+    email: raphaelle.delpech.18@ucl.ac.uk
+    affiliations:
+        - ref: ucl_1
   - name: Rudolf Uher
@@
   - name: Ioannis-Marios Rokas
-    email: <rokasgiannis93@gmail.com
+    email: rokasgiannis93@gmail.com
     affiliations:
@@
 The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
+Also, the addition of psychotherapy to standard care did not improve outcomes (REF).
 Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
@@
 This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation, we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
+To ensure that our results are not biased by misestimation (REF), we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
 
@@
 Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
+Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
 
@@
 
-@tbl-baseline_results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
+tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
 The summary statistics are provided for each subgroup (i.e.
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-baseline_results
+#| label: tbl-baseline-results
 #| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies: Results for overall sample and sensitivity analyses"
@@
 
-On average, depression severity at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline_results).
+On average, depression severity at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline-results).
 When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 # looking at CDRS studies only, this is with only 2 levels
@@
 
-As can be seen in @tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
 We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-As seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
+As seen in fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
 In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
@@
 
-df_no_sites <- readxl:: read_excel("for_despina_and_giannis_200224.xlsx")
+df_no_sites <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
 
@@
   #italic(i = 2, italic = TRUE, part = "header") %>% 
-  add_footer_row(values = as_paragraph("Abbreviations: K = number of studies, SD = standard deviation, CI = 95% confidence interval, df = degrees of freedom"), colwidths = 10) %>%
+  add_footer_row(values = as_paragraph("Abbreviations: K = number of studies, SD = standard deviation, CI = 95% confidence interval, df = degrees of freedom."), colwidths = 10) %>%
   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
@@
 This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving randomisation to balance confounders is critical.
-However, we note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
+More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
+In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
+This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
+
+We note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
 Indeed, in Zhou et al.
@@
 CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial [@marchFluoxetineCognitiveBehavioralTherapy2004].
-More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
-This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
+We note that the Zhou metanalysis, which represents an admirable effort to synthesise the literature, reports on issues that may affect transitivity with tests of incoherence showing significant differences.
 
@@
 We also searched clinical trial registers for published and unpublished studies however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
-Please see @fig-prisma for the PRISMA flow diagram.
+Please see fig-prisma for the PRISMA flow diagram.
 
@@
 
-References for trials included in the existing meta-analyses drawn upon for this study can be found at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>
-for psychotherapy RCTs and at <https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5> for medication RCTs.
+References for trials included in the existing meta-analyses drawn upon for this study can be found at <https://docs.metapsy.org/databases/depression-childadol-psyctr/> for psychotherapy RCTs and at <https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5> for medication RCTs.
 Below are references for the seven additional RCTs identified in the original systematic review conducted for the current study.
@@
 Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available [here](https://docs.metapsy.org/databases/depression-childadol-psyctr/)).
+Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
 Whilst Cuijpers et al.
@@
 Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpersEffectsPsychologicalTreatments2021] literature search.
+We also included three studies from Zhou et al.
+(REF) which were not covered in the previous meta-analysis whilst fitting the date range.
 
@@
 
-where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
+where, $$\bar{X}$$is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
 The standard deviation is calculated thus:
@@
 
-$$θij​∼N(xij​β,τi2​)$$
-
-{#eq-8}
+$$θij​∼N(xij​β,τi2​)$$ {#eq-8}
 
@@
 
-$$ Yij=xijβ+ui+vij+ϵij $$
-
-{#eq-9}
+$$ Yij=xijβ+ui+vij+ϵij $$ {#eq-9}
 
@@
 
-$$ ui​∼N(0,τ2) $$
-
-{#eq-10} describes the deviation of each study from the overall mean effect size, and
-
-$$vij∼N(0,τi2)$$ {#eq11}
+$$ ui​∼N(0,τ2) $$ {#eq-10}
+
+describes the deviation of each study from the overall mean effect size, and
+
+$$vij∼N(0,τi2)$$ {#eq-11}
 
@@
 
-$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$
-
-{#eq-12}
+$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$ {#eq-12}
 
@@
 
-$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$
-
-{#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
+$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$ {#eq-13}
+
+Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
 The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
@@
 
-$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$
-
-{#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms.
+$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$ {#eq-14}
+
+This test allows us to assess the significance of the differences between treatment effects across study arms.
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r echo=FALSE, message=FALSE, warning=FALSE}
 #| label: tbl-all-trials
@@
 
- #png("plot_means_multi_no_wl.png")
- #plot_means_no_wl
- #dev.off()
+ png("plot_means_multi_no_wl.png")
+plot_means_no_wl
+ dev.off()
 
@@
 
-# png("plot_means_multi_cdrs.png")
-# plot_means_cdrs
-# dev.off()
+ png("plot_means_multi_cdrs.png")
+ plot_means_cdrs
+ dev.off()
 
@@
 # subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study)
-print(plot_means_hamd)
-
-# png("plot_means_multi_cdrs.png")
-# plot_means_cdrs
-# dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-hamd
-#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
-#| fig-cap-location: top
-
-coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_hamd <- plot_means_function(coef_and_se_means_hamd_study)
-print(plot_means_hamd)
-
-# png("plot_means_multi_cdrs.png")
-# plot_means_cdrs
-# dev.off()
+plot_means_multi_hamd <- plot_means_function(coef_and_se_means_hamd_study)
+print(plot_means_multi_hamd)
+
+ png("plot_means_multi_hamd.png")
+ plot_means_multi_hamd
+ dev.off()
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-
 #| label: fig-plot-means-var2

### 2024-09-06 Script for cleaning psychotherapy data.R
added Brent 1997 study from Zhou

@@ -154,7 +154,7 @@ df_clean_zhou <- df_studies_from_zhou %>%
            post_mean_control, post_sd_control, baseline_mean_control) %>% 
   na.omit()
 
-  `# create and store an empty vector
+  # create and store an empty vector
 
 responders_active <- 0
 responders_control <- 0

### 2024-09-09 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
some changes for revision

@@
   docx:
-    reference-doc: custom-reference-doc.docx
+    reference-doc: "bibliography/word-style-reference-doc.docx"
     fig-width: 9
@@
     tbl_caption: yes
-    numer-sections: true
-editor: visual
-bibliography: "emotion_concepts_paper.bib"
-csl: "vancouver.csl"
+    number-sections: true
+execute: 
+  echo: true
+  auto: true
+  warning: FALSE
+bibliography: "bibliography/references.bib"
+csl: "bibliography/vancouver_style.csl"
 font:
-  family: "Calibri"
-prefer-html: true
-fig-format: png
+  family: Calibri
 fig-cap-location: top
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r library, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
 
@@
 # For referencing
-bib_data <- ReadBib(here("emotion_concepts_paper.bib"))
+bib_data <- ReadBib(here("multilevel_metaregression", "bibliography", "references.bib"))
 
@@
 ```{r global_options, include=FALSE}
+
 knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
@@
 The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
-Also, the addition of psychotherapy to standard care did not improve outcomes (REF).
+Also, the addition of psychotherapy to standard care did not improve outcomes [@goodyer_randomised_2008].
 Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
@@
 the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
-
-<!-- Indeed, comparing outcomes (Y) between psychotherapy and medication trials requires us to contrast what is called the sample average treatment effect $\tau$ of each, defined in the following way: -->
-
-<!-- $$ -->
-
-<!-- \tau_{psy} =  E(Y_{1} - Y_{0} \,|\, S, psy) -->
-
-<!-- $$ $$ -->
-
-<!-- \tau_{med} =  E(Y_{1} - Y_{0} \,|\, S, med)\  -->
-
-<!-- $$ -->
-
-<!-- where the operator E denotes the expectation over the differences in outcomes between those who received the intervention (T = 1) and those who received the control condition (T = 0), for each sample, $S$, where psy and med stand for psychotherapy and medication respectively.
--->
-
-<!-- Obviously, this comparison rests on the assumption that trials in both modalities sample from the same population, $P$, of patients. Formally, this can be expressed as follows: -->
-
-<!-- $$E(Y_{1} \,|\, \text{S, psy}) = E(Y_{1} \,|\, P, \text{psy})$$ -->
-
-<!-- $$E(Y_{1} \,|\, \text{S, med}) = E(Y_{1} \,|\, P, \text{med})$$ -->
-
-<!-- signifying that the effect found in the population would be expected to be found in the same population for each treatment. -->
 
@@
 
-<!-- In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism: -->
-
-<!-- $$ -->
-
-<!-- \text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}} -->
-
-<!-- $$ -->
-
-<!-- where, $$\bar{X}$$ is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
-The standard deviation is calculated thus: -->
-
-<!-- $$ -->
-
-<!-- \text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}} -->
-
-<!-- $$ -->
-
-<!-- where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline. -->
-
 ### Trial design
@@
 
-<!-- which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as: -->
-
-<!-- $$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$ -->
-
-<!-- where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
--->
-
 Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023].
-
-<!-- If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
-For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
-If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani et al.'s meta-analysis.
--->
 
@@
 This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation (REF), we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
-
-<!-- This is calculated according to: -->
-
-<!-- $$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$ -->
-
-<!-- where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
-This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
-However, this practice has given rise to concerns about misestimation.
-Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e.
-bias estimation of the effects for the control group of medication compared to those of psychotherapy.
-Still, to alleviate such concerns we have used a simulations.
--->
-
-<!-- In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics: -->
-
-<!-- $$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$ -->
-
-<!-- for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
-We then used these simulated datasets in the subsequent meta-analyses.
--->
+To ensure that our results are not biased by misestimation [@cuijpers_pre-post_2017], we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
 
@@
 We estimated pooled SMDs for each arm by using multilevel models implemented in R's metafor package.
-
-<!--  Unlike the traditional random effects meta-analysis, which assumes that each study's true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
-This allows us to model variability at both the study level and the study arm level.
-The multilevel model assumes that each study's true effect size $\theta_{ij}$ (where $i$ indexes the study and $j$ indexes the study arm) is influenced by both the variability between studies and the variability between arms within each study.
-The model can be expressed as: -->
-
-<!-- $$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$ -->
-
-<!-- where, -->
-
-<!-- $$θij​∼N(xij​β,τi2​)$$ -->
-
-<!-- where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
-The true effect size $\theta_{ij}$ is modeled as a study-specific effect with an additional term representing the variability between arms within the study.
--->
-
-<!-- This gives rise to the following model: -->
-
-<!-- $$ Yij=xijβ+ui+vij+ϵij $$ -->
-
-<!-- where, -->
-
-<!-- $$ ui​∼N(0,τ2) $$ -->
-
-<!-- {#eq-10} describes the deviation of each study from the overall mean effect size, and -->
-
-<!-- $$vij∼N(0,τi2)$$ -->
-
-<!-- describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally, -->
-
-<!-- $$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$ -->
-
-<!-- {#eq-12} represents the sampling error. -->
-
-<!-- In this framework, we can model the means for each arm of the trials as follows: -->
-
-<!-- $$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$ -->
-
-<!-- {#eq-13} Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
-The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
-The confidence intervals for the means are constructed using the standard errors of the means, which account for the hierarchical structure of the data.
-Each coefficient represents the contrast between the reference category and each level.
-For example, $b_{3_{ij}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on these contrasts is conducted using the following test statistic: -->
-
-<!-- $$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$ -->
-
-<!-- {#eq-14} This test allows us to assess the significance of the differences between treatment effects across study arms. -->
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
+```{r set-up-z, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
 # my alpha for the z 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r define-functions, warning=FALSE, message = FALSE, echo=FALSE}
 #############Some custom made functions#############
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r import-dataset, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r metaregression-all, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
-
-# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-#  grab ids for those studies
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
-# We may have multiple controls per study id for this reason, though this isn't a problem 
-# conceptually.
-
-list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-})
-
-# count the number of studies
-cbt_fluox_esc_study <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids,
-         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
-study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# CB checked, looks good now.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
- coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
+```
+
+```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
+# # B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
+# #  grab ids for those studies
+# cbt_fluox_esc_study_ids <-
+#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+# 
+# # Use those ids to subset all dataframes in the list
+# # By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
+# # So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
+# # This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
+# # We may have multiple controls per study id for this reason, though this isn't a problem 
+# # conceptually.
+# 
+# list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
+#   df %>%
+#     filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
+#     filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+# })
+# 
+# # count the number of studies
+# cbt_fluox_esc_study <- df_long_for_metan %>%
+#   filter(new_study_id %in% cbt_fluox_esc_study_ids,
+#          !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
+# study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
+# # CB checked, looks good now.
+# 
+# # apply the metareg function to the list of cbt, fluox, esc
+# model_1 <- as.formula(~ four_level_var)
+# list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
+# 
+# # extract coefficients and model characteristics.
+# condition <- levels(list_df_simulated[[1]]$four_level_var)
+# aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
+# aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
+# 
+# # extract SMDs from the list for cbt fluox escit
+# means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
+# 
+# # calculate mean SMDs and ses
+# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+# coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
+#  coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
+# 
+# # add the ns to the dataframe
+# coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
+#                                         ungroup() %>% 
+#                                       select(condition, n),  
+#                                     by = "condition")
+```
+
+```{r metaregression-nowl, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
+```
+
+```{r metaregression-clin, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
+```
+
+```{r metaregression-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
+```
+
+```{r metaregression-hamd, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
+```
+
+```{r metaregression-postsd, warning=FALSE, message = FALSE, echo=FALSE}
+
 # G. Post SD Sensitivity Analysis ---------------------------------------
@@
 
+```
+
+```{r metaregression-var, warning=FALSE, message = FALSE, echo=FALSE}
+
 #H. Studies with variances <.02-----------------------------
@@
 
-# apply the metareg function to the list of clinical studies
+# apply the metareg function to the list
 model_1 <- as.formula(~ four_level_var)
@@
 
-# extract SMDs from the list for clinical studies
+# extract SMDs from the list
 means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
@@
                                         by = "condition")
-
 ```
@@
 
-tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
+@tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
 The summary statistics are provided for each subgroup (i.e.
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r characteristics-metanalysis, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
-```{r echo=FALSE, message=FALSE, warning=FALSE}
+```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
 # looking at CDRS studies only, this is with only 2 levels
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r baseline-severity-hamd-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
 ## this is for four levels
@@
 
-As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
 We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-As seen in fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
+As seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
 In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
@@
   )
+
+ png("plot_means_multi_all.png")
+ plot_means_multi_all
+ dev.off()
 ```
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r baseline-adjust-means, warning=FALSE, message = FALSE, echo=FALSE}
 # #### Let's start from the beginning and regress cohens on the baseline dataframe.
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r trial-sites, warning=FALSE, message = FALSE, echo=FALSE}
 ### Number of sites
@@
 
-# df_baseline_demographics %>%
-#   group_by(psy_or_med, site_binary) %>%
-#   summarize(num_trials = n())
+df_binary_site_count <- df_baseline_demographics %>% 
+  group_by(psy_or_med, site_binary) %>% 
+  summarize(num_trials = n())
 
@@
 Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
+Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 25 of 46 (54%) psychotherapy studies.
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r nature-intensity-comparison, warning=FALSE, message = FALSE, echo=FALSE}
 # We need to read in the appropriate dataset which describes the active and control conditions used in
@@
 
-```{r, echo=FALSE}
+```{r proportion-wl, echo=FALSE}
 # Filter the dataframe
@@
 We also included three studies from Zhou et al.
-(REF) which were not covered in the previous meta-analysis whilst fitting the date range.
+\[\@\] which were not covered in the previous meta-analysis whilst fitting the date range.
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
+```{r setting-z-2, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
 # my alpha for the z 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
+```{r sex-all-studies, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+mean_diff_min_max_scores <- df_long_for_metan %>% 
+  filter(arm_effect_size == "cohens_d_control") %>% 
+  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
+  ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) + 
+  geom_jitter(width = 0.2) + 
+  ggtitle("Post-Pre Differences in Mean Min-Max Scores") + 
+  ylab("Post-Pre Difference") +
+  xlab("Type of Study") +
+  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) +   theme_minimal()
+
+print(mean_diff_min_max_scores) 
+png("mean_diff_min_max_scores.png")
+mean_diff_min_max_scores
+dev.off()
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+# create baseline variances
+df_long_for_metan$variances <- (df_long_for_metan$perc_baseline_sd)^2
+
+plot_baseline_var <- df_long_for_metan %>% 
+  filter(arm_effect_size == "cohens_d_control") %>% 
+  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
+  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) + geom_jitter(width = 0.2) +  
+  ggtitle("Post-Pre Differences in Study Baseline Variances") + 
+  ylab("Baseline Variance") + 
+  xlab("Type of Study") + 
+  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + theme_minimal()
+
+print(plot_baseline_var)
+png("plot_baseline_var.png")
+plot_baseline_var
+dev.off()
+```
+
 ## Metaregression sensitivity analyses
+
+```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
+# # G. Post SD Sensitivity Analysis ---------------------------------------
+# 
+# ##--------- Data preparation
+# 
+# #For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
+# 
+# #create subset of first_row
+# 
+# df_first_row <- read.csv(here("df_first_row.csv"))
+# 
+# #create new_study_ids to match master dataset
+# df_first_row  <- df_first_row  %>%
+#   mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
+#                                   .default = study ))
+# 
+# df_first_row_reduced <- df_first_row %>%
+#   filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
+#   select(new_study_id, post_sd_active, post_sd_control)
+# 
+# #as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
+# 
+# df_first_row_reduced <- df_first_row_reduced %>%
+#   group_by(new_study_id) %>%
+#   slice_head(n = 1) %>%
+#   ungroup()
+# 
+# #create a column in master df that shows 1 if any missing post sds in first_row
+# 
+# df_long_for_metan_with_missing <- df_long_for_metan %>%
+#   left_join(df_first_row_reduced, by = "new_study_id") %>%
+#   mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
+#   select(-post_sd_active, -post_sd_control) %>%
+#   arrange(arm_effect_size, new_study_id)
+# 
+# #all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
+# 
+# df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
+#   filter(missing_post_sd == 0)
+# 
+# n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
+# n_distinct(df_long_for_metan$new_study_id) #88 studies total
+# nrow(df_long_for_metan_without_missing) #140 arms
+# nrow(df_long_for_metan) #203 arms
+# 
+# ##------------ Estimates 
+# 
+# #take study ids where study does not have missing post SD
+# sd_study_ids <-
+#   df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
+# 
+# # use those ids to subset all dataframes in the list
+# list_sd_study <- list()
+# 
+# for(i in 1: length(list_df_simulated)){
+#   
+#   list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+#                                                  %in% sd_study_ids,]
+# }
+# 
+# # count the number of studies
+# study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
+# 
+# # apply the metareg function to the list of clinical studies
+# model_1 <- as.formula(~ four_level_var)
+# list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
+# 
+# # extract coefficients and model characteristics.
+# condition <- levels(list_df_simulated[[1]]$four_level_var)
+# aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
+# 
+# # extract SMDs from the list for clinical studies
+# means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
+# 
+# # calculate mean SMDs and ses
+# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+# coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
+# coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
+# 
+# # add the ns to the dataframe
+# coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>% 
+#                                             ungroup() %>% 
+#                                             select(condition, n),  
+#                                           by = "condition")
+# 
+# #H. Studies with variances <.02-----------------------------
+# 
+# ##-----------Data preparation
+# 
+# #create column with variance in master df
+# df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
+# 
+# #take study ids where variance =2 or less
+# var2_study_ids <-
+#   df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
+# length(var2_study_ids)
+# 
+# ##------------Estimates
+# 
+# # use those ids to subset all dataframes in the list
+# list_var2_study <- list()
+# 
+# for(i in 1: length(list_df_simulated)){
+#   
+#   list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+#                                                %in% var2_study_ids,]
+# }
+# 
+# # count the number of studies
+# study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
+# 
+# # apply the metareg function to the list of clinical studies
+# model_1 <- as.formula(~ four_level_var)
+# list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
+# 
+# # extract coefficients and model characteristics.
+# condition <- levels(list_df_simulated[[1]]$four_level_var)
+# aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
+# 
+# # extract SMDs from the list for clinical studies
+# means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
+# 
+# # calculate mean SMDs and ses
+# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+# coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
+# coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
+# 
+# # add the ns to the dataframe
+# coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>% 
+#                                           ungroup() %>% 
+#                                           select(condition, n),  
+#                                         by = "condition")
+```
 
@@
 ```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# #| label: fig-stab-sims
-# #| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
-# #| fig-cap-location: top
-# 
-# # examine the stability of the simulations
-# 
-# z_psy_con_vs_med_con <- 0
-# for(i in 1: length(list_model_1_meta_reg)){
-# z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
-# 
-# }
-# 
-# stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-# 
-# stab_sims <- stability_sims %>%
-#   ggplot(aes(x = n_sims, y = z_value)) +
-#   geom_point() +
-#   geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-#   geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-#                arrow = arrow(length = unit(0.3, "cm")),
-#                color = "black") +
-#   annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-#   geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
-#                arrow = arrow(length = unit(0.3, "cm")),
-#                color = "black") +
-#   annotate("text", x = 300, y = 7.5, label = "simulated z-values",
-#            hjust = -0.1, vjust = 0) +
-#   theme_minimal() +
-#   labs(
-#     x = "Number of Simulations",
-#     y = "z-value",
-#     title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-#     subtitle = "Results from 1000 simulations with within-group standard errors"
-#   )
-# 
-# print(stab_sims)
+#| label: fig-stab-sims
+#| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
+#| fig-cap-location: top
+
+# examine the stability of the simulations
+
+z_psy_con_vs_med_con <- 0
+for(i in 1: length(list_model_1_meta_reg)){
+z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
+
+}
+
+stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
+
+stab_sims <- stability_sims %>%
+  ggplot(aes(x = n_sims, y = z_value)) +
+  geom_point() +
+  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
+  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
+  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
+               arrow = arrow(length = unit(0.3, "cm")),
+               color = "black") +
+  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
+           hjust = -0.1, vjust = 0) +
+  theme_minimal() +
+  labs(
+    x = "Number of Simulations",
+    y = "z-value",
+    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
+    subtitle = "Results from 1000 simulations with within-group standard errors"
+  )
+
+print(stab_sims)
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
+```{r , warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
 

### 2024-09-22 revision1_reply_to_reviewers.qmd
added cohen's d calculations

--- 2024-08-13 revision1_reply_to_reviewers.qmd
@@
 ---
-title: "revision1_reply_to_reviewers"
-format: docx
-editor: visual
+title: "Comparing Apples and Oranges in Youth Depression Treatments? A Quantitative Critique of the Evidence Base and Guidelines"
+subtitle: "Major Revision: Letter to Reviewers"
+format: 
+  docx:
+    fig-width: 9
+    fig-height: 7
+    fig_caption: true
+    tbl_caption: true
+    number-sections: true
+fig-cap-location: top
 ---
+
+```{r, include=FALSE}
+library(tidyverse)
+library(truncnorm)
+library(metafor)
+library(meta)
+library(kableExtra)
+library(flextable)
+library(magrittr)
+library(officer)
+library(RefManageR)
+library(ftExtra)
+library(dplyr)
+library(broom)
+library(effsize)
+library(here)
+
+#set source
+load("my_environment.RData") #image that contains objects after main qmd has been run
+```
 
@@
 
-This is to not unduly bias the results. We now present the analyses with all studies included in the Supplemental Materials.
+This is to not unduly bias the results. We now present the analyses with all studies included in the Supplemental Materials (see @tbl-all-studies-percfemale-results).
 
 ```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-
 #| label: tbl-all-studies-percfemale-results
@@
 
-```{r, warning=F}
+```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"} #  #}
 
@@
     color = "Type of Study",
-    size = "Baseline n"
-  ) +
+    size = "Baseline n") +
     scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
@@
         axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  )
+        axis.title.y = element_blank())
 ```
@@
 
-```{r, warning=F}
-
-df_long_for_metan %>%
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
+mean_diff_min_max_scores <- df_long_for_metan %>% 
   filter(arm_effect_size == "cohens_d_control") %>% 
@@
   ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) + 
-  geom_jitter(width = 0.2) + # Add jitter to points
+  geom_jitter(width = 0.2) + 
   ggtitle("Post-Pre Differences in Mean Min-Max Scores") + 
@@
   xlab("Type of Study") +
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + # Customize x-axis labels
-  theme_minimal()
+  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) +   theme_minimal()
+
+print(mean_diff_min_max_scores) 
+png("mean_diff_min_max_scores.png")
+mean_diff_min_max_scores 
+dev.off()
 
@@
 
-```{r, warning=F}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 # create baseline variances
@@
 
-df_long_for_metan %>%
+plot_baseline_var <- df_long_for_metan %>% 
   filter(arm_effect_size == "cohens_d_control") %>% 
   mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) +
-  geom_jitter(width = 0.2) + # Add jitter to points
+  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) + geom_jitter(width = 0.2) +  
   ggtitle("Post-Pre Differences in Study Baseline Variances") + 
@@
   xlab("Type of Study") + 
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + # Customize x-axis labels
-  theme_minimal()
+  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + theme_minimal()
+
+print(plot_baseline_var)
+png("plot_baseline_var.png")
+plot_baseline_var 
+dev.off()
 
@@
 ```{r, warning=F}
-
 #| label: fig-plot-means-var2
@@
 coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>% 
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
+  mutate(
+    condition = case_when(condition == "medication_control" ~ "Medication Control", condition == "medication_active" ~ "Medication Active", condition == "psychotherapy_control" ~ "Psychotherapy Control",
+condition == "psychotherapy_active" ~ "Psychotherapy Active", TRUE ~ as.character(condition)))
 
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
 plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study)
 print(plot_means_multi_var2)
-
-# png("plot_means_multi_var2.png")
-# plot_means_multi_var2
-# dev.off()
+png("plot_means_multi_var2.png")
+plot_means_multi_var2 # # dev.off() #  #
 
@@
 
-```{r, warning=F}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 #| label: fig-plot-means-var2
@@
 
-```{r, warning=F}
+```{r, warning=FALSE, message = FALSE, echo=FALSE}
 

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
added cohen's d calculations

@@
 
+```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
+
+mean_psych_overall <- 0.37
+mean_med_overall <- 0.42
+se_psych_overall <- 0.02
+se_med_overall <- 0.01
+n_psych_overall <- 49
+n_med_overall <- 31
+
+# Calculate standard deviation
+sd_psych_overall <- se_psych_overall * sqrt(n_psych_overall)
+sd_med_overall <- se_med_overall * sqrt(n_med_overall)
+
+#formula with pooled sd
+pooled_sd_overall <- sqrt(((sd_psych_overall^2 + sd_med_overall^2)/2))
+
+# Calculate Cohen's d
+cohens_d_overall <- (mean_psych_overall - mean_med_overall) / pooled_sd_overall
+
+## without subclinical
+
+mean_psych_sub <- 0.39
+mean_med_sub <- 0.42
+se_psych_sub <- 0.02
+se_med_sub <- 0.01
+n_psych_sub <- 41
+n_med_sub <- 31
+
+# Calculate standard deviation
+sd_psych_sub <- se_psych_sub * sqrt(n_psych_sub)
+sd_med_sub <- se_med_sub * sqrt(n_med_sub)
+
+#formula with pooled sd
+pooled_sd_sub <- sqrt(((sd_psych_sub^2 + sd_med_sub^2)/2))
+
+# Calculate Cohen's d
+cohens_d_sub <- (mean_psych_sub - mean_med_sub) / pooled_sd_sub
+cohens_d_sub
+cohens_d_overall
+```
+
 ### Baseline severity
@@
 
-As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = ``` r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2) ```) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
 
-# instances_count <- df_descr_psy_conditions_no_wl %>%
-#   filter(!is.na(total_hours)) %>%
-#   group_by(new_study_id, total_hours) %>%
-#   summarise(count = n()) %>%
-#   filter(count > 1) %>%
-#   summarise(total_instances = n())
+instances_count <- df_descr_psy_conditions_no_wl %>%
+  filter(!is.na(total_hours)) %>%
+  group_by(new_study_id, total_hours) %>%
+  summarise(count = n()) %>%
+  filter(count > 1) %>%
+  summarise(total_instances = n())
 

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Added tau squ for level 1 and 2

@@
   df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  tau_sq <- rep(NA, n_models)
+  tau_sq_1 <- rep(NA, n_models)
+  tau_sq_2 <- rep(NA, n_models)
   qe <- rep(NA, n_models)
@@
     model <- list_model_1_meta_reg[[i]]
-    tau_sq[i] <- model$tau2
+    tau_sq_1[i] <- model$sigma2[1]
+    tau_sq_2[i] <- model$sigma2[2]
     qe[i] <- model$QE
@@
     upper_ci = colMeans(df_upper_ci, na.rm = TRUE),
-    tau_sq = mean(tau_sq, na.rm = TRUE),
+    tau_sq_1 = mean(tau_sq_1, na.rm.= TRUE),
+    tau_sq_2 = mean(tau_sq_2, na.rm.= TRUE),
     qe = mean(qe, na.rm = TRUE),

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Added function to extract multilevel I2

@@
 
+###########8. Function for extracting multilevel I2 estimates
+
+extract_i2_values <- function(list_of_models) {
+  # Initialize vectors to store I2 values
+  i2_level2 <- numeric(length(list_of_models))
+  i2_level3 <- numeric(length(list_of_models))
+
+  # Loop through each fitted model from the list
+  for (i in seq_along(list_of_models)) {
+    model <- list_of_models[[i]]
+
+    # Calculate variance distribution using the existing function
+    i2_results <- dmetar::var.comp(model)
+
+    # Extract I2 values for level 2 and level 3 from the results
+    i2_level2[i] <- as.numeric(i2_results$results$I2[2]) # I2 for level 2
+    i2_level3[i] <- as.numeric(i2_results$results$I2[3]) # I2 for level 3
+  }
+
+  # Combine I2 values into a data frame
+  i2_data <- data.frame(
+    i2_level2 = i2_level2,
+    i2_level3 = i2_level3
+  )
+
+  return(i2_data)
+}
+
 ```
@@
                                     by = "condition")
+
+# Extract I2 values for each dataset
+i2_results_all <- extract_i2_values(list_model_1_meta_reg)
+
+# Calculate the mean and standard deviation of I2 values for each level
+i2_summary_all <- data.frame(
+  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
+  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
+  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
+  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
+)
+
 ```

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
Added t2 and i2 to metaregression table

@@
 )
-
 ```
@@
 ```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
-# # B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-# #  grab ids for those studies
-# cbt_fluox_esc_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-# 
-# # Use those ids to subset all dataframes in the list
-# # By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox. 
-# # So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria. 
-# # This leaves all the control conditions from trials where the active is cbt, fluox or esc. 
-# # We may have multiple controls per study id for this reason, though this isn't a problem 
-# # conceptually.
-# 
-# list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-#   df %>%
-#     filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-#     filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-# })
-# 
-# # count the number of studies
-# cbt_fluox_esc_study <- df_long_for_metan %>%
-#   filter(new_study_id %in% cbt_fluox_esc_study_ids,
-#          !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt")))) 
-# study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# # CB checked, looks good now.
-# 
-# # apply the metareg function to the list of cbt, fluox, esc
-# model_1 <- as.formula(~ four_level_var)
-# list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated[[1]]$four_level_var)
-# aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-# aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-# 
-# # extract SMDs from the list for cbt fluox escit
-# means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-# coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
-#  coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-# 
-# # add the ns to the dataframe
-# coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>% 
-#                                         ungroup() %>% 
-#                                       select(condition, n),  
-#                                     by = "condition")
+# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
+#  grab ids for those studies
+cbt_fluox_esc_study_ids <-
+  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
+
+# Use those ids to subset all dataframes in the list
+# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox.
+# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria.
+# This leaves all the control conditions from trials where the active is cbt, fluox or esc.
+# We may have multiple controls per study id for this reason, though this isn't a problem
+# conceptually.
+
+list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
+  df %>%
+    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
+    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+})
+
+# count the number of studies
+cbt_fluox_esc_study <- df_long_for_metan %>%
+  filter(new_study_id %in% cbt_fluox_esc_study_ids,
+         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
+study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
+# CB checked, looks good now.
+
+# apply the metareg function to the list of cbt, fluox, esc
+model_1 <- as.formula(~ four_level_var)
+list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
+aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
+
+# extract SMDs from the list for cbt fluox escit
+means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
+ coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
+
+# add the ns to the dataframe
+coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>%
+                                        ungroup() %>%
+                                      select(condition, n),
+                                    by = "condition")
 ```
@@
 # Filter the dataframe
-filtered_df <- df_long_for_metan %>%
-  filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
-
-# Count the occurrences of each type
-type_counts <- filtered_df %>%
-  count(type) %>%
-  mutate(total_count = sum(n),
-         wl_sum = sum(n[type == "wl"]),
-         wl_percentage = wl_sum / total_count * 100)
-
-# how many examples of matching of active and control in number of hours
-
-instances_count <- df_descr_psy_conditions_no_wl %>%
-  filter(!is.na(total_hours)) %>%
-  group_by(new_study_id, total_hours) %>%
-  summarise(count = n()) %>%
-  filter(count > 1) %>%
-  summarise(total_instances = n())
+# filtered_df <- df_long_for_metan %>%
+#   filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
+# 
+# # Count the occurrences of each type
+# type_counts <- filtered_df %>%
+#   count(type) %>%
+#   mutate(total_count = sum(n),
+#          wl_sum = sum(n[type == "wl"]),
+#          wl_percentage = wl_sum / total_count * 100)
+# 
+# # how many examples of matching of active and control in number of hours
+# 
+# instances_count <- df_descr_psy_conditions_no_wl %>%
+#   filter(!is.na(total_hours)) %>%
+#   group_by(new_study_id, total_hours) %>%
+#   summarise(count = n()) %>%
+#   filter(count > 1) %>%
+#   summarise(total_instances = n())
 
@@
 
+#add i2 to aggregate results
+aggregate_results_overall_i2 <- cbind(aggregate_results_overall, 
+                                   i2_2 = rep(i2_summary_all$mean_i2_level2, nrow(aggregate_results_overall)),
+                                   i2_3 = rep(i2_summary_all$mean_i2_level3, nrow(aggregate_results_overall)))
+
 # Regression results
 
-aggregate_results_overall <- aggregate_results_overall %>%
+aggregate_results_overall_i2 <- aggregate_results_overall_i2 %>%
   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2_1", "T2_2", "QE", "k", "I2_2", "I2_3")
 
@@
   autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
-                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
-                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "T2_2"],
+                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "I2_3"], 
+                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "I2_2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"], "."), colwidths = 6) %>%
   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
@@
 ```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
-# # G. Post SD Sensitivity Analysis ---------------------------------------
-# 
-# ##--------- Data preparation
-# 
-# #For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-# 
-# #create subset of first_row
-# 
-# df_first_row <- read.csv(here("df_first_row.csv"))
-# 
-# #create new_study_ids to match master dataset
-# df_first_row  <- df_first_row  %>%
-#   mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-#                                   .default = study ))
-# 
-# df_first_row_reduced <- df_first_row %>%
-#   filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-#   select(new_study_id, post_sd_active, post_sd_control)
-# 
-# #as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-# 
-# df_first_row_reduced <- df_first_row_reduced %>%
-#   group_by(new_study_id) %>%
-#   slice_head(n = 1) %>%
-#   ungroup()
-# 
-# #create a column in master df that shows 1 if any missing post sds in first_row
-# 
-# df_long_for_metan_with_missing <- df_long_for_metan %>%
-#   left_join(df_first_row_reduced, by = "new_study_id") %>%
-#   mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-#   select(-post_sd_active, -post_sd_control) %>%
-#   arrange(arm_effect_size, new_study_id)
-# 
-# #all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-# 
-# df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-#   filter(missing_post_sd == 0)
-# 
-# n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-# n_distinct(df_long_for_metan$new_study_id) #88 studies total
-# nrow(df_long_for_metan_without_missing) #140 arms
-# nrow(df_long_for_metan) #203 arms
-# 
-# ##------------ Estimates 
-# 
-# #take study ids where study does not have missing post SD
-# sd_study_ids <-
-#   df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-# 
-# # use those ids to subset all dataframes in the list
-# list_sd_study <- list()
-# 
-# for(i in 1: length(list_df_simulated)){
-#   
-#   list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-#                                                  %in% sd_study_ids,]
-# }
-# 
-# # count the number of studies
-# study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-# 
-# # apply the metareg function to the list of clinical studies
-# model_1 <- as.formula(~ four_level_var)
-# list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated[[1]]$four_level_var)
-# aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-# 
-# # extract SMDs from the list for clinical studies
-# means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-# coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-# coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-# 
-# # add the ns to the dataframe
-# coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>% 
-#                                             ungroup() %>% 
-#                                             select(condition, n),  
-#                                           by = "condition")
-# 
-# #H. Studies with variances <.02-----------------------------
-# 
-# ##-----------Data preparation
-# 
-# #create column with variance in master df
-# df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-# 
-# #take study ids where variance =2 or less
-# var2_study_ids <-
-#   df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-# length(var2_study_ids)
-# 
-# ##------------Estimates
-# 
-# # use those ids to subset all dataframes in the list
-# list_var2_study <- list()
-# 
-# for(i in 1: length(list_df_simulated)){
-#   
-#   list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-#                                                %in% var2_study_ids,]
-# }
-# 
-# # count the number of studies
-# study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-# 
-# # apply the metareg function to the list of clinical studies
-# model_1 <- as.formula(~ four_level_var)
-# list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated[[1]]$four_level_var)
-# aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-# 
-# # extract SMDs from the list for clinical studies
-# means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-# coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-# coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-# 
-# # add the ns to the dataframe
-# coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>% 
-#                                           ungroup() %>% 
-#                                           select(condition, n),  
-#                                         by = "condition")
+# G. Post SD Sensitivity Analysis ---------------------------------------
+
+##--------- Data preparation
+
+#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
+
+#create subset of first_row
+
+df_first_row <- read.csv(here("df_first_row.csv"))
+
+#create new_study_ids to match master dataset
+df_first_row  <- df_first_row  %>%
+  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
+                                  .default = study ))
+
+df_first_row_reduced <- df_first_row %>%
+  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
+  select(new_study_id, post_sd_active, post_sd_control)
+
+#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
+
+df_first_row_reduced <- df_first_row_reduced %>%
+  group_by(new_study_id) %>%
+  slice_head(n = 1) %>%
+  ungroup()
+
+#create a column in master df that shows 1 if any missing post sds in first_row
+
+df_long_for_metan_with_missing <- df_long_for_metan %>%
+  left_join(df_first_row_reduced, by = "new_study_id") %>%
+  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
+  select(-post_sd_active, -post_sd_control) %>%
+  arrange(arm_effect_size, new_study_id)
+
+#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
+
+df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
+  filter(missing_post_sd == 0)
+
+n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
+n_distinct(df_long_for_metan$new_study_id) #88 studies total
+nrow(df_long_for_metan_without_missing) #140 arms
+nrow(df_long_for_metan) #203 arms
+
+##------------ Estimates
+
+#take study ids where study does not have missing post SD
+sd_study_ids <-
+  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
+
+# use those ids to subset all dataframes in the list
+list_sd_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                                 %in% sd_study_ids,]
+}
+
+# count the number of studies
+study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
+coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
+
+# add the ns to the dataframe
+coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
+                                            ungroup() %>%
+                                            select(condition, n),
+                                          by = "condition")
+
+#H. Studies with variances <.02-----------------------------
+
+##-----------Data preparation
+
+#create column with variance in master df
+df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
+
+#take study ids where variance =2 or less
+var2_study_ids <-
+  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
+length(var2_study_ids)
+
+##------------Estimates
+
+# use those ids to subset all dataframes in the list
+list_var2_study <- list()
+
+for(i in 1: length(list_df_simulated)){
+
+  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
+                                               %in% var2_study_ids,]
+}
+
+# count the number of studies
+study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
+
+# apply the metareg function to the list of clinical studies
+model_1 <- as.formula(~ four_level_var)
+list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
+
+# extract coefficients and model characteristics.
+condition <- levels(list_df_simulated[[1]]$four_level_var)
+aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
+
+# extract SMDs from the list for clinical studies
+means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
+
+# calculate mean SMDs and ses
+condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
+coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
+coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
+
+# add the ns to the dataframe
+coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
+                                          ungroup() %>%
+                                          select(condition, n),
+                                        by = "condition")
 ```

### 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
final analyses before revision submission

@@
     # Calculate variance distribution using the existing function
-    i2_results <- dmetar::var.comp(model)
+    i2_results <- var.comp(model)
 
@@
 
- png("plot_means_multi_all.png")
- plot_means_multi_all
- dev.off()
 ```
@@
 # Assign new column names to the data frame
-colnames(aggregate_results_overall) <- new_column_names
-
-table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
-table_aggregate_results_overall[1, 4] <- NA
-
-flextable(table_aggregate_results_overall) %>%
+colnames(aggregate_results_overall_i2) <- new_column_names
+
+table_aggregate_results_overall_i2 <- aggregate_results_overall_i2[, 1:6]
+table_aggregate_results_overall_i2[1, 4] <- NA
+
+flextable(table_aggregate_results_overall_i2) %>%
   set_table_properties(width = 1) %>%
   autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "T2_2"],
-                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall[1, "I2_3"], 
-                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall[1, "I2_2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"], "."), colwidths = 6) %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "T2_2"],
+                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "I2_3"], 
+                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "I2_2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall_i2[1, "k"], "."), colwidths = 6) %>%
   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
+  align(j = 2:ncol(table_aggregate_results_overall_i2), align = "center", part = "all") %>% 
   align(j = 1, align = "left", part = "all") %>% 

### 2024-09-23 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
changed dimensions for plots for word

@@
 
-list_df_simulated[[1]] %>%
+plot_smd_diff_control <- list_df_simulated[[1]] %>%
   filter(arm_effect_size == "cohens_d_control") %>%
@@
 
+print(plot_smd_diff_control)
+
+png("plot_smd_diff_control.png", width=6.5, height=4, units="in", res=300)
+ plot_smd_diff_control
+ dev.off()
+
 ```
@@
 
- png("plot_means_multi_all.png")
+ png("plot_means_multi_all.png", width=6.5, height=4, units="in", res=300)
  plot_means_multi_all
@@
 print(mean_diff_min_max_scores) 
-png("mean_diff_min_max_scores.png")
+png("mean_diff_min_max_scores.png", width=6.5, height=4, units="in", res=300)
 mean_diff_min_max_scores
@@
 print(plot_baseline_var)
-png("plot_baseline_var.png")
+png("plot_baseline_var.png", width=6.5, height=4, units="in", res=300)
 plot_baseline_var
@@
 
- png("plot_means_multi_no_wl.png")
+ png("plot_means_multi_no_wl.png", width=6.5, height=4, units="in", res=300)
 plot_means_no_wl
@@
 
-png("plot_means_multi_clin.png")
+png("plot_means_multi_clin.png", width=6.5, height=4, units="in", res=300)
 plot_means_clin
@@
 
- png("plot_means_multi_cdrs.png")
+ png("plot_means_multi_cdrs.png", width=6.5, height=4, units="in", res=300)
  plot_means_cdrs
@@
 
- png("plot_means_multi_hamd.png")
+ png("plot_means_multi_hamd.png", width=6.5, height=4, units="in", res=300)
  plot_means_multi_hamd
@@
 
- png("plot_means_multi_sd.png")
+ png("plot_means_multi_sd.png", width=6.5, height=4, units="in", res=300)
  plot_means_multi_sd
@@
 
- png("plot_means_multi_var2.png")
+ png("plot_means_multi_var2.png", width=6.5, height=4, units="in", res=300)
  plot_means_multi_var2

### 2024-09-23 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
fixed figures

@@
 
- png("plot_means_multi_all.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_all.png", width=6.5, height=6, units="in", res=300)
  plot_means_multi_all
@@
 
- png("plot_means_multi_no_wl.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_no_wl.png", width=6.5, height=6, units="in", res=300)
 plot_means_no_wl
@@
 
-png("plot_means_multi_clin.png", width=6.5, height=4, units="in", res=300)
+png("plot_means_multi_clin.png", width=6.5, height=6, units="in", res=300)
 plot_means_clin
@@
 
- png("plot_means_multi_cdrs.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_cdrs.png", width=6.5, height=6, units="in", res=300)
  plot_means_cdrs
@@
 
- png("plot_means_multi_hamd.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_hamd.png", width=6.5, height=6, units="in", res=300)
  plot_means_multi_hamd
@@
 
- png("plot_means_multi_sd.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_sd.png", width=6.5, height=6, units="in", res=300)
  plot_means_multi_sd
@@
 
- png("plot_means_multi_var2.png", width=6.5, height=4, units="in", res=300)
+ png("plot_means_multi_var2.png", width=6.5, height=6, units="in", res=300)
  plot_means_multi_var2

### 2024-10-04 multilevel_metaregres_text.qmd
saving test files

--- 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
@@
 ---
-title: "Comparing Apples and Oranges in Youth Depression Treatments?"
-subtitle: "A Quantitative Critique of the Evidence Base and Guidelines"
-author:
-  - name: Argyris Stringaris
-    email: a.stringaris@ucl.ac.uk
-    affiliations: 
-        - id: ucl_1
-          name: University College London
-          department: Divisions of Psychiatry and Psychology and Language Science
-          address: 1-19 Torrington Place
-          city: London, UK
-          state: 
-          postal-code: WC1E 7HB
-          country: United Kingdom
-    attributes:
-        corresponding: true
-    note: 
-  - name: Charlotte Burman
-    email: charlotte.burman@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-  - name: Raphaelle Delpech
-    email: raphaelle.delpech.18@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Rudolf Uher
-    email: uher@Dal.Ca
-    affiliations:
-        - id: dal
-          name: Dalhousie University
-          department: Department of Psychiatry
-          address: 
-          city: Nova Scotia
-          state: 
-          postal-code: 
-          country: Canada
-  - name: Dayna Bhudia
-    email: dayna.bhudia@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Despoina Miliou
-    email: dgmiliou@outlook.com.gr
-    affiliations:
-        - ref: ucl_1
-  - name: Ioannis-Marios Rokas
-    email: rokasgiannis93@gmail.com
-    affiliations:
-        - ref: ucl_1
-  - name: Marinos Kyriakopoulos
-  - name: Lucy Foulkes
-    email: lucy.foulkes@psych.ox.ac.uk
-    affiliations:
-        - id: OU
-          name: University of Oxford
-          department: Experimental Psychology
-          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
-          city: Oxford
-          postal-code: OX2 6GG
-          country: United Kingdom
-    note:
-  - name: Carmen Moreno
-    email: cmoreno@hggm.es
-    affiliations:
-        - id: HGM
-          name: Hospital Gregorio Marañón
-          department: Department of Psychiatry
-          address: 46 C. del Dr. Esquerdo
-          city: Madrid
-          state:
-          postal-code: 28007
-          country: Spain
-  - name: Samuele Cortese
-    email: samuele.cortese@soton.ac.uk
-    affiliations:
-        - id: soton
-          name: University of Southampton
-          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
-          address: Highfield Campus, Building 44
-          city: Southampton
-          state:
-          postal-code: SO17 1BJ
-          country: United Kingdom
-  - name: Glyn Lewis
-    email: glyn.lewis@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1        
-  - name: Georgina Krebs
-    email: g.krebs@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-keywords: 
-  - depression
-  - adolescents
-  - antidepressants
-  - psychotherapy
-date: last-modified
-format:
-  docx:
-    reference-doc: "bibliography/word-style-reference-doc.docx"
-    fig-width: 9
-    fig-height: 7
-    fig_caption: yes
-    tbl_caption: yes
-    number-sections: true
-execute: 
-  echo: true
-  auto: true
-  warning: FALSE
-bibliography: "bibliography/references.bib"
-csl: "bibliography/vancouver_style.csl"
-font:
-  family: Calibri
-fig-cap-location: top
+title: "section_for_multi_level_metareg"
+format: html
+editor: visual
 ---
 
-##
+###
 
-------------------------------------------------------------------------
-
-------------------------------------------------------------------------
-
-```{r library, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
-
-###########Libraries needed
-library(tidyverse)
-library(truncnorm)
-library(metafor)
-library(meta)
-library(kableExtra)
-library(flextable)
-library(magrittr)
-library(officer)
-library(RefManageR)
-library(ftExtra)
-library(dplyr)
-library(broom)
-library(effsize)
-library(here)
-
-#setting paths using here package
-here::here()
-
-# For referencing
-bib_data <- ReadBib(here("multilevel_metaregression", "bibliography", "references.bib"))
-
-```
-
-```{r global_options, include=FALSE}
-
-knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
-```
-
-# Abstract
-
-**Objectives:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
-In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
-**Methods:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-Using meta-analyses, we compared a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
-Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
-**Results:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
-There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.70)) vs psychotherapy controls (SMD=-0.5 (95% CI: -0.75 to -0.25)).
-Within psychotherapy RCTs, control conditions were less intensive on average than active conditions.
-**Conclusions:** Medication and psychotherapy RCTs differ on fundamental participant and methodological characteristics, thereby violating key conditions for valid comparison between them.
-Psychotherapy controls often involve little therapist contact and are easy-to-beat comparators.
-These findings cast doubt on the confidence with which psychotherapy is recommended for youth depression, and highlight the pressing need to improve the evidence base.
-
-# Key messages
-
-Psychotherapy is recommended before medication for most cases of depression in children and adolescents, a recommendation that is based on indirect comparisons of outcomes from randomised controlled trials (RCTs) within each treatment modality.
-We examine the validity of these inferences by scrutinising the comparability of psychotherapy and medication RCTs.
-We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the within-group effect sizes of medication controls (i.e.
-pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
-We also examine the quality of controls used in psychotherapy RCTs and find that they are poorly matched to active intervention arms in ways such as human contact hours, and hence represent poor and easy to beat comparators.
-Our findings underscore the need for a higher quality evidence base upon which to base treatment guidelines and clinical decision making.
-
-# Background
-
-Should a child or an adolescent receive psychotherapy or medication for their depression, and what information should be used to guide decision-making?
-
-For adolescent depression, there are limited head-to-head trials of medication and psychotherapy, and hence recommendations are derived from indirect comparisons of treatment efficacy.
-The National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend psychotherapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
-This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
-However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
-treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
-pill placebo) or psychotherapy controls.
-The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
-Also, the addition of psychotherapy to standard care did not improve outcomes [@goodyer_randomised_2008].
-Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
-
-In this paper, we examine whether the existing evidence for adolescent depression treatments can offer valid answers to this question.
-We provide a conceptual framework and test a series of hypotheses using data from existing trials.
-Two points are crucial to indirect comparisons of treatment modalities.
-First, whether the participants in trials are comparable across modalities.
-Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
-
-Starting with the first point, comparison between different trials assumes that they sample from the same population.
-If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
-
-The assumption that medication and psychotherapy trials sample from the same population may not be valid as patients and parents often have treatment preferences [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
-Moreover, treatment preferences correlate with clinically-relevant participant characteristics, including severity and sex.
-Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and if they differ across psychotherapy and medication trials they may confound comparisons.
-
-Regarding the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the "cutting edge" treatment, whilst those in the control are dissatisfied for having missed out (i.e.
-"disappointment bias" [@reltonEthicsTrialsCohorts2017].
-By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022], suggesting that expectancy effects are well-matched across conditions.
-Since expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011], if expectancy differs between medication and psychotherapy trials, comparisons between them, including in NMA, become questionable.
-
-Another difference in design is the number of trial sites.
-The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011; @meisterPlaceboResponseRates2020].
-This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
-
-An inter-related issue concerns the effect of control conditions.
-Often psychotherapy and medication are compared on the basis of their respective effect sizes (i.e.
-differences between the active and control conditions for each modality).
-For these to be comparable, medication and psychotherapy controls ought to be equal in their effects.
-Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% versus 60% and another from a difference of 40% versus 0% (i.e.
-from different points of reference).
-
-Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention [@guoChapterCounterfactualFramework2014]: what would have been the outcome had an individual not received the intervention, with all else being equal.
-Pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
-In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g.
-in number of hours of therapist contact).
-
-# Objective
-
-In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-We hypothesise that there are substantial differences between psychotherapy and medication RCTs, making their comparison problematic, which we examine in the following ways.
-First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline depression severity; b) percentage females; and c) mean age.
-Second, we examine trial characteristics including the efficacy of the control arms, using random-effects meta-regression, and the number of trial sites.
-Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
-
-# Study selection and analysis
-
-The study protocol was registered on the Open Science Framework (OSF) and can be found at <https://osf.io/bfmc6>.
-
-A detailed description of our methods, including formalisms on which analyses are based, can be found in the Supplement.
-
-## Included studies
-
-We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
-For the psychotherapy trials, we utilised open data from the previous meta-analysis (see <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
-For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
-
-For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and one author completed data extraction for these papers (see @fig-prisma for PRISMA diagram).
-
-## Statistical analysis
-
-### Sample characteristics
-
-We conducted random-effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms, sex and age.
-Meta-analyses were implemented using R's meta package.
-
-### Trial design
-
-#### Measures of effect
-
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression scale used (selected according to the hierarchy defined in the Supplement).
-
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023].
-
-For meta-analysis it is necessary to estimate a standard error of the SMD.
-This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation [@cuijpers_pre-post_2017], we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
-
-#### Multilevel model metaregression
-
-We estimated pooled SMDs for each arm by using multilevel models implemented in R's metafor package.
-
-We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
-The SMDs are the means across the 1000 simulated datasets.
-
-#### Number of sites
-
-We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
-
-### Sensitivity analyses
-
-```{r set-up-z, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
-# my alpha for the z 
-target_probability <- 1 - 0.05
-
-#start here 
-x <- 1
-
-# two decimals should be fine
-tolerance <- 1e-3
-
-#find the z value using the pnorm function
-while (abs(pnorm(x)) < target_probability ) {
-  x <- x + tolerance  
-}
-
-# Adjust the step size based on your problem  
-cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
-
-x
-
-```
-
-We conducted a series of sensitivity analyses where we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
-Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
-Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
-We plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
-
-Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
-
-### Comparing the control and active arms of psychotherapy trials
-
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions: the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
-
-```{r define-functions, warning=FALSE, message = FALSE, echo=FALSE}
-#############Some custom made functions#############
-
-###### 1. Simulation Function for SEs
-simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
-                                                                                              # of unique ids to which a correlation coef
-                                                                                              # is allocated.
-  set.seed(seed)
-
-  # Empty list to store simulated dfs
-  list_df_simulated <- list()
-
-  for (i in 1:num_repetitions) {
-    # Simulate the vector
-    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations
-
-    # Create a copy of the original dataframe
-    df_simulated_copy <- df
-
-    # Add/update the sims column
-    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]
-
-    # Remove duplicated columns
-    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]
-
-    # Calculate the ses
-    df_simulated_copy <- df_simulated_copy %>% 
-      group_by(new_study_id, baseline_n) %>% 
-      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
-                                   (cohens_d^2/(2*baseline_n))))
-
-    # Add the simulated dataframe to the list
-    list_df_simulated[[i]] <- df_simulated_copy
-  }
-
-  return(list_df_simulated)
-}
-
-###############2. Simulation function for multilevel metaregression
-
-  run_multi_metaregression <- function(list_of_datasets, model_formula) {
-    list_model_meta_reg <- list()
-
-    for (i in seq_along(list_of_datasets)) {
-      # Check if required columns are present
-      if(!all(c("cohens_d", "simulated_se", "new_study_id", "arm_id") %in% names(list_of_datasets[[i]]))) {
-        stop("Dataset is missing one or more required columns: 'cohens_d', 'simulated_se', 'new_study_id', 'arm_id'")
-      }
-
-      # Fit the meta-regression model
-      list_model_meta_reg[[i]] <- metafor::rma.mv(yi = cohens_d,
-                                                  V = simulated_se^2,
-                                                  random = ~ 1 | new_study_id/arm_id,
-                                                  # this is where 
-                                                  # we specify the random
-                                                  # effect structure
-                                                  data = list_of_datasets[[i]],
-                                                  method = "ML",
-                                                  mods = model_formula,
-                                                  # here we specify the 
-                                                  # fixed effects as before
-                                                  test = "knha")
-    }
-
-    return(list_model_meta_reg)
-  }
-
-#########3. Function to count studies with missingness etc.
-
-count_studies <- function(df) {
-  df_count_studies <- df %>%
-    group_by(psy_or_med, arm_effect_size) %>%
-    count(is.na(cohens_d)) %>%
-    rename(is_missing = `is.na(cohens_d)`) %>%
-    mutate(
-      condition = case_when(
-        psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-        psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-        psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-        psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control"
-      )
-    )
-
-  df_count_studies$condition <- factor(df_count_studies$condition)  # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
-
-  return(df_count_studies)
-}
-
-##########4. Function to extract mean coefficients and to extract model characteristics
-
-aggregate_model_results <- function(list_model_1_meta_reg, condition) {
-  n_models <- length(list_model_1_meta_reg)
-  n_conditions <- length(condition)
-
-  df_coefs <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_se <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_z_value <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_lower_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  tau_sq_1 <- rep(NA, n_models)
-  tau_sq_2 <- rep(NA, n_models)
-  qe <- rep(NA, n_models)
-  k <- rep(NA, n_models)
-
-  for (i in seq_len(n_models)) {
-    model <- list_model_1_meta_reg[[i]]
-    tau_sq_1[i] <- model$sigma2[1]
-    tau_sq_2[i] <- model$sigma2[2]
-    qe[i] <- model$QE
-    k[i] <- model$k
-    coefs <- model$beta
-    ses <- model$se
-    zvals <- model$zval
-    lower_ci <- model$ci.lb
-    upper_ci <- model$ci.ub
-
-    for (j in seq_len(n_conditions)) {
-      if (!is.null(coefs[j])) {
-        df_coefs[i, j] <- coefs[j]
-        df_se[i, j] <- ses[j]
-        df_z_value[i, j] <- zvals[j]
-        df_lower_ci[i, j] <- lower_ci[j]
-        df_upper_ci[i, j] <- upper_ci[j]
-      }
-    }
-  }
-
-  df_coefficients_model <- data.frame(
-    coefficients = colMeans(df_coefs, na.rm = TRUE),
-    se = colMeans(df_se, na.rm = TRUE),
-    z_value = colMeans(df_z_value, na.rm = TRUE),
-    lower_ci = colMeans(df_lower_ci, na.rm = TRUE),
-    upper_ci = colMeans(df_upper_ci, na.rm = TRUE),
-    tau_sq_1 = mean(tau_sq_1, na.rm.= TRUE),
-    tau_sq_2 = mean(tau_sq_2, na.rm.= TRUE),
-    qe = mean(qe, na.rm = TRUE),
-    k = mean(k, na.rm = TRUE)
-  )
-
-  return(df_coefficients_model)
-}
-
-###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy variable. The output is used below in 5.
-# it is a slightly awkward one, because I couldn't' come up with a better way to add the intercept to each coefficient
-# given the named output of the built in coef function. here I extract the coefficients
-
-extract_coefficients_func <- function(df_with_coefs){
-  list_coefs <- list()
-  coefs <- 0
-  coefficient_output <- 0
-
-  for(i in 1: length(coefficients(df_with_coefs))){
-
-    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
-                         length(coefficients(df_with_coefs)) - 1 ))
-    coefs[i] <- coef(df_with_coefs)[[i]]
-
-    coefficient_output <- temp_vec + coefs
-
-    st_error_output <- df_with_coefs$se
-
-    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))
-
-    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
-    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
-  }
-  return (df_coefficients )
-}
-
-############5. Function to get the means out of the SMDs (this is similar to Func 3 and I should at some point create one more general one)
-# here the argument list_of_dfs is the list of extracted coefficients that you get out of the extract_coefficients_func
-# which itself you get from the run_metaregression function. The argument conditions refers to the levels of the variable that describes each study arm
-
-calculate_mean_coefs_ses <- function(list_of_dfs, conditions) {
-  df_coefs <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
-  df_se <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
-
-  for (i in 1:length(list_of_dfs)) {
-    for (j in 1:length(conditions)) {
-      df_coefs[i, j] <- list_of_dfs[[i]]$coefficients[j]
-      df_se[i, j] <- list_of_dfs[[i]]$se[j]
-    }
-  }
-
-  df_mean_coefs_ses <- data.frame(
-    coef_means = colMeans(df_coefs),
-    se_means = colMeans(df_se)
-  )
-
-  df_mean_coefs_ses$lower_ci <- df_mean_coefs_ses$coef_means - 1.96 * df_mean_coefs_ses$se_means
-  df_mean_coefs_ses$upper_ci <- df_mean_coefs_ses$coef_means + 1.96 * df_mean_coefs_ses$se_means
-
-  return(df_mean_coefs_ses)
-}
-
-###############6. Function for plotting the SMDs
-plot_means_function <- function(dataframe) {
-  dataframe$text_label <- 0
-
-  for (i in 1:nrow(dataframe)) {
-    dataframe$text_label[i] <- paste(
-      dataframe$condition[i], "\n",
-      round(dataframe$coef_means[i], 2),
-      "[" ,
-      round(dataframe$lower_ci[i], 2), 
-      round(dataframe$upper_ci[i], 2),
-      "]"
-    ) 
-  }
-
-  # Recode condition for ease of plotting
-  dataframe$condition <- str_replace_all(dataframe$condition, "_", " ")
-
-  # Encode colours
-  redish_palette <- c("Medication Control" = "deeppink4", "Medication Active" = "deeppink")
-  blueish_palette <- c("Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-
-  # Plotting
-  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
-                                      colour = condition, label = text_label)) +
-    geom_point(label=dataframe$k) +
-    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
-    geom_text(vjust = +1.5, size = 4.5) +
-    scale_size_continuous(guide = "none") +
-    guides(colour = FALSE) + 
-    scale_color_manual(values = c(redish_palette, blueish_palette)) +
-    theme_minimal() +
-    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
-    ylab("") +
-    ylim(0, nrow(dataframe) + 1) +
-    xlim(-3.0, 0.5) +
-    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey50") +
-    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
-    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey50", vjust = 0.5, hjust = 1, size = 4.5) +
-    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
-    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)+
-    theme(axis.title.x = element_text(size = 12, family  = "Calibri"), 
-          axis.text.x  = element_text(size = 12, family = "Calibri"),
-          axis.text.y = (element_blank()),
-          plot.title = element_text(size = 12, family =  "Calibri", face= "italic"),
-          plot.subtitle = element_text(size = 12, family =  "Calibri", face= "italic")) +
-    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey50", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
-    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)
-
-  return(plot_means)
-}
-
-###########7. Function for baseline SMD results
-library(broom)
-run_metareg_and_extract <- function(dataframe, model_1, condition) {
-  # Run metareg
-  inst_baseline_metareg <- rma(yi = baseline_mean,
-                               sei = baseline_stand_error,
-                               data = dataframe,
-                               method = "ML",
-                               mods = model_1,
-                               test = "knha")
-
-  # Extract coefficients from the list
-  baseline_metareg_results <- tidy(inst_baseline_metareg)
-  baseline_metareg_results$condition <- condition
-  coefs_for_inst_baseline <- tidy(inst_baseline_metareg)$estimate
-
-  # Calculate SMDs
-  smds_for_inst_baseline <- c(coefs_for_inst_baseline[1], coefs_for_inst_baseline[-1] + coefs_for_inst_baseline[1])
-
-  # Calculate upper and lower CIs
-  upper_cis_for_inst_baseline <- smds_for_inst_baseline + 1.96 * tidy(inst_baseline_metareg)$std.error
-  lower_cis_for_inst_baseline <- smds_for_inst_baseline - 1.96 * tidy(inst_baseline_metareg)$std.error
-
-  # Create dataframe with results
-  df_baseline_means_with_cis <- data.frame(
-    baseline_smds = smds_for_inst_baseline,
-    upper_cis_smds = upper_cis_for_inst_baseline,
-    lower_cis_smds = lower_cis_for_inst_baseline,
-    condition = condition
-  )
-
-  # Return the two dataframes
-  return(list(baseline_metareg_results = baseline_metareg_results, df_baseline_means_with_cis = df_baseline_means_with_cis))
-}
-
-###########8. Function for extracting multilevel I2 estimates
-
-extract_i2_values <- function(list_of_models) {
-  # Initialize vectors to store I2 values
-  i2_level2 <- numeric(length(list_of_models))
-  i2_level3 <- numeric(length(list_of_models))
-
-  # Loop through each fitted model from the list
-  for (i in seq_along(list_of_models)) {
-    model <- list_of_models[[i]]
-
-    # Calculate variance distribution using the existing function
-    i2_results <- var.comp(model)
-
-    # Extract I2 values for level 2 and level 3 from the results
-    i2_level2[i] <- as.numeric(i2_results$results$I2[2]) # I2 for level 2
-    i2_level3[i] <- as.numeric(i2_results$results$I2[3]) # I2 for level 3
-  }
-
-  # Combine I2 values into a data frame
-  i2_data <- data.frame(
-    i2_level2 = i2_level2,
-    i2_level3 = i2_level3
-  )
-
-  return(i2_data)
-}
-
-```
-
-```{r import-dataset, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Transforming data ------------------------------------------------------
-# import master dataset
-
-df_appl_v_orange <-readxl::read_excel(here("df_appl_v_orange.xlsx"))
-
-# Here we add in instrument end point values (mins / maxs).
-# We will use these to transform the scale into % as follows: (observed score - min of the scale)/(max-min)
-# We have done this for both means and standard deviations.
-
-df_scale_ranges <- read.csv(here("scale_ranges.csv"))
-df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this is the best way to estimate the SD of the linear transformation of the score 
-  mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_control = baseline_sd_control  / (scale_max - scale_min)) %>% 
-  mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_active = post_sd_active  / (scale_max - scale_min)) %>% 
-  mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_control = post_sd_control  / (scale_max - scale_min))
-
-# Need to use SMDs (ie our Cohen's d) and then use standard error of SMD, to achieve this I need test-retest reliabilities of instruments.
-
-# CDRS reliability taken from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
-# Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
-# Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
-# for the CDRS-R total score in 53 clinic-referred 6- to 12-year-olds.
-
-### A few more tidying things from Argyris before doing meta-analyses
-# Discovered some errors in the percentage women variable. Have gone back and checked. 
-df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1
-df_appl_v_orange[df_appl_v_orange$study=="Clarke, 1995",]$percent_women <-47.3
-df_appl_v_orange[df_appl_v_orange$study=="Moeini, 2019",]$percent_women <-100
-df_appl_v_orange[df_appl_v_orange$study=="Santomauro, 2016",]$percent_women <-40
-
-# Calculate SE for baseline severity --------------------------------------
-
-df_appl_v_orange$baseline_st_error_active <- 
-  df_appl_v_orange$baseline_sd_active/sqrt(df_appl_v_orange$baseline_n_active)
-
-df_appl_v_orange$baseline_st_error_control <-
-  df_appl_v_orange$baseline_sd_control/sqrt(df_appl_v_orange$baseline_n_control)
-
-# Turn into a long database with unique rows ------------------------------
-
-### Important: create a dataset that will have unique control studies (see problem that we identified, namely common control conditions)
-# create new id to help with better identification and work with duplicates (see below) 
-df_appl_v_orange  <- df_appl_v_orange  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-# We are going to use the descr_active and descr_control columns rather than active_type and control_type columns, as these have unique values for each study.
-However the descr columns are empty for med studies, so I'm going to paste values across to fix this error.
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(descr_control = if_else(is.na(descr_control), control_type, descr_control ))
-
-# Step 1: keep only the rows with the top instrument in our hierarchy
-df_with_distinct_instruments <-  df_appl_v_orange %>%          
-  group_by(new_study_id) %>% 
-  filter(instrument_value == min(instrument_value)) # coded for the smallest number to be best.
-
-write.csv(df_with_distinct_instruments, "df_with_distinct_instruments.csv")
-
-# Step 2: turn dataframes to long
-
-# A small bit of cleaning so the code below will work
-
-df_with_distinct_instruments <- df_with_distinct_instruments %>% 
-  rename (percent_women_active = active_percent_women, 
-          percent_women_control = control_percent_women,
-          percent_women_overall = percent_women)
-
-# A: turn long the rows with active
-active_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
-                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
-  rename(treatment = descr_active) %>% 
-  rename(type = active_type) %>% 
-  rename_with(~ str_remove(., "_active")) %>% 
-  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
-  group_by(new_study_id) %>% #go through each study id and remove duplicates
-  distinct(treatment, .keep_all = TRUE)
-
-control_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
-                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
-  rename(treatment = descr_control) %>% 
-  rename(type = control_type) %>% 
-  rename_with(~ str_remove(., "_control")) %>% 
-  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
-  group_by(new_study_id) %>% #go through each study id and remove duplicates
-  distinct(treatment, .keep_all = TRUE)
-
-df_long_for_metan <- rbind(active_df, control_df)
-
-# I'm going to remove the March / TADS psy control row.
-It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist as such (the control is placebo, which is not a psy control).
-
-df_long_for_metan <- df_long_for_metan %>%
-  filter(!(new_study_id == "March, 2004" & is.na(treatment)))
-
-# I'm going to perform  the operations to calculate overall age and percent women here now.
-We just want this per study rather than per arm for the first set of meta-analyses as we are going to compare psy vs med (2 subgroups) rather than the 4 arms
-
-df_long_for_metan <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(n_overall = sum(baseline_n)) %>% 
-  mutate(age_overall = sum(age_m * baseline_n) / sum(baseline_n)) %>% 
-  mutate(mean_age = coalesce(age_overall, age_m_overall)) %>% 
-  mutate(pooled_sd_age = sqrt(sum((age_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(se_age = pooled_sd_age / sqrt(n_overall)) %>% 
-  mutate(sex_overall = sum(percent_women * baseline_n) / sum(baseline_n)) %>% 
-  mutate(percent_women = coalesce(percent_women_overall, sex_overall))
-
-# Now just get rid of the unnecessary columns as these are causing clutter
-
-df_long_for_metan <- df_long_for_metan %>% 
-  select(-c(percent_women_overall, age_m, age_sd, age_m_overall, age_sd_overall, age_overall, sex_overall))
-
-# Remember that these are now per study, not per arm.
-
-# Create SEs proportions for percentage women --------------------------------------------
-
-# We also need to calculate SE for proportion women for the baseline calculations
-# for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
-
-df_long_for_metan <- df_long_for_metan %>% 
-  mutate(product_perc_women = (percent_women/100)* (1-(percent_women/100)) )
-
-df_long_for_metan <- df_long_for_metan %>% 
-  mutate(percent_women_std_error = sqrt(product_perc_women/ n_overall))
-
-# Create unique IDs by arm for multilevel metaregression
-
-df_long_for_metan <- df_long_for_metan %>%
-  group_by(new_study_id) %>%
-  mutate(arm_id = paste0(new_study_id, "_", row_number())) %>%
-  ungroup()
-
-#dim(df_long_for_metan ) #check dimension
-#make sure no study lost
-#length(unique(df_long_for_metan$new_study_id ) ) == # #length(unique(df_appl_v_orange$new_study_id ) )
-
-# Now check again the studies with muliple arms
-# Now checking if this worked with the studies that I used to illustrate the problem above. 
-# df_long_for_metan[df_long_for_metan$new_study_id == "Stallard, 2012",]
-# df_long_for_metan[df_long_for_metan$new_study_id == "Atkinson, 2014",]
-# # also check one which is single to make sure it is kept
-# df_long_for_metan[df_long_for_metan$new_study_id == "Ackerson, 1998",]
-
-# For response rate, recalculating after turning long and doing all the imputations
-
-# df_long_for_metan <- df_long_for_metan %>%
-#   rowwise() %>%
-#   mutate(responders = sum(rnorm(baseline_n, post_mean, 
-#                                 post_sd) < (baseline_mean/ 2)))
-# 
-# df_long_for_metan <- df_long_for_metan %>%
-#   rowwise() %>%
-#   mutate(resp_rate = responders/baseline_n)
-# 
-# summary_resp_rate <- df_long_for_metan %>%
-#   group_by(group) %>%
-#   summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
-#             sd_resp_rate = sd(resp_rate, na.rm = TRUE), 
-#             n = n())
-
-# save this as the master dataframe  --------------------------------------
-# use this dataframe to perform all operations below
-
-write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
-
-########### simulate so that each study has a value from a distribution of 
-######## of correlations.
-
-# I will generate random numbers per study id from a distribution with these parameters. 
-# it is reasonable to generate one random correlation value per study as there is no reason why the correlation should
-# systematically vary within studies
-
-# Use the function I have created for this
-
-df_long_for_metan <- read.csv("df_long_for_metan.csv")
-
-list_df_simulated <-  simulate_dataframes_for_st_errors (df = df_long_for_metan, 
-                                              num_repetitions = 1000, 
-                                              seed  = 1974,
-                                              n = length(unique(df_long_for_metan$new_study_id)), 
-                                              a = 0.45, 
-                                              b = .9, 
-                                              mean = 0.65, 
-                                              sd = 0.2)
-
-#check this worked
-
-#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
-#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
-
-```
-
-# Findings
-
-```{r metaregression-all, warning=FALSE, message = FALSE, echo=FALSE}
-
-# This chunk of code needs to be here because some of the data needed for the included studies summary lives here
-
-# Get Ns, run metareg, prepare graphing ------------------------------------------------------
-
-# add a new multilevel variable to the simulated data for the regression
-
-for(i in 1: length(list_df_simulated)){
-
-list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
-  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
-                                                       "medication_control",
-                                                       "medication_active", 
-                                                       "psychotherapy_control",
-                                                       "psychotherapy_active")
-}
-
-# check it worked
-# list_df_simulated[[2]] %>% 
-# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
-
-######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
-# A) the overall sample
-# B) the CBT vs Fluox and Escitalopram sample
-# C) the no WL sample
-# D) clinical levels of depression
-# E) the CDRS only sample
-# E) HAMD sensitivity analysis
-# G) Studies with post SD
-# H) Studies with variance <.02
-
-# A. Estimate Means and CIs for the overall ----------------------------------
-
-# count studies
-# count the number of studies
-n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
-df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
-# CB checked both, both correct.
-
-# specify model
-model_1 <- as.formula(~ four_level_var)
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_1_meta_reg <- run_multi_metaregression(list_df_simulated, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
-aggregate_results_overall <- cbind(aggregate_results_overall, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)
-
-df_mean_coefs_from_sim <- data.frame(cbind(condition,df_mean_coefs_from_sim))
-
-# add the ns
-df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-
-# Extract I2 values for each dataset
-i2_results_all <- extract_i2_values(list_model_1_meta_reg)
-
-# Calculate the mean and standard deviation of I2 values for each level
-i2_summary_all <- data.frame(
-  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
-  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
-  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
-  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
-)
-```
-
-```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
-# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-#  grab ids for those studies
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox.
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria.
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc.
-# We may have multiple controls per study id for this reason, though this isn't a problem
-# conceptually.
-
-list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-})
-
-# count the number of studies
-cbt_fluox_esc_study <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids,
-         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# CB checked, looks good now.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
- coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-```
-
-```{r metaregression-nowl, warning=FALSE, message = FALSE, echo=FALSE}
-
-# C. Estimate Means and CIs without WL ---------------------------------------
-
- # grab the ids for no waitlist
-no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
-
-# use them to loop over the simulated list to subset all the dataframes.
-
-list_no_wl <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% no_wl_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
-})
-
-# count studies 
-no_wl_studies <- df_long_for_metan %>% 
-  filter(new_study_id %in% no_wl_ids) %>%
-  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
-study_count_no_wl_study <- count_studies(no_wl_studies)
-# CB checked, looks good!
-
-# use this model as above
-model_1 <- as.formula(~ four_level_var)
-
-# apply the metareg function to the list of no wl
-list_model_1_no_wl <- run_multi_metaregression(list_no_wl , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
-aggregate_results_no_wl <- cbind(aggregate_results_no_wl, condition)
-
-# now use the function to extract the coefficients
-means_no_wl <-  lapply(list_model_1_no_wl, extract_coefficients_func)
-
-# run the mean function for no wl
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
-coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
-
-coef_and_se_means_no_wl <- left_join(coef_and_se_means_no_wl, study_count_no_wl_study[study_count_no_wl_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-clin, warning=FALSE, message = FALSE, echo=FALSE}
-
-# D. Clinical Levels Depression Sensitivity Analysis---------------------------------------
-
-# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
-
-#take study ids where sample has clinical levels of depression
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_clin_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% clin_study_ids,]
-}
-
-# count the number of studies
-study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_clin_study <- run_multi_metaregression(list_clin_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
-coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
-
-# add the ns to the dataframe
-coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
-
-# E. CDRS Sensitivity Analysis ---------------------------------------
-
-cdrs_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_cdrs_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% cdrs_study_ids,]
-}
-
-# count the number of studies
-study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of cdrs studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cdrs_study <- run_multi_metaregression(list_cdrs_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
-
-# extract SMDs from the list for cdrs
-means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
-coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cdrs_study <- left_join(coef_and_se_means_cdrs_study, study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-hamd, warning=FALSE, message = FALSE, echo=FALSE}
-
-# F. HAMD Sensitivity Analysis ---------------------------------------
-
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_hamd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_hamd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% hamd_study_ids,]
-}
-
-# count the number of studies
-study_count_hamd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% hamd_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of cdrs studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_hamd_study <- run_multi_metaregression(list_hamd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_hamd_study <-  aggregate_model_results(list_model_1_hamd_study, condition)
-
-# extract SMDs from the list for cdrs
-means_hamd_study <-  lapply(list_model_1_hamd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_hamd_study <- calculate_mean_coefs_ses(means_hamd_study, condition)
-coef_and_se_means_hamd_study <- data.frame(cbind(condition, coef_and_se_means_hamd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_hamd_study <- left_join(coef_and_se_means_hamd_study, study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-
-```
-
-```{r metaregression-postsd, warning=FALSE, message = FALSE, echo=FALSE}
-
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
-
-```
-
-```{r metaregression-var, warning=FALSE, message = FALSE, echo=FALSE}
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
-
-## Included studies
-
-Data for included studies are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-Please see @fig-prisma for a summary of the sources of included RCTs.
-
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r sum(df_count_studies[df_count_studies$condition == "medication_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "medication_control", "n"])` control arms of medication trials; and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_control", "n"])` control arms from psychotherapy RCTs.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-
-Placebo pill was the control condition for all medication trials.
-In psychotherapy trials, the control arm included 14 waitlist, 25 treatment-as-usual (TAU), and 19 other control conditions (e.g.
-relaxation training, attention control, counselling).
-
-```{r, echo=FALSE}
-#| label: fig-prisma
-#| fig-cap: "PRISMA chart summarising sources of included studies"
-#| fig-cap-location: top
-knitr::include_graphics(here("PRISMA.png"))
-```
-
-## Sample characteristics at baseline in medication and psychotherapy trials
-
-@tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
-The summary statistics are provided for each subgroup (i.e.
-medication and psychotherapy) and the p-value derives from the test for subgroup differences.
-
-```{r characteristics-metanalysis, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Start by looking at demographics at baseline
-# Currently we have both control and active conditions, we just need each study once
-
-df_baseline_demographics <- df_long_for_metan %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-# This is the function to extract statistics
-
-extract_stats <- function(df) {
-
-  # get the summary table with results
-  statistics <- summary(df, byvar = "psy_or_med")
-
-  df_stats <- tibble(
-  subgroup = statistics$subgroup.levels,
-  k_study = statistics$k.study.w,
-  TE_random = statistics$TE.random.w,
-  seTE_random = statistics$seTE.random.w,
-  lower_random = statistics$lower.random.w,
-  upper_random = statistics$upper.random.w,
-  tau2 = statistics$tau2.w)
-
-  # Add an empty row at the top and column on right (this is for the test for subgroup differences p value)
-  df_stats <- rbind(data.frame(subgroup = NA, k_study = NA, TE_random = NA, seTE_random = NA, 
-                             lower_random = NA, upper_random = NA, tau2 = NA), df_stats)
-  df_stats <- cbind(df_stats, pval_between = NA)
-
-  # Set the value in the last row and last column as the between groups p val
-  df_stats[1, "pval_between"] <- statistics$pval.Q.b.random
-
-  return(df_stats)
-
-}
-
-#A. Baseline severity meta-analysis--------------
-
-# Overall psy vs med
-
-# Need to calculate the variables first
-df_for_baseline_severity <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall)) %>%  # now also do this for untransformed variable
-  mutate(baseline_overall = sum(baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_sd_baseline = sqrt(sum((baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(se_baseline = pooled_sd_baseline / sqrt(n_overall))
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-    filter(new_study_id != "March, 2004")  # removing TADS because it does not technically belong to either the psy or med groups
-
-met_sev <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev <- extract_stats(met_sev)
-
-# Clinical sample
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_baseline_severity_clin <- df_for_baseline_severity %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_sev_clin <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity clinical",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_clin <- extract_stats(met_sev_clin)
-
-# cbt + med
-
-# cbt_meds_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-# 
-# df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_sev_cbt <- metagen(TE = perc_baseline_overall,
-#                            seTE = perc_se_baseline,
-#                            studlab = new_study_id,
-#                            data = df_for_baseline_severity_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "baseline severity cbt + med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# results_met_sev_cbt <- extract_stats(met_sev_cbt)
-
-# no wl
-
-no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
-
-df_for_baseline_severity_no_wl <- df_for_baseline_severity %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_sev_no_wl <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity no wl studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_no_wl <- extract_stats(met_sev_no_wl)
-
-#B. Sex meta-analysis
-
-# Now start looking at perc_women variable
-# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.
-
-df_for_sex_metan <- df_baseline_demographics %>% 
-  filter(!is.na(percent_women))
-
-df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(percent_women != 100) # filter out studies with only women
-
-df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-met_perc_women_overall <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies")
-
-met_perc_women_overall <- update(met_perc_women_overall,
-                              subgroup = df_for_sex_metan$psy_or_med, subgroup.name = "treatment modality",
-                              tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-
-results_met_perc_women_overall <- extract_stats(met_perc_women_overall)
-
-# looking at clinical sample only
-
-df_for_sex_metan_clin <- df_for_sex_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_perc_women_clin <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across clinical studies")
-
-met_perc_women_clin <- update(met_perc_women_clin,
-                           subgroup = df_for_sex_metan_clin$psy_or_med, subgroup.name = "treatment modality",
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_clin <- extract_stats(met_perc_women_clin)
-
-# # Now looking at the CBT + med studies only
-# 
-# df_for_sex_metan_cbt <- df_for_sex_metan %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_perc_women_cbt <- metagen(TE = percent_women,
-#                            seTE = percent_women_std_error,
-#                            studlab = new_study_id,
-#                            data = df_for_sex_metan_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "percentage women across cbt and med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# # Apply the function to the meta-analysis result
-# results_met_perc_women_cbt <- extract_stats(met_perc_women_cbt)
-
-# Now the no waitlist group
-
-df_for_sex_metan_no_wl <- df_for_sex_metan %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_perc_women_no_wl <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies with controls that are not wl",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_wl <- extract_stats(met_perc_women_no_wl)
-
-# C. Age meta-analysis--------------------
-
-# We have several studies for which we are missing SE for age. I am going to perform an imputation by taking an average
-# for the studies we do have, per modality, and substituting this in for missing values.
-
-df_baseline_demographics$se_age <- as.numeric(df_baseline_demographics$se_age)
-
-mean_se_age_psy <- df_baseline_demographics %>%
-  filter(psy_or_med == 1) %>%
-  summarise(mean_se_age_psy = mean(se_age, na.rm = TRUE))
-
-mean_se_age_med <- df_baseline_demographics %>%
-  filter(psy_or_med == 0) %>%
-  summarise(mean_se_age_med = mean(se_age, na.rm = TRUE))
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  mutate(se_age = ifelse(!is.na(se_age), se_age,
-                         ifelse(psy_or_med == 1, mean_se_age_psy, mean_se_age_med)))
-
-df_for_age_metan <- df_baseline_demographics %>% 
-  filter(!is.na(mean_age))
-
-df_for_age_metan <- df_for_age_metan %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-# Age meta analysis
-
-df_for_age_metan$se_age <- as.numeric(df_for_age_metan$se_age)
-
-met_age <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age <- extract_stats(met_age)
-
-# Looking at clinical sample only
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_age_metan_clin <- df_for_age_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_age_clin <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across clinical studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age_clin <- extract_stats(met_age_clin)
-
-# # Now cbt + med studies only
-# 
-# df_for_age_metan_cbt <- df_for_age_metan %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_age_cbt <- metagen(TE = mean_age,
-#                            seTE = se_age,
-#                            studlab = new_study_id,
-#                            data = df_for_age_metan_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "age across cbt + med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# results_met_age_cbt <- extract_stats(met_age_cbt)
-
-# Now excluding wl
-
-df_for_age_metan_no_wl <- df_for_age_metan %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_age_no_wl <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across no wl studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age_no_wl <- extract_stats(met_age_no_wl)
-
-# This is if we want to have all sensitivity analyses in table one
-
-df_overall_baseline_results <- rbind(results_met_sev, results_met_sev_clin, results_met_sev_no_wl, results_met_perc_women_overall, results_met_perc_women_clin, results_met_perc_women_no_wl, results_met_age, results_met_age_clin, results_met_age_no_wl)
-
-# For row names
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(subgroup = case_when(
-    row_number() %in% c(1, 10, 19) ~ "Overall",
-    row_number() %in% c(4, 13, 22) ~ "Excluding subclinical",
-    row_number() %in% c(7, 16, 25) ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_overall_baseline_results) <- new_column_names
-
-# Rounding
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-big_border = fp_border(color="black", width = 1)
-small_border = fp_border(color="lightgray", width = 1)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-baseline-results
-#| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies: Results for overall sample and sensitivity analyses"
-#| tbl-cap-location: top
-
-df_overall_baseline_results %>% 
-  mutate(category = case_when(
-    row_number() %in% 1:9 ~ "Baseline Severity of Depressive Symptoms*",
-    row_number() %in% 10:18 ~ "Percent Female",
-    row_number() %in% 19:27 ~ "Age",
-    TRUE ~ ""
-  )) %>% # grouping rows
-  group_by(category) %>%
-  as_flextable(hide_grouplabel = TRUE) %>% 
-  paginate(group = "category") %>% 
-  bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
-  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
-  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>% # indent some rows
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  add_footer_row(values = as_paragraph(
-    "Abbreviations: K = number of studies, SE = standard error, CI = 95% confidence interval, T2 = estimate of between-study heterogeneity",
-    "*These are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
-range of 96).
-Mean severity was 0.36 for psychotherapy studies and 0.42 for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS."), colwidths = 8) %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-```
-
-```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
-
-mean_psych_overall <- 0.37
-mean_med_overall <- 0.42
-se_psych_overall <- 0.02
-se_med_overall <- 0.01
-n_psych_overall <- 49
-n_med_overall <- 31
-
-# Calculate standard deviation
-sd_psych_overall <- se_psych_overall * sqrt(n_psych_overall)
-sd_med_overall <- se_med_overall * sqrt(n_med_overall)
-
-#formula with pooled sd
-pooled_sd_overall <- sqrt(((sd_psych_overall^2 + sd_med_overall^2)/2))
-
-# Calculate Cohen's d
-cohens_d_overall <- (mean_psych_overall - mean_med_overall) / pooled_sd_overall
-
-## without subclinical
-
-mean_psych_sub <- 0.39
-mean_med_sub <- 0.42
-se_psych_sub <- 0.02
-se_med_sub <- 0.01
-n_psych_sub <- 41
-n_med_sub <- 31
-
-# Calculate standard deviation
-sd_psych_sub <- se_psych_sub * sqrt(n_psych_sub)
-sd_med_sub <- se_med_sub * sqrt(n_med_sub)
-
-#formula with pooled sd
-pooled_sd_sub <- sqrt(((sd_psych_sub^2 + sd_med_sub^2)/2))
-
-# Calculate Cohen's d
-cohens_d_sub <- (mean_psych_sub - mean_med_sub) / pooled_sd_sub
-cohens_d_sub
-cohens_d_overall
-```
-
-### Baseline severity
-
-On average, depression severity at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline-results).
-When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
-This difference did not reach statistical significance when excluding studies that recruited samples with sub-clinical depression.
-
-```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
-# looking at CDRS studies only, this is with only 2 levels
-
-df_for_baseline_severity_cdrs <- df_for_baseline_severity %>%
-  filter(new_study_id %in% cdrs_study_ids)
-
-met_sev_cdrs <- metagen(TE = baseline_overall,
-                           seTE = se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_cdrs,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cdrs",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_cdrs <- extract_stats(met_sev_cdrs)
-
-# looking at HAMD studies only,
-
-df_for_baseline_severity_hamd <- df_for_baseline_severity %>%
-  filter(new_study_id %in% hamd_study_ids)
-
-met_sev_hamd <- metagen(TE = baseline_overall,
-                           seTE = se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_hamd,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cdrs",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_hamd <- extract_stats(met_sev_hamd)
-```
-
-```{r baseline-severity-hamd-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
-## this is for four levels
-### get CDRS studies
-cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-
-#turn sds to sec
-cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
-                                                              #throughout
-
-results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,
-                                                         model_1, condition)
-
-results_cdrs_metareg_baseline[[2]] <- left_join(results_cdrs_metareg_baseline[[2]], study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-
-### get HAM-D studies
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-                                                          %in% hamd_study_ids,]
-
-hamd_studies_for_baseline_metareg <- list_hamd_study #
-
-#turn sds to sec
-hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
-                                                              #throughout
-results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg,
-                                                         model_1, condition)
-
-results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-results_hamd_metareg_baseline[[2]] <- left_join(results_hamd_metareg_baseline[[2]], study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-
-```
-
-To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS and HAM-D, on which there was a sufficient number of studies to metanalyse.
-As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplemental Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
-
-### Sex
-
-For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016; see @tbl-all-studies-percfemale-results in Supplement for results with full sample).
-As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
-On average, samples were `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`) female across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`) female across medication trials.
-Excluding sub-clinical and waitlist control studies yielded similar results.
-
-### Age
-
-As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = ``` r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2) ```) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
-There were no significant differences in mean age between modalities on further sensitivity analyses.
-
-## Trial design
-
-### Standardised mean differences of control conditions in psychotherapy and medication studies
-
-We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-As seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
-In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
-#| label: smd-diff-control
-#| fig-cap: "Pre-Post Standardised Mean Differences (SMD) of Control Arms"
-#| fig-cap-location: top
-
-list_df_simulated[[1]] %>%
-  filter(arm_effect_size == "cohens_d_control") %>%
-  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
-  geom_jitter(height = 0.2, alpha = 0.7) +
-  geom_point(alpha = 0.7) +
-  labs(
-    x = "SMD",
-    y = "",
-    color = "Type of Study",
-    size = "Baseline n"
-  ) +
-  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
-  theme_minimal() +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-all
-#| fig-cap: "Meta-analytic estimates of within-group changes for overall sample"
-#| fig-cap-location: top
-
-df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
-plot_means_multi_all <- plot_means_function(df_mean_coefs_from_sim)
-print(plot_means_multi_all)
-
- png("plot_means_multi_all.png")
- plot_means_multi_all
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-coefs-overall
-# #| tbl-cap: "Summary statistics of the estimated SMDs"
-# #| tbl-cap-location: top
-# 
-# # Prepare to tabulate
-# 
-# table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   relocate("n", .after = "condition") 
-# 
-# new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_mean_coefs_from_sim) <- new_column_names
-# 
-# flextable(table_mean_coefs_from_sim) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>% 
-#   # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
-#   # add_header_row(values = "Table 3", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-##### Sensitivity analyses
-
-We conducted a series of sensitivity analyses (all figures in the Supplement).
-Excluding waitlist control studies (see @fig-plot-means-no-wl) and sub-clinical studies (see @fig-plot-means-clin) yielded a pattern of results very similar to the overall analyses.
-Next, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAMD (see @fig-plot-means-hamd).
-Medication control and psychotherapy control conditions remained significantly different, though the small number of studies resulted in less precise estimates of the SMDs.
-Conversely, restricting the analysis to studies with variance below 0.02 yielded a similar pattern of results, but with increased precision in SMD estimates across conditions (see @fig-plot-means-var2).
-Finally, we showed that different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
-
-##### Addressing regression to the mean
-
-```{r baseline-adjust-means, warning=FALSE, message = FALSE, echo=FALSE}
-# #### Let's start from the beginning and regress cohens on the baseline dataframe.
-# 
-# # create a new list with dfs for the sims
-# df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# # rename the cohens_d value to make space for the new cohen's d
-# df_long_for_metan_adj_cohens_d <-
-#   df_long_for_metan_adj_cohens_d %>%
-# rename(unadjusted_cohens_d = cohens_d,
-# )
-# # estimate the cohen's d from the residuals
-# model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
-# 
-# # there is a great effect of the baseline means, as shown here
-# results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-# 
-# # extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-# df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-# 
-# # apply function to simulate standard errors
-# list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
-#                                    num_repetitions = 1000,
-#                                    seed  = 1974,
-#                                    n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
-#                                    a = 0.45,
-#                                    b = .9,
-#                                    mean = 0.65,
-#                                    sd = 0.2)
-# 
-# 
-# # add the four level variable and re-level
-# for(i in 1: length(list_df_simulated_adj_cohens_d)){
-# 
-#   list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-#   list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
-#     mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-#                                       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-#     )
-# 
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-# 
-#   # relevel so that medication control becomes the reference category for the regression
-#   #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-#                                                          "medication_control",
-#                                                          "medication_active",
-#                                                          "psychotherapy_control",
-#                                                          "psychotherapy_active")
-# }
-# 
-# 
-# 
-# 
-# 
-# # Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# # specify model
-# model_x <- as.formula(~ four_level_var)
-# 
-# # run metareg function
-# # here you can use the simulated results directly
-# list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-# aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-# aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-# 
-# # extract SMDs from the  list
-# list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-# 
-# df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
-#
-
-####code to extract baseline-adjusted post means
-
-de_meaned_baseline_mean <- (list_df_simulated[[1]]$perc_baseline_mean - mean(list_df_simulated[[1]]$perc_baseline_mean, na.rm = TRUE))
-
-lm_for_baseline_means <- lm(list_df_simulated[[1]]$perc_post_mean ~ de_meaned_baseline_mean + list_df_simulated[[1]]$four_level_var, na.action=na.exclude, )
-
-coefs_lm_for_baseline_means  <- broom:: tidy(lm_for_baseline_means)
-
-condition <- coefs_lm_for_baseline_means$term
-
-smds <-c(coefs_lm_for_baseline_means$estimate[1], coefs_lm_for_baseline_means$estimate[-1] + coefs_lm_for_baseline_means$estimate[1])
-
-upper_ci <- smds + coefs_lm_for_baseline_means$std.error*1.96
-
-lower_ci <- smds - coefs_lm_for_baseline_means$std.error*1.96
-
-de_meaned_smd_with_cis <- data.frame (
-
-  condition = levels(list_df_simulated[[1]]$four_level_var),
-
-  smds = smds[-2],
-
-  lower_ci = lower_ci[-2],
-
-  upper_ci = upper_ci[-2]
-
-)
-
-```
-
-We addressed potential regression to the mean by including the baseline score for each depression scale in the linear regression model as per equation 3 in @barnettRegressionMeanWhat2004 (see @tbl-de-meaned in the Supplement).
-The difference between the medication control and psychotherapy control arms remained significantly different.
-
-### Number of trial sites
-
-```{r trial-sites, warning=FALSE, message = FALSE, echo=FALSE}
-### Number of sites
-# Write results, tabulate.
-
-## This data lives in this spreadsheet for psy trials, we need to merge it in
-
-df_no_sites <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
-
-df_no_sites <- df_no_sites %>% 
-  select(c(new_study_id, number_of_sites)) %>% 
-  filter(!is.na(number_of_sites)) %>% 
-  distinct(new_study_id, .keep_all = TRUE) %>% 
-  mutate(number_of_sites = as.numeric(number_of_sites))
-
-df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-# we have different vectors for psy and med trials, lets coalesce
-
-df_baseline_demographics <- df_baseline_demographics %>%
-  mutate(no_sites = as.numeric(no_sites)) %>% 
-  mutate(sites = coalesce(no_sites, number_of_sites)) %>%
-  select(-no_sites, -number_of_sites)
-
-# we have a few rogue studies (Kitchen, McCarty and Wright). Kitchen was too recent (after 2021), McCarty and Wright are not in Cuijpers' master
-# dataset for some reason, though they are in the list of included studies in the table in his MA. For now I'm going to remove them because 
-# we don't have data for these trials.
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
-
-# Now create binary variable, single or multi site trial
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  mutate(site_binary = case_when(sites == 1 ~ "single", 
-                                 sites > 1 ~ "multi",
-                                 TRUE ~ NA_character_))
-
-df_binary_site_count <- df_baseline_demographics %>% 
-  group_by(psy_or_med, site_binary) %>% 
-  summarize(num_trials = n())
-
-# Lets look at results
-
-# summary stats
-df_sites_summary_stats <- df_baseline_demographics %>%
-  group_by(psy_or_med) %>%
-  summarise(
-    n = n(),
-    mean_sites = mean(sites, na.rm = TRUE),
-    sd_sites = sd(sites, na.rm = TRUE),
-  )
-
-# Tabulate
-# Rounding
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-# Row names
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(psy_or_med = case_when(
-    psy_or_med == 0 ~ "Medication",
-    psy_or_med == 1 ~ "Psychotherapy",
-    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
-  ))
-
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  rename(
-    Modality = psy_or_med,
-    K = n,
-    Mean = mean_sites,
-    SD = sd_sites
-  )
-
-# t-test
-sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
-
-sites_t_test_stats <- data.frame(
-  statistic = sites_t_test$statistic,
-  df = sites_t_test$parameter,
-  p_value = sites_t_test$p.value,
-  ci_lower = sites_t_test$conf.int[1],
-  ci_upper = sites_t_test$conf.int[2]
-)
-
-sites_t_test_stats <- sites_t_test_stats %>%
-  mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2))) %>% 
-  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-## | label: tbl-sites-summary
-## | tbl-cap: "Number of sites across medication and psychotherapy studies"
-## | tbl-cap-location: top
-#
-# flextable(df_sites_summary_stats) %>%
-#   set_table_properties(width = 1, layout = "fixed") %>%
-#   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
-#                       "; ", as_i("p "), sites_t_test_stats$p_value, 
-#                       "; 95% CI: ", sites_t_test_stats$ci_lower,
-#                       "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
-#   # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
-#   # add_header_row(values = "Table 2", colwidths = 4) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>% 
-#   autofit() %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 25 of 46 (54%) psychotherapy studies.
-
-## Comparing the nature and intensity of control conditions in psychotherapy trials
-
-```{r nature-intensity-comparison, warning=FALSE, message = FALSE, echo=FALSE}
-# We need to read in the appropriate dataset which describes the active and control conditions used in
-# psychotherapy trials.
-
-df_descr_psy_conditions <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
-
-# checking id matchup
-# discrepancies <- setdiff(df_descr_psy_conditions$new_study_id, df_long_for_metan$new_study_id)
-
-# Cleaning the dataset
-# For now lets look at variables pertaining to the nature / intensity of interventions
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  select(c(new_study_id, `Psychotherapy/control`, levels_var, number_of_sites, Number_of_sessions,
-           frequency_weeks, Length_of_sessions_mins, Total_hours_of_intervention_hours, total_hours_gsh,
-           Total_period_of_intervention_weeks, Format_group_individual, Delivery, Involvement_of_others))
-
-# rename for clarity and to match master dataframe
-df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  rename(treatment = 'Psychotherapy/control', no_sites = number_of_sites, no_sessions =
-           Number_of_sessions, freq_weeks = frequency_weeks, length_sessions_mins =
-           Length_of_sessions_mins, total_hours = Total_hours_of_intervention_hours,
-         total_period_weeks = Total_period_of_intervention_weeks, format = Format_group_individual, delivery =
-           Delivery, family_involv = Involvement_of_others)
-
-check <- df_descr_psy_conditions %>% 
-  filter(treatment == 'wlc')
-
-# Visual inspection
-
-# There are two studies where the waitlist condition has some intervention (i.e. values should not be set to 0)
-# Otherwise, I want values to be set to 0, not NA.
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate(
-    no_sessions = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, no_sessions),
-    freq_weeks = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, freq_weeks),
-    length_sessions_mins = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, length_sessions_mins),
-    total_hours = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, total_hours)
-  )
-
-# Now cau
-
-check <- df_descr_psy_conditions %>% 
-  filter(treatment == 'cau')
-
-# All studies except for Martinovic, Srivastava, Stikkelbroek and Weisz 2009 should have variables set to NA. 
-# This is because we cannot say that they did not feature 0 hours of intervention, but that for the most part
-# it is not reported or it is not possible to quantify.
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate(
-    no_sessions = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, no_sessions),
-    freq_weeks = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, freq_weeks),
-    length_sessions_mins = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, length_sessions_mins),
-    total_hours = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, total_hours)
-  )
-
-# Now other controls
-
-check <- df_descr_psy_conditions %>%
-  filter(!(treatment %in% c('cau', 'wlc'))) %>% 
-  filter(levels_var == "psychotherapy_control")
-
-# Made a few manual adjustments in the original excel sheet.
-
-# List of columns to clean
-columns_to_clean <- c(
-  "no_sessions",
-  "freq_weeks",
-  "length_sessions_mins",
-  "total_hours",
-  "total_period_weeks"
-)
-
-# Convert non-numeric values to NA in specified columns
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate_at(vars(columns_to_clean), ~as.numeric(as.character(.)))
-
-# Giannis' function for summary stats
-
-group_function <- function(dataframe, my_groups, columns) {
-  result_dataframe <- data.frame(
-    Group = character(),
-    Column = character(),
-    K = numeric(),
-    Mean = numeric(),
-    SD = numeric(),
-    Median = numeric(),
-    IQR = numeric(),
-    stringsAsFactors = FALSE
-  )
-  unique_groups <- unique(dataframe[[my_groups]])
-  for (group in unique_groups) {
-    group_data <- dataframe[dataframe[[my_groups]] == group, ]
-    for (col in columns) {
-      col_data <- group_data[[col]]
-      n <- sum(!is.na(col_data))
-      mean_val <- mean(col_data, na.rm = TRUE)
-      SD <- sd(col_data, na.rm = TRUE)
-      median_val <- median(col_data, na.rm = TRUE)
-      iqr <- IQR(col_data, na.rm = TRUE)
-      result_dataframe <- rbind(result_dataframe,
-                                data.frame(Column = col, Group = group, K = n, Mean = mean_val,
-                                           SD = SD, Median = median_val,
-                                           IQR = iqr, stringsAsFactors = FALSE))
-    }
-  }
-  return(result_dataframe)
-}
-
-# Filter out wl conditions
-# df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  # filter(new_study_id %in% no_wl_ids)
-
-# count_wl <- df_long_for_metan %>% 
-#   filter(treatment == "wlc") %>% 
-#   distinct(new_study_id) %>% 
-#   nrow()
-# 
-# count_cau <- df_long_for_metan %>% 
-#   filter(treatment == "cau") %>% 
-#   distinct(new_study_id) %>% 
-#   nrow()
-
-sessions <- group_function(df_descr_psy_conditions,"levels_var","no_sessions")
-frequency <- group_function(df_descr_psy_conditions,"levels_var","freq_weeks")
-length_sessions_mins <- group_function(df_descr_psy_conditions,"levels_var","length_sessions_mins")
-total_hours <- group_function(df_descr_psy_conditions,"levels_var","total_hours")
-total_period_weeks <- group_function(df_descr_psy_conditions,"levels_var","total_period_weeks")
-
-control_summary <- rbind(sessions, frequency, length_sessions_mins, total_hours)
-
-control_summary <- control_summary %>% 
-  select(-c(Median, IQR))
-
-control_summary <- control_summary %>%
-  mutate(Group = case_when(
-    Group == "psychotherapy_active" ~ "Active",
-    Group == "psychotherapy_control" ~ "Control",
-    TRUE ~ as.character(Group)  # Keep other values unchanged
-  ))
-
-control_summary <- control_summary %>%
-  mutate(Column = case_when(
-    Column == "no_sessions" ~ "Number of sessions",
-    Column == "freq_weeks" ~ "Intensity (sessions per week)",
-    Column == "length_sessions_mins" ~ "Session length (mins)",
-    Column == "total_hours" ~ "Total intervention hours",
-    TRUE ~ as.character(Column)  # Keep original value if no match
-  ))
-
-# other_ctr_ids <- df_long_for_metan[df_long_for_metan$type == "other ctr",]$new_study_id
-# testing <- df_descr_psy_conditions %>% 
-#   filter(new_study_id %in% other_ctr_ids)
-# view(testing)
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-
-# for t test table
-
-control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
-
-# For row names
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests) <- new_column_names
-
-#Rounding
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
-
-# function for between group effect sizes (cohens d)
-# 
-# effect_btwn <- function(df) {
-#   pooled_sd <- sqrt(((df$N[1]-1)*df$SD[1]^2 + (df$N[2]-1)*df$SD[2]^2) / (df$N[1] + df$N[2] - 2))
-#   mean_diff <- df$Mean[1] - df$Mean[2]
-#   effect_btwn <- mean_diff / pooled_sd
-#   return(effect_btwn)
-# }
-# 
-# session_es <- effect_btwn(sessions)
-# frequency_es <- effect_btwn(frequency)
-# length_sessions_mins_es <- effect_btwn(length_sessions_mins)
-# total_hours_es <- effect_btwn(total_hours)
-# total_period_weeks_es <- effect_btwn(total_period_weeks)
-
-# using a package to calculate instead
-
-session_es <- cohen.d(df_descr_psy_conditions$no_sessions ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-frequency_es <- cohen.d(df_descr_psy_conditions$freq_weeks ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-length_sessions_mins_es <- cohen.d(df_descr_psy_conditions$length_sessions_mins ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-total_hours_es <- cohen.d(df_descr_psy_conditions$total_hours ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-
-# going to try displaying summary statistics and t-tests in one place
-
-control_summary <- cbind(control_summary, 
-                          "Cohen's d" = rep(NA, nrow(control_summary)),
-                         "Upper CI" = rep(NA, nrow(control_summary)),
-                         "Lower CI" = rep(NA, nrow(control_summary)),
-                         t = rep(NA, nrow(control_summary)), 
-                          df = rep(NA, nrow(control_summary)), 
-                          "p-value" = rep(NA, nrow(control_summary)))
-
-# Update the first row with session_es
-control_summary[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  session_es$estimate, session_es$conf.int[1], session_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[1], control_summary_t_tests$df[1], 
-  control_summary_t_tests$`p-value`[1]
-)
-
-# Update the third row with frequency_es
-control_summary[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  frequency_es$estimate, frequency_es$conf.int[1], frequency_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[2], control_summary_t_tests$df[2], 
-  control_summary_t_tests$`p-value`[2]
-)
-
-# Update the fifth row with length_sessions_mins_es
-control_summary[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  length_sessions_mins_es$estimate, length_sessions_mins_es$conf.int[1], length_sessions_mins_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[3], control_summary_t_tests$df[3], 
-  control_summary_t_tests$`p-value`[3]
-)
-
-# Update the seventh row with total_hours_es
-control_summary[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  total_hours_es$estimate, total_hours_es$conf.int[1], total_hours_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[4], control_summary_t_tests$df[4], 
-  control_summary_t_tests$`p-value`[4]
-)
-
-control_summary <- control_summary %>%
-  mutate(
-    `Cohen's d` = as.numeric(`Cohen's d`),
-    `Upper CI` = as.numeric(`Upper CI`),
-    `Lower CI` = as.numeric(`Lower CI`)
-  ) %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-# # plot
-# 
-# ggplot(df_descr_psy_conditions_no_wl, aes(x = total_hours, fill = levels_var)) +
-#   geom_histogram(position = "identity", alpha = 0.5, binwidth = 5, color = "black") +
-#   facet_wrap(~ levels_var, ncol = 2) +
-#   theme_minimal() +
-#   labs(title = "Histograms of Number of Total Hours by Group",
-#        x = "Number of Hours",
-#        y = "Frequency") +
-#   scale_fill_manual(values = c("lightpink", "lightblue"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-intensity-of-int
-#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-#| tbl-cap-location: top
-
-as_grouped_data(control_summary, groups = "Column") %>% 
-  as_flextable(hide_grouplabel = TRUE ) %>% 
-  bold(i = c(1, 4, 7, 10), bold = TRUE, part = "body") %>%  
-  set_table_properties(width = 1) %>%  # Set table width 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:9, align = "center", part = "all") %>% 
-  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
-  # add_header_row(values = "Table 5", colwidths = 4) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  add_footer_row(values = as_paragraph("Abbreviations: K = number of studies, SD = standard deviation, CI = 95% confidence interval, df = degrees of freedom."), colwidths = 10) %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(j = 1:4, part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = c(1,4), part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all") 
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-t-tests-intensity
-# #| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-# #| tbl-cap-location: top
-# 
-# flextable(control_summary_t_tests) %>%
-#   set_table_properties(width = 1) %>%  # Set table width %>% 
-#   autofit() %>%  # Autofit column widths 
-#   align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   #italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   paginate(init = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-As seen in @tbl-intensity-of-int, active conditions featured significantly more sessions when compared to control conditions.
-Sessions in active conditions were longer and more frequent, resulting in significantly more intervention hours overall.
-Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data.
-We performed a sensitivity analysis where we excluded trials using waitlist controls; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
-
-# Conclusions and Clinical Implications
-
-```{r proportion-wl, echo=FALSE}
-# Filter the dataframe
-# filtered_df <- df_long_for_metan %>%
-#   filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
-# 
-# # Count the occurrences of each type
-# type_counts <- filtered_df %>%
-#   count(type) %>%
-#   mutate(total_count = sum(n),
-#          wl_sum = sum(n[type == "wl"]),
-#          wl_percentage = wl_sum / total_count * 100)
-# 
-# # how many examples of matching of active and control in number of hours
-# 
-# instances_count <- df_descr_psy_conditions_no_wl %>%
-#   filter(!is.na(total_hours)) %>%
-#   group_by(new_study_id, total_hours) %>%
-#   summarise(count = n()) %>%
-#   filter(count > 1) %>%
-#   summarise(total_instances = n())
-
-```
-
-This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence, by looking at two key conditions for comparability.
-First, whether the participants of trials in one modality are comparable to those in another modality.
-Second, whether conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
-
-Starting with the first question, we found that participants in medication trials are comparable on age but are more likely to be male and have more severe depression compared to those in psychotherapy trials.
-This indicates that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability.
-
-Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressants [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
-Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however these are within people who have chosen to be in the particular trial and modality.
-Moreover, severity may represent different subtypes in terms of course of depression and real-life outcomes [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
-
-We then turned to our second question about whether trial design conditions are comparable between modalities.
-We found that medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
-Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy [@dechartresSingleCenterTrialsShow2011]; [@meisterPlaceboResponseRates2020].
-Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
-
-Second, psychotherapy controls have moderate effect sizes (-0.5) whereas medication controls have very large effect sizes (-1.9).
-Our analysis could be critiqued as it compares within arm symptom change per trial, therefore effectively breaking randomisation.
-This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving randomisation to balance confounders is critical.
-More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
-This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
-
-We note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
-Indeed, in Zhou et al.
-[@zhouComparativeEfficacyAcceptability2020] the estimates for psychotherapy controls, TAU and waitlist conditions favoured placebo (though CIs were broad because these were indirectly estimated), as did estimates for psychodynamic and behavioural therapy.
-CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial [@marchFluoxetineCognitiveBehavioralTherapy2004].
-We note that the Zhou metanalysis, which represents an admirable effort to synthesise the literature, reports on issues that may affect transitivity with tests of incoherence showing significant differences.
-
-Moving beyond comparison between modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving treatment.
-An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind) yet psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption.
-In order to test that a psychological treatment is effective per se (e.g.
-because of the specific techniques) rather than because of generic effects (e.g.
-pleasant human contact), aspects such as therapist contact time should be matched.
-Many (24%) psychotherapy RCTs used waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
-TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
-Importantly, controls were often poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
-Overall, there is poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
-
-Given all of the above, the empirical basis for comparing psychotherapy and medication for adolescent depression is weak, and hence it is difficult to generate guidelines and recommend one treatment over another.
-Indeed, we believe that our findings have several implications for patients, their families, clinicians and policy makers.
-
-First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is a need to revisit guidelines and public information in light of the limitations.
-
-Second, the low quality of psychotherapy control conditions should prompt consideration of how to create fair comparators.
-Investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of RCTs where such rigor has been applied (e.g.
-Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
-Moreover, there is a place for comparing interventions to TAU, since these represent real-world comparators.
-However issues of disappointment bias should be addressed to avoid inflating treatment estimates.
-
-Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-The first obstacle is the comparability of the populations taking part.
-Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive [@kingImpactParticipantPhysician2005].
-And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
-
-In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression.
-Our data question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, need better evidence on which to base their choices.
-
-# Supplemental Materials
-
-## Systematic review description and search terms
-
-We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
-after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review).
-We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
-We used the same search terms as Cipriani [@ciprianiComparativeEfficacyTolerability2016] with one additional search term to include only placebo-controlled trials (see below).
-We additionally applied filters to specify our date range, and to exclude reviews and non-human studies.
-We also searched clinical trial registers for published and unpublished studies however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
-Please see fig-prisma for the PRISMA flow diagram.
-
-We used Covidence, an online software tool, to manage our systematic review.
-Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and data extraction was completed for these papers.
-
-**Search terms**
-
-Explicit search strategy: title/abstract = (depress\* or dysthymi\* or "mood disorder\*" or "affective disorder\*") AND (adolesc\* or child\* or boy\* or girl\* or juvenil\* or minors or paediatri\* or pediatri\* or pubescen\* or school\* or student\* or teen\* or young or youth\*) AND (selective serotonin reuptake inhibitor or SSRI or citalopram or fluoxetine or paroxetine or sertraline or escitalopram or fluvoxamine or serotonin norepinephrine reuptake inhibitor\* or SNRI or venlafaxine or duloxetine or milnacipran or reboxetine or bupropion or noradrenergic and specific serotonergic antidepressants or NaSSA or mirtazapine or TCA or tricyclic or amersergide or amineptine or amitriptyline or amoxapine or butriptyline or chlorpoxiten or clomipramine or clorimipramine or demexiptiline or desipramine or dibenzipin or dothiepin or doxepin or imipramine or lofepramine or melitracen or metapramine or nortriptyline or noxiptiline or opipramol or protriptyline or quinupramine or tianeptine or trimipramine) AND (placebo)
-
-##References for included trials
-
-References for trials included in the existing meta-analyses drawn upon for this study can be found at <https://docs.metapsy.org/databases/depression-childadol-psyctr/> for psychotherapy RCTs and at <https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5> for medication RCTs.
-Below are references for the seven additional RCTs identified in the original systematic review conducted for the current study.
-
-*Publications*
-
-Atkinson, S., Lubaczewski, S., Ramaker, S., England, R.
-D., Wajsbrot, D.
-B., Abbas, R., & Findling, R.
-L.
-(2018).
-Desvenlafaxine versus placebo in the treatment of children and adolescents with major depressive disorder.
-*Journal of Child and Adolescent Psychopharmacology, 28(1),* 55-65.
-DOI: 10.1089/cap.2017.0099
-
-Durgam, S., Chen, C.
-Z., Migliore, R., Prakash, C., Edwards, J., & Findling, R.
-L.
-(2018).
-A phase 3, double-blind, randomized, placebo-controlled study of vilazodone in adolescents with major depressive disorder.
-*Pediatric Drugs, 20(4),* 353-363.
-DOI: 10.1007/s40272-018-0290-4
-
-Findling, R.
-L., McCusker, E., & Strawn, J.
-R.
-(2020).
-A randomized, double-blind, placebo-controlled trial of vilazodone in children and adolescents with major depressive disorder with twenty-six-week open-label follow-up.
-*Journal of Child and Adolescent Psychopharmacology, 30(6),* 355-365.
-DOI: 10.1089/cap.2019.0176
-
-Le Noury, J., Nardo, J.
-M., Healy, D., Jureidini, J., Raven, M., Tufanaru, C., & Abi-Jaoude, E.
-(2015).
-Restoring Study 329: efficacy and harms of paroxetine and imipramine in treatment of major depression in adolescence.
-*BMJ, 351,*, h4320.
-DOI: 10.1136/bmj.h4320
-
-Weihs, K.
-L., Murphy, W., Abbas, R., Chiles, D., England, R.
-D., Ramaker, S., & Wajsbrot, D.
-B.
-(2018).
-Desvenlafaxine versus placebo in a fluoxetine-referenced study of children and adolescents with major depressive disorder.
-Journal of Child and Adolescent Psychopharmacology, 28(1), 36-46.
-DOI: 10.1089/cap.2017.0100
-
-*Unpublished clinical trials*
-
-Active Reference (Fluoxetine) Fixed-dose Study of Vortioxetine in Paediatric Patients Aged 12 to 17 Years With Major Depressive Disorder (MDD).
-ClinicalTrials.gov Identifier: NCT02709746.
-Accessed 17 Jan 2024.
-
-Safety and Efficacy of Levomilnacipran ER in Adolescent Participants With Major Depressive Disorder. ClinicalTrials.gov Identifier: NCT02431806. Accessed 17 Jan 2024.
-
-## Hierarchy of depression symptom severity measurement scales
-
-Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. [@ciprianiComparativeEfficacyTolerability2016].
-
-1.  Children's Depression Rating Scale (CDRS)
-2.  Hamilton Depression Rating Scale (HAMD)
-3.  Montgomery Asberg Depression Rating Scale (MADRS)
-4.  Beck Depression Inventory (BDI)
-5.  Children's Depression Inventory (CDI)
-6.  Schedule for Affective Disorders and Schizophrenia for School-Aged Children (K-SADS)
-7.  Mood and Feeling Questionnaire (MFQ)
-8.  Reynolds Adolescent Depression Scale (RADS)
-9.  Bellevue Index of Depression (BID)
-10. Child Depression Scale (CDS)
-11. Centre for Epidemiological Studies Depression Scale (CES-D)
-12. Child Assessment Schedule (CAS)
-13. Child Behaviour Checklist-Depression (CBCL-D)
-
-## Full description of methods (including formalisms)
-
-## Included studies
-
-We drew upon RCTs included in two recent comprehensive meta-analyses with open data available for each medication and psychotherapy, and supplemented them with an updated systematic review.
-Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
-Whilst Cuijpers et al.
-[@cuijpersEffectsPsychologicalTreatments2021] excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
-We also included studies which had data available for other variables in interest, including number of sites or baseline demographics; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpersEffectsPsychologicalTreatments2021] literature search.
-We also included three studies from Zhou et al.
-\[\@\] which were not covered in the previous meta-analysis whilst fitting the date range.
-
-Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
-A dataset was made available online though did not include means or standard deviations at baseline or post-test.
-We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
-We excluded three studies because they had no control arm.
-We were unable to locate and therefore complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986).
-Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
-
-We conducted a systematic search for medication studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
-Please see the Supplemental Materials for further details.
-Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and data extraction was completed for these papers.
-
-## Statistical Analysis
-
-### Sample characteristics
-
-We conducted a series of random-effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
-Meta-analyses were implemented using R's Meta package (version 7.0-0).
-
-In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
-
-$$
-\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where, $$\bar{X}$$is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
-The standard deviation is calculated thus:
-
-$$
-\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline.
-
-### Trial design
-
-#### Measures of effect
-
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as:
-
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
-
-where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
-If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
-For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
-If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani et al.'s meta-analysis (for medication studies only).
-
-For the purposes of meta-analysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
-
-$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$
-
-where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
-This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
-However, this practice has given rise to concerns about misestimation.
-Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e.
-bias estimation of the effects for the control group of medication compared to those of psychotherapy.
-Still, to alleviate such concerns we have used a simulations.
-
-In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
-
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
-
-for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
-We then used these simulated datasets in the subsequent meta-analyses.
-
-#### Multilevel model metaregression
+### Multilevel Model Metaregression
 
 We estimated pooled standardized mean differences for each arm by using multilevel models implemented in R's metafor package.
-Unlike the traditional random effects meta-analysis, which assumes that each study's true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
+Unlike the traditional random effects meta-analysis, which assumes that each study’s true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
 This allows us to model variability at both the study level and the study arm level.
@@
 $$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$
+{#eq-7}
 
@@
 
-$$θij​∼N(xij​β,τi2​)$$ {#eq-8}
+$$θij​∼N(xij​β,τi2​)$$
+
+{#eq-8}
 
@@
 
-$$ Yij=xijβ+ui+vij+ϵij $$ {#eq-9}
+$$
+Yij=xijβ+ui+vij+ϵij
+$$
+
+{#eq-9}
 
@@
 
-$$ ui​∼N(0,τ2) $$ {#eq-10}
+$$
+ui​∼N(0,τ2)
+$$
 
+{#eq-10}
 describes the deviation of each study from the overall mean effect size, and
 
-$$vij∼N(0,τi2)$$ {#eq-11}
+$$vij∼N(0,τi2)$$
+{#eq11}
 
@@
 
-$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$ {#eq-12}
+$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$
+
+{#eq-12}
 
@@
 
-$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$ {#eq-13}
+$$ \begin{aligned} Υ_{ij} &=
+\begin{cases}
+0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\
+1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\
+2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\
+3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\
+\end{cases}
+\end{aligned}
+$$
 
+{#eq-13}
 Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
@@
 
-$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$ {#eq-14}
+$$
+z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})}
+$$
 
+{#eq-14}
 This test allows us to assess the significance of the differences between treatment effects across study arms.
-
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
-
-We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
-The SMDs are the means across the 1000 simulated datasets.
-
-#### Number of sites
-
-We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
-
-### Sensitivity Analyses
-
-```{r setting-z-2, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
-# my alpha for the z 
-target_probability <- 1 - 0.05
-
-#start here 
-x <- 1
-
-# two decimals should be fine
-tolerance <- 1e-3
-
-#find the z value using the pnorm function
-while (abs(pnorm(x)) < target_probability ) {
-  x <- x + tolerance  
-}
-
-# Adjust the step size based on your problem  
-cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
-
-x
-
-```
-
-We conducted a series of sensitivity analyses.
-For each of the meta-analyses we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
-Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
-Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
-To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
-
-Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
-
-### Comparing the control and active arms of psychotherapy trials
-
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions.
-We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
-Where a range was provided, the maximum was encoded (e.g.
-if a paper reported that an intervention involved 8-10 sessions lasting 50-60 minutes, we encoded the number and duration of sessions as 10 and 60, respectively).
-If sessions varied in frequency across an intervention, we calculated an average by dividing total number of sessions by length of intervention period.
-Similarly, if the length of sessions varied across the course of the intervention, we calculated a weighted average.
-Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
-
-## Summary of all included trials
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-all-trials
-#| tbl-cap: "Summary of included RCTs"
-#| tbl-cap-location: top
-
-table_all_trials <- df_long_for_metan %>% 
-  select(psy_or_med, new_study_id, arm_effect_size, type, baseline_n, instrument_name, baseline_mean, baseline_sd, post_mean, post_sd, cohens_d)
-
-table_all_trials <- table_all_trials %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(psy_or_med = ifelse(psy_or_med == 0, "Medication", "Psychotherapy")) %>% 
-  mutate(arm_effect_size = ifelse(arm_effect_size == "cohens_d_active", "Active", "Control"))
-
-new_column_names <- c("psy_or_med", "Study", "Arm", "Description", "N", "Instrument", "Baseline M", "Baseline SD", "Post M", "Post SD", "Cohen's d")
-
-# Assign new column names to the data frame
-colnames(table_all_trials) <- new_column_names
-
-table_all_trials %>% 
-  arrange(psy_or_med, Study) %>% 
-  group_by(psy_or_med) %>%
-  as_flextable(hide_grouplabel = TRUE) %>% 
-  merge_v(j = ~Study) %>% 
-  align(j = 4:10, align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  bg(i = c(1, 86), bg = "#F2F2F2", part = "body") %>% 
-  bold(i = c(1, 86), bold = TRUE, part = "body") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  set_table_properties(width = 1, layout = "autofit")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-hamd-baseline
-#| tbl-cap: "HAM-D scores at baseline across psychotherapy and medication RCTs"
-#| tbl-cap-location: top
-
-# now for the ham-d
-# For row names
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_hamd) <- new_column_names
-
-# Rounding
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-results_met_sev_hamd %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the HAMD baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_2_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_hamd_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-# 
-# # Regression results
-# 
-# table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-# 
-# # Assign new column names to the data frame
-# colnames(table_1_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_hamd_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-cdrs-baseline
-#| tbl-cap: "CDRS scores at baseline across psychotherapy and medication RCTs"
-#| tbl-cap-location: top
-
-# For row names
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_cdrs) <- new_column_names
-
-# Rounding
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  slice(1, 3, 2)
-
-results_met_sev_cdrs %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the CDRS baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_2_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-# 
-# # Regression results
-# 
-# table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-# 
-# # Assign new column names to the data frame
-# colnames(table_1_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r sex-all-studies, warning=FALSE, message = FALSE, echo=FALSE}
-
-#Repeating meta-analyses on sample characteristics including studies with females only
-
-#An issue that arise when trying to include studies with 100% female is that their SE ends up being 0, which is treated as NA in the metagen function.
-One way to circumvent this is to apply a continuity correction by adding a constant (e.g 0.5) to percent female.
-These studies will now be treated as having 99.5% females.
-
-#overall sample------------
-
-df_for_sex_metan_no_excl <- df_baseline_demographics %>% 
-  filter(!is.na(percent_women)) %>% #use full dataset to include all studies
-  filter(new_study_id != "March, 2004")# removing TADS because it does not technically belong to either the psy or med groups
-
-#using the formula for se (p*(1-p)/n) we add a constant for studies w 100% female
-
-correction_constant <- 0.5
-
-df_for_sex_metan_no_excl <- df_for_sex_metan_no_excl %>% 
-  mutate(constant_percent_women = ifelse(percent_women==100,percent_women-correction_constant,percent_women)) %>%
-  mutate(product_perc_women=(constant_percent_women/100)*(1-(constant_percent_women/100))) %>%
-  mutate(percent_women_std_error = sqrt(product_perc_women / n_overall))
-
-met_perc_women_no_excl  <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies")
-
-    #Issue: standard error is 0 for 100% female studies so the model     treats them as NA! fix if we want to include all studies in these analyses
-
-met_perc_women_no_excl <- update(met_perc_women_no_excl,
-                              subgroup = df_for_sex_metan_no_excl$psy_or_med, subgroup.name = "treatment modality",
-                              tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-
-results_met_perc_women_no_excl <- extract_stats(met_perc_women_no_excl)
-
-# Clinical only-------------
-
-df_for_sex_metan_no_excl_clin <- df_for_sex_metan_no_excl %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_perc_women_no_excl_clin <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across clinical studies")
-
-met_perc_women_no_excl_clin <- update(met_perc_women_no_excl_clin,
-                           subgroup = df_for_sex_metan_no_excl_clin$psy_or_med, subgroup.name = "treatment modality",
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_excl_clin <- extract_stats(met_perc_women_no_excl_clin)
-
-# Excluding wl--------------
-
-df_for_sex_metan_no_excl_no_wl <- df_for_sex_metan_no_excl %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_perc_women_no_excl_no_wl <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies with controls that are not wl",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_excl_no_wl <- extract_stats(met_perc_women_no_excl_no_wl)
-
-## Combine results for table
-
-df_baseline_results_no_excl <- rbind(results_met_perc_women_no_excl, results_met_perc_women_no_excl_clin, results_met_perc_women_no_excl_no_wl)
-
-# For row names
-df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
-  mutate(subgroup = case_when(
-    row_number() %in% 1 ~ "Overall",
-    row_number() %in% 4 ~ "Excluding subclinical",
-    row_number() %in% 7 ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_baseline_results_no_excl) <- new_column_names
-
-# Rounding
-df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-big_border = fp_border(color="black", width = 1)
-small_border = fp_border(color="lightgray", width = 1)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-all-studies-percfemale-results
-#| tbl-cap: "Percentage female at baseline across medication and psychotherapy studies: Results for sample including all female studies"
-#| tbl-cap-location: top
-
-df_baseline_results_no_excl %>% 
-  as_flextable() %>% 
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
-  bg(i = 1, bg  = "#F2F2F2", part = "body") %>% # identify category sections
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% # indent some rows
-  align(j = 2:ncol(df_baseline_results_no_excl), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  line_spacing(space = .7, part = "all") %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-```
-
-#### Multilevel metaregression results
-
-In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-Here, medication control is the reference category to which all others are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p\<0.0001).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
-#| label: tbl-results-overall
-#| tbl-cap: "Results from metaregression with overall sample"
-#| tbl-cap-location: top
-
-#add i2 to aggregate results
-aggregate_results_overall_i2 <- cbind(aggregate_results_overall, 
-                                   i2_2 = rep(i2_summary_all$mean_i2_level2, nrow(aggregate_results_overall)),
-                                   i2_3 = rep(i2_summary_all$mean_i2_level3, nrow(aggregate_results_overall)))
-
-# Regression results
-
-aggregate_results_overall_i2 <- aggregate_results_overall_i2 %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "coefficients")
-
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2_1", "T2_2", "QE", "k", "I2_2", "I2_3")
-
-# Assign new column names to the data frame
-colnames(aggregate_results_overall_i2) <- new_column_names
-
-table_aggregate_results_overall_i2 <- aggregate_results_overall_i2[, 1:6]
-table_aggregate_results_overall_i2[1, 4] <- NA
-
-flextable(table_aggregate_results_overall_i2) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "T2_2"],
-                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "I2_3"], 
-                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "I2_2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall_i2[1, "k"], "."), colwidths = 6) %>%
-  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-  # add_header_row(values = "Table 4", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_aggregate_results_overall_i2), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-mean_diff_min_max_scores <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) + 
-  geom_jitter(width = 0.2) + 
-  ggtitle("Post-Pre Differences in Mean Min-Max Scores") + 
-  ylab("Post-Pre Difference") +
-  xlab("Type of Study") +
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) +   theme_minimal()
-
-print(mean_diff_min_max_scores) 
-png("mean_diff_min_max_scores.png")
-mean_diff_min_max_scores
-dev.off()
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# create baseline variances
-df_long_for_metan$variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-plot_baseline_var <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) + geom_jitter(width = 0.2) +  
-  ggtitle("Post-Pre Differences in Study Baseline Variances") + 
-  ylab("Baseline Variance") + 
-  xlab("Type of Study") + 
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + theme_minimal()
-
-print(plot_baseline_var)
-png("plot_baseline_var.png")
-plot_baseline_var
-dev.off()
-```
-
-## Metaregression sensitivity analyses
-
-```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-no-wl
-#| fig-cap: "Meta-analytic estimates of within-group changes: waitlist studies excluded"
-#| fig-cap-location: top
-#| fig-title: Figure S
-
-coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl)
-print(plot_means_no_wl)
-
- png("plot_means_multi_no_wl.png")
-plot_means_no_wl
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-clin
-#| fig-cap: "Meta-analytic estimates of within-group changes: subclinical studies excluded"
-#| fig-cap-location: top
-
-coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
-plot_means_clin <- plot_means_function(coef_and_se_means_clin_study)
-print(plot_means_clin)
-
-png("plot_means_multi_clin.png")
-plot_means_clin
-dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-cdrs
-#| fig-cap: "Meta-analytic estimates of within-group changes: CDRS studies only"
-#| fig-cap-location: top
-
-coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
-plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study)
-print(plot_means_cdrs)
-
- png("plot_means_multi_cdrs.png")
- plot_means_cdrs
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-hamd
-#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
-#| fig-cap-location: top
-
-coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_multi_hamd <- plot_means_function(coef_and_se_means_hamd_study)
-print(plot_means_multi_hamd)
-
- png("plot_means_multi_hamd.png")
- plot_means_multi_hamd
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-postsd
-#| fig-cap: "Meta-analytic estimates of within-group changes: studies with post SD"
-#| fig-cap-location: top
-
-coef_and_se_means_sd_study <- coef_and_se_means_sd_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: studies with post SD"
-plot_means_multi_sd <- plot_means_function(coef_and_se_means_sd_study)
-print(plot_means_multi_sd)
-
- png("plot_means_multi_sd.png")
- plot_means_multi_sd
- dev.off()
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-var2
-#| fig-cap: "Meta-analytic estimates of within-group changes: studies with variance <0.02"
-#| fig-cap-location: top
-
-coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study)
-print(plot_means_multi_var2)
-
- png("plot_means_multi_var2.png")
- plot_means_multi_var2
- dev.off()
-```
-
-#### Effect of standard errors of the SMDs
-
-It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
-To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
-If standard error distributions were influential, this should show up as substantial variability across simulations.
-We test this idea in the @fig-stab-sims which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in @tbl-results-overall).
-As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
-the value of z = 1.645.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-stab-sims
-#| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
-#| fig-cap-location: top
-
-# examine the stability of the simulations
-
-z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_meta_reg)){
-z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
-
-}
-
-stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-
-stab_sims <- stability_sims %>%
-  ggplot(aes(x = n_sims, y = z_value)) +
-  geom_point() +
-  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
-           hjust = -0.1, vjust = 0) +
-  theme_minimal() +
-  labs(
-    x = "Number of Simulations",
-    y = "z-value",
-    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-    subtitle = "Results from 1000 simulations with within-group standard errors"
-  )
-
-print(stab_sims)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-adj-smds
-# #| tbl-cap: "SMDs adjusted by baseline scores"
-# #| tbl-cap-location: top
-# 
-# table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) 
-# 
-# new_column_names <- c("Condition", "Coefficient", "SE", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_mean_coefs_from_sim_adjusted_cohens_d) <- new_column_names
-# 
-# flextable(table_mean_coefs_from_sim_adjusted_cohens_d) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_mean_coefs_from_sim_adjusted_cohens_d), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-# 
-# aggregate_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>% 
-#   relocate("condition", .before = "coefficients") 
-# 
-# new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
-# 
-# # Assign new column names to the data frame
-# colnames(aggregate_results_overall_adjusted_cohens_d) <- new_column_names
-# 
-# table_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d[, 1:6]
-# 
-# flextable(table_results_overall_adjusted_cohens_d) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "T2"],
-#                       "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "I2"], 
-#                       "; ", as_i("K"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "k"],
-#                       "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "R2"], "."), colwidths = 6) %>%
-#   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-#   # add_header_row(values = "Table 4", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-de-meaned
-#| tbl-cap: "Results from baseline-adjusted model"
-#| tbl-cap-location: top
-
-de_meaned_smd_with_cis <- de_meaned_smd_with_cis %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-new_column_names <- c("Condition", "SMDs", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(de_meaned_smd_with_cis) <- new_column_names
-
-flextable(de_meaned_smd_with_cis) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(de_meaned_smd_with_cis), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-
-table_coefs_lm_for_baseline_means <- coefs_lm_for_baseline_means[c(1, 3:5),]
-
-table_coefs_lm_for_baseline_means <- table_coefs_lm_for_baseline_means %>%
-  mutate(across(where(is.numeric) & !matches("p.value"), ~ round(., 2))) %>%
-  mutate(`p.value` = ifelse(`p.value` < 0.001, "< 0.001", sprintf("%.3f", `p.value`)))
-
-new_column_names <- c("Condition", "Estimate", "SE", "t value", "p-value")
-
-# Assign new column names to the data frame
-colnames(table_coefs_lm_for_baseline_means) <- new_column_names
-
-table_coefs_lm_for_baseline_means$Condition <- c("Medication Control", "Medication Active", "Psychotherapy Control", "Psychotherapy Active")
-
-flextable(table_coefs_lm_for_baseline_means) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  # italic(i = 2, italic = TRUE, part = "header") %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_coefs_lm_for_baseline_means), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  font(fontname = "Calibri", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-```
-
-```{r , warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-
-# We want to compare active v control arms when we filter out wl conditions
-
-df_descr_psy_conditions_no_wl <- df_descr_psy_conditions %>% 
-  filter(new_study_id %in% no_wl_ids)
-
-df_descr_psy_conditions_no_wl <- df_descr_psy_conditions_no_wl %>% 
-    filter(!(treatment == "wlc"))
-
-sessions <- group_function(df_descr_psy_conditions_no_wl,"levels_var","no_sessions")
-frequency <- group_function(df_descr_psy_conditions_no_wl,"levels_var","freq_weeks")
-length_sessions_mins <- group_function(df_descr_psy_conditions_no_wl,"levels_var","length_sessions_mins")
-total_hours <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_hours")
-
-control_summary_no_wl <- rbind(sessions, frequency, length_sessions_mins, total_hours)
-
-control_summary_no_wl <- control_summary_no_wl %>% 
-  select(-c(Median, IQR))
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(Group = case_when(
-    Group == "psychotherapy_active" ~ "Active",
-    Group == "psychotherapy_control" ~ "Control",
-    TRUE ~ as.character(Group)  # Keep other values unchanged
-  ))
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(Column = case_when(
-    Column == "no_sessions" ~ "Number of sessions",
-    Column == "freq_weeks" ~ "Intensity (sessions per week)",
-    Column == "length_sessions_mins" ~ "Session length (mins)",
-    Column == "total_hours" ~ "Total intervention hours",
-    TRUE ~ as.character(Column)  # Keep original value if no match
-  ))
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions_no_wl)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions_no_wl)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions_no_wl)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-
-control_summary_t_tests_no_wl <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
-
-# For row names
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests_no_wl) <- new_column_names
-
-#Rounding
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
-
-# calculating with my function
-
-# session_es_no_wl <- effect_btwn(sessions)
-# frequency_es_no_wl <- effect_btwn(frequency)
-# length_sessions_mins_es_no_wl <- effect_btwn(length_sessions_mins)
-# total_hours_es_no_wl <- effect_btwn(total_hours)
-# total_period_weeks_es_no_wl <- effect_btwn(total_period_weeks)
-
-# using a package to calculate instead
-
-session_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$no_sessions ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-frequency_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$freq_weeks ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-length_sessions_mins_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$length_sessions_mins ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-total_hours_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$total_hours ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-
-# going to try displaying summary statistics and t-tests in one place
-
-control_summary_no_wl <- cbind(control_summary_no_wl, 
-                          "Cohen's d" = rep(NA, nrow(control_summary_no_wl)),
-                         "Upper CI" = rep(NA, nrow(control_summary_no_wl)),
-                         "Lower CI" = rep(NA, nrow(control_summary_no_wl)),
-                         t = rep(NA, nrow(control_summary_no_wl)), 
-                          df = rep(NA, nrow(control_summary_no_wl)), 
-                          "p-value" = rep(NA, nrow(control_summary_no_wl)))
-
-# Update the first row with session_es_no_wl
-control_summary_no_wl[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  session_es_no_wl$estimate, session_es_no_wl$conf.int[1], session_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[1], control_summary_t_tests_no_wl$df[1], 
-  control_summary_t_tests_no_wl$`p-value`[1]
-)
-
-# Update the third row with frequency_es_no_wl
-control_summary_no_wl[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  frequency_es_no_wl$estimate, frequency_es_no_wl$conf.int[1], frequency_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[2], control_summary_t_tests_no_wl$df[2], 
-  control_summary_t_tests_no_wl$`p-value`[2]
-)
-
-# Update the fifth row with length_sessions_mins_es_no_wl
-control_summary_no_wl[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  length_sessions_mins_es_no_wl$estimate, length_sessions_mins_es_no_wl$conf.int[1], length_sessions_mins_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[3], control_summary_t_tests_no_wl$df[3], 
-  control_summary_t_tests_no_wl$`p-value`[3]
-)
-
-# Update the seventh row with total_hours_es_no_wl
-control_summary_no_wl[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  total_hours_es_no_wl$estimate, total_hours_es_no_wl$conf.int[1], total_hours_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[4], control_summary_t_tests_no_wl$df[4], 
-  control_summary_t_tests_no_wl$`p-value`[4]
-)
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(
-    `Cohen's d` = as.numeric(`Cohen's d`),
-    `Upper CI` = as.numeric(`Upper CI`),
-    `Lower CI` = as.numeric(`Lower CI`)
-  ) %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-intensity-of-int-no-wl
-#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
-#| tbl-cap-location: top
-
-as_grouped_data(control_summary_no_wl, groups = "Column") %>% 
-  as_flextable(hide_grouplabel = TRUE ) %>% 
-  bold(i = c(1, 4, 7, 10), bold = TRUE, part = "body") %>%  
-  set_table_properties(width = 1) %>%  # Set table width 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:9, align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
-  # add_header_row(values = "Table 5", colwidths = 4) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(j = 1:4, part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = c(1,4), part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-t-tests-intensity-no-wl
-# #| tbl-cap: "Results for t-tests comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
-# #| tbl-cap-location: top
-# 
-# flextable(control_summary_t_tests_no_wl) %>%
-#   set_table_properties(width = 1) %>%  # Set table width %>% 
-#   autofit() %>%  # Autofit column widths 
-#   align(j = 2:ncol(control_summary_t_tests_no_wl), align = "center", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   #italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   paginate(init = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Plots  -----------------------
-
-#define groups
-# df_long_for_metan <- df_long_for_metan %>%
-#   mutate(
-#     group = case_when(
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-#       TRUE ~ NA_character_
-#     )
-#   )
-# 
-# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-
-# # Scatter plot cohens d per arm
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
-# Box plot Cohens d by group
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_fill_manual(values = group_colors) +
-#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
-```
-
-# References

### 2024-10-04 multilevel_metaregression/manuscript_render_test.qmd
saving test files

--- 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
@@
 title: "Comparing Apples and Oranges in Youth Depression Treatments?"
-subtitle: "A Quantitative Critique of the Evidence Base and Guidelines"
-author:
-  - name: Argyris Stringaris
-    email: a.stringaris@ucl.ac.uk
-    affiliations: 
-        - id: ucl_1
-          name: University College London
-          department: Divisions of Psychiatry and Psychology and Language Science
-          address: 1-19 Torrington Place
-          city: London, UK
-          state: 
-          postal-code: WC1E 7HB
-          country: United Kingdom
-    attributes:
-        corresponding: true
-    note: 
-  - name: Charlotte Burman
-    email: charlotte.burman@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-  - name: Raphaelle Delpech
-    email: raphaelle.delpech.18@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Rudolf Uher
-    email: uher@Dal.Ca
-    affiliations:
-        - id: dal
-          name: Dalhousie University
-          department: Department of Psychiatry
-          address: 
-          city: Nova Scotia
-          state: 
-          postal-code: 
-          country: Canada
-  - name: Dayna Bhudia
-    email: dayna.bhudia@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Despoina Miliou
-    email: dgmiliou@outlook.com.gr
-    affiliations:
-        - ref: ucl_1
-  - name: Ioannis-Marios Rokas
-    email: rokasgiannis93@gmail.com
-    affiliations:
-        - ref: ucl_1
-  - name: Marinos Kyriakopoulos
-  - name: Lucy Foulkes
-    email: lucy.foulkes@psych.ox.ac.uk
-    affiliations:
-        - id: OU
-          name: University of Oxford
-          department: Experimental Psychology
-          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
-          city: Oxford
-          postal-code: OX2 6GG
-          country: United Kingdom
-    note:
-  - name: Carmen Moreno
-    email: cmoreno@hggm.es
-    affiliations:
-        - id: HGM
-          name: Hospital Gregorio Marañón
-          department: Department of Psychiatry
-          address: 46 C. del Dr. Esquerdo
-          city: Madrid
-          state:
-          postal-code: 28007
-          country: Spain
-  - name: Samuele Cortese
-    email: samuele.cortese@soton.ac.uk
-    affiliations:
-        - id: soton
-          name: University of Southampton
-          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
-          address: Highfield Campus, Building 44
-          city: Southampton
-          state:
-          postal-code: SO17 1BJ
-          country: United Kingdom
-  - name: Glyn Lewis
-    email: glyn.lewis@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1        
-  - name: Georgina Krebs
-    email: g.krebs@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-keywords: 
-  - depression
-  - adolescents
-  - antidepressants
-  - psychotherapy
-date: last-modified
+author: "Argyris Stringaris"
+date: "05-09-2024"
 format:
@@
     fig-height: 7
-    fig_caption: yes
-    tbl_caption: yes
+    fig_caption: true
+    tbl_caption: true
     number-sections: true
@@
   echo: true
-  auto: true
   warning: FALSE
@@
 library(here)
+library(officer)
 
@@
 # For referencing
-bib_data <- ReadBib(here("multilevel_metaregression", "bibliography", "references.bib"))
-
+bib_data <- ReadBib(here::here("multilevel_metaregression", "bibliography", "references.bib"))
+
+#some set-up for flextables
+big_border = fp_border(color="black", width = 1)
+small_border = fp_border(color="lightgray", width = 1)
 ```
@@
 In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
+
 **Methods:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
@@
 Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
+
 **Results:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
@@
 Within psychotherapy RCTs, control conditions were less intensive on average than active conditions.
+
 **Conclusions:** Medication and psychotherapy RCTs differ on fundamental participant and methodological characteristics, thereby violating key conditions for valid comparison between them.
@@
 
-```{r define-functions, warning=FALSE, message = FALSE, echo=FALSE}
+```{r define-functions, warning=FALSE, message = FALSE, echo=FALSE, cache=FALSE}
 #############Some custom made functions#############
@@
   df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  tau_sq_1 <- rep(NA, n_models)
-  tau_sq_2 <- rep(NA, n_models)
+  tau_sq <- rep(NA, n_models)
   qe <- rep(NA, n_models)
@@
     model <- list_model_1_meta_reg[[i]]
-    tau_sq_1[i] <- model$sigma2[1]
-    tau_sq_2[i] <- model$sigma2[2]
+    tau_sq[i] <- model$tau2
     qe[i] <- model$QE
@@
     upper_ci = colMeans(df_upper_ci, na.rm = TRUE),
-    tau_sq_1 = mean(tau_sq_1, na.rm.= TRUE),
-    tau_sq_2 = mean(tau_sq_2, na.rm.= TRUE),
+    tau_sq = mean(tau_sq, na.rm = TRUE),
     qe = mean(qe, na.rm = TRUE),
@@
 
-###########8. Function for extracting multilevel I2 estimates
-
-extract_i2_values <- function(list_of_models) {
-  # Initialize vectors to store I2 values
-  i2_level2 <- numeric(length(list_of_models))
-  i2_level3 <- numeric(length(list_of_models))
-
-  # Loop through each fitted model from the list
-  for (i in seq_along(list_of_models)) {
-    model <- list_of_models[[i]]
-
-    # Calculate variance distribution using the existing function
-    i2_results <- var.comp(model)
-
-    # Extract I2 values for level 2 and level 3 from the results
-    i2_level2[i] <- as.numeric(i2_results$results$I2[2]) # I2 for level 2
-    i2_level3[i] <- as.numeric(i2_results$results$I2[3]) # I2 for level 3
-  }
-
-  # Combine I2 values into a data frame
-  i2_data <- data.frame(
-    i2_level2 = i2_level2,
-    i2_level3 = i2_level3
-  )
-
-  return(i2_data)
-}
-
 ```
 
-```{r import-dataset, warning=FALSE, message = FALSE, echo=FALSE}
+```{r import-dataset, warning=FALSE, message = FALSE, echo=FALSE, cache=FALSE}
 
@@
 
-df_appl_v_orange <-readxl::read_excel(here("df_appl_v_orange.xlsx"))
+df_appl_v_orange <-readxl::read_excel(here::here("df_appl_v_orange.xlsx"))
 
@@
 
-df_scale_ranges <- read.csv(here("scale_ranges.csv"))
+df_scale_ranges <- read.csv(here::here("scale_ranges.csv"))
 df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
@@
 
-```{r metaregression-all, warning=FALSE, message = FALSE, echo=FALSE}
+```{r run-metaregressions, cache=FALSE, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 # A) the overall sample
-# B) the CBT vs Fluox and Escitalopram sample
-# C) the no WL sample
-# D) clinical levels of depression
-# E) the CDRS only sample
+# B) the no WL sample
+# C) clinical levels of depression
+# D) the CDRS only sample
 # E) HAMD sensitivity analysis
-# G) Studies with post SD
-# H) Studies with variance <.02
+# F) Studies with post SD
+# G) Studies with variance <.02
 
@@
                                     by = "condition")
-
-# Extract I2 values for each dataset
-i2_results_all <- extract_i2_values(list_model_1_meta_reg)
-
-# Calculate the mean and standard deviation of I2 values for each level
-i2_summary_all <- data.frame(
-  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
-  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
-  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
-  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
-)
-```
-
-```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
-# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-#  grab ids for those studies
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox.
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria.
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc.
-# We may have multiple controls per study id for this reason, though this isn't a problem
-# conceptually.
-
-list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-})
-
-# count the number of studies
-cbt_fluox_esc_study <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids,
-         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# CB checked, looks good now.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
- coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-```
-
-```{r metaregression-nowl, warning=FALSE, message = FALSE, echo=FALSE}
-
-# C. Estimate Means and CIs without WL ---------------------------------------
+# C. Estimate Means and CIs without WL---------------------------------------
 
@@
                                     by = "condition")
-```
-
-```{r metaregression-clin, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
-```
-
-```{r metaregression-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
-```
-
-```{r metaregression-hamd, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
                                     by = "condition")
-
 ```
 
-```{r metaregression-postsd, warning=FALSE, message = FALSE, echo=FALSE}
-
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
+## Included studies
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, results='hide'}
+#| label: tbl-all-trials
+#| tbl-cap: "Summary of included RCTs"
+#| tbl-cap-location: top
+
+table_all_trials <- df_long_for_metan %>% 
+  select(psy_or_med, new_study_id, arm_effect_size, type, baseline_n, instrument_name, baseline_mean, baseline_sd, post_mean, post_sd, cohens_d)
+
+table_all_trials <- table_all_trials %>%
+  mutate(across(where(is.numeric), ~round(., 2))) %>% 
+  mutate(psy_or_med = ifelse(psy_or_med == 0, "Medication", "Psychotherapy")) %>% 
+  mutate(arm_effect_size = ifelse(arm_effect_size == "cohens_d_active", "Active", "Control"))
+
+new_column_names <- c("psy_or_med", "Study", "Arm", "Description", "N", "Instrument", "Baseline M", "Baseline SD", "Post M", "Post SD", "Cohen's d")
+
+# Assign new column names to the data frame
+colnames(table_all_trials) <- new_column_names
+
+table_all_trials %>% 
+  arrange(psy_or_med, Study) %>% 
+  group_by(psy_or_med) %>%
+  as_flextable(hide_grouplabel = TRUE) %>% 
+  merge_v(j = ~Study) %>% 
+  align(j = 4:10, align = "center", part = "all") %>% 
+  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
+  bold(part = "header") %>%   # Bold the relevant header rows
+  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
+  bg(i = c(1, 86), bg = "#F2F2F2", part = "body") %>% 
+  bold(i = c(1, 86), bold = TRUE, part = "body") %>% 
+  border_remove() %>% # this is to remove borders that look strange
+  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
+  vline(j = 1, part = "body", border = small_border) %>% 
+  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
+  hline(part = "header", border = big_border) %>% 
+  line_spacing(space = .7, part = "all") %>% 
+  set_table_properties(width = 1, layout = "autofit")
 
 ```
-
-```{r metaregression-var, warning=FALSE, message = FALSE, echo=FALSE}
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
-
-## Included studies
 
@@
 
-```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
-
-mean_psych_overall <- 0.37
-mean_med_overall <- 0.42
-se_psych_overall <- 0.02
-se_med_overall <- 0.01
-n_psych_overall <- 49
-n_med_overall <- 31
-
-# Calculate standard deviation
-sd_psych_overall <- se_psych_overall * sqrt(n_psych_overall)
-sd_med_overall <- se_med_overall * sqrt(n_med_overall)
-
-#formula with pooled sd
-pooled_sd_overall <- sqrt(((sd_psych_overall^2 + sd_med_overall^2)/2))
-
-# Calculate Cohen's d
-cohens_d_overall <- (mean_psych_overall - mean_med_overall) / pooled_sd_overall
-
-## without subclinical
-
-mean_psych_sub <- 0.39
-mean_med_sub <- 0.42
-se_psych_sub <- 0.02
-se_med_sub <- 0.01
-n_psych_sub <- 41
-n_med_sub <- 31
-
-# Calculate standard deviation
-sd_psych_sub <- se_psych_sub * sqrt(n_psych_sub)
-sd_med_sub <- se_med_sub * sqrt(n_med_sub)
-
-#formula with pooled sd
-pooled_sd_sub <- sqrt(((sd_psych_sub^2 + sd_med_sub^2)/2))
-
-# Calculate Cohen's d
-cohens_d_sub <- (mean_psych_sub - mean_med_sub) / pooled_sd_sub
-cohens_d_sub
-cohens_d_overall
-```
-
 ### Baseline severity
@@
 To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS and HAM-D, on which there was a sufficient number of studies to metanalyse.
-As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplemental Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
+As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplement), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
 
@@
 For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016; see @tbl-all-studies-percfemale-results in Supplement for results with full sample).
-As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
+As can be seen in @tbl-baseline-results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
 On average, samples were `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`) female across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`) female across medication trials.
@@
 
-As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = ``` r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2) ```) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
+As can be seen in @tbl-baseline-results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2)`) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
 There were no significant differences in mean age between modalities on further sensitivity analyses.
@@
   )
-
 ```
@@
 
- png("plot_means_multi_all.png")
- plot_means_multi_all
- dev.off()
+# png("plot_means_multi_all.png")
+# plot_means_multi_all
+# dev.off()
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-coefs-overall
-# #| tbl-cap: "Summary statistics of the estimated SMDs"
-# #| tbl-cap-location: top
-# 
-# # Prepare to tabulate
-# 
-# table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   relocate("n", .after = "condition") 
-# 
-# new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_mean_coefs_from_sim) <- new_column_names
-# 
-# flextable(table_mean_coefs_from_sim) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>% 
-#   # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
-#   # add_header_row(values = "Table 3", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
+##### Sensitivity analyses
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+#| label: fig-plot-means-no-wl
+#| fig-cap: "Meta-analytic estimates of within-group changes: waitlist studies excluded"
+#| fig-cap-location: top
+#| fig-title: Figure S
+
+coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
+plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl)
+print(plot_means_no_wl)
+
+ #png("plot_means_multi_no_wl.png")
+#plot_means_no_wl
+ #dev.off()
 
@@
 
-##### Sensitivity analyses
+```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+#| label: fig-plot-means-clin
+#| fig-cap: "Meta-analytic estimates of within-group changes: subclinical studies excluded"
+#| fig-cap-location: top
+
+coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
+plot_means_clin <- plot_means_function(coef_and_se_means_clin_study)
+print(plot_means_clin)
+
+# png("plot_means_multi_clin.png")
+# plot_means_clin
+# dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+#| label: fig-plot-means-cdrs
+#| fig-cap: "Meta-analytic estimates of within-group changes: CDRS studies only"
+#| fig-cap-location: top
+
+coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
+plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study)
+print(plot_means_cdrs)
+
+ # png("plot_means_multi_cdrs.png")
+ # plot_means_cdrs
+ # dev.off()
+
+```
+
+```{r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+#| label: fig-plot-means-hamd
+#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
+#| fig-cap-location: top
+
+coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
+  mutate(condition = case_when(
+    condition == "medication_control" ~ "Medication Control",
+    condition == "medication_active" ~ "Medication Active",
+    condition == "psychotherapy_control" ~ "Psychotherapy Control",
+    condition == "psychotherapy_active" ~ "Psychotherapy Active",
+    TRUE ~ as.character(condition)))
+
+# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
+plot_means_multi_hamd <- plot_means_function(coef_and_se_means_hamd_study)
+print(plot_means_multi_hamd)
+
+ # png("plot_means_multi_hamd.png")
+ # plot_means_multi_hamd
+ # dev.off()
+
+```
+
+`{# {r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'} # #| label: fig-plot-means-postsd # #| fig-cap: "Meta-analytic estimates of within-group changes: studies with post SD" # #| fig-cap-location: top #  # coef_and_se_means_sd_study <- coef_and_se_means_sd_study %>% #   mutate(condition = case_when( #     condition == "medication_control" ~ "Medication Control", #     condition == "medication_active" ~ "Medication Active", #     condition == "psychotherapy_control" ~ "Psychotherapy Control", #     condition == "psychotherapy_active" ~ "Psychotherapy Active", #     TRUE ~ as.character(condition))) #  # # subtitle_text_hamd <- "Metanalytic estimates of within-group changes: studies with post SD" # plot_means_multi_sd <- plot_means_function(coef_and_se_means_sd_study) # print(plot_means_multi_sd) #  #  # png("plot_means_multi_sd.png") #  # plot_means_multi_sd #  # dev.off()`
+
+`{# {r, warning=FALSE, message = FALSE, echo=FALSE, results='hide'} # #| label: fig-plot-means-var2 # #| fig-cap: "Meta-analytic estimates of within-group changes: studies with variance <0.02" # #| fig-cap-location: top #  # coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>% #   mutate(condition = case_when( #     condition == "medication_control" ~ "Medication Control", #     condition == "medication_active" ~ "Medication Active", #     condition == "psychotherapy_control" ~ "Psychotherapy Control", #     condition == "psychotherapy_active" ~ "Psychotherapy Active", #     TRUE ~ as.character(condition))) #  # # subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only" # plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study) # print(plot_means_multi_var2) #  #  # png("plot_means_multi_var2.png") #  # plot_means_multi_var2 #  # dev.off()`
 
@@
 
-df_binary_site_count <- df_baseline_demographics %>% 
-  group_by(psy_or_med, site_binary) %>% 
-  summarize(num_trials = n())
+# df_baseline_demographics %>%
+#   group_by(psy_or_med, site_binary) %>%
+#   summarize(num_trials = n())
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-## | label: tbl-sites-summary
-## | tbl-cap: "Number of sites across medication and psychotherapy studies"
-## | tbl-cap-location: top
-#
-# flextable(df_sites_summary_stats) %>%
-#   set_table_properties(width = 1, layout = "fixed") %>%
-#   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
-#                       "; ", as_i("p "), sites_t_test_stats$p_value, 
-#                       "; 95% CI: ", sites_t_test_stats$ci_lower,
-#                       "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
-#   # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
-#   # add_header_row(values = "Table 2", colwidths = 4) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>% 
-#   autofit() %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
 Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 25 of 46 (54%) psychotherapy studies.
+Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-t-tests-intensity
-# #| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-# #| tbl-cap-location: top
-# 
-# flextable(control_summary_t_tests) %>%
-#   set_table_properties(width = 1) %>%  # Set table width %>% 
-#   autofit() %>%  # Autofit column widths 
-#   align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   #italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   paginate(init = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
 As seen in @tbl-intensity-of-int, active conditions featured significantly more sessions when compared to control conditions.
@@
 # Conclusions and Clinical Implications
-
-```{r proportion-wl, echo=FALSE}
-# Filter the dataframe
-# filtered_df <- df_long_for_metan %>%
-#   filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
-# 
-# # Count the occurrences of each type
-# type_counts <- filtered_df %>%
-#   count(type) %>%
-#   mutate(total_count = sum(n),
-#          wl_sum = sum(n[type == "wl"]),
-#          wl_percentage = wl_sum / total_count * 100)
-# 
-# # how many examples of matching of active and control in number of hours
-# 
-# instances_count <- df_descr_psy_conditions_no_wl %>%
-#   filter(!is.na(total_hours)) %>%
-#   group_by(new_study_id, total_hours) %>%
-#   summarise(count = n()) %>%
-#   filter(count > 1) %>%
-#   summarise(total_instances = n())
-
-```
 
@@
 
-# Supplemental Materials
-
-## Systematic review description and search terms
-
-We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
-after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review).
-We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
-We used the same search terms as Cipriani [@ciprianiComparativeEfficacyTolerability2016] with one additional search term to include only placebo-controlled trials (see below).
-We additionally applied filters to specify our date range, and to exclude reviews and non-human studies.
-We also searched clinical trial registers for published and unpublished studies however all RCTs meeting inclusion criteria had already been identified from the database search outlined above.
-Please see fig-prisma for the PRISMA flow diagram.
-
-We used Covidence, an online software tool, to manage our systematic review.
-Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and data extraction was completed for these papers.
-
-**Search terms**
-
-Explicit search strategy: title/abstract = (depress\* or dysthymi\* or "mood disorder\*" or "affective disorder\*") AND (adolesc\* or child\* or boy\* or girl\* or juvenil\* or minors or paediatri\* or pediatri\* or pubescen\* or school\* or student\* or teen\* or young or youth\*) AND (selective serotonin reuptake inhibitor or SSRI or citalopram or fluoxetine or paroxetine or sertraline or escitalopram or fluvoxamine or serotonin norepinephrine reuptake inhibitor\* or SNRI or venlafaxine or duloxetine or milnacipran or reboxetine or bupropion or noradrenergic and specific serotonergic antidepressants or NaSSA or mirtazapine or TCA or tricyclic or amersergide or amineptine or amitriptyline or amoxapine or butriptyline or chlorpoxiten or clomipramine or clorimipramine or demexiptiline or desipramine or dibenzipin or dothiepin or doxepin or imipramine or lofepramine or melitracen or metapramine or nortriptyline or noxiptiline or opipramol or protriptyline or quinupramine or tianeptine or trimipramine) AND (placebo)
-
-##References for included trials
-
-References for trials included in the existing meta-analyses drawn upon for this study can be found at <https://docs.metapsy.org/databases/depression-childadol-psyctr/> for psychotherapy RCTs and at <https://ora.ox.ac.uk/objects/uuid:e0b5ae23-d562-4348-94b8-84f70b7812c5> for medication RCTs.
-Below are references for the seven additional RCTs identified in the original systematic review conducted for the current study.
-
-*Publications*
-
-Atkinson, S., Lubaczewski, S., Ramaker, S., England, R.
-D., Wajsbrot, D.
-B., Abbas, R., & Findling, R.
-L.
-(2018).
-Desvenlafaxine versus placebo in the treatment of children and adolescents with major depressive disorder.
-*Journal of Child and Adolescent Psychopharmacology, 28(1),* 55-65.
-DOI: 10.1089/cap.2017.0099
-
-Durgam, S., Chen, C.
-Z., Migliore, R., Prakash, C., Edwards, J., & Findling, R.
-L.
-(2018).
-A phase 3, double-blind, randomized, placebo-controlled study of vilazodone in adolescents with major depressive disorder.
-*Pediatric Drugs, 20(4),* 353-363.
-DOI: 10.1007/s40272-018-0290-4
-
-Findling, R.
-L., McCusker, E., & Strawn, J.
-R.
-(2020).
-A randomized, double-blind, placebo-controlled trial of vilazodone in children and adolescents with major depressive disorder with twenty-six-week open-label follow-up.
-*Journal of Child and Adolescent Psychopharmacology, 30(6),* 355-365.
-DOI: 10.1089/cap.2019.0176
-
-Le Noury, J., Nardo, J.
-M., Healy, D., Jureidini, J., Raven, M., Tufanaru, C., & Abi-Jaoude, E.
-(2015).
-Restoring Study 329: efficacy and harms of paroxetine and imipramine in treatment of major depression in adolescence.
-*BMJ, 351,*, h4320.
-DOI: 10.1136/bmj.h4320
-
-Weihs, K.
-L., Murphy, W., Abbas, R., Chiles, D., England, R.
-D., Ramaker, S., & Wajsbrot, D.
-B.
-(2018).
-Desvenlafaxine versus placebo in a fluoxetine-referenced study of children and adolescents with major depressive disorder.
-Journal of Child and Adolescent Psychopharmacology, 28(1), 36-46.
-DOI: 10.1089/cap.2017.0100
-
-*Unpublished clinical trials*
-
-Active Reference (Fluoxetine) Fixed-dose Study of Vortioxetine in Paediatric Patients Aged 12 to 17 Years With Major Depressive Disorder (MDD).
-ClinicalTrials.gov Identifier: NCT02709746.
-Accessed 17 Jan 2024.
-
-Safety and Efficacy of Levomilnacipran ER in Adolescent Participants With Major Depressive Disorder. ClinicalTrials.gov Identifier: NCT02431806. Accessed 17 Jan 2024.
-
-## Hierarchy of depression symptom severity measurement scales
-
-Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. [@ciprianiComparativeEfficacyTolerability2016].
-
-1.  Children's Depression Rating Scale (CDRS)
-2.  Hamilton Depression Rating Scale (HAMD)
-3.  Montgomery Asberg Depression Rating Scale (MADRS)
-4.  Beck Depression Inventory (BDI)
-5.  Children's Depression Inventory (CDI)
-6.  Schedule for Affective Disorders and Schizophrenia for School-Aged Children (K-SADS)
-7.  Mood and Feeling Questionnaire (MFQ)
-8.  Reynolds Adolescent Depression Scale (RADS)
-9.  Bellevue Index of Depression (BID)
-10. Child Depression Scale (CDS)
-11. Centre for Epidemiological Studies Depression Scale (CES-D)
-12. Child Assessment Schedule (CAS)
-13. Child Behaviour Checklist-Depression (CBCL-D)
-
-## Full description of methods (including formalisms)
-
-## Included studies
-
-We drew upon RCTs included in two recent comprehensive meta-analyses with open data available for each medication and psychotherapy, and supplemented them with an updated systematic review.
-Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
-Whilst Cuijpers et al.
-[@cuijpersEffectsPsychologicalTreatments2021] excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
-We also included studies which had data available for other variables in interest, including number of sites or baseline demographics; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpersEffectsPsychologicalTreatments2021] literature search.
-We also included three studies from Zhou et al.
-\[\@\] which were not covered in the previous meta-analysis whilst fitting the date range.
-
-Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
-A dataset was made available online though did not include means or standard deviations at baseline or post-test.
-We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
-We excluded three studies because they had no control arm.
-We were unable to locate and therefore complete extraction for two RCTs (Almeida-Montes, 2005; Eli Lilly, 1986).
-Many studies did not report complete data; we contacted all corresponding authors to request missing data, though did not receive any responses.
-
-We conducted a systematic search for medication studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
-Please see the Supplemental Materials for further details.
-Our search produced 538 studies, 88 of which were duplicates and subsequently removed.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and data extraction was completed for these papers.
-
-## Statistical Analysis
-
-### Sample characteristics
-
-We conducted a series of random-effects meta-analyses and tested for subgroup differences between psychotherapy and medication trials in sample characteristics including sex, age, and severity of depressive symptoms at baseline.
-Meta-analyses were implemented using R's Meta package (version 7.0-0).
-
-In order to compare depression severity across the variety of instruments the studies used, we performed a min-max normalisation to turn each study arm mean score at baseline into a percentage using the following formalism:
-
-$$
-\text{outcome}_{percent} = \frac{\bar{X} - \text{scale}_{min}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where, $$\bar{X}$$is the mean score for each study arm on the primary outcome questionnaire, and ${scale}_{min}$ and ${scale}_{max}$ are the minimum and maximum possible values of the scale in question, respectively.
-The standard deviation is calculated thus:
-
-$$
-\text{SD}_{Xpercent} = \frac{\text{SD}_{X}}{\text{scale}_{max} - \text{scale}_{min}}
-$$
-
-where $\text{SD}_{X}$ is the original standard deviation of the mean at baseline.
-
-### Trial design
-
-#### Measures of effect
-
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD), which we defined following [@lakensCalculatingReportingEffect2013, @cummingUnderstandingNewStatistics2013] as:
-
-$$SMD_{change} = \frac{Mean_{t_{2}} - Mean_{t_{1}}}{\frac{SD_{t{2}} + SD_{t{1}}}2}\ $$
-
-where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
-If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
-For conditions where the SD was missing at one time point, the baseline SD was substituted by the post-test SD, and vice versa.
-If the SD was not available at either time point, missing values were replaced by the mean of the SDs available for comparable cases (defined as same trial type (psy or med), same instrument, same timepoint (pre or post), and same arm (control or active)).
-Where there were missing means at either baseline or post-test, missing values were calculated using mean change scores, preferring the change scores reported in the paper itself, though where this was unavailable, using the change scores reported in the dataset from Cipriani et al.'s meta-analysis (for medication studies only).
-
-For the purposes of meta-analysis, it is necessary to estimate a standard error of the SMD. This is calculated according to:
-
-$$ SE_{SMD} = \sqrt{\frac{2(1 -r_{t_{1}t_{2}})}{n} + \frac{SMD^2}{2n}}$$
-
-where $n$ refers to the study sample size and $r_{t_{1}t_{2}}$ refers to the correlation between the outcome score obtained at baseline and at the end point.
-This correlation is typically not reported in studies and is often imputed using previously reported correlations for the instruments used.
-However, this practice has given rise to concerns about misestimation.
-Whilst such misestimation is possible, there is no reason to expect that it would be systematic, i.e.
-bias estimation of the effects for the control group of medication compared to those of psychotherapy.
-Still, to alleviate such concerns we have used a simulations.
-
-In particular, we simulated one thousand truncated distribution of standard errors with the following general characteristics:
-
-$$r_{t_{1}t_{2}} \sim \mathcal{TN}(\mu, \sigma, a, b)$$
-
-for which we chose the mean to be $\mu = 0.65$, the standard deviation to be $\ sigma = 0.2$, and the upper and lower bounds to be $a = 0.45$ and $b = 0.9$, respectively.
-We then used these simulated datasets in the subsequent meta-analyses.
-
-#### Multilevel model metaregression
-
-We estimated pooled standardized mean differences for each arm by using multilevel models implemented in R's metafor package.
-Unlike the traditional random effects meta-analysis, which assumes that each study's true effect size $\theta_{k}$ varies due to heterogeneity between studies, our multilevel model accounts for the hierarchical structure of the data, with study arms nested within study IDs.
-This allows us to model variability at both the study level and the study arm level.
-
-The multilevel model assumes that each study's true effect size $\theta_{ij}$ (where $i$ indexes the study and $j$ indexes the study arm) is influenced by both the variability between studies and the variability between arms within each study.
-The model can be expressed as:
-
-$$Yij ∼ \mathcal{N}(\theta_{ij}, \sigma_{ij}^2)$$
-
-where,
-
-$$θij​∼N(xij​β,τi2​)$$ {#eq-8}
-
-where $Y_{ij}$ is the observed effect size for the $j$th arm in the $i$th study, which has a normal distribution with mean $\theta_{ij}$ and sampling error variance $\sigma_{ij}^2$.
-The true effect size $\theta_{ij}$ is modeled as a study-specific effect with an additional term representing the variability between arms within the study.
-
-This gives rise to the following model:
-
-$$ Yij=xijβ+ui+vij+ϵij $$ {#eq-9}
-
-where,
-
-$$ ui​∼N(0,τ2) $$ {#eq-10}
-
-describes the deviation of each study from the overall mean effect size, and
-
-$$vij∼N(0,τi2)$$ {#eq-11}
-
-describes the deviation of each arm from the study-specific effect, with $\tau_{i}^2$ representing the heterogeneity within studies. Finally,
-
-$$\epsilon_{ij} \sim \mathcal{N}(0, \sigma_{ij}^2)$$ {#eq-12}
-
-represents the sampling error.
-
-In this framework, we can model the means for each arm of the trials as follows:
-
-$$ \begin{aligned} Υ_{ij} &= \begin{cases} 0 & \text{MedControl:} \quad b_0 + u_i + v_{ij} + \epsilon_{ij}\\ 1 & \text{MedActive:} \quad b_0 + b_{1_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 2 & \text{PsyActive:} \quad b_0 + b_{2_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ 3 & \text{PsyControl:} \quad b_0 + b_{3_{ij}} + u_i + v_{ij} + \epsilon_{ij} \\ \end{cases} \end{aligned} $$ {#eq-13}
-
-Here, the mean effect size for each level is the sum of $b_0$, the intercept for the reference category (medication control), with the coefficient for each level (e.g., $b_{3_{ij}}$ for psychotherapy controls).
-The variability between studies and arms within studies is captured by $u_i$ and $v_{ij}$, respectively.
-The confidence intervals for the means are constructed using the standard errors of the means, which account for the hierarchical structure of the data.
-Each coefficient represents the contrast between the reference category and each level.
-For example, $b_{3_{ij}}$ represents the contrast between psychotherapy and medication control arms.
-Inference on these contrasts is conducted using the following test statistic:
-
-$$ z = \frac{\hat{\beta}}{\text{SE}(\hat{\beta})} $$ {#eq-14}
-
-This test allows us to assess the significance of the differences between treatment effects across study arms.
-
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
-
-We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
-The SMDs are the means across the 1000 simulated datasets.
-
-#### Number of sites
-
-We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
-
-### Sensitivity Analyses
-
-```{r setting-z-2, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
-# my alpha for the z 
-target_probability <- 1 - 0.05
-
-#start here 
-x <- 1
-
-# two decimals should be fine
-tolerance <- 1e-3
-
-#find the z value using the pnorm function
-while (abs(pnorm(x)) < target_probability ) {
-  x <- x + tolerance  
-}
-
-# Adjust the step size based on your problem  
-cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
-
-x
-
-```
-
-We conducted a series of sensitivity analyses.
-For each of the meta-analyses we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
-Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
-Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
-To inspect whether this is the case, we plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
-
-Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
-
-### Comparing the control and active arms of psychotherapy trials
-
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions.
-We extracted data pertaining to the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
-Where a range was provided, the maximum was encoded (e.g.
-if a paper reported that an intervention involved 8-10 sessions lasting 50-60 minutes, we encoded the number and duration of sessions as 10 and 60, respectively).
-If sessions varied in frequency across an intervention, we calculated an average by dividing total number of sessions by length of intervention period.
-Similarly, if the length of sessions varied across the course of the intervention, we calculated a weighted average.
-Phone call, web-chat and online sessions were encoded as sessions, however guided self-help components were not.
-
-## Summary of all included trials
-
-```{r echo=FALSE, message=FALSE, warning=FALSE}
-#| label: tbl-all-trials
-#| tbl-cap: "Summary of included RCTs"
-#| tbl-cap-location: top
-
-table_all_trials <- df_long_for_metan %>% 
-  select(psy_or_med, new_study_id, arm_effect_size, type, baseline_n, instrument_name, baseline_mean, baseline_sd, post_mean, post_sd, cohens_d)
-
-table_all_trials <- table_all_trials %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>% 
-  mutate(psy_or_med = ifelse(psy_or_med == 0, "Medication", "Psychotherapy")) %>% 
-  mutate(arm_effect_size = ifelse(arm_effect_size == "cohens_d_active", "Active", "Control"))
-
-new_column_names <- c("psy_or_med", "Study", "Arm", "Description", "N", "Instrument", "Baseline M", "Baseline SD", "Post M", "Post SD", "Cohen's d")
-
-# Assign new column names to the data frame
-colnames(table_all_trials) <- new_column_names
-
-table_all_trials %>% 
-  arrange(psy_or_med, Study) %>% 
-  group_by(psy_or_med) %>%
-  as_flextable(hide_grouplabel = TRUE) %>% 
-  merge_v(j = ~Study) %>% 
-  align(j = 4:10, align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  bg(i = c(1, 86), bg = "#F2F2F2", part = "body") %>% 
-  bold(i = c(1, 86), bold = TRUE, part = "body") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  set_table_properties(width = 1, layout = "autofit")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-hamd-baseline
-#| tbl-cap: "HAM-D scores at baseline across psychotherapy and medication RCTs"
-#| tbl-cap-location: top
-
-# now for the ham-d
-# For row names
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_hamd) <- new_column_names
-
-# Rounding
-results_met_sev_hamd <- results_met_sev_hamd %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-results_met_sev_hamd %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_hamd), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the HAMD baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_hamd_metareg_baseline <- results_hamd_metareg_baseline[[2]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_2_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_hamd_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_2_hamd_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-# 
-# # Regression results
-# 
-# table_1_hamd_metareg_baseline <- results_hamd_metareg_baseline[[1]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-# 
-# # Assign new column names to the data frame
-# colnames(table_1_hamd_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_hamd_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_1_hamd_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-cdrs-baseline
-#| tbl-cap: "CDRS scores at baseline across psychotherapy and medication RCTs"
-#| tbl-cap-location: top
-
-# For row names
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(subgroup = if_else(subgroup == 0, "Medication", "Psychotherapy"))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(results_met_sev_cdrs) <- new_column_names
-
-# Rounding
-results_met_sev_cdrs <- results_met_sev_cdrs %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.))) %>% 
-  slice(1, 3, 2)
-
-results_met_sev_cdrs %>% 
-  as_flextable() %>% 
-  align(j = 2:ncol(results_met_sev_cdrs), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-# # All of the below is for the CDRS baseline meta-analysis when we have 4 levels
-# # Prepare to tabulate
-# 
-# table_2_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[2]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "baseline_smds") %>%
-#   relocate("n", .before = "baseline_smds") %>%
-#   relocate("lower_cis_smds", .before = "upper_cis_smds")
-# 
-# new_column_names <- c("Condition", "N", "Baseline Scores", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_2_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_2_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_2_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-# 
-# # Regression results
-# 
-# table_1_cdrs_metareg_baseline <- results_cdrs_metareg_baseline[[1]] %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>%
-#   relocate("condition", .before = "term") %>%
-#   select(-c("term", "type"))
-# 
-# new_column_names <- c("Condition", "Estimate", "SE", "Statistic", "p value")
-# 
-# # Assign new column names to the data frame
-# colnames(table_1_cdrs_metareg_baseline) <- new_column_names
-# 
-# flextable(table_1_cdrs_metareg_baseline) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>%
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>%
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>%
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   align(j = 2:ncol(table_1_cdrs_metareg_baseline), align = "center", part = "all") %>%
-#   align(j = 1, align = "left", part = "all") %>%
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>%
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r sex-all-studies, warning=FALSE, message = FALSE, echo=FALSE}
-
-#Repeating meta-analyses on sample characteristics including studies with females only
-
-#An issue that arise when trying to include studies with 100% female is that their SE ends up being 0, which is treated as NA in the metagen function.
-One way to circumvent this is to apply a continuity correction by adding a constant (e.g 0.5) to percent female.
-These studies will now be treated as having 99.5% females.
-
-#overall sample------------
-
-df_for_sex_metan_no_excl <- df_baseline_demographics %>% 
-  filter(!is.na(percent_women)) %>% #use full dataset to include all studies
-  filter(new_study_id != "March, 2004")# removing TADS because it does not technically belong to either the psy or med groups
-
-#using the formula for se (p*(1-p)/n) we add a constant for studies w 100% female
-
-correction_constant <- 0.5
-
-df_for_sex_metan_no_excl <- df_for_sex_metan_no_excl %>% 
-  mutate(constant_percent_women = ifelse(percent_women==100,percent_women-correction_constant,percent_women)) %>%
-  mutate(product_perc_women=(constant_percent_women/100)*(1-(constant_percent_women/100))) %>%
-  mutate(percent_women_std_error = sqrt(product_perc_women / n_overall))
-
-met_perc_women_no_excl  <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies")
-
-    #Issue: standard error is 0 for 100% female studies so the model     treats them as NA! fix if we want to include all studies in these analyses
-
-met_perc_women_no_excl <- update(met_perc_women_no_excl,
-                              subgroup = df_for_sex_metan_no_excl$psy_or_med, subgroup.name = "treatment modality",
-                              tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-
-results_met_perc_women_no_excl <- extract_stats(met_perc_women_no_excl)
-
-# Clinical only-------------
-
-df_for_sex_metan_no_excl_clin <- df_for_sex_metan_no_excl %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_perc_women_no_excl_clin <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across clinical studies")
-
-met_perc_women_no_excl_clin <- update(met_perc_women_no_excl_clin,
-                           subgroup = df_for_sex_metan_no_excl_clin$psy_or_med, subgroup.name = "treatment modality",
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_excl_clin <- extract_stats(met_perc_women_no_excl_clin)
-
-# Excluding wl--------------
-
-df_for_sex_metan_no_excl_no_wl <- df_for_sex_metan_no_excl %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_perc_women_no_excl_no_wl <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_excl_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies with controls that are not wl",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_excl_no_wl <- extract_stats(met_perc_women_no_excl_no_wl)
-
-## Combine results for table
-
-df_baseline_results_no_excl <- rbind(results_met_perc_women_no_excl, results_met_perc_women_no_excl_clin, results_met_perc_women_no_excl_no_wl)
-
-# For row names
-df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
-  mutate(subgroup = case_when(
-    row_number() %in% 1 ~ "Overall",
-    row_number() %in% 4 ~ "Excluding subclinical",
-    row_number() %in% 7 ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_baseline_results_no_excl) <- new_column_names
-
-# Rounding
-df_baseline_results_no_excl <- df_baseline_results_no_excl %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
-big_border = fp_border(color="black", width = 1)
-small_border = fp_border(color="lightgray", width = 1)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-all-studies-percfemale-results
-#| tbl-cap: "Percentage female at baseline across medication and psychotherapy studies: Results for sample including all female studies"
-#| tbl-cap-location: top
-
-df_baseline_results_no_excl %>% 
-  as_flextable() %>% 
-  bold(i = c(1, 4, 7), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
-  bg(i = 1, bg  = "#F2F2F2", part = "body") %>% # identify category sections
-  padding(i = c(2, 3, 5, 6, 8, 9), j = 1, padding.left = 10) %>% # indent some rows
-  align(j = 2:ncol(df_baseline_results_no_excl), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  line_spacing(space = .7, part = "all") %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-```
-
-#### Multilevel metaregression results
-
-In @tbl-results-overall, we present the regression that tests our hypothesis about differences between medication and psychotherapy controls.
-Here, medication control is the reference category to which all others are compared.
-The strongest difference between arms, as judged by the z-value, is between the psychotherapy and medication controls with a z-value of `r round(aggregate_results_overall[aggregate_results_overall$condition == "psychotherapy_control", ]$z_value, 2)` (p\<0.0001).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE, ft.align="left"}
-#| label: tbl-results-overall
-#| tbl-cap: "Results from metaregression with overall sample"
-#| tbl-cap-location: top
-
-#add i2 to aggregate results
-aggregate_results_overall_i2 <- cbind(aggregate_results_overall, 
-                                   i2_2 = rep(i2_summary_all$mean_i2_level2, nrow(aggregate_results_overall)),
-                                   i2_3 = rep(i2_summary_all$mean_i2_level3, nrow(aggregate_results_overall)))
-
-# Regression results
-
-aggregate_results_overall_i2 <- aggregate_results_overall_i2 %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition))) %>% 
-  relocate("condition", .before = "coefficients")
-
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2_1", "T2_2", "QE", "k", "I2_2", "I2_3")
-
-# Assign new column names to the data frame
-colnames(aggregate_results_overall_i2) <- new_column_names
-
-table_aggregate_results_overall_i2 <- aggregate_results_overall_i2[, 1:6]
-table_aggregate_results_overall_i2[1, 4] <- NA
-
-flextable(table_aggregate_results_overall_i2) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "T2_2"],
-                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "I2_3"], 
-                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "I2_2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall_i2[1, "k"], "."), colwidths = 6) %>%
-  # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-  # add_header_row(values = "Table 4", colwidths = 6) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_aggregate_results_overall_i2), align = "center", part = "all") %>% 
-  align(j = 1, align = "left", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>% 
-  paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-mean_diff_min_max_scores <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) + 
-  geom_jitter(width = 0.2) + 
-  ggtitle("Post-Pre Differences in Mean Min-Max Scores") + 
-  ylab("Post-Pre Difference") +
-  xlab("Type of Study") +
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) +   theme_minimal()
-
-print(mean_diff_min_max_scores) 
-png("mean_diff_min_max_scores.png")
-mean_diff_min_max_scores
-dev.off()
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# create baseline variances
-df_long_for_metan$variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-plot_baseline_var <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) + geom_jitter(width = 0.2) +  
-  ggtitle("Post-Pre Differences in Study Baseline Variances") + 
-  ylab("Baseline Variance") + 
-  xlab("Type of Study") + 
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + theme_minimal()
-
-print(plot_baseline_var)
-png("plot_baseline_var.png")
-plot_baseline_var
-dev.off()
-```
-
-## Metaregression sensitivity analyses
-
-```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-no-wl
-#| fig-cap: "Meta-analytic estimates of within-group changes: waitlist studies excluded"
-#| fig-cap-location: top
-#| fig-title: Figure S
-
-coef_and_se_means_no_wl <- coef_and_se_means_no_wl %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_no_wl <- "Metanalytic estimates of within-group changes: wl excluded"
-plot_means_no_wl <- plot_means_function(coef_and_se_means_no_wl)
-print(plot_means_no_wl)
-
- png("plot_means_multi_no_wl.png")
-plot_means_no_wl
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-clin
-#| fig-cap: "Meta-analytic estimates of within-group changes: subclinical studies excluded"
-#| fig-cap-location: top
-
-coef_and_se_means_clin_study <- coef_and_se_means_clin_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_clin <- "Metanalytic estimates of within-group changes: subclinical studies excluded"
-plot_means_clin <- plot_means_function(coef_and_se_means_clin_study)
-print(plot_means_clin)
-
-png("plot_means_multi_clin.png")
-plot_means_clin
-dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-cdrs
-#| fig-cap: "Meta-analytic estimates of within-group changes: CDRS studies only"
-#| fig-cap-location: top
-
-coef_and_se_means_cdrs_study <- coef_and_se_means_cdrs_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_cdrs <- "Metanalytic estimates of within-group changes: CDRS studies only"
-plot_means_cdrs <- plot_means_function(coef_and_se_means_cdrs_study)
-print(plot_means_cdrs)
-
- png("plot_means_multi_cdrs.png")
- plot_means_cdrs
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-hamd
-#| fig-cap: "Meta-analytic estimates of within-group changes: HAM-D studies only"
-#| fig-cap-location: top
-
-coef_and_se_means_hamd_study <- coef_and_se_means_hamd_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_multi_hamd <- plot_means_function(coef_and_se_means_hamd_study)
-print(plot_means_multi_hamd)
-
- png("plot_means_multi_hamd.png")
- plot_means_multi_hamd
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-postsd
-#| fig-cap: "Meta-analytic estimates of within-group changes: studies with post SD"
-#| fig-cap-location: top
-
-coef_and_se_means_sd_study <- coef_and_se_means_sd_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: studies with post SD"
-plot_means_multi_sd <- plot_means_function(coef_and_se_means_sd_study)
-print(plot_means_multi_sd)
-
- png("plot_means_multi_sd.png")
- plot_means_multi_sd
- dev.off()
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-var2
-#| fig-cap: "Meta-analytic estimates of within-group changes: studies with variance <0.02"
-#| fig-cap-location: top
-
-coef_and_se_means_var2_study <- coef_and_se_means_var2_study %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_hamd <- "Metanalytic estimates of within-group changes: HAM-D studies only"
-plot_means_multi_var2 <- plot_means_function(coef_and_se_means_var2_study)
-print(plot_means_multi_var2)
-
- png("plot_means_multi_var2.png")
- plot_means_multi_var2
- dev.off()
-```
-
-#### Effect of standard errors of the SMDs
-
-It could be argued that the choice of standard errors of the changes for the calculation of the confidence intervals could have affect the results in one or the other direction.
-To address such concerns we have simulated 1000 different datasets with SMDs coming from a broad distribution.
-If standard error distributions were influential, this should show up as substantial variability across simulations.
-We test this idea in the @fig-stab-sims which displays across the 1000 simulations the z-value of the contrast between medication and psychotherapy control arms (the mean of which we presented in @tbl-results-overall).
-As can be seen, the variability in the z-score is minimal and consistently far away from the threshold for significance, i.e.
-the value of z = 1.645.
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-stab-sims
-#| fig-cap: "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms"
-#| fig-cap-location: top
-
-# examine the stability of the simulations
-
-z_psy_con_vs_med_con <- 0
-for(i in 1: length(list_model_1_meta_reg)){
-z_psy_con_vs_med_con[i] <- list_model_1_meta_reg[[i]]$zval[condition=="psychotherapy_control"]
-
-}
-
-stability_sims <- data.frame(n_sims = 1:1000, z_value = z_psy_con_vs_med_con)
-
-stab_sims <- stability_sims %>%
-  ggplot(aes(x = n_sims, y = z_value)) +
-  geom_point() +
-  geom_hline(yintercept = 1.65, linetype = "dotted", color = "red") +
-  geom_segment(aes(x = 300, xend = 300, y = 2, yend = 1.65),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 2.0, label = "p < 0.05 threshold (values above line significant)", hjust = -0.1, vjust = 0) +
-  geom_segment(aes(x = 300, xend = 300, y = 7.5, yend = min(stability_sims$z_value-0.3)),
-               arrow = arrow(length = unit(0.3, "cm")),
-               color = "black") +
-  annotate("text", x = 300, y = 7.5, label = "simulated z-values",
-           hjust = -0.1, vjust = 0) +
-  theme_minimal() +
-  labs(
-    x = "Number of Simulations",
-    y = "z-value",
-    title = "Stability of the Statistic of the Difference between Medication and Psychotherapy Control Arms",
-    subtitle = "Results from 1000 simulations with within-group standard errors"
-  )
-
-print(stab_sims)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-adj-smds
-# #| tbl-cap: "SMDs adjusted by baseline scores"
-# #| tbl-cap-location: top
-# 
-# table_mean_coefs_from_sim_adjusted_cohens_d <- df_mean_coefs_from_sim_adjusted_cohens_d %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) 
-# 
-# new_column_names <- c("Condition", "Coefficient", "SE", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_mean_coefs_from_sim_adjusted_cohens_d) <- new_column_names
-# 
-# flextable(table_mean_coefs_from_sim_adjusted_cohens_d) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_mean_coefs_from_sim_adjusted_cohens_d), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-# 
-# aggregate_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   mutate(condition = case_when(
-#     condition == "medication_control" ~ "Medication Control",
-#     condition == "medication_active" ~ "Medication Active",
-#     condition == "psychotherapy_control" ~ "Psychotherapy Control",
-#     condition == "psychotherapy_active" ~ "Psychotherapy Active",
-#     TRUE ~ as.character(condition))) %>% 
-#   relocate("condition", .before = "coefficients") 
-# 
-# new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "I2", "k", "R2")
-# 
-# # Assign new column names to the data frame
-# colnames(aggregate_results_overall_adjusted_cohens_d) <- new_column_names
-# 
-# table_results_overall_adjusted_cohens_d <- aggregate_results_overall_adjusted_cohens_d[, 1:6]
-# 
-# flextable(table_results_overall_adjusted_cohens_d) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "T2"],
-#                       "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "I2"], 
-#                       "; ", as_i("K"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "k"],
-#                       "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall_adjusted_cohens_d[1, "R2"], "."), colwidths = 6) %>%
-#   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
-#   # add_header_row(values = "Table 4", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-de-meaned
-#| tbl-cap: "Results from baseline-adjusted model"
-#| tbl-cap-location: top
-
-de_meaned_smd_with_cis <- de_meaned_smd_with_cis %>%
-  mutate(across(where(is.numeric), ~round(., 2))) %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-new_column_names <- c("Condition", "SMDs", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(de_meaned_smd_with_cis) <- new_column_names
-
-flextable(de_meaned_smd_with_cis) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  font(fontname = "Calibri", part = "all") %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(de_meaned_smd_with_cis), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-
-table_coefs_lm_for_baseline_means <- coefs_lm_for_baseline_means[c(1, 3:5),]
-
-table_coefs_lm_for_baseline_means <- table_coefs_lm_for_baseline_means %>%
-  mutate(across(where(is.numeric) & !matches("p.value"), ~ round(., 2))) %>%
-  mutate(`p.value` = ifelse(`p.value` < 0.001, "< 0.001", sprintf("%.3f", `p.value`)))
-
-new_column_names <- c("Condition", "Estimate", "SE", "t value", "p-value")
-
-# Assign new column names to the data frame
-colnames(table_coefs_lm_for_baseline_means) <- new_column_names
-
-table_coefs_lm_for_baseline_means$Condition <- c("Medication Control", "Medication Active", "Psychotherapy Control", "Psychotherapy Active")
-
-flextable(table_coefs_lm_for_baseline_means) %>%
-  set_table_properties(width = 1) %>%
-  autofit() %>%
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>%
-  # italic(i = 2, italic = TRUE, part = "header") %>%
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>%
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>%
-  # padding(i = 2, padding.bottom = 15, part = "header") %>%
-  align(j = 2:ncol(table_coefs_lm_for_baseline_means), align = "center", part = "all") %>%
-  align(j = 1, align = "left", part = "all") %>%
-  font(fontname = "Calibri", part = "all") %>%
-  paginate(init = TRUE, hdr_ftr = TRUE) %>%
-  line_spacing(space = .7, part = "all")
-```
-
-```{r , warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-
-# We want to compare active v control arms when we filter out wl conditions
-
-df_descr_psy_conditions_no_wl <- df_descr_psy_conditions %>% 
-  filter(new_study_id %in% no_wl_ids)
-
-df_descr_psy_conditions_no_wl <- df_descr_psy_conditions_no_wl %>% 
-    filter(!(treatment == "wlc"))
-
-sessions <- group_function(df_descr_psy_conditions_no_wl,"levels_var","no_sessions")
-frequency <- group_function(df_descr_psy_conditions_no_wl,"levels_var","freq_weeks")
-length_sessions_mins <- group_function(df_descr_psy_conditions_no_wl,"levels_var","length_sessions_mins")
-total_hours <- group_function(df_descr_psy_conditions_no_wl,"levels_var","total_hours")
-
-control_summary_no_wl <- rbind(sessions, frequency, length_sessions_mins, total_hours)
-
-control_summary_no_wl <- control_summary_no_wl %>% 
-  select(-c(Median, IQR))
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(Group = case_when(
-    Group == "psychotherapy_active" ~ "Active",
-    Group == "psychotherapy_control" ~ "Control",
-    TRUE ~ as.character(Group)  # Keep other values unchanged
-  ))
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(Column = case_when(
-    Column == "no_sessions" ~ "Number of sessions",
-    Column == "freq_weeks" ~ "Intensity (sessions per week)",
-    Column == "length_sessions_mins" ~ "Session length (mins)",
-    Column == "total_hours" ~ "Total intervention hours",
-    TRUE ~ as.character(Column)  # Keep original value if no match
-  ))
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions_no_wl)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions_no_wl)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions_no_wl)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions_no_wl)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-
-control_summary_t_tests_no_wl <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
-
-# For row names
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests_no_wl) <- new_column_names
-
-#Rounding
-control_summary_t_tests_no_wl <- control_summary_t_tests_no_wl %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
-
-# calculating with my function
-
-# session_es_no_wl <- effect_btwn(sessions)
-# frequency_es_no_wl <- effect_btwn(frequency)
-# length_sessions_mins_es_no_wl <- effect_btwn(length_sessions_mins)
-# total_hours_es_no_wl <- effect_btwn(total_hours)
-# total_period_weeks_es_no_wl <- effect_btwn(total_period_weeks)
-
-# using a package to calculate instead
-
-session_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$no_sessions ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-frequency_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$freq_weeks ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-length_sessions_mins_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$length_sessions_mins ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-total_hours_es_no_wl <- cohen.d(df_descr_psy_conditions_no_wl$total_hours ~ df_descr_psy_conditions_no_wl$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-
-# going to try displaying summary statistics and t-tests in one place
-
-control_summary_no_wl <- cbind(control_summary_no_wl, 
-                          "Cohen's d" = rep(NA, nrow(control_summary_no_wl)),
-                         "Upper CI" = rep(NA, nrow(control_summary_no_wl)),
-                         "Lower CI" = rep(NA, nrow(control_summary_no_wl)),
-                         t = rep(NA, nrow(control_summary_no_wl)), 
-                          df = rep(NA, nrow(control_summary_no_wl)), 
-                          "p-value" = rep(NA, nrow(control_summary_no_wl)))
-
-# Update the first row with session_es_no_wl
-control_summary_no_wl[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  session_es_no_wl$estimate, session_es_no_wl$conf.int[1], session_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[1], control_summary_t_tests_no_wl$df[1], 
-  control_summary_t_tests_no_wl$`p-value`[1]
-)
-
-# Update the third row with frequency_es_no_wl
-control_summary_no_wl[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  frequency_es_no_wl$estimate, frequency_es_no_wl$conf.int[1], frequency_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[2], control_summary_t_tests_no_wl$df[2], 
-  control_summary_t_tests_no_wl$`p-value`[2]
-)
-
-# Update the fifth row with length_sessions_mins_es_no_wl
-control_summary_no_wl[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  length_sessions_mins_es_no_wl$estimate, length_sessions_mins_es_no_wl$conf.int[1], length_sessions_mins_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[3], control_summary_t_tests_no_wl$df[3], 
-  control_summary_t_tests_no_wl$`p-value`[3]
-)
-
-# Update the seventh row with total_hours_es_no_wl
-control_summary_no_wl[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  total_hours_es_no_wl$estimate, total_hours_es_no_wl$conf.int[1], total_hours_es_no_wl$conf.int[2], 
-  control_summary_t_tests_no_wl$`t statistic`[4], control_summary_t_tests_no_wl$df[4], 
-  control_summary_t_tests_no_wl$`p-value`[4]
-)
-
-control_summary_no_wl <- control_summary_no_wl %>%
-  mutate(
-    `Cohen's d` = as.numeric(`Cohen's d`),
-    `Upper CI` = as.numeric(`Upper CI`),
-    `Lower CI` = as.numeric(`Lower CI`)
-  ) %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-intensity-of-int-no-wl
-#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
-#| tbl-cap-location: top
-
-as_grouped_data(control_summary_no_wl, groups = "Column") %>% 
-  as_flextable(hide_grouplabel = TRUE ) %>% 
-  bold(i = c(1, 4, 7, 10), bold = TRUE, part = "body") %>%  
-  set_table_properties(width = 1) %>%  # Set table width 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:9, align = "center", part = "all") %>% 
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
-  # add_header_row(values = "Table 5", colwidths = 4) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(j = 1:4, part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = c(1,4), part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-t-tests-intensity-no-wl
-# #| tbl-cap: "Results for t-tests comparing the intensity of the intervention between active and control arms of psychotherapy studies: waitlist studies excluded"
-# #| tbl-cap-location: top
-# 
-# flextable(control_summary_t_tests_no_wl) %>%
-#   set_table_properties(width = 1) %>%  # Set table width %>% 
-#   autofit() %>%  # Autofit column widths 
-#   align(j = 2:ncol(control_summary_t_tests_no_wl), align = "center", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   #italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   paginate(init = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# Plots  -----------------------
-
-#define groups
-# df_long_for_metan <- df_long_for_metan %>%
-#   mutate(
-#     group = case_when(
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "Medication Active",
-#       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "Medication Control",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "Psychotherapy Active",
-#       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "Psychotherapy Control",
-#       TRUE ~ NA_character_
-#     )
-#   )
-# 
-# group_colors <- c("Medication Active" = "deeppink1", "Medication Control" = "deeppink4", "Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-
-# # Scatter plot cohens d per arm
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, color = group)) +
-#   geom_point(position = position_jitter(width = 0.2), size = 3) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3.5, yend = -3,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -4, yend = -4.5,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -4.5, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_color_manual(values = group_colors) +
-#   labs(title = "Scatter plot of Cohen's d by group", x = NULL, y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
-# Box plot Cohens d by group
-# 
-# ggplot(df_long_for_metan, aes(x = group, y = cohens_d, fill = group)) +
-#   geom_boxplot(outlier.shape = NA, position = position_dodge(0.8), color = "black", alpha = 0.5) +
-#   scale_y_continuous(limits = c(-3.5, 1), breaks = seq(-4, 1, by = 1)) +
-#   geom_hline(yintercept = 0, linetype = "dashed", color = "grey", size = 1) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -2.5, yend = -2,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -2.2, label = "Less Effective", color = "grey", vjust = 0, hjust = .2) +
-#   geom_segment(x = 4.5, xend = 4.5, y = -3, yend = -3.5,
-#                arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey") +
-#   geom_text(x = "Psychotherapy Control", y = -3.2, label = "More Effective", color = "grey", vjust = 0, hjust = .2) +
-#   scale_fill_manual(values = group_colors) +
-#   labs(title = "Box plot of cohens_d by group", x = "Group", y = "Cohen's d") +
-#   theme_minimal() +
-#   theme(legend.position = "none")
-
-```
-
-# References
+## References

### 2024-10-04 multilevel_metaregression/manuscript_render_test_supp.qmd
saving test files

--- 2024-09-22 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
@@
 title: "Comparing Apples and Oranges in Youth Depression Treatments?"
-subtitle: "A Quantitative Critique of the Evidence Base and Guidelines"
-author:
-  - name: Argyris Stringaris
-    email: a.stringaris@ucl.ac.uk
-    affiliations: 
-        - id: ucl_1
-          name: University College London
-          department: Divisions of Psychiatry and Psychology and Language Science
-          address: 1-19 Torrington Place
-          city: London, UK
-          state: 
-          postal-code: WC1E 7HB
-          country: United Kingdom
-    attributes:
-        corresponding: true
-    note: 
-  - name: Charlotte Burman
-    email: charlotte.burman@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-  - name: Raphaelle Delpech
-    email: raphaelle.delpech.18@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Rudolf Uher
-    email: uher@Dal.Ca
-    affiliations:
-        - id: dal
-          name: Dalhousie University
-          department: Department of Psychiatry
-          address: 
-          city: Nova Scotia
-          state: 
-          postal-code: 
-          country: Canada
-  - name: Dayna Bhudia
-    email: dayna.bhudia@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-  - name: Despoina Miliou
-    email: dgmiliou@outlook.com.gr
-    affiliations:
-        - ref: ucl_1
-  - name: Ioannis-Marios Rokas
-    email: rokasgiannis93@gmail.com
-    affiliations:
-        - ref: ucl_1
-  - name: Marinos Kyriakopoulos
-  - name: Lucy Foulkes
-    email: lucy.foulkes@psych.ox.ac.uk
-    affiliations:
-        - id: OU
-          name: University of Oxford
-          department: Experimental Psychology
-          address: Anna Watts Building, Radcliffe Observatory Quarter, Woodstock Road
-          city: Oxford
-          postal-code: OX2 6GG
-          country: United Kingdom
-    note:
-  - name: Carmen Moreno
-    email: cmoreno@hggm.es
-    affiliations:
-        - id: HGM
-          name: Hospital Gregorio Marañón
-          department: Department of Psychiatry
-          address: 46 C. del Dr. Esquerdo
-          city: Madrid
-          state:
-          postal-code: 28007
-          country: Spain
-  - name: Samuele Cortese
-    email: samuele.cortese@soton.ac.uk
-    affiliations:
-        - id: soton
-          name: University of Southampton
-          department: Centre for Innovation in Mental Health (CIMH), School of Psychology
-          address: Highfield Campus, Building 44
-          city: Southampton
-          state:
-          postal-code: SO17 1BJ
-          country: United Kingdom
-  - name: Glyn Lewis
-    email: glyn.lewis@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1        
-  - name: Georgina Krebs
-    email: g.krebs@ucl.ac.uk
-    affiliations:
-        - ref: ucl_1
-    note:
-keywords: 
-  - depression
-  - adolescents
-  - antidepressants
-  - psychotherapy
-date: last-modified
+subtitle: "Supplemental Materials"
+author: "Argyris Stringaris"
+date: "05-09-2024"
 format:
@@
 font:
-  family: Calibri
+  family: "Calibri"
 fig-cap-location: top
@@
 
-```{r library, warning=FALSE, message = FALSE, echo=FALSE, results='hide'}
+```{r library, warning=FALSE, message = FALSE, echo=FALSE}
 
@@
 
+#Upload environment after main manuscript analyses
+load("env_main_manuscript")
+
 # For referencing
@@
 
-```
-
-```{r global_options, include=FALSE}
-
-knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
-```
-
-# Abstract
-
-**Objectives:** Should a young person receive psychotherapy or medication for their depression, and on what evidence do we base this decision?
-In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
-**Methods:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-Using meta-analyses, we compared a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
-Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
-**Results:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
-There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.70)) vs psychotherapy controls (SMD=-0.5 (95% CI: -0.75 to -0.25)).
-Within psychotherapy RCTs, control conditions were less intensive on average than active conditions.
-**Conclusions:** Medication and psychotherapy RCTs differ on fundamental participant and methodological characteristics, thereby violating key conditions for valid comparison between them.
-Psychotherapy controls often involve little therapist contact and are easy-to-beat comparators.
-These findings cast doubt on the confidence with which psychotherapy is recommended for youth depression, and highlight the pressing need to improve the evidence base.
-
-# Key messages
-
-Psychotherapy is recommended before medication for most cases of depression in children and adolescents, a recommendation that is based on indirect comparisons of outcomes from randomised controlled trials (RCTs) within each treatment modality.
-We examine the validity of these inferences by scrutinising the comparability of psychotherapy and medication RCTs.
-We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the within-group effect sizes of medication controls (i.e.
-pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
-We also examine the quality of controls used in psychotherapy RCTs and find that they are poorly matched to active intervention arms in ways such as human contact hours, and hence represent poor and easy to beat comparators.
-Our findings underscore the need for a higher quality evidence base upon which to base treatment guidelines and clinical decision making.
-
-# Background
-
-Should a child or an adolescent receive psychotherapy or medication for their depression, and what information should be used to guide decision-making?
-
-For adolescent depression, there are limited head-to-head trials of medication and psychotherapy, and hence recommendations are derived from indirect comparisons of treatment efficacy.
-The National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend psychotherapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
-This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
-However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
-treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
-pill placebo) or psychotherapy controls.
-The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
-Also, the addition of psychotherapy to standard care did not improve outcomes [@goodyer_randomised_2008].
-Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
-
-In this paper, we examine whether the existing evidence for adolescent depression treatments can offer valid answers to this question.
-We provide a conceptual framework and test a series of hypotheses using data from existing trials.
-Two points are crucial to indirect comparisons of treatment modalities.
-First, whether the participants in trials are comparable across modalities.
-Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
-
-Starting with the first point, comparison between different trials assumes that they sample from the same population.
-If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
-
-The assumption that medication and psychotherapy trials sample from the same population may not be valid as patients and parents often have treatment preferences [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
-Moreover, treatment preferences correlate with clinically-relevant participant characteristics, including severity and sex.
-Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and if they differ across psychotherapy and medication trials they may confound comparisons.
-
-Regarding the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the "cutting edge" treatment, whilst those in the control are dissatisfied for having missed out (i.e.
-"disappointment bias" [@reltonEthicsTrialsCohorts2017].
-By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022], suggesting that expectancy effects are well-matched across conditions.
-Since expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011], if expectancy differs between medication and psychotherapy trials, comparisons between them, including in NMA, become questionable.
-
-Another difference in design is the number of trial sites.
-The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011; @meisterPlaceboResponseRates2020].
-This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
-
-An inter-related issue concerns the effect of control conditions.
-Often psychotherapy and medication are compared on the basis of their respective effect sizes (i.e.
-differences between the active and control conditions for each modality).
-For these to be comparable, medication and psychotherapy controls ought to be equal in their effects.
-Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% versus 60% and another from a difference of 40% versus 0% (i.e.
-from different points of reference).
-
-Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention [@guoChapterCounterfactualFramework2014]: what would have been the outcome had an individual not received the intervention, with all else being equal.
-Pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
-In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g.
-in number of hours of therapist contact).
-
-# Objective
-
-In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-We hypothesise that there are substantial differences between psychotherapy and medication RCTs, making their comparison problematic, which we examine in the following ways.
-First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline depression severity; b) percentage females; and c) mean age.
-Second, we examine trial characteristics including the efficacy of the control arms, using random-effects meta-regression, and the number of trial sites.
-Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
-
-# Study selection and analysis
-
-The study protocol was registered on the Open Science Framework (OSF) and can be found at <https://osf.io/bfmc6>.
-
-A detailed description of our methods, including formalisms on which analyses are based, can be found in the Supplement.
-
-## Included studies
-
-We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
-For the psychotherapy trials, we utilised open data from the previous meta-analysis (see <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
-For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
-
-For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
-Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and one author completed data extraction for these papers (see @fig-prisma for PRISMA diagram).
-
-## Statistical analysis
-
-### Sample characteristics
-
-We conducted random-effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms, sex and age.
-Meta-analyses were implemented using R's meta package.
-
-### Trial design
-
-#### Measures of effect
-
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression scale used (selected according to the hierarchy defined in the Supplement).
-
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023].
-
-For meta-analysis it is necessary to estimate a standard error of the SMD.
-This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation [@cuijpers_pre-post_2017], we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
-
-#### Multilevel model metaregression
-
-We estimated pooled SMDs for each arm by using multilevel models implemented in R's metafor package.
-
-We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
-The SMDs are the means across the 1000 simulated datasets.
-
-#### Number of sites
-
-We also conducted a t-test to compare mean number of trial sites between psychotherapy and medication trials.
-
-### Sensitivity analyses
-
-```{r set-up-z, warning=FALSE, message = FALSE, echo = FALSE, output = FALSE }
-# my alpha for the z 
-target_probability <- 1 - 0.05
-
-#start here 
-x <- 1
-
-# two decimals should be fine
-tolerance <- 1e-3
-
-#find the z value using the pnorm function
-while (abs(pnorm(x)) < target_probability ) {
-  x <- x + tolerance  
-}
-
-# Adjust the step size based on your problem  
-cat("critical value of z =", x, "corresponding to an alpha = 0.05." , "\n")
-
-x
-
-```
-
-We conducted a series of sensitivity analyses where we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
-Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
-Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
-
-Further, we tested whether the simulated values for the standard error had a substantial influence on the estimation of the differences between the medication and psychotherapy control conditions.
-We plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
-
-Finally, we examined whether differential regression to the mean may account for differences in effect for psychotherapy and medication trials.
-
-### Comparing the control and active arms of psychotherapy trials
-
-We ran t-tests to compare the active and control arms of psychotherapy trials on key variables of interest regarding the intensity of the interventions: the number, duration and intensity of sessions, and the total cumulative hours and duration of the intervention.
-
-```{r define-functions, warning=FALSE, message = FALSE, echo=FALSE}
-#############Some custom made functions#############
-
-###### 1. Simulation Function for SEs
-simulate_dataframes_for_st_errors <- function(df, num_repetitions, seed, n, a, b, mean, sd) { # n refers to the number
-                                                                                              # of unique ids to which a correlation coef
-                                                                                              # is allocated.
-  set.seed(seed)
-
-  # Empty list to store simulated dfs
-  list_df_simulated <- list()
-
-  for (i in 1:num_repetitions) {
-    # Simulate the vector
-    simulated_correlations_vector <- truncnorm::rtruncnorm(n, a, b, mean, sd)  #using the truncnorm to create correlations
-
-    # Create a copy of the original dataframe
-    df_simulated_copy <- df
-
-    # Add/update the sims column
-    df_simulated_copy$correlation_sim_values <- simulated_correlations_vector[match(df_simulated_copy$new_study_id, unique(df_simulated_copy$new_study_id))]
-
-    # Remove duplicated columns
-    df_simulated_copy <- df_simulated_copy[, !duplicated(colnames(df_simulated_copy))]
-
-    # Calculate the ses
-    df_simulated_copy <- df_simulated_copy %>% 
-      group_by(new_study_id, baseline_n) %>% 
-      mutate(simulated_se = sqrt(((2*(1-correlation_sim_values))/baseline_n) + 
-                                   (cohens_d^2/(2*baseline_n))))
-
-    # Add the simulated dataframe to the list
-    list_df_simulated[[i]] <- df_simulated_copy
-  }
-
-  return(list_df_simulated)
-}
-
-###############2. Simulation function for multilevel metaregression
-
-  run_multi_metaregression <- function(list_of_datasets, model_formula) {
-    list_model_meta_reg <- list()
-
-    for (i in seq_along(list_of_datasets)) {
-      # Check if required columns are present
-      if(!all(c("cohens_d", "simulated_se", "new_study_id", "arm_id") %in% names(list_of_datasets[[i]]))) {
-        stop("Dataset is missing one or more required columns: 'cohens_d', 'simulated_se', 'new_study_id', 'arm_id'")
-      }
-
-      # Fit the meta-regression model
-      list_model_meta_reg[[i]] <- metafor::rma.mv(yi = cohens_d,
-                                                  V = simulated_se^2,
-                                                  random = ~ 1 | new_study_id/arm_id,
-                                                  # this is where 
-                                                  # we specify the random
-                                                  # effect structure
-                                                  data = list_of_datasets[[i]],
-                                                  method = "ML",
-                                                  mods = model_formula,
-                                                  # here we specify the 
-                                                  # fixed effects as before
-                                                  test = "knha")
-    }
-
-    return(list_model_meta_reg)
-  }
-
-#########3. Function to count studies with missingness etc.
-
-count_studies <- function(df) {
-  df_count_studies <- df %>%
-    group_by(psy_or_med, arm_effect_size) %>%
-    count(is.na(cohens_d)) %>%
-    rename(is_missing = `is.na(cohens_d)`) %>%
-    mutate(
-      condition = case_when(
-        psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-        psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-        psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-        psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control"
-      )
-    )
-
-  df_count_studies$condition <- factor(df_count_studies$condition)  # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-  df_count_studies$condition <- relevel(df_count_studies$condition, ref = "medication_control")
-
-  return(df_count_studies)
-}
-
-##########4. Function to extract mean coefficients and to extract model characteristics
-
-aggregate_model_results <- function(list_model_1_meta_reg, condition) {
-  n_models <- length(list_model_1_meta_reg)
-  n_conditions <- length(condition)
-
-  df_coefs <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_se <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_z_value <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_lower_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
-  tau_sq_1 <- rep(NA, n_models)
-  tau_sq_2 <- rep(NA, n_models)
-  qe <- rep(NA, n_models)
-  k <- rep(NA, n_models)
-
-  for (i in seq_len(n_models)) {
-    model <- list_model_1_meta_reg[[i]]
-    tau_sq_1[i] <- model$sigma2[1]
-    tau_sq_2[i] <- model$sigma2[2]
-    qe[i] <- model$QE
-    k[i] <- model$k
-    coefs <- model$beta
-    ses <- model$se
-    zvals <- model$zval
-    lower_ci <- model$ci.lb
-    upper_ci <- model$ci.ub
-
-    for (j in seq_len(n_conditions)) {
-      if (!is.null(coefs[j])) {
-        df_coefs[i, j] <- coefs[j]
-        df_se[i, j] <- ses[j]
-        df_z_value[i, j] <- zvals[j]
-        df_lower_ci[i, j] <- lower_ci[j]
-        df_upper_ci[i, j] <- upper_ci[j]
-      }
-    }
-  }
-
-  df_coefficients_model <- data.frame(
-    coefficients = colMeans(df_coefs, na.rm = TRUE),
-    se = colMeans(df_se, na.rm = TRUE),
-    z_value = colMeans(df_z_value, na.rm = TRUE),
-    lower_ci = colMeans(df_lower_ci, na.rm = TRUE),
-    upper_ci = colMeans(df_upper_ci, na.rm = TRUE),
-    tau_sq_1 = mean(tau_sq_1, na.rm.= TRUE),
-    tau_sq_2 = mean(tau_sq_2, na.rm.= TRUE),
-    qe = mean(qe, na.rm = TRUE),
-    k = mean(k, na.rm = TRUE)
-  )
-
-  return(df_coefficients_model)
-}
-
-###########4. Function to extract the SMDs  (SMD, ses, CI) for each level of the dummy variable. The output is used below in 5.
-# it is a slightly awkward one, because I couldn't' come up with a better way to add the intercept to each coefficient
-# given the named output of the built in coef function. here I extract the coefficients
-
-extract_coefficients_func <- function(df_with_coefs){
-  list_coefs <- list()
-  coefs <- 0
-  coefficient_output <- 0
-
-  for(i in 1: length(coefficients(df_with_coefs))){
-
-    temp_vec <- c(0, rep(coefficients(df_with_coefs)[[1]], 
-                         length(coefficients(df_with_coefs)) - 1 ))
-    coefs[i] <- coef(df_with_coefs)[[i]]
-
-    coefficient_output <- temp_vec + coefs
-
-    st_error_output <- df_with_coefs$se
-
-    df_coefficients <- data.frame(cbind(coefficients = coefficient_output, se = st_error_output ))
-
-    df_coefficients$lower_bound <- df_coefficients$coefficients - 1.96*df_coefficients$se
-    df_coefficients$upper_bound <- df_coefficients$coefficients + 1.96*df_coefficients$se
-  }
-  return (df_coefficients )
-}
-
-############5. Function to get the means out of the SMDs (this is similar to Func 3 and I should at some point create one more general one)
-# here the argument list_of_dfs is the list of extracted coefficients that you get out of the extract_coefficients_func
-# which itself you get from the run_metaregression function. The argument conditions refers to the levels of the variable that describes each study arm
-
-calculate_mean_coefs_ses <- function(list_of_dfs, conditions) {
-  df_coefs <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
-  df_se <- matrix(NA, nrow = length(list_of_dfs), ncol = length(conditions))
-
-  for (i in 1:length(list_of_dfs)) {
-    for (j in 1:length(conditions)) {
-      df_coefs[i, j] <- list_of_dfs[[i]]$coefficients[j]
-      df_se[i, j] <- list_of_dfs[[i]]$se[j]
-    }
-  }
-
-  df_mean_coefs_ses <- data.frame(
-    coef_means = colMeans(df_coefs),
-    se_means = colMeans(df_se)
-  )
-
-  df_mean_coefs_ses$lower_ci <- df_mean_coefs_ses$coef_means - 1.96 * df_mean_coefs_ses$se_means
-  df_mean_coefs_ses$upper_ci <- df_mean_coefs_ses$coef_means + 1.96 * df_mean_coefs_ses$se_means
-
-  return(df_mean_coefs_ses)
-}
-
-###############6. Function for plotting the SMDs
-plot_means_function <- function(dataframe) {
-  dataframe$text_label <- 0
-
-  for (i in 1:nrow(dataframe)) {
-    dataframe$text_label[i] <- paste(
-      dataframe$condition[i], "\n",
-      round(dataframe$coef_means[i], 2),
-      "[" ,
-      round(dataframe$lower_ci[i], 2), 
-      round(dataframe$upper_ci[i], 2),
-      "]"
-    ) 
-  }
-
-  # Recode condition for ease of plotting
-  dataframe$condition <- str_replace_all(dataframe$condition, "_", " ")
-
-  # Encode colours
-  redish_palette <- c("Medication Control" = "deeppink4", "Medication Active" = "deeppink")
-  blueish_palette <- c("Psychotherapy Active" = "steelblue1", "Psychotherapy Control" = "steelblue3")
-
-  # Plotting
-  plot_means <- ggplot(dataframe, aes(x = coef_means, y = 1:nrow(dataframe),
-                                      colour = condition, label = text_label)) +
-    geom_point(label=dataframe$k) +
-    geom_errorbar(aes(xmin = lower_ci, xmax = upper_ci), width = 0.2, position = position_dodge(0.5)) +
-    geom_text(vjust = +1.5, size = 4.5) +
-    scale_size_continuous(guide = "none") +
-    guides(colour = FALSE) + 
-    scale_color_manual(values = c(redish_palette, blueish_palette)) +
-    theme_minimal() +
-    xlab("Standardized Mean Difference (SMD) with 95% CIs") +
-    ylab("") +
-    ylim(0, nrow(dataframe) + 1) +
-    xlim(-3.0, 0.5) +
-    geom_vline(xintercept = 0, linetype = "dashed", size = 1.5, colour = "grey50") +
-    geom_segment(x = -1.25, xend = -1.75, y = 4.7, yend = 4.7, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
-    geom_text(x = -1.55, y = 4.9, label = "More Effective", color = "grey50", vjust = 0.5, hjust = 1, size = 4.5) +
-    geom_segment(x = -1.35, xend = -0.85, y = 4.9, yend = 4.9, arrow = arrow(length = unit(0.25, "cm"), type = "closed"), color = "grey50") +
-    geom_text(x = -1.05, y = 5.05, label = "Less Effective", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)+
-    theme(axis.title.x = element_text(size = 12, family  = "Calibri"), 
-          axis.text.x  = element_text(size = 12, family = "Calibri"),
-          axis.text.y = (element_blank()),
-          plot.title = element_text(size = 12, family =  "Calibri", face= "italic"),
-          plot.subtitle = element_text(size = 12, family =  "Calibri", face= "italic")) +
-    geom_curve(aes(x = 0.18, y = 4.73, xend = 0.02, yend = 4.5), color = "grey50", curvature = -0.2, arrow = arrow(length = unit(0.25, "cm"), type = "closed")) +
-    geom_text(x = 0.2, y = 4.75, label = "No Effect", color = "grey50", vjust = 0.5, hjust = 0, size = 4.5)
-
-  return(plot_means)
-}
-
-###########7. Function for baseline SMD results
-library(broom)
-run_metareg_and_extract <- function(dataframe, model_1, condition) {
-  # Run metareg
-  inst_baseline_metareg <- rma(yi = baseline_mean,
-                               sei = baseline_stand_error,
-                               data = dataframe,
-                               method = "ML",
-                               mods = model_1,
-                               test = "knha")
-
-  # Extract coefficients from the list
-  baseline_metareg_results <- tidy(inst_baseline_metareg)
-  baseline_metareg_results$condition <- condition
-  coefs_for_inst_baseline <- tidy(inst_baseline_metareg)$estimate
-
-  # Calculate SMDs
-  smds_for_inst_baseline <- c(coefs_for_inst_baseline[1], coefs_for_inst_baseline[-1] + coefs_for_inst_baseline[1])
-
-  # Calculate upper and lower CIs
-  upper_cis_for_inst_baseline <- smds_for_inst_baseline + 1.96 * tidy(inst_baseline_metareg)$std.error
-  lower_cis_for_inst_baseline <- smds_for_inst_baseline - 1.96 * tidy(inst_baseline_metareg)$std.error
-
-  # Create dataframe with results
-  df_baseline_means_with_cis <- data.frame(
-    baseline_smds = smds_for_inst_baseline,
-    upper_cis_smds = upper_cis_for_inst_baseline,
-    lower_cis_smds = lower_cis_for_inst_baseline,
-    condition = condition
-  )
-
-  # Return the two dataframes
-  return(list(baseline_metareg_results = baseline_metareg_results, df_baseline_means_with_cis = df_baseline_means_with_cis))
-}
-
-###########8. Function for extracting multilevel I2 estimates
-
-extract_i2_values <- function(list_of_models) {
-  # Initialize vectors to store I2 values
-  i2_level2 <- numeric(length(list_of_models))
-  i2_level3 <- numeric(length(list_of_models))
-
-  # Loop through each fitted model from the list
-  for (i in seq_along(list_of_models)) {
-    model <- list_of_models[[i]]
-
-    # Calculate variance distribution using the existing function
-    i2_results <- var.comp(model)
-
-    # Extract I2 values for level 2 and level 3 from the results
-    i2_level2[i] <- as.numeric(i2_results$results$I2[2]) # I2 for level 2
-    i2_level3[i] <- as.numeric(i2_results$results$I2[3]) # I2 for level 3
-  }
-
-  # Combine I2 values into a data frame
-  i2_data <- data.frame(
-    i2_level2 = i2_level2,
-    i2_level3 = i2_level3
-  )
-
-  return(i2_data)
-}
-
-```
-
-```{r import-dataset, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Transforming data ------------------------------------------------------
-# import master dataset
-
-df_appl_v_orange <-readxl::read_excel(here("df_appl_v_orange.xlsx"))
-
-# Here we add in instrument end point values (mins / maxs).
-# We will use these to transform the scale into % as follows: (observed score - min of the scale)/(max-min)
-# We have done this for both means and standard deviations.
-
-df_scale_ranges <- read.csv(here("scale_ranges.csv"))
-df_appl_v_orange <- full_join(df_appl_v_orange, df_scale_ranges, by = "instrument_name")
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(perc_baseline_mean_active = (baseline_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_active = baseline_sd_active / (scale_max - scale_min)) %>%  # this is the best way to estimate the SD of the linear transformation of the score 
-  mutate(perc_baseline_mean_control = (baseline_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_baseline_sd_control = baseline_sd_control  / (scale_max - scale_min)) %>% 
-  mutate(perc_post_mean_active = (post_mean_active - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_active = post_sd_active  / (scale_max - scale_min)) %>% 
-  mutate(perc_post_mean_control = (post_mean_control - scale_min) / (scale_max - scale_min)) %>% 
-  mutate(perc_post_sd_control = post_sd_control  / (scale_max - scale_min))
-
-# Need to use SMDs (ie our Cohen's d) and then use standard error of SMD, to achieve this I need test-retest reliabilities of instruments.
-
-# CDRS reliability taken from here https://www.liebertpub.com/doi/epdf/10.1089/104454601317261546 
-# Using a   2-week interval, and different psychiatrists from the first to the second assessment, 
-# Poz-nanski et    al. (1984) demonstrated high reliability (r=   0.86) 
-# for the CDRS-R total score in 53 clinic-referred 6- to 12-year-olds.
-
-### A few more tidying things from Argyris before doing meta-analyses
-# Discovered some errors in the percentage women variable. Have gone back and checked. 
-df_appl_v_orange[df_appl_v_orange$study_ID=="Fristad, 2019_cbt + placebo_placebo",]$percent_women <-43.1
-df_appl_v_orange[df_appl_v_orange$study=="Clarke, 1995",]$percent_women <-47.3
-df_appl_v_orange[df_appl_v_orange$study=="Moeini, 2019",]$percent_women <-100
-df_appl_v_orange[df_appl_v_orange$study=="Santomauro, 2016",]$percent_women <-40
-
-# Calculate SE for baseline severity --------------------------------------
-
-df_appl_v_orange$baseline_st_error_active <- 
-  df_appl_v_orange$baseline_sd_active/sqrt(df_appl_v_orange$baseline_n_active)
-
-df_appl_v_orange$baseline_st_error_control <-
-  df_appl_v_orange$baseline_sd_control/sqrt(df_appl_v_orange$baseline_n_control)
-
-# Turn into a long database with unique rows ------------------------------
-
-### Important: create a dataset that will have unique control studies (see problem that we identified, namely common control conditions)
-# create new id to help with better identification and work with duplicates (see below) 
-df_appl_v_orange  <- df_appl_v_orange  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-# We are going to use the descr_active and descr_control columns rather than active_type and control_type columns, as these have unique values for each study.
-However the descr columns are empty for med studies, so I'm going to paste values across to fix this error.
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(descr_active = if_else(is.na(descr_active ), active_type , descr_active ))
-
-df_appl_v_orange <- df_appl_v_orange %>% 
-  mutate(descr_control = if_else(is.na(descr_control), control_type, descr_control ))
-
-# Step 1: keep only the rows with the top instrument in our hierarchy
-df_with_distinct_instruments <-  df_appl_v_orange %>%          
-  group_by(new_study_id) %>% 
-  filter(instrument_value == min(instrument_value)) # coded for the smallest number to be best.
-
-write.csv(df_with_distinct_instruments, "df_with_distinct_instruments.csv")
-
-# Step 2: turn dataframes to long
-
-# A small bit of cleaning so the code below will work
-
-df_with_distinct_instruments <- df_with_distinct_instruments %>% 
-  rename (percent_women_active = active_percent_women, 
-          percent_women_control = control_percent_women,
-          percent_women_overall = percent_women)
-
-# A: turn long the rows with active
-active_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, active_type, descr_active, psy_or_med, baseline_n_active, cohens_d_active,
-                 baseline_mean_active, baseline_sd_active, post_mean_active, post_sd_active,
-                 perc_baseline_mean_active, perc_baseline_sd_active, perc_post_mean_active, perc_post_sd_active, percent_women_overall, percent_women_active, age_m_active, age_sd_active, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
-  rename(treatment = descr_active) %>% 
-  rename(type = active_type) %>% 
-  rename_with(~ str_remove(., "_active")) %>% 
-  mutate(arm_effect_size = "cohens_d_active") %>% # chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
-  group_by(new_study_id) %>% #go through each study id and remove duplicates
-  distinct(treatment, .keep_all = TRUE)
-
-control_df <- df_with_distinct_instruments %>% 
-  dplyr:: select(new_study_id, control_type, descr_control, psy_or_med, baseline_n_control, cohens_d_control,
-                 baseline_mean_control, baseline_sd_control,post_mean_control, post_sd_control,
-                 perc_baseline_mean_control, perc_baseline_sd_control, perc_post_mean_control, perc_post_sd_control, percent_women_overall, percent_women_control, age_m_control, age_sd_control, age_m_overall, age_sd_overall, no_sites, instrument_name) %>%
-  rename(treatment = descr_control) %>% 
-  rename(type = control_type) %>% 
-  rename_with(~ str_remove(., "_control")) %>% 
-  mutate(arm_effect_size = "cohens_d_control") %>% #chose this clunky name because I had used this variable name in previous code and don't want to bread the rest
-  group_by(new_study_id) %>% #go through each study id and remove duplicates
-  distinct(treatment, .keep_all = TRUE)
-
-df_long_for_metan <- rbind(active_df, control_df)
-
-# I'm going to remove the March / TADS psy control row.
-It is currently filled with NAs which implies missing data, however it is actually the case that this condition doesn't exist as such (the control is placebo, which is not a psy control).
-
-df_long_for_metan <- df_long_for_metan %>%
-  filter(!(new_study_id == "March, 2004" & is.na(treatment)))
-
-# I'm going to perform  the operations to calculate overall age and percent women here now.
-We just want this per study rather than per arm for the first set of meta-analyses as we are going to compare psy vs med (2 subgroups) rather than the 4 arms
-
-df_long_for_metan <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(n_overall = sum(baseline_n)) %>% 
-  mutate(age_overall = sum(age_m * baseline_n) / sum(baseline_n)) %>% 
-  mutate(mean_age = coalesce(age_overall, age_m_overall)) %>% 
-  mutate(pooled_sd_age = sqrt(sum((age_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(se_age = pooled_sd_age / sqrt(n_overall)) %>% 
-  mutate(sex_overall = sum(percent_women * baseline_n) / sum(baseline_n)) %>% 
-  mutate(percent_women = coalesce(percent_women_overall, sex_overall))
-
-# Now just get rid of the unnecessary columns as these are causing clutter
-
-df_long_for_metan <- df_long_for_metan %>% 
-  select(-c(percent_women_overall, age_m, age_sd, age_m_overall, age_sd_overall, age_overall, sex_overall))
-
-# Remember that these are now per study, not per arm.
-
-# Create SEs proportions for percentage women --------------------------------------------
-
-# We also need to calculate SE for proportion women for the baseline calculations
-# for proportions, this is calculated as sqrt(p(1-p)/n), which I implement stepwise below
-
-df_long_for_metan <- df_long_for_metan %>% 
-  mutate(product_perc_women = (percent_women/100)* (1-(percent_women/100)) )
-
-df_long_for_metan <- df_long_for_metan %>% 
-  mutate(percent_women_std_error = sqrt(product_perc_women/ n_overall))
-
-# Create unique IDs by arm for multilevel metaregression
-
-df_long_for_metan <- df_long_for_metan %>%
-  group_by(new_study_id) %>%
-  mutate(arm_id = paste0(new_study_id, "_", row_number())) %>%
-  ungroup()
-
-#dim(df_long_for_metan ) #check dimension
-#make sure no study lost
-#length(unique(df_long_for_metan$new_study_id ) ) == # #length(unique(df_appl_v_orange$new_study_id ) )
-
-# Now check again the studies with muliple arms
-# Now checking if this worked with the studies that I used to illustrate the problem above. 
-# df_long_for_metan[df_long_for_metan$new_study_id == "Stallard, 2012",]
-# df_long_for_metan[df_long_for_metan$new_study_id == "Atkinson, 2014",]
-# # also check one which is single to make sure it is kept
-# df_long_for_metan[df_long_for_metan$new_study_id == "Ackerson, 1998",]
-
-# For response rate, recalculating after turning long and doing all the imputations
-
-# df_long_for_metan <- df_long_for_metan %>%
-#   rowwise() %>%
-#   mutate(responders = sum(rnorm(baseline_n, post_mean, 
-#                                 post_sd) < (baseline_mean/ 2)))
-# 
-# df_long_for_metan <- df_long_for_metan %>%
-#   rowwise() %>%
-#   mutate(resp_rate = responders/baseline_n)
-# 
-# summary_resp_rate <- df_long_for_metan %>%
-#   group_by(group) %>%
-#   summarise(mean_resp_rate = mean(resp_rate, na.rm = TRUE),
-#             sd_resp_rate = sd(resp_rate, na.rm = TRUE), 
-#             n = n())
-
-# save this as the master dataframe  --------------------------------------
-# use this dataframe to perform all operations below
-
-write.csv(df_long_for_metan, "df_long_for_metan.csv", row.names = F)
-
-########### simulate so that each study has a value from a distribution of 
-######## of correlations.
-
-# I will generate random numbers per study id from a distribution with these parameters. 
-# it is reasonable to generate one random correlation value per study as there is no reason why the correlation should
-# systematically vary within studies
-
-# Use the function I have created for this
-
-df_long_for_metan <- read.csv("df_long_for_metan.csv")
-
-list_df_simulated <-  simulate_dataframes_for_st_errors (df = df_long_for_metan, 
-                                              num_repetitions = 1000, 
-                                              seed  = 1974,
-                                              n = length(unique(df_long_for_metan$new_study_id)), 
-                                              a = 0.45, 
-                                              b = .9, 
-                                              mean = 0.65, 
-                                              sd = 0.2)
-
-#check this worked
-
-#list_df_simulated[[10]][,c("new_study_id", "correlation_sim_values", "simulated_se")] # looks right
-#summary(list_df_simulated[[1000]]$correlation_sim_values, na.rm = T) # as expected # the mean is around the parameter I gave
-
-```
-
-# Findings
-
-```{r metaregression-all, warning=FALSE, message = FALSE, echo=FALSE}
-
-# This chunk of code needs to be here because some of the data needed for the included studies summary lives here
-
-# Get Ns, run metareg, prepare graphing ------------------------------------------------------
-
-# add a new multilevel variable to the simulated data for the regression
-
-for(i in 1: length(list_df_simulated)){
-
-list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
-  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-
-  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
-
-  # relevel so that medication control becomes the reference category for the regression
-#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
-                                                       "medication_control",
-                                                       "medication_active", 
-                                                       "psychotherapy_control",
-                                                       "psychotherapy_active")
-}
-
-# check it worked
-# list_df_simulated[[2]] %>% 
-# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
-
-######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
-# A) the overall sample
-# B) the CBT vs Fluox and Escitalopram sample
-# C) the no WL sample
-# D) clinical levels of depression
-# E) the CDRS only sample
-# E) HAMD sensitivity analysis
-# G) Studies with post SD
-# H) Studies with variance <.02
-
-# A. Estimate Means and CIs for the overall ----------------------------------
-
-# count studies
-# count the number of studies
-n_unique_studies <- length(unique(df_long_for_metan$new_study_id)) # CHARLOTTE please check
-df_count_studies <- count_studies(df_long_for_metan) # CHARLOTTE please check
-# CB checked both, both correct.
-
-# specify model
-model_1 <- as.formula(~ four_level_var)
-
-# run metareg function 
-# here you can use the simulated results directly
-list_model_1_meta_reg <- run_multi_metaregression(list_df_simulated, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_overall <-  aggregate_model_results(list_model_1_meta_reg, condition)
-aggregate_results_overall <- cbind(aggregate_results_overall, condition)
-
-# extract SMDs from the  list
-list_dummy_var_means <-  lapply(list_model_1_meta_reg, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-df_mean_coefs_from_sim <- calculate_mean_coefs_ses(list_dummy_var_means, condition)
-
-df_mean_coefs_from_sim <- data.frame(cbind(condition,df_mean_coefs_from_sim))
-
-# add the ns
-df_mean_coefs_from_sim <- left_join(df_mean_coefs_from_sim, df_count_studies[df_count_studies$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-
-# Extract I2 values for each dataset
-i2_results_all <- extract_i2_values(list_model_1_meta_reg)
-
-# Calculate the mean and standard deviation of I2 values for each level
-i2_summary_all <- data.frame(
-  mean_i2_level2 = mean(i2_results_all$i2_level2, na.rm = TRUE),
-  sd_i2_level2 = sd(i2_results_all$i2_level2, na.rm = TRUE),
-  mean_i2_level3 = mean(i2_results_all$i2_level3, na.rm = TRUE),
-  sd_i2_level3 = sd(i2_results_all$i2_level3, na.rm = TRUE)
-)
-```
-
-```{r metaregression-fluox, warning=FALSE, message = FALSE, echo=FALSE}
-# B. Estimate Means and CIs for CBT Fluox Esc --------------------------------
-#  grab ids for those studies
-cbt_fluox_esc_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-
-# Use those ids to subset all dataframes in the list
-# By searching for IDs we have mistakenly included multiple active arms. E.g. for Atkinson which has dulox and fluox.
-# So we need to further subset the simulated dfs. For the active arms, I am filtering out conditions that do not meet our criteria.
-# This leaves all the control conditions from trials where the active is cbt, fluox or esc.
-# We may have multiple controls per study id for this reason, though this isn't a problem
-# conceptually.
-
-list_cbt_fluox_esc_study <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% cbt_fluox_esc_study_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-})
-
-# count the number of studies
-cbt_fluox_esc_study <- df_long_for_metan %>%
-  filter(new_study_id %in% cbt_fluox_esc_study_ids,
-         !(arm_effect_size == "cohens_d_active" & !(type %in% c("Fluoxetine", "Escitalopram", "cbt"))))
-study_count_cbt_fluox_esc_study <- count_studies(cbt_fluox_esc_study)
-# CB checked, looks good now.
-
-# apply the metareg function to the list of cbt, fluox, esc
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cbt_fluox_esc_study <- run_multi_metaregression(list_cbt_fluox_esc_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cbt_fluox_esc_study <-  aggregate_model_results(list_model_1_cbt_fluox_esc_study, condition)
-aggregate_results_cbt_fluox_esc_study <- cbind(aggregate_results_cbt_fluox_esc_study, condition)
-
-# extract SMDs from the list for cbt fluox escit
-means_cbt_fluox_esc_study <-  lapply(list_model_1_cbt_fluox_esc_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cbt_fluox_esc_study <- calculate_mean_coefs_ses(means_cbt_fluox_esc_study, condition)
- coef_and_se_means_cbt_fluox_esc_study <- data.frame(cbind(condition, coef_and_se_means_cbt_fluox_esc_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cbt_fluox_esc_study <- left_join(coef_and_se_means_cbt_fluox_esc_study, study_count_cbt_fluox_esc_study[study_count_cbt_fluox_esc_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-```
-
-```{r metaregression-nowl, warning=FALSE, message = FALSE, echo=FALSE}
-
-# C. Estimate Means and CIs without WL ---------------------------------------
-
- # grab the ids for no waitlist
-no_wl_ids <-df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
-
-# use them to loop over the simulated list to subset all the dataframes.
-
-list_no_wl <- lapply(list_df_simulated, function(df) {
-  df %>%
-    filter(new_study_id %in% no_wl_ids) %>%
-    filter(!(arm_effect_size == "cohens_d_control" & type == "wl")) 
-})
-
-# count studies 
-no_wl_studies <- df_long_for_metan %>% 
-  filter(new_study_id %in% no_wl_ids) %>%
-  filter(!(arm_effect_size == "cohens_d_control" & type == "wl"))
-study_count_no_wl_study <- count_studies(no_wl_studies)
-# CB checked, looks good!
-
-# use this model as above
-model_1 <- as.formula(~ four_level_var)
-
-# apply the metareg function to the list of no wl
-list_model_1_no_wl <- run_multi_metaregression(list_no_wl , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_no_wl <-  aggregate_model_results(list_model_1_no_wl, condition)
-aggregate_results_no_wl <- cbind(aggregate_results_no_wl, condition)
-
-# now use the function to extract the coefficients
-means_no_wl <-  lapply(list_model_1_no_wl, extract_coefficients_func)
-
-# run the mean function for no wl
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_no_wl <- calculate_mean_coefs_ses(means_no_wl, condition)
-coef_and_se_means_no_wl <- data.frame(cbind(condition,coef_and_se_means_no_wl))
-
-coef_and_se_means_no_wl <- left_join(coef_and_se_means_no_wl, study_count_no_wl_study[study_count_no_wl_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-clin, warning=FALSE, message = FALSE, echo=FALSE}
-
-# D. Clinical Levels Depression Sensitivity Analysis---------------------------------------
-
-# We need to decide how we want to do this. We have mdd, mood, sub, and cut categories. For now I'll just exclude sub.
-
-#take study ids where sample has clinical levels of depression
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_clin_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_clin_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% clin_study_ids,]
-}
-
-# count the number of studies
-study_count_clin_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% clin_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_clin_study <- run_multi_metaregression(list_clin_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_clin_study <-  aggregate_model_results(list_model_1_clin_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_clin_study <-  lapply(list_model_1_clin_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_clin_study <- calculate_mean_coefs_ses(means_clin_study, condition)
-coef_and_se_means_clin_study <- data.frame(cbind(condition, coef_and_se_means_clin_study))
-
-# add the ns to the dataframe
-coef_and_se_means_clin_study <- left_join(coef_and_se_means_clin_study, study_count_clin_study[study_count_clin_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
-
-# E. CDRS Sensitivity Analysis ---------------------------------------
-
-cdrs_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "cdrs",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_cdrs_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_cdrs_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% cdrs_study_ids,]
-}
-
-# count the number of studies
-study_count_cdrs_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% cdrs_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of cdrs studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_cdrs_study <- run_multi_metaregression(list_cdrs_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_cdrs_study <-  aggregate_model_results(list_model_1_cdrs_study, condition)
-
-# extract SMDs from the list for cdrs
-means_cdrs_study <-  lapply(list_model_1_cdrs_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_cdrs_study <- calculate_mean_coefs_ses(means_cdrs_study, condition)
-coef_and_se_means_cdrs_study <- data.frame(cbind(condition, coef_and_se_means_cdrs_study))
-
-# add the ns to the dataframe
-coef_and_se_means_cdrs_study <- left_join(coef_and_se_means_cdrs_study, study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-```
-
-```{r metaregression-hamd, warning=FALSE, message = FALSE, echo=FALSE}
-
-# F. HAMD Sensitivity Analysis ---------------------------------------
-
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_hamd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_hamd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                          %in% hamd_study_ids,]
-}
-
-# count the number of studies
-study_count_hamd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% hamd_study_ids,])
-# CB checked, correct.
-
-# apply the metareg function to the list of cdrs studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_hamd_study <- run_multi_metaregression(list_hamd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_hamd_study <-  aggregate_model_results(list_model_1_hamd_study, condition)
-
-# extract SMDs from the list for cdrs
-means_hamd_study <-  lapply(list_model_1_hamd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_hamd_study <- calculate_mean_coefs_ses(means_hamd_study, condition)
-coef_and_se_means_hamd_study <- data.frame(cbind(condition, coef_and_se_means_hamd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_hamd_study <- left_join(coef_and_se_means_hamd_study, study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>% 
-                                        ungroup() %>% 
-                                      select(condition, n),  
-                                    by = "condition")
-
-```
-
-```{r metaregression-postsd, warning=FALSE, message = FALSE, echo=FALSE}
-
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
-
-```
-
-```{r metaregression-var, warning=FALSE, message = FALSE, echo=FALSE}
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
-
-## Included studies
-
-Data for included studies are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-Please see @fig-prisma for a summary of the sources of included RCTs.
-
-In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r sum(df_count_studies[df_count_studies$condition == "medication_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "medication_control", "n"])` control arms of medication trials; and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_control", "n"])` control arms from psychotherapy RCTs.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-
-Placebo pill was the control condition for all medication trials.
-In psychotherapy trials, the control arm included 14 waitlist, 25 treatment-as-usual (TAU), and 19 other control conditions (e.g.
-relaxation training, attention control, counselling).
-
-```{r, echo=FALSE}
-#| label: fig-prisma
-#| fig-cap: "PRISMA chart summarising sources of included studies"
-#| fig-cap-location: top
-knitr::include_graphics(here("PRISMA.png"))
-```
-
-## Sample characteristics at baseline in medication and psychotherapy trials
-
-@tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
-The summary statistics are provided for each subgroup (i.e.
-medication and psychotherapy) and the p-value derives from the test for subgroup differences.
-
-```{r characteristics-metanalysis, warning=FALSE, message = FALSE, echo=FALSE}
-
-# Start by looking at demographics at baseline
-# Currently we have both control and active conditions, we just need each study once
-
-df_baseline_demographics <- df_long_for_metan %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-# This is the function to extract statistics
-
-extract_stats <- function(df) {
-
-  # get the summary table with results
-  statistics <- summary(df, byvar = "psy_or_med")
-
-  df_stats <- tibble(
-  subgroup = statistics$subgroup.levels,
-  k_study = statistics$k.study.w,
-  TE_random = statistics$TE.random.w,
-  seTE_random = statistics$seTE.random.w,
-  lower_random = statistics$lower.random.w,
-  upper_random = statistics$upper.random.w,
-  tau2 = statistics$tau2.w)
-
-  # Add an empty row at the top and column on right (this is for the test for subgroup differences p value)
-  df_stats <- rbind(data.frame(subgroup = NA, k_study = NA, TE_random = NA, seTE_random = NA, 
-                             lower_random = NA, upper_random = NA, tau2 = NA), df_stats)
-  df_stats <- cbind(df_stats, pval_between = NA)
-
-  # Set the value in the last row and last column as the between groups p val
-  df_stats[1, "pval_between"] <- statistics$pval.Q.b.random
-
-  return(df_stats)
-
-}
-
-#A. Baseline severity meta-analysis--------------
-
-# Overall psy vs med
-
-# Need to calculate the variables first
-df_for_baseline_severity <- df_long_for_metan %>% 
-  group_by(new_study_id) %>%
-  mutate(perc_baseline_overall = sum(perc_baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_perc_sd_baseline = sqrt(sum((perc_baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(perc_se_baseline = pooled_perc_sd_baseline / sqrt(n_overall)) %>%  # now also do this for untransformed variable
-  mutate(baseline_overall = sum(baseline_mean * baseline_n) / sum(baseline_n)) %>% 
-  mutate(pooled_sd_baseline = sqrt(sum((baseline_sd^2) * (baseline_n - 1)) / sum(baseline_n - 1))) %>% 
-  mutate(se_baseline = pooled_sd_baseline / sqrt(n_overall))
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-  distinct(new_study_id, .keep_all = TRUE)
-
-df_for_baseline_severity <- df_for_baseline_severity %>% 
-    filter(new_study_id != "March, 2004")  # removing TADS because it does not technically belong to either the psy or med groups
-
-met_sev <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev <- extract_stats(met_sev)
-
-# Clinical sample
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_baseline_severity_clin <- df_for_baseline_severity %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_sev_clin <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity clinical",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_clin <- extract_stats(met_sev_clin)
-
-# cbt + med
-
-# cbt_meds_study_ids <-
-#   df_appl_v_orange[df_appl_v_orange$active_type == "cbt" | df_appl_v_orange$active_type == "Fluoxetine" | df_appl_v_orange$active_type == "Escitalopram",]$new_study_id
-# 
-# df_for_baseline_severity_cbt <- df_for_baseline_severity %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_sev_cbt <- metagen(TE = perc_baseline_overall,
-#                            seTE = perc_se_baseline,
-#                            studlab = new_study_id,
-#                            data = df_for_baseline_severity_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "baseline severity cbt + med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# results_met_sev_cbt <- extract_stats(met_sev_cbt)
-
-# no wl
-
-no_wl_ids <- df_appl_v_orange[df_appl_v_orange$control_type != "wl",]$new_study_id
-
-df_for_baseline_severity_no_wl <- df_for_baseline_severity %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_sev_no_wl <- metagen(TE = perc_baseline_overall,
-                           seTE = perc_se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity no wl studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_no_wl <- extract_stats(met_sev_no_wl)
-
-#B. Sex meta-analysis
-
-# Now start looking at perc_women variable
-# The metagen function doesn't like when NAs result in the TE vector being a different length to subgroup vector. Need to start by removing NAs.
-
-df_for_sex_metan <- df_baseline_demographics %>% 
-  filter(!is.na(percent_women))
-
-df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(percent_women != 100) # filter out studies with only women
-
-df_for_sex_metan <- df_for_sex_metan %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-met_perc_women_overall <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies")
-
-met_perc_women_overall <- update(met_perc_women_overall,
-                              subgroup = df_for_sex_metan$psy_or_med, subgroup.name = "treatment modality",
-                              tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-
-results_met_perc_women_overall <- extract_stats(met_perc_women_overall)
-
-# looking at clinical sample only
-
-df_for_sex_metan_clin <- df_for_sex_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_perc_women_clin <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across clinical studies")
-
-met_perc_women_clin <- update(met_perc_women_clin,
-                           subgroup = df_for_sex_metan_clin$psy_or_med, subgroup.name = "treatment modality",
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_clin <- extract_stats(met_perc_women_clin)
-
-# # Now looking at the CBT + med studies only
-# 
-# df_for_sex_metan_cbt <- df_for_sex_metan %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_perc_women_cbt <- metagen(TE = percent_women,
-#                            seTE = percent_women_std_error,
-#                            studlab = new_study_id,
-#                            data = df_for_sex_metan_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "percentage women across cbt and med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# # Apply the function to the meta-analysis result
-# results_met_perc_women_cbt <- extract_stats(met_perc_women_cbt)
-
-# Now the no waitlist group
-
-df_for_sex_metan_no_wl <- df_for_sex_metan %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_perc_women_no_wl <- metagen(TE = percent_women,
-                           seTE = percent_women_std_error,
-                           studlab = new_study_id,
-                           data = df_for_sex_metan_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "percentage women across studies with controls that are not wl",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-# Apply the function to the meta-analysis result
-results_met_perc_women_no_wl <- extract_stats(met_perc_women_no_wl)
-
-# C. Age meta-analysis--------------------
-
-# We have several studies for which we are missing SE for age. I am going to perform an imputation by taking an average
-# for the studies we do have, per modality, and substituting this in for missing values.
-
-df_baseline_demographics$se_age <- as.numeric(df_baseline_demographics$se_age)
-
-mean_se_age_psy <- df_baseline_demographics %>%
-  filter(psy_or_med == 1) %>%
-  summarise(mean_se_age_psy = mean(se_age, na.rm = TRUE))
-
-mean_se_age_med <- df_baseline_demographics %>%
-  filter(psy_or_med == 0) %>%
-  summarise(mean_se_age_med = mean(se_age, na.rm = TRUE))
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  mutate(se_age = ifelse(!is.na(se_age), se_age,
-                         ifelse(psy_or_med == 1, mean_se_age_psy, mean_se_age_med)))
-
-df_for_age_metan <- df_baseline_demographics %>% 
-  filter(!is.na(mean_age))
-
-df_for_age_metan <- df_for_age_metan %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-# Age meta analysis
-
-df_for_age_metan$se_age <- as.numeric(df_for_age_metan$se_age)
-
-met_age <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age <- extract_stats(met_age)
-
-# Looking at clinical sample only
-
-clin_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$diagnosis != "sub",]$new_study_id
-
-df_for_age_metan_clin <- df_for_age_metan %>%
-  filter(new_study_id %in% clin_study_ids)
-
-met_age_clin <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_clin,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across clinical studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age_clin <- extract_stats(met_age_clin)
-
-# # Now cbt + med studies only
-# 
-# df_for_age_metan_cbt <- df_for_age_metan %>%
-#   filter(new_study_id %in% cbt_meds_study_ids) 
-# 
-# met_age_cbt <- metagen(TE = mean_age,
-#                            seTE = se_age,
-#                            studlab = new_study_id,
-#                            data = df_for_age_metan_cbt,
-#                            sm = "",
-#                            fixed = FALSE,
-#                            random = TRUE,
-#                            method.tau = "REML",
-#                            hakn = TRUE,
-#                            title = "age across cbt + med studies",
-#                            subgroup = psy_or_med,
-#                            tau.common = FALSE)
-# 
-# results_met_age_cbt <- extract_stats(met_age_cbt)
-
-# Now excluding wl
-
-df_for_age_metan_no_wl <- df_for_age_metan %>%
-  filter(new_study_id %in% no_wl_ids)
-
-met_age_no_wl <- metagen(TE = mean_age,
-                           seTE = se_age,
-                           studlab = new_study_id,
-                           data = df_for_age_metan_no_wl,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "age across no wl studies",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_age_no_wl <- extract_stats(met_age_no_wl)
-
-# This is if we want to have all sensitivity analyses in table one
-
-df_overall_baseline_results <- rbind(results_met_sev, results_met_sev_clin, results_met_sev_no_wl, results_met_perc_women_overall, results_met_perc_women_clin, results_met_perc_women_no_wl, results_met_age, results_met_age_clin, results_met_age_no_wl)
-
-# For row names
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(subgroup = case_when(
-    row_number() %in% c(1, 10, 19) ~ "Overall",
-    row_number() %in% c(4, 13, 22) ~ "Excluding subclinical",
-    row_number() %in% c(7, 16, 25) ~ "Excluding waitlist",
-    TRUE ~ if_else(subgroup == 0, "Medication", "Psychotherapy")
-  ))
-
-# Define new column names
-new_column_names <- c("Subgroup", "K", "Mean", "SE", "Lower CI", "Upper CI", "T2", "p-value")
-
-# Assign new column names to the data frame
-colnames(df_overall_baseline_results) <- new_column_names
-
-# Rounding
-df_overall_baseline_results <- df_overall_baseline_results %>%
-  mutate(across(.cols = 2:(ncol(.) - 1), ~ round(., 2))) %>%
-  mutate_at(vars(ncol(.)), ~ round(., 3)) %>%
-  mutate_all(~if_else(is.na(.), "", as.character(.)))
-
+#some set-up for flextables
 big_border = fp_border(color="black", width = 1)
 small_border = fp_border(color="lightgray", width = 1)
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-baseline-results
-#| tbl-cap: "Sample characteristics at baseline across medication and psychotherapy studies: Results for overall sample and sensitivity analyses"
-#| tbl-cap-location: top
-
-df_overall_baseline_results %>% 
-  mutate(category = case_when(
-    row_number() %in% 1:9 ~ "Baseline Severity of Depressive Symptoms*",
-    row_number() %in% 10:18 ~ "Percent Female",
-    row_number() %in% 19:27 ~ "Age",
-    TRUE ~ ""
-  )) %>% # grouping rows
-  group_by(category) %>%
-  as_flextable(hide_grouplabel = TRUE) %>% 
-  paginate(group = "category") %>% 
-  bold(i = c(1, 2, 5, 8, 11, 12, 15, 18, 21, 22, 25, 28), j = NULL, bold = TRUE, part = "body") %>%  # Bold specific rows
-  # set_table_properties(layout = "fixed") %>%  # Autofit column widths
-  bg(i = c(1, 11, 21), bg  = "#F2F2F2", part = "body") %>% # identify category sections
-  padding(i = c(3, 4, 6, 7, 9, 10, 13, 14, 16, 17, 19, 20, 23, 24, 26, 27, 29, 30), j = 1, padding.left = 10) %>% # indent some rows
-  align(j = 2:ncol(df_overall_baseline_results), align = "center", part = "all") %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row  
-  # italic(i = 2, italic = TRUE, part = "header") %>% 
-  border_remove() %>% # this is to remove borders that look strange
-  hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = 1, part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "all" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  line_spacing(space = .7, part = "all") %>% 
-  add_footer_row(values = as_paragraph(
-    "Abbreviations: K = number of studies, SE = standard error, CI = 95% confidence interval, T2 = estimate of between-study heterogeneity",
-    "*These are baseline depression scores transformed to reflect percentage of a scale range (see Supplement for detailed description).To take an example, the CDRS gives a possible total score from 17 to 113 (i.e.
-range of 96).
-Mean severity was 0.36 for psychotherapy studies and 0.42 for medication studies, which would translate to 51.56 (17 + 0.36 x 96) and 57.32 (17 + 0.42 x 96), respectively, as equivalent scores on the CDRS."), colwidths = 8) %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  autofit()
-
-```
-
-```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
-
-mean_psych_overall <- 0.37
-mean_med_overall <- 0.42
-se_psych_overall <- 0.02
-se_med_overall <- 0.01
-n_psych_overall <- 49
-n_med_overall <- 31
-
-# Calculate standard deviation
-sd_psych_overall <- se_psych_overall * sqrt(n_psych_overall)
-sd_med_overall <- se_med_overall * sqrt(n_med_overall)
-
-#formula with pooled sd
-pooled_sd_overall <- sqrt(((sd_psych_overall^2 + sd_med_overall^2)/2))
-
-# Calculate Cohen's d
-cohens_d_overall <- (mean_psych_overall - mean_med_overall) / pooled_sd_overall
-
-## without subclinical
-
-mean_psych_sub <- 0.39
-mean_med_sub <- 0.42
-se_psych_sub <- 0.02
-se_med_sub <- 0.01
-n_psych_sub <- 41
-n_med_sub <- 31
-
-# Calculate standard deviation
-sd_psych_sub <- se_psych_sub * sqrt(n_psych_sub)
-sd_med_sub <- se_med_sub * sqrt(n_med_sub)
-
-#formula with pooled sd
-pooled_sd_sub <- sqrt(((sd_psych_sub^2 + sd_med_sub^2)/2))
-
-# Calculate Cohen's d
-cohens_d_sub <- (mean_psych_sub - mean_med_sub) / pooled_sd_sub
-cohens_d_sub
-cohens_d_overall
-```
-
-### Baseline severity
-
-On average, depression severity at baseline was significantly higher in medication trials compared to psychotherapy trials (see @tbl-baseline-results).
-When excluding RCTs that used waitlist as their control, baseline severity remained significantly higher in medication trials compared to psychotherapy trials.
-This difference did not reach statistical significance when excluding studies that recruited samples with sub-clinical depression.
-
-```{r baseline-severity, echo=FALSE, message=FALSE, warning=FALSE}
-# looking at CDRS studies only, this is with only 2 levels
-
-df_for_baseline_severity_cdrs <- df_for_baseline_severity %>%
-  filter(new_study_id %in% cdrs_study_ids)
-
-met_sev_cdrs <- metagen(TE = baseline_overall,
-                           seTE = se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_cdrs,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cdrs",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_cdrs <- extract_stats(met_sev_cdrs)
-
-# looking at HAMD studies only,
-
-df_for_baseline_severity_hamd <- df_for_baseline_severity %>%
-  filter(new_study_id %in% hamd_study_ids)
-
-met_sev_hamd <- metagen(TE = baseline_overall,
-                           seTE = se_baseline,
-                           studlab = new_study_id,
-                           data = df_for_baseline_severity_hamd,
-                           sm = "",
-                           fixed = FALSE,
-                           random = TRUE,
-                           method.tau = "REML",
-                           hakn = TRUE,
-                           title = "baseline severity cdrs",
-                           subgroup = psy_or_med,
-                           tau.common = FALSE)
-
-results_met_sev_hamd <- extract_stats(met_sev_hamd)
-```
-
-```{r baseline-severity-hamd-cdrs, warning=FALSE, message = FALSE, echo=FALSE}
-## this is for four levels
-### get CDRS studies
-cdrs_studies_for_baseline_metareg <- list_cdrs_study[[1]] # created this above, you can take any of these, as the means and sds are repeated.
-
-#turn sds to sec
-cdrs_studies_for_baseline_metareg$baseline_stand_error <- cdrs_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(cdrs_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
-                                                              #throughout
-
-results_cdrs_metareg_baseline <- run_metareg_and_extract(cdrs_studies_for_baseline_metareg,
-                                                         model_1, condition)
-
-results_cdrs_metareg_baseline[[2]] <- left_join(results_cdrs_metareg_baseline[[2]], study_count_cdrs_study[study_count_cdrs_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-
-### get HAM-D studies
-hamd_study_ids <-
-  df_appl_v_orange[df_appl_v_orange$instrument_name == "hamd",]$new_study_id
-
-list_hamd_study <- list_df_simulated[[1]][list_df_simulated[[1]]$new_study_id
-                                                          %in% hamd_study_ids,]
-
-hamd_studies_for_baseline_metareg <- list_hamd_study #
-
-#turn sds to sec
-hamd_studies_for_baseline_metareg$baseline_stand_error <- hamd_studies_for_baseline_metareg$baseline_sd/
-                                        sqrt(hamd_studies_for_baseline_metareg$baseline_n)
-
-model_1 <- as.formula(~ four_level_var)
-condition <-  levels(list_df_simulated[[1]]$four_level_var) # this is the four level var
-                                                              #throughout
-results_hamd_metareg_baseline <- run_metareg_and_extract(hamd_studies_for_baseline_metareg,
-                                                         model_1, condition)
-
-results_hamd_metareg_baseline$condition <-  levels(list_df_simulated[[1]]$four_level_var)
-
-results_hamd_metareg_baseline[[2]] <- left_join(results_hamd_metareg_baseline[[2]], study_count_hamd_study[study_count_hamd_study$is_missing == FALSE, ] %>%
-                                        ungroup() %>%
-                                      select(condition, n),
-                                    by = "condition")
-
-```
-
-To ensure that this was not an artefact of variable transformation, we also compared means at baseline in the two instruments, CDRS and HAM-D, on which there was a sufficient number of studies to metanalyse.
-As can be seen in @tbl-hamd-baseline and @tbl-cdrs-baseline (see Supplemental Materials), the number of studies is much smaller, but the pattern of differences is the same for the HAM-D and the CDRS, though it does not reach statistical significance for the latter.
-
-### Sex
-
-For this analysis, we excluded the two psychotherapy trials which included entirely female samples (Moeini, 2019; Shomaker, 2016; see @tbl-all-studies-percfemale-results in Supplement for results with full sample).
-As can be seen in @tbl-baseline_results, psychotherapy trials featured a significantly higher percentage of females when compared to medication trials.
-On average, samples were `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 1][[2]],2)`) female across psychotherapy trials and `r round(results_met_perc_women_overall$TE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`% (*SE* = `r round(results_met_perc_women_overall$seTE_random[results_met_perc_women_overall$subgroup == 0][[2]],2)`) female across medication trials.
-Excluding sub-clinical and waitlist control studies yielded similar results.
-
-### Age
-
-As can be seen in tbl-baseline_results, mean age was `r round(results_met_age$TE_random[results_met_age$subgroup == 1][[2]],2)` (*SE* = ``` r``round(results_met_age$seTE_random[results_met_age$subgroup == 1][[2]],2) ```) across psychotherapy trials and `r round(results_met_age$TE_random[results_met_age$subgroup == 0][[2]],2)` (*SE* = `r round(results_met_age$seTE_random[results_met_age$subgroup == 0][[2]],2)`) across medication trials, with no significant between group differences.
-There were no significant differences in mean age between modalities on further sensitivity analyses.
-
-## Trial design
-
-### Standardised mean differences of control conditions in psychotherapy and medication studies
-
-We applied metaregression to obtain the SMDs and confidence intervals of each of the four study arms.
-As seen in @fig-plot-means-all there were substantial differences between the four arms of the meta-analysis with striking differences between the medication and psychotherapy control arms.
-In particular, pill placebo had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "medication_control", ]$upper_ci, 2)`) whereas psychotherapy controls had an SMD = `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$coef_means, 2)` (95% CI: `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$lower_ci, 2)` to `r round(df_mean_coefs_from_sim[df_mean_coefs_from_sim$condition == "psychotherapy_control", ]$upper_ci, 2)` ).
-
-```{r, warning=FALSE, message = FALSE, echo = FALSE}
-#| label: smd-diff-control
-#| fig-cap: "Pre-Post Standardised Mean Differences (SMD) of Control Arms"
-#| fig-cap-location: top
-
-list_df_simulated[[1]] %>%
-  filter(arm_effect_size == "cohens_d_control") %>%
-  ggplot(aes(x = cohens_d, y = 0, color = as.factor(psy_or_med), size = baseline_n)) +
-  geom_jitter(height = 0.2, alpha = 0.7) +
-  geom_point(alpha = 0.7) +
-  labs(
-    x = "SMD",
-    y = "",
-    color = "Type of Study",
-    size = "Baseline n"
-  ) +
-  scale_color_discrete(name = "Type of Study", labels = c("Medication", "Psychological Therapy")) +
-  theme_minimal() +
-  theme(
-    axis.text.y = element_blank(),
-    axis.ticks.y = element_blank(),
-    axis.title.y = element_blank()
-  )
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-#| label: fig-plot-means-all
-#| fig-cap: "Meta-analytic estimates of within-group changes for overall sample"
-#| fig-cap-location: top
-
-df_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-  mutate(condition = case_when(
-    condition == "medication_control" ~ "Medication Control",
-    condition == "medication_active" ~ "Medication Active",
-    condition == "psychotherapy_control" ~ "Psychotherapy Control",
-    condition == "psychotherapy_active" ~ "Psychotherapy Active",
-    TRUE ~ as.character(condition)))
-
-# subtitle_text_all <- "Metanalytic estimates of within-group changes: all studies"
-plot_means_multi_all <- plot_means_function(df_mean_coefs_from_sim)
-print(plot_means_multi_all)
-
- png("plot_means_multi_all.png")
- plot_means_multi_all
- dev.off()
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-coefs-overall
-# #| tbl-cap: "Summary statistics of the estimated SMDs"
-# #| tbl-cap-location: top
-# 
-# # Prepare to tabulate
-# 
-# table_mean_coefs_from_sim <- df_mean_coefs_from_sim %>%
-#   mutate(across(where(is.numeric), ~round(., 2))) %>%
-#   relocate("n", .after = "condition") 
-# 
-# new_column_names <- c("Condition", "N", "Coefficient", "SE", "Lower CI", "Upper CI")
-# 
-# # Assign new column names to the data frame
-# colnames(table_mean_coefs_from_sim) <- new_column_names
-# 
-# flextable(table_mean_coefs_from_sim) %>%
-#   set_table_properties(width = 1) %>%
-#   autofit() %>%
-#   font(fontname = "Calibri", part = "all") %>% 
-#   # add_header_row(values = "Summary statistics of the estimated SMDs", colwidths = 6) %>%
-#   # add_header_row(values = "Table 3", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   align(j = 2:ncol(df_mean_coefs_from_sim), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-##### Sensitivity analyses
-
-We conducted a series of sensitivity analyses (all figures in the Supplement).
-Excluding waitlist control studies (see @fig-plot-means-no-wl) and sub-clinical studies (see @fig-plot-means-clin) yielded a pattern of results very similar to the overall analyses.
-Next, we examined the data including only those studies that used the CDRS (see @fig-plot-means-cdrs) or the HAMD (see @fig-plot-means-hamd).
-Medication control and psychotherapy control conditions remained significantly different, though the small number of studies resulted in less precise estimates of the SMDs.
-Conversely, restricting the analysis to studies with variance below 0.02 yielded a similar pattern of results, but with increased precision in SMD estimates across conditions (see @fig-plot-means-var2).
-Finally, we showed that different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
-
-##### Addressing regression to the mean
-
-```{r baseline-adjust-means, warning=FALSE, message = FALSE, echo=FALSE}
-# #### Let's start from the beginning and regress cohens on the baseline dataframe.
-# 
-# # create a new list with dfs for the sims
-# df_long_for_metan_adj_cohens_d <- df_long_for_metan
-# # rename the cohens_d value to make space for the new cohen's d
-# df_long_for_metan_adj_cohens_d <-
-#   df_long_for_metan_adj_cohens_d %>%
-# rename(unadjusted_cohens_d = cohens_d,
-# )
-# # estimate the cohen's d from the residuals
-# model_adjust_cohens_d <-  lm(df_long_for_metan_adj_cohens_d$unadjusted_cohens_d ~ df_long_for_metan_adj_cohens_d$perc_baseline_mean, na.action=na.exclude)
-# 
-# # there is a great effect of the baseline means, as shown here
-# results_adjusted_cohens_d <- broom:: tidy(model_adjust_cohens_d )
-# 
-# # extract the residuals which are the adjusted cohen's d, to get the simulated standard errors
-# df_long_for_metan_adj_cohens_d$cohens_d <- residuals(model_adjust_cohens_d )
-# 
-# # apply function to simulate standard errors
-# list_df_simulated_adj_cohens_d <- simulate_dataframes_for_st_errors(df = df_long_for_metan_adj_cohens_d,
-#                                    num_repetitions = 1000,
-#                                    seed  = 1974,
-#                                    n = length(unique(df_long_for_metan_adj_cohens_d$new_study_id)),
-#                                    a = 0.45,
-#                                    b = .9,
-#                                    mean = 0.65,
-#                                    sd = 0.2)
-# 
-# 
-# # add the four level variable and re-level
-# for(i in 1: length(list_df_simulated_adj_cohens_d)){
-# 
-#   list_df_simulated_adj_cohens_d[[i]]$arm_effect_size <- factor(list_df_simulated_adj_cohens_d[[i]]$arm_effect_size)
-#   list_df_simulated_adj_cohens_d[[i]] <- list_df_simulated_adj_cohens_d[[i]] %>%
-#     mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-#                                       psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-#                                       psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-#     )
-# 
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <- factor(list_df_simulated_adj_cohens_d[[i]]$four_level_var) # turn to factor
-# 
-#   # relevel so that medication control becomes the reference category for the regression
-#   #  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-#   list_df_simulated_adj_cohens_d[[i]]$four_level_var <-   fct_relevel(list_df_simulated_adj_cohens_d[[i]]$four_level_var,
-#                                                          "medication_control",
-#                                                          "medication_active",
-#                                                          "psychotherapy_control",
-#                                                          "psychotherapy_active")
-# }
-# 
-# 
-# 
-# 
-# 
-# # Run metaregression model (assuming that the four level variable is present given that I create this dataframe from the list_)
-# # specify model
-# model_x <- as.formula(~ four_level_var)
-# 
-# # run metareg function
-# # here you can use the simulated results directly
-# list_model_1_meta_reg_adj_cohens_d <- run_metaregression(list_df_simulated_adj_cohens_d, model_x)
-# 
-# # extract coefficients and model characteristics.
-# condition <- levels(list_df_simulated_adj_cohens_d[[1]]$four_level_var)
-# aggregate_results_overall_adjusted_cohens_d <-  aggregate_model_results(list_model_1_meta_reg_adj_cohens_d, condition)
-# aggregate_results_overall_adjusted_cohens_d <- cbind(aggregate_results_overall_adjusted_cohens_d, condition)
-# 
-# # extract SMDs from the  list
-# list_dummy_var_means_adjusted_cohens_d <-  lapply(list_model_1_meta_reg_adj_cohens_d, extract_coefficients_func)
-# 
-# # calculate mean SMDs and ses
-# df_mean_coefs_from_sim_adjusted_cohens_d <- calculate_mean_coefs_ses(list_dummy_var_means_adjusted_cohens_d, condition)
-# 
-# df_mean_coefs_from_sim_adjusted_cohens_d <- data.frame(cbind(condition, df_mean_coefs_from_sim_adjusted_cohens_d))
-#
-
-####code to extract baseline-adjusted post means
-
-de_meaned_baseline_mean <- (list_df_simulated[[1]]$perc_baseline_mean - mean(list_df_simulated[[1]]$perc_baseline_mean, na.rm = TRUE))
-
-lm_for_baseline_means <- lm(list_df_simulated[[1]]$perc_post_mean ~ de_meaned_baseline_mean + list_df_simulated[[1]]$four_level_var, na.action=na.exclude, )
-
-coefs_lm_for_baseline_means  <- broom:: tidy(lm_for_baseline_means)
-
-condition <- coefs_lm_for_baseline_means$term
-
-smds <-c(coefs_lm_for_baseline_means$estimate[1], coefs_lm_for_baseline_means$estimate[-1] + coefs_lm_for_baseline_means$estimate[1])
-
-upper_ci <- smds + coefs_lm_for_baseline_means$std.error*1.96
-
-lower_ci <- smds - coefs_lm_for_baseline_means$std.error*1.96
-
-de_meaned_smd_with_cis <- data.frame (
-
-  condition = levels(list_df_simulated[[1]]$four_level_var),
-
-  smds = smds[-2],
-
-  lower_ci = lower_ci[-2],
-
-  upper_ci = upper_ci[-2]
-
-)
-
-```
-
-We addressed potential regression to the mean by including the baseline score for each depression scale in the linear regression model as per equation 3 in @barnettRegressionMeanWhat2004 (see @tbl-de-meaned in the Supplement).
-The difference between the medication control and psychotherapy control arms remained significantly different.
-
-### Number of trial sites
-
-```{r trial-sites, warning=FALSE, message = FALSE, echo=FALSE}
-### Number of sites
-# Write results, tabulate.
-
-## This data lives in this spreadsheet for psy trials, we need to merge it in
-
-df_no_sites <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
-
-df_no_sites <- df_no_sites %>% 
-  select(c(new_study_id, number_of_sites)) %>% 
-  filter(!is.na(number_of_sites)) %>% 
-  distinct(new_study_id, .keep_all = TRUE) %>% 
-  mutate(number_of_sites = as.numeric(number_of_sites))
-
-df_baseline_demographics <- full_join(df_baseline_demographics, df_no_sites, by = "new_study_id")
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  filter(new_study_id != "March, 2004") # removing TADS because it does not technically belong to either the psy or med groups
-
-# we have different vectors for psy and med trials, lets coalesce
-
-df_baseline_demographics <- df_baseline_demographics %>%
-  mutate(no_sites = as.numeric(no_sites)) %>% 
-  mutate(sites = coalesce(no_sites, number_of_sites)) %>%
-  select(-no_sites, -number_of_sites)
-
-# we have a few rogue studies (Kitchen, McCarty and Wright). Kitchen was too recent (after 2021), McCarty and Wright are not in Cuijpers' master
-# dataset for some reason, though they are in the list of included studies in the table in his MA. For now I'm going to remove them because 
-# we don't have data for these trials.
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  filter(!(new_study_id %in% c("Kitchen, 2021", "McCarty, 2013", "Wright, 2020")))
-
-# Now create binary variable, single or multi site trial
-
-df_baseline_demographics <- df_baseline_demographics %>% 
-  mutate(site_binary = case_when(sites == 1 ~ "single", 
-                                 sites > 1 ~ "multi",
-                                 TRUE ~ NA_character_))
-
-df_binary_site_count <- df_baseline_demographics %>% 
-  group_by(psy_or_med, site_binary) %>% 
-  summarize(num_trials = n())
-
-# Lets look at results
-
-# summary stats
-df_sites_summary_stats <- df_baseline_demographics %>%
-  group_by(psy_or_med) %>%
-  summarise(
-    n = n(),
-    mean_sites = mean(sites, na.rm = TRUE),
-    sd_sites = sd(sites, na.rm = TRUE),
-  )
-
-# Tabulate
-# Rounding
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-# Row names
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  mutate(psy_or_med = case_when(
-    psy_or_med == 0 ~ "Medication",
-    psy_or_med == 1 ~ "Psychotherapy",
-    TRUE ~ as.character(psy_or_med)  # Keep other values unchanged
-  ))
-
-df_sites_summary_stats <- df_sites_summary_stats %>%
-  rename(
-    Modality = psy_or_med,
-    K = n,
-    Mean = mean_sites,
-    SD = sd_sites
-  )
-
-# t-test
-sites_t_test <- t.test(sites ~ psy_or_med, data = df_baseline_demographics)
-
-sites_t_test_stats <- data.frame(
-  statistic = sites_t_test$statistic,
-  df = sites_t_test$parameter,
-  p_value = sites_t_test$p.value,
-  ci_lower = sites_t_test$conf.int[1],
-  ci_upper = sites_t_test$conf.int[2]
-)
-
-sites_t_test_stats <- sites_t_test_stats %>%
-  mutate(across(.cols = c(statistic, df, ci_lower, ci_upper), ~ round(., 2))) %>% 
-  mutate(p_value = ifelse(p_value < 0.001, "< 0.001", as.character(round(p_value, 3))))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-## | label: tbl-sites-summary
-## | tbl-cap: "Number of sites across medication and psychotherapy studies"
-## | tbl-cap-location: top
-#
-# flextable(df_sites_summary_stats) %>%
-#   set_table_properties(width = 1, layout = "fixed") %>%
-#   add_footer_row(values = as_paragraph(as_i("t"), "(", sites_t_test_stats$df, ") = ", sites_t_test_stats$statistic,
-#                       "; ", as_i("p "), sites_t_test_stats$p_value, 
-#                       "; 95% CI: ", sites_t_test_stats$ci_lower,
-#                       "-", sites_t_test_stats$ci_upper, "."), colwidths = 4) %>% 
-#   # add_header_row(values = "Number of sites across medication and psychotherapy studies", colwidths = 4) %>%
-#   # add_header_row(values = "Table 2", colwidths = 4) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   # italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   # padding(i = 2, padding.bottom = 15, part = "header") %>%
-#   padding(i = c(1, 2), j = 1, padding.left = 10) %>% 
-#   align(j = 2:ncol(df_sites_summary_stats), align = "center", part = "all") %>% 
-#   align(j = 1, align = "left", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>% 
-#   autofit() %>% 
-#   paginate(init = TRUE, hdr_ftr = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 25 of 46 (54%) psychotherapy studies.
-
-## Comparing the nature and intensity of control conditions in psychotherapy trials
-
-```{r nature-intensity-comparison, warning=FALSE, message = FALSE, echo=FALSE}
-# We need to read in the appropriate dataset which describes the active and control conditions used in
-# psychotherapy trials.
-
-df_descr_psy_conditions <- readxl:: read_excel(here("for_despina_and_giannis_200224.xlsx"))
-
-# checking id matchup
-# discrepancies <- setdiff(df_descr_psy_conditions$new_study_id, df_long_for_metan$new_study_id)
-
-# Cleaning the dataset
-# For now lets look at variables pertaining to the nature / intensity of interventions
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  select(c(new_study_id, `Psychotherapy/control`, levels_var, number_of_sites, Number_of_sessions,
-           frequency_weeks, Length_of_sessions_mins, Total_hours_of_intervention_hours, total_hours_gsh,
-           Total_period_of_intervention_weeks, Format_group_individual, Delivery, Involvement_of_others))
-
-# rename for clarity and to match master dataframe
-df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  rename(treatment = 'Psychotherapy/control', no_sites = number_of_sites, no_sessions =
-           Number_of_sessions, freq_weeks = frequency_weeks, length_sessions_mins =
-           Length_of_sessions_mins, total_hours = Total_hours_of_intervention_hours,
-         total_period_weeks = Total_period_of_intervention_weeks, format = Format_group_individual, delivery =
-           Delivery, family_involv = Involvement_of_others)
-
-check <- df_descr_psy_conditions %>% 
-  filter(treatment == 'wlc')
-
-# Visual inspection
-
-# There are two studies where the waitlist condition has some intervention (i.e. values should not be set to 0)
-# Otherwise, I want values to be set to 0, not NA.
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate(
-    no_sessions = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, no_sessions),
-    freq_weeks = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, freq_weeks),
-    length_sessions_mins = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, length_sessions_mins),
-    total_hours = ifelse(treatment == "wlc" & !(new_study_id %in% c("Ackerson, 1998", "Diamond, 2002")), 0, total_hours)
-  )
-
-# Now cau
-
-check <- df_descr_psy_conditions %>% 
-  filter(treatment == 'cau')
-
-# All studies except for Martinovic, Srivastava, Stikkelbroek and Weisz 2009 should have variables set to NA. 
-# This is because we cannot say that they did not feature 0 hours of intervention, but that for the most part
-# it is not reported or it is not possible to quantify.
-
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate(
-    no_sessions = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, no_sessions),
-    freq_weeks = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, freq_weeks),
-    length_sessions_mins = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, length_sessions_mins),
-    total_hours = ifelse(treatment == "cau" & !(new_study_id %in% c("Martinovic, 2006", "Srivastava, 2020", "Stikkelbroek, 2020", "Weisz, 2009")), NA, total_hours)
-  )
-
-# Now other controls
-
-check <- df_descr_psy_conditions %>%
-  filter(!(treatment %in% c('cau', 'wlc'))) %>% 
-  filter(levels_var == "psychotherapy_control")
-
-# Made a few manual adjustments in the original excel sheet.
-
-# List of columns to clean
-columns_to_clean <- c(
-  "no_sessions",
-  "freq_weeks",
-  "length_sessions_mins",
-  "total_hours",
-  "total_period_weeks"
-)
-
-# Convert non-numeric values to NA in specified columns
-df_descr_psy_conditions <- df_descr_psy_conditions %>%
-  mutate_at(vars(columns_to_clean), ~as.numeric(as.character(.)))
-
-# Giannis' function for summary stats
-
-group_function <- function(dataframe, my_groups, columns) {
-  result_dataframe <- data.frame(
-    Group = character(),
-    Column = character(),
-    K = numeric(),
-    Mean = numeric(),
-    SD = numeric(),
-    Median = numeric(),
-    IQR = numeric(),
-    stringsAsFactors = FALSE
-  )
-  unique_groups <- unique(dataframe[[my_groups]])
-  for (group in unique_groups) {
-    group_data <- dataframe[dataframe[[my_groups]] == group, ]
-    for (col in columns) {
-      col_data <- group_data[[col]]
-      n <- sum(!is.na(col_data))
-      mean_val <- mean(col_data, na.rm = TRUE)
-      SD <- sd(col_data, na.rm = TRUE)
-      median_val <- median(col_data, na.rm = TRUE)
-      iqr <- IQR(col_data, na.rm = TRUE)
-      result_dataframe <- rbind(result_dataframe,
-                                data.frame(Column = col, Group = group, K = n, Mean = mean_val,
-                                           SD = SD, Median = median_val,
-                                           IQR = iqr, stringsAsFactors = FALSE))
-    }
-  }
-  return(result_dataframe)
-}
-
-# Filter out wl conditions
-# df_descr_psy_conditions <- df_descr_psy_conditions %>% 
-  # filter(new_study_id %in% no_wl_ids)
-
-# count_wl <- df_long_for_metan %>% 
-#   filter(treatment == "wlc") %>% 
-#   distinct(new_study_id) %>% 
-#   nrow()
-# 
-# count_cau <- df_long_for_metan %>% 
-#   filter(treatment == "cau") %>% 
-#   distinct(new_study_id) %>% 
-#   nrow()
-
-sessions <- group_function(df_descr_psy_conditions,"levels_var","no_sessions")
-frequency <- group_function(df_descr_psy_conditions,"levels_var","freq_weeks")
-length_sessions_mins <- group_function(df_descr_psy_conditions,"levels_var","length_sessions_mins")
-total_hours <- group_function(df_descr_psy_conditions,"levels_var","total_hours")
-total_period_weeks <- group_function(df_descr_psy_conditions,"levels_var","total_period_weeks")
-
-control_summary <- rbind(sessions, frequency, length_sessions_mins, total_hours)
-
-control_summary <- control_summary %>% 
-  select(-c(Median, IQR))
-
-control_summary <- control_summary %>%
-  mutate(Group = case_when(
-    Group == "psychotherapy_active" ~ "Active",
-    Group == "psychotherapy_control" ~ "Control",
-    TRUE ~ as.character(Group)  # Keep other values unchanged
-  ))
-
-control_summary <- control_summary %>%
-  mutate(Column = case_when(
-    Column == "no_sessions" ~ "Number of sessions",
-    Column == "freq_weeks" ~ "Intensity (sessions per week)",
-    Column == "length_sessions_mins" ~ "Session length (mins)",
-    Column == "total_hours" ~ "Total intervention hours",
-    TRUE ~ as.character(Column)  # Keep original value if no match
-  ))
-
-# other_ctr_ids <- df_long_for_metan[df_long_for_metan$type == "other ctr",]$new_study_id
-# testing <- df_descr_psy_conditions %>% 
-#   filter(new_study_id %in% other_ctr_ids)
-# view(testing)
-
-# t tests
-
-session_no_t_test <- t.test(no_sessions ~ levels_var, data = df_descr_psy_conditions)
-freq_t_test <- t.test(freq_weeks ~ levels_var, data = df_descr_psy_conditions)
-session_length_t_test <- t.test(length_sessions_mins ~ levels_var, data = df_descr_psy_conditions)
-total_hours_t_test <- t.test(total_hours ~ levels_var, data = df_descr_psy_conditions)
-
-extract_t_test_stats <- function(df) {
-
-  t_test_stats <- data.frame(
-  outcome = df$data.name,
-  statistic = df$statistic,
-  df = df$parameter,
-  p_value = df$p.value,
-  ci_lower = df$conf.int[1],
-  ci_upper = df$conf.int[2])
-
-  return(t_test_stats)
-
-}
-
-results_session_no_t_test <- extract_t_test_stats(session_no_t_test)
-results_freq_t_test <- extract_t_test_stats(freq_t_test)
-results_session_length_t_test <- extract_t_test_stats(session_length_t_test)
-results_total_hours_t_test <- extract_t_test_stats(total_hours_t_test)
-
-# for t test table
-
-control_summary_t_tests <- rbind(results_session_no_t_test, results_freq_t_test, results_session_length_t_test, results_total_hours_t_test)
-
-# For row names
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(outcome = case_when(
-    row_number() == 1 ~ "Number of sessions",
-    row_number() == 2 ~ "Intensity (sessions per week)",
-    row_number() == 3 ~ "Session length (mins)",
-    row_number() == 4 ~ "Total intervention hours"
-  ))
-
-# Define new column names
-new_column_names <- c("Outcome", "t statistic", "df", "p-value", "Lower CI", "Upper CI")
-
-# Assign new column names to the data frame
-colnames(control_summary_t_tests) <- new_column_names
-
-#Rounding
-control_summary_t_tests <- control_summary_t_tests %>%
-  mutate(across(where(is.numeric) & !matches("p-value"), ~ round(., 2))) %>%
-  mutate(`p-value` = ifelse(`p-value` < 0.001, "< 0.001", sprintf("%.3f", `p-value`)))
-
-# function for between group effect sizes (cohens d)
-# 
-# effect_btwn <- function(df) {
-#   pooled_sd <- sqrt(((df$N[1]-1)*df$SD[1]^2 + (df$N[2]-1)*df$SD[2]^2) / (df$N[1] + df$N[2] - 2))
-#   mean_diff <- df$Mean[1] - df$Mean[2]
-#   effect_btwn <- mean_diff / pooled_sd
-#   return(effect_btwn)
-# }
-# 
-# session_es <- effect_btwn(sessions)
-# frequency_es <- effect_btwn(frequency)
-# length_sessions_mins_es <- effect_btwn(length_sessions_mins)
-# total_hours_es <- effect_btwn(total_hours)
-# total_period_weeks_es <- effect_btwn(total_period_weeks)
-
-# using a package to calculate instead
-
-session_es <- cohen.d(df_descr_psy_conditions$no_sessions ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-frequency_es <- cohen.d(df_descr_psy_conditions$freq_weeks ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-length_sessions_mins_es <- cohen.d(df_descr_psy_conditions$length_sessions_mins ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-total_hours_es <- cohen.d(df_descr_psy_conditions$total_hours ~ df_descr_psy_conditions$levels_var, pooled = TRUE, paired = FALSE, within=FALSE, na.rm=FALSE )
-
-# going to try displaying summary statistics and t-tests in one place
-
-control_summary <- cbind(control_summary, 
-                          "Cohen's d" = rep(NA, nrow(control_summary)),
-                         "Upper CI" = rep(NA, nrow(control_summary)),
-                         "Lower CI" = rep(NA, nrow(control_summary)),
-                         t = rep(NA, nrow(control_summary)), 
-                          df = rep(NA, nrow(control_summary)), 
-                          "p-value" = rep(NA, nrow(control_summary)))
-
-# Update the first row with session_es
-control_summary[1, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  session_es$estimate, session_es$conf.int[1], session_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[1], control_summary_t_tests$df[1], 
-  control_summary_t_tests$`p-value`[1]
-)
-
-# Update the third row with frequency_es
-control_summary[3, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  frequency_es$estimate, frequency_es$conf.int[1], frequency_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[2], control_summary_t_tests$df[2], 
-  control_summary_t_tests$`p-value`[2]
-)
-
-# Update the fifth row with length_sessions_mins_es
-control_summary[5, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  length_sessions_mins_es$estimate, length_sessions_mins_es$conf.int[1], length_sessions_mins_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[3], control_summary_t_tests$df[3], 
-  control_summary_t_tests$`p-value`[3]
-)
-
-# Update the seventh row with total_hours_es
-control_summary[7, c("Cohen's d", "Upper CI", "Lower CI", "t", "df", "p-value")] <- c(
-  total_hours_es$estimate, total_hours_es$conf.int[1], total_hours_es$conf.int[2], 
-  control_summary_t_tests$`t statistic`[4], control_summary_t_tests$df[4], 
-  control_summary_t_tests$`p-value`[4]
-)
-
-control_summary <- control_summary %>%
-  mutate(
-    `Cohen's d` = as.numeric(`Cohen's d`),
-    `Upper CI` = as.numeric(`Upper CI`),
-    `Lower CI` = as.numeric(`Lower CI`)
-  ) %>%
-  mutate(across(where(is.numeric), ~round(., 2)))
-
-# # plot
-# 
-# ggplot(df_descr_psy_conditions_no_wl, aes(x = total_hours, fill = levels_var)) +
-#   geom_histogram(position = "identity", alpha = 0.5, binwidth = 5, color = "black") +
-#   facet_wrap(~ levels_var, ncol = 2) +
-#   theme_minimal() +
-#   labs(title = "Histograms of Number of Total Hours by Group",
-#        x = "Number of Hours",
-#        y = "Frequency") +
-#   scale_fill_manual(values = c("lightpink", "lightblue"))
-
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-#| label: tbl-intensity-of-int
-#| tbl-cap: "Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-#| tbl-cap-location: top
-
-as_grouped_data(control_summary, groups = "Column") %>% 
-  as_flextable(hide_grouplabel = TRUE ) %>% 
-  bold(i = c(1, 4, 7, 10), bold = TRUE, part = "body") %>%  
-  set_table_properties(width = 1) %>%  # Set table width 
-  autofit() %>%  # Autofit column widths 
-  align(j = 2:9, align = "center", part = "all") %>% 
-  # add_header_row(values = "Comparing the intensity of the intervention between active and control arms of psychotherapy studies", colwidths = 4) %>% # This is a work around for the problems with rendering captions
-  # add_header_row(values = "Table 5", colwidths = 4) %>% 
-  bold(part = "header") %>%   # Bold the relevant header rows
-  bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-  #italic(i = 2, italic = TRUE, part = "header") %>% 
-  add_footer_row(values = as_paragraph("Abbreviations: K = number of studies, SD = standard deviation, CI = 95% confidence interval, df = degrees of freedom."), colwidths = 10) %>%
-  font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-  border_remove() %>% # this is to remove borders around the caption that look strange
-  hline(j = 1:4, part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-  vline(j = c(1,4), part = "body", border = small_border) %>% 
-  border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-  hline(part = "header", border = big_border) %>% 
-  #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  paginate(init = TRUE) %>% 
-  line_spacing(space = .7, part = "all") 
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE, ft.align="left"}
-# #| label: tbl-t-tests-intensity
-# #| tbl-cap: "Results for t-tests Comparing the intensity of the intervention between active and control arms of psychotherapy studies"
-# #| tbl-cap-location: top
-# 
-# flextable(control_summary_t_tests) %>%
-#   set_table_properties(width = 1) %>%  # Set table width %>% 
-#   autofit() %>%  # Autofit column widths 
-#   align(j = 2:ncol(control_summary_t_tests), align = "center", part = "all") %>% 
-#   font(fontname = "Calibri", part = "all") %>%   # Set font to Calibri
-#   #add_header_row(values = "Results for t-tests comparing intervention intensity between active and control arms of psychotherapy trials", colwidths = 6) %>% # This is a work around for the problems with rendering captions
-#   #add_header_row(values = "Table 6", colwidths = 6) %>% 
-#   bold(part = "header") %>%   # Bold the relevant header rows
-#   bg(bg = "#F2F2F2", part = "header") %>%   # Add light grey background to header row %>% 
-#   #italic(i = 2, italic = TRUE, part = "header") %>% 
-#   border_remove() %>% # this is to remove borders around the caption that look strange
-#   hline(part = "body", border = small_border) %>%  # Add light grey horizontal lines all  rows
-#   vline(j = 1, part = "body", border = small_border) %>% 
-#   border_outer(border = small_border, part = "body" ) %>%  # Add outer borders
-#   hline(part = "header", border = big_border) %>% 
-#   #padding(i = 2, padding.bottom = 15, part = "header") %>% 
-#   paginate(init = TRUE) %>% 
-#   line_spacing(space = .7, part = "all")
-
-```
-
-As seen in @tbl-intensity-of-int, active conditions featured significantly more sessions when compared to control conditions.
-Sessions in active conditions were longer and more frequent, resulting in significantly more intervention hours overall.
-Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data.
-We performed a sensitivity analysis where we excluded trials using waitlist controls; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
-
-# Conclusions and Clinical Implications
-
-```{r proportion-wl, echo=FALSE}
-# Filter the dataframe
-# filtered_df <- df_long_for_metan %>%
-#   filter(psy_or_med == 1, arm_effect_size == "cohens_d_control")
-# 
-# # Count the occurrences of each type
-# type_counts <- filtered_df %>%
-#   count(type) %>%
-#   mutate(total_count = sum(n),
-#          wl_sum = sum(n[type == "wl"]),
-#          wl_percentage = wl_sum / total_count * 100)
-# 
-# # how many examples of matching of active and control in number of hours
-# 
-# instances_count <- df_descr_psy_conditions_no_wl %>%
-#   filter(!is.na(total_hours)) %>%
-#   group_by(new_study_id, total_hours) %>%
-#   summarise(count = n()) %>%
-#   filter(count > 1) %>%
-#   summarise(total_instances = n())
-
-```
-
-This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence, by looking at two key conditions for comparability.
-First, whether the participants of trials in one modality are comparable to those in another modality.
-Second, whether conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
-
-Starting with the first question, we found that participants in medication trials are comparable on age but are more likely to be male and have more severe depression compared to those in psychotherapy trials.
-This indicates that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability.
-
-Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressants [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
-Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however these are within people who have chosen to be in the particular trial and modality.
-Moreover, severity may represent different subtypes in terms of course of depression and real-life outcomes [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
-
-We then turned to our second question about whether trial design conditions are comparable between modalities.
-We found that medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
-Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy [@dechartresSingleCenterTrialsShow2011]; [@meisterPlaceboResponseRates2020].
-Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
-
-Second, psychotherapy controls have moderate effect sizes (-0.5) whereas medication controls have very large effect sizes (-1.9).
-Our analysis could be critiqued as it compares within arm symptom change per trial, therefore effectively breaking randomisation.
-This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving randomisation to balance confounders is critical.
-More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
-This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
-
-We note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
-Indeed, in Zhou et al.
-[@zhouComparativeEfficacyAcceptability2020] the estimates for psychotherapy controls, TAU and waitlist conditions favoured placebo (though CIs were broad because these were indirectly estimated), as did estimates for psychodynamic and behavioural therapy.
-CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial [@marchFluoxetineCognitiveBehavioralTherapy2004].
-We note that the Zhou metanalysis, which represents an admirable effort to synthesise the literature, reports on issues that may affect transitivity with tests of incoherence showing significant differences.
-
-Moving beyond comparison between modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving treatment.
-An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind) yet psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption.
-In order to test that a psychological treatment is effective per se (e.g.
-because of the specific techniques) rather than because of generic effects (e.g.
-pleasant human contact), aspects such as therapist contact time should be matched.
-Many (24%) psychotherapy RCTs used waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
-TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
-Importantly, controls were often poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
-Overall, there is poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
-
-Given all of the above, the empirical basis for comparing psychotherapy and medication for adolescent depression is weak, and hence it is difficult to generate guidelines and recommend one treatment over another.
-Indeed, we believe that our findings have several implications for patients, their families, clinicians and policy makers.
-
-First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is a need to revisit guidelines and public information in light of the limitations.
-
-Second, the low quality of psychotherapy control conditions should prompt consideration of how to create fair comparators.
-Investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of RCTs where such rigor has been applied (e.g.
-Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
-Moreover, there is a place for comparing interventions to TAU, since these represent real-world comparators.
-However issues of disappointment bias should be addressed to avoid inflating treatment estimates.
-
-Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-The first obstacle is the comparability of the populations taking part.
-Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive [@kingImpactParticipantPhysician2005].
-And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
-
-In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression.
-Our data question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, need better evidence on which to base their choices.
+```
+
+```{r global_options, include=FALSE}
+
+knitr::opts_chunk$set(tab.cap.fp_text = officer::fp_text_lite(italic = FALSE, bold = TRUE))
+```
 
@@
 
-#add i2 to aggregate results
-aggregate_results_overall_i2 <- cbind(aggregate_results_overall, 
-                                   i2_2 = rep(i2_summary_all$mean_i2_level2, nrow(aggregate_results_overall)),
-                                   i2_3 = rep(i2_summary_all$mean_i2_level3, nrow(aggregate_results_overall)))
-
 # Regression results
 
-aggregate_results_overall_i2 <- aggregate_results_overall_i2 %>%
+aggregate_results_overall <- aggregate_results_overall %>%
   mutate(across(where(is.numeric), ~round(., 2))) %>%
@@
 
-new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2_1", "T2_2", "QE", "k", "I2_2", "I2_3")
+new_column_names <- c("Condition", "Coefficient", "SE", "z value", "Lower CI", "Upper CI", "T2", "QE", "k")
 
 # Assign new column names to the data frame
-colnames(aggregate_results_overall_i2) <- new_column_names
-
-table_aggregate_results_overall_i2 <- aggregate_results_overall_i2[, 1:6]
-table_aggregate_results_overall_i2[1, 4] <- NA
-
-flextable(table_aggregate_results_overall_i2) %>%
+colnames(aggregate_results_overall) <- new_column_names
+
+table_aggregate_results_overall <- aggregate_results_overall[, 1:6]
+table_aggregate_results_overall[1, 4] <- NA
+
+flextable(table_aggregate_results_overall) %>%
   set_table_properties(width = 1) %>%
   autofit() %>%
-  add_footer_row(values = as_paragraph("T", as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "T2_1"], ";", as_i("T"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "T2_2"],
-                      "; ", as_i("I"), as_sup("2"), as_sub("L3"), " = ", aggregate_results_overall_i2[1, "I2_3"], 
-                      "; ", as_i("I"), as_sup("2"), as_sub("L2"), " = ", aggregate_results_overall_i2[1, "I2_2"], 
-                      "; ", as_i("K"), " = ", aggregate_results_overall_i2[1, "k"], "."), colwidths = 6) %>%
+  add_footer_row(values = as_paragraph("T", as_sup("2"), " = ", aggregate_results_overall[1, "T2"],
+                      "; ", as_i("I"), as_sup("2"), " = ", aggregate_results_overall[1, "I2"], 
+                      "; ", as_i("K"), " = ", aggregate_results_overall[1, "k"],
+                      "; ", as_i("R"), as_sup("2"), " = ", aggregate_results_overall[1, "R2"], "."), colwidths = 6) %>%
   # add_header_row(values = "Results from metaregression with overall sample", colwidths = 6) %>%
@@
   # padding(i = 2, padding.bottom = 15, part = "header") %>% 
-  align(j = 2:ncol(table_aggregate_results_overall_i2), align = "center", part = "all") %>% 
+  align(j = 2:ncol(table_aggregate_results_overall), align = "center", part = "all") %>% 
   align(j = 1, align = "left", part = "all") %>% 
@@
 
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-mean_diff_min_max_scores <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = mean_dif, x = as.factor(psy_or_med), size = baseline_n)) + 
-  geom_jitter(width = 0.2) + 
-  ggtitle("Post-Pre Differences in Mean Min-Max Scores") + 
-  ylab("Post-Pre Difference") +
-  xlab("Type of Study") +
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) +   theme_minimal()
-
-print(mean_diff_min_max_scores) 
-png("mean_diff_min_max_scores.png")
-mean_diff_min_max_scores
-dev.off()
-```
-
-```{r, warning=FALSE, message = FALSE, echo=FALSE}
-# create baseline variances
-df_long_for_metan$variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-plot_baseline_var <- df_long_for_metan %>% 
-  filter(arm_effect_size == "cohens_d_control") %>% 
-  mutate(mean_dif = perc_post_mean - perc_baseline_mean) %>% 
-  ggplot(aes(y = variances, x = as.factor(psy_or_med), size = baseline_n)) + geom_jitter(width = 0.2) +  
-  ggtitle("Post-Pre Differences in Study Baseline Variances") + 
-  ylab("Baseline Variance") + 
-  xlab("Type of Study") + 
-  scale_x_discrete(labels = c("0" = "Medication", "1" = "Psychological Therapy")) + theme_minimal()
-
-print(plot_baseline_var)
-png("plot_baseline_var.png")
-plot_baseline_var
-dev.off()
-```
-
 ## Metaregression sensitivity analyses
-
-```{r supp-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
-# G. Post SD Sensitivity Analysis ---------------------------------------
-
-##--------- Data preparation
-
-#For this we need to filter the master df by missing post_sd_active and post_sd_control in df_first_row
-
-#create subset of first_row
-
-df_first_row <- read.csv(here("df_first_row.csv"))
-
-#create new_study_ids to match master dataset
-df_first_row  <- df_first_row  %>%
-  mutate(new_study_id = case_when(psy_or_med == 0 ~ paste(study,year, sep = ", "),
-                                  .default = study ))
-
-df_first_row_reduced <- df_first_row %>%
-  filter(!(new_study_id == "March, 2004" & is.na(control_type))) %>%
-  select(new_study_id, post_sd_active, post_sd_control)
-
-#as first_row has multiple rows per study (showing different arm pairs), I will keep only one row per study
-
-df_first_row_reduced <- df_first_row_reduced %>%
-  group_by(new_study_id) %>%
-  slice_head(n = 1) %>%
-  ungroup()
-
-#create a column in master df that shows 1 if any missing post sds in first_row
-
-df_long_for_metan_with_missing <- df_long_for_metan %>%
-  left_join(df_first_row_reduced, by = "new_study_id") %>%
-  mutate(missing_post_sd = ifelse(is.na(post_sd_active) | is.na(post_sd_control), 1, 0)) %>%
-  select(-post_sd_active, -post_sd_control) %>%
-  arrange(arm_effect_size, new_study_id)
-
-#all studies missing sds in active are also missing them in control, so we can go ahead and filter out all arms of these studies
-
-df_long_for_metan_without_missing <- df_long_for_metan_with_missing %>%
-  filter(missing_post_sd == 0)
-
-n_distinct(df_long_for_metan_without_missing$new_study_id) #61 studies
-n_distinct(df_long_for_metan$new_study_id) #88 studies total
-nrow(df_long_for_metan_without_missing) #140 arms
-nrow(df_long_for_metan) #203 arms
-
-##------------ Estimates
-
-#take study ids where study does not have missing post SD
-sd_study_ids <-
-  df_long_for_metan_with_missing[df_long_for_metan_with_missing$missing_post_sd ==0,]$new_study_id
-
-# use those ids to subset all dataframes in the list
-list_sd_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_sd_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                                 %in% sd_study_ids,]
-}
-
-# count the number of studies
-study_count_sd_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% sd_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_sd_study <- run_multi_metaregression(list_sd_study , model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_sd_study <-  aggregate_model_results(list_model_1_sd_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_sd_study <-  lapply(list_model_1_sd_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_sd_study <- calculate_mean_coefs_ses(means_sd_study, condition)
-coef_and_se_means_sd_study <- data.frame(cbind(condition, coef_and_se_means_sd_study))
-
-# add the ns to the dataframe
-coef_and_se_means_sd_study <- left_join(coef_and_se_means_sd_study, study_count_sd_study[study_count_sd_study$is_missing == FALSE, ] %>%
-                                            ungroup() %>%
-                                            select(condition, n),
-                                          by = "condition")
-
-#H. Studies with variances <.02-----------------------------
-
-##-----------Data preparation
-
-#create column with variance in master df
-df_long_for_metan$baseline_variances <- (df_long_for_metan$perc_baseline_sd)^2
-
-#take study ids where variance =2 or less
-var2_study_ids <-
-  df_long_for_metan[df_long_for_metan$baseline_variances<=0.02,]$new_study_id
-length(var2_study_ids)
-
-##------------Estimates
-
-# use those ids to subset all dataframes in the list
-list_var2_study <- list()
-
-for(i in 1: length(list_df_simulated)){
-
-  list_var2_study[[i]] <- list_df_simulated[[i]][list_df_simulated[[i]]$new_study_id
-                                               %in% var2_study_ids,]
-}
-
-# count the number of studies
-study_count_var2_study <- count_studies(df_long_for_metan[df_long_for_metan$new_study_id %in% var2_study_ids,])
-
-# apply the metareg function to the list of clinical studies
-model_1 <- as.formula(~ four_level_var)
-list_model_1_var2_study <- run_multi_metaregression(list_var2_study, model_1)
-
-# extract coefficients and model characteristics.
-condition <- levels(list_df_simulated[[1]]$four_level_var)
-aggregate_results_var2_study <-  aggregate_model_results(list_model_1_var2_study, condition)
-
-# extract SMDs from the list for clinical studies
-means_var2_study <-  lapply(list_model_1_var2_study, extract_coefficients_func)
-
-# calculate mean SMDs and ses
-condition <- levels(list_df_simulated[[1]]$four_level_var) # for the conditino argument
-coef_and_se_means_var2_study <- calculate_mean_coefs_ses(means_var2_study, condition)
-coef_and_se_means_var2_study <- data.frame(cbind(condition, coef_and_se_means_var2_study))
-
-# add the ns to the dataframe
-coef_and_se_means_var2_study <- left_join(coef_and_se_means_var2_study, study_count_var2_study[study_count_var2_study$is_missing == FALSE, ] %>%
-                                          ungroup() %>%
-                                          select(condition, n),
-                                        by = "condition")
-```
 
@@
 
-# References
+## References

### 2024-10-04 multilevel_metaregression/extra_material_from_render_test.R

@@ -1,0 +1,2933 @@
+# Findings
+
+```{r run-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
+
+# This chunk of code needs to be here because some of the data needed for the included studies summary lives here
+
+# Get Ns, run metareg, prepare graphing ------------------------------------------------------
+
+
+# add a new multilevel variable to the simulated data for the regression
+
+for(i in 1: length(list_df_simulated)){
+  
+list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
+  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
+    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
+                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
+                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
+    )
+  
+  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
+  
+  # relevel so that medication control becomes the reference category for the regression
+#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
+list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
+                                                       "medication_control",
+                                                       "medication_active", 
+                                                       "psychotherapy_control",
+                                                       "psychotherapy_active")
+}
+
+# check it worked
+# list_df_simulated[[2]] %>% 
+# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
+
+######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
+# A) the overall sample
+# B) the CBT vs Fluox and Escitalopram sample
+# C) the no WL sample
+# D) clinical levels of depression
+# E) the CDRS only sample
+# E) HAMD sensitivity analysis
+# G) Studies with post SD
[…]

### 2024-10-04 multilevel_metaregression/multilevel_heterogeneity.R

@@ -1,0 +1,191 @@
+
+###############2. Simulation function for multilevel metaregression
+
+run_multi_metaregression <- function(list_of_datasets, model_formula) {
+  list_model_meta_reg <- list()
+  
+  for (i in seq_along(list_of_datasets)) {
+    # Check if required columns are present
+    if(!all(c("cohens_d", "simulated_se", "new_study_id", "arm_id") %in% names(list_of_datasets[[i]]))) {
+      stop("Dataset is missing one or more required columns: 'cohens_d', 'simulated_se', 'new_study_id', 'arm_id'")
+    }
+    
+    # Fit the meta-regression model
+    list_model_meta_reg[[i]] <- metafor::rma.mv(yi = cohens_d,
+                                                V = simulated_se^2,
+                                                random = ~ 1 | new_study_id/arm_id,
+                                                # this is where 
+                                                # we specify the random
+                                                # effect structure
+                                                data = list_of_datasets[[i]],
+                                                method = "ML",
+                                                mods = model_formula,
+                                                # here we specify the 
+                                                # fixed effects as before
+                                                test = "knha")
+  }
+  
+  return(list_model_meta_reg)
+}
+
+
+##########4. Function to extract mean coefficients and to extract model characteristics
+
+aggregate_model_results <- function(list_model_1_meta_reg, condition) {
+  n_models <- length(list_model_1_meta_reg)
+  n_conditions <- length(condition)
+  
+  df_coefs <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_se <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_z_value <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_lower_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  df_upper_ci <- matrix(NA, nrow = n_models, ncol = n_conditions)
+  tau_sq <- rep(NA, n_models)
+  qe <- rep(NA, n_models)
+  k <- rep(NA, n_models)
+  
+  for (i in seq_len(n_models)) {
+    model <- list_model_1_meta_reg[[i]]
+    tau_sq[i] <- model$tau2
+    qe[i] <- model$QE
[…]

### 2024-10-04 simulated_coefficients_histograms.R

@@ -1,0 +1,41 @@
+#Looking at mean SMD across simulations for psy vs med and control vs active
+library(ggplot2)
+library(ggforce)
+
+list_model_1_meta_reg #contains metaregression results for each of the 1000 simulations
+
+coefs_test <- do.call(rbind, lapply(list_dummy_var_means, function(sim) sim$coefficients))
+df_coefs_test <- data.frame(coefs_test)
+
+col_names <- c("Medication_Control", "Medication_Active", "Psychotherapy_Control", "Psychotherapy_Active")
+colnames(df_coefs_test) <- col_names
+
+df_coefs_long <- gather(df_coefs_test, key = "condition", value = "coefs", Medication_Control:Psychotherapy_Active)
+
+#creating separate histograms
+
+coefs_hist <- ggplot(df_coefs_long, aes(x = coefs)) +
+  geom_histogram(binwidth = 0.001, color = "black", fill = "lightblue") +
+  facet_wrap(~ condition, scales = "free_x") +
+  theme_minimal() +
+  labs(title = "Distribution of Coefficients by Condition",
+       x = "Coefficient",
+       y = "Frequency") +
+  theme(panel.spacing.x = unit(3, "lines"))
+
+ggsave("simulated_coefficients_by_condition_hist.jpeg", coefs_hist)
+
+#creating one graph with a common x axis
+
+coefs_one_graph <- ggplot(df_coefs_long, aes(x = coefs, fill = condition)) +
+  geom_histogram(binwidth = 0.001, color = "black", position = "identity", alpha = 0.5) +
+  theme_minimal() +
+  labs(title = "Distribution of Coefficients by Condition",
+       x = "Coefficient",
+       y = "Frequency") +
+  scale_fill_manual(values = c("Medication_Control" = "blue", 
+                               "Medication_Active" = "red", 
+                               "Psychotherapy_Control" = "green", 
+                               "Psychotherapy_Active" = "purple")) +
+  theme(legend.title = element_blank(),
+        legend.position = "right")

### 2024-10-04 manuscript_with_multilevel_metan.qmd
more cleaning and updated main qmd to match revision

--- 2024-09-23 multilevel_metaregression/manuscript_with_multilevel_metan.qmd
@@
   docx:
-    reference-doc: "bibliography/word-style-reference-doc.docx"
+    reference-doc: "Render_files/custom-reference-doc.docx"
     fig-width: 9
@@
   warning: FALSE
-bibliography: "bibliography/references.bib"
-csl: "bibliography/vancouver_style.csl"
+bibliography: "Render_files/References/emotion_concepts_paper.bib"
+csl: "Render_files/References/vancouver.csl"
 font:
@@
 
-###########Libraries needed
+########### Packages needed
 library(tidyverse)
@@
 
-# For referencing
-bib_data <- ReadBib(here("multilevel_metaregression", "bibliography", "references.bib"))
-
 ```
@@
 In this paper, we test whether the basic conditions required to draw valid inferences to answer this question are currently met.
-**Methods:** We included 88 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+
+**Methods:** We included 92 RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
 Using meta-analyses, we compared a) participant characteristics and b) trial characteristics in medication and psychotherapy trials.
 Lastly, we examined whether psychotherapy controls are well-matched to active conditions.
+
 **Results:** Participants in medication RCTs had higher depression severity and were more frequently male compared to psychotherapy RCTs.
-There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.70)) vs psychotherapy controls (SMD=-0.5 (95% CI: -0.75 to -0.25)).
+There was a dramatic difference in the within-subject improvement due to placebo (SMD=-1.9 (95% CI: -2.10 to -1.7)) vs psychotherapy controls (SMD=-0.6 (95% CI: -0.86 to -0.32)).
 Within psychotherapy RCTs, control conditions were less intensive on average than active conditions.
+
 **Conclusions:** Medication and psychotherapy RCTs differ on fundamental participant and methodological characteristics, thereby violating key conditions for valid comparison between them.
@@
 
+**What is already known on this topic**
+
 Psychotherapy is recommended before medication for most cases of depression in children and adolescents, a recommendation that is based on indirect comparisons of outcomes from randomised controlled trials (RCTs) within each treatment modality.
+
+**What this study adds**
+
 We examine the validity of these inferences by scrutinising the comparability of psychotherapy and medication RCTs.
-We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the within-group effect sizes of medication controls (i.e.
-pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
+
+We find significant differences in sample characteristics (namely depression severity and sex composition) and trial design features, such that the within-group effect sizes of medication controls (i.e. pill placebo) are much larger than those for psychotherapy controls, and that medication RCTs feature significantly more trial sites.
+
 We also examine the quality of controls used in psychotherapy RCTs and find that they are poorly matched to active intervention arms in ways such as human contact hours, and hence represent poor and easy to beat comparators.
+
+**How this study might affect research, practice or policy**
+
 Our findings underscore the need for a higher quality evidence base upon which to base treatment guidelines and clinical decision making.
@@
 For adolescent depression, there are limited head-to-head trials of medication and psychotherapy, and hence recommendations are derived from indirect comparisons of treatment efficacy.
-The National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend psychotherapy (specifically cognitive behaviour therapy (CBT) or interpersonal therapy (IPT)) over medication in most cases [@niceDepressionChildrenYoung2019].
-This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@ciprianiComparativeEfficacyTolerability2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious [@cuijpersEffectsPsychologicalTreatments2021].
-However, a recent network meta-analysis (NMA) [@zhouComparativeEfficacyAcceptability2020], an established method of comparing treatments using both direct and indirect (i.e.
-treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication control (i.e.
-pill placebo) or psychotherapy controls.
-The only head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not [@marchFluoxetineCognitiveBehavioralTherapy2004].
-Also, the addition of psychotherapy to standard care did not improve outcomes [@goodyer_randomised_2008].
-Given this confusing evidence base, how should patients, carers, clinicians and policy makers make treatment decisions?
+The National Institute of Health and Care Excellence (NICE) guidelines for adolescent depression recommend psychotherapy over medication in most cases.[@nice_depression_2019] This is in keeping with two sources of evidence relating to child and adolescent depression: meta-analyses of medication randomised controlled trials (RCTs) that cast doubt on the efficacy of antidepressants, with the exception of fluoxetine [@cipriani_comparative_2016]; and meta-analyses of psychotherapy RCTs that conclude psychotherapy to be efficacious.[@cuijpers_effects_2021] However, a recent network meta-analysis (NMA),[@zhou_comparative_2020] an established method of comparing treatments using both direct and indirect (i.e. treatment A with treatment C, via studies that directly compare A with B and B with C) evidence, concluded that only fluoxetine alone and fluoxetine administered together with CBT were significantly more effective than medication- (i.e. pill placebo) or psychotherapy-controls.
+A large head-to-head RCT comparing modalities found that fluoxetine, alone and in combination with CBT, was superior to pill placebo, though CBT alone was not.[@march_fluoxetine_2004] Also, the addition of psychotherapy to standard care did not improve outcomes.[@goodyer_randomised_2008] Given this confusing evidence base, how should we make treatment decisions?
 
@@
 Two points are crucial to indirect comparisons of treatment modalities.
-First, whether the participants in trials are comparable across modalities.
+First, whether the participants in trials are comparable across modalities, or differ in potential effect modifiers.
 Second, whether key conditions of the trial, such as the effects of control conditions or the number of sites involved, are comparable.
 
-Starting with the first point, comparison between different trials assumes that they sample from the same population.
-If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e.
-the requirement that the different sets of randomized trials are similar on average [@chaimaniChapter11Undertaking2023]) are questionable.
-
-The assumption that medication and psychotherapy trials sample from the same population may not be valid as patients and parents often have treatment preferences [@jaycoxAdolescentPrimaryCare2006; @langerParentYouthPreferences2021; @mchughPatientPreferencePsychological2013], meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
+Starting with the first point, comparison between different trials assumes that they sample from populations that are comparable in terms of characteristics that could be effect modifiers.
+If not, the validity of any comparisons, including those conducted through NMA (which rests on the principal of transitivity, i.e. the requirement that the different sets of randomized trials are similar on average)[@chaimani_chapter_2023] are questionable.
+
+The assumption that medication and psychotherapy trials sample from comparable population may not be valid as patients and parents often have treatment preferences,[@jaycox_adolescent_2006; @langer_parent_2021; @mchugh_patient_2013] meaning that there is likely to be a self-selection bias in who participates in psychotherapy and medication trials.
 Moreover, treatment preferences correlate with clinically-relevant participant characteristics, including severity and sex.
-Some of these characteristics, such as severity, may moderate treatment response [@courtneyPredictorsModeratorsMediators2022; @lorenzo-luacesDoubleTroubleSymptom2020] and if they differ across psychotherapy and medication trials they may confound comparisons.
-
-Regarding the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms [@calvoInterventionAdolescentsEarlyOnset2014].
-This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the "cutting edge" treatment, whilst those in the control are dissatisfied for having missed out (i.e.
-"disappointment bias" [@reltonEthicsTrialsCohorts2017].
-By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation [@linAssessmentBlindingRandomized2022], suggesting that expectancy effects are well-matched across conditions.
-Since expectancy is substantially associated with treatment outcomes [@constantinoExpectations2011], if expectancy differs between medication and psychotherapy trials, comparisons between them, including in NMA, become questionable.
+Some of these characteristics, such as severity, may moderate treatment response [@courtney_predictors_2022; @lorenzo-luaces_double_2020] and may confound comparisons.
+
+Regarding the second point, differences in trial design may impact outcomes in a differential way between medication and psychotherapy trials.[@del_giovane_combining_2019] Most obviously, participants in psychotherapy trials are generally unblinded to treatment allocation, with the exception perhaps of trials that compare two equally plausible treatment arms.[@calvo_intervention_2014] This creates differential expectations which may favour the psychotherapy active condition, as participants are content to be receiving the “cutting edge” treatment, whilst those in the control are dissatisfied for having missed out (i.e. “disappointment bias”).[@relton_ethics_2017] By contrast, in new antidepressant trials, patients (and raters) were largely unable to judge treatment allocation,[@lin_assessment_2022] suggesting that expectancy effects are well-matched across conditions.
+Since expectancy is substantially associated with treatment outcomes,[@constantino_expectations_2011] if expectancy differs between medication and psychotherapy trials, comparisons between them, including in NMA, become questionable.
 
 Another difference in design is the number of trial sites.
-The number of sites in medication trials is positively related to the magnitude of placebo response [@bridgePlaceboResponseRandomized2009; @dechartresSingleCenterTrialsShow2011; @meisterPlaceboResponseRates2020].
-This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
+The number of sites in medication trials is positively related to the magnitude of placebo response.[@bridge_placebo_2009, @dechartres_single-center_2011, @meister_placebo_2020] This phenomenon may be due to lower quality of assessments in multi-site trials, with higher rates of classification errors and therefore higher apparent spontaneous remission or regression to the mean.
 
 An inter-related issue concerns the effect of control conditions.
-Often psychotherapy and medication are compared on the basis of their respective effect sizes (i.e.
-differences between the active and control conditions for each modality).
+Often psychotherapy and medication are compared on the basis of their respective effect sizes (i.e. differences between the active and control conditions for each modality).
 For these to be comparable, medication and psychotherapy controls ought to be equal in their effects.
-Otherwise, misleading conclusions could be drawn, e.g.
-two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% versus 60% and another from a difference of 40% versus 0% (i.e.
-from different points of reference).
-
-Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention [@guoChapterCounterfactualFramework2014]: what would have been the outcome had an individual not received the intervention, with all else being equal.
-Pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
-In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g.
-in number of hours of therapist contact).
+Otherwise, misleading conclusions could be drawn, e.g. two effect sizes of 40% would be considered equal, even if one arose from a difference of 100% versus 60% and another from a difference of 40% versus 0% (i.e. from different points of reference).
+
+Additionally, control conditions in RCTs should generate counterfactual conditions to the intervention: what would have been the outcome had an individual not received the intervention, with all else being equal.[@guo_chapter_2014] Pill placebo, where the appearance of the drug is faithfully emulated, is an effort for all else to be equal.
+In psychotherapy trials, control conditions may not be so well matched to the intervention (e.g. in number of contact hours).
 
@@
 
-In this study we examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
-We hypothesise that there are substantial differences between psychotherapy and medication RCTs, making their comparison problematic, which we examine in the following ways.
-First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline depression severity; b) percentage females; and c) mean age.
+We examine RCTs of psychotherapy and medication for child and adolescent depression (mean age 4-18 years).
+We posit there are substantial differences between psychotherapy and medication RCTs, making their comparison problematic and examine the following: First, we conduct meta-analyses to compare sample characteristics of medication and psychotherapy trials including: a) baseline depression severity; b) percentage females; and c) mean age.
 Second, we examine trial characteristics including the efficacy of the control arms, using random-effects meta-regression, and the number of trial sites.
-Third, we examine the quality of psychotherapy control conditions by scrutinising the extent to which they are matched to the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
+Third, we scrutinise the extent to which psychotherapy controls matched the active intervention in ways such as number and frequency of sessions, and hence whether they represent fair pairings from which to draw valid efficacy inferences.
 
@@
 
-The study protocol was registered on the Open Science Framework (OSF) and can be found at <https://osf.io/bfmc6>.
-
 A detailed description of our methods, including formalisms on which analyses are based, can be found in the Supplement.
@@
 
-We included RCTs identified in a recent meta-analysis of psychotherapy versus control [@cuijpersEffectsPsychologicalTreatments2021] and an NMA examining the efficacy of antidepressants [@ciprianiComparativeEfficacyTolerability2016] for depression in children and adolescents.
-For the psychotherapy trials, we utilised open data from the previous meta-analysis (see <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
-For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
-
-For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
+We included RCTs identified in a recent meta-analysis of psychotherapy versus control,[@cuijpers_effects_2021] an NMA examining the efficacy of antidepressants,[@cipriani_comparative_2016] and an NMA comparing both treatment types [@zhou_comparative_2020] for depression in children and adolescents.
+For the psychotherapy trials, we utilised open data from the previous meta-analysis.\[@cuijpers_effects_2021 For medication trials, we were unable to access the full dataset used in the NMA and hence extracted data from the included studies ourselves.
+
+For medication trials, we also conducted a systematic search for studies published after the final search date of Cipriani et al.’s [@cipriani_comparative_2016] review up to the final search date of Cuijpers et al’s [@cuijpers_effects_2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
 Two authors screened 450 titles and abstracts, and 38 full text records.
-Seven studies met inclusion criteria and one author completed data extraction for these papers (see @fig-prisma for PRISMA diagram).
+Seven studies met inclusion criteria and one author completed data extraction for these papers.
 
@@
 We conducted random-effects meta-analyses and tested subgroup differences (psychotherapy vs medication trials) in severity of depressive symptoms, sex and age.
-Meta-analyses were implemented using R's meta package.
+Meta-analyses were implemented using R’s meta package.
 
@@
 
-As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression scale used (selected according to the hierarchy defined in the Supplement).
-
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023].
+As the measure of effect of each individual study, we used the within-group Standardised Mean Difference (SMD) for the primary depression scale used (selected using the hierarchy in the Supplement).
+
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in this Cochrane Handbook.[@higgins_chapter_2023]
 
@@
 This requires a correlation between the pre- and post-measures, a statistic typically not reported.
-To ensure that our results are not biased by misestimation [@cuijpers_pre-post_2017], we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses (please refer to Supplement for full details).
+To ensure that our results are not biased by misestimation,[@cuijpers_pre-post_2017] we simulated n=1000 datasets for different values (0.45 to 0.9) of this correlation and used these datasets in subsequent analyses.
 
@@
 
-We estimated pooled SMDs for each arm by using multilevel models implemented in R's metafor package.
-
-We present the SMDs of each of the four treatment arms (medication control, medication active, psychotherapy control, psychotherapy active) under investigation.
+We estimated the pooled SMD for each arm by using multilevel models implemented in R’s metafor package.
+
+We present the SMDs of each of the four treatment arms (medication-control, medication-active, psychotherapy-control, psychotherapy-active) under investigation.
 The SMDs are the means across the 1000 simulated datasets.
@@
 
-We conducted a series of sensitivity analyses where we excluded studies that 1) used waitlist as their control and 2) recruited participants with subclinical levels of depression.
-Next, we conducted two analyses where we included only trials that used the Children's Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
-Additonally, we restricted two analyses to studies with variance below 0.02 and which reported SD at outcome respectively.
+We conducted a series of sensitivity analyses where we excluded studies that used waitlist as their control and recruited participants with subclinical levels of depression.
+Next, we included only trials that used the Children’s Depression Rating Scale, Revised (CDRS-R) or the Hamilton Depression Rating Scale (HAM-D) as outcome instruments.
+Next, we restricted the analysis to studies with variance below 0.02.
 
@@
 We plotted the z-value of the difference between the two coefficients against the number of simulations.
-We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = `r x` corresponding to an alpha = 0.05.
+We make inference on the stability of the difference, by counting the proportion of times that the z-value is above the critical value of z = 1.645 corresponding to an alpha = 0.05.
 
@@
 
-Data for included studies are summarised in @tbl-all-trials and are also available as a csv dataframe on \[<https://github.com/transatlantic-comppsych/apples_oranges>\].
-Please see @fig-prisma for a summary of the sources of included RCTs.
+Data for included studies are summarised in @tbl-all-trials and available on the project repository (“df_long_for_metan.csv”)[@stringaris_apples_2023].
 
 In total, there were `r length(unique(df_long_for_metan$new_study_id))` RCTs which included `r sum(df_count_studies[df_count_studies$condition == "medication_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "medication_control", "n"])` control arms of medication trials; and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_active", "n"])` active arms and `r sum(df_count_studies[df_count_studies$condition == "psychotherapy_control", "n"])` control arms from psychotherapy RCTs.
-Note that the number of active and control arms does not exactly match because some studies feature more than one control or active arm.
-
-Placebo pill was the control condition for all medication trials.
-In psychotherapy trials, the control arm included 14 waitlist, 25 treatment-as-usual (TAU), and 19 other control conditions (e.g.
-relaxation training, attention control, counselling).
+Note that the number of active and control arms does not match because some studies feature more than one control or active arm.
+
+Placebo pill was the control condition for all medication trials. In psychotherapy trials, the control arm included 14 waitlist, 25 treatment-as-usual (TAU), and 19 other control conditions.
 
@@
 @tbl-baseline-results summarises the results from each of the meta-analyses examining sample characteristics at baseline.
-The summary statistics are provided for each subgroup (i.e.
-medication and psychotherapy) and the p-value derives from the test for subgroup differences.
+The summary statistics are provided for each subgroup and the p-value derives from the test for subgroup differences.
 
@@
 Medication control and psychotherapy control conditions remained significantly different, though the small number of studies resulted in less precise estimates of the SMDs.
-Conversely, restricting the analysis to studies with variance below 0.02 yielded a similar pattern of results, but with increased precision in SMD estimates across conditions (see @fig-plot-means-var2).
+Restricting the analysis to studies with variance below 0.02 yielded a similar pattern of results, but with increased precision in SMD estimates across conditions (see @fig-plot-means-var2).
 Finally, we showed that different values for the pre-post measure correlation had minimal effect on the estimated outcomes (see @fig-stab-sims).
@@
 
-We addressed potential regression to the mean by including the baseline score for each depression scale in the linear regression model as per equation 3 in @barnettRegressionMeanWhat2004 (see @tbl-de-meaned in the Supplement).
+We addressed potential regression to the mean by including the baseline score for each depression scale in the linear regression model as per equation 3 in [@barnett_regression_2004] (see @tbl-de-meaned).
 The difference between the medication control and psychotherapy control arms remained significantly different.
@@
 Average number of trial sites was significantly higher in medication trials (*M* = `r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Medication"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Medication"]`) compared to psychotherapy studies (*M* =`r df_sites_summary_stats$Mean[df_sites_summary_stats$Modality == "Psychotherapy"]`, *SD* =`r df_sites_summary_stats$SD[df_sites_summary_stats$Modality == "Psychotherapy"]`)(*t* (`r round (sites_t_test$parameter, 2)`) = `r round(sites_t_test$statistic,2)`, *p* =`r sites_t_test_stats$p_value`).
-Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 25 of 46 (54%) psychotherapy studies.
+Of those studies with data available, 26 of 28 (93%) medication trials were multisite, compared to 24 of 45 (54%) psychotherapy studies.
 
@@
 Notably, many control conditions were very poorly described and their intensity could not be quantified, resulting in missing data.
-We performed a sensitivity analysis where we excluded trials using waitlist controls; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial, with between-group Cohen's ds ranging from 0.41-0.54 (please see @tbl-intensity-of-int-no-wl in the Supplement).
+We performed a sensitivity analysis where we excluded trials using waitlist controls; with the exception of number of sessions, differences between active and control arms were no longer statistically significant though remained substantial (see @tbl-intensity-of-int-no-wl).
 
@@
 
-This paper sought to address the question of whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence, by looking at two key conditions for comparability.
+We examined whether psychotherapy and medication can be meaningfully compared on the basis of the existing evidence, by looking at two key conditions for comparability.
 First, whether the participants of trials in one modality are comparable to those in another modality.
@@
 
-Starting with the first question, we found that participants in medication trials are comparable on age but are more likely to be male and have more severe depression compared to those in psychotherapy trials.
-This indicates that different people enter medication and psychotherapy trials, thereby violating basic assumptions of comparability.
-
-Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressants [@stoneResponseAcuteMonotherapy2022] or that their response to pill placebo is lower [@bridgePlaceboResponseRandomized2009].
-Other studies argue against severity as a treatment moderator [@trogerBaselineDepressionSeverity2024; @weitzBaselineDepressionSeverity2015], however these are within people who have chosen to be in the particular trial and modality.
-Moreover, severity may represent different subtypes in terms of course of depression and real-life outcomes [@lamersSixyearLongitudinalCourse2016; @simmonds-buckleyDepressionSubtypesTheir2021].
-
-We then turned to our second question about whether trial design conditions are comparable between modalities.
-We found that medication trials are vastly more likely to be multi-site than their psychotherapy counterparts; in the current study, 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
-Multisite trials are associated with higher pill placebo response [@bridgePlaceboResponseRandomized2009], and are less common in publicly-funded trials which show lower pill placebo efficacy [@dechartresSingleCenterTrialsShow2011]; [@meisterPlaceboResponseRates2020].
-Also, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed or modified by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
-
-Second, psychotherapy controls have moderate effect sizes (-0.5) whereas medication controls have very large effect sizes (-1.9).
-Our analysis could be critiqued as it compares within arm symptom change per trial, therefore effectively breaking randomisation.
-This criticism would apply if our aim were to draw inferences about the efficacy of each arm --- in which case preserving randomisation to balance confounders is critical.
-More importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and therefore respond differently.
-In either case (difference in efficacy vs difference in trial participant profile), the substantial disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
-This is particularly problematic as clinicians as well as policy makers often resort to between-group effect sizes to summarise findings, which our findings make obvious is misleading.
-
-We note that our findings are largely in keeping with those of the NMA, which is designed to preserve the randomisation structure.
-Indeed, in Zhou et al.
-[@zhouComparativeEfficacyAcceptability2020] the estimates for psychotherapy controls, TAU and waitlist conditions favoured placebo (though CIs were broad because these were indirectly estimated), as did estimates for psychodynamic and behavioural therapy.
-CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial [@marchFluoxetineCognitiveBehavioralTherapy2004].
-We note that the Zhou metanalysis, which represents an admirable effort to synthesise the literature, reports on issues that may affect transitivity with tests of incoherence showing significant differences.
-
-Moving beyond comparison between modalities, we examined whether psychotherapy controls are reasonable counterfactuals to receiving treatment.
-An obvious disadvantage of psychotherapy trials is that they are typically unblinded (and hard to blind) yet psychotherapy trials are unlikely to fulfill some other basic conditions of the "all else is equal" assumption.
-In order to test that a psychological treatment is effective per se (e.g.
-because of the specific techniques) rather than because of generic effects (e.g.
-pleasant human contact), aspects such as therapist contact time should be matched.
-Many (24%) psychotherapy RCTs used waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
+Starting with the first question, we found that participants in medication trials are comparable on age but are more likely to be male and have more severe depression compared to those in psychotherapy.
+This indicates that different people enter medication and psychotherapy trials; as these could be effect modifiers, they may violate basic assumptions of comparability.
+
+Severity is particularly important as it may moderate treatment response, with some evidence suggesting that those with higher baseline scores respond more to antidepressants [@stone_response_2022] or that their response to pill placebo is lower.[@bridge_placebo_2009] Other studies argue against severity as a treatment moderator, [@troger_baseline_2024, @weitz_baseline_2015] however these are within people who have chosen to be in the particular trial and modality.
+Moreover, severity may represent different subtypes in terms of course of depression and real-life outcomes.[@lamers_six-year_2016, @simmonds-buckley_depression_2021]
+
+We then asked whether trial design conditions are comparable between modalities.
+Medication trials were more likely to be multi-site than their psychotherapy counterparts: 93% of medication RCTs were multisite compared to 54% of psychotherapy RCTs.
+Multisite trials are associated with higher pill placebo response,[@bridge_placebo_2009] and are less common in publicly-funded trials which show lower pill placebo efficacy.[@dechartres_single-center_2011, [@meister_placebo_2020] This aligns with medication trials being more frequently funded by pharmaceutical companies (68% in Zhou [@zhou_comparative_2020]), which can introduce bias in the RCT.
+ However, in single-site trials, principal investigators are often intellectually invested in the treatment (in psychotherapy these are often treatments developed by the PI); this is in stark contrast to the incentive structure in multi-site trials where the number of recruited participants is the primary unit of reimbursement.
+Indeed, concerns about allegiance bias in psychotherapy trials have been raised previously.[@dragioti_disclosure_2015] Psychotherapy trials also tend to receive higher bias ratings compared to medication trials (e.g.
+78% against 20% in Zhou \[@zhou_comparative_2020\]), further complicating comparisons.
+
+Second, psychotherapy controls have moderate effect sizes (-0.6) whereas medication controls have very large effect sizes (-1.9).
+Our analysis could be critiqued as it compares withinarm symptom change per trial.
+This criticism applies if our aim were to draw inferences about the efficacy of each arm — where preserving randomisation to balance confounders is critical.
+Importantly, we do not claim that these differences are genuinely due to efficacy differences; they may well be because people who attend psychotherapy and medication trials are different and respond differently.
+In either case, the disparity in the response to control conditions is reason for concern about our ability to draw inferences from comparisons of modalities.
+This is problematic as clinicians and policy-makers often resort to between-group effect sizes to summarise findings, which our findings show is misleading.
+
+Our findings are largely in keeping with those of the NMA,[@zhou_comparative_2020] which is designed to preserve the randomisation structure.
+In Zhou et al., the estimates for psychotherapy controls, TAU and waitlist conditions favoured placebo (though CIs were broad because these were indirectly estimated), as did estimates for psychodynamic and behavioural therapy.
+CBT did not differentiate from placebo, a result that is likely heavily weighted by the results of their direct comparison in the TADS trial.[@march_fluoxetine_2004] It is possible that any intervention that establishes an alliance between participants and providers are equally beneficial,[@cohen_are_2008, @goodyer_cognitive_2017] raising questions about whether specific psychological interventions with highly trained therapists are necessary.
+This should be considered as a null hypothesis against which to test alternatives.
+We note that the Zhou NMA, an admirable effort to synthesise the literature, reports on issues that may affect transitivity with tests of incoherence showing significant differences.
+
+We next examined whether psychotherapy controls are reasonable counterfactuals to receiving treatment.
+An obvious disadvantage of psychotherapy trials is that they are typically unblinded and may be inherently impossible to blind.
+Yet, psychotherapy trials are unlikely to fulfill other basic conditions of the “all else is equal” assumption.
+In order to test that a psychological treatment is effective per se (e.g. because of the specific techniques) rather than because of generic effects (e.g. pleasant human contact), aspects such as therapist contact time should be matched.
+Many (23%) psychotherapy RCTs used waitlist controls, which by definition do not match for hours of therapist contact, and are often associated with disappointment bias.
 TAU and other psychotherapy control conditions varied drastically; 9 RCTs used controls that exactly matched the active arm in total number of contact hours, though several studies used bibliotherapy or online-only control conditions which did not involve any direct therapist contact.
-Importantly, controls were often poorly described, resulting in difficulties quantifying their intensity and hence evaluating their adequacy as counterfactual conditions.
-Overall, there is poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of the efficacy of psychological treatments.
+Importantly, controls were often poorly described, resulting in difficulties in evaluating their adequacy as counterfactual conditions.
+Overall, there is poor matching of control to active treatment conditions in psychotherapy RCTs, with the latter typically featuring considerably more contact hours, which may artificially inflate estimates of efficacy.
 
 Given all of the above, the empirical basis for comparing psychotherapy and medication for adolescent depression is weak, and hence it is difficult to generate guidelines and recommend one treatment over another.
+Alternative reasons for recommending psychotherapy over medication in guidelines (e.g.
+the presumed better side effect profile), should be clearly stated and supported by evidence.
 Indeed, we believe that our findings have several implications for patients, their families, clinicians and policy makers.
 
-First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is a need to revisit guidelines and public information in light of the limitations.
-
-Second, the low quality of psychotherapy control conditions should prompt consideration of how to create fair comparators.
+First, the grounds for comparison between medication and psychotherapy should be seen as shaky, rather than offering confidence, and there is an urgent need to revisit guidelines and public information in light of the limitations.
+
+Second, the overreliance on easy-to-beat control conditions in psychotherapy trials should prompt consideration of how to create fair comparators.
 Investment should be directed into providing rigorous evidence that establishes depression psychotherapies as more efficacious than fair controls.
-There are examples of RCTs where such rigor has been applied (e.g.
-Bolton, 2007; Liddle, 1990; Rohde, 2004) in matching active and control arms on variables such as therapist time and attention, provision of homework, and small group interaction.
-Moreover, there is a place for comparing interventions to TAU, since these represent real-world comparators.
+There are examples of RCTs where such rigor has been applied in matching active and control arms on variables such as therapist time and provision of homework.[@bolton_interventions_2007, @liddle_cognitivebehaviour_1990, @rohde_efficacyeffectiveness_2004] Moreover, there is a place for comparing interventions to TAU since these represent real-world comparators.
 However issues of disappointment bias should be addressed to avoid inflating treatment estimates.
 
-Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials [@delgiovaneCombiningPharmacologicalNonpharmacological2019].
-The first obstacle is the comparability of the populations taking part.
-Head-to-head comparisons of psychotherapy with medication (as done in [@marchFluoxetineCognitiveBehavioralTherapy2004]) are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive [@kingImpactParticipantPhysician2005].
-And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
-
-In summary, the current findings give cause for consternation about the state of the evidence for treatments of youth depression.
-Our data question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
-Returning to our motivating question, the stakeholders, including patients and clinicians, need better evidence on which to base their choices.
+Third, our findings make clear the inherent difficulties of comparing psychotherapy with medication trials.[@del_giovane_combining_2019] The first obstacle is the comparability of the populations taking part.
+Head-to-head comparisons of psychotherapy with medication are more favourable in this regard, yet even so these trials might sample the population of those who are indifferent to which treatment they receive.[@troger_baseline_2024] And even in such a design, difficulties with blinding of the psychotherapy control would have to be overcome to draw valid inferences.
+
+In summary, our results question the state of knowledge about the efficacy of psychotherapies and the extent to which giving them primacy in the treatment of depression is justified and beneficial for young people.
+Returning to our motivating question, stakeholders, including patients and clinicians, need better evidence on which to base their choices.
 
@@
 We conducted a systematic search for medication studies published from 31 May 2015 up to 1 Jan 2021 (i.e.
-after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review).
+after the final search date of Cipriani et al.'s [@cipriani_comparative_2016] review up to the final search date of Cuijpers et al's \[@cuijpers_effects_2021\]).
 We searched PubMed, the Cochrane Central Register of Controlled Trials, Embase, Web of Science, CINAHL, PsycINFO and LiLACS for randomised controlled trials (RCTs) comparing any antidepressant with placebo in the treatment of children and adolescents with a primary diagnosis of major depressive disorder.
-We used the same search terms as Cipriani [@ciprianiComparativeEfficacyTolerability2016] with one additional search term to include only placebo-controlled trials (see below).
+We used the same search terms as Cipriani [@cipriani_comparative_2016] with one additional search term to include only placebo-controlled trials (see below).
 We additionally applied filters to specify our date range, and to exclude reviews and non-human studies.
@@
 
-Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. [@ciprianiComparativeEfficacyTolerability2016].
+Where multiple depression rating scales were used, we selected the best available measure according to the following hierarchy used in Cipriani et al. [@cipriani_comparative_2016].
 
@@
 Please refer to these original meta-analyses for a detailed description of their search strategy and study selection criteria.
-Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpersEffectsPsychologicalTreatments2021] (dataset available at <https://docs.metapsy.org/databases/depression-childadol-psyctr/>).
+Psychotherapy studies were drawn from a systematic review and meta-analysis of randomised trials comparing psychotherapy for youth depression against control conditions [@cuijpers_effects_2021 (dataset available at [@cuijpers_depression_2023]).
 Whilst Cuijpers et al.
-[@cuijpersEffectsPsychologicalTreatments2021] excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
+[@cuijpers_effects_2021] excluded studies for which the primary outcome variable could not be calculated due to missing data, we included these studies and performed the imputations outlined below.
 We also included studies which had data available for other variables in interest, including number of sites or baseline demographics; hence we have more psychotherapy studies included in this review compared to the original meta-analysis.
-Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpersEffectsPsychologicalTreatments2021] literature search.
+Whilst the online database is regularly updated, we chose to exclude studies published after the final date of Cuijpers et al.'s [@cuijpers_effects_2021] literature search.
 We also included three studies from Zhou et al.
-\[\@\] which were not covered in the previous meta-analysis whilst fitting the date range.
-
-Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents [@ciprianiComparativeEfficacyTolerability2016].
-A dataset was made available online though did not include means or standard deviations at baseline or post-test.
+[@zhou_comparative_2020] which were not covered in the previous meta-analysis whilst fitting the date range.
+
+Medication studies were drawn from a network meta-analysis examining the efficacy and tolerability of antidepressants and placebo for major depressive disorder in children and adolescents.[@cipriani_comparative_2016] A dataset was made available online though did not include means or standard deviations at baseline or post-test.
 We were unable to access the full dataset used in this meta-analysis, and hence completed extraction from the included studies ourselves.
@@
 
-We conducted a systematic search for medication studies published after the final search date of Cipriani et al.'s [@ciprianiComparativeEfficacyTolerability2016] review up to the final search date of Cuijpers et al's [@cuijpersEffectsPsychologicalTreatments2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
+We conducted a systematic search for medication studies published after the final search date of Cipriani et al.'s [@cipriani_comparative_2016] review up to the final search date of Cuijpers et al's [@cuijpers_effects_2021] review to ensure we analysed an equivalently up-to-date database of medication trials.
 Please see the Supplemental Materials for further details.
@@
 where, $Mean_{t_{2}}$ and $Mean_{t_{1}}$ refer to the means of the main outcome score at the end and beginning of the intervention respectively and $SD_{t_{2}}$ and $SD_{t_{1}}$ to the respective standard deviations.
-Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook [@higginsChapterChoosingEffect2023], in the following order.
+Where individual studies did not report all data required to calculate the SMD, we imputed missing data according to the methods summarised in the Cochrane Handbook,[@higgins_chapter_2023] in the following order.
 If a study reported the standard error of the mean, the SD was obtained simply by multiplying the SE by the square root of the sample size.
@@
 
-We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives [@inthoutHartungKnappSidikJonkmanMethodRandom2014].
+We used maximum likelihood (ML) to estimate model and applied Hartung-Knapp adjustment to reduce the chance of false positives.[@inthout_hartung-knapp-sidik-jonkman_2014]
 

### 2025-01-20 multilevel_metaregression/extra_material_from_render_test.R
final re-structuring

@@ -1,2933 +1,0 @@
-# Findings
-
-```{r run-metaregressions, warning=FALSE, message = FALSE, echo=FALSE}
-
-# This chunk of code needs to be here because some of the data needed for the included studies summary lives here
-
-# Get Ns, run metareg, prepare graphing ------------------------------------------------------
-
-
-# add a new multilevel variable to the simulated data for the regression
-
-for(i in 1: length(list_df_simulated)){
-  
-list_df_simulated[[i]]$arm_effect_size <- factor(list_df_simulated[[i]]$arm_effect_size)
-  list_df_simulated[[i]] <- list_df_simulated[[i]] %>% 
-    mutate(four_level_var = case_when(psy_or_med == 0 & arm_effect_size == "cohens_d_active" ~ "medication_active",
-                                      psy_or_med == 0 & arm_effect_size == "cohens_d_control" ~ "medication_control",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_active" ~ "psychotherapy_active",
-                                      psy_or_med == 1 & arm_effect_size == "cohens_d_control" ~ "psychotherapy_control")
-    )
-  
-  list_df_simulated[[i]]$four_level_var <- factor(list_df_simulated[[i]]$four_level_var) # turn to factor
-  
-  # relevel so that medication control becomes the reference category for the regression
-#  list_df_simulated[[i]]$four_level_var <- relevel(list_df_simulated[[1]]$four_level_var, ref = "medication_control")
-list_df_simulated[[i]]$four_level_var <-   fct_relevel(list_df_simulated[[i]]$four_level_var,
-                                                       "medication_control",
-                                                       "medication_active", 
-                                                       "psychotherapy_control",
-                                                       "psychotherapy_active")
-}
-
-# check it worked
-# list_df_simulated[[2]] %>% 
-# dplyr:: select(psy_or_med, arm_effect_size, four_level_var)
-
-######## NOW RUN METAREGRESSIONS AND GET Coefficients for 
-# A) the overall sample
-# B) the CBT vs Fluox and Escitalopram sample
-# C) the no WL sample
-# D) clinical levels of depression
-# E) the CDRS only sample
-# E) HAMD sensitivity analysis
-# G) Studies with post SD
[…]
